### 2017-11-01 Maths Notes/C3/C3/C3.tex
Initial upload of all files

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{amssymb}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{mwe}
\usepackage{float}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - C3}
\rfoot{Page \thepage}

\newcommand{\R}{\mathbb{R}}
\pgfplotsset{ytick style={draw=none}}
\pgfplotsset{xtick style={draw=none}}
\renewcommand{\arraystretch}{3}

\begin{document}
\begin{center}
\underline{\huge C3}
\end{center}
\begin{obeylines}

\section{Algebraic fractions}
Any polynomial $F(x)$ can be put in the form:
$F(x)=Q(x)\times$divisor+remainder
Where Q(x) is the quotient
\section{Functions}
\subsection{Range and domain}
The input to a function is the \textbf{Domain}\\
The output from a function is the \textbf{Range}
\subsection{Function mapping}
One-to-one function: One element in the domain maps to one element in the range
Many-to-one function: To elements of the domain maps to one element in the range
Not a function: One input maps to two outputs
\subsection{Mappings to functions by changing the domain}
Consider $y=\sqrt{x}$
If the domain is all the real numbers $x \in \Re$ then it is not a function as values less than 0 don't get mapped anywhere.
The domain must be restricted to $x\geq 0$
\subsection{Combining functions}
$fg(x)$ means apply g to x, then apply f
$f^2(x)$ means $ff(x)$
\subsection{Inverse functions}
The inverse of $f(x)$ is written as $f^{-1}x$
The domain of $f(x)$ is the range of $f^{-1}x$
The range of $f(x)$ is the domain of $f^{-1}x$

Example, find the inverse function of $y=2x^2-7$:
$y+7=2x^2$\\
$\dfrac{y+7}{2}=x^2$\\
$x=\sqrt{\dfrac{y+7}{2}}$\\
$f^{-1}x=\sqrt{\dfrac{y+7}{2}}$\\

When finding the graph of an inverse function, reflect $f(x)$ in the line y=x.

\section{The exponential and log functions}
\subsection{Exponential functions}
Exponential functions are in the form $y=a^x$, graphs of these functions all pass through (0,1) as $a^0=1$ for any value of a.
\subsection{Functions including e}
The function $y=e^x$ is the function where the gradient is identical to the function.
$y=e^x \dfrac{dy}{dx}=e^x$
\newpage
Below is the graph of $y=e^x$
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=0]
\addplot[color=black,domain=-2:2]{exp(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);

\end{axis}
\end{tikzpicture}
$y=e^{-x}$
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=0]
\addplot[color=black, domain=-2:2]{1/exp(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);

\end{axis}
\end{tikzpicture}

$y=e^{2x}$ (black) $y=e^x$ (red)
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=0]
\addplot[color=black,domain=-1:1, ]{e^(2*x)};
\addplot[color=red,domain=-2:2, ]{exp(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);

\end{axis}
\end{tikzpicture}

$y=10e^{-x}$ (black) $y=e^{-x}$ (red)
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=0]
\addplot[color=black,domain=-1:1]{(10*(e^(-x)))};
\addplot[color=red,domain=-1:1]{1/e^(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);

\end{axis}
\end{tikzpicture}

\subsection{Formulas for exponential growth or decay}
Example:
$P=16000e^{-\dfrac{t}{10}}$
Where P is the Price in £s and t is the years from new
\textit{What was the price when new?}
Substitute t=0
$ $
$P=16000e^{-\dfrac{0}{10}}$
$ $
$P=16000 \times 1$
\newpage
\textit{What is the value at 5 years old}
Substitute t=5
$ $
$P=16000e^{-\frac{5}{10}}$
$P=\mathsterling 9704.49$
\textit{What does the model say about the eventual value of the car}
As $t \rightarrow \infty$, $e^{-\frac{t}{10}} \rightarrow \infty$
Therefore $P \rightarrow 16000 \times 0 = 0$
The eventual value is zero.

\subsection{The inverse of the exponential function}
The inverse of $e^x$ is $\log_ex$ (also written as $\ln x$)
Examples:
If $e^x=3$ then $x=\ln3$
If $\ln x=4$ then $x=e^4$
$ $
$y=e^{x}$ (Red) $y=\ln x$ (Black)
\begin{tikzpicture}[scale=0.5]
\begin{axis}
\addplot[color=black,domain=0:4, ]{ln(x)};
\addplot[color=red,domain=-2:2, ]{exp(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);

\end{axis}
\end{tikzpicture}

The function $f(x)=\ln x$ has domain \{$x \in \mathbb{R}$, $x>0$\} and range \{$f(x) \in \mathbb{R}$\}

\section{Numerical methods}
\subsection{Approximations for roots based on graphs}
Approximations for roots can be found graphically by plotting the function and finding where the line crosses the x axis. This value is one of the roots of the function.

If trying to find a range in which a root can be found, substitute the values at the extreme of the range, and if there is a change in sign between the two results, there will be a root in the range.

The exception to this rule is $f(x)=\dfrac{1}{x}$ and transformations of this as there is a discontinuity at x=0. The function changes sign in the interval that includes x=0, but there is not a root.

\subsection{Iteration for finding approximations of roots}
To solve an equation of the form $f(x)=0$ by an iterative method, rearrange $f(x)=0$ into a for $x=g(x)$ and use the iterative formula $x_{n+1}=g(x_n)$.
$ $

Example, find a root of the equation $x^2-4x+1=0$
Re-write as $x=4-\dfrac{1}{x}$

Create the formula $x_{n+1}=4-\dfrac{1}{x_n}$
You get given a rough approximation, $x_0=3$
Substitute
$x_1=4-\dfrac{1}{x_0}$
$x_1=4-\dfrac{1}{3}$
$x_1=\dfrac{11}{3}$
$ $
$x_2=4-\dfrac{1}{\frac{11}{3}}$
$x_2=\dfrac{41}{11}$
Continuing this increases the accuracy of the result.
This may not work and will not converge to a root.
\section{Transforming graphs of functions}
\subsection{$\mathbf{y=|f(x)|}$ Graphs}
The modulus of a number is written as $|a|$, this is the positive numerical value.
When $f(x) \geq 0, |f(x)|=f(x)$
When $f(x)<0, |f(x)|=-f(x)$
$ $

\end{obeylines}

\begin{figure}[H]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.5]
\begin{axis}[]
\addplot[color=red,domain=-4:4, ]{x};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
        \caption{$y=x$}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-4]
\addplot[color=red,domain=-4:4, ]{abs(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}      
        \caption{$y=|x|$}
    \end{minipage}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-10,ymax=10]
\addplot[color=red,domain=-2:3, ]{3*x-2};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
        \caption{$y=3x-2$}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-10,ymax=10]
\addplot[color=red,domain=-2:3,samples=300 ]{abs(3*x-2)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
        \caption{$y=|3x-2|$}
    \end{minipage}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.5]
\begin{axis}
\addplot[color=red,domain=-4:7,samples=500 ]{x^2-3*x-10};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
        \caption{$y=x^2-3x-10$}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-15]
\addplot[color=red,domain=-4:7,samples=500 ]{abs(x^2-3*x-10)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}        
        \caption{$y=|x^2-3x-10|$}
    \end{minipage}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-1]
\addplot[color=red,domain=-360:360,samples=500 ]{sin(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
        \caption{$y=sin(x)$}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-1]
\addplot[color=red,domain=-360:360,samples=500 ]{abs(sin(x))};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}        
        \caption{$y=|sin(x)|$}
    \end{minipage}
\end{figure}

\subsection{$\mathbf{y=f(|x|)}$ Graphs}
To plot the graph of $y=|x|-2$, first sketch the graph of $y=x-2$ for $x \geq  0$:
\\
        \begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-4, xmin=-4, ymax=4, xmax=4]
\addplot[color=red,domain=0:5,samples=100 ]{x-2};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
\\
Then reflect that graph in the y axis
\\
        \begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-4, xmin=-4, ymax=4, xmax=4]
\addplot[color=red,domain=-5:5,samples=100 ]{abs(x)-2};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
\\
Examples:
\begin{figure}[H]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-4,xmin=-4,xmax=4]
\addplot[color=red,domain=0:4,samples=500 ]{4*x-x^3};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
        \caption{$y=4x-x^3$}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-4,xmax=4,xmin=-4]
\addplot[color=red,domain=-4:4,samples=500 ]{4*abs(x)-(abs(x))^3};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}        
        \caption{$y=4|x|-{|x|}^3$}
    \end{minipage}
\end{figure}

\subsection{Graph transformations}
\begin{itemize}
\item $f(x+a)$ - Horizontal translation of $\mathbf{-a}$
\item $f(x)+a$ - Vertical translation of $\mathbf{+a}$
\item $f(ax)$ - Horizontal stretch of scale factor $\mathbf{\frac{1}{a}}$
\item $f(-x)$ - Reflection in the \textbf{y axis}
\item $af(x)$ - Vertical stretch of scale factor $\mathbf{a}$
\item $-f(x)$ - Reflection in the \textbf{x axis}
\end{itemize}
\section{Trigonometry}
\begin{itemize}
\item $\sec\theta=\dfrac{1}{\cos\theta}$
\item $\csc\theta=\dfrac{1}{\sin\theta}=cosec\theta$
\item $\cot\theta=\dfrac{1}{\tan\theta}$
\item $\cot\theta=\dfrac{\cos\theta}{\sin\theta}$
\end{itemize}
\subsection{Graphs of the new functions}
$\sec(x)$
\\
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymax=10,ymin=-10]
\addplot[color=red,domain=-360:360,samples=400,restrict y to domain=-15:15]
{sec(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis 
cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis 
cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
\\
$\csc(x)$
\\
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymax=10,ymin=-10]
\addplot[color=red,domain=-360:360,samples=101,unbounded coords=jump]{cosec(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
\\
$\cot(x)$
\\
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymax=10,ymin=-10]
\addplot[color=red,domain=-360:360,samples=101,unbounded coords=jump]{cot(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
\subsection{New identities}
\begin{itemize}
\item $1+\tan^2\theta=\sec^2\theta$
\item $1+\cot^2\theta=\csc^2\theta$
\end{itemize}
\subsection{Graphs of inverse functions}
$y=\arcsin(x)$
\\
\begin{tikzpicture}
  \begin{axis}[domain = -1:1, samples = 100,scale=0.5]
    \addplot[color = red]  {asin(x)/180*pi};
      \end{axis}
\end{tikzpicture}
\\
$y=\arccos(x)$
\\
\begin{tikzpicture}
  \begin{axis}[domain = -1:1, samples = 100,scale=0.5]
    \addplot[color = red]  {acos(x)/180*pi};
      \end{axis}
\end{tikzpicture}
\\
$y=\arctan(x)$
\\
\begin{tikzpicture}
  \begin{axis}[domain = -1:1, samples = 100,scale=0.5]
    \addplot[color = red]  {atan(x)/180*pi};
      \end{axis}
\end{tikzpicture}
\section{Further trigonometric identities and their applications}
\begin{itemize}
\item $\sin(a\pm b)\equiv\sin A\sin B\pm\cos A\sin B$
\item $\cos(a\pm b)\equiv\cos A\cos B\mp\sin A\sin B$
\item $\tan(a\pm b)\equiv\dfrac{\tan A\pm\tan B}{1\mp\tan A\tan B}$
\end{itemize}
\subsection{Double angle formulae}
\begin{itemize}
\item $\sin 2A\equiv 2\sin A\cos A$
\item $\cos 2A\equiv\cos^2A-\sin^2A\equiv 2\cos^2A-1\equiv 1-2\sin^2A$
\item $\tan 2A\equiv\dfrac{2\tan A}{1-\tan^2A}$
\end{itemize}
\subsection{The R formula}
For positive values of \textit{a} and \textit{b}
\\
$a\sin\theta\pm b\cos\theta$ can be expressed in the form $R\sin(\theta\pm\alpha)$, where $0<\alpha<90$
\\
$a\cos\theta\pm b\sin\theta$ can be expressed in the form $R\cos(\theta\mp\alpha)$, where $0<\alpha<90$ 
\\
$R\cos\alpha=a$, $R\sin\alpha=b$
\\
$R=\sqrt{a^2+b^2}$
\\
\section{Differentiation}
\subsection{The chain rule}
If $y=[f(x)]^n$ then $\dfrac{dy}{dx}=n[f(x)]^{n-1}f'x)$
\\
If $y=f[g(x)]$ then $\dfrac{dy}{dx}=f'[g(x)]g'(x)$
\\
\textbf{Example}
\\
$f(x)=3x^4+x$
\\
$f'(x)=12x^3+1$
\\
$\dfrac{dy}{dx}=5(3x^4+x)^4(12x^2+1)$
\\
\subsubsection{Another form of the chain rule}
$\dfrac{dy}{dx}=\dfrac{dy}{du}\times\dfrac{du}{dx}$
\\
\textbf{Example}
\\
$y=(x^2-7x)^4$
\\
$u=(x^2-7x)^4$
\\
$y=u^4$
\\
$\dfrac{du}{dx}=2x-7$\\
$\dfrac{dy}{du}=4u^3$\\
\textit{Using the chain rule:}\\
$\dfrac{dy}{dx}=4u^3\times(2x-7)$\\
$\dfrac{dy}{dx}=4(2x-7)(x^2-7x)^3$\\
\subsection{The product rule}
The product rule is used to differentiate the product of two functions.
\\
If $y=uv$ then $\dfrac{dy}{dx}=u\dfrac{dv}{dx}+v\dfrac{du}{dx}$
\\
\textbf{Example}:\\
$f(x)=x^2\sqrt{3x-1}$\\
$u=x^2$, $v=(3x-1)^{\frac{1}{2}}$\\
$\dfrac{du}{dx}=2x$ and $\dfrac{dv}{dx}=\dfrac{3}{2}(3x-1)^{-\frac{1}{2}}$\\
$f'(x)=x^2\times\frac{3}{2}(3x-1)^{-\frac{1}{2}}+\sqrt{3x-1}\times 2x$\\
$f'(x)=\dfrac{15x^2-4x}{2\sqrt{3x-1}}$\\
$f'(x)=\dfrac{x(15x-4)}{2\sqrt{3x-1}}$\\
\subsection{The quotient rule}
\
If $y=\dfrac{u(x)}{v(x)}$ then $\dfrac{dy}{dx}=\dfrac{v\dfrac{du}{dx}-u\dfrac{dv}{dx}}{v^2}$\\
\textbf{Example}\\
$y=\dfrac{x}{2x+5}$\\
$u=x, v=2x+5$\\
$\dfrac{du}{dx}=1$, $\dfrac{dv}{dx}=2$\\
$\dfrac{dy}{dx}=\dfrac{(2x+5)\times1-x\times2}{(2x+5)^2}$\\
$\dfrac{dy}{dx}=\dfrac{5}{(2x+5)^2}$\\
\subsection{The exponential function}
If $y=e^x$ then $\dfrac{dy}{dx}=e^x$\\
If $y=e^{f(x)}$ then $\dfrac{dy}{dx}=f'(x)e^{f(x)}$\\
\textbf{Example}\\
$y=e^{2x+3}$\\
$\dfrac{dy}{dx}2x+3=2$\\
$\dfrac{dy}{dx}e^{2x+3}=2e^{2x+3}$\\
\subsection{The logarithmic function}
If $y=\ln(x)$ then $\dfrac{dy}{dx}=\dfrac{1}{x}$\\
If $y=\ln[f(x)]$ then $\dfrac{dy}{dx}=\dfrac{f'(x)}{f(x)}$\\
\textbf{Example}\\
$y=\ln(6x-1)$\\
$\dfrac{dy}{dx}6x-1=6$\\
$\dfrac{dy}{dx}\ln(6x-1)=\dfrac{6}{6x-1}$
\subsection{Trig functions}
\subsubsection{Sin}
If $y=\sin(x)$ then $\dfrac{dy}{dx}=\cos(x)$\\
If $y=\sin f(x)$ then $\dfrac{dy}{dx}=f'(x)\cos f(x)$
\subsubsection{Cos}
If $y=\cos(x)$ then $\dfrac{dy}{dx}=-\sin(x)$\\
If $y=\cos f(x)$ then $\dfrac{dy}{dx}=-f'(x)\sin f(x)$\\
\subsubsection{Tan}
If $y=\tan(x)$ then $\dfrac{dy}{dx}=\sec^2(x)$\\
If $y=\tan f(x)$ then $\dfrac{dy}{dx}=f'(x)\sec^2f(x)$\\
\subsubsection{Csc}
If $y=\csc(x)$ then $\dfrac{dy}{dx}=-\csc(x)\cot(x)$\\
If $y=\csc f(x)$ then $\dfrac{dy}{dx}=-f'(x)\csc f(x)\cot f(x)$\\
\subsubsection{Sec}
If $y=\sec(x)$ then $\dfrac{dy}{dx}=\sec(x)\tan(x)$\\
If $y=\sec f(x)$ then $\dfrac{dy}{dx}=f'(x)\sec f(x)\tan f(x)$\\
\subsubsection{Cot}
If $y=\cot(x)$ then $\dfrac{dy}{dx}=-\csc^2(x)$\\
If $y=\cot f(x)$ then $\dfrac{dy}{dx}=-f'(x)\csc^2f(x)$\\
\newpage
\begin{center}
\underline{\huge Differentiation Table}
\end{center}

\begin{center}

\begin{Large}

\begin{tabular}{|c|c|}
 \hline
 $y$&$\dfrac{dy}{dx}$\\
 \hline
 $[f(x)]^n$&$n(f(x))^{n-1}f'(x)$\\
 \hline
 $uv$&$u\dfrac{dv}{dx}+v\dfrac{du}{dx}$\\
 \hline
 $\dfrac{f(x)}{g(x)}$&$\dfrac{f'(x)g(x)-f(x)g'(x)}{g(x)^2}$\\
 \hline
 $e^{f(x)}$&$f'(x)e^{f(x)}$\\
 \hline
 $\ln|f(x)|$&$\dfrac{f'(x)}{f(x)}$\\
 \hline
 $y=\sin f(x)$&$\dfrac{dy}{dx}=f'(x)\cos f(x)$\\
 \hline
 $y=\cos f(x)$&$\dfrac{dy}{dx}=-f'(x)\sin f(x)$\\
 \hline
 $y=\tan f(x)$&$\dfrac{dy}{dx}=f'(x)\sec^2f(x)$\\
 \hline
 $y=\csc f(x)$&$\dfrac{dy}{dx}=-f'(x)\csc f(x)\cot f(x)$\\
 \hline
 $y=\sec f(x)$&$\dfrac{dy}{dx}=f'(x)\sec f(x)\tan f(x)$\\
 \hline
 $y=\cot f(x)$&$\dfrac{dy}{dx}=-f'(x)\csc^2f(x)$\\
 \hline
\end{tabular}
\end{Large}
\end{center}

\end{document}

### 2017-11-01 Maths Notes/C4/Coordinate Geometry/Coordinate Geometry.tex
Initial upload of all files

--- 2017-11-01 Maths Notes/C3/C3/C3.tex
@@
 \usepackage{float}
+\usepackage{polynom}
 
@@
 \rhead{Sam Robbins 13SE}
-\lhead{A Level Maths - C3}
+\lhead{A Level Maths - C4}
 \rfoot{Page \thepage}
@@
 \pgfplotsset{xtick style={draw=none}}
-\renewcommand{\arraystretch}{3}
 
@@
 \begin{center}
-\underline{\huge C3}
+\underline{\huge Coordinate Geometry}
 \end{center}
-\begin{obeylines}
-
-\section{Algebraic fractions}
-Any polynomial $F(x)$ can be put in the form:
-$F(x)=Q(x)\times$divisor+remainder
-Where Q(x) is the quotient
-\section{Functions}
-\subsection{Range and domain}
-The input to a function is the \textbf{Domain}\\
-The output from a function is the \textbf{Range}
-\subsection{Function mapping}
-One-to-one function: One element in the domain maps to one element in the range
-Many-to-one function: To elements of the domain maps to one element in the range
-Not a function: One input maps to two outputs
-\subsection{Mappings to functions by changing the domain}
-Consider $y=\sqrt{x}$
-If the domain is all the real numbers $x \in \Re$ then it is not a function as values less than 0 don't get mapped anywhere.
-The domain must be restricted to $x\geq 0$
-\subsection{Combining functions}
-$fg(x)$ means apply g to x, then apply f
-$f^2(x)$ means $ff(x)$
-\subsection{Inverse functions}
-The inverse of $f(x)$ is written as $f^{-1}x$
-The domain of $f(x)$ is the range of $f^{-1}x$
-The range of $f(x)$ is the domain of $f^{-1}x$
-
-Example, find the inverse function of $y=2x^2-7$:
-$y+7=2x^2$\\
-$\dfrac{y+7}{2}=x^2$\\
-$x=\sqrt{\dfrac{y+7}{2}}$\\
-$f^{-1}x=\sqrt{\dfrac{y+7}{2}}$\\
-
-When finding the graph of an inverse function, reflect $f(x)$ in the line y=x.
-
-\section{The exponential and log functions}
-\subsection{Exponential functions}
-Exponential functions are in the form $y=a^x$, graphs of these functions all pass through (0,1) as $a^0=1$ for any value of a.
-\subsection{Functions including e}
-The function $y=e^x$ is the function where the gradient is identical to the function.
-$y=e^x \dfrac{dy}{dx}=e^x$
-\newpage
-Below is the graph of $y=e^x$
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=0]
-\addplot[color=black,domain=-2:2]{exp(x)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-
-\end{axis}
-\end{tikzpicture}
-$y=e^{-x}$
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=0]
-\addplot[color=black, domain=-2:2]{1/exp(x)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-
-\end{axis}
-\end{tikzpicture}
-
-$y=e^{2x}$ (black) $y=e^x$ (red)
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=0]
-\addplot[color=black,domain=-1:1, ]{e^(2*x)};
-\addplot[color=red,domain=-2:2, ]{exp(x)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-
-\end{axis}
-\end{tikzpicture}
-
-$y=10e^{-x}$ (black) $y=e^{-x}$ (red)
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=0]
-\addplot[color=black,domain=-1:1]{(10*(e^(-x)))};
-\addplot[color=red,domain=-1:1]{1/e^(x)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-
-\end{axis}
-\end{tikzpicture}
-
-\subsection{Formulas for exponential growth or decay}
-Example:
-$P=16000e^{-\dfrac{t}{10}}$
-Where P is the Price in £s and t is the years from new
-\textit{What was the price when new?}
-Substitute t=0
-$ $
-$P=16000e^{-\dfrac{0}{10}}$
-$ $
-$P=16000 \times 1$
-\newpage
-\textit{What is the value at 5 years old}
-Substitute t=5
-$ $
-$P=16000e^{-\frac{5}{10}}$
-$P=\mathsterling 9704.49$
-\textit{What does the model say about the eventual value of the car}
-As $t \rightarrow \infty$, $e^{-\frac{t}{10}} \rightarrow \infty$
-Therefore $P \rightarrow 16000 \times 0 = 0$
-The eventual value is zero.
-
-\subsection{The inverse of the exponential function}
-The inverse of $e^x$ is $\log_ex$ (also written as $\ln x$)
-Examples:
-If $e^x=3$ then $x=\ln3$
-If $\ln x=4$ then $x=e^4$
-$ $
-$y=e^{x}$ (Red) $y=\ln x$ (Black)
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}
-\addplot[color=black,domain=0:4, ]{ln(x)};
-\addplot[color=red,domain=-2:2, ]{exp(x)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-
-\end{axis}
-\end{tikzpicture}
-
-The function $f(x)=\ln x$ has domain \{$x \in \mathbb{R}$, $x>0$\} and range \{$f(x) \in \mathbb{R}$\}
-
-\section{Numerical methods}
-\subsection{Approximations for roots based on graphs}
-Approximations for roots can be found graphically by plotting the function and finding where the line crosses the x axis. This value is one of the roots of the function.
-
-If trying to find a range in which a root can be found, substitute the values at the extreme of the range, and if there is a change in sign between the two results, there will be a root in the range.
-
-The exception to this rule is $f(x)=\dfrac{1}{x}$ and transformations of this as there is a discontinuity at x=0. The function changes sign in the interval that includes x=0, but there is not a root.
-
-\subsection{Iteration for finding approximations of roots}
-To solve an equation of the form $f(x)=0$ by an iterative method, rearrange $f(x)=0$ into a for $x=g(x)$ and use the iterative formula $x_{n+1}=g(x_n)$.
-$ $
-
-Example, find a root of the equation $x^2-4x+1=0$
-Re-write as $x=4-\dfrac{1}{x}$
-
-Create the formula $x_{n+1}=4-\dfrac{1}{x_n}$
-You get given a rough approximation, $x_0=3$
-Substitute
-$x_1=4-\dfrac{1}{x_0}$
-$x_1=4-\dfrac{1}{3}$
-$x_1=\dfrac{11}{3}$
-$ $
-$x_2=4-\dfrac{1}{\frac{11}{3}}$
-$x_2=\dfrac{41}{11}$
-Continuing this increases the accuracy of the result.
-This may not work and will not converge to a root.
-\section{Transforming graphs of functions}
-\subsection{$\mathbf{y=|f(x)|}$ Graphs}
-The modulus of a number is written as $|a|$, this is the positive numerical value.
-When $f(x) \geq 0, |f(x)|=f(x)$
-When $f(x)<0, |f(x)|=-f(x)$
-$ $
-
-\end{obeylines}
-
-\begin{figure}[H]
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.5]
-\begin{axis}[]
-\addplot[color=red,domain=-4:4, ]{x};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}
-        \caption{$y=x$}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=-4]
-\addplot[color=red,domain=-4:4, ]{abs(x)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}      
-        \caption{$y=|x|$}
-    \end{minipage}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=-10,ymax=10]
-\addplot[color=red,domain=-2:3, ]{3*x-2};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}
-        \caption{$y=3x-2$}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=-10,ymax=10]
-\addplot[color=red,domain=-2:3,samples=300 ]{abs(3*x-2)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}
-        \caption{$y=|3x-2|$}
-    \end{minipage}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.5]
-\begin{axis}
-\addplot[color=red,domain=-4:7,samples=500 ]{x^2-3*x-10};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}
-        \caption{$y=x^2-3x-10$}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=-15]
-\addplot[color=red,domain=-4:7,samples=500 ]{abs(x^2-3*x-10)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}        
-        \caption{$y=|x^2-3x-10|$}
-    \end{minipage}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=-1]
-\addplot[color=red,domain=-360:360,samples=500 ]{sin(x)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}
-        \caption{$y=sin(x)$}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=-1]
-\addplot[color=red,domain=-360:360,samples=500 ]{abs(sin(x))};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}        
-        \caption{$y=|sin(x)|$}
-    \end{minipage}
-\end{figure}
-
-\subsection{$\mathbf{y=f(|x|)}$ Graphs}
-To plot the graph of $y=|x|-2$, first sketch the graph of $y=x-2$ for $x \geq  0$:
+\section{Parametric equations}
+In parametric equations, coordinates x and y are expressed as functions.\\
+$x=f(t)$ and $y=g(t)$ where t is the independent variable (called a parameter)
+\subsection{Converting parametric equations into Cartesian form}
+\textbf{Example 1}\\
+$x=2t$\\
+$y=t^2$\\
 \\
-        \begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=-4, xmin=-4, ymax=4, xmax=4]
-\addplot[color=red,domain=0:5,samples=100 ]{x-2};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}
+$t=\dfrac{x}{2}$\\
 \\
-Then reflect that graph in the y axis
+$y=\frac{1}{4}x^2$\\
 \\
-        \begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=-4, xmin=-4, ymax=4, xmax=4]
-\addplot[color=red,domain=-5:5,samples=100 ]{abs(x)-2};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}
+\textbf{Example 2}\\
+$x=\sin(t)+2$\\
+$y=\cos(t)-3$\\
 \\
-Examples:
-\begin{figure}[H]
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=-4,xmin=-4,xmax=4]
-\addplot[color=red,domain=0:4,samples=500 ]{4*x-x^3};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}
-        \caption{$y=4x-x^3$}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymin=-4,xmax=4,xmin=-4]
-\addplot[color=red,domain=-4:4,samples=500 ]{4*abs(x)-(abs(x))^3};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}        
-        \caption{$y=4|x|-{|x|}^3$}
-    \end{minipage}
-\end{figure}
-
-\subsection{Graph transformations}
-\begin{itemize}
-\item $f(x+a)$ - Horizontal translation of $\mathbf{-a}$
-\item $f(x)+a$ - Vertical translation of $\mathbf{+a}$
-\item $f(ax)$ - Horizontal stretch of scale factor $\mathbf{\frac{1}{a}}$
-\item $f(-x)$ - Reflection in the \textbf{y axis}
-\item $af(x)$ - Vertical stretch of scale factor $\mathbf{a}$
-\item $-f(x)$ - Reflection in the \textbf{x axis}
-\end{itemize}
-\section{Trigonometry}
-\begin{itemize}
-\item $\sec\theta=\dfrac{1}{\cos\theta}$
-\item $\csc\theta=\dfrac{1}{\sin\theta}=cosec\theta$
-\item $\cot\theta=\dfrac{1}{\tan\theta}$
-\item $\cot\theta=\dfrac{\cos\theta}{\sin\theta}$
-\end{itemize}
-\subsection{Graphs of the new functions}
-$\sec(x)$
+$\sin(t)=x-2$\\
+$\cos(t)=y+3$\\
 \\
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymax=10,ymin=-10]
-\addplot[color=red,domain=-360:360,samples=400,restrict y to domain=-15:15]
-{sec(x)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis 
-cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis 
-cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}
+$\sin^2\theta+\cos^2\theta=1$\\
+$(x-2)^2+(y+3)^2=1$
+\section{Parametric differentiation}
+The chain rule can be used to differentiate parametric equations\\
+$\dfrac{dy}{dx}=\dfrac{dy}{dt}\times\dfrac{dt}{dx}$\\
+This can be used to find the gradient of normals and tangents.\\
 \\
-$\csc(x)$
+\textbf{Example}\\
+$x=t^3+t$\\
+$y=t^2+1$\\
 \\
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymax=10,ymin=-10]
-\addplot[color=red,domain=-360:360,samples=101,unbounded coords=jump]{cosec(x)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}
+\textbf{Differentiate the x and y terms}\\
+$\dfrac{dy}{dt}=2t$\\
+$\dfrac{dx}{dt}=3t^2+1$\\
 \\
-$\cot(x)$
+\textbf{Invert the differential of x to fit the formula}\\
+$\dfrac{dt}{dx}=\dfrac{1}{3t^2+1}$\\
 \\
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[ymax=10,ymin=-10]
-\addplot[color=red,domain=-360:360,samples=101,unbounded coords=jump]{cot(x)};
-\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
-\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
-\end{axis}
-\end{tikzpicture}
-\subsection{New identities}
-\begin{itemize}
-\item $1+\tan^2\theta=\sec^2\theta$
-\item $1+\cot^2\theta=\csc^2\theta$
-\end{itemize}
-\subsection{Graphs of inverse functions}
-$y=\arcsin(x)$
-\\
-\begin{tikzpicture}
-  \begin{axis}[domain = -1:1, samples = 100,scale=0.5]
-    \addplot[color = red]  {asin(x)/180*pi};
-      \end{axis}
-\end{tikzpicture}
-\\
-$y=\arccos(x)$
-\\
-\begin{tikzpicture}
-  \begin{axis}[domain = -1:1, samples = 100,scale=0.5]
-    \addplot[color = red]  {acos(x)/180*pi};
-      \end{axis}
-\end{tikzpicture}
-\\
-$y=\arctan(x)$
-\\
-\begin{tikzpicture}
-  \begin{axis}[domain = -1:1, samples = 100,scale=0.5]
-    \addplot[color = red]  {atan(x)/180*pi};
-      \end{axis}
-\end{tikzpicture}
-\section{Further trigonometric identities and their applications}
-\begin{itemize}
-\item $\sin(a\pm b)\equiv\sin A\sin B\pm\cos A\sin B$
-\item $\cos(a\pm b)\equiv\cos A\cos B\mp\sin A\sin B$
-\item $\tan(a\pm b)\equiv\dfrac{\tan A\pm\tan B}{1\mp\tan A\tan B}$
-\end{itemize}
-\subsection{Double angle formulae}
-\begin{itemize}
-\item $\sin 2A\equiv 2\sin A\cos A$
-\item $\cos 2A\equiv\cos^2A-\sin^2A\equiv 2\cos^2A-1\equiv 1-2\sin^2A$
-\item $\tan 2A\equiv\dfrac{2\tan A}{1-\tan^2A}$
-\end{itemize}
-\subsection{The R formula}
-For positive values of \textit{a} and \textit{b}
-\\
-$a\sin\theta\pm b\cos\theta$ can be expressed in the form $R\sin(\theta\pm\alpha)$, where $0<\alpha<90$
-\\
-$a\cos\theta\pm b\sin\theta$ can be expressed in the form $R\cos(\theta\mp\alpha)$, where $0<\alpha<90$ 
-\\
-$R\cos\alpha=a$, $R\sin\alpha=b$
-\\
-$R=\sqrt{a^2+b^2}$
-\\
-\section{Differentiation}
-\subsection{The chain rule}
-If $y=[f(x)]^n$ then $\dfrac{dy}{dx}=n[f(x)]^{n-1}f'x)$
-\\
-If $y=f[g(x)]$ then $\dfrac{dy}{dx}=f'[g(x)]g'(x)$
-\\
-\textbf{Example}
-\\
-$f(x)=3x^4+x$
-\\
-$f'(x)=12x^3+1$
-\\
-$\dfrac{dy}{dx}=5(3x^4+x)^4(12x^2+1)$
-\\
-\subsubsection{Another form of the chain rule}
-$\dfrac{dy}{dx}=\dfrac{dy}{du}\times\dfrac{du}{dx}$
-\\
-\textbf{Example}
-\\
-$y=(x^2-7x)^4$
-\\
-$u=(x^2-7x)^4$
-\\
-$y=u^4$
-\\
-$\dfrac{du}{dx}=2x-7$\\
-$\dfrac{dy}{du}=4u^3$\\
-\textit{Using the chain rule:}\\
-$\dfrac{dy}{dx}=4u^3\times(2x-7)$\\
-$\dfrac{dy}{dx}=4(2x-7)(x^2-7x)^3$\\
-\subsection{The product rule}
-The product rule is used to differentiate the product of two functions.
-\\
-If $y=uv$ then $\dfrac{dy}{dx}=u\dfrac{dv}{dx}+v\dfrac{du}{dx}$
-\\
-\textbf{Example}:\\
-$f(x)=x^2\sqrt{3x-1}$\\
-$u=x^2$, $v=(3x-1)^{\frac{1}{2}}$\\
-$\dfrac{du}{dx}=2x$ and $\dfrac{dv}{dx}=\dfrac{3}{2}(3x-1)^{-\frac{1}{2}}$\\
-$f'(x)=x^2\times\frac{3}{2}(3x-1)^{-\frac{1}{2}}+\sqrt{3x-1}\times 2x$\\
-$f'(x)=\dfrac{15x^2-4x}{2\sqrt{3x-1}}$\\
-$f'(x)=\dfrac{x(15x-4)}{2\sqrt{3x-1}}$\\
-\subsection{The quotient rule}
-\
-If $y=\dfrac{u(x)}{v(x)}$ then $\dfrac{dy}{dx}=\dfrac{v\dfrac{du}{dx}-u\dfrac{dv}{dx}}{v^2}$\\
-\textbf{Example}\\
-$y=\dfrac{x}{2x+5}$\\
-$u=x, v=2x+5$\\
-$\dfrac{du}{dx}=1$, $\dfrac{dv}{dx}=2$\\
-$\dfrac{dy}{dx}=\dfrac{(2x+5)\times1-x\times2}{(2x+5)^2}$\\
-$\dfrac{dy}{dx}=\dfrac{5}{(2x+5)^2}$\\
-\subsection{The exponential function}
-If $y=e^x$ then $\dfrac{dy}{dx}=e^x$\\
-If $y=e^{f(x)}$ then $\dfrac{dy}{dx}=f'(x)e^{f(x)}$\\
-\textbf{Example}\\
-$y=e^{2x+3}$\\
-$\dfrac{dy}{dx}2x+3=2$\\
-$\dfrac{dy}{dx}e^{2x+3}=2e^{2x+3}$\\
-\subsection{The logarithmic function}
-If $y=\ln(x)$ then $\dfrac{dy}{dx}=\dfrac{1}{x}$\\
-If $y=\ln[f(x)]$ then $\dfrac{dy}{dx}=\dfrac{f'(x)}{f(x)}$\\
-\textbf{Example}\\
-$y=\ln(6x-1)$\\
-$\dfrac{dy}{dx}6x-1=6$\\
-$\dfrac{dy}{dx}\ln(6x-1)=\dfrac{6}{6x-1}$
-\subsection{Trig functions}
-\subsubsection{Sin}
-If $y=\sin(x)$ then $\dfrac{dy}{dx}=\cos(x)$\\
-If $y=\sin f(x)$ then $\dfrac{dy}{dx}=f'(x)\cos f(x)$
-\subsubsection{Cos}
-If $y=\cos(x)$ then $\dfrac{dy}{dx}=-\sin(x)$\\
-If $y=\cos f(x)$ then $\dfrac{dy}{dx}=-f'(x)\sin f(x)$\\
-\subsubsection{Tan}
-If $y=\tan(x)$ then $\dfrac{dy}{dx}=\sec^2(x)$\\
-If $y=\tan f(x)$ then $\dfrac{dy}{dx}=f'(x)\sec^2f(x)$\\
-\subsubsection{Csc}
-If $y=\csc(x)$ then $\dfrac{dy}{dx}=-\csc(x)\cot(x)$\\
-If $y=\csc f(x)$ then $\dfrac{dy}{dx}=-f'(x)\csc f(x)\cot f(x)$\\
-\subsubsection{Sec}
-If $y=\sec(x)$ then $\dfrac{dy}{dx}=\sec(x)\tan(x)$\\
-If $y=\sec f(x)$ then $\dfrac{dy}{dx}=f'(x)\sec f(x)\tan f(x)$\\
-\subsubsection{Cot}
-If $y=\cot(x)$ then $\dfrac{dy}{dx}=-\csc^2(x)$\\
-If $y=\cot f(x)$ then $\dfrac{dy}{dx}=-f'(x)\csc^2f(x)$\\
-\newpage
-\begin{center}
-\underline{\huge Differentiation Table}
-\end{center}
-
-\begin{center}
-
-\begin{Large}
-
-\begin{tabular}{|c|c|}
- \hline
- $y$&$\dfrac{dy}{dx}$\\
- \hline
- $[f(x)]^n$&$n(f(x))^{n-1}f'(x)$\\
- \hline
- $uv$&$u\dfrac{dv}{dx}+v\dfrac{du}{dx}$\\
- \hline
- $\dfrac{f(x)}{g(x)}$&$\dfrac{f'(x)g(x)-f(x)g'(x)}{g(x)^2}$\\
- \hline
- $e^{f(x)}$&$f'(x)e^{f(x)}$\\
- \hline
- $\ln|f(x)|$&$\dfrac{f'(x)}{f(x)}$\\
- \hline
- $y=\sin f(x)$&$\dfrac{dy}{dx}=f'(x)\cos f(x)$\\
- \hline
- $y=\cos f(x)$&$\dfrac{dy}{dx}=-f'(x)\sin f(x)$\\
- \hline
- $y=\tan f(x)$&$\dfrac{dy}{dx}=f'(x)\sec^2f(x)$\\
- \hline
- $y=\csc f(x)$&$\dfrac{dy}{dx}=-f'(x)\csc f(x)\cot f(x)$\\
- \hline
- $y=\sec f(x)$&$\dfrac{dy}{dx}=f'(x)\sec f(x)\tan f(x)$\\
- \hline
- $y=\cot f(x)$&$\dfrac{dy}{dx}=-f'(x)\csc^2f(x)$\\
- \hline
-\end{tabular}
-\end{Large}
-\end{center}
+\textbf{Multiply together to make one fraction}\\
+$\dfrac{dy}{dx}=\dfrac{2t}{3t^2+1}$
 

### 2017-11-01 Maths Notes/D2/Transportation problems/Transportation problems.tex
Initial upload of all files

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{enumerate}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}	
\newcommand{\cred}[1]{\color{red}#1}
\newcommand{\cblue}[1]{\color{blue}#1}
\newcommand{\cgreen}[1]{\color{green}#1}
\hyphenpenalty=10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - D2}
\rfoot{Page \thepage}
\begin{document}
\begin{center}
\underline{\huge Transportation Problems}
\end{center}
\begin{obeylines}
\section{Terminology used in describing and modelling the transportation problem}
In order to solve transportation problems you need to consider:
\begin{itemize}
\item The capacity of each of the supply points - The quantity of goods that can be produced at each factory or held at each warehouse. Called \textbf{supply} or \textbf{stock}
\item The amount required at each of the demand points - The quantity of goods that are needed at each shop or by each customer. Called \textbf{demand} or \textbf{destination}
\item The unit cost of transporting goods from the supply points to the demand points
\end{itemize}
\subsection{Solving the transportation problem}
\begin{enumerate}
\item Find an initial solution that uses all the stock and meets all the demands
\item Calculate the total cost of this solution and see if it can be reduced by using routes not currently in the solution (if not then optimal)
\item If the cost can be reduced by a different route, put as many units across it as possible
\item Check to see if optimal, if not, go to 3
\item When no further savings are possible, an optimal solution has been found
\end{enumerate}
\section{Finding an initial solution to the transportation problem}
A method called the \textbf{north-west corner method} is used.
First, create a table with rows for source and columns for destination. Add demand at the bottom of each column and stock at the end of each row.
\begin{enumerate}
\item At the top left-hand corner of the table, allocate the maximum stock to meet demand
\item If stock is emptied, move down 1 and allocate
\item If demand is met, move 1 right and allocate
\item When all the stock is assigned and all the demands met, stop
\end{enumerate}
\end{obeylines}
\subsection{Example}
\textbf{What would be given in the question:}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&Depot W&Depot X&Depot Y&Depot Z&Stock\\
\hline
Supplier A&180&110&130&290&14\\
\hline
Supplier B&190&250&150&280&16\\
\hline
Supplier C&240&270&190&120&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\textbf{Set up the table with stock and demand}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&&&&&14\\
\hline
B&&&&&16\\
\hline
C&&&&&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\newpage
\textbf{Start by filling the top left corner}\\
11 is put here as it is the demand for \textbf{W} but does not exceed the stock of \textbf{A}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&11&&&&14\\
\hline
B&&&&&16\\
\hline
C&&&&&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\textbf{Move 1 right as the demand has been satisfied}\\
3 is put here as it is the remainder of the stock of \textbf{A} and does not exceed the demand of \textbf{X}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&11&3&&&14\\
\hline
B&&&&&16\\
\hline
C&&&&&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\textbf{Move 1 down as the stock of A has been exhausted}\\
12 is put here as it satisfies the demand for \textbf{X} but does not exceed the supply of \textbf{B}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&\textcolor{red}{11}&\textcolor{red}{3}&&&14\\
\hline
B&&\textcolor{red}{12}&&&16\\
\hline
C&&&&&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\textbf{Move 1 right as the supply of B has not yet been exhausted}\\
4 is put here as it is the maximum \textbf{B} is able to supply and does not exceed the demand of \textbf{Y}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&\textcolor{red}{11}&\textcolor{red}{3}&&&14\\
\hline
B&&\textcolor{red}{12}&\textcolor{red}{4}&&16\\
\hline
C&&&&&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\textbf{Move 1 down as the stock of B has been exhausted}\\
10 is put this as it meets the demand of \textbf{Y} without exceeding the stock of \textbf{C}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&\textcolor{red}{11}&\textcolor{red}{3}&&&14\\
\hline
B&&\textcolor{red}{12}&\textcolor{red}{4}&&16\\
\hline
C&&&\cred{10}&&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\textbf{Move 1 right as the demand for Y has been met}\\
10 is put here as it meets the demand of \textbf{Z} and exhausts the stock of \textbf{C}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&\textcolor{red}{11}&\textcolor{red}{3}&&&14\\
\hline
B&&\textcolor{red}{12}&\textcolor{red}{4}&&16\\
\hline
C&&&\cred{10}&\cred{10}&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\newpage
The total cost of transportation can then be found by multiplying the value in the square to be transported by the cost of that square.
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&\textcolor{red}{11}$\times180$&\textcolor{red}{3}$\times110$&&&14\\
\hline
B&&\textcolor{red}{12}$\times250$&\textcolor{red}{4}$\times150$&&16\\
\hline
C&&&\textcolor{red}{10}$\times190$&\textcolor{red}{10}$\times120$&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
The sum of those multiplications is £9010, the cost of transportation.
\section{Unbalanced transportation problems}
When total supply$>$total demand, the problem is \textbf{unbalanced}\\
For an unbalanced transportation problem, add a dummy demand point with demand chosen to make demand and supply equal. All transportation costs of the dummy point is \textbf{zero}.
\subsection{Example}
\begin{center}
\begin{tabular}{ |c|c|c|c|c| }
\hline
&A&B&C&Supply\\
\hline
X&9&11&10&40\\
\hline
Y&10&8&12&60\\
\hline
Z&12&7&8&50\\
\hline
Demand&50&40&30&\\
\hline
\end{tabular}
\end{center}
Because 40+60+50>50+40+30 the problem is unbalanced.\\
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&A&B&C&D&Supply\\
\hline
X&9&11&10&0&40\\
\hline
Y&10&8&12&0&60\\
\hline
Z&12&7&8&0&50\\
\hline
Demand&50&40&30&30&\\
\hline
\end{tabular}
\end{center}
The problem can then be solved as normal
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&A&B&C&D&Supply\\
\hline
X&\cred{40}&&&&40\\
\hline
Y&\cred{10}&\cred{40}&\cred{10}&&60\\
\hline
Z&&&\cred{20}&\cred{30}&50\\
\hline
Demand&50&40&30&30&\\
\hline
\end{tabular}
\end{center}
\section{Degenerate solutions}
If the number of cells filled in a solution is less than suppliers+demanders-1 then the solution is \textbf{degenerate}.\\
\\
This happens when an entry, other than the last, satisfies both supply and demand at the same time, leading to the selector moving diagonally.\\
\\
The algorithm requires for n+m-1 cells to be used in every solution, so a zero needs to be placed in a currently unused cell.
\newpage
\subsection{Example}
\begin{center}
\begin{tabular}{ |c|c|c|c|c| }
\hline
&A&B&C&Supply\\
\hline
W&10&11&6&30\\
\hline
X&4&5&9&20\\
\hline
Y&3&8&7&35\\
\hline
Z&11&10&9&35\\
\hline
Demand&39&40&50&\\
\hline
\end{tabular}
\end{center}
This then gives the solution:
\begin{center}
\begin{tabular}{ |c|c|c|c|c| }
\hline
&A&B&C&Supply\\
\hline
W&\cred{30}&&&30\\
\hline
X&&\cred{20}&&20\\
\hline
Y&&\cred{20}&\cred{15}&35\\
\hline
Z&&&\cred{35}&35\\
\hline
Demand&39&40&50&\\
\hline
\end{tabular}
\end{center}
The problem with this is that it moves from AW to BX diagonally. This is solved by adding a zero in a place the selector could have moved after AW (BW or AX).
\begin{center}
\begin{tabular}{ |c|c|c|c|c| }
\hline
&A&B&C&Supply\\
\hline
W&\cred{30}&&&30\\
\hline
X&\textcolor{blue}{0}&\cred{20}&&20\\
\hline
Y&&\cred{20}&\cred{15}&35\\
\hline
Z&&&\cred{35}&35\\
\hline
Demand&39&40&50&\\
\hline
\end{tabular}
\end{center}
When doing this don't worry about where the zero goes, it can go in any empty space.
\section{Shadow costs}
Transportation costs are made up of two costs, one for source and one for destination, the cost of using that route is called the \textbf{shadow cost}.\\
\subsection{Description}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&\cred{180}&\cred{110}&&&14\\
\hline
B&&\cred{250}&\cred{150}&&16\\
\hline
C&&&\cred{190}&\cred{120}&20\\
\hline
Demand&11&15&14&10&50\\
\hline
\end{tabular}
\end{center}
Simultaneous equations can then be set up from this, for example:\\
S(A)+D(W)=180\\
S(A)+D(X)=110\\
S(B)+D(X)=250\\
As there are 5 equations and 6 unknowns relative costs need to be used.\\
\subsection{Method}
\begin{enumerate}
\item Set the source cost of the top left corner to zero
\item Move along the row and use \textbf{cost of destination =total cost-cost of supply}
\item When all the costs for that row have been found, move down one row and use the data already found to determine the supply cost
\item Repeat step 2 and step 3 until all costs have been found.
\end{enumerate}
\subsection{Example}
\textbf{Set up a table with space for shadow costs}\\
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c| }
\hline
Shadow costs&&&&&&\\
\hline
&&Depot W&Depot X&Depot Y&Depot Z&Stock\\
\hline
&Supply A&\cred{180}&\cred{110}&&&14\\
\hline
&Supply B&&\cred{250}&\cred{150}&&16\\
\hline
&Supply C&&&\cred{190}&\cred{120}&20\\
\hline
&Demand&11&15&14&10&50\\
\hline
\end{tabular}
\end{center}
\textbf{Set the cost of source for the top left corner to zero and use to fill out the depot cost for the row}\\
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c| }
\hline
Shadow costs&&180&110&&&\\
\hline
&&Depot W&Depot X&Depot Y&Depot Z&Stock\\
\hline
0&Supply A&\cred{180}&\cred{110}&&&14\\
\hline
&Supply B&&\cred{250}&\cred{150}&&16\\
\hline
&Supply C&&&\cred{190}&\cred{120}&20\\
\hline
&Demand&11&15&14&10&50\\
\hline
\end{tabular}
\end{center}
\textbf{Move 1 row down and use filled out values to determine all the values for that row}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c| }
\hline
Shadow costs&&180&110&10&&\\
\hline
&&Depot W&Depot X&Depot Y&Depot Z&Stock\\
\hline
0&Supply A&\cred{180}&\cred{110}&&&14\\
\hline
140&Supply B&&\cred{250}&\cred{150}&&16\\
\hline
&Supply C&&&\cred{190}&\cred{120}&20\\
\hline
&Demand&11&15&14&10&50\\
\hline
\end{tabular}
\end{center}
\textbf{Repeat step above}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c| }
\hline
Shadow costs&&180&110&10&-60&\\
\hline
&&Depot W&Depot X&Depot Y&Depot Z&Stock\\
\hline
0&Supply A&\cred{180}&\cred{110}&&&14\\
\hline
140&Supply B&&\cred{250}&\cred{150}&&16\\
\hline
180&Supply C&&&\cred{190}&\cred{120}&20\\
\hline
&Demand&11&15&14&10&50\\
\hline
\end{tabular}
\end{center}
\textbf{Write all the costs individually}\\
S(A)=0\\
S(B)=140\\
S(C)=180\\
D(W)=180\\
D(X)=110\\
D(Y)=10\\
D(Z)=-60\\
\section{Improvement indices}
Improvement indices look at each unused route and calculate the reduction in cost by using that route.\\
The formula for an improvement index for PX= $\mathbf{I_{PQ}=C(PQ)-S(P)-D(Q)}$\\
The route with the most negative improvement index will be introduced to the solution.\\
The route introduced to the solution is called the \textbf{entering cell} and the route it replaces is called the \textbf{exiting cell}.\\
If there are two equal entering or exiting cells choose either.\\
If there are no negative improvement indices the solution is \textbf{optimal}.
\subsection{Example}
\textbf{Start with the shadow costs}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c| }
\hline
Shadow costs&&180&110&10&-60&\\
\hline
&&Depot W&Depot X&Depot Y&Depot Z&Stock\\
\hline
0&Supply A&\cred{180}&\cred{110}&&&14\\
\hline
140&Supply B&&\cred{250}&\cred{150}&&16\\
\hline
180&Supply C&&&\cred{190}&\cred{120}&20\\
\hline
&Demand&11&15&14&10&50\\
\hline
\end{tabular}
\end{center}
\textbf{Use the formula to calculate improvement indices}\\
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c| }
\hline
Shadow costs&&180&110&10&-60&\\
\hline
&&Depot W&Depot X&Depot Y&Depot Z&Stock\\
\hline
0&Supply A&\cred{0}&\cred{0}&\cblue{120}&\cblue{350}&14\\
\hline
140&Supply B&\cblue{-130}&\cred{0}&\cred{0}&\cblue{200}&16\\
\hline
180&Supply C&\cblue{-120}&\cblue{20}&\cred{0}&\cred{0}&20\\
\hline
&Demand&11&15&14&10&50\\
\hline
\end{tabular}
\end{center}
This shows that BW is the entering cell as it has the lowest improvement index.
\section{Stepping stone method}
The stepping stone method is a method to find a more optimal solution given improvement indices.\\
This looks for a cycle of adjustments, increasing the value in one cell and reducing in the next and so on.
\subsection{Method}
\begin{enumerate}
\item Create a cycle of adjustments with the rules:
\begin{enumerate}
\item Within any row or column there can only be one increasing and one decreasing cell
\item With the exception of the entering cell, adjustments can only be made to filled cells
\end{enumerate}
\item Once the cycle of adjustments has been found, transfer the maximum number of units through this cycle. This will be equal to the smallest number in the decreasing cells to avoid negative units.
\item Adjust the solution to incorporate this solution
\end{enumerate}
\subsection{Example}
\textbf{Start with the initial solution}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&\cblue{11}&\cblue{3}&&&14\\
\hline
B&&\cblue{12}&\cblue{4}&&16\\
\hline
C&&&\cblue{10}&\cblue{10}&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\textbf{Insert a theta in the value with the most negative improvement index}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&\cblue{11}&\cblue{3}&&&14\\
\hline
B&\cgreen{$\theta}$&\cblue{12}&\cblue{4}&&16\\
\hline
C&&&\cblue{10}&\cblue{10}&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\textbf{Subtract theta from AW to keep the demand at W correct. Then add theta to AX to keep the stock at AX correct, finally subtract theta from BX to keep the demand at X correct}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&\cred{$11-\theta$}&\cgreen{$3+\theta$}&&&14\\
\hline
B&\cgreen{$\theta}$&\cred{$12-\theta$}&\cblue{4}&&16\\
\hline
C&&&\cblue{10}&\cblue{10}&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\textbf{Substitute 11 for theta as that is the smallest value in a decreasing cell}
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&\cred{$11-11$}&\cgreen{$3+11$}&&&14\\
\hline
B&\cgreen{$11$}&\cred{$12-11$}&\cblue{4}&&16\\
\hline
C&&&\cblue{10}&\cblue{10}&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
\textbf{Write the improved solution and find the cost}

\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
\hline
&W&X&Y&Z&Stock\\
\hline
A&&\cblue{$14$}&&&14\\
\hline
B&\cblue{$11$}&\cblue{$1$}&\cblue{4}&&16\\
\hline
C&&&\cblue{10}&\cblue{10}&20\\
\hline
Demand&11&15&14&10&50\\ 
\hline
\end{tabular}
\end{center}
The cost of this is £7580, a reduction from the initial solution.\\
\textbf{AW has become empty, meaning it is the exiting cell}\\
\textbf{To find an optimal solution, new shadow costs and improvement indices would need to be found}

\end{document}

### 2017-11-01 Maths Notes/M2/Centres of mass/Centres of mass.tex
Initial upload of all files

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - M2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Centres of mass}
\end{center}
\begin{obeylines}
\section{Centre if mass of a discrete mass distribution}
$\bar{x}=\dfrac{\Sigma m_ix_i}{\Sigma m_i}$\\
$\bar{y}=\dfrac{\Sigma m_iy_i}{\Sigma m_i}$\\
\textbf{Example}\\
\end{obeylines}
\begin{tabular}{|c|c|c|c|}
 \hline
 Mass&$2$&$3$&$2$\\
 \hline
 $x$&2&3&-3\\
 \hline
 $y$&3&6&2\\
 \hline

\end{tabular}
\\
\\
\begin{obeylines}
$\bar{x}=\dfrac{2\times 2+3\times3+2\times-3}{2+3+2}=1$
$\bar{y}=\dfrac{2\times3+3\times6+2\times2}{2+3+2}=4$
\section{Uniform laminae}
For a triangular lamina the centre of mass is $\frac{2}{3}$ along the line from the vertex to the middle of the line opposite.
For a sector of a circle, radius r, where the angle at the centre is $2\alpha$ the centre of mass is $\dfrac{2r\sin\alpha}{3\alpha}$
\section{Rods}
In a circular arc, radius r, where the angle at the centre is $2\alpha$, the centre of mass is $\dfrac{r\sin\alpha}{\alpha}$ away from the centre.
\section{Equilibrium}
To avoid tipping, the lime of action of the weight must be within the side of the lamina in contact with the plane.
If a lamina is suspended from a fixed point, the centre of mass will be vertically below the point of suspension.
Assumptions made in equilibrium calculations:
\begin{itemize}
\item No friction at the point of suspension
\item The mass of each area is uniform
\item The mass is uniform at the join
\end{itemize}

Test

\end{obeylines}

\end{document}

### 2017-11-01 Maths Notes/M2/Collisions/Collisions.tex
Initial upload of all files

--- 2017-11-01 Maths Notes/M2/Centres of mass/Centres of mass.tex
@@
 \begin{center}
-\underline{\huge Centres of mass}
+\underline{\huge Collisions}
 \end{center}
 \begin{obeylines}
-\section{Centre if mass of a discrete mass distribution}
-$\bar{x}=\dfrac{\Sigma m_ix_i}{\Sigma m_i}$\\
-$\bar{y}=\dfrac{\Sigma m_iy_i}{\Sigma m_i}$\\
-\textbf{Example}\\
-\end{obeylines}
-\begin{tabular}{|c|c|c|c|}
- \hline
- Mass&$2$&$3$&$2$\\
- \hline
- $x$&2&3&-3\\
- \hline
- $y$&3&6&2\\
- \hline
-
-\end{tabular}
-\\
-\\
-\begin{obeylines}
-$\bar{x}=\dfrac{2\times 2+3\times3+2\times-3}{2+3+2}=1$
-$\bar{y}=\dfrac{2\times3+3\times6+2\times2}{2+3+2}=4$
-\section{Uniform laminae}
-For a triangular lamina the centre of mass is $\frac{2}{3}$ along the line from the vertex to the middle of the line opposite.
-For a sector of a circle, radius r, where the angle at the centre is $2\alpha$ the centre of mass is $\dfrac{2r\sin\alpha}{3\alpha}$
-\section{Rods}
-In a circular arc, radius r, where the angle at the centre is $2\alpha$, the centre of mass is $\dfrac{r\sin\alpha}{\alpha}$ away from the centre.
-\section{Equilibrium}
-To avoid tipping, the lime of action of the weight must be within the side of the lamina in contact with the plane.
-If a lamina is suspended from a fixed point, the centre of mass will be vertically below the point of suspension.
-Assumptions made in equilibrium calculations:
-\begin{itemize}
-\item No friction at the point of suspension
-\item The mass of each area is uniform
-\item The mass is uniform at the join
-\end{itemize}
-
-Test
+\section{Impulse and momentum}
+Impulse=$mv-mu$=$Ft$\\
+Total momentum before collision=total momentum after\\
+\section{Coefficient of restitution}
+This tells us how well something bounces, it is given the symbol \textbf{e}.\\
+If $e=1$ the ball returns to it's original height\\
+If $e=0$ the ball doesn't bounce\\
+$e=\dfrac{\text{Speed of seperation}}{\text{Speed of approach}}$
 
 \end{obeylines}
-
 \end{document}

### 2017-11-01 Maths Notes/M2/Kinematics/Kinematics.tex
Initial upload of all files

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - M2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Kinematics}
\end{center}
\begin{obeylines}
\section{Horizontal Projections}
For a \textbf{constant speed} use \textbf{$Speed=\dfrac{Distance}{Time}$}

For a \textbf{constant acceleration} use \textbf{SUVAT}

For all projections:
\begin{itemize}
\item Assume air resistance to be zero
\item Resolve horizontal and vertical motion
\item Horizontal - Constant speed
\item Vertical - Constant acceleration

\end{itemize}

\section{Angular projections}
The same as horizontal projections but the initial vertical velocity isn't zero.
Example:
A particle is projected at a speed of $49ms^{-1}$ at an angle of $45 \degree$ above the horizontal.
\textit{What is the time taken for the particle to reach its maximum height?}
\begin{itemize}
\item u=$49\sin45$
\item v=0
\item a=-g
\item t=?
\end{itemize}
$0=49\sin45-gt$
$t=\dfrac{49\sin45}{g}=\dfrac{5\sqrt{2}}{2}\approx3.54$
\textit{What is the maximum height reached?}
\begin{itemize}
\item u=$49\sin45$
\item v=0
\item a=-g
\item s=?
\end{itemize}
$v^2=u^2+2as$
0=$(49\sin45)^2-2gs$
$S=\dfrac{(49\sin45)^2}{2g}=61.3$
\textit{What is the time of the flight?}
\begin{itemize}
\item u=$49\sin45$
\item a=-g
\item S=0
\item t=?
\end{itemize}
$S=ut+\dfrac{1}{2}at^2$
$ $
$0=(49\sin45)t-\dfrac{1}{2}gt^2$
0=$t(49\sin45-\dfrac{gt}{2}$
$t=0$
$49\sin45=\dfrac{gt}{2}$
$t=\dfrac{2\times49\sin45}{g}=7.07$
\textit{What is the horizontal range of the particle?}
\begin{itemize}
\item t=7.07
\item Speed=$49\cos45$
\end{itemize}
$S=45\cos45\times7.07=245$

\end{obeylines}
\end{document}

### 2017-11-01 Maths Notes/S2/Binomial and Poisson/Poisson and Binomial.tex
Initial upload of all files

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Binomial and Poisson Distributions}
\end{center}
\begin{obeylines}
\section{The Binomial Distribution}
\subsection{Introduction to the binomial distribution}
The binomial distribution is a \textbf{discrete} distribution.
Conditions for a binomial distribution:
\begin{itemize}
\item There are a fixed number of trials, \textbf{n}
\item There are two outcomes (success and failure)
\item Each trial is independent
\item The probability of success is constant, \textbf{p}
\end{itemize}
Formula:
For $X~B(n,p)$

$P(X=r)=\binom{n}{r}p^r(1-p)^{n-r}$

Example:
If 25 dice are thrown, find the probability three sixes are obtained.
$X~B(25,\frac{1}{6})$
$P(X=3)=\binom{25}{3}(\frac{1}{6})^3(\frac{5}{6})^{22}=0.1929$
\subsection{Use of tables}
Tables give "less than or equal to" probabilities.

Example:
$X~B(5,0.35)$
$P(x\leq3)=0.9640$ (in the table where n=5, p=0.35 and x=3)
$P(x<4)=0.9640$ (the data is discrete)
$P(x=3)=P(x\leq3)-P(x\leq2)$
$P(x=3)=0.9640-0.7648$
$ $
$P(x\geq3)=1-P(X\leq2)$
$P(x\geq3)=1-0.7648$
$P(x\geq3)=0.2352$
\subsection{Dealing with $P>\frac{1}{2}$}
Example:
In the production of a car it is found that 85 \% are without defects.
The cars are produces in batches of 50
\textit{Find the probability there are at least 40 defect-free cars in a batch}
X=Number of cars without defects
$X~B(50,0.85)$
$P(X\geq40)$
Y=Number of cars with defects
$Y~B(50,0.15)$
$P(Y\leq10)=0.8801=P(x\geq40)$
\subsection{Mean and variance of the binomial distribution}
$E(X)=np$
$Var(x)=np(1-p)$
$\sigma(x)=\sqrt{Var(x)}$
Example 1:
$X~B(80,0.4)$ \textit{Find $E(x)$ and $\sigma$}
$E(x)=80\times0.4=32$
$\sigma=80\times0.4(1-0.4)=4.38$
$ $
\newpage
Example 2:
$E(x)=8$
$Var(x)=6.4$
\textit{Find n and p}
$np-np^2=6.4$
$8-np^2=6.4$
$np^2=1.6$
$ $
$p=\dfrac{np^2}{np}=\dfrac{1.6}{8}=0.2$
$ $
$n=\dfrac{np}{p}=\dfrac{8}{0.2}=40$
\section{The Poisson Distribution}
\subsection{Introduction to the Poisson Distribution}
The conditions for a poisson distribution are:
\begin{itemize}
\item Events occur at random
\item Events occur independently of each other
\item The average rate of occurrences remains constant
\item There is zero probability of simultaneous occurrences 
\end{itemize}
$P(x=r)=\dfrac{e^{-\lambda}\lambda^r}{r!}$
$\lambda$ represents the mean number of occurrences in the time period.
\textbf{Example}
$x\sim P_o(4)$
$P(x=2)=\dfrac{e^{-4}\times 4^2}{2!}=0.1465$
\subsection{Mean and variance of the poisson distribution}
If $X~P_o(\lambda)$ then $E(x)=\mu=\lambda$ and $Var(x)=\lambda$
\subsection{Using the Poisson as an approximation of the binomial}
You can use the Poisson distribution as an approximation if:
\begin{itemize}
\item P is small $(<0.1)$
\item n is large $(>50)$
\end{itemize}
$\lambda=np$
$X\sim B(n,p)\approx Y\sim P_o(np)$
\textbf{Example}
$X\sim B(250,0.01)\approx X\sim P_o(2.5)$

\end{obeylines}
\end{document}

### 2017-11-01 Maths Notes/S2/Hypothesis testing/Hypothesis testing.tex
Initial upload of all files

--- 2017-11-01 Maths Notes/S2/Binomial and Poisson/Poisson and Binomial.tex
@@
 \begin{center}
-\underline{\huge Binomial and Poisson Distributions}
+\underline{\huge Hypothesis testing}
 \end{center}
-\begin{obeylines}
-\section{The Binomial Distribution}
-\subsection{Introduction to the binomial distribution}
-The binomial distribution is a \textbf{discrete} distribution.
-Conditions for a binomial distribution:
-\begin{itemize}
-\item There are a fixed number of trials, \textbf{n}
-\item There are two outcomes (success and failure)
-\item Each trial is independent
-\item The probability of success is constant, \textbf{p}
-\end{itemize}
-Formula:
-For $X~B(n,p)$
+\section{Tests of hypotheses}
+\textbf{Statistical hypothesis} - An assertion or conjecture concerning a population.\\
+\\
+To test the validity of a statement a random sample is taken from the population and that data can them be used to provide evidence that either supports or does not support the hypothesis.\\
+\\
+\textbf{Null hypothesis} - $H_0$ - A hypothesis assumed to be true
+\textbf{Alternative hypothesis} - $H_1$ - The situation if $H_0$ is false.
 
-$P(X=r)=\binom{n}{r}p^r(1-p)^{n-r}$
+If the data leads to rejection of the null hypothesis the alternative hypothesis will be accepted.
 
-Example:
-If 25 dice are thrown, find the probability three sixes are obtained.
-$X~B(25,\frac{1}{6})$
-$P(X=3)=\binom{25}{3}(\frac{1}{6})^3(\frac{5}{6})^{22}=0.1929$
-\subsection{Use of tables}
-Tables give "less than or equal to" probabilities.
+The sample data is used to evaluate the \textbf{test statistic}, probabilities related to it can be calculated using the null hypothesis.
 
-Example:
-$X~B(5,0.35)$
-$P(x\leq3)=0.9640$ (in the table where n=5, p=0.35 and x=3)
-$P(x<4)=0.9640$ (the data is discrete)
-$P(x=3)=P(x\leq3)-P(x\leq2)$
-$P(x=3)=0.9640-0.7648$
-$ $
-$P(x\geq3)=1-P(X\leq2)$
-$P(x\geq3)=1-0.7648$
-$P(x\geq3)=0.2352$
-\subsection{Dealing with $P>\frac{1}{2}$}
-Example:
-In the production of a car it is found that 85 \% are without defects.
-The cars are produces in batches of 50
-\textit{Find the probability there are at least 40 defect-free cars in a batch}
-X=Number of cars without defects
-$X~B(50,0.85)$
-$P(X\geq40)$
-Y=Number of cars with defects
-$Y~B(50,0.15)$
-$P(Y\leq10)=0.8801=P(x\geq40)$
-\subsection{Mean and variance of the binomial distribution}
-$E(X)=np$
-$Var(x)=np(1-p)$
-$\sigma(x)=\sqrt{Var(x)}$
-Example 1:
-$X~B(80,0.4)$ \textit{Find $E(x)$ and $\sigma$}
-$E(x)=80\times0.4=32$
-$\sigma=80\times0.4(1-0.4)=4.38$
-$ $
-\newpage
-Example 2:
-$E(x)=8$
-$Var(x)=6.4$
-\textit{Find n and p}
-$np-np^2=6.4$
-$8-np^2=6.4$
-$np^2=1.6$
-$ $
-$p=\dfrac{np^2}{np}=\dfrac{1.6}{8}=0.2$
-$ $
-$n=\dfrac{np}{p}=\dfrac{8}{0.2}=40$
-\section{The Poisson Distribution}
-\subsection{Introduction to the Poisson Distribution}
-The conditions for a poisson distribution are:
-\begin{itemize}
-\item Events occur at random
-\item Events occur independently of each other
-\item The average rate of occurrences remains constant
-\item There is zero probability of simultaneous occurrences 
-\end{itemize}
-$P(x=r)=\dfrac{e^{-\lambda}\lambda^r}{r!}$
-$\lambda$ represents the mean number of occurrences in the time period.
-\textbf{Example}
-$x\sim P_o(4)$
-$P(x=2)=\dfrac{e^{-4}\times 4^2}{2!}=0.1465$
-\subsection{Mean and variance of the poisson distribution}
-If $X~P_o(\lambda)$ then $E(x)=\mu=\lambda$ and $Var(x)=\lambda$
-\subsection{Using the Poisson as an approximation of the binomial}
-You can use the Poisson distribution as an approximation if:
-\begin{itemize}
-\item P is small $(<0.1)$
-\item n is large $(>50)$
-\end{itemize}
-$\lambda=np$
-$X\sim B(n,p)\approx Y\sim P_o(np)$
-\textbf{Example}
-$X\sim B(250,0.01)\approx X\sim P_o(2.5)$
+Critical values are the range of values that if the test statistic is found in the null hypothesis will be rejected.
 
-\end{obeylines}
 \end{document}

### 2017-11-01 Physics Notes/Capacitors/Capacitors.tex
Initial upload of all files

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{circuitikz}
\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Fields}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Capacitors}
\end{center}
A capacitor is constructed from two conducting plates separated by an insulator.\\
Charge can flow onto and off the plates but not across the plates.\\
\\
\textbf{Charging circuit for a capacitor}\\
\begin{center}
\begin{circuitikz}[american voltages]
\draw
  (0,0) to [short] (3,0)
  to [battery] (4,0)
  (4,0) to[short] (5,0)
  (4.4,-3) node[spdt](spdt) {}
  (5,0) to[short] (spdt.out 1)
  (spdt.in) to [capacitor] (2,-3)
  (2,-3) to[short] (0,-3)
(0,-3) to[short] (0,0)
(spdt.out 2) to [short] (5,-5) 
(5,-5) to[lamp] (1,-5) 
(1,-5) to[short] (0,-5)
(0,-5) to[short] (0,-3)
  ;
  \end{circuitikz}
  \end{center}

When charging the current flows round the top half of the circuit, when discharging the SPDT is changed to the other output and the current flows round the bottom half of the circuit.\\
\\
Capacitors can be used as simple timers in circuits.
\\
\\
The time it takes to charge/discharge depends on:
\begin{itemize}
\item The capacitance of the capacitor \textbf{(C)}
\item The resistance of the charging/discharging circuit \textbf{(R)}
\end{itemize}

\end{document}

### 2017-11-01 Physics Notes/Further Mechanics and Thermal Physics/Circular Motion/Circular Motion.tex
Initial upload of all files

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{tikz}
\usetikzlibrary{scopes}
\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Further Mechanics and Thermal Physics}
\rfoot{Page \thepage}
\pgfdeclarelayer{background layer}
\pgfdeclarelayer{foreground layer}
\pgfsetlayers{background layer,main,foreground layer}

\begin{document}
\begin{center}
\underline{\huge Circular Motion}
\end{center}
\section{Introduction to circular motion}
For an object to be going in a circle a force is needed to accelerate the object. This is because in a circle an object is constantly changing velocity, even if it isn't changing speed.\\
Centripetal force is not an extra force, it is just the name for a resultant force.\\
For an object to be deflected towards the centre, there needs to be a force acting towards the centre.
\subsection{Definitions}
\begin{tabular}{|c|c|c|c|}
\hline
Quantity&Symbol&Unit&Definition\\
\hline
Period&T&Seconds,s&The time taken for an object to complete one revolution\\
\hline
Frequency&f&Hertz,hz&The number of revolutions per second\\
\hline
Angular velocity&$\omega$&$\textrm{rads}^{-1}$&The rate of change in angle(the angle covered per second)\\
\hline
\end{tabular}
\subsection{Formula not on formula book}
$\omega=\dfrac{\Delta\theta}{\Delta t}$\\
$a=\dfrac{\Delta V}{\Delta t}$\\
Don't forget application of  $F=ma$ with the equations for force
\section{Circular motion for going over a hump}
\begin{tikzpicture}[
    force/.style={>=latex,draw=black,fill=black},
    m/.style={rectangle,draw=black,fill=white,minimum size=0.3cm,thin},
]
    \node[m] (m) {};
    {[force,->]
        \draw (m.north) -- ++(0,1) node[above] {$r$};
        \draw (m.south) -- ++(0,-1) node[below] {$mg$};
    }
\end{tikzpicture}
\\
For an object going over a hump the force of the weight is in the opposite direction to the reaction force.\\
The object will leave the ground if $mg>r$.
\subsection{Calculations}
$F_c=mg-R=\dfrac{mv^2}{r}$\\
\textbf{Calculating the speed at which the car will leave the ground (R=0)}\\
$mg=\dfrac{mv_0^2}{r} \qquad V_0=\sqrt{gr}$\\
Once the car has left the ground, use SUVAT equations rather than circular motion.
\section{Roundabouts}
On a roundabout the centripetal force is provided by friction.\\
$F_r=\dfrac{mv_0^2}{r}$\\
To avoid slipping, the centripetal force must be less than the maximum possible for the car and road surface.\\
\textbf{Example question}
\textit{The maximum possible force of friction between a car and the road is 800N, given a mass of 1000kg and a radius of 5m, what is the maximum speed the car can go without slipping}
\newpage
\section{Banked motion}
N is the reaction force\\
$n\sin\theta=\dfrac{mv^2}{r}$ - Force towards the centre of notion is equal to the centripetal force\\
$N\cos\theta=mg$ - The force vertically downwards is equal to the weight\\
$\tan\theta=\dfrac{v^2}{rg}$ - Combining the equations\\
$v^2=gr\tan\theta$ - Re-write
\section{Forces in a circle}
\begin{tikzpicture}[
    force/.style={>=latex,draw=black,fill=black},
    m/.style={rectangle,draw=black,fill=lightgray,minimum size=0.3cm,thin},
]
    \node[m] (m) at (0,-2) {};
    \node[m] (m2) at (0,2) {};
    \node[m] (m3) at (2,0) {};
    {[force,->]
        \draw (m.north) -- ++(0,0.7) node[above] {$R$};
        \draw (m.south) -- ++(0,-0.7) node[right] {$mg$};
    }
    {[force,->]
        \draw (m2.south) -- ++(0,-0.7) node[below] {$R+mg$};
    }
    {[force,->]
        \draw (m3.west) -- ++(-0.7,0) node[left] {$R$};
        \draw (m3.south) -- ++(0,-0.7) node[below right] {$mg$};
    }

\begin{pgfonlayer}{background layer}
    \draw[color=black, very thick](0,0) circle (2);
    \end{pgfonlayer}{background layer}
\end{tikzpicture}
\\
Top: Centripetal force = $R+W$\\
Side: Centripetal force = $R$\\
Bottom: Centripetal force = $R-W$\\
At the top of the loop r=0\\
$v=\sqrt{gr}$

\end{document}

### 2017-11-01 Physics Notes/Textbook Notes/Capacitors/Capacitor.tex
Initial upload of all files

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[english]{babel}
\usepackage{fancyhdr}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Fields}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Physics Capacitor Notes}
\end{center}

\begin{obeylines}
\section{Introduction to Capacitors}
A capacitor is a device used to store charge, constructed of two parallel metal gates near each other with an insulator in between. One conductor gains electrons and the other one loses them.

The charge on a capacitor with constant current is $Q=It$. Voltage across a capacitor is directly proportional to the current stored.

The unit of capacitance is the Farad, equal to one coulomb per volt. It will usually be given in $\mu F$, $nF$ or $pF$.
$ $
$C=\dfrac{Q}{V}$

\section{Uses of Capacitors}
\begin{itemize}
\item Smoothing circuits
\item Back-up power supplies
\item Timing circuits
\item Pulse producing circuits
\item Tuning circuits
\item Filter circuits (remove unwanted frequencies)
\end{itemize}

\section{Capacitor discharge through a fixed resistor}
As a capacitor discharges through a fixed resistor the current reduces to zero. This is because as charge reduces, voltage reduces. Because $Current = \dfrac{pd}{resistance}$ and resistance is constant current decreases as voltage decreases. Current and voltage decrease exponentially over time, giving their graph with time a curve. If the initial charge is Q, and after t the charge is 0.8 Q then after nt the charge will be $0.8^nQ$. 
This is because
$I=\dfrac{V}{R}=\dfrac{Q}{CR}$
$ $
$\Delta Q=-I \Delta t$
$ $
$\dfrac{dQ}{dt}=-\dfrac{Q}{CR}$
$ $
$\int\dfrac{dQ}{Q}=-\int\dfrac{1}{CR}dt$
$lnQ=-\dfrac{t}{CR}+A$
$ $
$Q=e^{-\dfrac{t}{RC}+A}=e^{-\dfrac{t}{RC}}e^A=Qe^{-\dfrac{t}{RC}}$

Time Constant = RC, unit=seconds
\section{Charging a capacitor through a fixed resistor}
As the capacitor charge increases the charging current decreases. When the capacitor is fully charged, its PD=Source PD and the current is 0. The time constant for the circuit is the time it takes for the capacitor to reach 63\% charge.
Source PD = Resistor PD + Capacitor PD
$V_0=IR+\dfrac{Q}{C}$ at any time
Initial current $(I_0)=\dfrac{V_0}{R}$ assuming the capacitor is initially uncharged.
At time $t$ after the charging starts $I=I_0e^{\dfrac{-t}{RC}}$
$V_0=V_0e^{\dfrac{-t}{RC}}+\dfrac{Q}{C}$
$\dfrac{Q}{C}=V_0(1-e^{\dfrac{-t}{RC}})$
$V=\dfrac{Q}{C}$
$Q=CV_0(1-e^{\dfrac{-t}{RC}})$
At time t=0:
$e^{\dfrac{-t}{RC}}=1$ so Q=0 and V=0
As time $t \rightarrow \infty$:
$e^{\dfrac{-t}{RC}}=0$
$Q \rightarrow Q_0$
$V \rightarrow V_0$

\section{Dielectric action}	
The charge stored on the plates on a capacitor can be increased by inserting a \textbf{Dielectric} between the plates. These are electrically insulating materials that increase the charge storing ability. Polythene and waxed paper are examples of this.

When a dielectric is placed in a capacitor and connected to a battery the molecules become polarised, meaning that electrons are pulled slightly towards the positive plate.

This causes more charge to be stored on the plates as:
\begin{itemize}
\item The positive side of the dielectric attracts more electrons from the battery onto the negative plate
\item The negative side of the dielectric pushed electrons back to the battery from the positive plate
\end{itemize}
\section{Relative permittivity}
Relative permittivity is the ratio of charge stored without a dielectric, compared to that with a dielectric.
Relative permittivitty $\epsilon _r=\dfrac{Q}{Q_0}$
Q = Charge stored when the area between the plates is completely filled with dielectric substances.
$Q_0$ = Charge without any dielectric.

For a fixed voltage $\epsilon _r = \dfrac{C}{C_0}$

The relative permittivity is also called the dielectric constant.

\section{Capacitor design}
Capacitance = $\dfrac{A \epsilon _0 \epsilon _r}{d}$
A= Surface area
D = Distance between plates
A large capacitance can be achieved by:
\begin{itemize}
\item Making the area as large as possible
\item Making the plate spacing as small as possible
\item Filling the space between the plates with a dielectric which has a relative permittivity as large as possible.
\end{itemize}

\section{Polarisation mechanisms}
\subsection{Orientation polarisation}
For molecules where covalent bonds are formed between atoms of different elements. This forms a dipole as the electrons are shared unequally. When an electric field is applied the atoms are displaced in opposite directions, to align with the field.
\subsection{Ionic polarisation}
For substances where ions are held together by ionic bonds. Opposite direction displacement.
\subsection{Electronic polarisation}
Electrons in each atom are displaced relative to the nucleus when an electric field is applied. The electron distribution and the nucleus form a dipole.

\end{obeylines}

\end{document}

### 2017-11-01 Maths Notes/S2/Hypothesis testing/Hypothesis testing.tex
Update to S2 notes on hypothesis testing, still needs more information

@@
 
-Critical values are the range of values that if the test statistic is found in the null hypothesis will be rejected.
+If the test statistic is found in the \textbf{critical region} the null hypothesis will be rejected.
+
+The \textbf{boundary values} of the critical region are called the critical values.
+\section{Method}
+\begin{enumerate}
+\item Establish the null and alternative hypothesis ($H_0$ and $H_1$)
+\item Define distribution under $H_0$
+\item Decide on the significance level
+\item Collect data, state the test statistic, X=
+\item Calculate the probability of obtaining the test statistic or a more extreme result (same direction as $H_1$)
+\item Compare this to the sig level as a decimal
+\begin{itemize}
+\item If \textbf{greater} than the sig level, it is a \textbf{non significant} result, it is not in the critical region and we \textbf{do not} reject $H_0$
+\item If \textbf{less} than sig level, it is a \textbf{significant result}, it is in the critical region and we \textbf{reject} $H_0$ 
+\end{itemize}
+\item Interpret the results in terms of the original claim
+\end{enumerate}
 

### 2017-11-02 Maths Notes/S2/Hypothesis testing/Hypothesis testing.tex
Update hypothesis test

@@
 \usepackage{gensymb}
+\usepackage{amssymb}
 
@@
 \end{enumerate}
+\subsection{Example}
+\textbf{Establish the null and alternative hypothesis}\\
+$H_0:p=0.5$\\
+$H_1:p>0.5$\\
+\\
+\textbf{Define the distribution under $\mathbf{H_O}$}\\
+Under $H_0$ $X\sim B(15,0.5)$\\
+\\
+\textbf{Decide on the significance level}\\
+$5\%$\\
+\\
+\textbf{Collect data, state the test statistic}\\
+X=12\\
+\\
+\textbf{Calculate the probability of obtaining the test statistic or a more extreme result}\\
+\begin{tabular}{r l}
+$P(X\geqslant 12)$&$=1-P(X\leqslant 11)$\\
+&$=1-0.9824$\\
+&$=0.0176$\\
+\end{tabular}
+\\
+\textbf{Compare this to the sig level as a decimal}
+$0.0176<0.05$\\
+\\
+\textbf{Interpret the results in terms of the original claim}\\
+There is evidence to reject $H_0$ in favour of $H_1$. The test is significant.
+\subsection{Finding critical values}
+We require a value c such that:\\
+$P(X\geqslant c)<0.05$\\
+$1-P(X\leqslant c-1)<0.05$\\
+$P(X\leqslant c-1)>0.95$\\
+\\
+\textbf{Test against tables}\\
+$P(X<11)=0.9824$\\
+\\
+$c-1=11$\\
+$c=12$
+\subsection{Two tailed tests}
 

### 2017-11-05 Physics Notes/Capacitors/Capacitors.tex
Weekend Updates
C4,D2,M2,Physics-Capacitors

@@
 A capacitor is constructed from two conducting plates separated by an insulator.\\
-Charge can flow onto and off the plates but not across the plates.\\
-\\
-\textbf{Charging circuit for a capacitor}\\
+Charge can flow onto and off the plates but not across the plates.
+
+\section{Charging circuit for a capacitor}
 \begin{center}
@@
 \end{itemize}
+\section{Energy stored in a capacitor}
+\begin{tikzpicture}[scale=0.5]
+\begin{axis}[xmin=0,ymin=-0.01,ylabel=V,xlabel=Q,axis lines=middle,label style={font=\LARGE},
+ytick={2},yticklabels=v,
+ticklabel style = {font=\LARGE},
+xtick={1.5,2.5},xticklabels={q,q+$\Delta$q}
+]
+\addplot[mark=none]{x};
+\addplot [mark=none] coordinates {(1.5,0) (1.5, 1.5)};
+\addplot [mark=none] coordinates {(2.5,0) (2.5, 2.5)};
+\addplot[mark=none,domain=0:2]{2};
+\end{axis}
+\filldraw[black, ultra thin,fill=gray!70] (2.5,0) -- (4.2,0) -- (4.2,3.5) -- (2.5,2.1) -- cycle;
+\end{tikzpicture}\\
+Area under graph=work done\\
+V is the average P.D. as charge increases from q to q+$\Delta$q\\
+$\Delta \text{w=v}\Delta \text{q}$\\
+\\
+$Q=\frac{1}{2}QV=E$  \textbf{(Work done=energy stored)}\\
+\\
+How to answer the exam question: Show that the energy stored by a capacitor is given by $E=\frac{1}{2}QV$
+\begin{enumerate}
+\item Sketch a graph of Q against V and describe what it shows
+\item Describe that electrical energy is the product of charge and voltage
+\item State QV is represented by the area under the line
+\item The area under the line is a triangle with area =$\frac{1}{2}QV$
+\item Therefore $E=\frac{1}{2}QV$
+\end{enumerate}
+$E=\frac{1}{2}QV$\\
+$Q=CV$\\
+Therefore:\\
+$E=\frac{1}{2}CV^2$\\
+$E=\frac{1}{2}\dfrac{Q^2}{C}$\\
+\\
+The battery supplies energy QV to the circuit but the capacitor only stores $\frac{1}{2}QV$, this means that 50\% of the energy provided by the battery is wasted due to resistance in the circuit.
 

### 2017-11-05 Maths Notes/M2/Collisions/Collisions.tex
Weekend Updates

@@
 $e=\dfrac{\text{Speed of seperation}}{\text{Speed of approach}}$
-
+\subsection{Alternate form of coefficient of restitution formula}
+$mgh=\frac{1}{2}mv^2$\\
+$v=\sqrt{2gh}$\\
+$e=\dfrac{\sqrt{2gh_2}}{\sqrt{2gh_1}}$\\
+$e=\dfrac{\sqrt{h_2}}{\sqrt{h_1}}$\\
+$h_2$ - the height the ball bounces back to\\
+$h_1$ - the height the ball is dropped from\\
+\subsection{Calculations involving coefficient of restitution}
+When doing calculations involving the coefficient of restitution both the calculation for CoR and conservation of momentum will be needed.
+\textbf{Conservation of momentum:}
+$m_1u_1+m_2u_2=m_1v_1+m_2v_2$\\
+\textbf{Coefficient of restitution}
+$e=\dfrac{v_1}{u_1}$
 \end{obeylines}

### 2017-11-07 Cyber Security/Cyber Security.tex
Initialised notes on Cyber Security

--- 2017-11-01 Maths Notes/S2/Hypothesis testing/Hypothesis testing.tex
@@
 \rhead{Sam Robbins 13SE}
-\lhead{A Level Maths - S2}
+\lhead{GCHQ Cyberfirst}
 \rfoot{Page \thepage}
@@
 \begin{center}
-\underline{\huge Hypothesis testing}
+\underline{\huge Cyber Security Notes}
 \end{center}
-\section{Tests of hypotheses}
-\textbf{Statistical hypothesis} - An assertion or conjecture concerning a population.\\
-\\
-To test the validity of a statement a random sample is taken from the population and that data can them be used to provide evidence that either supports or does not support the hypothesis.\\
-\\
-\textbf{Null hypothesis} - $H_0$ - A hypothesis assumed to be true
-\textbf{Alternative hypothesis} - $H_1$ - The situation if $H_0$ is false.
-
-If the data leads to rejection of the null hypothesis the alternative hypothesis will be accepted.
-
-The sample data is used to evaluate the \textbf{test statistic}, probabilities related to it can be calculated using the null hypothesis.
-
-Critical values are the range of values that if the test statistic is found in the null hypothesis will be rejected.
 

### 2017-11-07 Cyber Security/Cyber Security.tex
Update Cyber Security Notes up to DNS

@@
 
+\usepackage{titlesec}
+
+\setcounter{secnumdepth}{4}
+
+\titleformat{\paragraph}
+{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
+\titlespacing*{\paragraph}
+{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
+
 \begin{document}
@@
 \end{center}
+\section{Security Essentials}
+\begin{itemize}
+\item Integrity
+\item Availability 
+\item Confidentiality 
+\end{itemize}
+\section{Introductory definitions}
+\begin{itemize}
+\item Information Assets - Data to be protected
+\item Authentication - Verifying the identity of a user
+\item Non-repudiation - Ensuring a user cannot deny something later or claim something is false
+\item Malware - A contraction of malicious software
+\item Ransomware - Malware that demands money to stop from doing something
+\item Spyware - Malware that records the activity of the user
+\item Botnets - Malware that records the activities of the user
+\item Vulnerability - A point at which there is potential for a security breach
+\item Threat - Some danger that can exploit a vulnerability
+\item Countermeasure - An action taken to protect information from threats and vulnerabilities
+\end{itemize}
+\section{Passwords}
+\subsection{Aims of a password}
+\begin{itemize}
+\item Memorable enough that the user can remember it without writing it down
+\item Long and unique enough that no one else can guess it
+\end{itemize}
+As these two aims are a contradiction, password must be a compromise between the two
+\subsection{Transfer of passwords}
+Passwords transmitted and stored in plaintext are insecure
+\subsection{Securing of passwords}
+Passwords are often encrypted using \textbf{SSL}(secure socket layer)\\
+\\
+\textbf{Hashing}- Encrypting a password using one way encryption, any subsequent password is encrypted using the same method and compared to the stored hashed password.
+\subsubsection{Salting}
+\textbf{Salting} - Adding a value to the password before encryption.\\
+Salting means that even if two people choose identical passwords, the stored password will be different.\\
+Salting is only effective if:
+\begin{itemize}
+\item Salts are truly random
+\item The salt is sufficiently long enough to avoid the attacker just adapting their dictionary to include all salted values
+\end{itemize}
+\subsection{Password managers}
+Requirements for a password manager:
+\begin{itemize}
+\item The password manager should require a password to start it, preventing unwanted access
+\item It should lock itself after a period of inactivity
+\item The passwords should be encrypted
+\end{itemize}
+\section{Types of cyber attacks}
+\subsection{Virus}
+A virus is a self replicating program often intended to cause harm
+\subsection{Worms}
+Four stages of a worm attack:
+\begin{itemize}
+\item First stage - Worm probes other machines, looking for a vulnerability to exploit
+\item Second stage - Penetrate the machine, exploiting the vulnerability
+\item Third stage - The worm downloads itself onto the machine and stores itself there
+\item Fourth stage - Probe other machines (back to stage 1)
+\end{itemize}
+\subsection{Trojans}
+\textbf{Trojan} - A seemingly legitimate program that causes damage behind the scenes\\
+Trojans are not self replicating
+\subsection{Phishing}
+\textbf{Phishing} - The process of luring people to disclose confidential information\\
+Phishing relies on people trusting official looking messages
+\subsection{Spam Messages}
+\textbf{SMTP}(Simple Mail Transfer Protocol) defines a standard template of commands for different email programs.\\
+This was created to a small number of users so did not include the ability to verify emails, meaning that phishing becomes possible.
+\subsection{Spoofing}
+Spoofing is where people pretend to be a person or device that they are not
+\subsection{Botnets}
+Botnets are used to coordinate the activity of many computers, these are often used for further cyber attacks.
+\section{Antivirus software}
+\textbf{Malware signature} - A distinctive pattern of data, either in memory or in a file\\
+\\
+\textbf{Heuristics} - The use of rules to identify viruses based on previous exposure to viruses.
+Heuristics may execute programs in a virtual machine, checking the requests and actions the malware makes to see if it poses a threat to the computer.\\
+\\
+\textbf{Sandbox} - A way for computers to run programs in a controlled environment. This constrains computing resources, allowing the program to not cause a threat to the computer.\\
+\\
+\textbf{Signed programs} - The sue of cryptography when companies issue copies of a program, so that the user can check it for authenticity.
+\section{How the internet works}
+The internet comprises of a hierarchy of individual networks that have been connected to each other.\\
+\\
+Key factors in the design of the internet:
+\begin{itemize}
+\item Should not have a central controlling computer. Every computer on the network has the same authority
+\item The network should be able to deliver information between any two computers on the network, even if come of the machines in the network have failed.
+There should be a large number of alternative routes through the network
+\end{itemize}
+\subsection{Datagrams(packets)}
+When a large amount of data is sent over the internet it is split into small, uniformly sized blocks called "datagrams", also called "packets"\\
+\\
+\textbf{Header} - Sender and recipient's address, unique number, data stamp and error correcting information\\
+\textbf{Payload} - The actual information being delivered
+\subsection{Wireless networks}
+WiFi allows devices to be connected together wirelessly to form a LAN\\
+WiFi refers to the wireless LAN standard from the Institute of Electrical and Electronic Engineers (IEEE) called the 802.11 family.\\
+\\
+\textbf{SSID} - The name of the network (Service Set IDentifier)\\
+The SSID allows nodes on a wireless LAN to distinguish themselves from nodes on other wireless LANs in the same physical space.
+\section{Network security challenges}
+\textbf{Packet Sniffing} - The copying of datagrams without the recipient knowing
+\subsection{Security risks of wireless networking}
+A wireless network should ensure that an eavesdropper is not able to convert wireless signals into the original message. This ensures \textbf{confidentiality}.
+\subsubsection{Man in the middle attacks}
+A man in the middle attack is where malicious users interpose themselves between the sender and receiver to modify or destroy the messages being sent.
+This compromises the \textbf{integrity} of the data being transferred.
+\subsubsection{Denial of service attacks}
+An attacker could transmit lots or random data on the frequency used by the wireless network, congesting the network and so preventing others from sending data.
+This compromises the \textbf{availability} of the network.
+\newpage
+\subsection{How encryption helps prevent security issues in wireless networks}
+Encryption helps ensure:
+\begin{itemize}
+\item \textbf{Confidentiality} - Encryption keys are needed to decrypt information, meaning attackers can't recover the information
+\item \textbf{Integrity} - Encryption prevents messages from being modified without the receivers knowledge
+\item \textbf{Authentication} - Encryption proves the identities of the sender and receiver
+\end{itemize}
+\subsection{Implementation of encryption in WiFi}
+\subsubsection{WEP(Wired Equivalent Privacy)}
+WEP has many serious problems as the encryption key can be computed in a few minutes. Many devices still support this to ensure compatibility but it should not be used.
+\subsubsection{WPA2(WiFi Protected Access 2)}
+This uses a more secure key to encrypt data that WEP, this is the default for WiFi networks. All WiFi devices must support it to be compliant with the 802.11 standard.
+\section{The role of standards in the internet}
+\subsection{Why standards are needed on the internet}
+Standards are needed to ensure that all devices can communicate with each other.
+\subsection{TCP/IP Protocols}
+\subsubsection{TCP}
+TCP ensures that data can be sent reliably over the internet. This works through software ports to keep data separate on the same computer.\\
+The port decides how the data is handled when it reaches it's destination.\\
+\\
+Common TCP Ports:
+\begin{itemize}
+\item 20 and 21 - FTP - for sending and receiving files(20) and control(21)
+\item 22 - SSH for secure logins
+\item 25 - SMTP(Simple Mail transfer protocol) - Email
+\item 80 - HTTP(HyperText Transfer Protocol) - Web Pages
+\end{itemize}
+\textbf{Traffic type} - The type of data and the port associated with it. For example SSH or HTTP.
+\\
+TCP also ensures all data sent from a computer is received by the destination.
+It does this by waiting for acknowledgements of receipt from the remote computer, and if the data was not received, sending the message again.\\
+\\
+Applications where latency is more important than accuracy, such as video conferencing, use \textbf{UDP} to send and receive data.
+\subsubsection{IP}
+\textbf{IP} - Internet Protocol\\
+IP is only concerned with moving data, it doesn't check the data has arrived(handled by TCP).\\
+\\
+When IP receives data from TCP in the computer it wraps the TCP datagram in an IP datagram with senders and receivers address, along with other information.\\
+\\
+When IP receives data from the internet, it removes the IO datagram and passes it to TCP.
+\section{Test}
+This is some test text
+\paragraph{Test}
+How is this
 

### 2017-11-07 Cyber Security/Cyber Security.tex
Cyber Security Notes update

@@
 When IP receives data from the internet, it removes the IO datagram and passes it to TCP.
-\section{Test}
-This is some test text
-\paragraph{Test}
-How is this
+\paragraph{IP addresses}
+Every computer connected to the internet has an IP Address\\
+\\
+There are two forms of IP addresses \textbf{IPv4} and \textbf{IPv6}.
+\paragraph{IPv6}
+IPv6 can support $3.5\times10^{38}$ IP addresses, meaning it is able to accommodate any demand.
+IPv6 is intended to replace IPv4, however it is taking a long time, the best solution so far is to map all IPv4 addresses to IPv6.
+\paragraph{Reserved IP Numbers}
+There are many IP addresses reserved for private networks, outside of the internet, for example:
+\begin{itemize}
+\item 10.0.0.0 to 10.255.255.255
+\item 169.254.0.0 to 169.254.255.255
+\item 172.16.0.0 to 172.31.255.255
+\item 192.168.0.0 to 192.168.255.255
+\end{itemize}
+\subsection{DNS}
+A DNS translates an readable address(e.g. google.com) to an IP address
 

### 2017-11-08 Cyber Security/Cyber Security.tex
Cyber Security notes update to VPN

@@
 \subsection{DNS}
-A DNS translates an readable address(e.g. google.com) to an IP address
-
+A DNS translates an readable address(e.g. google.com) to an IP address.\\
+When a computer needs to get an IP address from a hostname it contacts the DNS responsible for the Top level domain (.com in this case).
+This DNS then responds with the correct IP address.
+The computer then uses this to contact the server.
+\subsection{Difference between the Internet and the World Wide Web}
+The world wide web is the part of the internet than can be accessed through HTTP.\\
+The internet covers all communication between online systems, such as FTP or SSH.\\
+\section{Cryptography}
+\subsection{Basics of cryptography}
+\subsection{Terminology}
+\begin{itemize}
+\item \textbf{plaintext} - Information that can be read directly by humans
+\item \textbf{ciphertext} - The encrypted data
+\item \textbf{a cipher} - The mathematics that turn ciphertext into plaintext
+\item \textbf{encryption} - Converting plaintext to ciphertext
+\item \textbf{decryption} - Reverting ciphertext to plaintext
+\end{itemize}
+\subsection{Encryption keys}
+\textbf{Keys} - Pieces of information that determine the output from an encryption process.\\
+A single cipher can produce an extremely large number of different outputs with different key values. This means communication is secure, even if the cipher is known to 3rd parties.\\
+\\
+An encryption key is a binary string. The total number of keys for a given key length is $2^{\text{key length}}$
+\paragraph{The problem of short keys}
+Short keys are vulnerable to \textbf{brute force} attacks.
+\subsection{The problem of key distribution}
+If encryption keys are stolen or copied during transit, the encryption is useless.\\
+\\
+The number of keys needed for large number of parties becomes difficult to manage. The number of keys is calculated by $\dfrac{n(n-1)}{2}$ where n is the number of communicating parties.
+\subsection{Asymmetric/public key cryptography}
+Public key cryptography requires two keys:
+\begin{itemize}
+\item \textbf{Private key} - Kept safe and not distributed
+\item \textbf{Public key} - Sent to anyone they want to exchange encrypted information with
+\end{itemize}
+The message is encrypted with the \textbf{public key}, but can only be decrypted using the \textbf{private key}.\\
+\\
+This method of encryption is secure as it means that any data intercepted cannot be turned into the message.
+\subsection{Why isn't the internet encrypted}
+The amount of computing power required to encrypt and decrypt all traffic sent over the internet would lead to significant costs.\\
+Some applications on the internet selectively use cryptography for key tasks(online payments).
+\subsection{Comparison of cryptographic techniques}
+\subsubsection{DES(Data Encryption Standard)}
+DES was developed in the 1970s, it has relatively small key sizes, so is possible to break with a brute force attack.
+Because this was developed when computers were primitive, brute force was not a problem at it's invention, however it is now.\\
+Triple DES provides additional security by doing 3 rounds of DES encryption, each with a different, 56 bit key.\\
+Triple DES will remain secure until at least 2030.
+\subsubsection{AES(Advanced Encryption Standard)}
+AES was adopted as a standard in 2001, it uses symmetric cyphers with either 128,192 or 256 bits.\\
+It is widely used in commercial applications as it is free. Many microprocessors now include AES in their instruction sets to speed up encryption and decryption.
+\subsubsection{Blowfish}
+Blowfish was developed in the 1990s, but wasn't widely accepted like AES is. This uses key lengths from 1 to 448 and there has been no successful attempt to break the encryption.
+\subsection{Using cryptography to prove identity}
+This works by checking that your copy of a piece of data us an exact match for the one you requested.
+\subsubsection{Hashing}
+Hashing is the mathematical process of converting data of any size into data of a fixed length.\\
+Hashing only works in one way, meaning the data cannot be reconstructed from a hash.\\
+If there is a difference of one bit in a file there will be a large difference in the hash.\\
+MD5, SHA-1 and SHA-2 are in common use. Both MD5 and SHA-1 are flawed as "collisions" can occur where two pieces of different data can generate the same hash value.
+\subsection{Digital signatures and certificates}
+A digital signature is used to ensure that data originated from its supposed author.\\
+A digital signature works by encrypting data with a private key, meaning that anyone with the public key can decrypt it.
+They know that only the person with the private key could have sent that message.
+\subsection{Encrypted network connections}
+In 1995 SSL was introduced, this allowed for encrypted traffic on the internet for things like online payments. This has now been replaced with TLS(Transport layer security).
+\subsubsection{TLS/SSL}
+These methods use a combination of asymmetric and symmetric encryption to exchange data.
+When a web browser connects to a server it undergoes a "handshake" which agrees the type of cryptography that will be used.\\
+\\
+After the handshake the server transmits a public key and certificate of authenticity to the users computer, the users computer then checks this.
+The user's computer then generates a \textbf{master secret}, encrypts it with the server's public key and sends it back.\\
+\\
+The server then decrypts the master secret.
+This secret means that both the server and computer can now generate identical copies of a \textbf{symmetric encryption key}, without transmitting this key in plaintext to each other.\\
+\\
+The computers then confirm with each other that all other transactions will take place using the key(called the session key). The computers can now perform a secure transaction.\\
+\\
+At the end of the session, the computers confirm that the transaction has finished and deletes their key.
+\section{Network Security}
+\subsection{Protecting data on the network}
+\subsubsection{Firewall basics}
+A firewall is a barrier that blocks all dangerous communication from spreading across a network.\\
+\\
+Firewalls block network communication by looking at the addressing and protocol information in the data packet's header.
+This header is compared to rules in the firewall's software to determine whether to let the packet in.\\
+\subsubsection{Personal firewalls}
+A firewall is only able to protect the computer it is installed on and devices attached to it, meaning it is called a personal firewall.\\
+\\
+These are especially useful for portable devices as these will be connected to a wide range of computer networks.
+\subsection{VPNs}
+\subsubsection{VPN basics}
+A VPN is a way of creating a private network across an untrusted network, such as the internet.
+VPNs are used for:
+\begin{itemize}
+\item To securely connect isolated LANs across the internet
+\item To allow mobile users to access a corporate network using the internet
+\item To control access within an intranet environment
+\end{itemize}
+\paragraph{VPN concepts}
+VPNs are typically implemented using dedicated network devices and software.
+The software is made of two parts, the \textbf{client} and the \textbf{server}.
+The client connects users to the VPN and the server authenticates users and routes traffic.\\
+\\
+The VPN software creates a "tunnel" between the VPN client and server. This tunnel can be established on an untrusted network.
 \end{document}

### 2017-11-09 Cyber Security/Cyber Security.tex
Cyber Security Notes - Finished

@@
 The VPN software creates a "tunnel" between the VPN client and server. This tunnel can be established on an untrusted network.
+\subsubsection{Securing a VPN}
+\paragraph{Encryption}
+VPNs use public encryption standards due to their increased reliability compared to proprietary standards.
+\paragraph{Authenticity and integrity}
+It is vital to ensure that data can be trusted, VPNs use the following method to ensure authenticity:
+\begin{itemize}
+\item Hashes
+\item Digital Signatures
+\item MACs(Message Authentication Codes)
+\end{itemize}
+\textbf{MACs} are appended to messages and act as an authenticator. They are similar to digital signatures but use symmetric encryption.
+\subsubsection{VPN Protocols}
+\paragraph{PPTP(Point to point tunnelling protocol)}
+PPTP was designed by a consortium led by Microsoft. This standard did not use a single form of authentication or encryption, this meant that different PPTP systems were incompatible with each other
+\paragraph{L2TP(Layer 2 Tunnelling Protocol)}
+This is an adaptation of a protocol known as L2F. This combines the features of PPTP and L2F.
+\paragraph{IPSec(Internet Protocol Security)}
+This is the most widely supported protocol. This is very secure due to its use of well known and trusted technologies, which had been under a lot of scrutiny to ensure there are no vulnerabilities.
+\subsubsection{Security risks of a VPN}
+\paragraph{Security of remote machines}
+Remote machines connected to a VPN must be themselves secure, otherwise they would be a vulnerability into a company network.
+\paragraph{Security of the VPN implementation}
+If an insecure VPN implementation, such as PPTP then the network will be insecure.
+\paragraph{Security of network availability}
+AS VPNs rely on the internet for delivering information, there are no guarantees about the reliability.
+\subsection{Detecting attacks}
+\subsubsection{Intrusion detection system(IDS)}
+An there are two types of IDS:
+\begin{itemize}
+\item \textbf{Network intrusion detection system(NIDS)} - Monitors data passing over a network
+\item \textbf{Host intrusion detection system(HIDS)} - Monitoring data to and from a computer
+\end{itemize}
+An IDS can support a network firewall. An IDS then scans any traffic passing through the firewall using a \textbf{NIDS} while also detecting attacks from in the computer using a \textbf{HIDS}.
+\paragraph{Weaknesses}
+\begin{itemize}
+\item Too sensitive, leading to false positives
+\item Not sensitive enough, leading to slow attacks getting through
+\item Relies on software suppliers issuing updates of known signatures
+\end{itemize}
+\subsubsection{How an IDS works in practice}
+\paragraph{Anomaly detection}
+Anomaly detection works on having a model of "normal" network behaviour of users and applications.
+This means that the system is able to detect previously unknown attacks by looking for patterns that deviate from normal behaviour.\\
+A disadvantage of this is that legitimate activities may be incorrectly identified.
+\paragraph{Misuse detection}
+Misuse detection works on the system knowing a set of attack patterns, or "signatures" to compare network activity against.\\
+This has the advantage of minimising false positives. There is the disadvantage that it can only identify attacks where there is a known pattern.
+\subsubsection{Honeypots}
+Sometimes network administrators want to study attacks to develop suitable countermeasures, or as part of an investigation for criminal prosecution.\\
+\\
+One method of doing this is to focus attackers on a computer that seems legitimate, but is actually a closely monitored trap known as a \textbf{honeypot}.
+This means all the attackers actions can be reported without risk to data.\\
+\\
+\section{When your defences fail}
+\subsection{What's the worst that could happen?}
+\subsubsection{Identity theft}
+\textbf{Identity theft} - Where an attacker uses stolen information to impersonate another person.\\
+\paragraph{Preventing identity theft}
+Identity theft can be prevented using an antivirus program and not responding to phishing emails.
+\paragraph{Detecting identity theft}
+Signs a victim might notice:
+\begin{itemize}
+\item Unexplained bank withdrawals
+\item Expected official letters not arriving
+\item Cards or cheques declined
+\item Contacted by debt collectors
+\item Notice from a company that data has been compromised
+\item Bank provider making contact about suspicious behaviour
+\end{itemize}
+\subsubsection{Loss of data}
+Data loss means either the deletion of data or the unauthorised copying of data.
+\paragraph{Insider attacks}
+Insider attacks are where the attacker has direct access to a computer.
+\paragraph{Risks of data loss}
+There are many costs of data loss, including:
+\begin{itemize}
+\item The cost of recreating the data
+\item The cost of continuing without that data
+\item The cost of informing others about the loss
+\end{itemize}
+\subsection{Cyber Security and the law}
+\subsubsection{Laws and Computers}
+\paragraph{Criminal and civil law}
+Law in Britain is divided into two categories:
+\begin{itemize}
+\item \textbf{Criminal law} - Punishing behaviour that is considered unacceptable.
+The majority of cases are brought by the state against individuals and companies.
+These causes require a high standard of proof to secure a convictions.
+They have high punishments.
+\item \textbf{Civil law} - Concerned with disputes, brought before the court by individuals.
+Cover things like property law, contracts and noise.
+These require a lower standard of proof and have financial punishments.
+\end{itemize}
+\paragraph{Bills, acts and laws}
+\textbf{Act of Parliament} - A law approved by the British Parliament\\
+\\
+\textbf{Bill} - The draft of an act which is debated in the house of commons. If the house of Lords and the house of Commons agree the bill is given Royal Ascent and becomes an Act.\\
+\\
+There is often a delay between enactment and implementation in a bill as processes need to be put in place to achieve compliance.
+\subsubsection{The Data Protection Act 1998}
+The data protection act says that organisations are legally obliged to act responsibly with respect to personal information on any living individual on computer databases.\\
+\\
+The DPA enforces strict rules on the storage and processing of electronic data that can uniquely identify a living person.\\
+\\
+\textbf{Data} - A representation of information so that it can be conveyed, manipulated or stored.\\
+\\
+\textbf{Information} - The meaning that we give to data in particular contexts.
+\subsubsection{The Investigatory Powers Act 2016 (IPA)}
+This governs the use of surveillance by public bodies.\\
+\\
+This ensures that intrusive powers are subject to strict safeguards. It allows public bodies to access communication records from communication providers when necessary.\\
+\subsubsection{The Computer Misuse Act 1990(CMA)}
+The original CMA included three new criminal offences:
+\begin{itemize}
+\item Unauthorised access to computer materials
+\item Unauthorised access with intent of committing or aiding further offences
+\end{itemize}
+This has been amended to include denial of service attacks.
+\subsubsection{The Fraud Act 2006}
+This defines fraud in 3 ways:
+\begin{itemize}
+\item False representation
+\item Failing to disclose information
+\item Abusing power
+\end{itemize}
+This can be used to prosecute people:
+\begin{itemize}
+\item Dishonestly obtaining electronic communications services
+\item Cloning mobile phones to bill calls to another person
+\item Reprogramming mobile phones to interfere with their operation
+\item Breaking encryption on encrypted communications services
+\end{itemize}
+\subsubsection{Lawful Business Practice Regulations}
+In UK law, employers have certain rights to monitor communications made by their employees.\\
+\\
+These regulations exist so that employers can ensure that their networks are used in a manner that does not bring the company into disrepute, be used for illegal activities or for personal reasons.\\
+\\
+\subsection{Recovering from attacks on information security}
+\subsubsection{Making your information less vulnerable}
+Firewalls on routers and devices, along with encrypting important information makes data less vulnerable.\\
+Specifying file permissions on important files means that some users won't be able to destroy important data.
+\paragraph{Disabling ports}
+Software can be used to disable USB ports, preventing attacks through them.
+\subsubsection{Protecting data for the future}
+Backups protect from:
+\begin{itemize}
+\item Accidentally deleting a file or program
+\item Losing disks, computers or memory cards
+\item Hardware failures, such as a hard disk crash
+\item Software bugs causing data to be corrupted
+\item Disasters such as fire or flooding
+\item Crimes
+\end{itemize}
+\subsubsection{Remote backups}
+Remote backups allow for protection against data loss by storing backups away from their centre of operation.
+\paragraph{Offsite backups}
+Specialised companies offer storage space to hold backups
+\paragraph{Backing up to the cloud}
+Backing up to the cloud is much cheaper than a dedicated offsite backup, this allows access at any time. However if all data is lost it would take a long time to download all the data.
+\subsubsection{Archiving data}
+Important files should be archived so that they are never overwritten. In the UK this is handled by the National Archives and the British Library.
+\section{Managing security risks}
+\subsection{Analysing security risks}
+\subsubsection{Information as an asset}
+\paragraph{Risk Management}
+Information security risk management assesses the value of information asset belonging to an organisation and protects them on an ongoing basis.\\
+\paragraph{Imperatives and incentives}
+\textbf{Imperatives} - Pressures that force you to act\\
+\textbf{Incentives} - The rewards and opportunities that arise from acting\\
+\\
+The imperatives for information security arise from legislation and regulation.\\
+\\
+The incentive for information security is trust, companies are more likely to work together if their information is secure.
+\subsubsection{Risk analysis}
+\textbf{Risk} - The chance of adverse consequences or loss occurring\\
+\\
+Risks are analysed based on their likelihood and impact
+\subsection{Managing the risks}
+\subsubsection{Staying safe online}
+\paragraph{Updates}
+Software and operating systems should be kept updated in order to be protected from new cyber attacks.
+\paragraph{Basic checklist to stay safe}
+\begin{itemize}
+\item Set up a personal firewall
+\item Install an antivirus program
+\item Get used to making backups
+\item Make sure computers need a password to log in
+\item Use hard disk encryption
+\end{itemize}
+\subsubsection{Risk management in practice}
+Countermeasures to risk:
+\begin{itemize}
+\item Avoiding the risk
+\item Modifying the risk to be less
+\item Transferring the risk to others
+\item Accepting the risk
+\end{itemize}
+
 \end{document}

### 2017-11-12 Maths Notes/M2/Collisions/Collisions.tex
Updated notes to current date (12/11/17)

--- 2017-11-01 Maths Notes/M2/Collisions/Collisions.tex
@@
 \end{center}
-\begin{obeylines}
 \section{Impulse and momentum}
 Impulse=$mv-mu$=$Ft$\\
-Total momentum before collision=total momentum after\\
+Total momentum before collision=total momentum after
 \section{Coefficient of restitution}
@@
 If $e=0$ the ball doesn't bounce\\
+\\
 $e=\dfrac{\text{Speed of seperation}}{\text{Speed of approach}}$
+\subsection{Alternate form of coefficient of restitution formula}
+$mgh=\frac{1}{2}mv^2$\\
+\\
+$v=\sqrt{2gh}$\\
+\\
+$e=\dfrac{\sqrt{2gh_2}}{\sqrt{2gh_1}}$\\
+\\
+$e=\dfrac{\sqrt{h_2}}{\sqrt{h_1}}$\\
+\\
+$h_2$ - the height the ball bounces back to\\
+\\
+$h_1$ - the height the ball is dropped from
+\subsection{Calculations involving coefficient of restitution}
+When doing calculations involving the coefficient of restitution both the calculation for CoR and conservation of momentum will be needed.\\
+\textbf{Conservation of momentum:}
+$m_1u_1+m_2u_2=m_1v_1+m_2v_2$\\
+\\
+\textbf{Coefficient of restitution}\\
+\\
+$e=\dfrac{v_1}{u_1}$
+\subsection{Successive Impacts}
+In some cases calculations will involve the impacts of multiple balls successively, like in newton's cradle.
+\subsubsection{Example}
+\textit{Three perfectly elastic particles A, B and C with masses 3kg, 2kg and 1kg respectively lie at rest in a straight line on a smooth horizontal table in alphabetical order.
+A is projected towards B with speed $5ms^{-1}$ and after A has collided with B, B collides with C}\\
+\\
+$5\times3=3V_A+2V_B$\\
+\\
+$1=\dfrac{SoS}{SoA}$ therefore $SoS=SoA$ so $V_B-V_A=5$ so $V_B=5+V_A$\\
+\\
+$15=10+2V_A+3V_A$\\
+\\
+$15=2V_B+3$ so after 1st collision $V_B=6$\\
+\\
+$15=10+5V_A$ so $\mathbf{V_A=1}$\\
+\\
+\textbf{2nd Collision}\\
+\\
+$2\times6=2V_B+V_C$\\
+\\
+$V_C-V_B=6$\\
+\\
+$12=3V_B+6$\\
+\\
+$3V_B=6$\\
+\\
+$\mathbf{V_B=2}$\\
+\\
+$V_C=6+2=8$
 
-\end{obeylines}
 \end{document}

### 2017-11-12 Maths Notes/S2/Hypothesis testing/Hypothesis testing.tex
Updated notes to current date (12/11/17)

@@
 \subsection{Two tailed tests}
+When doing a two tailed test the significance level must be split in two. For example if the significance level is 5\% then it must be split into 2.5\% for each tail.\\
+\\
+Two tailed test also concern equal or not equal, rather than inequalities, for example:\\
+$H_0 : p=0.15$\\
+$H_1 : p\neq0.15$
 

### 2017-11-12 Physics Notes/Capacitors/Capacitors.tex
Updated notes to current date (12/11/17)

@@
 \pgfplotsset{width=10cm,compat=1.9}
-
+\usepackage{relsize}
 \titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
@@
 The battery supplies energy QV to the circuit but the capacitor only stores $\frac{1}{2}QV$, this means that 50\% of the energy provided by the battery is wasted due to resistance in the circuit.
-
+\section{Charging and discharging a capacitor}
+\begin{tikzpicture}[scale=0.5]
+\begin{axis}[ticks=none,ylabel=Voltage\textbackslash V,xlabel=Time\textbackslash S,axis lines=middle,
+label style={font=\large},xmin=0,xmax=2, 
+ x label style={at={(axis description cs:0.5,0)},anchor=north,font=\LARGE},
+ y label style={at={(axis description cs:0,.5)},rotate=90,anchor=south,font=\LARGE},
+]
+\addplot[mark=none,domain=0:2]{1/exp(x)};
+\end{axis}
+\end{tikzpicture}\\
+The smaller the resistor connected to the capacitor, the steeper the initial gradient\\
+\\
+$\text{p.d.}\propto \text{rate of change of p.d.}$\\
+\\
+\textbf{Formula for discharge of a capacitor}\\
+$\mathlarger{\mathlarger{Q=Q_0e^{-\frac{t}{RC}}}}$\\
+\\
+Where:\\
+Q=Charge at time, t\\
+$Q_0$=Initial charge\\
+\\
+$\mathlarger{\mathlarger{e^{-\frac{t}{RC}}}}$=Multiplication factor between 0 and 1\\
+\\
+This also works for:\\
+\\
+$\mathlarger{\mathlarger{V=V_0e^{-\frac{t}{RC}}}}$\\
+\textbf{Formula for charging of a capacitor}\\
+$\mathlarger{\mathlarger{Q=Q_0(1-e^{-\frac{t}{RC}})}}$\\
+\\
+\textbf{Rearranging for time}\\
+\\
+$\mathlarger{\mathlarger{V=V_0e^{-\frac{t}{RC}}}}$\\
+\\
+$\dfrac{V}{V_0}=e^{-\frac{t}{RC}}$\\
+$\ln\Big(\dfrac{V}{V_0}\Big)=-\dfrac{t}{RC}$\\
+$t=-RC\ln\Big(\dfrac{V}{V_0}\Big)$\\
+$t=RC\ln\Big(\dfrac{V_0}{V}\Big)$\\
+\\
+\subsection{Proof of the units of the time constant being seconds}
+$\tau=RC$\\\\
+$\tau=\dfrac{V}{I}\times\dfrac{Q}{V}=\dfrac{Q}{I}$\\
+\\
+$\dfrac{Q}{I}=t$(unit seconds)
 \end{document}

### 2017-11-12 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
Updated notes to current date (12/11/17)

--- 2017-11-01 Physics Notes/Further Mechanics and Thermal Physics/Circular Motion/Circular Motion.tex
@@
 \pgfplotsset{width=10cm,compat=1.9}
+\usepackage{gensymb}
 
@@
 \begin{center}
-\underline{\huge Circular Motion}
+\underline{\huge Thermal Physics}
 \end{center}
-\section{Introduction to circular motion}
-For an object to be going in a circle a force is needed to accelerate the object. This is because in a circle an object is constantly changing velocity, even if it isn't changing speed.\\
-Centripetal force is not an extra force, it is just the name for a resultant force.\\
-For an object to be deflected towards the centre, there needs to be a force acting towards the centre.
-\subsection{Definitions}
-\begin{tabular}{|c|c|c|c|}
+\section{Differences between heat and temperature}
+\begin{tabular}{|c|c|c|}
 \hline
-Quantity&Symbol&Unit&Definition\\
+&Heat&Temperature\\
 \hline
-Period&T&Seconds,s&The time taken for an object to complete one revolution\\
+Definition&Thermal energy(transferred from hot to cooler places)&A comparative measure of how hot something is\\
 \hline
-Frequency&f&Hertz,hz&The number of revolutions per second\\
+Unit&Joule&Kelvin\\
 \hline
-Angular velocity&$\omega$&$\textrm{rads}^{-1}$&The rate of change in angle(the angle covered per second)\\
+Measured using&Joulemeter&Thermometer\\
 \hline
 \end{tabular}
-\subsection{Formula not on formula book}
-$\omega=\dfrac{\Delta\theta}{\Delta t}$\\
-$a=\dfrac{\Delta V}{\Delta t}$\\
-Don't forget application of  $F=ma$ with the equations for force
-\section{Circular motion for going over a hump}
-\begin{tikzpicture}[
-    force/.style={>=latex,draw=black,fill=black},
-    m/.style={rectangle,draw=black,fill=white,minimum size=0.3cm,thin},
-]
-    \node[m] (m) {};
-    {[force,->]
-        \draw (m.north) -- ++(0,1) node[above] {$r$};
-        \draw (m.south) -- ++(0,-1) node[below] {$mg$};
-    }
-\end{tikzpicture}
+\section{Graph of heating water}
+\includegraphics[width=3in]{water_heat_curve.jpg}
+\section{Specific heat capacity}
+\textbf{Specific heat capacity} - The energy needed to raise the temperature of 1kg of a material by 1K\\
 \\
-For an object going over a hump the force of the weight is in the opposite direction to the reaction force.\\
-The object will leave the ground if $mg>r$.
-\subsection{Calculations}
-$F_c=mg-R=\dfrac{mv^2}{r}$\\
-\textbf{Calculating the speed at which the car will leave the ground (R=0)}\\
-$mg=\dfrac{mv_0^2}{r} \qquad V_0=\sqrt{gr}$\\
-Once the car has left the ground, use SUVAT equations rather than circular motion.
-\section{Roundabouts}
-On a roundabout the centripetal force is provided by friction.\\
-$F_r=\dfrac{mv_0^2}{r}$\\
-To avoid slipping, the centripetal force must be less than the maximum possible for the car and road surface.\\
-\textbf{Example question}
-\textit{The maximum possible force of friction between a car and the road is 800N, given a mass of 1000kg and a radius of 5m, what is the maximum speed the car can go without slipping}
-\newpage
-\section{Banked motion}
-N is the reaction force\\
-$n\sin\theta=\dfrac{mv^2}{r}$ - Force towards the centre of notion is equal to the centripetal force\\
-$N\cos\theta=mg$ - The force vertically downwards is equal to the weight\\
-$\tan\theta=\dfrac{v^2}{rg}$ - Combining the equations\\
-$v^2=gr\tan\theta$ - Re-write
-\section{Forces in a circle}
-\begin{tikzpicture}[
-    force/.style={>=latex,draw=black,fill=black},
-    m/.style={rectangle,draw=black,fill=lightgray,minimum size=0.3cm,thin},
-]
-    \node[m] (m) at (0,-2) {};
-    \node[m] (m2) at (0,2) {};
-    \node[m] (m3) at (2,0) {};
-    {[force,->]
-        \draw (m.north) -- ++(0,0.7) node[above] {$R$};
-        \draw (m.south) -- ++(0,-0.7) node[right] {$mg$};
-    }
-    {[force,->]
-        \draw (m2.south) -- ++(0,-0.7) node[below] {$R+mg$};
-    }
-    {[force,->]
-        \draw (m3.west) -- ++(-0.7,0) node[left] {$R$};
-        \draw (m3.south) -- ++(0,-0.7) node[below right] {$mg$};
-    }
-
-\begin{pgfonlayer}{background layer}
-    \draw[color=black, very thick](0,0) circle (2);
-    \end{pgfonlayer}{background layer}
-\end{tikzpicture}
+$c=\dfrac{Q}{m\Delta\theta}$\\
 \\
-Top: Centripetal force = $R+W$\\
-Side: Centripetal force = $R$\\
-Bottom: Centripetal force = $R-W$\\
-At the top of the loop r=0\\
-$v=\sqrt{gr}$
+c=Specific heat capacity - $Jkg^{-1} \ \degree C$\\
+m=Mass - $kg$\\
+$\Delta\theta$ = Temperature change - $\degree C$\\
+Q = Heat energy - $J$
+\subsection{Latent heat}
+\textbf{Specific latent heat of fusion, $\mathbf{L_f}$} \quad \textcolor{red}{$Q=mL_f$}\\
+The energy needed to change 1kg of a solid to a liquid without a temperature change\\
+\\
+\textbf{Specific latent heat of vaporisation, $\mathbf{L_v}$} \quad \textcolor{red}{$Q=mL_v$}\\
+The energy needed to change 1kg of a liquid to a vapour without a temperature change
 

### 2017-11-12 Maths Notes/D2/Travelling Salesman Problem/Travelling Salesman Problem.tex
Updated Timetable to current week

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{enumerate}
\usepackage{amssymb}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{tikz}
\usetikzlibrary{calc}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}	
\newcommand{\cred}[1]{\color{red}#1}
\newcommand{\cblue}[1]{\color{blue}#1}
\newcommand{\cgreen}[1]{\color{green}#1}
\hyphenpenalty=10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - D2}
\rfoot{Page \thepage}
\usepackage{float}

\newcommand{\tikzmark}[1]{\tikz[overlay,remember picture] \node (#1) {};}

\newcommand{\DrawVLine}[3][]{%
    \begin{tikzpicture}[overlay,remember picture]
        \draw [#1] ($(#2.north)$) -- ($(#3.north)$);
    \end{tikzpicture}%
}%
\newcommand{\DrawLine}[3][]{%
    \begin{tikzpicture}[overlay,remember picture]
        \draw [#1] ($(#2)+(-0.4,0.6ex)$) -- ($(#3)+(0.6,0.6ex)$);
    \end{tikzpicture}%
}%

\begin{document}
\begin{center}
\underline{\huge Allocation Problems}
\end{center}
\section{Cost Matrices}
\begin{itemize}
\item Require the same number of tasks as workers
\item Only relative costs are important
\end{itemize}
To find a reduced cost matrix:
\begin{enumerate}
\item Subtract the least value in each row from each element of that row
\item Using the new matrix, subtract the least value in each column from each element in that column
\end{enumerate}
\section{Hungarian algorithm}
\begin{enumerate}
\item Find the reduced cost matrix
\item Determine the minimum number of horizontal or vertical straight lines which will cover all the zeros in the matrix
\begin{itemize}
\item If lines $\geqslant$ n, where the matrix is n$\times$n then STOP
\item If lines $<$n, the matrix can be improved and continue 
\end{itemize}
\item Draw in the lines and look for the smallest uncovered element, call it $e$
\item Add $e$ to all covered elements, add it twice if covered twice
\item Subtract $e$ from \textbf{all} elements of the matrix (even those that just had $e$ added)
\item Repeat steps 2-5 until an optimal solution is found
\end{enumerate}
\subsection{Example}
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&250&80&160\\
\hline
Percival&230&90&150\\
\hline
Spike&230&110&140\\
\hline
\end{tabular}\\
\\
\textbf{Find the reduced cost matrix - First process rows}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&170&0&80\\
\hline
Percival&140&0&60\\
\hline
Spike&120&0&30\\
\hline
\end{tabular}\\
\\
\textbf{Find the reduced cost matrix - process columns}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&50&0&50\\
\hline
Percival&20&0&30\\
\hline
Spike&0&0&0\\
\hline
\end{tabular}\\
\textbf{Draw lines to cover zeros}\\
$
\begin{array}{|c|c|c|c|}
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartB}}&
\multicolumn{1}{c}{}\\
\hline
&Dig&Weed&Cut\\
\hline
Boris&50&0&50\\
\hline
Percival&20&0&30\\
\hline
\tikzmark{StartA}Spike&0&0&\tikzmark{EndA}0\\
\hline

\multicolumn{1}{c}{}&
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndB}}}&
\multicolumn{1}{c}{}\\
\end{array}\\
$
\DrawLine[red, very thick,dotted]{StartA}{EndA}
\DrawVLine[red,very thick,dotted]{StartB}{EndB}
\\
\textbf{Compare to dimension of matrix}\\
2 Lines$\leqslant$3$\times$3 matrix\\
\\
\textbf{Find the smallest uncovered element}\\
20 (Percival digging)\\
\\
\\
\textbf{Add e to all covered elements, and add twice for double covering}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&50&20&50\\
\hline
Percival&20&20&30\\
\hline
Spike&20&40&20\\
\hline
\end{tabular}\\
\\
\textbf{Subtract e from all elements}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&30&0&30\\
\hline
Percival&0&0&10\\
\hline
Spike&0&20&0\\
\hline
\end{tabular}\\
\\
\textbf{Draw lines to cover zeros}\\
\\
$
\begin{array}{|c|c|c|c|}
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartA}}&
\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartB}}&
\multicolumn{1}{c}{}\\
\hline
&Dig&Weed&Cut\\
\hline
Boris&30&0&30\\
\hline
Percival&0&0&10\\
\hline
\tikzmark{StartC}Spike&0&20&\tikzmark{EndC}0\\
\hline
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndA}}}&
\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndB}}}&
\multicolumn{1}{c}{}\\
\end{array}\\
$
\DrawVLine[red, very thick,dotted]{StartA}{EndA}
\DrawVLine[red, very thick,dotted]{StartB}{EndB}
\DrawLine[red, very thick,dotted]{StartC}{EndC}
\\
\textbf{Compare to dimension of matrix}\\
3 lines=$3\times3$ matrix - Optimal solution
\section{Dummy Locations}
When the problem is not n$\times$n a dummy location is used, this has zeroes in all the elements.
\subsection{Example}
\begin{tabular}{|c|c|c|c|}
\hline
&Task A&Task B&Task C\\
\hline
Mark&12&23&15\\
\hline
Nicky&14&21&17\\
\hline
Nigel&13&22&20\\
\hline
Susie&14&24&13\\
\hline
\end{tabular}\\
\\
\textbf{Add another task with zero cost}\\
\begin{tabular}{|c|c|c|c|c|}
\hline
&Task A&Task B&Task C&Task D\\
\hline
Mark&12&23&15&0\\
\hline
Nicky&14&21&17&0\\
\hline
Nigel&13&22&20&0\\
\hline
Susie&14&24&13&0\\
\hline
\end{tabular}\\
\\
\textbf{This is then processed as usual}
\section{Incomplete data}
The algorithm can also work on incomplete data (where a person cannot to a task). To do this assign values to the tasks that cannot be done that are at least \textbf{twice as large} as the largest value.
\subsection{Example}
\begin{tabular}{|c|c|c|c|c|}
\hline
&Chinese&French&Indian&Italian\\
\hline
Denis&-&27&15&40\\
\hline
Hilary&14&21&17&13\\
\hline
Robert&20&-&13&-\\
\hline
Trudy&14&24&10&30\\
\hline
\end{tabular}
\newpage
\textbf{The cells with dashes in are then replaced with 100}\\
\begin{tabular}{|c|c|c|c|c|}
\hline
&Chinese&French&Indian&Italian\\
\hline
Denis&\textcolor{red}{100}&27&15&40\\
\hline
Hilary&14&21&17&13\\
\hline
Robert&20&\textcolor{red}{100}&13&\textcolor{red}{100}\\
\hline
Trudy&14&24&10&30\\
\hline
\end{tabular}\\
\\
\textbf{This can then be processed as normal}
\end{document}

### 2017-11-12 Maths Notes/D2/Travelling Salesman Problem/Travelling Salesman Problem.tex
Notes and Timetable update

@@
 \begin{center}
-\underline{\huge Allocation Problems}
+\underline{\huge Travelling Salesman Problem}
 \end{center}
-\section{Cost Matrices}
-\begin{itemize}
-\item Require the same number of tasks as workers
-\item Only relative costs are important
-\end{itemize}
-To find a reduced cost matrix:
-\begin{enumerate}
-\item Subtract the least value in each row from each element of that row
-\item Using the new matrix, subtract the least value in each column from each element in that column
-\end{enumerate}
-\section{Hungarian algorithm}
-\begin{enumerate}
-\item Find the reduced cost matrix
-\item Determine the minimum number of horizontal or vertical straight lines which will cover all the zeros in the matrix
-\begin{itemize}
-\item If lines $\geqslant$ n, where the matrix is n$\times$n then STOP
-\item If lines $<$n, the matrix can be improved and continue 
-\end{itemize}
-\item Draw in the lines and look for the smallest uncovered element, call it $e$
-\item Add $e$ to all covered elements, add it twice if covered twice
-\item Subtract $e$ from \textbf{all} elements of the matrix (even those that just had $e$ added)
-\item Repeat steps 2-5 until an optimal solution is found
-\end{enumerate}
-\subsection{Example}
-\begin{tabular}{|c|c|c|c|}
-\hline
-&Dig&Weed&Cut\\
-\hline
-Boris&250&80&160\\
-\hline
-Percival&230&90&150\\
-\hline
-Spike&230&110&140\\
-\hline
-\end{tabular}\\
+\section{Definitions}
+The travelling salesman problem looks for a \textbf{walk} that gives the minimum \textbf{tour}.\\
 \\
-\textbf{Find the reduced cost matrix - First process rows}\\
-\begin{tabular}{|c|c|c|c|}
-\hline
-&Dig&Weed&Cut\\
-\hline
-Boris&170&0&80\\
-\hline
-Percival&140&0&60\\
-\hline
-Spike&120&0&30\\
-\hline
-\end{tabular}\\
+\textbf{Walk} - A finite series of edges so that the end of one vertex is the start of the next\\
 \\
-\textbf{Find the reduced cost matrix - process columns}\\
-\begin{tabular}{|c|c|c|c|}
-\hline
-&Dig&Weed&Cut\\
-\hline
-Boris&50&0&50\\
-\hline
-Percival&20&0&30\\
-\hline
-Spike&0&0&0\\
-\hline
-\end{tabular}\\
-\textbf{Draw lines to cover zeros}\\
-$
-\begin{array}{|c|c|c|c|}
-\multicolumn{1}{c}{}&
-\multicolumn{1}{c}{}&
-\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartB}}&
-\multicolumn{1}{c}{}\\
-\hline
-&Dig&Weed&Cut\\
-\hline
-Boris&50&0&50\\
-\hline
-Percival&20&0&30\\
-\hline
-\tikzmark{StartA}Spike&0&0&\tikzmark{EndA}0\\
-\hline
-
-\multicolumn{1}{c}{}&
-\multicolumn{1}{c}{}&
-\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndB}}}&
-\multicolumn{1}{c}{}\\
-\end{array}\\
-$
-\DrawLine[red, very thick,dotted]{StartA}{EndA}
-\DrawVLine[red,very thick,dotted]{StartB}{EndB}
+\textbf{Tour} - A walk that visits every vertex and returns to the starting vertex
 \\
-\textbf{Compare to dimension of matrix}\\
-2 Lines$\leqslant$3$\times$3 matrix\\
+\textbf{Add more information about upper and lower bounds here when you understand it more}
+\section{The differences between classical and practical problems}
+\textbf{Classical Problem} - Must visit each vertex \textbf{only once} before returning to the start.\\
+\textbf{Practical Problem} - Must visit each vertex \textbf{at least once} before returning to the start
+\section{Converting a network into a complete network of least distances}
+If a network is converted into a complete network of least distances, the classical and practical problem are the same.\\
 \\
-\textbf{Find the smallest uncovered element}\\
-20 (Percival digging)\\
+To create a complete network of least distances, you must ensure the \textbf{triangle inequality} holds for all triangles in the network.\\
 \\
+\textbf{Triangle inequality:}\\
+The longest side of any triangle $\leqslant$ The sum of the two shorter sides\\
 \\
-\textbf{Add e to all covered elements, and add twice for double covering}\\
-\begin{tabular}{|c|c|c|c|}
-\hline
-&Dig&Weed&Cut\\
-\hline
-Boris&50&20&50\\
-\hline
-Percival&20&20&30\\
-\hline
-Spike&20&40&20\\
-\hline
-\end{tabular}\\
-\\
-\textbf{Subtract e from all elements}\\
-\begin{tabular}{|c|c|c|c|}
-\hline
-&Dig&Weed&Cut\\
-\hline
-Boris&30&0&30\\
-\hline
-Percival&0&0&10\\
-\hline
-Spike&0&20&0\\
-\hline
-\end{tabular}\\
-\\
-\textbf{Draw lines to cover zeros}\\
-\\
-$
-\begin{array}{|c|c|c|c|}
-\multicolumn{1}{c}{}&
-\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartA}}&
-\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartB}}&
-\multicolumn{1}{c}{}\\
-\hline
-&Dig&Weed&Cut\\
-\hline
-Boris&30&0&30\\
-\hline
-Percival&0&0&10\\
-\hline
-\tikzmark{StartC}Spike&0&20&\tikzmark{EndC}0\\
-\hline
-\multicolumn{1}{c}{}&
-\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndA}}}&
-\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndB}}}&
-\multicolumn{1}{c}{}\\
-\end{array}\\
-$
-\DrawVLine[red, very thick,dotted]{StartA}{EndA}
-\DrawVLine[red, very thick,dotted]{StartB}{EndB}
-\DrawLine[red, very thick,dotted]{StartC}{EndC}
-\\
-\textbf{Compare to dimension of matrix}\\
-3 lines=$3\times3$ matrix - Optimal solution
-\section{Dummy Locations}
-When the problem is not n$\times$n a dummy location is used, this has zeroes in all the elements.
-\subsection{Example}
-\begin{tabular}{|c|c|c|c|}
-\hline
-&Task A&Task B&Task C\\
-\hline
-Mark&12&23&15\\
-\hline
-Nicky&14&21&17\\
-\hline
-Nigel&13&22&20\\
-\hline
-Susie&14&24&13\\
-\hline
-\end{tabular}\\
-\\
-\textbf{Add another task with zero cost}\\
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-&Task A&Task B&Task C&Task D\\
-\hline
-Mark&12&23&15&0\\
-\hline
-Nicky&14&21&17&0\\
-\hline
-Nigel&13&22&20&0\\
-\hline
-Susie&14&24&13&0\\
-\hline
-\end{tabular}\\
-\\
-\textbf{This is then processed as usual}
-\section{Incomplete data}
-The algorithm can also work on incomplete data (where a person cannot to a task).
-To do this assign values to the tasks that cannot be done that are at least \textbf{twice as large} as the largest value.
-\subsection{Example}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-&Chinese&French&Indian&Italian\\
-\hline
-Denis&-&27&15&40\\
-\hline
-Hilary&14&21&17&13\\
-\hline
-Robert&20&-&13&-\\
-\hline
-Trudy&14&24&10&30\\
-\hline
-\end{tabular}
-\newpage
-\textbf{The cells with dashes in are then replaced with 100}\\
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-&Chinese&French&Indian&Italian\\
-\hline
-Denis&\textcolor{red}{100}&27&15&40\\
-\hline
-Hilary&14&21&17&13\\
-\hline
-Robert&20&\textcolor{red}{100}&13&\textcolor{red}{100}\\
-\hline
-Trudy&14&24&10&30\\
-\hline
-\end{tabular}\\
-\\
-\textbf{This can then be processed as normal}
+In a network where the triangle inequality does not hold, replace the longest arc with the sum of the two shorter ones.
 \end{document}

### 2017-11-15 Physics Notes/Capacitors/Capacitors.tex
Update to capacitor notes

--- 2017-11-05 Physics Notes/Capacitors/Capacitors.tex
@@
 The battery supplies energy QV to the circuit but the capacitor only stores $\frac{1}{2}QV$, this means that 50\% of the energy provided by the battery is wasted due to resistance in the circuit.
-
+\section{Charging and discharging a capacitor}
+\begin{tikzpicture}[scale=0.5]
+\begin{axis}[ticks=none,ylabel=Voltage\textbackslash V,xlabel=Time\textbackslash S,axis lines=middle,
+label style={font=\large},xmin=0,xmax=2, 
+ x label style={at={(axis description cs:0.5,0)},anchor=north,font=\LARGE},
+ y label style={at={(axis description cs:0,.5)},rotate=90,anchor=south,font=\LARGE},
+]
+\addplot[mark=none,domain=0:2]{1/exp(x)};
+\end{axis}
+\end{tikzpicture}\\
+The smaller the resistor connected to the capacitor, the steeper the initial gradient\\
+\\
+$\text{p.d.}\propto \text{rate of change of p.d.}$\\
+\\
+\textbf{Formula for discharge of a capacitor}\\
+$\mathlarger{\mathlarger{Q=Q_0e^{-\frac{t}{RC}}}}$\\
+\\
+Where:\\
+Q=Charge at time, t\\
+$Q_0$=Initial charge\\
+\\
+$\mathlarger{\mathlarger{e^{-\frac{t}{RC}}}}$=Multiplication factor between 0 and 1\\
+\\
+This also works for:\\
+\\
+$\mathlarger{\mathlarger{V=V_0e^{-\frac{t}{RC}}}}$\\
+\textbf{Formula for charging of a capacitor}\\
+$\mathlarger{\mathlarger{Q=Q_0(1-e^{-\frac{t}{RC}})}}$\\
+\\
+\textbf{Rearranging for time}\\
+\\
+$\mathlarger{\mathlarger{V=V_0e^{-\frac{t}{RC}}}}$\\
+\\
+$\dfrac{V}{V_0}=e^{-\frac{t}{RC}}$\\
+$\ln\Big(\dfrac{V}{V_0}\Big)=-\dfrac{t}{RC}$\\
+$t=-RC\ln\Big(\dfrac{V}{V_0}\Big)$\\
+$t=RC\ln\Big(\dfrac{V_0}{V}\Big)$\\
+\\
+\subsection{Proof of the units of the time constant being seconds}
+$\tau=RC$\\\\
+$\tau=\dfrac{V}{I}\times\dfrac{Q}{V}=\dfrac{Q}{I}$\\
+\\
+$\dfrac{Q}{I}=t$(unit seconds)
+\section{Capacitor Discharge Theory}
+RC controls the date of discharge
+\subsection{How much time remains after 1 time constant}
+$Q=Q_0e^{-\frac{t}{RC}}$\\
+\\
+$Q=Q_0e^{-\frac{RC}{RC}}$\\
+\\
+$Q=Q_0e^{-1}$\\
+\\
+$e^{-1}$ is approximately 37\%, this means that when charge is 37\% of the initial value, 1 time constant will have passed.
+\subsection{Alternate way of finding the time constant}
+The $x$ intercept of the graph of voltage against time if the initial gradient is continued is the time constant.
+\subsection{3rd method of finding the time constant}
+The formula $V=V_0e^{-\frac{t}{RC}}$ can be rearranged to $RC=\dfrac{t}{\ln(\frac{v_0}{v})}$.\\
+This means that using the initial voltage and the voltage at a point in time, the time constant can be calculated.
 \end{document}

### 2017-11-16 Maths Notes/D2/Travelling Salesman Problem/Travelling Salesman Problem.tex
Update to Notes

@@
 In a network where the triangle inequality does not hold, replace the longest arc with the sum of the two shorter ones.
+\section{Using a Minimum Spanning tree to find the upper bound of the travelling salesman problem}
+Method:
+\begin{itemize}
+\item Find the minimum spanning tree(Prim's or Kruskal's). This guarantees all vertexes are included.
+\item Double the length of the minimum spanning tree as the route includes going there and back.
+\item Find "short cuts"(using the non included arcs to bypass repeated edges.
+\end{itemize}
+This algorithm gives the initial upper bound
 \end{document}

### 2017-11-16 Maths Notes/S2/Population and Samples/Population and Samples.tex
Update to Notes

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}
\usepackage{tabularx}
\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Population and Samples}
\end{center}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
  \textbf{Term} & \textbf{Definition} \\
\hline
Population&A collection of individual people or items\\
\hline
Finite population&Countable\\
\hline
Infinite population&Impossible to count (different from infinite number, e.g. grains of sand)\\
\hline
Census&Information obtained from all members of the population\\
\hline
Advantages of a census&
\begin{itemize}
\item Every single member of the population is used
\item It is unbiased
\item It gives an accurate answer
\end{itemize}\\
\hline
Disadvantages of a census&
\begin{itemize}
\item Takes a long time
\item Costly
\item Difficult to ensure the whole population is surveyed
\end{itemize}\\
\hline
Sample&A subset of the population\\
\hline
Sampling units&Individual units of the population (e.g. people)\\
\hline
Sampling frame&Individually named or numbered sampling units to form a list or other representation of data\\
\hline
Advantages of sampling&
\begin{itemize}
\item If the population is large and well mixed the sample will be representative
\item Cheaper than a census
\item Advantageous when testing results in destruction
\item Data is more readily available
\end{itemize}\\
\hline
Disadvantages of sampling&
\begin{itemize}
\item Uncertainty as there is variation between samples
\item Could have bias
\end{itemize}\\
\hline
Bias&Anything which prevents a sample becoming truly representative\\
\hline
Statistic&A quantity calculated solely from the observations in a sample. It does not involve any unknown parameters\\
\hline
Simple random sampling&A sample taken so every possible sample has equal chance of being selected\\
\hline
\end{tabularx}

\end{document}

### 2017-11-18 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
Notes Update

@@
 The energy needed to change 1kg of a liquid to a vapour without a temperature change
-
+\subsection{How to determine the specific heat capacity of a metal}
+\includegraphics[width=2in]{SHC_Experiment.jpg}
+\begin{enumerate}
+\item Set up the experiment with a voltmeter and ammeter to determine the electrical power of the heater
+\item Allow time for the heat to conduct through the metal (until there is a temperature rise)
+\item Start a stopclock, record the V, I and temperature
+\item Record V, I and T every 2 minutes for 20 minutes
+\end{enumerate}
+\section{Boyle's law}
+Boyle's law - Pressure is inversely proportional to volume\\
+Gases - Free moving particles, no forces\\
+$$\text{Boyle's law: } P=kV^{g}$$
+$$\ln(P)=\ln(k)+g\ln(V)$$
+$$\text{This is in the form y=c+mx}$$
 \end{document}

### 2017-11-18 Physics Notes/Practical Notes/Practical Notes.tex
Notes Update

--- 2017-11-05 Physics Notes/Capacitors/Capacitors.tex
@@
 \rhead{Sam Robbins 13SE}
-\lhead{A Level Physics - Fields}
+\lhead{A Level Physics - Practical Skills}
 \rfoot{Page \thepage}
@@
 \begin{center}
-\underline{\huge Capacitors}
+\underline{\huge Practical Skills}
 \end{center}
-A capacitor is constructed from two conducting plates separated by an insulator.\\
-Charge can flow onto and off the plates but not across the plates.
-
-\section{Charging circuit for a capacitor}
-\begin{center}
-\begin{circuitikz}[american voltages]
-\draw
-  (0,0) to [short] (3,0)
-  to [battery] (4,0)
-  (4,0) to[short] (5,0)
-  (4.4,-3) node[spdt](spdt) {}
-  (5,0) to[short] (spdt.out 1)
-  (spdt.in) to [capacitor] (2,-3)
-  (2,-3) to[short] (0,-3)
-(0,-3) to[short] (0,0)
-(spdt.out 2) to [short] (5,-5) 
-(5,-5) to[lamp] (1,-5) 
-(1,-5) to[short] (0,-5)
-(0,-5) to[short] (0,-3)
-  ;
-  \end{circuitikz}
-  \end{center}
-
-When charging the current flows round the top half of the circuit, when discharging the SPDT is changed to the other output and the current flows round the bottom half of the circuit.\\
+\section{\% error on gradient}
+Total \% error = \% error on X + \% error on Y\\
 \\
-Capacitors can be used as simple timers in circuits.
-\\
-\\
-The time it takes to charge/discharge depends on:
-\begin{itemize}
-\item The capacitance of the capacitor \textbf{(C)}
-\item The resistance of the charging/discharging circuit \textbf{(R)}
-\end{itemize}
-\section{Energy stored in a capacitor}
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[xmin=0,ymin=-0.01,ylabel=V,xlabel=Q,axis lines=middle,label style={font=\LARGE},
-ytick={2},yticklabels=v,
-ticklabel style = {font=\LARGE},
-xtick={1.5,2.5},xticklabels={q,q+$\Delta$q}
-]
-\addplot[mark=none]{x};
-\addplot [mark=none] coordinates {(1.5,0) (1.5, 1.5)};
-\addplot [mark=none] coordinates {(2.5,0) (2.5, 2.5)};
-\addplot[mark=none,domain=0:2]{2};
-\end{axis}
-\filldraw[black, ultra thin,fill=gray!70] (2.5,0) -- (4.2,0) -- (4.2,3.5) -- (2.5,2.1) -- cycle;
-\end{tikzpicture}\\
-Area under graph=work done\\
-V is the average P.D. as charge increases from q to q+$\Delta$q\\
-$\Delta \text{w=v}\Delta \text{q}$\\
-\\
-$Q=\frac{1}{2}QV=E$  \textbf{(Work done=energy stored)}\\
-\\
-How to answer the exam question: Show that the energy stored by a capacitor is given by $E=\frac{1}{2}QV$
-\begin{enumerate}
-\item Sketch a graph of Q against V and describe what it shows
-\item Describe that electrical energy is the product of charge and voltage
-\item State QV is represented by the area under the line
-\item The area under the line is a triangle with area =$\frac{1}{2}QV$
-\item Therefore $E=\frac{1}{2}QV$
-\end{enumerate}
-$E=\frac{1}{2}QV$\\
-$Q=CV$\\
-Therefore:\\
-$E=\frac{1}{2}CV^2$\\
-$E=\frac{1}{2}\dfrac{Q^2}{C}$\\
-\\
-The battery supplies energy QV to the circuit but the capacitor only stores $\frac{1}{2}QV$, this means that 50\% of the energy provided by the battery is wasted due to resistance in the circuit.
-
+\% error on X = 1 Small Square/Number of squares on triangle\\
+\% error on Y = 1 Small Square/Number of squares on triangle\\
 \end{document}

### 2017-11-23 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
Notes Update

@@
 \usepackage{gensymb}
-
+\usepackage{tabularx}
 \titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
@@
 \end{enumerate}
-\section{Boyle's law}
+\section{Gas laws}
+\subsection{Boyle's law}
 Boyle's law - Pressure is inversely proportional to volume\\
@@
 $$\text{This is in the form y=c+mx}$$
+\subsection{Summary of gas laws}
+\begin{tabularx}{\textwidth}{|X|X|X|X|}
+\hline
+Law&Proportionality&Constant&Equation\\
+\hline
+Boyle's&$p\propto\dfrac{1}{v}$&Temperature, moles&$p_1v_1=p_2v_2$\\
+\hline
+Charles'&$V\propto T$&Pressure, moles&$\dfrac{v_1}{T_1}=\dfrac{v_2}{T_2}$\\
+\hline
+Gay-Lussac&$p\propto T$&Volume, moles&$\dfrac{p_1}{T_1}=\dfrac{P_2}{T_2}$\\
+\hline
+\end{tabularx}
+\newpage
+\subsection{Ideal Gas equation}
+$$pV=nRT$$\\
+\\
+p=Pressure(Pascals)\\
+V=Volume($m^3$)\\
+n=Number of moles\\
+R=Universal gas constant=$8.31JK^{-1}mol^{-1}$\\
+T=Temperature(K)
 \end{document}

### 2017-11-25 Maths Notes/S2/Hypothesis testing 2/Hypothesis testing 2.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}

\usepackage{pgfplots}
\pgfmathdeclarefunction{gauss}{2}{%
  \pgfmathparse{1/(#2*sqrt(2*pi))*exp(-((x-#1)^2)/(2*#2^2))}%
}

\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}
\usepackage{tabularx}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30,text width=2cm]
\tikzstyle{arrow} = [thick,->,>=stealth]

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Hypothesis testing}
\end{center}
\section{Performing a hypothesis test}
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
Method&Example\\
\hline
\textbf{Establish the null and alternative hypothesis} \newline($H_0$ and $H_1$)&$H_0:p=0.5$\newline$H_1:p>0.5$\\
\hline
\textbf{Define the distribution under $\mathbf{H_0}$}&Under $H_0$ $X\sim B(15,0.5)$\\
\hline
\textbf{Decide on the significance level}&$5\%$\\
\hline
\textbf{Collect data, state the test statistic}&X=12\\
\hline
\textbf{Calculate the probability of obtaining the test statistic or a more extreme result}&
\begin{tabular}{r l}
$P(X\geqslant 12)$&$=1-P(X\leqslant 11)$\\
&$=1-0.9824$\\
&$=0.0176$\\
\end{tabular}
\\
\hline
\textbf{Compare this to the sig level as a decimal}&$0.0176<0.05$\\
\hline
\textbf{Interpret the results in terms of the original claim}&
There is evidence to reject $H_0$ in favour of $H_1$. The test is significant.\\
\hline
\end{tabularx}}
\section{Finding the critical region}
\begin{tikzpicture}
\begin{axis}[
  no markers, domain=0:8, samples=100,
  every axis y label/.style={at=(current axis.above origin),anchor=south},
  every axis x label/.style={at=(current axis.right of origin),anchor=west},
  height=5cm, width=12cm,
  xtick={2,6},xticklabels={5\%,95\%}, ytick=\empty,
  enlargelimits=false, clip=false,   ]
  \addplot [fill=cyan!20, draw=none, domain=0:2] {gauss(4,1)} \closedcycle;
  \addplot [fill=cyan!20, draw=none, domain=6:8] {gauss(4,1)} \closedcycle;
  \addplot [very thick,cyan!50!black] {gauss(4,1)};
\end{axis}
\end{tikzpicture}
\\
If the test statistic is found in the critical region $H_0$ will be rejected
\subsection{Finding the Lower critical value}
$P(X\geqslant c)<0.95$\\
$1-P(X\leqslant c-1)<0.95$\\
$\mathbf{P(X\leqslant c-1)>0.05}$
\subsection{Finding the Upper critical value}
$P(X\geqslant c)<0.05$\\
$1-P(X\leqslant c-1)<0.05$\\
$\mathbf{P(X\leqslant c-1)>0.95}$
\\
\\
\textbf{Then look these up in tables to find the critical values}

\newpage
\begin{center}

\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Start};
\node (pro1) [process, below of=start] {Establish the null and alternative hypothesis};
\node (pro2) [process, below of=pro1] {Define the distribution under $H_0$};
\node (pro3) [process, below of=pro2] {Decide on the significance level};
\node (pro4) [process, below of=pro3] {Collect data and state the test statistic};
\node (pro5) [process, below of=pro4] {Calculate the probability of obtaining the test statictc or a more extreme result};
\node (dec1) [decision, below of=pro5, yshift=-1cm] {Compare the result to the sig level};
\node (pro6) [process, below of=dec1,yshift=-1cm] {Non significant result, not in critical region, do not reject $H_0$};
\node (pro7) [process, right of=dec1,xshift=6cm] {Significant result, in critical region, reject $H_0$};
\node (pro8) [process, below of=pro6] {Interpret the results in terms of the original claim};
\node (stop) [startstop, below of=pro8] {Stop};

\draw [arrow] (start) -- (pro1);
\draw [arrow] (pro1) -- (pro2);
\draw [arrow] (pro2) -- (pro3);
\draw [arrow] (pro3) -- (pro4);
\draw [arrow] (pro4) -- (pro5);
\draw [arrow] (pro5) -- (dec1);
\draw [arrow] (dec1) -- node[anchor=east] {Greater} (pro6);
\draw [arrow] (dec1) -- node[anchor=south] {Smaller} (pro7);
\draw [arrow] (pro6) -- (pro8);
\draw [arrow] (pro7) |- (pro8);
\draw [arrow] (pro8) -- (stop);
\end{tikzpicture}

\end{center}
\end{document}

### 2017-11-25 Maths Notes/C3/C3 - 2/C3 mark ii.tex
Update to C3 Notes

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{amssymb}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{mwe}
\usepackage{float}
\usepackage{tabularx}
\usepackage{tikz}
\usetikzlibrary{calc,trees,positioning,arrows,fit,shapes,calc,decorations.markings}
\tikzset{->-/.style={decoration={
  markings,
  mark=at position .5 with {\arrow{>}}},postaction={decorate}}}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - C3}
\rfoot{Page \thepage}

\newcommand{\R}{\mathbb{R}}
\pgfplotsset{ytick style={draw=none}}
\pgfplotsset{xtick style={draw=none}}

\begin{document}
\begin{center}
\underline{\huge C3}
\end{center}
\section{Algebraic fractions}
Algebraic fractions can be simplified by equating the fraction to an equation made of constants
\subsection{Example}
$\dfrac{x^3+2x^2-6x+1}{x-1}\equiv Ax^2+Bx+C+\dfrac{D}{x-1}$\\
\\
\\
$x^3+2x^2-6x+1\equiv(x-1)(Ax^2+Bx+C)+D$\\
\\
$x^3+2x^2-6x+1\equiv Ax^3+(B-A)x^2+(C-B)x+(D-C)1$\\
\\
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
Term&Calculation&Final Value\\
\hline
$x^3$ coefficient&$1=A$&$\mathbf{A=1}$\\
\hline
$x^2$ coefficient&$2=B-A$&$\mathbf{B=3}$\\
\hline
$x$ coefficient&$-6=C-B$&$\mathbf{C=-3}$\\
\hline
Constant term&$1=D-C$&$\mathbf{D=-2}$\\
\hline
\end{tabularx}
\\
\\
\\
$x^2+3x-3+\dfrac{-2}{x-2}$
\section{Functions}
\subsection{Definitions}
\textbf{Domain} - The input to a function\\
\textbf{Range} - The output from a function
\subsection{Function mapping}

\begin{figure}[h]
    \centering
    \begin{minipage}{0.28\textwidth}
        \centering
         \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt},scale=0.7]
  \node[ele,] (a1) at (0,4) {};    
  \node[ele,] (a2) at (0,3) {};    
  \node[ele,] (a3) at (0,2) {};
  \node[ele,] (a4) at (0,1) {};

  \node[ele,,] (b1) at (4,4) {};
  \node[ele,,] (b2) at (4,3) {};
  \node[ele,,] (b3) at (4,2) {};
  \node[ele,,] (b4) at (4,1) {};

  \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
  \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;  
  \draw[->-,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
  \draw[->-,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
  \draw[->-,thick,shorten <=2pt,shorten >=2] (a3) -- (b3);
  \draw[->-,thick,shorten <=2pt,shorten >=2] (a4) -- (b4);
 \end{tikzpicture}
        \caption{One-to-one function}
    \end{minipage}\hfill
    \begin{minipage}{0.28\textwidth}
        \centering
                          \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt},scale=0.7]
  \node[ele,] (a1) at (0,4) {};    
  \node[ele,] (a2) at (0,3) {};    
  \node[ele,] (a3) at (0,2) {};
  \node[ele,] (a4) at (0,1) {};

  \node[ele,,] (b1) at (4,4) {};
  \node[ele,,] (b4) at (4,1) {};

  \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
  \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;  
  \draw[->-,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
  \draw[->-,thick,shorten <=2pt,shorten >=2] (a2) -- (b1);
  \draw[->-,thick,shorten <=2pt,shorten >=2] (a3) -- (b4);
  \draw[->-,thick,shorten <=2pt,shorten >=2] (a4) -- (b4);
 \end{tikzpicture}
        \caption{Many-to-one function}
    \end{minipage}\hfill
    \begin{minipage}{0.28\textwidth}
        \centering
                          \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt},scale=0.7]
  \node[ele,] (a1) at (0,4) {};    
  \node[ele,] (a4) at (0,1) {};

  \node[ele,,] (b1) at (4,4) {};
  \node[ele,,] (b2) at (4,3) {};
  \node[ele,,] (b3) at (4,2) {};
  \node[ele,,] (b4) at (4,1) {};

  \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
  \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;  
  \draw[->-,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
  \draw[->-,thick,shorten <=2pt,shorten >=2] (a1) -- (b2);
  \draw[->-,thick,shorten <=2pt,shorten >=2] (a4) -- (b3);
  \draw[->-,thick,shorten <=2pt,shorten >=2] (a4) -- (b4);
 \end{tikzpicture}
        \caption{Not a function}
    \end{minipage}
\end{figure}
A function is a mapping so that every element of the domain maps to exactly one element of the range
\subsubsection{Changing non functions to functions}
Some non functions can be changed to functions by restricting the domain\\
For example for $f(x)=\sqrt x$ where $x\in\mathbb{R}$ all positive values get mapped, however negative numbers don't, see below:
\begin{figure}[h]
 \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt},scale=0.5]
  \node[ele,label=left:$2$] (a1) at (0,4) {};    
  \node[ele,label=left:$1$] (a2) at (0,3) {};    
  \node[ele,label=left:$0$] (a3) at (0,2) {};
  \node[ele,label=left:$-1$] (a4) at (0,1) {};

  \node[ele,,label=right:$\sqrt{2}$] (b1) at (6,4) {};
  \node[ele,,label=right:$1$] (b2) at (6,3) {};
  \node[ele,,label=right:$0$] (b3) at (6,2) {};
  \node[ele,,] (b4) at (6,1) {};

  \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2.5cm] {} ;
  \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2.5cm] {} ;  
  \draw[->,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
  \draw[->,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
  \draw[->,thick,shorten <=2pt,shorten >=2] (a3) -- (b3);
 \end{tikzpicture}
 \end{figure}\\
This means that the domain must be restricted to $x\geqslant0$
\end{document}

### 2017-11-26 Maths Notes/C3/C3 - 2/C3 mark ii.tex
Update to notes

@@
 This means that the domain must be restricted to $x\geqslant0$
+\subsection{Inverse functions}
+The inverse of $f(x)$ is written as $f^{-1}(x)$\\
+The domain and range of inverse function are the opposite of the normal function.
+\subsubsection{Finding the inverse function}
+To find the inverse function isolate $x$ then replace $x$ with $f^{-1}(x)$ and $y$ with $x$\\
+\\
+$y=2x^2-7$\\
+\\
+$y=7=2x^2$\\
+\\
+$\dfrac{y+7}{2}=x^2$\\
+\\
+$x=\sqrt{\dfrac{y+7}{2}}$\\
+\\
+$f^{-1}(x)=\sqrt{\dfrac{x+7}{2}}$\\
+\\
+\textbf{To show this graph it is the reflection of the normal function in the line $\mathbf{y=x}$}
+\section{Exponential and log functions}
+\subsection{Formulas for exponential growth or decay}
+Example:
+$P=16000e^{-\dfrac{t}{10}}$
+Where P is the Price in £s and t is the years from new\\
+\\
+\textit{What was the price when new?}\\
+\textbf{Substitute t=0}\\
+\\
+$P=16000e^{-\dfrac{0}{10}}$\\
+$P=16000 \times 1$\\
+\\
+\textit{What is the value at 5 years old}\\
+\textbf{Substitute t=5}\\
+$P=16000e^{-\frac{5}{10}}$\\
+$P=\mathsterling 9704.49$\\
+\\
+\textit{What does the model say about the eventual value of the car}\\
+As $t \rightarrow \infty$, $e^{-\frac{t}{10}} \rightarrow \infty$\\
+Therefore $P \rightarrow 16000 \times 0 = 0$\\
+The eventual value is zero.
+\subsection{The inverse of the exponential function}
+The function $f(x)=\ln x$ has domain \{$x \in \mathbb{R}$, $x>0$\} and range \{$f(x) \in \mathbb{R}$\}
+\newpage
+\section{Numerical methods}
+\subsection{Approximations for roots based on graphs}
+\begin{tikzpicture}
+\begin{axis}[axis lines=middle,ymin=-6,scale=0.5,xmax=6]
+
+\addplot[color=red]{x-4};
+\end{axis}
+\end{tikzpicture}\\
+On this graph if the value of $f(x)$ was to be found at 2 it would be \textbf{negative}, whereas if it was to be found at 6 it would be \textbf{positive}, this implies that there is a root in-between 2 and 6\\
+\\
+The exception to this rule is $f(x)=\frac{1}{x}$ as there is a discontinuity at $x=0$, however there is no root
+\subsection{Iteration for finding approximations of roots}
+To solve an equation of the form $f(x)=0$ by an iterative method, rearrange $f(x)=0$ into a for $x=g(x)$ and use the iterative formula $x_{n+1}=g(x_n)$.\\
+\\
+Example, find a root of the equation $x^2-4x+1=0$\\
+Re-write as $x=4-\dfrac{1}{x}$\\
+
+Create the formula $x_{n+1}=4-\dfrac{1}{x_n}$\\
+You get given a rough approximation, $x_0=3$\\
+Substitute\\
+$x_1=4-\dfrac{1}{x_0}$\\
+$x_1=4-\dfrac{1}{3}$\\
+$x_1=\dfrac{11}{3}$\\
+\\
+$x_2=4-\dfrac{1}{\frac{11}{3}}$\\
+$x_2=\dfrac{41}{11}$\\
+Continuing this increases the accuracy of the result.\\
+This may not work and will not converge to a root.
+\section{Further Trigonometric identities and their applications}
+\subsection{The R formula}
+For positive values of \textit{a} and \textit{b}
+\\
+$a\sin\theta\pm b\cos\theta$ can be expressed in the form $R\sin(\theta\pm\alpha)$, where $0<\alpha<90$
+\\
+$a\cos\theta\pm b\sin\theta$ can be expressed in the form $R\cos(\theta\mp\alpha)$, where $0<\alpha<90$ 
+\\
+$R=\sqrt{a^2+b^2}$
+\\
+$\alpha=\arctan(\frac{b}{a})$
 \end{document}

### 2017-11-29 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
Notes Update

@@
 T=Temperature(K)
+\section{Brownian Motion}
+The random and unpredictable motion of a particle such as a smoke particle caused by molecules of the surrounding substance colliding at random with the particle.
+Its discovery provided evidence for the existence of atoms.
+\section{Kinetic theory of gases}
+This is a model of gas behaviour based on known laws of physics.\\
+\\
+On the other hand the gas laws are empirical and are based on experimental results only.\\
+\subsection{Assumptions for an ideal gas}
+\begin{enumerate}
+\item Newton's laws of motion can be applied
+\item The molecules of a particular gas are identical
+\item The size of the particles are negligible compared to the distance between them
+\item The molecules exert NO forces on each other, including during collision.
+Gravitational force is neglected.
+When not colliding, the particles move with constant velocity, and that velocity is random.
+\item All collisions are perfectly elastic
+\item The duration of the collision is negligible compared to the time between collisions.
+\item There are a large number of particles so that statistics can be meaningfully applied.
+\end{enumerate}
 \end{document}

### 2017-12-01 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
Update to font
Physics notes update

@@
 \usepackage{tikz}
-\usetikzlibrary{scopes}
+\usepackage{relsize}
+\usetikzlibrary{scopes,quotes,arrows.meta,arrows,shapes.geometric}
 \pgfplotsset{width=10cm,compat=1.9}
@@
 \renewcommand{\indent}{\hspace*{\tindent}}
-
+\tikzstyle{arrow} = [thick,->,>=stealth]
 \pagestyle{fancy}
@@
 n=Number of moles\\
-R=Universal gas constant=$8.31JK^{-1}mol^{-1}$\\
+R=Universal gas constant=$8.31JK^{-1}\text{mol}^{-1}$\\
 T=Temperature(K)
@@
 \end{enumerate}
+\newpage
+\section{Derivation of the relationship between gas pressure and speed}
+
+\begin{tikzpicture}[every edge quotes/.append style={auto, text=black},scale=0.7]
+  \pgfmathsetmacro{\cubex}{5}
+  \pgfmathsetmacro{\cubey}{5}
+  \pgfmathsetmacro{\cubez}{5}
+  \draw [arrow] (-1,-1,1) -- (0,-1,1) node[below] {$C_{x\mathsmaller{1}}$};
+  \filldraw [red] (-1,-1,1) circle (6pt);
+  \draw [draw=black, every edge/.append style={draw=black, densely dashed, opacity=.5}]
+    (0,0,0) coordinate (o) -- ++(-\cubex,0,0) coordinate (a) -- ++(0,-\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubez)  -- ++(\cubex,0,0) coordinate (c) -- cycle
+    (o) -- ++(0,0,-\cubez) coordinate (d) -- ++(0,-\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
+    (o) -- (a) -- ++(0,0,-\cubez) coordinate (f) edge (g) -- (d) -- cycle;
+  \path [every edge/.append style={draw=black, |-|}]
+    (b) +(0,-5pt) coordinate (b1) edge ["l"'] (b1 -| c)
+    (b) +(-5pt,0) coordinate (b2) edge ["l"] (b2 |- a)
+    (c) +(3.5pt,-3.5pt) coordinate (c2) edge ["l"'] ([xshift=3.5pt,yshift=-3.5pt]e)
+    ;
+\end{tikzpicture}
+\\
+\textcolor{red}{Newton's $3^{\text{rd}}$ law - Every action has an equal and opposite reaction}\\
+$\Delta mc=mc_{x1}--mc_{x1}=2mc_{x1}$\\
+\\
+\\
+\textcolor{red}{Use $\text{Velocity}=\dfrac{\text{Distance}}{\text{Time}}$}\\
+Time=$\dfrac{\text{Distance}}{\text{Velocity}}=\dfrac{2l}{c_{x1}}$\\
+\\
+\\
+\textcolor{red}{Use force$=\dfrac{\text{Change in momentum}}{\text{time}}$}\\
+$\text{Force}=\dfrac{\Delta mc}{\Delta t}=\dfrac{2mc{x1}}{2l/c_{x1}}=\dfrac{mc_{x1}^2}{l}$\\
+\\
+\\
+\textcolor{red}{Use Pressure$=\dfrac{\text{Force}}{\text{Area}}$}\\
+\\
+$p_1=\dfrac{mc_{x1}^2/l}{l^2}=\dfrac{mc_{x1}^2}{l^3}$\\
+\\
+\\
+\textcolor{red}{Expand for N particles}\\
+$p=\Sigma p_n=p_1+p_2+p_3...+p_N$\\
+\\
+$p=\dfrac{mc_{x1}^2}{l^3}+\dfrac{mc_{x2}^2}{l^3}+\dfrac{mc_{x3}^2}{l^3}+\dfrac{mc_{xN}^2}{l^3}$\\
+\\
+$p=\dfrac{m}{l^3}(c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2)$\\
+\\
+\\
+\textcolor{red}{The mean of all the squares of the velocities is written as $\mathlarger{\bar{c_x^2}}$}\\
+\\
+$\mathlarger{\bar{c_x^2}}=\dfrac{c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2}{N}$\\
+\\
+$N\mathlarger{\bar{c_x^2}}=c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2$\\
+\\
+\\
+\textcolor{red}{Simplify expression for pressure}\\
+\\
+$p=\dfrac{Nm\mathlarger{\bar{c_x^2}}}{l^3}$\\
+\\
+\\
+\\
+\textcolor{red}{Consider in 3 dimensions}\\
+\\
+$\mathlarger{\bar{c^2}=\bar{c_x^2}+\bar{c_y^2}+\bar{c_z^2}}$\\
+\\
+\\
+\textcolor{red}{Average of mean square velocity for each dimension are equal}\\
+\\
+$\mathlarger{\bar{c_x^2}=\bar{c_y^2}=\bar{c_z^2}}$\\
+\\
+\\
+\textcolor{red}{Simplify 3D formula}\\
+\\
+$\mathlarger{\dfrac{\bar{c^2}}{3}=\bar{c_x^2}=\bar{c_y^2}=\bar{c_z^2}}$\\
+\\
+\\
+\textcolor{red}{Simplify pressure formula}\\
+\\
+$p=\dfrac{1}{3}\times\dfrac{Nm\mathlarger{\bar{c^2}}}{l^3}$\\
+\\
+\\
+\textcolor{red}{Insert Density formula}\\
+\\
+$\rho=\dfrac{\text{Mass}}{\text{Volume}}=\dfrac{Nm}{l^3}$
+\\
+\\
+\\
+\textcolor{red}{Substitute into Pressure formula}\\
+\\
+$$p=\frac{1}{3}\rho\mathlarger{\bar{c^2}}$$
 \end{document}

### 2017-12-01 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
Notes Update

@@
   \path [every edge/.append style={draw=black, |-|}]
-    (b) +(0,-5pt) coordinate (b1) edge ["l"'] (b1 -| c)
-    (b) +(-5pt,0) coordinate (b2) edge ["l"] (b2 |- a)
-    (c) +(3.5pt,-3.5pt) coordinate (c2) edge ["l"'] ([xshift=3.5pt,yshift=-3.5pt]e)
+    (b) +(0,-5pt) coordinate (b1) edge ["$l$"'] (b1 -| c)
+    (b) +(-5pt,0) coordinate (b2) edge ["$l$"] (b2 |- a)
+    (c) +(3.5pt,-3.5pt) coordinate (c2) edge ["$l$"'] ([xshift=3.5pt,yshift=-3.5pt]e)
     ;

### 2017-12-03 Maths Notes/M2/Centres of mass/Centres of mass.tex
Notes Update
Notes update - Centres of mass
M2 Notes update with CoM equilibrium problems

@@
 \usepackage{gensymb}
+\usepackage{tabularx}
 
@@
 
-Test
+\end{obeylines}
+\newpage
+\begin{center}
+\underline{\huge Centres of mass example - Equilibrium problems}
+\end{center}
+\includegraphics[width=1.5in]{Equilibrium_Problem.JPG}\\
+\\
+\textit{(a) Find the distance of the centre of mass of the lamina from AF. }\\
 
-\end{obeylines}
+\textbf{1. Find the masses and locations of all areas or rods and put in a table}\\
+\\
+{\renewcommand{\arraystretch}{1.5}
+\begin{tabularx}{\textwidth}{|X|X|X|}
+\hline
+Mass(m)&$4a^2$&$-a^2$\\
+\hline
+Distance From AF(x)&$a$&$\frac{3}{2}a$\\
+\hline
+mx&$4a^3$&$-\frac{3}{2}a^3$\\
+\hline
+\end{tabularx}}
+\\
+\\
+\textbf{2. Use the formula to find the centre of mass}\\
+\\
+\textcolor{red}{$\bar{x}=\dfrac{\Sigma m_ix_i}{\Sigma m_i}$}\\
+\\
+$\bar{x}=\dfrac{\frac{5}{2}a^3}{3a^2}=\dfrac{5a}{6}$\\
+\\
+\textit{The lamina is freely suspended from A and hangs in equilibrium.}\\
+\textit{(b) Find, in degrees to one decimal place, the angle which AF makes with the vertical.}\\
+\\
+\textbf{Use symmetry to find the y coordinate of the centre of mass}\\
+\\
+\begin{tikzpicture}[scale=1.9]
+\tikzstyle{ann} = [fill=white,font=\footnotesize,inner sep=1pt]
+
+\draw[black, thick] (0,0) -- (0,2) -- (1,2) -- (1,1) -- (2,1) -- (2,0) -- cycle;
+\draw[arrows=<->](0,5/6)--(5/6,5/6);
+\node[ann] at (5/12,5/6) {$\frac{5}{6}$};
+\draw [blue,dashed] (0,0) -- (2,2);
+\draw[arrows=<->](5/6,0)--(5/6,5/6);
+\node[ann] at (5/6,5/12) {$\frac{5}{6}$};
+\end{tikzpicture}
+\\
+\\
+\textbf{Re-draw to find angle}\\
+\begin{tikzpicture}[scale=1.9]
+\tikzstyle{ann} = [fill=white,font=\footnotesize,inner sep=1pt]
+\tikzstyle{angle} = [fill=none,font=\tiny,inner sep=1pt]
+\draw[black, thick] (0,0) -- (0,2) -- (1,2) -- (1,1) -- (2,1) -- (2,0) -- cycle;
+\draw[arrows=<->](0,5/6)--(5/6,5/6);
+\node[ann] at (5/12,5/6) {$\frac{5}{6}$};
+\draw[arrows=<->](5/6,5/6) -- (5/6,2);
+\node[ann] at (5/6,17/12) {$\frac{7}{6}$};
+\draw [blue,dashed] (0,2) -- (5/6,5/6);
+\draw[thick] (5/24,41/24) arc (0:-90:0.2);
+\node[ann] at (0.1,1.7) {$\theta$};
+\end{tikzpicture}\\
+\\
+$\tan(\theta)=\dfrac{5/6}{7/6}$\\
+\\
+$\theta=35.5\degree$
+\newpage
 

### 2017-12-04 Maths Notes/M2/Collisions/Collisions.tex
Notes Update

--- 2017-11-01 Maths Notes/M2/Collisions/Collisions.tex
@@
 \renewcommand{\indent}{\hspace*{\tindent}}
-
+\pretolerance=10000
+\hyphenpenalty=10000
 \pagestyle{fancy}
@@
 If $e=0$ the ball doesn't bounce\\
+\\
 $e=\dfrac{\text{Speed of seperation}}{\text{Speed of approach}}$
+\subsection{Alternate form of coefficient of restitution formula}
+$mgh=\frac{1}{2}mv^2$\\
+\\
+$v=\sqrt{2gh}$\\
+\\
+$e=\dfrac{\sqrt{2gh_2}}{\sqrt{2gh_1}}$\\
+\\
+$e=\dfrac{\sqrt{h_2}}{\sqrt{h_1}}$\\
+\\
+$h_2$ - the height the ball bounces back to\\
+\\
+$h_1$ - the height the ball is dropped from
+\subsection{Calculations involving coefficient of restitution}
+When doing calculations involving the coefficient of restitution both the calculation for CoR and conservation of momentum will be needed.\\
+\textbf{Conservation of momentum:}
+$m_1u_1+m_2u_2=m_1v_1+m_2v_2$\\
+\\
+\textbf{Coefficient of restitution}\\
+\\
+$e=\dfrac{v_1}{u_1}$
+\subsection{Successive Impacts}
+In some cases calculations will involve the impacts of multiple balls successively, like in newton's cradle.
+\subsubsection{Example}
+\textit{Three perfectly elastic particles A, B and C with masses 3kg, 2kg and 1kg respectively lie at rest in a straight line on a smooth horizontal table in alphabetical order.
+A is projected towards B with speed $5ms^{-1}$ and after A has collided with B, B collides with C}\\
+\\
+$5\times3=3V_A+2V_B$\\
+\\
+$1=\dfrac{SoS}{SoA}$ therefore $SoS=SoA$ so $V_B-V_A=5$ so $V_B=5+V_A$\\
+\\
+$15=10+2V_A+3V_A$\\
+\\
+$15=2V_B+3$ so after 1st collision $V_B=6$\\
+\\
+$15=10+5V_A$ so $\mathbf{V_A=1}$\\
+\\
+\textbf{2nd Collision}\\
+\\
+$2\times6=2V_B+V_C$\\
+\\
+$V_C-V_B=6$\\
+\\
+$12=3V_B+6$\\
+\\
+$3V_B=6$\\
+\\
+$\mathbf{V_B=2}$\\
+\\
+$V_C=6+2=8$
+\newpage
+\begin{center}
+\underline{\huge Collisions example - Direct Impact}
+\end{center}
+\textit{A small ball A of mass 3m is moving with speed u in a straight line on a smooth horizontal
+table. The ball collides directly with another small ball B of mass m moving with speed u
+towards A along the same straight line. The coefficient of restitution between A and B is $\frac{1}{2}$
+The balls have the same radius and can be modelled as particles.}\\
+\\
+\textit{Find the speed of A immediately after the collision}\\
+\\
+\\
+\textbf{1. Draw the diagram in its initial state}\\
+\\
+\begin{tikzpicture}
+\filldraw[color=black,fill=none,very thick](3,0.5) circle (0.5) node{B};
+\filldraw[color=black,fill=none,very thick](-3,0.5) circle (0.5) node{A};
+\draw (-4,0) -- (4,0);
+\draw[arrows=->](-2.5,0.5)--(-1.5,0.5) node[above]{$u$};
+\draw[arrows=->](2.5,0.5)--(1.5,0.5) node[above]{$u$};
+\end{tikzpicture}\\
+\\
+\textbf{2. Apply the conservation of momentum formula (make sure to remember different directions)}\\
+\textcolor{red}{$m_1u_1+m_2u_2=m_1v_1+m_2v_2$}\\
+\\
+$3mu-mu=3mv+mw$\\
+\\
+$\underline{2u=3v+w}$\\
+\\
+\textbf{3. Apply Newton's law of restitution}\\
+\\
+\textcolor{red}{$e=\dfrac{\text{Speed of separation}}{\text{Speed of approach}}$}\\
+\\
+\\
+$\dfrac{1}{2}=\dfrac{w-v}{2u}$\\
+\\
+$u=w-v$\\
+\\
+$\underline{u+v=w}$\\
+\\
+\textbf{4. Combine the results from momentum and restitution}\\
+\\
+$2u=3v+u+v$\\
+\\
+$u=4v$\\
+\\
+$v=\frac{1}{4}u$\\
+\\
+$\underline{|v|=\frac{1}{4}u}$\\
+\\
+\textit{Find the speed of B immediately after the collision}\\
+\\
+\textbf{Combine the result from Newton's law of restitution and the speed of A}\\
+\\
+$u=w-\frac{1}{4}u$\\
+\\
+$\underline{|w|=\frac{5}{4}u}$
+\newpage
+\textit{After the collision B hits a smooth vertical wall which is perpendicular to the direction of
+motion of B. The coefficient of restitution between B and the wall is $\frac{2}{5}$}\\
+\\
+\textit{Find the speed of B immediately after hitting the wall}\\
+\\
+\textbf{Apply Newton's law of restitution}\\
+\\
+\textcolor{red}{$e=\dfrac{\text{Speed of separation}}{\text{Speed of approach}}$}\\
+\\
+\\
+$\dfrac{2}{5}=\dfrac{V}{\frac{5}{4}u}$\\
+\\
+\\
+$V=\frac{2}{5}\times\frac{5}{4}u=\underline{\frac{1}{2}u}$\\
+\\
+\textit{The first collision between A and B occurred at a distance 4a from the wall. The balls collide
+again T seconds after the first collision.}\\
+\\
+\textit{Show that $T=\dfrac{112a}{15u}$}\\
+\\
+\textbf{Re-draw diagram to show new information}\\
+\\
+\begin{tikzpicture}
+\filldraw[color=black,fill=none,very thick](3,0.5) circle (0.5) node{B};
+\filldraw[color=black,fill=none,very thick](-3,0.5) circle (0.5) node{A};
+\draw (-4,0) -- (6,0);
+\draw (6,0) -- (6,2);
+\draw[arrows=->](-2.5,0.5)--(-1.5,0.5) node[above]{$\frac{1}{4}u$};
+\draw[arrows=->](2.5,0.5)--(1.5,0.5) node[above]{$\frac{1}{2}u$};
+\end{tikzpicture}\\
+\\
+\textbf{Calculate the time it takes for B to approach the wall}\\
+\\
+\textcolor{red}{Time$=\dfrac{\text{Distance}}{\text{Speed}}$}\\
+\\
+\\
+Time= $\dfrac{4a}{\frac{5}{4}u}=\dfrac{16a}{5u}$\\
+\\
+\textbf{Calculate the distance A moves towards the wall}\\
+\\
+$\text{Distance}=\dfrac{1}{4}u\times\dfrac{16a}{5u}=\dfrac{4}{5}a$\\
+\\
+\textbf{Calculate the speed A and B approach each other}\\
+\\
+$\dfrac{1}{4}u+\dfrac{1}{2}u=\dfrac{3}{4}u$\\
+\\
+\textbf{Calculate the distance between A and B immediately after B has collided with the wall}\\
+\\
+$4a-\dfrac{4}{5}a=\dfrac{16}{5}a$\\
+\\
+\textbf{Calculate time based on speed and distance}\\
+\\
+$t=\dfrac{\frac{16}{5}a}{\frac{3}{4}u}=\dfrac{64a}{15u}$\\
+\\
+\textbf{Add times to calculate total time}\\
+\\
+$\dfrac{16a}{5u}+\dfrac{64a}{15u}=\dfrac{112a}{15u}$
 
-\end{obeylines}
 \end{document}

### 2017-12-05 Maths Notes/M2/Collisions/Collisions.tex
Notes Update

@@
 $\dfrac{16a}{5u}+\dfrac{64a}{15u}=\dfrac{112a}{15u}$
+\newpage
+\begin{center}
+\underline{\huge Collisions example - Oblique Impact}
+\end{center}
+\includegraphics[width=1.5in]{oblique.png}\\
+\\
+\textit{A small smooth ball B, moving on a horizontal plane, collides with a fixed vertical wall.\\
+Immediately before the collision the angle between the direction of motion of B and the wall is $2\theta$ where $0\degree < \theta < 45\degree$.
+Immediately after the collision the angle between the direction of motion
+of B and the wall is $\theta$ as shown in the diagram above. Given that the coefficient of restitution
+between B and the wall is $\frac{3}{8}$ , find the value of $\tan\theta$.}\\
+\\
+\textbf{Conservation of momentum}\\
+\textcolor{red}{$m_1u_1=m_1v_1\Rightarrow u_1=v_1$}\\
+\\
+$u\cos2\theta=v\cos\theta$\\
+\\
+\textbf{Apply Newton's law of restitution}\\
+\\
+\textcolor{red}{$e=\dfrac{\text{Speed of separation}}{\text{Speed of approach}}$}\\
+\\
+$\dfrac{3}{8}=\dfrac{v\sin\theta}{u\sin2\theta}$\\
+\\
+\\
+$3u\sin2\theta=8v\sin\theta$\\
+\\
+\textbf{Combine result from Conservation of Momentum and Restitution}
 

### 2017-12-05 Maths Notes/M2/Dynamics/Dynamics.tex
Notes Update

--- 2017-11-12 Maths Notes/M2/Collisions/Collisions.tex
@@
 \usepackage{gensymb}
-
+\usepackage{tikz}
+\usetikzlibrary{positioning}
 \pgfplotsset{width=10cm,compat=1.9}
@@
 \begin{center}
-\underline{\huge Collisions}
+\underline{\huge Dynamics}
 \end{center}
-\section{Impulse and momentum}
-Impulse=$mv-mu$=$Ft$\\
-Total momentum before collision=total momentum after
-\section{Coefficient of restitution}
-This tells us how well something bounces, it is given the symbol \textbf{e}.\\
-If $e=1$ the ball returns to it's original height\\
-If $e=0$ the ball doesn't bounce\\
-\\
-$e=\dfrac{\text{Speed of seperation}}{\text{Speed of approach}}$
-\subsection{Alternate form of coefficient of restitution formula}
-$mgh=\frac{1}{2}mv^2$\\
-\\
-$v=\sqrt{2gh}$\\
-\\
-$e=\dfrac{\sqrt{2gh_2}}{\sqrt{2gh_1}}$\\
-\\
-$e=\dfrac{\sqrt{h_2}}{\sqrt{h_1}}$\\
-\\
-$h_2$ - the height the ball bounces back to\\
-\\
-$h_1$ - the height the ball is dropped from
-\subsection{Calculations involving coefficient of restitution}
-When doing calculations involving the coefficient of restitution both the calculation for CoR and conservation of momentum will be needed.\\
-\textbf{Conservation of momentum:}
-$m_1u_1+m_2u_2=m_1v_1+m_2v_2$\\
-\\
-\textbf{Coefficient of restitution}\\
-\\
-$e=\dfrac{v_1}{u_1}$
-\subsection{Successive Impacts}
-In some cases calculations will involve the impacts of multiple balls successively, like in newton's cradle.
-\subsubsection{Example}
-\textit{Three perfectly elastic particles A, B and C with masses 3kg, 2kg and 1kg respectively lie at rest in a straight line on a smooth horizontal table in alphabetical order.
-A is projected towards B with speed $5ms^{-1}$ and after A has collided with B, B collides with C}\\
-\\
-$5\times3=3V_A+2V_B$\\
-\\
-$1=\dfrac{SoS}{SoA}$ therefore $SoS=SoA$ so $V_B-V_A=5$ so $V_B=5+V_A$\\
-\\
-$15=10+2V_A+3V_A$\\
-\\
-$15=2V_B+3$ so after 1st collision $V_B=6$\\
-\\
-$15=10+5V_A$ so $\mathbf{V_A=1}$\\
-\\
-\textbf{2nd Collision}\\
-\\
-$2\times6=2V_B+V_C$\\
-\\
-$V_C-V_B=6$\\
-\\
-$12=3V_B+6$\\
-\\
-$3V_B=6$\\
-\\
-$\mathbf{V_B=2}$\\
-\\
-$V_C=6+2=8$
-
+\newpage
+\begin{center}
+\underline{\huge Dynamics Example - F=ma on a slope}
+\end{center}
+\textit{A car of mass 1500 kg is moving up a straight road, which is inclined at an angle $\theta$ to the
+horizontal, where $\sin\theta=\frac{1}{14}$ The resistance to the motion of the car from non-gravitational
+forces is constant and is modelled as a single constant force of magnitude 650 N. The car’s
+engine is working at a rate of 30 kW.\\
+Find the acceleration of the car at the instant when its speed is 15$\text{ms}^{-1}$. }
 \end{document}

### 2017-12-05 Maths Notes/M2/Dynamics/Dynamics.tex
Revert "Sync"
This reverts commit afd846016fd941977674624eb08aa111cdfc48a5.

@@
 \usepackage{tikz}
-\usetikzlibrary{positioning}
+\usetikzlibrary{positioning,scopes,decorations.text}
 \pgfplotsset{width=10cm,compat=1.9}
@@
 Find the acceleration of the car at the instant when its speed is 15$\text{ms}^{-1}$. }
+\\
+\\
+\textbf{Draw a diagram to represent the question}
+\\
+\\
+\def\iangle{35} % Angle of the inclined plane
+
+\def\down{-90}
+\def\arcr{0.5cm} % Radius of the arc used to indicate angles
+\begin{tikzpicture}[
+    force/.style={>=latex,draw=blue,fill=blue},
+    calculatedforce/.style={>=latex,draw=red,fill=red},
+    axis/.style={densely dashed,gray,font=\small},
+    M/.style={rectangle,draw,fill=lightgray,minimum size=0.5cm,thin},
+    m/.style={rectangle,draw=black,fill=lightgray,minimum size=0.3cm,thin},
+    plane/.style={draw=black,fill=blue!10},
+    string/.style={draw=red, thick},
+    pulley/.style={thick},
+    scale=2.25
+]
+
+    %% Free body diagram of M
+    \begin{scope}[rotate=\iangle]
+        \node[M,transform shape] (M) {};
+        % Draw axes and help lines
+
+        {[axis,-]
+            \draw (M.center) -- (0,-1) node[right] {};
+
+            % Indicate angle. The code is a bit awkward.
+
+            \draw[solid,shorten >=0.5pt] (\down-\iangle:\arcr)
+                arc(\down-\iangle:\down:\arcr);
+            \node at (\down-0.5*\iangle:1.3*\arcr) {$\theta$};
+        }
+
+        % Forces
+        {[force,->]
+            % Assuming that Mg = 1. The normal force will therefore be cos(alpha)
+            \draw (M.south) -- ++(0,{cos(\iangle)*1.5}) node[above right] {$R$};
+            \draw (M.west) -- ++(-1,0) node[left] {$650N$};
+            \draw (M.east) -- ++(1,0) node[above] {$T$};
+
+            }
+        {[calculatedforce,->]
+
+        \draw (0,-1) -- ++(-0.7,0) node[pos=0,right,sloped] {};
+        }
+        \draw[black, thick] (-3,-0.25) -- (2,-0.25);
+		\node at (0,-1.13) (nodeA) {};
+		\node at (-0.7,-1.13) (nodeB) {};
+		\draw [decoration={text along path,text={{$1500g\sin\theta$}{}},text align={center}},decorate]  (nodeB) -- (nodeA);
+
+    \end{scope}
+    % Draw gravity force. The code is put outside the rotated
+    % scope for simplicity. No need to do any angle calculations. 
+    \draw[force,->] (M.center) -- ++(0,-1.5) node[below] {$1500g$};
+    \draw[black, thick] (-2.31,-1.93) -- (1.76,-1.93);
+    \draw[thick, -] (-1.8,-1.93) arc (0:36:0.5);
+    \node[] at (-1.93,-1.8) {$\theta$};
+
+    %%
+
+\\
+;
+\end{tikzpicture}
+\\
+\\
+\textbf{Apply Newton's Second Law (F=ma)}\\
+\\
+$T-650-1500g\sin\theta=1500a$\\
+\\
+\textbf{Use $\text{Power=Force}\times\text{Velocity}$}\\
+\\
+$30,000=T\times15$\\
+\\
+$T=\dfrac{30,000}{15}=2000$\\
+\\
+\textbf{Solve, substituting power result into Newton's Second Law result}\\
+\\
+$2000-650-1500\times9.8\times\frac{1}{14}=1500a$\\
+\\
+\\
+$a=\dfrac{2000-650-1500\times9.8\times\frac{1}{14}}{1500}=0.2$
+
 \end{document}

### 2017-12-06 Maths Notes/M2/Dynamics/Dynamics.tex
Notes Update

@@
 $a=\dfrac{2000-650-1500\times9.8\times\frac{1}{14}}{1500}=0.2$
+\newpage
+\begin{center}
+\underline{\huge Dynamics Example - Momentum and Impulse}
+\end{center}
+
+\textit{A ball of mass 0.5 kg is moving with velocity $(10\mathbf{i} + 24\mathbf{j}) \ \text{ms}^{-1}$ when it is struck by a bat.\\
+Immediately after the impact the ball is moving with velocity $20\mathbf{i} \ \text{ms}^{-1}$. }
+\\
+\\
+\textit{Find the magnitude of the impulse of the bat on the ball}\\
+\\
+\textbf{Apply the impulse formula}\\
+\\
+\textcolor{red}{$I=m(v-u)$}\\
+\\
+$I=0.5(20\mathbf{i}-(10\mathbf{i}+24\mathbf{j}))=\underline{5\mathbf{i}-12\mathbf{j}}$\\
+\\
+\textbf{Find the magnitude}\\
+\\
+$I=\sqrt{5^2+(-12)^2}=\underline{13Ns}$\\
+\\
+\textit{Find the size of the angle between the vector i and the impulse exerted by the bat on the ball}\\
+\\
+\\
+\textbf{Draw diagram to show vector}\\
+\\
+\begin{tikzpicture}[scale=0.3]
+\draw[black, ultra thick] (0,0) -- (5,0) -- (5,-12) -- cycle;
+\draw (0,0) -- (5,0) node [midway, above, sloped] (TextNode) {$5$};
+\draw (5,-12) -- (5,0) node [midway, below, sloped] (TextNode) {$12$};
+\draw[thick, -] (2,0) arc (0:-69:2);
+\node[] at (1,-0.9) {$\theta$};
+\end{tikzpicture}\\
+\\
+\textbf{Use trigonometry to find angle}\\
+\\
+$\theta=\arctan\Big(\dfrac{12}{5}\Big)=67.4\degree$\\
+\\
+\textit{Find the kinetic energy lost by the ball in the impact}\\
+\\
+\textcolor{red}{$\Delta E_k=E_{k2}-E_{k1}$}\\
+\\
+$\Delta E_k=\frac{1}{2}\times0.5\times20^2-\frac{1}{2}\times0.5\times(10^2+24^2)=-69J$
 

### 2017-12-06 Maths Notes/M2/Kinematics/Kinematics.tex
Notes Update

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{relsize}
 \usepackage{titlesec}
@@
 $S=45\cos45\times7.07=245$
+\end{obeylines}
+\section{Displacement, velocity and acceleration}
+$v=\dfrac{dx}{dt}$\\
+\\
+$a=\dfrac{dv}{dt}$\\
+\\
+\begin{tikzpicture}
+  \node (disp) {\textbf{Displacement} $x$};
+  \node[right=2cm of disp] (vel) {\textbf{Velocity} $v$};
+  \node[right=2cm of vel] (acc) {\textbf{Acceleration} $a$};
+  \draw[-stealth,shorten >= 2pt] (disp.north) to[bend left] node[midway,above] {Differentiate} (vel.north);
+  \draw[-stealth] (vel.south) to[bend left] node[midway,below] {Integrate} (disp.south);
+  \draw[-stealth,shorten >= 2pt] (vel.north) to[bend left] node[midway,above] {Differentiate} (acc.north);
+    \draw[-stealth] (acc.south) to[bend left] node[midway,below] {Integrate} (vel.south);
+\end{tikzpicture}
+\newpage
+\begin{center}
+\underline{\huge Kinematics Example - Problems with calculus}
+\end{center}
+\textit{A particle P moves along the x-axis in a straight line so that, at time t seconds, the velocity of P is $v \ \text{ms}^{-1}$, where}\\
+\\
+$
+  v=\left\{
+  \begin{array}{@{}ll@{}}
+    10t-2t^2, & \text{for}\ 0\leqslant t \leqslant 6  \\
+    -\dfrac{432}{t^2}, & t>6
+  \end{array}\right.
+$\\
+\\
+\\
+\textit{At $t = 0$, P is at the origin O. Find the displacement of P from O when}\\
+\\
+$\mathit{t = 6}$\\
+\\
+\textbf{Integrate velocity}\\
+\\
+\textcolor{red}{$\mathlarger{x=\int v \ dt}$}\\
+\\
+$x=\int 10t-2t^2 \ dt= 5t^2-\frac{2}{3}t^3+c$\\
+\\
+\\
+\textbf{Substitute in the value of t}\\
+\\
+$t=6$\\
+\\
+$x=5\times6^2-\frac{2}{3}\times6^3=36m$\\
+\\
+\\
+$\mathit{t = 10}$
+\\
+\textbf{Integrate velocity for the second half of the journey}\\
+\\
+$x=\mathlarger{\int-\dfrac{432}{t^2} \ dt=\int-432t^{-2} \ dt=\dfrac{-432t^{-1}}{-1}+k=\dfrac{432}{t}+k}$\\
+\\
+\textbf{Find value of k by using known distance at t=6}\\
+\\
+$t=6 \ \ x=36$\\
+\\
+$36=\dfrac{432}{6}+k$\\
+\\
+$k=36-72=-36$\\
+\\
+\textbf{Find distance using value of k and t}\\
+\\
+$t=10$\\
+\\
+$x=\dfrac{432}{10}-36=7.2\text{m}$
 
-\end{obeylines}
 \end{document}

### 2017-12-07 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
Notes Update

--- 2017-11-29 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
@@
 \end{enumerate}
+\newpage
+\section{Derivation of the relationship between gas pressure and speed}
+
+\begin{tikzpicture}[every edge quotes/.append style={auto, text=black},scale=0.7]
+  \pgfmathsetmacro{\cubex}{5}
+  \pgfmathsetmacro{\cubey}{5}
+  \pgfmathsetmacro{\cubez}{5}
+  \draw [arrow] (-1,-1,1) -- (0,-1,1) node[below] {$C_{x\mathsmaller{1}}$};
+  \filldraw [red] (-1,-1,1) circle (6pt);
+  \draw [draw=black, every edge/.append style={draw=black, densely dashed, opacity=.5}]
+    (0,0,0) coordinate (o) -- ++(-\cubex,0,0) coordinate (a) -- ++(0,-\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubez)  -- ++(\cubex,0,0) coordinate (c) -- cycle
+    (o) -- ++(0,0,-\cubez) coordinate (d) -- ++(0,-\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
+    (o) -- (a) -- ++(0,0,-\cubez) coordinate (f) edge (g) -- (d) -- cycle;
+  \path [every edge/.append style={draw=black, |-|}]
+    (b) +(0,-5pt) coordinate (b1) edge ["$l$"'] (b1 -| c)
+    (b) +(-5pt,0) coordinate (b2) edge ["$l$"] (b2 |- a)
+    (c) +(3.5pt,-3.5pt) coordinate (c2) edge ["$l$"'] ([xshift=3.5pt,yshift=-3.5pt]e)
+    ;
+\end{tikzpicture}
+\\
+\textcolor{red}{Newton's $3^{\text{rd}}$ law - Every action has an equal and opposite reaction}\\
+$\Delta mc=mc_{x1}--mc_{x1}=2mc_{x1}$\\
+\\
+\\
+\textcolor{red}{Use $\text{Velocity}=\dfrac{\text{Distance}}{\text{Time}}$}\\
+Time=$\dfrac{\text{Distance}}{\text{Velocity}}=\dfrac{2l}{c_{x1}}$\\
+\\
+\\
+\textcolor{red}{Use force$=\dfrac{\text{Change in momentum}}{\text{time}}$}\\
+$\text{Force}=\dfrac{\Delta mc}{\Delta t}=\dfrac{2mc{x1}}{2l/c_{x1}}=\dfrac{mc_{x1}^2}{l}$\\
+\\
+\\
+\textcolor{red}{Use Pressure$=\dfrac{\text{Force}}{\text{Area}}$}\\
+\\
+$p_1=\dfrac{mc_{x1}^2/l}{l^2}=\dfrac{mc_{x1}^2}{l^3}$\\
+\\
+\\
+\textcolor{red}{Expand for N particles}\\
+$p=\Sigma p_n=p_1+p_2+p_3...+p_N$\\
+\\
+$p=\dfrac{mc_{x1}^2}{l^3}+\dfrac{mc_{x2}^2}{l^3}+\dfrac{mc_{x3}^2}{l^3}+\dfrac{mc_{xN}^2}{l^3}$\\
+\\
+$p=\dfrac{m}{l^3}(c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2)$\\
+\\
+\\
+\textcolor{red}{The mean of all the squares of the velocities is written as $\mathlarger{\bar{c_x^2}}$}\\
+\\
+$\mathlarger{\bar{c_x^2}}=\dfrac{c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2}{N}$\\
+\\
+$N\mathlarger{\bar{c_x^2}}=c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2$\\
+\\
+\\
+\textcolor{red}{Simplify expression for pressure}\\
+\\
+$p=\dfrac{Nm\mathlarger{\bar{c_x^2}}}{l^3}$\\
+\\
+\\
+\\
+\textcolor{red}{Consider in 3 dimensions}\\
+\\
+$\mathlarger{\bar{c^2}=\bar{c_x^2}+\bar{c_y^2}+\bar{c_z^2}}$\\
+\\
+\\
+\textcolor{red}{Average of mean square velocity for each dimension are equal}\\
+\\
+$\mathlarger{\bar{c_x^2}=\bar{c_y^2}=\bar{c_z^2}}$\\
+\\
+\\
+\textcolor{red}{Simplify 3D formula}\\
+\\
+$\mathlarger{\dfrac{\bar{c^2}}{3}=\bar{c_x^2}=\bar{c_y^2}=\bar{c_z^2}}$\\
+\\
+\\
+\textcolor{red}{Simplify pressure formula}\\
+\\
+$p=\dfrac{1}{3}\times\dfrac{Nm\mathlarger{\bar{c^2}}}{l^3}$\\
+\\
+\\
+\textcolor{red}{Insert Density formula}\\
+\\
+$\rho=\dfrac{\text{Mass}}{\text{Volume}}=\dfrac{Nm}{l^3}$
+\\
+\\
+\\
+\textcolor{red}{Substitute into Pressure formula}\\
+\\
+$$p=\frac{1}{3}\rho\mathlarger{\bar{c^2}}$$
+\newpage
+\section{The relationship between kinetic energy and temperature}
+$ $\\
+$p=\frac{1}{3}\rho\bar{c^2}$\\
+\\
+\textcolor{red}{Replace density with mass divided by volume}\\
+\\
+$p=\frac{1}{3}\times\frac{M}{V}\bar{c^2}$\\
+\\
+\textcolor{red}{Multiply both sides by V and rearrange to have kinetic energy in brackets}\\
+\\
+$pV=\frac{2}{3}(\frac{1}{2}M\bar{c^2})$\\
+\\
+\textcolor{red}{Replace M(Mass of all particles) with Nm(Number of particles $\times$ the mass of one particle}\\
+\\
+$pV=\frac{2N}{3}(\frac{1}{2}m\bar{c^2})$\\
+\\
+\textcolor{red}{Replace pV with nRT from Gas law equation}\\
+\\
+$nRT=\frac{2N}{3}(\frac{1}{2}m\bar{c^2})$\\
+\\
+\textcolor{red}{Divide both sides by n and simplify $\frac{N}{n}$ to Avagadro's constant}\\
+\\
+$RT=\frac{2}{3}N_A(\frac{1}{2}m\bar{c^2})$\\
+\\
+\textcolor{red}{Divide both sides by Avagadro's constant and simplify $\frac{R}{N_A}$ to Boltzman's Constant}\\
+\\
+$kT=\frac{2}{3}(\frac{1}{2}m\bar{c^2})$\\
+\\
+\textcolor{red}{Rearrange to have only kinetic energy on one side}\\
+\\
+$\frac{3}{2}kT=\frac{1}{2}m\bar{c^2}$\\
+\\
+\\
+This shows that Average KE $\propto$ Temperature\\
+\\
+\section{Root mean square velocity}
+$C_\text{RMS}=\mathlarger{\sqrt{\bar{c^2}}}$
+
 \end{document}

### 2017-12-07 Physics Notes/Magnetic Fields/Magnetic Fields.tex
Notes Update

--- 2017-11-05 Physics Notes/Capacitors/Capacitors.tex
@@
 \usepackage{fancyhdr}
-\usepackage{circuitikz}
+
 \pgfplotsset{width=10cm,compat=1.9}
@@
 \begin{center}
-\underline{\huge Capacitors}
+\underline{\huge Magnetic Fields}
 \end{center}
-A capacitor is constructed from two conducting plates separated by an insulator.\\
-Charge can flow onto and off the plates but not across the plates.
-
-\section{Charging circuit for a capacitor}
-\begin{center}
-\begin{circuitikz}[american voltages]
-\draw
-  (0,0) to [short] (3,0)
-  to [battery] (4,0)
-  (4,0) to[short] (5,0)
-  (4.4,-3) node[spdt](spdt) {}
-  (5,0) to[short] (spdt.out 1)
-  (spdt.in) to [capacitor] (2,-3)
-  (2,-3) to[short] (0,-3)
-(0,-3) to[short] (0,0)
-(spdt.out 2) to [short] (5,-5) 
-(5,-5) to[lamp] (1,-5) 
-(1,-5) to[short] (0,-5)
-(0,-5) to[short] (0,-3)
-  ;
-  \end{circuitikz}
-  \end{center}
-
-When charging the current flows round the top half of the circuit, when discharging the SPDT is changed to the other output and the current flows round the bottom half of the circuit.\\
+\section{Charged Particles in magnetic fields}
+Force is always perpendicular to the direction - no change in speed to the electrons.\\
 \\
-Capacitors can be used as simple timers in circuits.
+If electrons are confined to a wire $F=BIl$\\
 \\
+The same equation applies for many charges where:\\
 \\
-The time it takes to charge/discharge depends on:
-\begin{itemize}
-\item The capacitance of the capacitor \textbf{(C)}
-\item The resistance of the charging/discharging circuit \textbf{(R)}
-\end{itemize}
-\section{Energy stored in a capacitor}
-\begin{tikzpicture}[scale=0.5]
-\begin{axis}[xmin=0,ymin=-0.01,ylabel=V,xlabel=Q,axis lines=middle,label style={font=\LARGE},
-ytick={2},yticklabels=v,
-ticklabel style = {font=\LARGE},
-xtick={1.5,2.5},xticklabels={q,q+$\Delta$q}
-]
-\addplot[mark=none]{x};
-\addplot [mark=none] coordinates {(1.5,0) (1.5, 1.5)};
-\addplot [mark=none] coordinates {(2.5,0) (2.5, 2.5)};
-\addplot[mark=none,domain=0:2]{2};
-\end{axis}
-\filldraw[black, ultra thin,fill=gray!70] (2.5,0) -- (4.2,0) -- (4.2,3.5) -- (2.5,2.1) -- cycle;
-\end{tikzpicture}\\
-Area under graph=work done\\
-V is the average P.D. as charge increases from q to q+$\Delta$q\\
-$\Delta \text{w=v}\Delta \text{q}$\\
+$I=\dfrac{Q}{t} \quad l=vt$\\
 \\
-$Q=\frac{1}{2}QV=E$  \textbf{(Work done=energy stored)}\\
+$F=B\times\frac{Q}{t}\times vt$\\
 \\
-How to answer the exam question: Show that the energy stored by a capacitor is given by $E=\frac{1}{2}QV$
-\begin{enumerate}
-\item Sketch a graph of Q against V and describe what it shows
-\item Describe that electrical energy is the product of charge and voltage
-\item State QV is represented by the area under the line
-\item The area under the line is a triangle with area =$\frac{1}{2}QV$
-\item Therefore $E=\frac{1}{2}QV$
-\end{enumerate}
-$E=\frac{1}{2}QV$\\
-$Q=CV$\\
-Therefore:\\
-$E=\frac{1}{2}CV^2$\\
-$E=\frac{1}{2}\dfrac{Q^2}{C}$\\
+$F=BQv$\\
 \\
-The battery supplies energy QV to the circuit but the capacitor only stores $\frac{1}{2}QV$, this means that 50\% of the energy provided by the battery is wasted due to resistance in the circuit.
+\subsection{The hall probe}
+This is used to measure the strength of magnetic fields. It consists of a thin slice of semiconductor material with a constant current flowing through it.\\
+\\
+The negative charges go to the bottom of the material and so the top is positively charged, this creates a potential difference.\\
+\\
+$F_B=F_E$\\
+\\
+$BQV=\dfrac{VQ}{d}$\\
+\\
+$V=Bvd$\\
+\\
+$V\propto B$\\
+\\
+By measuring the voltage across the probe the magnetic field strength can be measured.
 

### 2017-12-08 Physics Notes/AS Level/Current Electricity/Current Electricity.tex
Physics Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{circuitikz}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{relsize}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{AS Level Physics - Electricity}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Current electricity}
\end{center}
\section{Basics of electricity}
\begin{itemize}
\item Current - The rate of flow of charge
\item Potential difference - Work done per unit charge
\end{itemize}
\section{Current-voltage characteristics}
\subsection{Ohmic Conductor}
\begin{tikzpicture}
\begin{axis}[axis lines=middle, ticks=none,scale=0.5,    ylabel = Current,xlabel=Voltage,ylabel style={rotate=90}
]
\addplot[color=black]{x};
\end{axis}
\end{tikzpicture}
\subsection{Bulb}
\begin{tikzpicture}
\begin{axis}[axis lines=middle, ticks=none,scale=0.5,    ylabel = Current,xlabel=Voltage,ylabel style={rotate=90}
]
\addplot[color=black,domain=-90:90]{sin(x)};
\end{axis}
\end{tikzpicture}
\subsection{Diode}
\includegraphics[width=2in]{diode.jpeg}\\
Ohm's Law: Current is proportional to voltage\\
\newpage
\section{Resistivity}
$\downarrow$ Temperature $\downarrow$ Resistance of any conductor\\
\\
\begin{tikzpicture}
\begin{axis}[axis lines=middle, ticks=none,scale=0.5,    ylabel = Resistance,xlabel=Temperature,ylabel style={rotate=90},xmin=0,xmax=5,ymin=0
]
\addplot[color=black,domain=1:4]{1/exp(x)};
\end{axis}
\end{tikzpicture}
\section{Superconductivity}
Below a certain temperature (critical temperature) the resistance of a material will be zero, this is described as superconductivity. The critical temperature depends on the material.\\
\\
Applications:\\
\begin{itemize}
\item Producing strong magnetic fields
\item The reduction in energy loss when transmitting power
\end{itemize}
\section{Circuits}
\subsection{Resistors}
\textbf{Series}: $R_T=R_1+R_2+R_3...$\\
\\
\textbf{Parallel}: $\dfrac{1}{R_T}=\dfrac{1}{R_1}+\dfrac{1}{R_2}+\dfrac{1}{R_3}...$
\subsection{Current}
\textbf{Series}: Current in = Current out. Current through multiple components is the same as through one\\
\textbf{Parallel}: Current into a junction = current out of a junction
\subsection{Voltage}
\textbf{Series}: Total voltage = the sum of voltages in the circuit\\
\textbf{Parallel}: Voltage in parallel components is equal
\section{Potential Dividers}
A potential divider is used to supply constant or variable potential difference from a power supply\\
\\
$\mathlarger{V_{Out}=V_{In}\dfrac{R_1}{R_1+R_2}}$\\
\\
Potential dividers can be used as part of sensor circuits to increase or decrease voltage based on environmental conditions\\
\newpage
\section{Electromotive force and internal resistance}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
Switch Open&Switch Closed\\
\hline
Voltmeter reads $\epsilon$&Voltmeter reads $\epsilon-IR$\\
\hline
\end{tabularx}
\subsection{Voltage Current Graph}
\begin{tikzpicture}
\begin{axis}[axis lines=middle,scale=0.5,    ylabel = Resistance,xlabel=Temperature,ylabel style={rotate=90,anchor=north},xlabel style={anchor=south},xmin=0,xmax=7,ymin=0,ymax=7,xtick={5},xticklabels={Short Circuit Current},ytick={5},yticklabels={$\epsilon$}
]
\addplot[color=black,domain=0:5]{-x+5};
\end{axis}
\end{tikzpicture}

\end{document}

### 2017-12-10 Physics Notes/AS Level/Mechanics and Materials/Force, Energy and Momentum/Force, Energy and Momentum - AS.tex
The Big Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{circuitikz}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{relsize}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{AS Level Physics - Mechanics and Materials}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Force, Energy and Momentum}
\end{center}
\section{Scalars and Vectors}
\textbf{Scalar} - Magnitude\\
\textbf{Vector} - Magnitude and Direction
\section{Moments}
\subsection{Moment}
$$\text{Force}\times \text{Perpendicular distance from the point to the line of action of the force}$$
\subsection{Couple}
$$\text{A pair of equal and opposite coplanar forces}$$
\subsection{Moment of a couple}
$$\text{Force}\times\text{Perpendicular distance between the lines of action of the forces}$$
\subsection{Principle of moments}
\begin{center}
For an object in equilibrium, \textbf{Clockwise Moments=Anticlockwise Moments}
\end{center}
\section{Graphs with respect to time}
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
\textbf{Type of Graph}&\textbf{Gradient}&\textbf{Area Under Graph}\\
\hline
Distance Time&Velocity&-\\
\hline
Velocity time&Acceleration&Displacement\\
\hline
Acceleration time&-&Change in velocity\\
\hline
\end{tabularx}
\section{Projectile motion}
For a falling object with no air resistance there is no horizontal acceleration or deceleration 
\subsection{Terminal Velocity}

\begin{tikzpicture}[
    force/.style={>=latex,draw=blue,fill=blue},
    m/.style={rectangle,draw=black,fill=lightgray,minimum size=0.3cm,thin},
]
    \node[m] (m) {};
    {[force,->]
        \draw (m.north) -- ++(0,1) node[above] {Drag};
        \draw (m.south) -- ++(0,-1) node[below] {$mg$};
    }
\end{tikzpicture}\\
As an object accelerates speed increases so drag increases, when \textbf{Drag=mg} the object has reached \textbf{terminal velocity} meaning that it now travels at a \textbf{constant velocity}
\subsection{The effect of air resistance}
\includegraphics[scale=0.25]{Air_Resistance.JPG}\\
\textcolor{orange}{No Air Resistance}\\
\textcolor{red}{Air resistance
\begin{itemize}
\item Steeper descent
\item Peak Further Left
\item Smaller Range
\end{itemize}}
\subsubsection{Factors that affect air resistance}
\begin{itemize}
\item Surface area
\item Air Pressure/Density
\item Speed
\item Roughness of shape
\end{itemize}
\section{Newton's laws of motion}
\textbf{First Law} - Objects either stay at rest or move with a constant velocity unless acted on by a resultant force\\
\textbf{Second law} - For an object with constant mass its acceleration will be directly proportional to the resultant force $F=ma$\\
\textbf{Third law} - Every action has an equal and opposite reaction
\section{Momentum}
$\text{Momentum=Mass}\times\text{Velocity}$\\
In a collision \textbf{Momentum is conserved}\\
\textbf{Impulse}=Change in momentum\\
The area under a force time graph is the impulse\\
\textbf{Elastic collision} - A collision with no loss of kinetic energy\\
\textbf{Inelastic collision} - A collision with a loss of kinetic energy
\section{Work, energy and power}
Rate of doing work=Rate of energy transfer\\
The area under a force displacement graph is the \textbf{work done}
\section{Conservation of energy}
\textbf{Principle of conservation of energy} - In an isolated system the total energy remains constant

\end{document}

### 2017-12-10 Physics Notes/AS Level/Mechanics and Materials/Materials/Materials - AS.tex
The Big Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{circuitikz}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{relsize}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{AS Level Physics - Mechanics and Materials}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Materials}
\end{center}
\section{Bulk Properties of solids}
\textbf{Hooke's law} - Force is directly proportional to extension, provided the proportionality limit has not been reached
\subsection{Spring constant}
\subsubsection{Series}
$$\text{Spring constant}=\dfrac{\text{Spring constant of one spring}}{\text{Number of springs}}$$
\subsubsection{Parallel}
$$\text{Spring constant=Spring constant of one spring} \times \text{Number of springs}$$
\subsection{Material properties}
\textbf{Brittle material} - Snap\\
\textbf{Ductile material} - Stretch\\
\textbf{Plastic Behaviour} - The behaviour of a material after it has reached it's elastic limit
\subsection{Stress strain graph of a metal wire}
\includegraphics[width=4in]{Stress_Strain.jpg}\\
\section{The Young Modulus}
The \textbf{gradient}of a stress strain graph is the Young Modulus\\
\\
\textbf{Units} of Young Modulus: $\text{Nm}^{-2}$ or Pa\\
\\
\textbf{Stiff Material} - \textbf{High} Young Modulus\\
\textbf{Flexible Material} - \textbf{Low} Young Modulus\\
\newpage
\subsection{Searle's apparatus for measuring Young's Modulus}
\includegraphics[width=3in]{Searle.jpg}\\
\subsection{Vernier apparatus for measuring Young's Modulus}
\includegraphics[width=3in]{young_modulus.jpg}\\
\newpage
\section{Stress Strain Graphs}
\subsection{Rubber}
\includegraphics[width=2in]{rubber.jpg}\\
\subsection{Metal}
\includegraphics[width=2in]{metal.jpg}\\
\subsection{Polythene}
\includegraphics[width=2in]{Polythene.png}\\
\end{document}

### 2017-12-10 Physics Notes/AS Level/Current Electricity/Current Electricity.tex
Notes Update

@@
 \begin{tikzpicture}
-\begin{axis}[axis lines=middle,scale=0.5,    ylabel = Resistance,xlabel=Temperature,ylabel style={rotate=90,anchor=north},xlabel style={anchor=south},xmin=0,xmax=7,ymin=0,ymax=7,xtick={5},xticklabels={Short Circuit Current},ytick={5},yticklabels={$\epsilon$}
+\begin{axis}[axis lines=middle,scale=0.5,    ylabel = Vr,xlabel=Current,ylabel style={rotate=90,anchor=south},xlabel style={anchor=south},xmin=0,xmax=7,ymin=0,ymax=7,xtick={5},xticklabels={Short Circuit Current},ytick={5},yticklabels={$\epsilon$}
 ]

### 2017-12-10 Physics Notes/AS Level/Particles and radiation/Electromagnetic Radiation and quantum phenomena/Electromagnetic Radiation - AS.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{circuitikz}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{relsize}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty=10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{AS Level Physics - Particles and Radiation}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Electromagnetic radiation and quantum phenomena}
\end{center}
\section{The photoelectric effect}
\textbf{The photoelectric effect - Metals liberate electrons when hit by photons}\\
\begin{tabularx}{\textwidth}{|X|X|}
\hline
\textbf{Observation}&\textbf{Explanation}\\
\hline
There is a minimum frequency required to liberate an electron, called the threshold frequency&At the minimum frequency KE=0 so the frequency must be Planck's Constant$\times$Frequency\\
\hline
Above the threshold frequency electrons are emitted immediately, regardless of intensity&Energy is immediately passed on\\
\hline
Intensity and electrons per second are directly proportional&1 photon liberates 1 electron\\
\hline
Below the threshold frequency no electrons are emitted, no matter the intensity&At the minimum frequency KE=0 so the frequency must be Planck's Constant$\times$Frequency\\
\hline
The electrons are emitted with a range of speeds unrelated to intensity&Through the metal the collisions for each electron vary, varying KE\\
\hline
Increasing frequency increases maximum speed but not number liberated per second&1 Photon liberates 1 electron\\
\hline
\end{tabularx}
\subsection{Why the photoelectric effect can't be explained by the wave model}
Waves transfer energy, it would be expected that the more intense the source the more energy the electrons would have.\\
Given enough time electrons should be emitted with waves
\subsection{Millikan's experiment}
\begin{tikzpicture}
\begin{axis}[axis lines=middle,scale=0.8,ylabel = KE,xlabel=Frequency,ylabel style={rotate=90,anchor=south},xlabel style={anchor=south},xmin=0,xmax=7,ymin=-5,ymax=7,xtick={2},xticklabels={$F_0$},ytick={-2},yticklabels={$-\Phi$}
]
\addplot[color=black,domain=0:7]{x-2};
\end{axis}
\end{tikzpicture}\\
$F_0$ - Threshold Frequency\\
$-\Phi$ - Negative work function\\
\textbf{Gradient} - Planck's Constant\\
Equation of line - $E_K=hf-\phi$ 
\newpage
\section{Collisions of electrons with atoms}
\textbf{Ionisation} - The adding or removal of electrons from an element\\
\textbf{Excitation} - The moving of an electron to a higher energy level\\
\subsection{How a fluorescent lamp works}
\begin{enumerate}
\item In a sealed unit with a phosphor coating on the inside of the glass. A small amount of mercury and an inert gas at a low pressure
\item When the voltage is switched on electrons move from the cathode to the anode
\item The electrons collide with the mercury, turning it into a vapour
\item Once a vapour, the moving electrons can then collide with the mercury gas atoms, exciting the bound electrons
\item The fired electron has undergone collisional excitation so has less energy
\item The mercury excitation produces UV rays
\item The phosphor coating is a chemical designed so it has UV excitation energy similar to the mercury excitation energy
\item The phosphor absorbs photons and emits visible light
\end{enumerate}
\section{Energy levels and photon emission}
\subsection{Absorption Spectra}
This happens when a cool material is placed between a hot light and the observer.\\
This causes dark lines in the spectrum\\
From this it can be inferred that atoms only absorb radiation of certain frequencies.\\
This technique can be used to identify different atoms\\
The difference in absorption is caused by different numbers of electrons\\
\subsection{Emission spectra}
This is caused when a gas is heated\\
The lines have the same wavelengths as absorption but the lines are light, rather than dark\\
This is caused by electrons becoming excited and so emitting an electron\\
\begin{tabularx}{\textwidth}{|X|X|}
\hline
\textbf{Observation}&\textbf{Reason}\\
\hline
Discrete lines&The electrons are absorbing/emitting photons\\
\hline
The spectrum does not depend on the isotope&The electrons are arranged in shells\\
\hline
The spectral lines get closer together as the energy increases&The photons need a certain amount of energy to excite an electron\\
\hline
\end{tabularx}
\subsection{The hydrogen atom}
The hydrogen atom is used as the example for energy level calculations. The ground state is the state of minimum energy, calculations can be performed for all the energy levels
\section{Wave-Particle Duality}
Electron diffraction suggests that particles possess wave properties. The photoelectric effect suggests electromagnetic waves have a particle nature.\\
The amount of diffraction changes when the momentum of the particle changes as it has a different de Broglie wavelength.
\end{document}

### 2017-12-10 Physics Notes/AS Level/Particles and radiation/Particles/Particles - AS.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{circuitikz}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{relsize}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{AS Level Physics - Particles and Radiation}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Particles}
\end{center}
\section{Constituents of the atom}
\textbf{Specific charge} - The charge to mass ratio\\
\textbf{Isotope} - An atom with the same number of protons as an element but a different number of neutrons
\section{Stable and unstable nuclei}
\subsection{The strong nuclear force}
$0fm-0.5fm$ - \textbf{Repulsion}\\
$0.5fm-3fm$ - \textbf{Attraction}\\
$3fm+$ - \textbf{No force}
\subsection{Alpha decay}
An atom emits an alpha particle (Helium Nucleus/2 protons and 2 neutrons)\\
Reduces \textit{Mass Number} by \textbf{4} and \textit{proton number} by \textbf{2}
\subsection{Beta decay}
Neutron$\rightarrow$Proton+Electron+Neutrino\\
The neutrino was hypothesised to conserve energy
\section{Particles, antiparticles and photons}
For every particle there is a corresponding antiparticle (can be itself)\\
\\
{\def\arraystretch{1.5}
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
\textbf{Property}&\textbf{Particle}&\textbf{Antiparticle}\\
\hline
Mass&x&x\\
\hline
\textcolor{red}{Charge}&x&-x\\
\hline
Rest Energy&x&x\\
\hline
\textcolor{red}{Baryon Number}&x&-x\\
\hline
\textcolor{red}{Lepton Number}&x&-x\\
\hline
\textcolor{red}{Strangeness}&x&-x\\
\hline
\end{tabularx}}
\\
\\
When a particle and antiparticle collide they annihilate each other\\
A particle-antiparticle pair can be produced from energy
\section{Particle interactions}
Fundamental interactions:\\
{\def\arraystretch{1.5}

\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
\textbf{Force}&\textbf{Affects}&\textbf{Gauge Boson}&\textbf{Range}\\
\hline
Gravitational&Mass&Graviton&Infinite\\
\hline
Electromagnetic&Charge&Photon&Infinite\\
\hline
Nuclear Strong&Quarks&Gluon(Pion)&$10^{-15}$m\\
\hline
Nuclear Weak&Leptons+Quarks&$W^+,W^-,Z^0$&$10^{-18}$m\\
\hline
\end{tabularx}}\\
\\
\newpage
The exchange particles provide the forces between elementary particles\\
Virtual photons are the exchange particle of the electromagnetic force\\
Examples of the weak interaction:
\begin{itemize}
\item $\beta^+$ Decay
\item $\beta^-$ Decay
\item Electron capture
\item Electron-proton collisions
\end{itemize}
\section{Classification of particles}
\subsection{Hadrons}
Hadrons are subject to the strong interaction\\
There are two types of hadrons:
\begin{itemize}
\item Baryon(3 Quarks)
\item Meson (Quark-Antiquark pair)
\end{itemize}
The baryon number is conserved in an interaction\\
All baryons will eventually decay into protons\\
Kaons can decay into pions\\
\subsection{Leptons}
Types of lepton(All have a lepton number of 1):
\begin{itemize}
\item Electron
\item Muon
\item Electron Neutrino (Approximated to massless)
\item Muon Neutrino (Approximated to massless)
\end{itemize}
Lepton number is conserved during an interaction\\
Muons decay into electrons\\
\subsection{Strange particles}
Produced through the strong interaction\\
Decay through the weak interaction
\newpage
\section{Quarks and antiquarks}
\subsection{Baryons}
{\def\arraystretch{1.2}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
Proton&UUD\\
\hline
Neutron&DUD\\
\hline
\end{tabularx}}
\subsection{Mesons}
\subsubsection{Pions(All 0 Strangeness)}
{\def\arraystretch{1.5}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
$\pi^0$&$U\bar{U}$ or $D\bar{D}$\\
\hline
$\pi^+$&$U\bar{D}$\\
\hline
$\pi^-$&$D\bar{U}$\\
\hline
\end{tabularx}}
\subsubsection{Kaons (All strange)}
{\def\arraystretch{1.5}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
$K^+$&$U\bar{S}$\\
\hline
$K^-$&$\bar{U}S$\\
\hline
$K^0$&$D\bar{S}$\\
\hline
$\bar{K^0}$&$\bar{D}S$\\
\hline
\end{tabularx}}

\end{document}

### 2017-12-10 Physics Notes/AS Level/Waves/Progressive and stationary waves/Progressive and Stationary waves- AS.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{circuitikz}
\usetikzlibrary{decorations.pathmorphing,arrows}

\pgfplotsset{width=10cm,compat=1.9}
\usepackage{relsize}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{AS Level Physics - Waves}
\rfoot{Page \thepage}

\pgfkeys{/pgfplots/Axis Style/.style={
    width=13.5cm, height=10cm,
    axis x line=center, 
    axis y line=middle, 
    samples=100,
    ymin=-1.2, ymax=1.2,
    xmin=0, xmax=13.0,
    domain=-4*pi:4*pi
}}
\pgfkeys{/pgfplots/Stationary Wave/.style={
    width=13.5cm, height=5cm,
    axis x line=center, 
    axis y line=middle, 
    samples=100,
    ymin=-1.2, ymax=1.2,
    xmin=0, xmax=13.0,
    domain=-4*pi:4*pi
}}

\begin{document}
\begin{center}
\underline{\huge Progressive and stationary waves}
\end{center}
\section{Progressive waves}
\subsection{Transverse wave}
\begin{tikzpicture}[scale=0.8]
\tikzstyle{vlabel} = [fill=white,font=\footnotesize,inner sep=1pt,rotate=90]
\tikzstyle{hlabel} = [fill=white,font=\normalsize,inner sep=1pt]
\node[vlabel] at (1.2,6) {Amplitude};
\draw[arrows=<->,red,ultra thick](1.35,4.2)--(1.35,7.6);
\node[hlabel] at (7,3.3) {Wavelength};
\draw[arrows=<->,red,ultra thick](3,3.6)--(8.9,3.6);

\begin{axis}[
    Axis Style,
    y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
    ylabel = {Displacement},
    xlabel= {Distance},
    ticks=none
]
\addplot [mark=none, ultra thick, black] {sin(deg(x))};
\end{axis}
\end{tikzpicture}
\\
\\
Wave direction and energy are perpendicular
\subsection{Longitudinal wave}
\begin{tikzpicture}[decoration={coil},scale=1.8]
\tikzstyle{hlabel} = [fill=white,font=\normalsize,inner sep=1pt]
\node[hlabel] at (5,0.8) {Wavelength};

\draw[arrows=<->,red,ultra thick](3.26,0.5)--(6.74,0.5);
\draw[arrows=->,red,ultra thick](3.26,-1)--(3.26,-0.5);
\draw[arrows=->,red,ultra thick](8.5,-1)--(8.5,-0.5);
\node[hlabel] at (3.26,-1.2) {Compression};
\node[hlabel] at (8.5,-1.2) {Rarefaction};
\draw[decorate, decoration={aspect=0.3, segment length=3mm, amplitude=3mm}] (0,0) --(3.03,0);
\draw[decorate, decoration={aspect=0.3, segment length=0.5mm, amplitude=-3mm}] (3.03,0) -- (3.49,0); 
\draw[decorate, decoration={aspect=0.3, segment length=3mm, amplitude=-3mm}] (3.48,0) -- (6.51,0);
\draw[decorate, decoration={aspect=0.3, segment length=0.5mm, amplitude=-3mm}] (6.51,0) -- (6.97,0);
\draw[decorate, decoration={aspect=0.3, segment length=3mm, amplitude=-3mm}] (6.97,0) -- (10,0);
\end{tikzpicture}
\\
\\
wave direction and energy are parallel
\subsection{Definitions}
\textbf{Displacement} - Distance from equilibrium  to the position of the particle\\
\textbf{Amplitude} - The maximum displacement of a particle\\
\textbf{Wavelength} - The distance from a point on a wave to the same point on the next wave\\
\textbf{Complete cycle} - The cycle from one point of maximum displacement to the next section of maximum displacement\\
\textbf{Period} - The time for 1 complete cycle\\
\textbf{Frequency} - The number of complete cycles per second
\newpage
\subsection{Polarisation}
Polarised light all travels in the same direction\\
Unpolarised light travels in all directions\\
Unpolarised light can be polarised using a polarising filter which contains stripes, only allowing one direction of light through\\
\textbf{Only transverse waves can be polarised}
\\
\\
\begin{tikzpicture}[x={(0.866cm,-0.5cm)}, y={(0.866cm,0.5cm)}, z={(0cm,1cm)}, scale=.8,
    %Option for nice arrows
    >=stealth, %
    inner sep=0pt, outer sep=2pt,%
    axis/.style={thick,<-},
    wave/.style={thick,color=#1,smooth},
    polaroid/.style={fill=black!60!white, opacity=0.3},
]
    % Colors
    \colorlet{darkgreen}{green!50!black}
    \colorlet{lightgreen}{green!80!black}
    \colorlet{darkred}{red!50!black}
    \colorlet{lightred}{red!80!black}

    % Frame
    \coordinate (O) at (0, 0, 0);
    \draw[axis] (O) -- +(14, 0,   0);
    \draw[thick,dashed] (-2,0,0) -- (0,0,0);

    % Electric field vectors
    \draw[wave=blue, variable=\x,samples at={0,0.25,...,6}]
        plot (\x,{sin(2*\x r)},0);
    %Polarized light between polaroid and thin section
    \foreach \x in{0, 0.25,...,6}
        \draw[color=blue,->] (\x,0,0) -- (\x,{sin(2*\x r)},0);

    \draw (3,1,1) node [text width=2.5cm, text centered]{Polarized light};

    %Crystal thin section
    \begin{scope}[thick]
        \draw (6,-2,-1.5) -- (6,-2,1.5) node [above, sloped, midway]{Polarising filter}
                -- (6, 2, 1.5) -- (6, 2, -1.5) -- cycle % First face
            (6,  -2, -1.5) -- (6.2, -2,-1.5)
            (6,   2, -1.5) -- (6.2,  2,-1.5)
            (6,  -2,  1.5) -- (6.2, -2, 1.5)
            (6,   2,  1.5) -- (6.2,  2, 1.5)
            (6.2,-2, -1.5) -- (6.2, -2, 1.5) -- (6.2, 2, 1.5) 
                -- (6.2, 2, -1.5) -- cycle; % Second face
    \end{scope}

    %Rays leaving thin section
    \draw[wave=darkred,   variable=\x, samples at={6.2,6.45,...,12}] 
        plot (\x, {0.26*0.26*sin(2*(\x-0.5) r)},  {0.966*0.26*sin(2*(\x-0.5) r)});  %n'g-oriented ray
    \draw[wave=darkgreen, variable=\x, samples at={6.2,6.45,...,12}]
        plot (\x, {0.966*0.966*sin(2*(\x-0.1) r)},{-0.26*0.966*sin(2*(\x-0.1) r)}); %n'p-oriented ray
    \draw (10,1,1) node [text width=2.5cm, text centered] {Unpolarised light};

    \foreach \x in{6.2,6.45,...,12} {
        \draw[color=darkgreen, ->] (\x, 0, 0) --
            (\x, {0.966*0.966*sin(2*(\x-0.1) r)}, {-0.26*0.966*sin(2*(\x-0.1) r)});
        \draw[color=darkred,   ->] (\x, 0, 0) --
            (\x, {0.26*0.26*sin(2*(\x-0.5) r)}, {0.966*0.26*sin(2*(\x-0.5) r)});
            }
\end{tikzpicture}
\section{The superposition of waves and stationary waves}
Stationary waves are formed when a wave collides with itself after reflection\\
\\
\\
\begin{tikzpicture}
\draw[black,ultra thick] (11.5,0.2) -- ++(0,3.1);
\draw[black,ultra thick] (11.5,0.3) -- (12,0.7);
\draw[black,ultra thick] (11.5,1) -- ++(0.5,0.4);
\draw[black,ultra thick] (11.5,1.7) -- ++(0.5,0.4);
\draw[black,ultra thick] (11.5,2.4) -- ++(0.5,0.4);
\draw[black,ultra thick] (11.5,3.1) -- ++(0.5,0.4);
\tikzstyle{hlabel} = [font=\normalsize,inner sep=1pt]
\draw[arrows=->,red,ultra thick](3.26,3.5)--(6.74,3.5);
\node[hlabel,red] at (5,3.7) {Incoming wave};
\draw[arrows=<-,blue,ultra thick](3.26,-0.2)--(6.74,-0.2);
\node[hlabel,blue] at (5,-0.4) {Reflected wave};
\draw[arrows=->,orange,ultra thick](10.1,-0.7)-- ++(0,0.8);
\node[hlabel,orange] at (10.1,-0.9) {Antinode};

\draw[arrows=->,orange,ultra thick](8.65,4.5)-- ++(0,-2.5);
\node[hlabel,orange] at (8.65,4.7) {Node};

\begin{axis}[
    Stationary Wave,
    ticks=none,
    axis line style={draw=none}
]
\addplot [mark=none, ultra thick, blue] {sin(deg(x))};
\addplot [mark=none, ultra thick, red] {sin(deg(x+pi))};
\end{axis}
\end{tikzpicture}
\\
When both waves are at equilibrium there is a \textbf{node}\\
When one wave is at a maximum and one at a minimum there is an \textbf{antinode}\\
\subsection{Sound}
\includegraphics[width=15cm]{Sound.jpg}\\
Dust heaps are made at nodes and dips are made at antinodes\\
$\lambda$=Distance between the nodes $\times2$
\subsection{Microwaves}
\includegraphics[width=10cm]{Microwaves.jpg}\\
The receiver can be moved to find areas of nodes or antinodes
\subsection{Harmonics}
\includegraphics[width=15cm]{Harmonics.jpg}\\

\end{document}

### 2017-12-10 Physics Notes/AS Level/Waves/Refraction, Diffraction and Interference/Refraction, Diffraction and Interference - AS.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{circuitikz}
\usetikzlibrary{decorations.pathmorphing,arrows,shapes,positioning,decorations.markings,angles,quotes}

\pgfplotsset{width=10cm,compat=1.9}
\usepackage{relsize}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{AS Level Physics - Waves}
\rfoot{Page \thepage}

\pgfkeys{/pgfplots/Axis Style/.style={
    width=13.5cm, height=10cm,
    axis x line=center, 
    axis y line=middle, 
    samples=100,
    ymin=-1.2, ymax=1.2,
    xmin=0, xmax=13.0,
    domain=-4*pi:4*pi
}}
\pgfkeys{/pgfplots/Stationary Wave/.style={
    width=13.5cm, height=5cm,
    axis x line=center, 
    axis y line=middle, 
    samples=100,
    ymin=-1.2, ymax=1.2,
    xmin=0, xmax=13.0,
    domain=-4*pi:4*pi
}}

\tikzstyle arrowstyle=[scale=1]
\tikzstyle directed=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrow[arrowstyle]{stealth}}}}]
\tikzstyle reverse directed=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrowreversed[arrowstyle]{stealth};}}}]

\begin{document}
\begin{center}
\underline{\huge Refraction, Diffraction and interference}
\end{center}
\section{Interference}
\textbf{Coherence} - Waves with the same frequency and a constant phase difference\\
\includegraphics[width=10cm]{Interference.jpg}\\
When two of the same type of point meet they cause \textbf{reinforcement/constructive interference}\\
When a point meets with its opposite they cause \textbf{cancellation/destructive interference}
\section{Diffraction}
\includegraphics[width=7cm]{Diffraction.png}
\subsection{Diffraction of different colours}
\includegraphics[width=7cm]{Diffraction_Colours.png}\\
Increasing wavelength:
\begin{itemize}
\item Central maxima becomes wider
\item Secondary maxima become wider apart
\end{itemize}
\newpage
\subsection{Deriving $n\lambda=d\sin\theta$}
\includegraphics[width=7cm]{nlambda_1.png}\\
\includegraphics[width=7cm]{nlambda_2.png}\\
Path difference =$d\sin\theta$\\
$n\lambda=d\sin\theta$
\section{Refraction}
\subsection{Refraction at a plane surface}

\begin{figure}[h]
    \centering
    \begin{minipage}{0.28\textwidth}
        \centering
\begin{tikzpicture}[scale=0.5]

    % define coordinates
    \coordinate (O) at (0,0) ;
    \coordinate (A) at (0,4) ;
    \coordinate (B) at (0,-4) ;

    % media
    \fill[blue!25!,opacity=.3] (-4,0) rectangle (4,4);
    \fill[blue!60!,opacity=.3] (-4,0) rectangle (4,-4);
    \node[right] at (2,2) {Air};
    \node[left] at (3,-1.8) {Water};

    % axis
    \draw[dash pattern=on5pt off3pt] (A) -- (B) ;

    % rays
    \draw[red,ultra thick,reverse directed] (O) -- (240:4.63);
    \draw[blue,directed,ultra thick] (O) -- (45:4.24);

    % angles
;
    \node[] (a) at (240:4.63)  {};
    \node[] (c) at (270:4)  {};
    \node[] (b) at (270:0)  {};

    \node[] (d) at (45:4.24)  {};
    \node[] (e) at (90:4)  {};

    \draw pic["$\theta_1$",draw=black,-,angle eccentricity=1.2,angle radius=1.5cm] {angle=a--b--c};
    \draw pic["$\theta_2$",draw=black,-,angle eccentricity=1.2,angle radius=1.5cm] {angle=d--b--e};

\end{tikzpicture}
        \caption{Normal Refraction}
    \end{minipage}\hfill
    \begin{minipage}{0.28\textwidth}
        \centering
\begin{tikzpicture}[scale=0.5]

    % define coordinates
    \coordinate (O) at (0,0) ;
    \coordinate (A) at (0,4) ;
    \coordinate (B) at (0,-4) ;

    % media
    \fill[blue!25!,opacity=.3] (-4,0) rectangle (4,4);
    \fill[blue!60!,opacity=.3] (-4,0) rectangle (4,-4);
    \node[right] at (2,2) {Air};
    \node[left] at (3,-1.8) {Water};

    % axis
    \draw[dash pattern=on5pt off3pt] (A) -- (B) ;

    % rays
    \draw[red,ultra thick,reverse directed] (O) -- (230:4.63);
    \draw[blue,directed,ultra thick] (O) -- (0:4);

    % angles
;
    \node[] (a) at (230:4.63)  {};
    \node[] (c) at (270:4)  {};
    \node[] (b) at (270:0)  {};

    \draw pic["$\theta_C$",draw=black,-,angle eccentricity=1.2,angle radius=1.5cm] {angle=a--b--c};   
\end{tikzpicture}
        \caption{Critical angle}
    \end{minipage}\hfill
    \begin{minipage}{0.28\textwidth}
        \centering
\begin{tikzpicture}[scale=0.5]

    % define coordinates
    \coordinate (O) at (0,0) ;
    \coordinate (A) at (0,4) ;
    \coordinate (B) at (0,-4) ;

    % media
    \fill[blue!25!,opacity=.3] (-4,0) rectangle (4,4);
    \fill[blue!60!,opacity=.3] (-4,0) rectangle (4,-4);
    \node[right] at (2,2) {Air};
    \node[left] at (-1.8,-3) {Water};

    % axis
    \draw[dash pattern=on5pt off3pt] (A) -- (B) ;

    % rays
    \draw[red,ultra thick,reverse directed] (O) -- (210:4.63);
    \draw[blue,directed,ultra thick] (O) -- (330:4.63);

    % angles
;
    \node[] (a) at (210:4.63)  {};
    \node[] (c) at (270:4)  {};
    \node[] (b) at (270:0)  {};

    \node[] (d) at (330:4.24)  {};
    \node[] (e) at (270:4)  {};

    \draw pic["$\theta_1$",draw=black,-,angle eccentricity=1.2,angle radius=1cm] {angle=a--b--c};
    \draw pic["$\theta_2$",draw=black,-,angle eccentricity=1.2,angle radius=1cm] {angle=e--b--d};

\end{tikzpicture}
        \caption{Total internal reflection}
    \end{minipage}
\end{figure}
The angle is measured from the normal to the ray\\
After the angle reaches the critical angle the ray will undergo \textbf{total internal reflection}
\subsection{Fibre Optics}
\includegraphics[width=7cm]{Fibre_Optic_1.png}\\
\includegraphics[width=7cm]{Fibre_Optic_2.jpg}\\
\subsubsection{Modal Dispersion}
Waves entering the fibre at different angles will reflect differently and so will have different path lengths
\subsubsection{Material Dispersion}
Different wavelengths of light enter the same but refract differently, causing a difference in path length

\end{document}

### 2017-12-11 Maths Notes/D2/Allocation Problems/Allocation Problems.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{enumerate}
\usepackage{amssymb}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{tikz}
\usetikzlibrary{calc,shapes.geometric, arrows}
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30,text width=2cm]
\tikzstyle{arrow} = [thick,->,>=stealth]

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}	
\newcommand{\cred}[1]{\color{red}#1}
\newcommand{\cblue}[1]{\color{blue}#1}
\newcommand{\cgreen}[1]{\color{green}#1}
\hyphenpenalty=10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - D2}
\rfoot{Page \thepage}
\usepackage{float}

\newcommand{\tikzmark}[1]{\tikz[overlay,remember picture] \node (#1) {};}

\newcommand{\DrawVLine}[3][]{%
    \begin{tikzpicture}[overlay,remember picture]
        \draw [#1] ($(#2.north)$) -- ($(#3.north)$);
    \end{tikzpicture}%
}%
\newcommand{\DrawLine}[3][]{%
    \begin{tikzpicture}[overlay,remember picture]
        \draw [#1] ($(#2)+(-0.4,0.6ex)$) -- ($(#3)+(0.6,0.6ex)$);
    \end{tikzpicture}%
}%

\begin{document}
\begin{center}
\underline{\huge Allocation Problems}
\end{center}
\section{Cost Matrices}
\begin{itemize}
\item Require the same number of tasks as workers
\item Only relative costs are important
\end{itemize}
To find a reduced cost matrix:
\begin{enumerate}
\item Subtract the least value in each row from each element of that row
\item Using the new matrix, subtract the least value in each column from each element in that column
\end{enumerate}
\section{Hungarian algorithm}
\begin{enumerate}
\item Find the reduced cost matrix
\item Determine the minimum number of horizontal or vertical straight lines which will cover all the zeros in the matrix
\begin{itemize}
\item If lines $\geqslant$ n, where the matrix is n$\times$n then STOP
\item If lines $<$n, the matrix can be improved and continue 
\end{itemize}
\item Draw in the lines and look for the smallest uncovered element, call it $e$
\item Add $e$ to all covered elements, add it twice if covered twice
\item Subtract $e$ from \textbf{all} elements of the matrix (even those that just had $e$ added)
\item Repeat steps 2-5 until an optimal solution is found
\end{enumerate}
\subsection{Example}
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&250&80&160\\
\hline
Percival&230&90&150\\
\hline
Spike&230&110&140\\
\hline
\end{tabular}\\
\\
\textbf{Find the reduced cost matrix - First process rows}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&170&0&80\\
\hline
Percival&140&0&60\\
\hline
Spike&120&0&30\\
\hline
\end{tabular}\\
\\
\textbf{Find the reduced cost matrix - process columns}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&50&0&50\\
\hline
Percival&20&0&30\\
\hline
Spike&0&0&0\\
\hline
\end{tabular}\\
\textbf{Draw lines to cover zeros}\\
$
\begin{array}{|c|c|c|c|}
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartB}}&
\multicolumn{1}{c}{}\\
\hline
&Dig&Weed&Cut\\
\hline
Boris&50&0&50\\
\hline
Percival&20&0&30\\
\hline
\tikzmark{StartA}Spike&0&0&\tikzmark{EndA}0\\
\hline

\multicolumn{1}{c}{}&
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndB}}}&
\multicolumn{1}{c}{}\\
\end{array}\\
$
\DrawLine[red, very thick,dotted]{StartA}{EndA}
\DrawVLine[red,very thick,dotted]{StartB}{EndB}
\\
\textbf{Compare to dimension of matrix}\\
2 Lines$\leqslant$3$\times$3 matrix\\
\\
\textbf{Find the smallest uncovered element}\\
20 (Percival digging)\\
\\
\\
\textbf{Add e to all covered elements, and add twice for double covering}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&50&20&50\\
\hline
Percival&20&20&30\\
\hline
Spike&20&40&20\\
\hline
\end{tabular}\\
\\
\textbf{Subtract e from all elements}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&30&0&30\\
\hline
Percival&0&0&10\\
\hline
Spike&0&20&0\\
\hline
\end{tabular}\\
\\
\textbf{Draw lines to cover zeros}\\
\\
$
\begin{array}{|c|c|c|c|}
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartA}}&
\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartB}}&
\multicolumn{1}{c}{}\\
\hline
&Dig&Weed&Cut\\
\hline
Boris&30&0&30\\
\hline
Percival&0&0&10\\
\hline
\tikzmark{StartC}Spike&0&20&\tikzmark{EndC}0\\
\hline
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndA}}}&
\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndB}}}&
\multicolumn{1}{c}{}\\
\end{array}\\
$
\DrawVLine[red, very thick,dotted]{StartA}{EndA}
\DrawVLine[red, very thick,dotted]{StartB}{EndB}
\DrawLine[red, very thick,dotted]{StartC}{EndC}
\\
\textbf{Compare to dimension of matrix}\\
3 lines=$3\times3$ matrix - Optimal solution
\section{Dummy Locations}
When the problem is not n$\times$n a dummy location is used, this has zeroes in all the elements.
\subsection{Example}
\begin{tabular}{|c|c|c|c|}
\hline
&Task A&Task B&Task C\\
\hline
Mark&12&23&15\\
\hline
Nicky&14&21&17\\
\hline
Nigel&13&22&20\\
\hline
Susie&14&24&13\\
\hline
\end{tabular}\\
\\
\textbf{Add another task with zero cost}\\
\begin{tabular}{|c|c|c|c|c|}
\hline
&Task A&Task B&Task C&Task D\\
\hline
Mark&12&23&15&0\\
\hline
Nicky&14&21&17&0\\
\hline
Nigel&13&22&20&0\\
\hline
Susie&14&24&13&0\\
\hline
\end{tabular}\\
\\
\textbf{This is then processed as usual}
\section{Incomplete data}
The algorithm can also work on incomplete data (where a person cannot to a task). To do this assign values to the tasks that cannot be done that are at least \textbf{twice as large} as the largest value.
\subsection{Example}
\begin{tabular}{|c|c|c|c|c|}
\hline
&Chinese&French&Indian&Italian\\
\hline
Denis&-&27&15&40\\
\hline
Hilary&14&21&17&13\\
\hline
Robert&20&-&13&-\\
\hline
Trudy&14&24&10&30\\
\hline
\end{tabular}
\newpage
\textbf{The cells with dashes in are then replaced with 100}\\
\begin{tabular}{|c|c|c|c|c|}
\hline
&Chinese&French&Indian&Italian\\
\hline
Denis&\textcolor{red}{100}&27&15&40\\
\hline
Hilary&14&21&17&13\\
\hline
Robert&20&\textcolor{red}{100}&13&\textcolor{red}{100}\\
\hline
Trudy&14&24&10&30\\
\hline
\end{tabular}\\
\\
\textbf{This can then be processed as normal}
\newpage
\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Start};
\node (pro1) [process, below of=start] {Find the reduced cost matrix};
\node (dec1) [decision, below of=pro1, yshift=-2cm] {Find the minimum number of straight lines to cover the zeroes};
\node (stop) [startstop, right of=dec1,xshift=5cm] {Stop};
\node (pro2) [process, below of=dec1,yshift=-2cm] {Draw in the lines and look for the smallest uncovered element, call it $e$};
\node (pro3) [process, below of=pro2] {Add $e$ to all covered elements, add it twice if covered twice};
\node (pro4) [process, below of=pro3] {Subtract $e$ from \textbf{all} elements of the matrix (even those that just had $e$ added)};
\draw [arrow] (start) -- (pro1);
\draw [arrow] (pro1) -- (dec1);
\draw [arrow] (dec1) -- node[anchor=east] {Lines$<$n} (pro2);
\draw [arrow] (dec1) -- node[anchor=south] {Lines$\geqslant$n} (stop);
\draw [arrow] (pro2) -- (pro3);
\draw [arrow] (pro3) -- (pro4);
\draw [arrow] (pro4.west) -- (-8,-14) -- (-8,-3.6) -- (dec1.north);

\end{tikzpicture}
\end{document}

### 2017-12-11 Maths Notes/D2/Transportation problems/Transportation problems.tex
Notes Update

@@
 \usepackage{enumerate}
+\usetikzlibrary{calc,shapes.geometric, arrows}
+\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
+\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
+\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
+\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30,text width=2cm]
+\tikzstyle{arrow} = [thick,->,>=stealth]
 
@@
 \textbf{To find an optimal solution, new shadow costs and improvement indices would need to be found}
+\newpage
+\section{Finding an initial solution to the transportation problem}
+\begin{tikzpicture}[node distance=2cm]
+\node (start) [startstop] {Start};
+\node (pro1) [process, below of=start] {Allocate NW Corner};
+\node (dec1) [decision, below of=pro1, yshift=-2cm] {Is all stock exhausted and all demand met?};
+\node (dec2) [decision, below of=dec1, yshift=-3cm] {Stock Empty?};
+
+\node (pro2) [process, below of=dec2,yshift=-1cm] {Down 1};
+\node (pro3) [process, right of=dec2,xshift=3cm] {Right 1 and Allocate};
+
+\node (dec3) [decision, below of=pro2, yshift=-1cm] {Demand Satistied?};
+\node (pro4) [process, right of=dec3,xshift=3cm] {Allocate};
+\node (pro5) [process, right of=dec3,xshift=3cm,yshift=-4cm] {Right 1 and Allocate};
+\node (stop) [startstop,left of=dec1,xshift=-3cm] {Stop};
+
+\draw [arrow] (start) -- (pro1);
+\draw [arrow] (pro1) -- (dec1);
+\draw [arrow] (pro2) -- (dec3);
+\draw [arrow] (dec1) -- node[anchor=south] {Yes} (stop);
+\draw [arrow] (dec1) -- node[anchor=east] {No} (dec2);
+\draw [arrow] (dec2) -- node[anchor=east] {Yes} (pro2);
+\draw [arrow] (dec2) -- node[anchor=south] {No} (pro3);
+
+\draw [arrow] (dec3) |- node[anchor=east,yshift=2cm] {Yes} (pro5);
+\draw [arrow] (dec3) -- node[anchor=south] {No} (pro4);
+\draw [arrow] (pro5.east) --  (9,-21)-- (9,-3.79)-- (dec1.north);
+\draw [arrow] (pro3.east) -- (9,-11);
+\draw [arrow] (pro4.east) -- (9,-17);
+\end{tikzpicture}
+\newpage
+\section{Finding an improvement to the initial solution}
 

### 2017-12-12 Maths Notes/D2/Travelling Salesman Problem/Travelling Salesman Problem.tex
D2 TSP Notes Update

@@
 \usepackage{tikz}
-\usetikzlibrary{calc}
+\usetikzlibrary{calc,shapes.geometric, arrows}
 \titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
@@
 }%
+
+\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
+\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
+\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
+\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30,text width=2cm]
+\tikzstyle{arrow} = [thick,->,>=stealth]
 
@@
 This algorithm gives the initial upper bound
+\section{Using a minimum spanning tree to find a lower bound}
+Method:
+\begin{enumerate}
+\item Remove a vertex from the matrix
+\item Find the minimum spanning tree for the remaining vertices (Residual Minimum Spanning Tree)
+\item Find the two shortest connectors to the removed vertex and add them to the RMST
+\item The greatest total from removing a vertex is the lower bound
+\end{enumerate}
+Notes
+\begin{itemize}
+\item The lower bound should be as large as possible to make the interval between upper and lower bounds smallest
+\item You have an optimal solution if
+\begin{itemize}
+\item The lower bound gives a tour, or
+\item The lower bound has the same value as the upper bound
+\end{itemize}
+\end{itemize}
+\section{Nearest Neighbour algorithm}
+\begin{enumerate}
+\item Select the vertex chosen to start at
+\item Go to the nearest unused vertex
+\item Repeat step 2 until all vertices are included
+\item Return to the start vertex directly from the end vertex
+\item Repeat for other vertices and select the tour with the smallest length as the upper bound
+\end{enumerate}
+\newpage
+\section{Flowchart of Nearest Neighbour}
+\begin{tikzpicture}[node distance=2cm]
+\node (start) [startstop] {Start};
+\node (pro1) [process, below of=start] {Select the vertex chosen to start at};
+\node (pro2) [process, below of=pro1] {Go to the nearest unused vertex};
+\node (dec1) [decision, below of=pro2, yshift=-1cm] {Visited all vertices?};
+\node (pro3) [process, below of=dec1,yshift=-1cm] {Return to the start vertex directly from the end vertex};
+\node (stop) [startstop,below of=pro3] {Stop};
+
+\draw [arrow] (start) -- (pro1);
+\draw [arrow] (pro1) -- (pro2);
+\draw [arrow] (pro2) -- (dec1);
+\draw [arrow] (pro3) -- (stop);
+\draw [arrow] (dec1) -- node[anchor=east] {Yes} (pro3);
+\draw [arrow] (dec1.east)  -- (4,-7) |- (pro2.east) node[anchor=east,yshift=-3.2cm] {No};
+
+\end{tikzpicture}
+
 \end{document}

### 2017-12-18 Physics Notes/Electromagnetic Induction/Electromagnetic Induction.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Fields}
\rfoot{Page \thepage}

\tikzstyle{arrow} = [thick,->,>=stealth]

\begin{document}
\begin{center}
\underline{\huge Electromagnetic Induction}
\end{center}
\section{Generating Electricity}
$ $\\
$ $\\

\begin{tikzpicture}
\tikzset{myptr/.style={decoration={markings,mark=at position 1 with %
    {\arrow[scale=3,>=stealth,blue]{>}}},postaction={decorate}}}
\pgfmathsetmacro{\cubex}{2}
\pgfmathsetmacro{\cubey}{1}
\pgfmathsetmacro{\cubez}{1}
\draw[black,fill=gray] (0,0,0) -- ++(-\cubex,0,0) -- ++(0,-\cubey,0) -- ++(\cubex,0,0) -- cycle;
\draw[black,fill=gray] (0,0,0) -- ++(0,0,-\cubez) -- ++(0,-\cubey,0) -- ++(0,0,\cubez) -- cycle;
\draw[black,fill=gray] (0,0,0) -- ++(-\cubex,0,0) -- ++(0,0,-\cubez) -- ++(\cubex,0,0) -- cycle;

\draw[black,fill=gray] (4,0,0) -- ++(-\cubex,0,0) -- ++(0,-\cubey,0) -- ++(\cubex,0,0) -- cycle;
\draw[black,fill=gray] (4,0,0) -- ++(0,0,-\cubez) -- ++(0,-\cubey,0) -- ++(0,0,\cubez) -- cycle;
\draw[black,fill=gray] (4,0,0) -- ++(-\cubex,0,0) -- ++(0,0,-\cubez) -- ++(\cubex,0,0) -- cycle;

\coordinate  (d5) at (1.5,0,5){};
\coordinate  (d6) at (1.5,0,-5){};

\draw []       (d5)--(d6);
\node[text width=4cm,red] at (1,-0.5) {\Large{N}};
\node[text width=4cm,red] at (4.9,-0.5) {\Large{S}};
\draw [arrow] (1.5,0,3) -- node[anchor=west,below,yshift=-10] {Motion of wire} (1.5,-1,3);
\draw [myptr] (1.5,0,-3) -- (1.5,0,-2.9);
\draw [myptr] (1.5,0,0) -- (1.5,0,0.1);
\draw [myptr] (1.5,0,2) -- (1.5,0,2.1);
\node[text width=4cm,blue] at (6,1.5) {\large{Direction of Current}};
\draw [black] plot [smooth] coordinates { (1.5,0,5) (0,0,4) (-2,0,2) (-3,0,0)};
\draw [black] plot [smooth] coordinates { (1.5,0,-5) (0,0,-4) (-2,0,-3) (-3,0,0)};
\node[cylinder, draw, shape aspect=.5,shape border rotate=90,fill=cyan] at (-3,0) {Meter};
\end{tikzpicture}
\end{document}

### 2018-01-03 Physics Notes/Electromagnetic Induction/Electromagnetic Induction.tex
Notes Update

@@
 \usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
 \usepackage{amsmath}
@@
 \usepackage{fancyhdr}
-\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes}
-
+\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing}
 \pgfplotsset{width=10cm,compat=1.9}
@@
 \node[cylinder, draw, shape aspect=.5,shape border rotate=90,fill=cyan] at (-3,0) {Meter};
+\end{tikzpicture}\\
+When a conductor is moved through a magnetic field an emf is \textbf{induced} across the ends of the conductor\\
+\\
+The emf will be greater when:
+\begin{itemize}
+\item The conductor is moved more quickly
+\item The magnetic field is stronger
+\item There is a longer length of conductor in the magnetic field
+\end{itemize}
+No emf will be induced if the conductor is parallel to the field lines\\
+\\
+A current will flow if the conductor is part of a complete circuit
+\subsection{Explaining electromagnetic induction}
+\begin{tikzpicture}
+\filldraw[color=black,fill=none,very thick](-1,0) circle (1.5);
+\draw[ultra thick, -,red] (-1,-1.5) arc (0:75:2);
+\draw[ultra thick, red] (-4,0.4) -- (-2.4,0.4);
+\draw[ultra thick, black] (0.06,1.06) -- (-2.06,-1.06);
+\draw[ultra thick, black] (-2.06,1.06) -- (0.06,-1.06);
+
+\end{tikzpicture}\\
+\\
+\begin{tikzpicture}
+\tikzstyle{arrow} = [thick,->,>=stealth]
+\filldraw[color=black,fill=none,very thick](-1,0) circle (1.5);
+\draw[ultra thick, -,red] (-1,-1.5) arc (0:75:2);
+\draw[ultra thick, red] (-4,0.4) -- (-2.4,0.4);
+\draw[ultra thick, black] (0.06,1.06) -- (-2.06,-1.06);
+\draw[ultra thick, black] (-2.06,1.06) -- (0.06,-1.06);
+
+\draw[ultra thick, blue] (-2.06,3) -- (-2.06,-3);
+\draw[ultra thick, blue] (-1.5,3) -- (-1.5,-3);
+
+\draw [arrow] (-1.5,-2) -- node[anchor=north] {Movement} (1,-2);
 \end{tikzpicture}
+\newpage
+\section{The laws of electromagnetic induction}
+\includegraphics[width=5cm]{magnetic_induction.jpg}\\
+North Pole - Anticlockwise current flow\\
+South Pole - Clockwise current flow\\
+\section{Lenz's law}
+The direction of the induced emf is always such as to oppose the change that is causing it.\\
+\includegraphics[width=5cm]{lenz.jpg}\\
+As the magnet is pushed into the coil it induces an emf in the coil, this produces a magnetic field which opposes the potion. When removing the magnet the polarity will be inversed.\\
+\section{Faraday's law}
+\begin{tikzpicture}
+\tikzstyle{arrow} = [thick,->,>=stealth]
+\filldraw[color=black,fill=none,very thick](-1,0) circle (1.5);
+
+\draw[ultra thick, black] (0.06,1.06) -- (-2.06,-1.06);
+\draw[ultra thick, black] (-2.06,1.06) -- (0.06,-1.06);
+
+\draw[ultra thick, blue] (-2.06,1.5) -- (-2.06,-1.5);
+\draw[ultra thick, blue] (-1.5,1.5) -- (-1.5,-1.5);
+
+\draw [arrow] (-1.5,-2) -- node[anchor=north] {\footnotesize{Movement of wire}} (1,-2);
+\draw[thick, <->] (-3,-1.5) -- (-3,1.5) node[anchor=east,midway] {l};
+
+\draw[thick, <->] (-2.5,2) -- (0.5,2) node[anchor=south,midway] {$\Delta S$};
+\end{tikzpicture}\\
+\\
+\begin{tabular}{r l}
+Work done&$=F\times S$\\
+&$=BIl\times\Delta S$
+\end{tabular}\\
+\\
+Charge transfer, $Q=I\times\Delta t$\\
+\\
+$\epsilon=\dfrac{\text{Work done}}{\text{Charge}}=\dfrac{BIl\times\Delta S}{I\times\Delta t}=\dfrac{BA}{\Delta t}$\\
+\\
+\textcolor{red}{B=Magnetic flux density=$\dfrac{\phi}{A}$}\\
+\textcolor{red}{$\phi$ = Magnetic flux}
+$$\epsilon=\dfrac{\phi}{\Delta t}$$
+\newpage
+Faraday's law of electromagnetic induction is equal to the rate of change of flux(linkage) through the circuit.\\
+\\
+Flux linkage refers to coils, $N\phi$ replaces $\phi$ where N is the number of coils.
+$$\epsilon=-N\dfrac{\Delta\phi}{\Delta t}$$
+This equation may need to be expanded depending on the example
+\subsection{Example}
+\begin{tikzpicture}[cross/.style={path picture={ 
+  \draw[black]
+(path picture bounding box.south east) -- (path picture bounding box.north west) (path picture bounding box.south west) -- (path picture bounding box.north east);
+}},decoration={coil}]
+
+ \node [draw,circle,cross,minimum width=2 mm] at (2,0){}; 
+ \node [draw,circle,cross,minimum width=2 mm] at (2,-0.5){};
+ \node [draw,circle,cross,minimum width=2 mm] at (2,-1){};
+ \node [draw,circle,cross,minimum width=2 mm] at (2,-1.5){};
+ \node [draw,circle,cross,minimum width=2 mm] at (2,-2){};
+
+  \node [draw,circle,cross,minimum width=2 mm] at (3,0){}; 
+ \node [draw,circle,cross,minimum width=2 mm] at (3,-0.5){};
+ \node [draw,circle,cross,minimum width=2 mm] at (3,-1){};
+ \node [draw,circle,cross,minimum width=2 mm] at (3,-1.5){};
+ \node [draw,circle,cross,minimum width=2 mm] at (3,-2){};
+
+   \node [draw,circle,cross,minimum width=2 mm] at (4,0){}; 
+ \node [draw,circle,cross,minimum width=2 mm] at (4,-0.5){};
+ \node [draw,circle,cross,minimum width=2 mm] at (4,-1){};
+ \node [draw,circle,cross,minimum width=2 mm] at (4,-1.5){};
+ \node [draw,circle,cross,minimum width=2 mm] at (4,-2){};
+
+ \draw[decorate, decoration={aspect=0.3, segment length=2mm, amplitude=3mm}] (0,0) --(0,-2);
+
+ \draw[thick, ->] (0.5,-1) -- (1.5,-1) ;
+\end{tikzpicture}\\
+\\
+\textcolor{red}{$\epsilon=-N\dfrac{B\Delta A}{\Delta t}$}
+
 \end{document}

### 2018-01-17 Physics Notes/AS Level/All/All.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{circuitikz}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{relsize}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\usepackage{relsize}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{AS Level Physics}
\rfoot{Page \thepage}
\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\begin{document}
\begin{center}
\underline{\huge AS Physics}
\end{center}
\section{Matter and radiation}
\subsection{Inside the atom}
\subsubsection{Specific charge}
$$\text{Specific Charge}=\dfrac{\text{Charge}}{\text{Mass}}$$
\subsection{Stable and unstable nuclei}
\subsubsection{The strong force}
0fm - 0.5fm - Repulsion\\
0.5fm - 3fm - Attraction\\
3fm+ - No force\\
\subsubsection{Radioactive decay}
\paragraph{Alpha Radiation}
$$\mathsmaller{^A_Z}X\rightarrow\mathsmaller{^{A-4}_{Z-2}}Y+\mathsmaller{^4_2}\alpha$$
\paragraph{Beta radiation}
$$\mathsmaller{^A_Z}X\rightarrow\mathsmaller{^{A}_{Z+1}}Y+\mathsmaller{^0_{-1}}\beta+\overline{\nu}$$
\paragraph{Gamma Radiation}
This is emitted by an unstable nucleus. It has no mass and no charge. It is caused by a nucleus having too much energy, following an alpha or beta emissions.
\subsection{Photons}
\subsubsection{Electromagnetic waves}
$$\text{The power of a laser beam}=nhf$$
n is the number of photons that pass a fixed point in a second
\subsection{Particles and antiparticles}
\subsubsection{Antimatter}
\paragraph{$\mathbf{\beta^+}$ decay}
$$\mathsmaller{^A_Z}X\rightarrow\mathsmaller{^{A}_{Z-1}}Y+\mathsmaller{^0_{+1}}\beta+\nu$$
\paragraph{Theory of antiparticles}
For every type of particle, there is a corresponding antiparticle that:
\begin{itemize}
\item Annihilates the particle and itself if they meet, converting their total mass into photons
\item Has exactly the same rest mass as the particle
\item Has exactly opposite charge to the particle if the particle has a charge
\end{itemize}
\textbf{Pair production} - A photon with sufficient energy can change into a particle-antiparticle pair\\
\\
To find the energy of an electron, use $E=mc^2$
\subsection{How particles interact}
\subsubsection{The weak nuclear force}
This affects both leptons and quarks\\
\paragraph{Exchange particle}
The W bosons:
\begin{itemize}
\item Have a non-zero rest pass
\item Have a very short range (0.001fm)
\item Are positively charged($W+$) or negatively charged ($W^-$)
\end{itemize}
Strangeness is not conserved with the weak nuclear force
\subsection{Electron capture}
$$p+e^-\rightarrow n+\nu$$
\section{Quarks and leptons}
\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
Particle&Charge&Antiparticle&Interaction\\
\hline
Proton&+1&Antiproton $\overline{p}$&Strong, weak, electromagnetic\\
\hline
Neutron&0&Antineutron $\overline{n}$&Strong, weak\\
\hline
Electron $e^-$&-1&Positron $e^+$&Weak, electromagnetic\\
\hline
Neutrino $\nu$&0&Antineutrino $\overline{v}$&Weak\\
\hline
Muon $\mu^-$&-1&Antimuon $\mu^+$&Weak, electromagnetic\\
\hline
$\pi$ meson $\pi^+,\pi^0,\pi^-$&+1,0,-1&Inverse symbol, $\pi^0$ is own antiparticle&Strong, electromagnetic (charged only)\\
\hline
K meson $K^+,K^0,K^-$&+1,0,-1&&Strong, electromagnetic (charged)\\
\hline
\end{tabularx}
\subsection{Leptons at work}
\subsubsection{Lepton rules}
\paragraph{Rule 1}
In an interaction between a \textbf{lepton} and a \textbf{hadron}, a neutrino or antineutrino can change into or from a corresponding charged lepton.
$$\nu_e+n\rightarrow p+e^-$$
\paragraph{Rule 2}
In \textbf{muon} decay, the muon changes into a muon neutrino. In addition an electron and electron neutrino are created to conserve charge.
$$\mu^-\rightarrow E^-+\overline{\nu_e}+\nu_\mu$$
\section{Quantum phenomena}
\subsection{Photoelectricity}
\subsubsection{The discovery of photoelectricity}
Observations made about photoelectricity:
\begin{enumerate}
\item Photoelectric emission of electron does take place if the frequency is below the \textbf{threshold} frequency
\item The number of electrons emitted per second is proportional to the intensity of the incident radiation
\item Photoelectric emission occurs instantaneously 
\end{enumerate}
\subsubsection{Formulae}
$hf=\phi+E_{Kmax}$\\
$\phi$ = $hf_0$ = Work Function - The minimum energy needed for an electron to escape from the metal surface\\
\subsection{Collisions of electrons with atoms}
\subsubsection{Ionisation}
\textbf{Ion} - An atom where the number of protons is not the same as the number of electrons\\
\textbf{Ionisation energy of a gas atom = eV}
\subsubsection{Excitation}
Excitation is where gas atoms absorb energy from electron collisions without ionising. This causes electrons to increase in the energy levels.
\subsection{Energy levels}
\subsubsection{Electrons in atoms}
\textbf{Ground state} - The lowest energy state of an atom\\
\textbf{Excited state} - An energy state above the ground state
\subsubsection{De-excitation}
Excited atoms are unstable and so will tend towards their ground state. When an electron moves down an energy level a photon is emitted with energy equivalent to the loss of energy by the electron.
\subsubsection{Excitation using photons}
An electron can absorb a photon and move to an outer shell where there is a vacancy. However the energy of the photon must be exactly the same as the gain of energy in the electron. If it is not then the photon will not be absorbed by the electron.
\subsection{Energy levels and spectra}
When the light from a filament lamp is split into a spectrum many discrete lines will be seen. These correspond to each of the energy levels of the atom
\subsection{Wave particle duality}
\textbf{Wave nature} - Diffraction\\
\textbf{Particle nature} - Photoelectric effect\\
\\
The wavelength of a matter particle is calculated by:
$$\lambda=\dfrac{h}{p}=\dfrac{h}{mv}$$\\
\section{Electric current}
\subsection{Potential difference and charge}
\textbf{Potential difference} - Work done per unit charge\\
\textbf{emf} - The electrical energy produced per unit charge passing through the source
\subsection{Resistance}
\subsubsection{Superconductivity}
A superconductor has \textbf{zero} resistivity at and below a \textbf{critical temperature}\\
Superconductors are used to make high-power electromagnets
\section{Direct current circuits}
\subsection{Circuit rules}
\subsubsection{Current}
\textbf{Series}: Current in = Current out. Current through multiple components is the same as through one\\
\textbf{Parallel}: Current into a junction = current out of a junction
\subsubsection{Voltage}
\textbf{Series}: Total voltage = the sum of voltages in the circuit\\
\textbf{Parallel}: Voltage in parallel components is equal
\subsection{Electromotive force and internal resistance}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
Switch Open&Switch Closed\\
\hline
Voltmeter reads $\epsilon$&Voltmeter reads $\epsilon-IR$\\
\hline
\end{tabularx}
\begin{tikzpicture}
\begin{axis}[axis lines=middle,scale=0.5,    ylabel = Vr,xlabel=Current,ylabel style={rotate=90,anchor=south},xlabel style={anchor=south},xmin=0,xmax=7,ymin=0,ymax=7,xtick={5},xticklabels={Short Circuit Current},ytick={5},yticklabels={$\epsilon$}
]
\addplot[color=black,domain=0:5]{-x+5};
\end{axis}
\end{tikzpicture}
\subsection{The potential divider}
$$V_{Out}=V_{In}\times\dfrac{R_2}{R_1+R_2}$$\\
\\
Sensors reduce their resistance if the condition of the environment increases.
\section{Forces in equilibrium}
\subsection{Moments}
\subsubsection{Couples}
\textbf{Couple} - A pair of equal and opposite forces acting on a body\\
$$\text{Moment/Torque of a couple}=\text{Force}\times\text{Perpendicular distance between the lines of action of the forces}$$
\subsection{Stability}
\textbf{Stable} - Returns of equilibrium after displacement\\
\textbf{Unstable} - Does not return to equilibrium after displacement.
\subsubsection{Tilting and toppling}
An object will fall if the line of action of the centre of mass of the object lies outside the base.
\end{document}

### 2018-01-18 Physics Notes/AS Level/All/All.tex
Notes update

@@
 An object will fall if the line of action of the centre of mass of the object lies outside the base.
+\section{On the move}
+\subsection{Speed and velocity}
+\subsubsection{Speed}
+\textbf{Displacement} - Distance in a given direction\\
+\textbf{Speed} - Change of distance per unit time\\
+\textbf{Velocity}- Change of displacement per unit time\\
+\section{Motion and force}
+\subsection{Newton's laws of motion}
+\textbf{First law} - Objects either stay at rest or remain in uniform motion unless acted on by a force.\\
+\textbf{Second law} - F=ma\\
+\textbf{Third law} - Every action has an equal and opposite reaction\\
+\\
+\textbf{Inertia} - The resistance of an object to change its motion.
+\subsubsection{Terminal speed}
+The \textbf{drag force} depends on:Inertia
+\begin{itemize}
+\item The shape of the object
+\item Its speed
+\item The viscosity of the fluid the object is travelling through
+\end{itemize}
+\section{Waves}
+\subsection{Waves and vibrations}
+\subsubsection{Definitions}
+\textbf{Displacement} - The distance and direction of a particle from its equilibrium position\\
+\textbf{Amplitude} - The maximum displacement of a particle\\
+\textbf{Wavelength} - The least distance between two adjacent vibrating particles with the same displacement and velocity at the same time\\
+\textbf{One complete cycle} - From maximum displacement to the next maximum displacement\\
+\textbf{Period} - The time for one complete wave to pass a fixed point\\
+\textbf{Frequency} - The number of cycles of vibration of a particle per second.
+\section{Optics}
+\subsection{The diffraction grating}
+\subsubsection{Types of spectra}
+\paragraph{Continuous spectra}
+The spectrum of light from a filament lamp is continuous. The hotter the light source, the shorter the wavelength of the brightest part of the spectrum.
+\paragraph{Line emission spectra}
+The light from a discharge tube emits light at specific wavelengths, meaning the spectra is of discrete lines. The wavelengths of the light are characteristic of the element that produces the light.
+\paragraph{Line absorption spectra}
+This is a continuous spectrum with narrow dark lines at certain wavelengths.
+This could be produced from the light from a filament lamp passing through a glowing gas.
+The elements in the gas absorb some of the photons, those that have exactly the correct energy to excite an electron.
 \end{document}

### 2018-01-26 Maths Notes/FP2/First Order Differential Equations/First Order Differential Equations.tex
First order differential equations notes

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - FP2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge First Order Differential Equations}
\end{center}
\section{Families of curves}
General solutions with a constant of integration C will give rise to a family of curves.\\
\\
If given boundary conditions we can find specific solutions.
\subsection{Example}
Find the solution to:\\
\\
$\dfrac{dy}{dx}=2$\\
\\
$y=2x+c$\\
\\

\begin{tikzpicture}
\begin{axis}[axis lines=middle,scale=0.5]
\addplot[color=red]{2*x};
\addplot[color=red]{2*x+2};
\addplot[color=red]{2*x+4};
\addplot[color=red]{2*x-2};
\addplot[color=red]{2*x-4};
\end{axis}
\end{tikzpicture}
\section{Introduction to first order differential equations}
Implicitly differentiate:\\
$x^3y \quad \textrm{wrt}x$\\
$3x^2y+x^3\dfrac{dy}{dx}$\\
\\
We can use this method in reverse to solve first order DEs
\subsection{Example 1}
$$x^3\dfrac{dy}{dx}+3x^2y=\sin(x)$$
\textcolor{red}{We look for standard patterns in the LHS and look to rewrite using the reverse implicit product rule}\\
$$\frac{d}{dx}(x^3y)=\sin(x)$$
$$x^3y=-\cos(x)+c$$
$$y=\frac{-\cos(x)+c}{x^3}$$
\textcolor{red}{If given an (x,y) point a particular solution can be found}\\
\\
In general:
$$\mathlarger{f(x)\frac{dy}{dx}+f'(x)y=\frac{d}{dx}(f(x)y)}$$
\newpage
\section{Solving first order DE using an integrating factor}
Solving $\dfrac{dy}{dx}+P(x)y=Q(x)$\\
\\
IF(Integrating factor) is found by finding $\mathlarger{e^{\int p(x) \ dx}}$ And multiplying the DE by the IF.\\
\\
This will result in the DE being in the form:
$$f(x)\frac{dy}{dx}+f'(x)y$$
\section{First order DE with given substitution}
\textbf{Type 1} reduces to separation of variables\\
\\
\textbf{Type 2} reduces to $\dfrac{d}{dx}(f(x)y)$ form\\
\subsection{Type 1}
\textit{Show that the substitution $z=\dfrac{y}{x}$ transforms}
$$(1)\quad \frac{dy}{dx}=\frac{x^2+3y^2}{2xy}$$
\begin{center}
to
\end{center}
$$(2)\quad x\frac{dz}{dx}=\frac{1+z^2}{2z}$$
\textcolor{red}{We need to find $\frac{dz}{dx}$ and replace y in (1)}\\
$$y=xz \quad \quad \frac{dy}{dx}=z+x\frac{dz}{dx}$$
$$x\frac{dz}{dx}=\frac{x^2+3(xz)^2}{2x(xz)}-z$$
$$x\frac{dz}{dx}=\frac{1+3z^2}{2z}-z$$
$$x\frac{dz}{dx}=\frac{1+z^2}{2z}$$
\textit{Solve (2) to find z as a function of x}\\
\textcolor{red}{Check if SoV is possible}\\
$$\mathlarger{\int}\frac{2z}{1+z^2} \ dz=\mathlarger{\int}\frac{1}{x} \ dx$$
$$\ln|1+z^2|=\ln|x|+c$$
$$1+z^2=A|x|$$
\textit{Substitute to obtain y in terms of x}\\
$$\Bigg(\frac{y}{x}\Bigg)=kx-1$$
$$\frac{y^2}{x^2}=kx-1$$
$$y^2=kx^3-x^2$$

\end{document}

### 2018-01-26 Physics Notes/Turning Points/Electrons/Electrons.tex
First order differential equations notes

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{blindtext}
\usepackage{textcomp}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Turning Points}
\begin{document}
\begin{center}
\underline{\huge Electrons}
\end{center}
\section{Discharge tube}
\begin{itemize}
\item As p.d. increased from 0V, initially no glow
\item p.d. increased further - suddenly glows can be seen and p.d. drops as the gas now conducts
\item Increasing p.d. further causes gas to glow brighter
\end{itemize}
When several kV is applied a narrow band "glow" causes gas to glow brighter
\subsection{Explanation of how it works}
\begin{itemize}
\item The high p.d. is sufficient to ionise the gas
\item The positive ions accelerate towards the cathode
\item The ions will hit the metal cathode with sufficient energy to release free electrons from the surface
\item The free electrons from the metal (low energy) can recombine with the gas ions-emitting photons and will be a continuous spectrum
\item The free electrons accelerate towards the anode. These free electrons will \textbf{inelastically} collide with gas atoms (and ions) causing bound electrons to be excited, then de-excited. This will produce a discrete spectrum which is seen in the positive column.
\section{Thermionic emission}
When a metal is heated the free electrons can gain enough energy to be released from the surface. This is called thermionic emission (similar to the photoelectric effect).\\
\\
In the presence of an electric field the thermionic electrons can be accelerated to form a narrow beam.\\
\\
When accelerated through a p.d. of \textbf{V} volts the electron gains \textbf{eV} in energy in the form of kinetic energy.
\newpage
\section{Determining the specific charge of an electron}
\subsection{Method 1}
1. Thermionic electrons are accelerated through a p.d. $V_a$ and gain kinetic energy:\\
$$eV_a=\frac{1}{2}mv^2 \quad \frac{e}{m}=\frac{\frac{1}{2}v^2}{v_a}$$
\end{itemize}
2. Electrons pass through an electric field (Field strength, E) and are deflected.\\
\\
3. A magnetic field (field strength, B) is applied at right angles to the E field until electron motion is again horizontal.
$$\textrm{At this point magnetic force=Electric force}$$
$$Bev=eE \quad v=\frac{E}{B}$$
$$\frac{e}{m}=\frac{1}{2v_a}\Bigg(\frac{E}{B}\Bigg)^2$$
\subsection{Method 2}
\includegraphics[width=10cm]{circluar_path.jpg}\\
Thermionic electrons are accelerated through a p.d. $V_a$\\
A magnetic field is applied perpendicular to the motion, causing the electrons to feel a force.\\
\\
$$\textrm{Magnetic force   F=Bev}$$
$$\textrm{This is the centripetal force} \frac{mv^2}{R}$$
$$\frac{e}{m}=\frac{v}{BR} \quad \quad v=\frac{e}{m}BR$$
$$\textrm{From accelerating p.d.}\quad eV_a=\frac{1}{2}mv^2$$
$$\frac{e}{m}=\frac{2V_a}{(BR)^2}$$
\end{document}

### 2018-01-27 Maths Notes/Core/C3/Graph Flashcards/main.tex
Notes Update

\documentclass[grid,avery5371]{flashcards}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{verse}
\usepackage[version=3]{mhchem}
\usepackage{graphicx}
\settowidth{\versewidth}{It lies behind stars and under hills,}
\addtolength{\versewidth}{2em}
\usepackage{pgfplots}
\geometry{headheight=12pt}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\title{Conversion flashcards}
\author{Sam Robbins}

\cardbackstyle[\large]{plain}
\cardfrontstyle[\large]{headings}
%\cardbackstyle[\large]{headings}

\begin{document}

\begin{flashcard}[]{\Huge{$e^x$}}
\begin{tikzpicture}[scale=0.8]
\begin{axis}[ymin=0,ticks=none]
\addplot[color=red,domain=-2:2]{exp(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);

\end{axis}
\end{tikzpicture}
\end{flashcard}

\begin{flashcard}[]{\Huge{$e^{-x}$}}
\begin{tikzpicture}[scale=0.8]
\begin{axis}[ymin=0,ticks=none]
\addplot[color=red, domain=-2:2]{1/exp(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);

\end{axis}
\end{tikzpicture}
\end{flashcard}

\begin{flashcard}[]{\Huge{\textcolor{red}{$e^x$}\\$e^{2x}$}}
\begin{tikzpicture}[scale=0.8]
\begin{axis}[ymin=0,ticks=none]
\addplot[color=black,domain=-1:1, ]{e^(2*x)};
\addplot[color=red,domain=-2:2, ]{exp(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);

\end{axis}
\end{tikzpicture}
\end{flashcard}

\begin{flashcard}[]{\Huge{\textcolor{red}{$e^{-x}$}\\$10e^{-x}$}}
\begin{tikzpicture}[scale=0.8]
\begin{axis}[ymin=0,ticks=none]
\addplot[color=black,domain=-1:1]{(10*(e^(-x)))};
\addplot[color=red,domain=-1:1]{1/e^(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);

\end{axis}
\end{tikzpicture}
\end{flashcard}

\begin{flashcard}[]{\Huge{\textcolor{red}{$e^{x}$}\\$\ln x$}}
\begin{tikzpicture}[scale=0.8]
\begin{axis}[ticks=none]
\addplot[color=black,domain=0:4, ]{ln(x)};
\addplot[color=red,domain=-2:2, ]{exp(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);

\end{axis}
\end{tikzpicture}

\end{flashcard}

\begin{flashcard}[$y=|x|$]{

\begin{tikzpicture}[scale=0.6]
\begin{axis}[ticks=none]
\addplot[color=red,domain=-4:4, ]{x};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}\\
$y=x$}
\begin{tikzpicture}[scale=0.6]
\begin{axis}[ymin=-4,ticks=none]
\addplot[color=red,domain=-4:4, ]{abs(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}\\
$y=|x|$
\end{flashcard}

\begin{flashcard}[$y=|3x-2|$]{
\begin{tikzpicture}[scale=0.6]
\begin{axis}[ymin=-10,ymax=10,ticks=none]
\addplot[color=red,domain=-2:3, ]{3*x-2};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}\\
$y=3x-2$}
\begin{tikzpicture}[scale=0.6]
\begin{axis}[ymin=-10,ymax=10,ticks=none]
\addplot[color=red,domain=-2:3,samples=300 ]{abs(3*x-2)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}\\
$y=|3x-2|$
\end{flashcard}

\begin{flashcard}[$y=|x^2-3x-10|$]{
\begin{tikzpicture}[scale=0.6]
\begin{axis}[ticks=none]
\addplot[color=red,domain=-4:7,samples=100 ]{x^2-3*x-10};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}\\
$y=x^2-3x-10$}

\begin{tikzpicture}[scale=0.6]
\begin{axis}[ymin=-15,ticks=none]
\addplot[color=red,domain=-4:7,samples=500 ]{abs(x^2-3*x-10)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}\\
$y=|x^2-3x-10|$

\end{flashcard}

\begin{flashcard}[$y=|\sin(x)|$]{
\begin{tikzpicture}[scale=0.6]
\begin{axis}[ymin=-1,ticks=none]
\addplot[color=red,domain=-360:360,samples=500 ]{sin(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}\\
$y=\sin(x)$}
\begin{tikzpicture}[scale=0.6]
\begin{axis}[ymin=-1,ticks=none]
\addplot[color=red,domain=-360:360,samples=500 ]{abs(sin(x))};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}\\
$y=|\sin(x)|$      
\end{flashcard}

\begin{flashcard}[$y=4|x|-|x|^3$]{
\begin{tikzpicture}[scale=0.6]
\begin{axis}[ymin=-4,xmin=-4,xmax=4,ticks=none]
\addplot[color=red,domain=0:4,samples=500 ]{4*x-x^3};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}\\
$y=4x-x^3,x\geqslant0$

}
\begin{tikzpicture}[scale=0.6]
\begin{axis}[ymin=-4,xmax=4,xmin=-4,ticks=none]
\addplot[color=red,domain=-4:4,samples=500 ]{4*abs(x)-(abs(x))^3};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}\\
$y=4|x|-|x|^3$
\end{flashcard}

\begin{flashcard}[]{\Huge{f(x+a)}}
\Huge{Horizontal translation of \textbf{-a}}
\end{flashcard}

\begin{flashcard}[]{\Huge{f(x)+a}}
\Huge{Vertical translation of \textbf{+a}}
\end{flashcard}

\begin{flashcard}[]{\Huge{f(ax)}}
\Huge{Horizontal stretch of scale factor $\mathbf{\frac{1}{a}}$}
\end{flashcard}

\begin{flashcard}[]{\Huge{f(-x)}}
\Huge{Reflection in the\\ \textbf{y axis}}
\end{flashcard}

\begin{flashcard}[]{\Huge{af(x)}}
\Huge{Vertical stretch of scale factor \textbf{a}}
\end{flashcard}

\begin{flashcard}[]{\Huge{-f(x)}}
\Huge{Reflection in the\\ \textbf{x axis}}
\end{flashcard}

\begin{flashcard}[]{\Huge{$\sec\theta$}}
\Huge{$\dfrac{1}{\cos\theta}$}
\end{flashcard}

\begin{flashcard}[]{\Huge{$\csc\theta$}}
\Huge{$\dfrac{1}{\sin\theta}$}
\end{flashcard}

\begin{flashcard}[]{\Huge{$\cot\theta$}}
\Huge{$\dfrac{1}{\tan\theta}=\dfrac{\cos\theta}{\sin\theta}$}
\end{flashcard}

\begin{flashcard}[]{\Huge{Graph of $\sec\theta$}}
\begin{tikzpicture}[scale=0.8]
\begin{axis}[ymax=10,ymin=-10,ticks=none]
\addplot[color=red,domain=-360:360,samples=400,restrict y to domain=-15:15]
{sec(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis 
cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis 
cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
\end{flashcard}

\begin{flashcard}[]{\Huge{Graph of $\csc\theta$}}
\begin{tikzpicture}[scale=0.8]
\begin{axis}[ymax=10,ymin=-10,ticks=none]
\addplot[color=red,domain=-360:360,samples=101,unbounded coords=jump]{cosec(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
\end{flashcard}

\begin{flashcard}[]{\Huge{Graph of $\cot\theta$}}
\begin{tikzpicture}[scale=0.8]
\begin{axis}[ymax=10,ymin=-10,ticks=none]
\addplot[color=red,domain=-360:360,samples=101,unbounded coords=jump]{cot(x)};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);
\end{axis}
\end{tikzpicture}
\end{flashcard}

\begin{flashcard}[]{\Huge{$\sec^2\theta$}}
\Huge{$1+\tan^2\theta$}
\end{flashcard}

\begin{flashcard}[]{\Huge{$\csc^2\theta$}}
\Huge{$1+\cot^2\theta$}
\end{flashcard}

\begin{flashcard}[]{\Huge{Graph of $\arcsin\theta$}}
\begin{tikzpicture}[]
  \begin{axis}[domain = -1:1, samples = 100,ytick style={draw=none},xtick style={draw=none},scale=0.7]
    \addplot[color = red]  {asin(x)/180*pi};
      \end{axis}
\end{tikzpicture}
\end{flashcard}

\begin{flashcard}[]{\Huge{Graph of $\arccos\theta$}}
\begin{tikzpicture}[]
  \begin{axis}[domain = -1:1, samples = 100,ytick style={draw=none},xtick style={draw=none},scale=0.7]
    \addplot[color = red]  {acos(x)/180*pi};
      \end{axis}
\end{tikzpicture}
\end{flashcard}

\begin{flashcard}[]{\Huge{Graph of $\arctan\theta$}}
\begin{tikzpicture}[]
  \begin{axis}[domain = -1:1, samples = 100,ytick style={draw=none},xtick style={draw=none},scale=0.7]
    \addplot[color = red]  {atan(x)/180*pi};
      \end{axis}
\end{tikzpicture}
\end{flashcard}

\begin{flashcard}[]{\Huge{$y=[f(x)]^n$}}
\Huge{$\dfrac{dy}{dx}=n[f(x)]^{n-1}f'(x)$}
\end{flashcard}

\begin{flashcard}[]{\Huge{$y=f[g(x)]$}}
\Huge{$\dfrac{dy}{dx}=f'[g(x)]g'(x)$}
\end{flashcard}

\begin{flashcard}[]{\Huge{$y=uv$}}
\Huge{$\dfrac{dy}{dx}=u\dfrac{dv}{dx}+v\dfrac{du}{dx}$}
\end{flashcard}

\end{document}

### 2018-01-27 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - FP2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Second Order Differential Equations}
\end{center}
In FP2 we are interested in solving 2nd ODEs of the form:
$$a\frac{d^2y}{dx^2}+b\frac{dy}{dx}+cy=f(x) \quad \quad \textrm{a,b,c are constants}$$
\\
We consider three distinct cases:\\
$b^2>4ac\quad$  (Two real solutions)\\
$b^2=4ac\quad$  (One repeated solution)\\
$b^2<4ac\quad$  (Two complex solutions)\\
\\
To solve \nth{2} ODEs of this form we first consider solutions to:
$$a\frac{d^2y}{dx^2}+b\frac{dy}{dx}+cy=0$$
The process of solving a \nth{2} ODE starts with a general solution to a \nth{1} ODE of form:
$$b\frac{dy}{dx}+cy=0$$
$$\mathlarger{\int}\frac{1}{b} \ dy=\mathlarger{\int}\frac{1}{-cy} \ dy$$
$$b\ln(y)=-cx+k$$
$$y=Ae^{-\frac{c}{b}x}$$
$$y=Ae^{mx}$$
\textcolor{red}{This was suggested to be a solution to the \nth{2} ODE as well}\\
\\
We take $y=e^{mx}$ as a starting point for finding general solutions to:
$$(1) \quad a\frac{d^2y}{dx^2}+b\frac{dy}{dx}+cy=0$$\\
If $y=e^{mx}$ is a solution to (1):
$$\frac{dy}{dx}=me^{mx}$$
$$\frac{d^2y}{dx^2}=m^2e^{mx}$$
Then substitute this into (1)
$$am^2e^{mx}+bme^{mx}+ce^{mx}=0$$
Factor out $e^{mx}$
$$e^{mx}(am^2+bm+c)$$
As $e^x$ must be greater than zero $am^2+bm+c=0$\\
This is a solvable quadratic called the \textbf{Auxiliary equation}
\newpage
\section{Two real roots $\mathbf{b^2>4ac}$}
$$(1) \quad a\frac{d^2y}{dx^2}+b\frac{dy}{dx}+cy=0$$\\
The general solution to (1) is in the form:
$$\mathlarger{y=Ae^{\alpha x}+Be^{\beta x}}$$
Where A and B are constants and $\alpha$ and $\beta$ are the roots to the AE
\subsection{Example}
$$(1) \quad 2\frac{d^2y}{dx^2}+5\frac{dy}{dx}+3y=0$$
Find the auxiliary equation
$$2m^2e^{mx}+5me^{mx}+3e^{mx}=0$$
$$e^{mx}(2m^2+5m+3=0$$
$m=-\dfrac{3}{2}\quad m=-1$
$$\textrm{General solution:} y=Ae^{\alpha x}+Be^{\beta x}$$
$$GS=Ae^{-\frac{3}{2}x}+Be^{-x}$$
\section{1 Real, Repeated root $\mathbf{b^2=4ac}$}
$$\textrm{General solution}: \mathlarger{(A+bx)e^{\alpha x}}$$
A and B are constants and $\alpha$ is the root of the AE
\subsection{Example}
\textit{Find the general solution of:}
$$\frac{d^2y}{dx^2}+8\frac{dy}{dx}+16y=0$$
Find the auxiliary equation
$$e^{mx}(m^2+8m+16)=0$$
Find the solution
$$m=-4$$
Substitute into the general solution formula
$$y=(A+Bx)e^{-4x}$$
\section{Imaginary only roots $\mathbf{b^2<4ac}$}
This is when the AI has roots of form $\pm \alpha i$
$$\textrm{General solution:} \quad \mathlarger{y=A\cos(\alpha x)+B\sin(\alpha x)}$$
\newpage
\section{Complex roots $\mathbf{b^2<4ac}$}
This is used when the root is in the form $\beta\pm\alpha i$
$$\textrm{General solution:} \quad \mathlarger{y=e^{\beta x}(A\cos(\alpha x)+B\sin(\alpha x))}$$
\subsection{Example}
\textit{Find the general solution of:}
$$\frac{d^2y}{dx^2}-6\frac{dy}{dx}+34y=0$$
Find the auxiliary equation
$$m^2-6m+34=0$$
Solve to find roots
$$\textrm{Roots}=\frac{6\pm\sqrt{36-4\times1\times34}}{2}=\frac{6\pm10i}{2}=3\pm5i$$
Substitute into general solution formula
$$\mathlarger{y=e^{3x}(A\cos(5x)+B\sin(5x))}$$
\end{document}

### 2018-01-27 Maths Notes/Mechanics/M2/Statics of rigid bodies/Statics of rigid bodies.tex
Notes Update

--- 2017-11-01 Maths Notes/M2/Kinematics/Kinematics.tex
@@
 \begin{center}
-\underline{\huge Kinematics}
+\underline{\huge Statics of rigid bodies}
 \end{center}
-\begin{obeylines}
-\section{Horizontal Projections}
-For a \textbf{constant speed} use \textbf{$Speed=\dfrac{Distance}{Time}$}
-
-For a \textbf{constant acceleration} use \textbf{SUVAT}
-
-For all projections:
+\section{Equilibrium of rigid bodies}
+When calculating moments, only use the component of the force acting perpendicular to the rod.\\
+\\
+A rigid body is in equilibrium if:
 \begin{itemize}
-\item Assume air resistance to be zero
-\item Resolve horizontal and vertical motion
-\item Horizontal - Constant speed
-\item Vertical - Constant acceleration
-
+\item The vector sum of the forces is zero
+\item The sum of the moments around any point is zero
 \end{itemize}
 
-\section{Angular projections}
-The same as horizontal projections but the initial vertical velocity isn't zero.
-Example:
-A particle is projected at a speed of $49ms^{-1}$ at an angle of $45 \degree$ above the horizontal.
-\textit{What is the time taken for the particle to reach its maximum height?}
-\begin{itemize}
-\item u=$49\sin45$
-\item v=0
-\item a=-g
-\item t=?
-\end{itemize}
-$0=49\sin45-gt$
-$t=\dfrac{49\sin45}{g}=\dfrac{5\sqrt{2}}{2}\approx3.54$
-\textit{What is the maximum height reached?}
-\begin{itemize}
-\item u=$49\sin45$
-\item v=0
-\item a=-g
-\item s=?
-\end{itemize}
-$v^2=u^2+2as$
-0=$(49\sin45)^2-2gs$
-$S=\dfrac{(49\sin45)^2}{2g}=61.3$
-\textit{What is the time of the flight?}
-\begin{itemize}
-\item u=$49\sin45$
-\item a=-g
-\item S=0
-\item t=?
-\end{itemize}
-$S=ut+\dfrac{1}{2}at^2$
-$ $
-$0=(49\sin45)t-\dfrac{1}{2}gt^2$
-0=$t(49\sin45-\dfrac{gt}{2}$
-$t=0$
-$49\sin45=\dfrac{gt}{2}$
-$t=\dfrac{2\times49\sin45}{g}=7.07$
-\textit{What is the horizontal range of the particle?}
-\begin{itemize}
-\item t=7.07
-\item Speed=$49\cos45$
-\end{itemize}
-$S=45\cos45\times7.07=245$
-
-\end{obeylines}
 \end{document}

### 2018-01-27 Maths Notes/Mechanics/M2/Work, energy and power/Work, energy and power.tex
Notes Update

--- 2017-11-01 Maths Notes/M2/Kinematics/Kinematics.tex
@@
 \begin{center}
-\underline{\huge Kinematics}
+\underline{\huge Work, energy and power}
 \end{center}
 \begin{obeylines}
-\section{Horizontal Projections}
-For a \textbf{constant speed} use \textbf{$Speed=\dfrac{Distance}{Time}$}
-
-For a \textbf{constant acceleration} use \textbf{SUVAT}
-
-For all projections:
-\begin{itemize}
-\item Assume air resistance to be zero
-\item Resolve horizontal and vertical motion
-\item Horizontal - Constant speed
-\item Vertical - Constant acceleration
-
-\end{itemize}
-
-\section{Angular projections}
-The same as horizontal projections but the initial vertical velocity isn't zero.
-Example:
-A particle is projected at a speed of $49ms^{-1}$ at an angle of $45 \degree$ above the horizontal.
-\textit{What is the time taken for the particle to reach its maximum height?}
-\begin{itemize}
-\item u=$49\sin45$
-\item v=0
-\item a=-g
-\item t=?
-\end{itemize}
-$0=49\sin45-gt$
-$t=\dfrac{49\sin45}{g}=\dfrac{5\sqrt{2}}{2}\approx3.54$
-\textit{What is the maximum height reached?}
-\begin{itemize}
-\item u=$49\sin45$
-\item v=0
-\item a=-g
-\item s=?
-\end{itemize}
-$v^2=u^2+2as$
-0=$(49\sin45)^2-2gs$
-$S=\dfrac{(49\sin45)^2}{2g}=61.3$
-\textit{What is the time of the flight?}
-\begin{itemize}
-\item u=$49\sin45$
-\item a=-g
-\item S=0
-\item t=?
-\end{itemize}
-$S=ut+\dfrac{1}{2}at^2$
+\section{Work}
+$\mathbf{Work(J)=Force(N)\times Distance(m)}$
+For work done against  gravity, use vertical distance.
+For work against friction, use distance in the direction of motion
+\section{Energy}
+$\mathbf{E_K=\frac{1}{2}mv^2}$
 $ $
-$0=(49\sin45)t-\dfrac{1}{2}gt^2$
-0=$t(49\sin45-\dfrac{gt}{2}$
-$t=0$
-$49\sin45=\dfrac{gt}{2}$
-$t=\dfrac{2\times49\sin45}{g}=7.07$
-\textit{What is the horizontal range of the particle?}
-\begin{itemize}
-\item t=7.07
-\item Speed=$49\cos45$
-\end{itemize}
-$S=45\cos45\times7.07=245$
-
+$\mathbf{GPE=E_P=mgh}$
+\section{Conservation of energy}
+A particle's total energy is constant if it is subject only to gravity (i.e. smooth surfaces)
+If there are frictional forces to consider then the loss of energy is the work done by friction.
+\section{Power}
+$\mathbf{Power=Force\times Velocity}$
+Usually given in kW
 \end{obeylines}

### 2018-01-27 Maths Notes/Statistics/S3/Sampling/Sampling.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{enumitem}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty=10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S3}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Sampling}
\end{center}
\begin{tabularx}{\textwidth}{|c|X|X|X|}
\hline
&What it is&Advantages&Disadvantages\\
\hline
Census&A collection of data from an entire population&Gives a completely accurate result&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Time consuming+Expensive
\item Can not be used when testing involves destruction
\item Large volume of data to process
\end{itemize}\\
\hline
Sample survey&A survey of a small sample of the population&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Cheaper
\item Quicker
\item Easier to process
\end{itemize}&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Data may not be accurate
\item Data may not be large enough to represent small sub groups
\end{itemize}\\
\hline
Random Sampling&Each thing has an equal chance of being selected&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Numbers truly random and free from bias
\item Easy to use
\item Each number has a known equal chance of being selected
\end{itemize}&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Not suitable when population is large
\end{itemize}\\
\hline
Lottery sampling&Each element of a population put on a ticket. Tickets drawn randomly from container(without displacement)&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Tickets are drawn at random
\item It is easy to use
\item Each ticket has a known chance of selection
\end{itemize}&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item It is not suitable when the population is large
\item A sampling frame is needed
\end{itemize}\\
\hline
Systematic sampling&Required elements are chosen at regular intervals in an ordered list&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Simple to use
\item Suitable for large samples
\end{itemize}&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Only random if ordered list is truly random
\item Can introduce bias
\end{itemize}\\
\hline
Stratified sampling&Population is divided into groups and a simple random sample is carried out in each group&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item It can give more accurate estimates than simple random sampling where clear strata are present
\item Reflects the population structure
\end{itemize}&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Within the strata, the problems are than same as for any simple random sample
\item If the strata are not clearly defined they may overlap
\end{itemize}\\
\hline
Quota sampling&The population is divided into groups by gender etc. A quota of people in each group is set to try and reflect the group's proportion in the whole population&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Enables fieldwork to be done quickly because a small sample size is taken.
\item Costs kept to a minimum
\item Administering test is easy
\end{itemize}&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Not possible to estimate the sampling errors
\item Interviewers may not be able to judge characteristics easily
\item Non responses are not recorded
\item Can introduce interview bias
\end{itemize}\\
\hline
\end{tabularx}
\newpage
\begin{center}
\underline{\huge Types of data}
\end{center}
\begin{tabularx}{\textwidth}{|c|X|X|}
\hline
Type of data&Advantages&Disadvantages\\
\hline
Primary&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item The collection method is known
\item The accuracy is known
\item The exact data needed is collected
\end{itemize}&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item It is costly in time and effort
\end{itemize}\\
\hline
Secondary&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item They are cheap to obtain
\item A large quantity of data is available
\item Much of the data has been collected for years and can be used to plot trends
\end{itemize}&
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Bias is not always recognised
\item It can be in a form that is difficult to deal with
\end{itemize}\\
\hline

\end{tabularx}

\end{document}

### 2018-01-28 Maths Notes/Statistics/S3/Estimation/Estimation.tex
S3 Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{enumitem}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty=10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S3}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Estimation, confidence intervals and tests}
\end{center}
\section{Estimators}
A statistic that is used to estimate a population parameter is an \textbf{estimator}.\\
A particular individual value is an \textbf{estimate}.\\
\textbf{Bias} is how far the estimator is from the true value\\
\\
If a statistic T is used as an estimator for a population parameter $\theta$ then the bias is:
$$E(T)-\theta$$
If $E(T)=\theta$ then the statistic is unbiased
\subsection{Proving $\mathbf{E(\overline{X})=\mu}$}
\textit{Prove that $\overline{X}$ is an unbiased estimator for $\mu$ when the population is normally distributed}\\
\\
A random sample $X_1,X_2,X_3...X_N$ is taken for a population with $X\sim N(\mu,\sigma^2)$
$$\overline{X}=\frac{1}{n}\sum X$$
$$E(\overline{X})=E\Big(\frac{1}{n}\sum X\Big)$$
$$E(\overline{X})=\frac{1}{n}\big(E(X_1)+E(X_2)+E(X_3)...+E(X_N)\big)$$
$$E(\overline{X})=\frac{1}{n}(\mu+\mu+\mu...+\mu)$$
$$E(\overline{X})=\frac{1}{n}(n\mu)$$
$$E(\overline{X})=\mu$$
\subsection{Variance}
$$Var(\overline{X})=\frac{\sigma^2}{\textrm{Sample size}}$$
\\
We use $S^2$ as an estimator for $\sigma^2$
$$S^2=\frac{1}{n-1}\Big(\Sigma X^2-n\overline{X}^2\Big)$$
\subsection{Uniform Distributions}
\textit{Random variable X is continuously uniform $[0,\alpha]$. A sample $X_1,X_2..X_N$ is taken}\\
\textit{Show that $\overline{X}$ is a biased estimate and state the bias}
$$\overline{X}=\frac{0+\alpha}{2}=\frac{\alpha}{2}$$
$$E(\overline{X})=E(\frac{\alpha}{2})=\frac{1}{2}E(\alpha)=\frac{\alpha}{2}$$
$$\textrm{Bias}=\frac{\alpha}{2}-\alpha=-\frac{\alpha}{2}$$
\newpage
\section{Standard error}
$$\textrm{Standard error}=\frac{\sigma}{\sqrt{n}} \ \textrm{or} \ \frac{s}{\sqrt{n}}$$
\end{document}

### 2018-01-28 Physics Notes/Fields and their consequences/Alternating Current/Alternating Current.tex
Physics notes update

--- 2018-01-17 Physics Notes/AS Level/All/All.tex
@@
 \usepackage{graphicx}
-\usepackage{tabularx}
 \usepackage[english]{babel}
@@
 \renewcommand{\indent}{\hspace*{\tindent}}
-\usepackage{relsize}
+
 \pagestyle{fancy}
@@
 \rhead{Sam Robbins 13SE}
-\lhead{AS Level Physics}
+\lhead{A Level Physics - Alternating Current}
 \rfoot{Page \thepage}
-\setcounter{secnumdepth}{4}
-\titleformat{\paragraph}
-{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
-\titlespacing*{\paragraph}
-{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
 
@@
 \begin{center}
-\underline{\huge AS Physics}
+\underline{\huge Alternating Current}
 \end{center}
-\section{Matter and radiation}
-\subsection{Inside the atom}
-\subsubsection{Specific charge}
-$$\text{Specific Charge}=\dfrac{\text{Charge}}{\text{Mass}}$$
-\subsection{Stable and unstable nuclei}
-\subsubsection{The strong force}
-0fm - 0.5fm - Repulsion\\
-0.5fm - 3fm - Attraction\\
-3fm+ - No force\\
-\subsubsection{Radioactive decay}
-\paragraph{Alpha Radiation}
-$$\mathsmaller{^A_Z}X\rightarrow\mathsmaller{^{A-4}_{Z-2}}Y+\mathsmaller{^4_2}\alpha$$
-\paragraph{Beta radiation}
-$$\mathsmaller{^A_Z}X\rightarrow\mathsmaller{^{A}_{Z+1}}Y+\mathsmaller{^0_{-1}}\beta+\overline{\nu}$$
-\paragraph{Gamma Radiation}
-This is emitted by an unstable nucleus. It has no mass and no charge. It is caused by a nucleus having too much energy, following an alpha or beta emissions.
-\subsection{Photons}
-\subsubsection{Electromagnetic waves}
-$$\text{The power of a laser beam}=nhf$$
-n is the number of photons that pass a fixed point in a second
-\subsection{Particles and antiparticles}
-\subsubsection{Antimatter}
-\paragraph{$\mathbf{\beta^+}$ decay}
-$$\mathsmaller{^A_Z}X\rightarrow\mathsmaller{^{A}_{Z-1}}Y+\mathsmaller{^0_{+1}}\beta+\nu$$
-\paragraph{Theory of antiparticles}
-For every type of particle, there is a corresponding antiparticle that:
-\begin{itemize}
-\item Annihilates the particle and itself if they meet, converting their total mass into photons
-\item Has exactly the same rest mass as the particle
-\item Has exactly opposite charge to the particle if the particle has a charge
-\end{itemize}
-\textbf{Pair production} - A photon with sufficient energy can change into a particle-antiparticle pair\\
+\section{Oscilloscopes}
+$x$-axis - Time base\\
+$y$-axis - Y Sensitivity\\
 \\
-To find the energy of an electron, use $E=mc^2$
-\subsection{How particles interact}
-\subsubsection{The weak nuclear force}
-This affects both leptons and quarks\\
-\paragraph{Exchange particle}
-The W bosons:
-\begin{itemize}
-\item Have a non-zero rest pass
-\item Have a very short range (0.001fm)
-\item Are positively charged($W+$) or negatively charged ($W^-$)
-\end{itemize}
-Strangeness is not conserved with the weak nuclear force
-\subsection{Electron capture}
-$$p+e^-\rightarrow n+\nu$$
-\section{Quarks and leptons}
-\begin{tabularx}{\textwidth}{|X|X|X|X|}
-\hline
-Particle&Charge&Antiparticle&Interaction\\
-\hline
-Proton&+1&Antiproton $\overline{p}$&Strong, weak, electromagnetic\\
-\hline
-Neutron&0&Antineutron $\overline{n}$&Strong, weak\\
-\hline
-Electron $e^-$&-1&Positron $e^+$&Weak, electromagnetic\\
-\hline
-Neutrino $\nu$&0&Antineutrino $\overline{v}$&Weak\\
-\hline
-Muon $\mu^-$&-1&Antimuon $\mu^+$&Weak, electromagnetic\\
-\hline
-$\pi$ meson $\pi^+,\pi^0,\pi^-$&+1,0,-1&Inverse symbol, $\pi^0$ is own antiparticle&Strong, electromagnetic (charged only)\\
-\hline
-K meson $K^+,K^0,K^-$&+1,0,-1&&Strong, electromagnetic (charged)\\
-\hline
-\end{tabularx}
-\subsection{Leptons at work}
-\subsubsection{Lepton rules}
-\paragraph{Rule 1}
-In an interaction between a \textbf{lepton} and a \textbf{hadron}, a neutrino or antineutrino can change into or from a corresponding charged lepton.
-$$\nu_e+n\rightarrow p+e^-$$
-\paragraph{Rule 2}
-In \textbf{muon} decay, the muon changes into a muon neutrino. In addition an electron and electron neutrino are created to conserve charge.
-$$\mu^-\rightarrow E^-+\overline{\nu_e}+\nu_\mu$$
-\section{Quantum phenomena}
-\subsection{Photoelectricity}
-\subsubsection{The discovery of photoelectricity}
-Observations made about photoelectricity:
-\begin{enumerate}
-\item Photoelectric emission of electron does take place if the frequency is below the \textbf{threshold} frequency
-\item The number of electrons emitted per second is proportional to the intensity of the incident radiation
-\item Photoelectric emission occurs instantaneously 
-\end{enumerate}
-\subsubsection{Formulae}
-$hf=\phi+E_{Kmax}$\\
-$\phi$ = $hf_0$ = Work Function - The minimum energy needed for an electron to escape from the metal surface\\
-\subsection{Collisions of electrons with atoms}
-\subsubsection{Ionisation}
-\textbf{Ion} - An atom where the number of protons is not the same as the number of electrons\\
-\textbf{Ionisation energy of a gas atom = eV}
-\subsubsection{Excitation}
-Excitation is where gas atoms absorb energy from electron collisions without ionising. This causes electrons to increase in the energy levels.
-\subsection{Energy levels}
-\subsubsection{Electrons in atoms}
-\textbf{Ground state} - The lowest energy state of an atom\\
-\textbf{Excited state} - An energy state above the ground state
-\subsubsection{De-excitation}
-Excited atoms are unstable and so will tend towards their ground state. When an electron moves down an energy level a photon is emitted with energy equivalent to the loss of energy by the electron.
-\subsubsection{Excitation using photons}
-An electron can absorb a photon and move to an outer shell where there is a vacancy.
-However the energy of the photon must be exactly the same as the gain of energy in the electron.
-If it is not then the photon will not be absorbed by the electron.
-\subsection{Energy levels and spectra}
-When the light from a filament lamp is split into a spectrum many discrete lines will be seen. These correspond to each of the energy levels of the atom
-\subsection{Wave particle duality}
-\textbf{Wave nature} - Diffraction\\
-\textbf{Particle nature} - Photoelectric effect\\
+The advantage of calculating peak to peak voltage over peak voltage is that it reduces the uncertainty in calculating the peak voltage.
+
+\section{Alternating and direct current}
+AC - Alternating Current - Current continuously changes direction\\
+DC - Direct Current - Current flows in one(same) direction\\
 \\
-The wavelength of a matter particle is calculated by:
-$$\lambda=\dfrac{h}{p}=\dfrac{h}{mv}$$\\
-\section{Electric current}
-\subsection{Potential difference and charge}
-\textbf{Potential difference} - Work done per unit charge\\
-\textbf{emf} - The electrical energy produced per unit charge passing through the source
-\subsection{Resistance}
-\subsubsection{Superconductivity}
-A superconductor has \textbf{zero} resistivity at and below a \textbf{critical temperature}\\
-Superconductors are used to make high-power electromagnets
-\section{Direct current circuits}
-\subsection{Circuit rules}
-\subsubsection{Current}
-\textbf{Series}: Current in = Current out. Current through multiple components is the same as through one\\
-\textbf{Parallel}: Current into a junction = current out of a junction
-\subsubsection{Voltage}
-\textbf{Series}: Total voltage = the sum of voltages in the circuit\\
-\textbf{Parallel}: Voltage in parallel components is equal
-\subsection{Electromotive force and internal resistance}
-\begin{tabularx}{\textwidth}{|X|X|}
-\hline
-Switch Open&Switch Closed\\
-\hline
-Voltmeter reads $\epsilon$&Voltmeter reads $\epsilon-IR$\\
-\hline
-\end{tabularx}
-\begin{tikzpicture}
-\begin{axis}[axis lines=middle,scale=0.5,    ylabel = Vr,xlabel=Current,ylabel style={rotate=90,anchor=south},xlabel style={anchor=south},xmin=0,xmax=7,ymin=0,ymax=7,xtick={5},xticklabels={Short Circuit Current},ytick={5},yticklabels={$\epsilon$}
-]
-\addplot[color=black,domain=0:5]{-x+5};
-\end{axis}
-\end{tikzpicture}
-\subsection{The potential divider}
-$$V_{Out}=V_{In}\times\dfrac{R_2}{R_1+R_2}$$\\
+Frequency - The number of waves passing a point per second (Hz)\\
+\section{Root mean square}
+Root mean square values are used to calculate average values for alternating current that are not zero\\
 \\
-Sensors reduce their resistance if the condition of the environment increases.
-\section{Forces in equilibrium}
-\subsection{Moments}
-\subsubsection{Couples}
-\textbf{Couple} - A pair of equal and opposite forces acting on a body\\
-$$\text{Moment/Torque of a couple}=\text{Force}\times\text{Perpendicular distance between the lines of action of the forces}$$
-\subsection{Stability}
-\textbf{Stable} - Returns of equilibrium after displacement\\
-\textbf{Unstable} - Does not return to equilibrium after displacement.
-\subsubsection{Tilting and toppling}
-An object will fall if the line of action of the centre of mass of the object lies outside the base.
+Peak voltage = $V_0 \quad$ Peak current=$I_0$\\
+$$V_{RMS}=\dfrac{V_0}{\sqrt{2}}$$
+$$I_{RMS}=\dfrac{I_0}{\sqrt{2}}$$\\
+\\
+Power, $P=IV$\\
+\\
+$P_{RMS}=I_{RMS}V_{RMS}=\dfrac{I_0}{\sqrt{2}}\times\dfrac{V_0}{\sqrt{2}}=\dfrac{P_0}{2}$
+
 \end{document}

### 2018-01-28 Physics Notes/Fields and their consequences/Capacitors/Capacitors.tex
Physics notes update

--- 2017-11-15 Physics Notes/Capacitors/Capacitors.tex
@@
 This means that using the initial voltage and the voltage at a point in time, the time constant can be calculated.
+\section{Dielectrics}
+Capacitance is increased by placing an insulator between the plates of a capacitor.\\
+\\
+This means that more charge is stored on the capacitor for a given p.d. as:
+\begin{itemize}
+\item The positive side of the dielectric attracts more electrons from the supply
+\item The negative side of the dielectric pushes more electrons towards the supply
+\end{itemize}
+$$ Q\propto C$$
+\section{Relative permittivity}
+This is the ration of charge stored with the dielectric compared to the charge stored with no dielectric.\\
+$$\epsilon_r=\dfrac{Q}{Q_0}$$
+$$\epsilon_r=\dfrac{C}{C_0}$$
+$$\epsilon=\epsilon_0\epsilon_r$$
+\subsection{Capacitor design}
+$C=\dfrac{A\epsilon_0\epsilon_r}{d}$ Therefore $C\propto A \quad C\propto \epsilon_r \quad C\propto \frac{1}{d}$
 \end{document}

### 2018-01-28 Physics Notes/Fields and their consequences/Electromagnetic Induction/Electromagnetic Induction.tex
Physics notes update

--- 2018-01-03 Physics Notes/Electromagnetic Induction/Electromagnetic Induction.tex
@@
 \pgfplotsset{width=10cm,compat=1.9}
-
+\usepackage[super]{nth}
 \titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
@@
 \renewcommand{\indent}{\hspace*{\tindent}}
-
+\hyphenpenalty =10000
 \pagestyle{fancy}
@@
 \rfoot{Page \thepage}
+\usepackage{mathtools}
+\usetikzlibrary{calc,quotes,angles}
 
@@
 
+\pgfkeys{/pgfplots/Axis Style/.style={
+    width=7cm, height=5cm,
+    axis x line=center, 
+    axis y line=middle, 
+    samples=300,
+    ymin=-1, ymax=1,
+    xmin=0, xmax=4,
+    domain=-4*pi:4*pi
+}}
+
+\pgfkeys{/pgfplots/Axis Style 2/.style={
+    width=13.5cm, height=8cm,
+    axis x line=center, 
+    axis y line=middle, 
+    samples=200,
+    ymin=-1, ymax=1,
+    xmin=0, xmax=6.5,
+    domain=-4*pi:2*pi
+}}
+
+\pgfkeys{/pgfplots/Axis Style 3/.style={
+    width=7cm, height=5cm,
+    axis x line=center, 
+    axis y line=middle, 
+    samples=200,
+    ymin=-1.5, ymax=1.5,
+    xmin=0, xmax=14.0,
+    domain=-4*pi:4*pi
+}}
 \begin{document}
@@
 \textcolor{red}{$\epsilon=-N\dfrac{B\Delta A}{\Delta t}$}
+\subsection{Magnets being dropped through a coil}
+\begin{tikzpicture}
+\begin{axis}[
+    Axis Style,
+    y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
+    x label style={anchor=west},
+    ylabel = {Voltage,v},
+    xlabel= {Time, t},
+    ticks=none
+]
+\addplot [mark=none, ultra thick, black,domain=0:3.55] {0.5*sin(deg(0.5*x^2))};
+\end{axis}
+\end{tikzpicture}
+\\
+\nth{1} peak - Wide, low\\
+\nth{2} peak - High, narrow\\
+\\
+This is because the magnet accelerates, meaning the entry takes more time, and as it is travelling at a lower velocity on entry, the rate of flux cutting, and so the voltage is lower than the exit.
+\section{EMF induced in a rotating coil}
+$ $\\
+\begin{tikzpicture}
+
+\draw[black,thick] (0,0)rectangle (1.5,3);
+\draw[black,thick] (5,0)rectangle (6.5,3);
+\draw[thick, ->,red] (1.5,2.8) -- (5,2.8);
+\draw[thick, ->,red] (1.5,2.2) -- (5,2.2);
+\draw[thick, ->,red] (1.5,1.6) -- (5,1.6);
+\draw[thick, ->,red] (1.5,1) -- (5,1);
+\draw[thick, ->,red] (1.5,0.4) -- (5,0.4);
+\draw[blue,thick,fill=blue] (2.5,1.5)rectangle (4,1.7);
+\draw [dashed,thick] (3.25,1.7) -- (3.25,3.5);
+\coordinate (a) at (3.25,1.7);
+\coordinate (b) at (3.25,2);
+\coordinate (c) at (3.55,1.7);
+\draw pic["$\theta$",draw=black,-,angle eccentricity=1.2,angle radius=0.5cm] {angle=c--a--b};
+\end{tikzpicture}
+\\
+$\theta$ = The angle between the field lines and a line perpendicular to the coil\\
+$$\textrm{Flux passing through the coil:} \ \phi=BA\cos\theta$$
+$$\textrm{Flux linkage:} \ N\phi=BAN\cos\theta$$
+\newpage
+As the coil rotates the flux linkage varies\\
+\begin{tikzpicture}[scale=0.6]
+\begin{axis}[
+    Axis Style 2,
+    ticks=none,
+    y label style={at={(axis description cs:-0.01,.5)},rotate=90,anchor=south},
+    ylabel = {Flux Linkage},
+    xlabel= {Time, t}
+]
+\addplot [mark=none, ultra thick, black] {cos(deg(x))};
+\end{axis}
+\draw[blue,thick,fill=blue] (0,-2)rectangle (0.25,-1);
+\draw[blue,thick,fill=blue] (2.5,-1.625)rectangle (3.5,-1.375);
+\draw[blue,thick,fill=blue] (5.6,-2)rectangle (5.85,-1);
+\draw[blue,thick,fill=blue] (8.2,-1.625)rectangle (9.2,-1.375);
+\end{tikzpicture}
+\\
+\\
+\\
+The speed that $\theta$ changes depends on angular velocity, $\omega$
+$$\theta=\omega t$$
+$$N\phi=BAN\cos(\omega t)$$
+\\
+EMF = Negative Rate of change of flux linkage\\
+$$-\frac{d}{dt}BAN\cos(\omega t)=BAN\omega\sin(\omega t)$$
+\begin{tikzpicture}[scale=0.6]
+\begin{axis}[
+    Axis Style 2,
+    ticks=none,
+    y label style={at={(axis description cs:-0.01,.5)},rotate=90,anchor=south},
+    ylabel = {EMF},
+    xlabel= {Time, t}
+]
+\addplot [mark=none, ultra thick, black] {sin(deg(x))};
+\end{axis}
+\draw[blue,thick,fill=blue] (0,-2)rectangle (0.25,-1);
+\draw[blue,thick,fill=blue] (2.5,-1.625)rectangle (3.5,-1.375);
+\draw[blue,thick,fill=blue] (5.6,-2)rectangle (5.85,-1);
+\draw[blue,thick,fill=blue] (8.2,-1.625)rectangle (9.2,-1.375);
+\end{tikzpicture}
+\newpage
+\subsection{Generators}
+These effects can be used to create generators
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+
+\includegraphics[width=7cm] {AC_Generator.jpg}  
+\caption{AC Generator}    
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+
+\begin{tikzpicture}
+\begin{axis}[
+    Axis Style 3,
+    ticks=none,
+    y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
+    ylabel = {EMF},
+    xlabel= {Time, t}
+]
+\addplot [mark=none, ultra thick, black] {sin(deg(x))};
+\end{axis}
+\end{tikzpicture}
+\caption{Graph of EMF from an AC generator}
+
+    \end{minipage}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+
+\includegraphics[width=7cm] {DC_Generator.jpg}  
+\caption{DC Generator}    
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+
+\begin{tikzpicture}
+\begin{axis}[
+    Axis Style 3,
+    ticks=none,
+    y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=north},
+    x label style={anchor=north},
+    ylabel = {EMF},
+    xlabel= {Time, t}
+]
+\addplot [mark=none, ultra thick, black] {abs(sin(deg(x)))};
+\end{axis}
+\end{tikzpicture}
+\caption{Graph of EMF from a DC generator}
+
+    \end{minipage}
+\end{figure}
+\newpage
+\section{Transformers}
+\subsection{Structure}
+\begin{center}
+\includegraphics[width=8cm] {transformer.png}  
+\end{center}
+\subsection{What they are designed to do}
+Increase or decrease an A.C. voltage\\
+Step up - Increase\\
+Step down - Decrease
+\subsection{How they work}
+\begin{itemize}
+\item Two coils, primary and secondary, connected by a soft iron core
+\item The primary coil is connected to a source of alternating p.d., creating an alternating magnetic field in the core
+\item The field passes through the secondary coil, creating an alternating emf in the secondary coil
+\item A transformer is designed so all the magnetic flux produced by the primary coil passes through the secondary coil
+\end{itemize}
+\subsection{How energy losses are reduced}
+\begin{enumerate}
+\item Low resistance windings to reduce power wasted due to the heating effect of the current
+\item A laminated core which consists of layers of iron separated by layers of insulator.
+Induced currents in the core itself, referred to as \textbf{eddy currents}, are reduced in this was so the magnetic flux is as high as possible.
+Also, the heating effect of the induced currents in the core are reduced
+\item A core of \textbf{soft iron} which is easily magnetised and demagnetised. This reduces power wasted through repeated magnetisation and demagnetisation of the core
+\end{enumerate}  
+\subsection{Equations}
+$$\frac{V_P}{V_S}=\frac{N_P}{N_S}=\frac{I_S}{I_P}$$
+$$\textrm{Efficiency}=\frac{I_SV_S}{I_PV_P}\times100$$
+\newpage
+\section{The national grid}
+Transmission of electrical power over long distances is much more efficient at high voltages compared to low voltages.
+\subsection{Transmit 1MW of power through wires of resistance $500\Omega$}
+\subsubsection{At 25kV}
+$$I=\frac{P}{V}=\frac{1\times10^6}{25\times10^3}=40A$$
+$$\textrm{Power lost as heat}=I^2R=40^2\times500=0.8MW=20\%  \ \textrm{Efficient}$$
+\subsubsection{At 400kV}
+$$I=\frac{P}{V}=\frac{1\times10^6}{400\times10^3}=2.5A$$
+$$\textrm{Power lost as heat}=I^2R=2.5^2\times500=0.003MW=99.7\%  \ \textrm{Efficient}$$
 

### 2018-01-28 Physics Notes/Fields and their consequences/Magnetic Fields/Magnetic Fields.tex
Physics notes update

--- 2017-12-07 Physics Notes/Magnetic Fields/Magnetic Fields.tex
@@
 \usepackage{fancyhdr}
+\usetikzlibrary{decorations, decorations.text,}
 
@@
 By measuring the voltage across the probe the magnetic field strength can be measured.
+\section{Charged particles in circular orbits}
+\textbf{Force} will always be perpendicular to the direction of motion\\
+No work is done by the magnetic field on the particles\\
+\\
+Direction changes but not speed\\
+Constant kinetic energy\\
+\\
+Path is circular\\
+Causes a centripetal acceleration\\
+\\
+\\
+$$F=BQv=\dfrac{mv^2}{r}$$
+$$r=\dfrac{mv}{BQ}$$
+\newpage
+\section{Applications}
+\subsection{Cyclotron}
+This is used in hospitals to produce high energy beams for radiotherapy.\\
+\includegraphics[width=10cm]{cyclotron.jpg}\\
+\begin{itemize}
+\item Proton source in centre
+\item Electric field in between C Cores to accelerate protons
+\item Magnetic field causes curved path
+\item r increases as v increases
+\end{itemize}
+\subsection{Mass Spectrometer}
+This is used to analyse the type of atoms present in a sample\\
+\\
+\\
+\begin{tikzpicture}
+\draw[ultra thick, ->,postaction={decorate, decoration={text along path, raise=4pt, text align={align=center}, text={Light ion}, reverse path}}] (6.5,0) arc (0:180:2);
+\draw[ultra thick, ->,postaction={decorate, decoration={text along path, raise=4pt, text align={align=center}, text={Heavy ion}, reverse path}}] (6.5,0) arc (0:180:3);
+\draw[red,thick,fill=red] (0,0)rectangle (3,-0.25) node[below,midway] {Detector};
+\draw[black,fill=black,thick] (5,0)rectangle (6,-0.25);
+\draw[black,fill=black,thick] (7,0)rectangle (8,-0.25);
+\draw[black,ultra thick] (6.5,0) -- (6.5,-2);
+\end{tikzpicture}
+\\
+\begin{itemize}
+\item Magnetic field out of diagram
+\item Atoms in the sample are ionised
+\item Directed in a narrow beam into the magnetic field
+\item Radius of path depends on specific charge
+\end{itemize}
+$r=\dfrac{mv}{BQ}$\\
+$r\propto\dfrac{1}{\frac{q}{m}}$
+\subsubsection{Velocity selector}
+\includegraphics[width=10cm]{velocity_selector.jpg}\\
+Negative ions fall to the bottom surface, causing the top surface to have a positive charge, creating a potential difference.
+For an ion to continue on a straight path the force from the magnetic field up must be equal to the force from the electric field down.\\
+\\
+$F=BQv=EQ$\\
+\\
+$BQv=\dfrac{V}{d}Q$\\
+\\
+$v=\dfrac{V}{Bd}$\\
+\\
+This means that only particles of speed $v$ will travel through the gap
 

### 2018-01-28 Physics Notes/Nuclear Physics/Radioactivity/Radioactivity.tex
Physics notes update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{tabularx}
\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty =10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Nuclear Physics}
\rfoot{Page \thepage}
\usepackage{mathtools}
\usetikzlibrary{calc,quotes,angles}
\tikzstyle{arrow} = [thick,->,>=stealth]
\begin{document}
\begin{center}
\underline{\huge Radioactivity}
\end{center}
\section{Rutherford Scattering}
\subsection{The plum pudding model}
\includegraphics[width=3cm] {plum.jpg}  
\includegraphics[width=3cm] {Plumpudding.png}
\\
The plum pudding model was the initial model of the atom, stating a sphere of positive charge with electrons embedded into it.
\subsection{Rutherford's experiment}
\includegraphics[width=6cm] {scatter.png}\\
Rutherford's experiment involved firing a beam of alpha particles at gold foil and measuring the paths of particles from the foil.
\begin{itemize}
\item Gold was used as it was expected to have a large nucleus
\item The screen fluoresces when collided with
\item This showed the atom was mostly empty space with a positive nucleus
\end{itemize}
\subsubsection{Results}

\begin{figure}[h]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering

\includegraphics[width=6cm]{foil.jpg}  
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
\begin{tabularx}{\textwidth}{|X|X|}
\hline
Observation&Explanation\\
\hline
Most electrons pass all the way through&Atoms are mostly empty space\\
\hline
Some are deflected&The atom has a positive centre\\
\hline
Some are deflected by significant angles&The positive charge is condensed in a small area\\
\hline
\end{tabularx}
    \end{minipage}
\end{figure}
\subsection{Estimating the size of the nucleus}  
\subsubsection{Closest approach method}
\begin{tikzpicture}
\filldraw[color=red, fill=red, very thick](0,0) circle (0.2);
\draw[thick, ->,black] (0.4,0) -- (4,0) node[above,yshift=0.3cm,xshift=-2cm] {\footnotesize{Velocity reduces on approach}};
\draw[color=red, very thick](6,0) circle (1) node[] {Au};
\draw[color=black, very thick,dashed](6,0) circle (2) node[above,yshift=2cm] {EPE};
\draw[thick, ->,black] (4,0) -- (1,-1);
\end{tikzpicture}\\
\\
KE=EPE
$$8.0\times10^{-13}=\frac{1}{4\pi\epsilon_0}\times\frac{Q_{Au}}{r}\times Q_{\alpha}$$
$$r=4.55\times10^{-14}$$
\subsubsection{Estimate from scattering data}
\begin{itemize}
\item About $\frac{1}{10,000}$ deflected through more than 90\degree
\item Foil had n layers of atoms
\end{itemize}
\begin{tikzpicture}
\draw[thick, stealth-stealth,black] (6.8,-0.4) -- (6.8,0.4) node[right,midway] {d} ;
\draw[color=red, very thick](6,0) circle (0.5) node[] {\tiny{Nucleus}};
\draw[color=black, very thick](6,0) circle (2) node[above,yshift=2cm] {Atom};
\draw[thick, stealth-stealth,black] (8.5,-2) -- (8.5,2) node[right,midway] {D};
\end{tikzpicture}\\
$$\frac{\frac{1}{4}\pi d^2}{\frac{1}{4}\pi D^2}=\frac{d^2}{D^2}=\frac{1}{10,000n}$$
$n=10^4$ layers
$$\frac{d^2}{D^2}=\frac{1}{10,000\times1\times10^4}$$
$$d=\frac{D}{10,000}$$
\end{document}

### 2018-01-28 Physics Notes/Practical Notes/Practicals/Simple Harmonic Motion/Simple Harmonic Motion Practicals.tex
Physics notes update

--- 2018-01-17 Physics Notes/AS Level/All/All.tex
@@
 \usepackage{graphicx}
-\usepackage{tabularx}
 \usepackage[english]{babel}
 \usepackage{fancyhdr}
-\usepackage{circuitikz}
+
 \pgfplotsset{width=10cm,compat=1.9}
-\usepackage{relsize}
+
 \titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
@@
 \rhead{Sam Robbins 13SE}
-\lhead{AS Level Physics}
+\lhead{A Level Physics - Practicals}
 \rfoot{Page \thepage}
-\setcounter{secnumdepth}{4}
-\titleformat{\paragraph}
-{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
-\titlespacing*{\paragraph}
-{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
 
@@
 \begin{center}
-\underline{\huge AS Physics}
+\underline{\huge Simple harmonic Motion Practical - Damped SHM}
 \end{center}
-\section{Matter and radiation}
-\subsection{Inside the atom}
-\subsubsection{Specific charge}
-$$\text{Specific Charge}=\dfrac{\text{Charge}}{\text{Mass}}$$
-\subsection{Stable and unstable nuclei}
-\subsubsection{The strong force}
-0fm - 0.5fm - Repulsion\\
-0.5fm - 3fm - Attraction\\
-3fm+ - No force\\
-\subsubsection{Radioactive decay}
-\paragraph{Alpha Radiation}
-$$\mathsmaller{^A_Z}X\rightarrow\mathsmaller{^{A-4}_{Z-2}}Y+\mathsmaller{^4_2}\alpha$$
-\paragraph{Beta radiation}
-$$\mathsmaller{^A_Z}X\rightarrow\mathsmaller{^{A}_{Z+1}}Y+\mathsmaller{^0_{-1}}\beta+\overline{\nu}$$
-\paragraph{Gamma Radiation}
-This is emitted by an unstable nucleus. It has no mass and no charge. It is caused by a nucleus having too much energy, following an alpha or beta emissions.
-\subsection{Photons}
-\subsubsection{Electromagnetic waves}
-$$\text{The power of a laser beam}=nhf$$
-n is the number of photons that pass a fixed point in a second
-\subsection{Particles and antiparticles}
-\subsubsection{Antimatter}
-\paragraph{$\mathbf{\beta^+}$ decay}
-$$\mathsmaller{^A_Z}X\rightarrow\mathsmaller{^{A}_{Z-1}}Y+\mathsmaller{^0_{+1}}\beta+\nu$$
-\paragraph{Theory of antiparticles}
-For every type of particle, there is a corresponding antiparticle that:
+\section{Equipment}
 \begin{itemize}
-\item Annihilates the particle and itself if they meet, converting their total mass into photons
-\item Has exactly the same rest mass as the particle
-\item Has exactly opposite charge to the particle if the particle has a charge
+\item String
+\item Metre ruler
+\item Wooden blocks
+\item Clamp and Stand
+\item Table Tennis ball
+\item G-Clamp
 \end{itemize}
-\textbf{Pair production} - A photon with sufficient energy can change into a particle-antiparticle pair\\
-\\
-To find the energy of an electron, use $E=mc^2$
-\subsection{How particles interact}
-\subsubsection{The weak nuclear force}
-This affects both leptons and quarks\\
-\paragraph{Exchange particle}
-The W bosons:
-\begin{itemize}
-\item Have a non-zero rest pass
-\item Have a very short range (0.001fm)
-\item Are positively charged($W+$) or negatively charged ($W^-$)
-\end{itemize}
-Strangeness is not conserved with the weak nuclear force
-\subsection{Electron capture}
-$$p+e^-\rightarrow n+\nu$$
-\section{Quarks and leptons}
-\begin{tabularx}{\textwidth}{|X|X|X|X|}
-\hline
-Particle&Charge&Antiparticle&Interaction\\
-\hline
-Proton&+1&Antiproton $\overline{p}$&Strong, weak, electromagnetic\\
-\hline
-Neutron&0&Antineutron $\overline{n}$&Strong, weak\\
-\hline
-Electron $e^-$&-1&Positron $e^+$&Weak, electromagnetic\\
-\hline
-Neutrino $\nu$&0&Antineutrino $\overline{v}$&Weak\\
-\hline
-Muon $\mu^-$&-1&Antimuon $\mu^+$&Weak, electromagnetic\\
-\hline
-$\pi$ meson $\pi^+,\pi^0,\pi^-$&+1,0,-1&Inverse symbol, $\pi^0$ is own antiparticle&Strong, electromagnetic (charged only)\\
-\hline
-K meson $K^+,K^0,K^-$&+1,0,-1&&Strong, electromagnetic (charged)\\
-\hline
-\end{tabularx}
-\subsection{Leptons at work}
-\subsubsection{Lepton rules}
-\paragraph{Rule 1}
-In an interaction between a \textbf{lepton} and a \textbf{hadron}, a neutrino or antineutrino can change into or from a corresponding charged lepton.
-$$\nu_e+n\rightarrow p+e^-$$
-\paragraph{Rule 2}
-In \textbf{muon} decay, the muon changes into a muon neutrino. In addition an electron and electron neutrino are created to conserve charge.
-$$\mu^-\rightarrow E^-+\overline{\nu_e}+\nu_\mu$$
-\section{Quantum phenomena}
-\subsection{Photoelectricity}
-\subsubsection{The discovery of photoelectricity}
-Observations made about photoelectricity:
+\section{Diagram}
+$ $\\
+\begin{tikzpicture}
+\draw[black, thick] (0,0) -- (0,-2);
+\draw[black, thick] (0,0) -- (1,-1.5);
+\filldraw[black] (0,-2) circle (5pt);
+\filldraw[black] (1,-1.5) circle (5pt);
+\draw[black, very thick] (-1,0)rectangle (1,0.5);
+\end{tikzpicture}
+\section{Procedure}
 \begin{enumerate}
-\item Photoelectric emission of electron does take place if the frequency is below the \textbf{threshold} frequency
-\item The number of electrons emitted per second is proportional to the intensity of the incident radiation
-\item Photoelectric emission occurs instantaneously 
+\item Set up the equipment as in the diagram
+\item Use the G-Clamp to fix the clamp stand to the bench
+\item Displace the ball 200mm to one side and release so it can oscillate. Take measurements to determine the time period of the oscillations
 \end{enumerate}
-\subsubsection{Formulae}
-$hf=\phi+E_{Kmax}$\\
-$\phi$ = $hf_0$ = Work Function - The minimum energy needed for an electron to escape from the metal surface\\
-\subsection{Collisions of electrons with atoms}
-\subsubsection{Ionisation}
-\textbf{Ion} - An atom where the number of protons is not the same as the number of electrons\\
-\textbf{Ionisation energy of a gas atom = eV}
-\subsubsection{Excitation}
-Excitation is where gas atoms absorb energy from electron collisions without ionising. This causes electrons to increase in the energy levels.
-\subsection{Energy levels}
-\subsubsection{Electrons in atoms}
-\textbf{Ground state} - The lowest energy state of an atom\\
-\textbf{Excited state} - An energy state above the ground state
-\subsubsection{De-excitation}
-Excited atoms are unstable and so will tend towards their ground state. When an electron moves down an energy level a photon is emitted with energy equivalent to the loss of energy by the electron.
-\subsubsection{Excitation using photons}
-An electron can absorb a photon and move to an outer shell where there is a vacancy.
-However the energy of the photon must be exactly the same as the gain of energy in the electron.
-If it is not then the photon will not be absorbed by the electron.
-\subsection{Energy levels and spectra}
-When the light from a filament lamp is split into a spectrum many discrete lines will be seen. These correspond to each of the energy levels of the atom
-\subsection{Wave particle duality}
-\textbf{Wave nature} - Diffraction\\
-\textbf{Particle nature} - Photoelectric effect\\
-\\
-The wavelength of a matter particle is calculated by:
-$$\lambda=\dfrac{h}{p}=\dfrac{h}{mv}$$\\
-\section{Electric current}
-\subsection{Potential difference and charge}
-\textbf{Potential difference} - Work done per unit charge\\
-\textbf{emf} - The electrical energy produced per unit charge passing through the source
-\subsection{Resistance}
-\subsubsection{Superconductivity}
-A superconductor has \textbf{zero} resistivity at and below a \textbf{critical temperature}\\
-Superconductors are used to make high-power electromagnets
-\section{Direct current circuits}
-\subsection{Circuit rules}
-\subsubsection{Current}
-\textbf{Series}: Current in = Current out. Current through multiple components is the same as through one\\
-\textbf{Parallel}: Current into a junction = current out of a junction
-\subsubsection{Voltage}
-\textbf{Series}: Total voltage = the sum of voltages in the circuit\\
-\textbf{Parallel}: Voltage in parallel components is equal
-\subsection{Electromotive force and internal resistance}
-\begin{tabularx}{\textwidth}{|X|X|}
-\hline
-Switch Open&Switch Closed\\
-\hline
-Voltmeter reads $\epsilon$&Voltmeter reads $\epsilon-IR$\\
-\hline
-\end{tabularx}
-\begin{tikzpicture}
-\begin{axis}[axis lines=middle,scale=0.5,    ylabel = Vr,xlabel=Current,ylabel style={rotate=90,anchor=south},xlabel style={anchor=south},xmin=0,xmax=7,ymin=0,ymax=7,xtick={5},xticklabels={Short Circuit Current},ytick={5},yticklabels={$\epsilon$}
-]
-\addplot[color=black,domain=0:5]{-x+5};
-\end{axis}
-\end{tikzpicture}
-\subsection{The potential divider}
-$$V_{Out}=V_{In}\times\dfrac{R_2}{R_1+R_2}$$\\
-\\
-Sensors reduce their resistance if the condition of the environment increases.
-\section{Forces in equilibrium}
-\subsection{Moments}
-\subsubsection{Couples}
-\textbf{Couple} - A pair of equal and opposite forces acting on a body\\
-$$\text{Moment/Torque of a couple}=\text{Force}\times\text{Perpendicular distance between the lines of action of the forces}$$
-\subsection{Stability}
-\textbf{Stable} - Returns of equilibrium after displacement\\
-\textbf{Unstable} - Does not return to equilibrium after displacement.
-\subsubsection{Tilting and toppling}
-An object will fall if the line of action of the centre of mass of the object lies outside the base.
+
 \end{document}

### 2018-01-29 Physics Notes/Nuclear Physics/Radioactivity/Radioactivity.tex
Physics notes update

@@
 $$d=\frac{D}{10,000}$$
+\newpage
+\section{Radioactive materials}
+\subsection{Sources of background radiation by most common}
+\begin{enumerate}
+\item Air (e.g. radon gas)
+\item Medical
+\item Ground and buildings
+\item Food and drink
+\item Cosmic rays
+\item Nuclear weapons
+\item Air travel
+\item Nuclear power
+\end{enumerate}
+\subsection{Geiger M\"{u}ller tube}
+\includegraphics[width=10cm]{geiger.png}\\
+When a particle of ionising radiation enters the tube, the particle ionises the gas atoms along its track.
+The negative ions are attracted to the rod and the positive ions to the wall.
+These ions cause further ionisation, creating enough ions for a current to flow.
+A pulse of charge passes round the circuit through resistor R, causing the voltage pulse across R which is recorded as a single count by the pulse counter\\
+\\
+The dead time of the tube, the time taken to regain its non conducting state after an ionising particle enters it, is typically of the order of 0.2ms.
+\newpage
+\begin{tabularx}{\textwidth}{|c|X|X|X|}
+\hline
+&Alpha&Beta&Gamma\\
+\hline
+Nature&2 Protons+2 Neutrons&High speed electron or positron&High energy photon\\
+\hline
+Range&Up to 10cm&Up to 1m&Infinite\\
+\hline 
+Deflection in a magnetic field&Deflected&Opposite direction to $\alpha$ particles and more easily deflected&Not deflected\\
+\hline
+Absorption&Paper&Aluminium&Lead \\
+\hline
+Ionisation&$10^4$ ions per mm&100 ions per mm&Very weak ionising effect\\
+\hline
+Energy of each particle&Constant for a given source&Varies up to a maximum for a given source&Constant for a given source\\
+\hline
+\end{tabularx}
+
 \end{document}

### 2018-01-29 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
Maths notes update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - FP2}
\rfoot{Page \thepage}

\usepackage{cancel}

\begin{document}
\begin{center}
\underline{\huge Further Complex Numbers}
\end{center}
\section{Expressions of complex numbers}
\subsection{$\mathbf{x+iy}$}
This expresses the coordinate of the point at the end of the vector on the argand diagram.
\\
\begin{center}

\begin{tikzpicture}[scale=0.6]
\begin{axis}[axis lines=middle,ymin=-2.5,ymax=2.5,xmin=-2.5,xmax=2.5,
xtick={-2},xticklabels={$\sqrt{3}$},ytick={1},yticklabels={1},ytick pos=right]
\pgfplotsset{every tick label/.append style={font=\Large}}

\addplot coordinates { (0,0) (-2,1) };
\addplot [dashed] coordinates { (-2,0) (-2,1) };
\addplot [dashed] coordinates { (0,1) (-2,1) };
\end{axis}
\end{tikzpicture}

\end{center}
\subsection{$\mathbf{r(\cos\theta+i\sin\theta)}$}
This expresses the length of the line and the angle anticlockwise from the positive x axis
\begin{center}

\begin{tikzpicture}[scale=0.6]
\begin{axis}[axis lines=middle,ymin=-2.5,ymax=2.5,xmin=-2.5,xmax=2.5,ticks=none]
\pgfplotsset{every tick label/.append style={font=\Large}}

\addplot coordinates { (0,0) (-2,1) };
\draw (axis cs: 0.7,0) arc[radius=80, start angle= 0, end angle= 150];
    \node[] at (axis cs: 0.7,0.7) {$\mathlarger{\frac{5\pi}{6}}$};
\node[blue] at (axis cs: -0.9,0.7) {$\mathlarger{2}$};

\end{axis}
\end{tikzpicture}
\end{center}
$$2\Bigg(\cos\Big(\frac{5\pi}{6}\Big)+i\sin\Big(\frac{5\pi}{6}\Big)\Bigg)$$
\subsection{$re^{i\theta}$}
This uses the same parameters as $r(\cos\theta+i\sin\theta)$
\newpage
\section{Multiplying and dividing complex numbers}
\subsection{Multiplying}
\subsubsection{Trigonometric form}
$$Z_1Z_2=r_1(\cos\theta_1+i\sin\theta_1)\times r_2(\cos\theta_2+i\sin\theta_2)$$
$$=r_1r_2(\cos\theta_1\cos\theta_2-\sin\theta_1\sin\theta_2+i\cos\theta_1\sin\theta_2+i\sin\theta_1\cos\theta_2)$$
Apply the cos addition formula to the first two terms
$$=r_1r_2(\cos(\theta_1+\theta_2)+i\cos\theta_1\sin\theta_2+i\sin\theta_1\cos\theta_2)$$
Apply the sin addition formula to the last two terms
$$=r_1r_2(\cos(\theta_1+\theta_2)+\sin(\theta_1+\theta_2))$$
\subsubsection{Exponential form}
$$\mathlarger{Z_1Z_2=r_1e^{i\theta_1}\times r_2e^{i\theta_2}}$$
Apply laws of indices 
$$\mathlarger{Z_1Z_2=r_1r_2e^{i(\theta_1+\theta_2)}}$$
\subsection{Dividing}

\end{document}

### 2018-01-30 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
Maths notes update

@@
 \usepackage{pgfplots}
+\usepackage{tabularx}
 \usepgfplotslibrary{fillbetween}
@@
 \subsection{Dividing}
+\subsubsection{Trigonometric form}
+$$\frac{Z_1}{Z_2}=\frac{r_1(\cos\theta_1+i\sin\theta_1)}{r_2(\cos\theta_2+i\sin\theta_2)}$$
+Multiply by the complex conjugate 
+$$\frac{Z_1}{Z_2}=\frac{r_1(\cos\theta_1+i\sin\theta_1)}{r_2(\cos\theta_2+i\sin\theta_2)}\times\frac{\cos\theta_2-i\sin\theta_2}{\cos\theta_2-i\sin\theta_2}$$
+Expand
+$$\frac{Z_1}{Z_2}=\frac{r_1}{r_2}\times\frac{cos\theta_1\cos\theta_2-i\cos\theta_1\sin\theta_2+i\sin\theta_1\cos\theta_2+\sin\theta_1\sin\theta_2}{\cos^2\theta_2-i\cos\theta_2\sin\theta_2+i\sin\theta_2\cos\theta_2+\sin^2\theta_2}$$
+Simplify
+$$\frac{Z_1}{Z_2}=\frac{r_1}{r_2}\times\Big(\cos(\theta_1-\theta_2)+i\sin(\theta_1-\theta_2)\Big)$$
+\subsubsection{Exponential form}
+$$\mathlarger{\frac{Z_1}{Z_2}=\frac{r_1}{r_2}\times\frac{e^{i\theta_1}}{e^{i\theta_2}}}$$
+$$\mathlarger{\frac{Z_1}{Z_2}=\frac{r_1}{r_2}\times e^{i(\theta_1-\theta_2)}}$$
+\subsection{Comparison}
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+Multiplying&Dividing\\
+\hline	
+Multiply modulus, add arguments&Divide modulus, subtract arguments\\
+\hline
+\end{tabularx}
+\newpage
+\section{De Moivre's Theorem}
+\textcolor{red}{$$\mathlarger{[r(\cos\theta+i\sin\theta)]^n=r^n(\cos(n\theta)+i\sin(n\theta))}$$}
+\subsection{Positive proof}
+Prove true for n=1
+$$r(\cos\theta+i\sin\theta)=r(\cos\theta+i\sin\theta)$$
+\begin{center}
+True for n=1
+\end{center}
+Assume true for n=k
+$$\mathlarger{[r(\cos\theta+i\sin\theta)]^k=r^k(\cos(k\theta)+i\sin(k\theta))}$$
+Prove true for n=k+1
+$$[r(\cos\theta+i\sin\theta)]^{k+1}$$
+$$[r(\cos\theta+i\sin\theta)]^k\times(r(\cos\theta+i\sin\theta))^1$$
+$$r^k(\cos(k\theta)+i\sin(k\theta))\times r(\cos\theta+i\sin\theta)$$
+$$r^kr(\cos(k\theta+\theta)+i\sin(k\theta+\theta))$$
+$$r^{k+1}(\cos((k+1)\theta)+i\sin((k+1)\theta))$$
+True
+\subsection{Negative proof}
+n=-m
+$$[r(\cos\theta+i\sin\theta)]^{-m}$$
+Multiply by complex conjugate
+$$\frac{1}{[r(\cos\theta+i\sin\theta)]^m}\times\frac{[r(\cos\theta-i\sin\theta)]^m}{[r(\cos\theta-i\sin\theta)]^m}$$
+Apply positive De Moivre's Theorem
+$$\mathlarger{\frac{r^m(\cos(m\theta)-i\sin(m\theta))}{r^m(\cos(m\theta)+i\sin(m\theta))\times r^m(\cos(m\theta)-i\sin(m\theta))}}$$
+Simplify and expand
+$$\mathlarger{\frac{\cos(m\theta)-i\sin(m\theta)}{r^m(\cos^2m\theta-i\cos m\theta\sin m\theta+i\cos m\theta\sin m\theta+\sin^2m\theta}}$$
+Simplify
+$$\frac{\cos m\theta-i\sin m\theta}{r^m}=r^{-m}(\cos m\theta-i\sin m\theta)$$
+Rewrite
+$$r^{-m}(\cos(-m\theta)+i\sin(-m\theta))$$
+Replace -m with n
+$$r^n(\cos(n\theta)+i\sin(n\theta))$$
 

### 2018-01-30 Maths Notes/Statistics/S3/Estimation/Estimation.tex
S3 Notes update

@@
 $$\textrm{Standard error}=\frac{\sigma}{\sqrt{n}} \ \textrm{or} \ \frac{s}{\sqrt{n}}$$
+\section{Central limit theorem}
+The central limit theorem (C.L.T.) states that if $X_1,X_2,X_3...$ is a random sample, from any distribution with mean $\mu$ and variance $\sigma^2$.
+Then the sample means, $\overline{X}$ are distributed with a normal distribution.
+$$\overline{X}\sim N(\mu,\frac{\sigma^2}{n})$$ 
+For this, the sample size must be greater than 50
 \end{document}

### 2018-01-30 EPQ/Final.tex
Further Maths+EPQ Update

\documentclass[titlepage]{article}[12pt] 
\usepackage{braket}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{soul}
\pgfplotsset{compat=newest}
\usepackage{tikz} 
\usepackage{circuitikz}
\usepackage{titlesec}

\usepackage{mathtools} % for 'bsmallmatrix' environment
\newenvironment{brsm}{% % short for 'bracketed small matrix'
  \bigl[ \begin{smallmatrix} }{%
  \end{smallmatrix} \bigr]}

\usepackage[style=verbose,bibstyle=numeric,sorting=none,backend=bibtex]{biblatex}
\addbibresource{Final.bib}

\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
\begin{document}
\title{To What Extent Could Quantum Computers Improve On Classical Computers?}
\author{Sam Robbins\\The King Edward VI School, Morpeth}
\renewcommand{\today}{}
\maketitle 
\tableofcontents
\newpage
\section{Introduction}
Quantum computing is a key concept in computing, as it is a method which allows for far faster computing, beyond the current limits of classical computing. My question is: to what extent could quantum computers improve on classical computers. I chose this topic because of its relevance to the future of computing and the impact it can have on the world. I am particularly interested in it due to my future plans to study Computer Science at university and my interest in Physics.

I am going to explore this subject by finding out the key ways in which quantum computers improve on classical computers, and compare the way a quantum computer carries out a process compared to a classical computer. After this I will compare the two methods, finding which is the best. I will also compare the hardware of both quantum and classical computers, comparing them and finding which scenarios each perform best in 
\\
Quantum computers are computers that work on a superposition of states, rather than the 1 and 0 as classical computers do. This allows for them to process data much faster due to more efficient algorithms able to utilise the larger number of states, alongside quantum properties such as entanglement. I will be comparing these to classical computers, which have been developed over a much longer time, allowing for the most efficient algorithms on that hardware to be created, however these can't be developed much further due to the physical limitations of classical computers.

\section{The Physics of Computers}
\subsection{The physics of classical computers}
\subsubsection{Transistors}
Classical computers work using transistors, these are in effect electronic switches which will either permit or deny current through them based on the current in the third leg.
   \begin{figure}[H]
\begin{center}
\begin{tikzpicture}
\fill[black!100] (0,0) -- (1,0) -- (1,1) -- (0,1) -- (0,0);
\draw (1,0) -- (2,0) -- (2,1) -- (1,1) -- (1,0);
\fill[black!100] (2,0) -- (3,0) -- (3,1) -- (2,1) -- (2,0);
\draw (0,0.5) -- (-1,0.5);
\draw (3,0.5) -- (4,0.5);
\draw (1.5,0) -- (1.5,-1);
\node[draw,text=white] at (0.5,0.5) {N};
\node[fill=white] at (1.5,0.5) {P};
\node[draw,text=white] at (2.5,0.5) {N};
\node[] at (-1.25,0.5) {E};
\node[] at (4.25,0.5) {C};
\node[] at (1.5,-1.25) {B};
\end{tikzpicture}
\end{center}
\centering 
\caption{PNP Transistor}
\end{figure} 
In this diagram the electrons are collected at the collector (C) and then taken into the N doped silicon. When electrons are provided to the base (B) they will flow into the P doped silicon. This will then cause electrons to flow from the collector to the emitter (E), producing a current.
\subsubsection{Transistors and Logic Gates}
Transistors can be arranged in many ways to produce logic gates. These are then used in various combinations to perform the mathematical operations that are used in classical algorithms.
\begin{figure}[H]
  \begin{center}
    \begin{circuitikz}
   \draw (0,0) node[npn](npn1) {}
  (npn1.base) node[anchor=east] {}
  (npn1.collector) node[anchor=south] {+}
  (npn1.emitter) node[anchor=north] {};
  \draw (0,-2) node[npn](npn2) {}
  (npn2.base) node[anchor=east] {}
  (npn2.collector) node[anchor=south] {}
  (npn2.emitter) node[anchor=north] {};
  \draw (npn1.emitter) to[short] (npn2.collector);
  \draw (npn1.base) to[short] (npn2.base);
  \draw (0,-1) to[short]node[anchor=west] {Y} (1,-1);
  \draw (-0.8,-1) to[short] node[anchor=east]{X} (-2,-1);
    \end{circuitikz}
    \caption{NOT Gate}
  \end{center}
\end{figure}
Above is shown the NOT gate, constructed from transistors, the input, X, will be inverted to Y.

\begin{figure}[H]
  \begin{center}
    \begin{circuitikz}
   \draw (0,0) node[npn](npn1) {}
  (npn1.base) node[anchor=east] {X}
  (npn1.collector) node[anchor=south] {+}
  (npn1.emitter) node[anchor=north] {};
  \draw (0,-2) node[npn](npn2) {}
  (npn2.base) node[anchor=east] {Y}
  (npn2.collector) node[anchor=south] {}
  (npn2.emitter) node[anchor=north] {Z};
  \draw (npn1.emitter) to[short] (npn2.collector);
    \end{circuitikz}
    \caption{AND Gate}
  \end{center}
\end{figure}
Above is the AND gate, this requires both X and Y to be on, in order for Z to be on. This is because when X is on it will provide current for Transistor 2, which will only transmit if Y is on.
\begin{figure}[H]
  \begin{center}
    \begin{circuitikz}
   \draw (0,0) node[npn](npn1) {}
  (npn1.base) node[anchor=east] {X}
  (npn1.collector) node[anchor=south] {}
  (npn1.emitter) node[anchor=north] {};
  \draw (0,-2) node[npn](npn2) {}
  (npn2.base) node[anchor=east] {Y}
  (npn2.collector) node[anchor=south] {}
  (npn2.emitter) node[anchor=north] {};
  \draw (0,0.7) to[short,*-*] node[anchor=east]{} (1,0.7);
  \draw (0,-1.3) to[short,*-*] node[anchor=east]{} (1,-1.3);
  \draw (1,1.5) node[label={[font=\footnotesize]above:+}] {} to[short,*-*] node[anchor=east]{} (1,-1.3);
  \draw (2,-0.7) to[short] node[anchor=east]{} (2,-3);
  \draw (2,-3) to[R] node[ground]{GND}  (2,-5);
  \draw (0,-0.7) to[short,*-*] node[anchor=east]{} (2,-0.7);
  \draw (0,-2.7) to[short,*-*] node[anchor=east]{} (2,-2.7);
  \draw (2,-2.7) to[short,*-*] node[anchor=east]{}  (3,-2.7)node[label={[font=\footnotesize]east:Z}] {};
    \end{circuitikz}
    \caption{OR Gate}
  \end{center}
\end{figure}
Above is the OR gate, the collectors of the transistors are connected to the + node, so that whenever the base (X or Y) receives an input, it will give an output to the collector. The collector of both transistors are connected to the output, so if one or both of them is on the output will be on.
\subsubsection{Moore's Law}
Moore's law \autocite{mooreslaw} states that: the transistor density of integrated circuits doubles every two years. This has held true for many years, however many argue that it will soon come to an end. The problem, which is the main limitation of classical computers, is the size that transistors can be made. Over many years the size has reduced, with recent processors having transistors of length around 10nm from collector to emitter. However, as the diameter of an atom is from 0.1 to 0.5nm, processor manufacturers will soon be unable to continue this miniaturisation. This could lead to an end to development in classical computers as if they can't get any smaller they can't get any faster.
\subsection{The Physics of quantum computers}
\subsubsection{Introduction to Qubits}
Qubits are the quantum equivalent of binary bits, they can take a combination of the ground state and the excited state. These states are derived from the energy states of electrons around a nucleus in current quantum computers, however in the future the nucleus could also be used. The power of a quantum computer over a classical one is due to the fact that it can take both of these simultaneously with different probability amplitudes (the square root of the probability that when measured it will be in that state).

\subsubsection{Motion}
Quantum computers work based on the spin of quantum particles\autocite{iontrap}. These can be electrons but development is being made into using a nucleus as the qubit in a quantum computer. These electrons are usually held in a mechanism called an ion trap, this is where ions are kept in one place, so that measurements can be made on them. These ions are kept in one place by using high frequency voltage, this causes it to vibrate in approximately one place. This motion is further reduced as the centre of the defined range has very low motion, which the ion naturally tends to as it is the state of least energy.
\subsubsection{Temperature}
The next challenge is ensuring that the thermal energies\autocite{energy} in the processor are small compared to the energies in the operating of the processor. The problem with this is that when operating the processor, very low energies are used. This is because the kinetic energy gained when an ion emits or absorbs a photon is in the order of between $1\times10^{-18}J$ and $1\times10^{-20}J$. The thermal energy inside the processor has to be less than this, requiring the temperature to be extremely close to absolute zero. In order to do this, the ion trap uses lasers. These cool the ions down as they provide energy in the direction opposite to their momentum, reducing overall energy. One of the largest problems in doing this is getting the correct frequency of light, this is because the ions will only be affected by the energy from the laser, if it is exactly the resonant frequency, this means that very precise lasers are required to cool the ions. One of the problems is ensuring that the lasers don't add energy to the ions. This is solved by using the Doppler Effect, this is where an object moving towards a wave will experience it at a higher frequency. This is used in a quantum computer, by providing light at a slightly lower frequency than required. This means that ions moving towards it will experience the correct frequency, reducing their energy, but those moving away will not gain any energy.
\subsubsection{Magnetic Field}
All qubits have a spin, which is what is measured in a quantum computer. The side effect of the spin is it creates a magnetic field. The problem with this is that surrounding magnetic fields can change the spin. This magnetic field created by the spin is so weak that it can be changed by the earth's magnetic field, the consequence of this is that a quantum computer can't work under normal magnetic conditions. To solve this the quantum computer is electromagnetically shielded. This is done using many superconducting magnetic fields, a side benefit of having to cool the computer close to absolute zero. These counteract any incoming magnetic fields, protecting the qubits in the processor. 
\subsubsection{Control}
To change the state of a qubit, it is illuminated by a laser, adding or reducing energy depending on direction relative to the movement of the qubit, changing the energy and so the state. However, the power of a quantum computer often comes from its ability to use two interacting qubits. To do this an XOR gate is required. The quantum version of an XOR gate is a CNOT gate, this flips qubit$_2$ if qubit$_1$ is equal to 1. This works by exciting qubit$_1$ in a way that it will become excited if its state is 1. The qubit is excited with too much energy, meaning that it starts to excite all the qubits in the system if qubit$_1$'s state was 1, meaning they require less energy to become excited. Qubit$_2$ is then given less energy than if it was in a state unaffected by qubit$_1$, this means that it will not become excited if qubit$_1$ wasn't, but it will become excited if it was. To finalise the operation, qubit$_1$ is given the same amount of energy as it was given originally, cancelling out the excitation it gave to all the qubits, putting all but qubit$_2$ back in their original state.
\subsection{Comparison}
Quantum computers rely on much more volatile states than classical computer do. This means that there is much more control required. The consequence of this is that quantum computers are much harder to build and manage, as well as them only being able to be used in one place. This limits them compared to classical computers which are now small and portable so can be used anywhere. As with the early classical computers, it is likely that quantum technology will develop such that they can be miniaturised, however that is not currently available. However, quantum computers may not need to be portable as the current uses for them don't require them to be moveable.

The physics of quantum computers is beneficial, in that it allows for the use of quantum algorithms. This can make the complexity in construction and maintenance worthwhile, however only in certain scenarios. It also could be argued that quantum computers are less complicated than classical computers as quantum computers are only used in certain cases, meaning that they only have a few thousand qubits, compared to classical computers which have transistors in the order of billions. This is partially due to the efficiency of quantum computing as, for example a NOT gate requires 2 transistors but only 1 qubit. Transistors are also of a larger size than qubits, meaning that more qubits can theoretically be placed in a given area. Quantum computers also have a larger potential for miniaturisation as they can be used with electrons, which are smaller than $10^{-18}$m, meaning that the limits of quantum computing are far smaller than the limits of quantum computing. This means that theoretically on a 3cm$\times3$cm processor there could me more than $9\times10^{32}$ qubits, far more than is possible with a regular CPU, which has around $3\times10^{16}$ transistors (if each transistor was composed of 3 atoms, which is the limit of what is possible without a scientific breakthrough). This means that a quantum computer could have over a quadrillion times more processing units than the best classical computers in a given chip size.

\section{Introduction to each method of operation}
\subsection{Quantum Computers}
\subsubsection{Qubit Notations}
The notation for qubits may appear similar to binary notation, however the meaning of them is very different. For a single Qubit system, the measurement will be in the format $\alpha\Ket{0}+\beta\Ket{1}$ \autocite{alpha_beta}. Where $\Ket{0}$ is equal to $\begin{brsm}1 \\ 0\end{brsm}$ and $\Ket{1}$ is equal to $\begin{brsm}0 \\ 1\end{brsm}$. The probability of the Qubit being measured as $\Ket{0}$ is $|\alpha|^2$ and the probability of the Qubit being measured as $\Ket{1}$ is $|\beta|^2$. These probabilities must add to 1 as there is a 100$\%$ chance it will be in one of the two states, this also means that the length of the vector $\begin{brsm}\alpha \\ \beta\end{brsm}$ is 1. This allows all quantum states to be expressed as points on a unit circle. An example of this is shown in figure 1, a representation of a vector in a Hilbert Space. This displays the state $\dfrac{1}{\sqrt{2}}\Ket{0}+\dfrac{1}{\sqrt{2}}\Ket{1}$, denoted as $\ket{+}$. This makes a $\dfrac{\pi}{4}$ angle with each axis as the probability of each is equal.

\begin{figure}[H]
\begin{tikzpicture}
  \begin{axis}[ 
  	ticks=none,
    width=4cm,height=4cm,
    axis x line = middle,
    axis y line = middle,
    xlabel={$\Ket{0}$},
    xlabel style={at=(current axis.right of origin), anchor=west},
    ylabel={$\Ket{1}$},
    ylabel style={at=(current axis.above origin), anchor=south},
    domain = 0:10,
    xmin = 0,
    xmax = 10,
    ymin = 0,
    ymax = 10,
    yticklabels={,,},
    xticklabels={,,},
  ]
    \addplot[samples=100] [domain=0:8] {x} node[above,pos=1] {$\Ket{+}$};
  \end{axis}
\end{tikzpicture}
\centering 
\caption{Superposition representation}
\end{figure}

When the probability of each state is different, for example, the state $\dfrac{1}{2}\ket{0}+\dfrac{\sqrt{3}}{2}\ket{1}$. The angle with the $\ket{0}$ axis is calculated by performing $\arctan\bigg(\dfrac{\beta}{\alpha}\bigg)$ so, in this case, the angle is $\arctan\bigg(\dfrac{\sqrt{3}\div2}{1\div2}\bigg)$ which is equal to an angle of $\dfrac{\pi}{3}$.

The value of a Qubit can be measured with regards to $\ket{0}$ and $\ket{1}$ as shown above, but it can also be measured in terms of $\ket{+}$ and $\ket{-}$ where $\ket{+}$ is equal to $\dfrac{1}{\sqrt{2}}\ket{0}+\dfrac{1}{\sqrt{2}}\ket{1}$ and $\ket{-}$ is equal to $\dfrac{1}{\sqrt{2}}\ket{0}-\dfrac{1}{\sqrt{2}}\ket{1}$. This is shown in Figure 2 which shows both the $\ket{0}\ket{1}$ and the $\ket{+}\ket{-}$ basis. This allows the state $\ket{\psi}$ to be measured in either of them. The sign and bit value cannot both be known perfectly, this is because when measured, for example in the $\ket{0}\ket{1}$ axis the superposition collapses and the value becomes 100$\%$ $\ket{0}$ or $\ket{1}$. This means that if a second measurement in the $\ket{+}\ket{-}$ basis was taken, the value would be different to the result if that was the first measurement. As an example, from the figure the state $\ket{\psi}$ is most likely to be measured as $\ket{0}$ as it makes the smallest angle with that axis. So when the value is then measured in the $\ket{+}\ket{-}$ axis there is an equal probability of either. However, if that had been measured first it would be most likely to come as a $\ket{+}$ as it makes the smallest angle with that axis.

\begin{figure}[H]
\begin{tikzpicture}
  \begin{axis}[
  	ticks=none,
    width=6cm,height=6cm,
    axis x line = middle,
    axis y line = middle,
    xlabel={$\Ket{0}$},
    xlabel style={at=(current axis.right of origin), anchor=west},
    ylabel={$\Ket{1}$},
    ylabel style={at=(current axis.above origin), anchor=south},
    domain = 0:10,
    xmin = -10,
    xmax = 10,
    enlarge y limits={rel=0.13},
    enlarge x limits={rel=0.13},
    ymin = -10,
    ymax = 10,
    yticklabels={},
    xticklabels={},
  ]
    \addplot[samples=100] {x} node[above,pos=1] {$\Ket{+}$};
    \addplot[samples=100] {-x} node[above,pos=1] {$\Ket{-}$};
    \addplot[samples=100] {0.5*x} node[above,pos=1] {$\Ket{\psi}$};
  \end{axis}
\end{tikzpicture}
\centering 
\caption{Different common superpositions}
\end{figure}
\subsubsection{Quantum Gates}
There are many quantum gates, some are very similar to classical gates but some do functions that could not be performed on a classical computer. 
\paragraph{Pauli X Operator}
One set of quantum gates are the Pauli Operators \autocite{pauli}, the Pauli X operator is shown by the 2$\times$2 matrix:

\[
 \begin{bmatrix}
  0 &1\\
  1&0
 \end{bmatrix}
\]

This performs a similar function to the classical NOT gate and obeys the following truth table
\begin{figure}[H]
\begin{center}
\def\arraystretch{1.6}
\begin{tabular}{ |c|c| } 
 \hline
 Input & Output \\ 
 \hline
 $\ket{0}$&$\ket{1}$\\ 
 \hline
 $\ket{1}$&$\ket{0}$\\ 
 \hline
 $\ket{+}$&$\ket{+}$\\
 \hline
 $\ket{-}$&$-\ket{-}$\\
 \hline
\end{tabular}
\end{center}
\centering 
\caption{Pauli X Operator Truth Table}
\end{figure}

The reason for this can be shown in the below calculation:
\[
\begin{bmatrix}
  0&1\\1&0
\end{bmatrix}
\begin{bmatrix}
  1\\0
\end{bmatrix}
=
\begin{bmatrix}
  0\\1
\end{bmatrix}
\]
\paragraph{Pauli Y Operator}
The Pauli Y operator performs both a bit and phase flip and is shown by the 2$\times$2 matrix
\[
\begin{bmatrix}
0&-i\\i&0
\end{bmatrix}
\]

The truth table of this gate is:
\begin{figure}[H]
\begin{center}
\def\arraystretch{1.6}
\begin{tabular}{ |c|c| } 
 \hline
 Input & Output \\ 
 \hline
 $\ket{0}$&$i\ket{1}$\\ 
 \hline
 $\ket{1}$&$-i\ket{0}$\\ 
 \hline
 $\ket{+}$&$-i\ket{-}$\\
 \hline
 $\ket{-}$&$i\ket{+}$\\
 \hline
\end{tabular}
\end{center}
\centering 
\caption{Pauli Y Operator Truth Table}
\end{figure}
The reason for this is explained in the following calculation:
\[
\begin{bmatrix}
  0&-i\\i&0
\end{bmatrix}
\begin{bmatrix}
  1\\0
\end{bmatrix}
=
\begin{bmatrix}
  0\\i
\end{bmatrix}
=i\ket{1}
\]

\paragraph{Pauli Z Operator}
The Pauli Z operator performs a phase flip, this in effect changes the sign in front of the vector. It uses the following matrix.

\[
 \begin{bmatrix}
  1&0\\
  0&-1
 \end{bmatrix}
\]
This is very similar to the identity matrix and so will not change the absolute value of any of the bits. However, it will change the sign due to the negative sign on the bottom right hand value of the matrix above.

\begin{figure}[H]
\begin{center}
\def\arraystretch{1.6}
\begin{tabular}{ |c|c| } 
 \hline
 Input & Output \\ 
 \hline
 $\ket{0}$&$\ket{0}$\\ 
 \hline
 $\ket{1}$&$-\ket{1}$\\ 
 \hline
 $\ket{+}$&$\ket{-}$\\
 \hline
 $\ket{-}$&$\ket{+}$\\
 \hline
\end{tabular}
\end{center}
\centering 
\caption{Pauli Z Operator Truth Table}
\end{figure}

This can be shown in the following calculation:

\[
\begin{bmatrix}
  1&0\\0&-1
\end{bmatrix}
\begin{bmatrix}
  0\\1
\end{bmatrix}
=
\begin{bmatrix}
  0\\-1
\end{bmatrix}
\]

\paragraph{The Hadamard Transform}
The Hadamard transform creates an equal superposition of $\ket{0}$ and $\ket{1}$. It does this using the matrix:
\[
\dfrac{1}{\sqrt{2}}
 \begin{bmatrix}
  1&1\\
  1&-1
 \end{bmatrix}
\]

This creates the truth table:
\begin{figure}[H]
\begin{center}
\def\arraystretch{1.6}
\begin{tabular}{ |c|c| } 
 \hline
 Input & Output \\ 
 \hline
 $\ket{0}$&$\ket{+}$\\ 
 \hline
 $\ket{1}$&$\ket{-}$\\ 
 \hline
 $\ket{+}$&$\ket{0}$\\
 \hline
 $\ket{-}$&$\ket{1}$\\
 \hline
\end{tabular}
\end{center}
\centering 
\caption{Haddamard Transform Truth Table}
\end{figure}

\subsection{How Classical Computers Work}
\subsubsection{Bit Notations}
Binary bits have much simpler notations than Qubits as they take one definite state, either a 1 or a 0. Larger strings of these can be used to define larger states by each position taking values of powers of two, with the smallest bit position being equal to $2^0$ which is equal to 1. The next bit position will take $2^1$ which is equal to 2. Groups of bits are used to show data, for example the byte (8 bits) can contain $2^8=256$ different combinations, easily allowing for the Latin alphabet and numbers along with many other alphabets.
\subsubsection{Classical Gates}
Computers construct logic gates from transistors this means that a CPU made out of transistors can create combinations of these gates which can be used to process data. The main logic gates are the AND, OR, NOT and XOR, with extra gates with an integrated NOT gate like a NOR gate. The only one bit gate is the NOT gate, this will invert the input, and follows the following truth table:

\begin{figure}[H]
\begin{center}
\begin{tabular}{ |c|c| } 
 \hline
 Input & Output \\ 
 \hline
 0&1\\ 
 1&0\\ 
 \hline
\end{tabular}
\end{center}
\centering 
\caption{NOT Gate Logic Table}
\end{figure}

The AND gate will only turn on if both inputs are on, and so follows the truth table in figure 4.
\begin{figure}[H]
\begin{center}
\begin{tabular}{ |c|c|c| } 
 \hline
 Input 1&Input 2&Output \\ 
 \hline
 0&0&0\\ 
 0&1&0\\ 
 1&0&0\\
 1&1&1\\
 \hline
\end{tabular}
\end{center}
\centering 
\caption{AND Gate Logic Table}
\end{figure}

The OR gate performs a similar function to the AND gate but will turn on the inputs if either of the inputs are on, as shown in the truth table in figure 5.
\begin{figure}[H]
\begin{center}
\begin{tabular}{ |c|c|c| } 
 \hline
 Input 1&Input 2&Output \\ 
 \hline
 0&0&0\\ 
 0&1&1\\ 
 1&0&1\\
 1&1&1\\
 \hline
\end{tabular}
\end{center}
\centering 
\caption{OR Gate Logic Table}
\end{figure}

The XOR gate is similar to the OR gate but will only turn on the output if only one output is on, following the truth table in figure 6.
\begin{figure}[H]
\begin{center}
\begin{tabular}{ |c|c|c| } 
 \hline
 Input 1&Input 2&Output \\ 
 \hline
 0&0&0\\ 
 0&1&1\\ 
 1&0&1\\
 1&1&0\\
 \hline
\end{tabular}
\end{center}
\centering 
\caption{XOR Gate Logic Table}
\end{figure}
\subsection{Comparison between the two methods of working}
The method of quantum computing compared to classical computing could be thought of as better due to its ability to take multiple states simultaneously. This means that operations can be performed on long strings of numbers represented in a superposition in one cycle. The same in classical computers would require one cycle for each value in a list.

However, the benefit of classical computers is the relative simplicity of the process, allowing for them to be more accessible. It also reduces the research and manufacture time as they are well documented as classical computers are much older inventions, with many experts in the field. 
  \section{Deutsch-Jozsa algorithm}
\subsection{How the Deutsch-Jozsa Algorithm works}
The Deutsch-Jozsa algorithm \autocite{deutsch} is used to find if a quantum function is constant or balanced. A constant function will give one result for any input. A balanced function will give one result for half the inputs and another result for the other half. The function will take an input $x$ and give an output of $f(x)$. To start this algorithm two qubits are needed, called $Q_1$ and $Q_2$. The Pauli x operator is applied to $Q_2$ to turn it from $\ket{0}$ to $\ket{1}$. The Hadamard transform is then applied to both Qubits, turning $Q_1$ into ${\dfrac{1}{\sqrt{2}}\ket{0}}+{\dfrac{1}{\sqrt{2}}\ket{1}}$ and $Q_2$ into ${\dfrac{1}{\sqrt{2}}\ket{0}}-{\dfrac{1}{\sqrt{2}}\ket{1}}$. These Qubits are then given to the quantum function, and because $Q_2$ is equal to $\ket{-}$ and $Q_1$v is equal to $\ket{+}$ the output from the function to $Q_1$ is $(-1)^{f(x)}\ket{0}+(-1)^{f(x)}\ket{1}$. The Hadamard transform is then applied again to $Q_1$, giving the result $[(-1)^{f(0)}+(-1)^{f(1)}]\ket{0}+[(-1)^{f(0)}-(-1)^{f(1)}]\ket{1}$. If the function is constant then f(0) = f(1) and because $(-1)^n+(-1)^n$ equals 2 if n is odd and -2 if n is even $\ket{1}$ will always have a value if the function is constant. However $(-1)^n-(-1)^n$ always equals zero and so $\ket{1}$ will not have a value. This means that if the function is constant $Q_1$ will have a value of $\ket{0}$. However if the function is balanced $f(0)\neq f(1)$ with a one bit binary output only 1 and 0 are permitted. As $(-1)^0+(-1)^1$ equals zero but $(-1)^1-(-1)^0=-2$ and $(-1)^0-(-1)^1=2$. This means that for a balanced function $Q_1=\ket{1}$
\subsection{A classical alternative to the Deutsch-Jozsa Algorithm}
The classical alternative to this algorithm would be to test the function with a maximum of half the range of the input numbers. Most times that range would not be necessary, as different output values would often come up earlier. If the function gives all one value it is constant but if two values are found it will be balanced.
 \subsection{Deutsch-Jozsa Algorithm compared to a classical method}
 The Deutsch-Jozsa algorithm can be considered to be superior to a classical algorithm, as it can find the correct solution with one query of the function, whereas classically it could take up to $2^{n-1}$ queries where n is the length of the input strings. Obviously for large number of bit inputs the Deutsch-Jozsa algorithm has far greater performance as it takes a constant number of queries, whereas classically it requires an exponential number of queries. However, the actual usefulness of either algorithm is severely limited as it can only be performed on quantum functions, a task not often faced in the current world.    
 \section{Searching Algorithms}
 \subsection{Binary Search}
 Binary search is a method used to find an item in an ordered list. It works by choosing the middle element of a list and checking if the desired item is before or after it and then discounting the other values based on this result. As shown below, when trying to find the value C with circles being selections and strikeouts being removals.

 \begin{figure}[H]
\begin{center}
\begin{tabular}{ c c c c c c}
A&B&C&D&E&F\\
 A&B&C&\textcircled{\st{D}}&\st{E}&\st{F}\\ 
 \st{A}&\textcircled{\st{B}}&C&\st{D}&\st{E}&\st{F}\\
  \st{A}&\st{B}&\textcircled{C}&\st{D}&\st{E}&\st{F}\\  
\end{tabular}
\end{center}
\centering 
\caption{Binary Search}
\end{figure}
This will find the correct value in a maximum of $\left \lfloor{log_2(N)+1}\right \rfloor $ comparisons with N being the length of the list, as shown in the above example as it took $\left \lfloor{log_2(6)+1}\right \rfloor =3 $ steps to find the position. Obviously this is worst case scenario and could only take 1 iteration if the required element is in the middle.
 \subsection{Grover's Algorithm}
Grover's Algorithm \autocite{grover} is an algorithm to find an object in an unordered list. It works by performing a Hadamard transform on the Qubit, turning it into multiple states with equal probability. For example, for 3 bit strings it would produce the superposition listed below:

  \begin{figure}[H]
\begin{center}
\def\arraystretch{2}
\begin{tabular}{ c}
$\dfrac{1}{2\sqrt{2}}\Ket{000}$+
$\dfrac{1}{2\sqrt{2}}\Ket{001}$+
$\dfrac{1}{2\sqrt{2}}\Ket{010}$+
$\dfrac{1}{2\sqrt{2}}\Ket{011}$+
$\dfrac{1}{2\sqrt{2}}\Ket{100}$+
$\dfrac{1}{2\sqrt{2}}\Ket{101}$+
$\dfrac{1}{2\sqrt{2}}\Ket{110}$+
$\dfrac{1}{2\sqrt{2}}\Ket{110}$+
$\dfrac{1}{2\sqrt{2}}\Ket{111}$
\end{tabular}
\end{center}
\centering 
\caption{State at the start of Grover's Algorithm}
\end{figure}

  \begin{figure}[H]
\begin{center}
\begin{tikzpicture}
        \begin{axis}[
        width=10cm,height=3cm,
            x tick label style={/pgf/number format/1000 sep=},
            ymin=0,
            ymax=4,
            xmin=$\ket{000}$,
            xmax=6,
            ytick={0,4},
yticklabels={0,$\dfrac{1}{2\sqrt{2}}$},
            ylabel=Probability Amplitude,
            legend style={at={(0.5,-0.1)},anchor=north,legend columns=-1},
            ybar interval=0.3,
            symbolic x coords = {$\ket{000}$, $\ket{001}$, $\ket{010}$, $\ket{011}$, $\ket{100}$, $\ket{101}$, $\ket{110}$,$\ket{111}$,6,0}            
        ]
        \addplot [color=black,fill=black] coordinates {($\ket{000}$,4) ($\ket{001}$,4) ($\ket{010}$,4) ($\ket{011}$,4) ($\ket{100}$,4) ($\ket{101}$,4) ($\ket{110}$,4)($\ket{111}$,4) (6,0)};        
        \draw ({rel axis cs:0,0}|-{axis cs:0,0}) -- ({rel axis cs:1,0}|-{axis cs:0,0});
\draw ({rel axis cs:0,0}-|{axis cs:0,0}) -- ({rel axis cs:0,1}-|{axis cs:0,0});
        \end{axis}
\end{tikzpicture}
\end{center}
\centering 
\caption{Visualisation of the state at the start of Grover's Algorithm}
\end{figure}

A function called the quantum oracle then looks at the state and turns the probability amplitude of the desired section negative. It does this through the process $\ket{x}\rightarrow(-1)^{f(x)}\ket{x}$ where f(x)=1 on the part of the superposition related to the desired element and f(x)=0 otherwise. More precisely, this creates the superposition 
$\dfrac{1}{\sqrt{2}}(\ket{x}\ket{f(x)}-\ket{x}\ket{1 \oplus f(x)})$ The consequence of this is that a negative value will be returned when f(x)=1 and a positive value will be returned when f(x)=0.

 This process will inverse the probability amplitude of the desired element, resulting in the state below attempting to search for $\ket{101}$.
  \begin{figure}[H]
\begin{center}
\begin{tikzpicture}
        \begin{axis}[
        width=10cm,height=4cm,
        ymin=-4,
        ymax=4,
        xmin=$\ket{000}$,
        xmax=6,
        x tick label style={/pgf/number format/1000 sep=},
        ytick={-4,0,4},
		yticklabels={$-\dfrac{1}{2\sqrt{2}}$,0,$\dfrac{1}{2\sqrt{2}}$},
        ylabel=Probability Amplitude,
        legend style={at={(0.5,-0.1)},anchor=north,legend columns=-1},
        ybar interval=0.3,
        symbolic x coords = {$\ket{000}$, $\ket{001}$, $\ket{010}$, $\ket{011}$, $\ket{100}$, $\ket{101}$, $\ket{110}$,$\ket{111}$,6,0}            
        ]
        \addplot [color=black,fill=black] coordinates {($\ket{000}$,4) ($\ket{001}$,4) ($\ket{010}$,4) ($\ket{011}$,4) ($\ket{100}$,4) ($\ket{101}$,-4) ($\ket{110}$,4)($\ket{111}$,4) (6,0)};        
        \draw ({rel axis cs:0,0}|-{axis cs:0,0}) -- ({rel axis cs:1,0}|-{axis cs:0,0});
\draw ({rel axis cs:0,0}-|{axis cs:0,0}) -- ({rel axis cs:0,1}-|{axis cs:0,0});
        \end{axis}
\end{tikzpicture}
\end{center}
\centering 
\caption{Visualisation after the oracle}
\end{figure}

After this, the states are then increased based on their difference from the mean and decreasing the amplitude if the difference is negative, resulting in a higher probability for the desired element.
  \begin{figure}[H]
\begin{center}
\begin{tikzpicture}
        \begin{axis}[
        width=10cm,height=5cm,
        ymax=5,
        ymin=0,
        xmin=$\ket{000}$,
        xmax=6,
            x tick label style={/pgf/number format/1000 sep=},
            ytick={0,1,5},
yticklabels={0,$\dfrac{1}{4\sqrt{2}}$,$\dfrac{5}{4\sqrt{2}}$},
            ylabel=Probability Amplitude,
            legend style={at={(0.5,-0.1)},anchor=north,legend columns=-1},
            ybar interval=0.3,
            symbolic x coords = {$\ket{000}$, $\ket{001}$, $\ket{010}$, $\ket{011}$, $\ket{100}$, $\ket{101}$, $\ket{110}$,$\ket{111}$,6,0}            
        ]
        \addplot [color=black,fill=black] coordinates {($\ket{000}$,1) ($\ket{001}$,1) ($\ket{010}$,1) ($\ket{011}$,1) ($\ket{100}$,1) ($\ket{101}$,5) ($\ket{110}$,1)($\ket{111}$,1) (6,0)};        
        \draw ({rel axis cs:0,0}|-{axis cs:0,0}) -- ({rel axis cs:1,0}|-{axis cs:0,0});
\draw ({rel axis cs:0,0}-|{axis cs:0,0}) -- ({rel axis cs:0,1}-|{axis cs:0,0});
        \end{axis}
\end{tikzpicture}
\end{center}
\centering 
\caption{Visualisation after transformation around the mean}
\end{figure}

After one run this has a probability of the desired element being measured of $\bigg(\dfrac{5}{4\sqrt{2}}\bigg)^2=\dfrac{25}{32}$, this puts the answer at a 78$\%$ probability of being correct when measured. In order to increase accuracy, this process is run $\dfrac{\pi}{4}\sqrt{2^N}$ times where N is the string length. For this example it would be $\dfrac{\pi}{4}\sqrt{2^3} = 2$ times. This would mean that another loop of the inversion around zero, followed by the transformation around the mean, would be required to improve it to a suitable level of accuracy. This would then result in a probability amplitude of $\dfrac{11}{8\sqrt{2}}$ for the correct element, giving a probability of 95$\%$, a much better success rate making the algorithm more reliable.

%\paragraph{Re-Do of Grovers}
%Grover's algorithm is a search algorithm for unordered lists, it does this by making the probability amplitude of the element to be searched for larger than the probability amplitude of all the other elements, making it a more likely result to come up.
%
%To perform this algorithm, initialise two qubits, Qubit 1 and Qubit 2. Apply the Hadamard transform to qubit 1 and apply the pauli X operator followed by the Hadamard transform to Qubit 2. Input this into the Quantum oracle in the function $\mathcal{O}(\ket{x}\otimes\ket{-})$, which can be expanded to $\dfrac{1}{\sqrt{2}}(\mathcal{O}\ket{x}\ket{0}-\mathcal{O}\ket{x}\ket{1}$. This can the quantum oracle sets $f(x)=1$ when $x$ is the desired element and $f(x)=0$ for all other elements. This means the function can be simplified to $\dfrac{1}{\sqrt{2}}(\ket{x}\ket{f(x)}-\ket{x}\ket{1\oplus f(x)})$. If f(x)=1 this can be simplified to $\dfrac{1}{\sqrt{2}}(\ket{x}\ket{1}-\ket{x}\ket{0})$ which is equal to $-\ket{x}\ket{-}$ which means that the probability amplitude of Qubit 1 has been inverted. If f(x)=0 it gives a result of $\ket{x}\ket{-}$, meaning that the state has not been changed.

\subsection{Grover's Algorithm compared to binary search}

The main advantage of Grover's Algorithm is that it can work on unordered lists, meaning that unlike binary search the list does not need sorting before an element can be found. The major advantage of this is that it does not also require a sorting algorithm and so is a much quicker option, meaning for larger databases it could be far superior. For large databases the extra storage required to hold the sorted data could mean that in binary search there would be a significant increase in storage costs as their requirements would in effect double if the data was not wanted to be stored in a sorted form. Another advantage of this is that the order of the data is often very important, and so by sorting it, the importance of the data is then lost. 
\\
\\
 The advantages of binary search are that it is a much quicker system to implement and is currently used in many facilities. This is because binary search can run on a classical computer, which is much cheaper both to buy and run than the quantum computer needed for Grover's algorithm.
\\
\\
Another advantage of binary search is that it can be used on explicit databases (databases spread over multiple storage areas) \autocite{practicalgrover} whereas Grover's algorithm cannot. This means that it is limited to a file stored in one place, vastly limiting its capability, as most large databases (an area where Grover's algorithm would be useful) are spread over multiple servers.For example, the millions of servers used by Google because it is impractical to store all the information in one place due to its size. Storing all the data in one place also reduces security and increases the impact of outages.
\\
\\
Binary search will also always give a correct answer, as opposed to the 90$\%$-100$\%$ accuracy of Grover's algorithm. This could be a large problem for large firms as a 10$\%$ failure rate over millions of searches would be unacceptable and so would mean that a classical algorithm would be the only option.

 \section{Factoring Algorithms}
 \subsection{RSA Encryption}
 The main use of factoring numbers is in encryption, this is because many encryption systems work on the factors of large numbers, I will explore this with the example of RSA.
 RSA encryption works by multiplying two large prime numbers together, this creates the number, n.
 This n is then used to encrypt a message using the form $E=m^emod(n)$ where e is an encrypting value. This is then decrypted using $m=E^dmod(n)$. A value denoted as $\phi(n)$ is a value based on the factors of n found by $(p-1)\times(q-1)$ where p and q are the factors. This value of $\phi(n)$ is then used to find e as it is any number less than n that is not a factor. The value of d is then found using $\dfrac{k\times\phi(n)+1}{e}$ where k is the first integer that makes d an integer value. 
\\
RSA can be broken by finding the prime factors of n. This then allows for $\phi(n)$ to be found, allowing for d to be found, as shown above. Then with the message,E,the decrypting value, d, and n the message can be decrypted.

\subsection{Quadratic Sieve}
The quadratic sieve \autocite{sieve} is a classical algorithm used to factor numbers, it is performed by expressing the number to be factorised as the difference of two squares.
Starting at $\sqrt{N}$ and increasing the value of x until $x^2-N=y^2$ as below in factorisation of 989
  \begin{figure}[H]
\begin{center}
\begin{tabular}{ c|c|c}
x&$y^2$&y\\
\hline
32&35&5.916\\
33&100&10

\end{tabular}
\end{center}
\centering 
\caption{Quadratic Sieve}
\end{figure}
Obviously, not all iterations of this will be as quick but this shows that $33^2-10^2$ is equal to 989, the factors can then be found from 33+10=43 and 33-10=23. However, this will not work for all numbers. Factors can also be computed from values $(y_1)^2$ and $(y_2)^2$  that are not square numbers but multiply together to give a square number and the corresponding $x_1$ and $x_2$. With A being $x_1 \times x_2$ and B being $\sqrt{y_1^2 \times y_2^2}$ The GCD of (A+B, N) and (A-B, N) are factors.

 \subsection{Shor's algorithm}
 Shor's algorithm \autocite{shor} is a quantum algorithm which also factorises numbers, however it performs it through a different method to the quadratic sieve. The first task is to find the period of $x^a mod n$ where x is any number, 2 in my example. A is then increased from 0. n is the number to be factored. This will then create a list of numbers when performed and the period is found where the pattern repeats itself. In my example I tried to factor 989, as also shown in the quadratic sieve section. This results in a period of 154. Another number is then calculated by dividing the period over 2, called z in the formula then doing $y=a^z mod n$, working to being $y=2^{77} mod989$ which results in y=300. From this number the GCD of (y+1,n) and (y-1,n) is calculated, these are easily calculated with Euclid's algorithm, a classical algorithm, demonstrated below, trying to calculate GCD(301,989) and GCD(299,989). For example for 301 and 989:
   \begin{figure}[H]
\begin{center}
989=301$\times$3+86\\
301=86$\times$3+43\\
86=43$\times$2+0
\end{center}
\centering 
\caption{Euclid's Algorithm}
\end{figure}
When the number is added, the greatest common divisor will be the number at the end above, in this example 43. Doing this again for the other two numbers gives 23, these two numbers are the prime factors of 989. This is how it is performed classically, however when trying to find the period of large numbers takes too much time. 
Shor's algorithm takes the number to be factored (N), and a random number (A) which is not a factor of N (GCD(N,A)=1). Another number, n, is chosen which dictates the size of the register, the larger this is the greater the time taken but the greater the accuracy. For this example N will be 39, A will be 7 and n will be 10. q is $2^n$ so in this case it is $2^{10}$.

The algorithm is started in the state $\ket{0}\ket{0}$, the QFT (Quantum Fourier Transform) is then applied to the first Qubit, changing it to the state:
   \begin{figure}[H]
\begin{center}
$\ket{\psi}=\dfrac{1}{\sqrt{q}}\sum\limits_{x=0}^{q-1}\ket{x}\ket{0}$
\end{center}
\centering 
\caption{Shor's Algorithm State 1}
\end{figure}
So with the numbers used in the example it is
   \begin{figure}[H]
\begin{center}
$\ket{\psi}=\dfrac{1}{2^5}\sum\limits_{x=0}^{{2^{10}}-1}\ket{x}\ket{0}$
\end{center}
\centering 
\caption{Shor's Algorithm State 2}
\end{figure}

Now $f(x)$ is calculated and put in the second register, in Shor's algorithm $f(x)$ is $a^x mod n$. This then creates the state
   \begin{figure}[H]
\begin{center}
$\ket{\psi}=\dfrac{1}{2^5}\sum\limits_{x=0}^{{2^{10}}-1}\ket{x}\ket{f(x)}$
\end{center}
\centering 
\caption{Shor's Algorithm State 3}
\end{figure}
The second qubit is then measured, this causes it to collapse to one state, meaning that the state will only include instances where f(x)=y, with y being the measured value. This now makes it easier to find the period, as the difference between values in the state is the period. The inverse QFT is then applied to this state.

This transformation then leads to a distribution of values with some having higher probability than others. The most likely values, divided by q, will approximately give a fraction, whose numerator is the period. For the numbers given above a likely value is 85. This is then divided by $2^{10}$ to give a fraction. This fraction is then converted, by continued fractions, into a number with a numerator of 1. This will give $\dfrac{1}{12}$, giving the period of 12.

This period is then used in the formula $a^{r/2}modN$ which is $7^6mod39=25$ the GCD of (25-1,37) and (25+1,39) are then found which are 3 and 13, which are the prime factors of 39.

 \subsection{Shor's algorithm compared to Quadratic Sieve}
For the example of factoring a larger number, for example 792347. Shor's algorithm runs in \\
$(2logN)(loglogN)(logloglogN)$ time. This means that it will run in 68 time units. However, the quadratic sieve runs in $e^{\sqrt{\ln(n)\ln(n)\ln(n)}}$ time which would mean it would run in $5.4\times10^{21}$ time units. This difference is because quadratic sieve runs in exponential time, whereas Shor's algorithm runs in log time, meaning that as the number gets larger the difference in speed for Shor's will be less than the difference for the quadratic sieve. Factoring becomes interesting regarding cryptography, this is because one of the most popular encryption methods is RSA. The current largest RSA number is RSA-2048, this is 2048 bits, equal to 617 digits. Using general number field sieve, the fastest algorithm for strings over 100 digits long, the time taken would be $4.8\times10^{34}$ units. This is much longer than the run time for Shor's algorithm for that number, which would be 40884 time units. The potential of Shor's algorithm could mean that current cryptography systems will be obsolete as the security of RSA comes from the fact that the numbers can't be factored. Supposing that the time units were seconds, the classical algorithm would take longer than the life of the universe as it would take $1.5\times10^{27}$ years and the life of the universe is $1.1\times10^{17}$ years. Comparing this to the run time of Shor's algorithm which is 11 hours, it is easy to see the danger that Shor's algorithm poses to existing encryption.

\section{Conclusion}
In conclusion the physics of quantum computers allow for superior computation to classical computers, but they come with the trade-off of increased manufacturing costs, increased power consumption and increased space requirements compared to a classical computer
\\
\\
Due to the increased popularity and reduced complexity of classical computers compared to quantum computers, how they work is much more widely known. This allows for far more people to be able to work on them, making it a better choice for companies to use them. 
\\
\\
Quantum algorithms allow for data to be processed much faster than classical algorithms, however there is currently only a few available algorithms, meaning the utility of quantum computing is not yet fully realised. Quantum algorithms also are only superior to classical algorithms when processing large values, meaning that they wouldn't provide any noticeable benefit to domestic consumers and may even perform worse than classical computers, whose main use is lots of short processes.
\\
\\
Currently quantum computers are only experimental, but some large companies, such as NASA, have bought a quantum computer in order to see what practical uses they can offer. However, companies such as Google may soon be able to find a practical use for them, for example, improving the speed of their search results, meaning they would be able to reduce the number of traditional servers, saving both power and space. 
\\
Without any breakthrough development in cooling technology, or a way to operate a quantum computer at room temperature, it is unlikely that quantum computers will be used directly by consumers in the foreseeable future. Instead they will be used as a replacement for supercomputers due to their reduced space and power requirements for the same performance. Therefore the only interaction consumers will have with quantum computers will be over the internet. This is because they have the power to increase the speed and accuracy of image recognition, search speed and may also revolutionise the encryption industry. 
\\
\\
I believe I have achieved what I have set out to achieve as I explored the utility of quantum computers and their limitations. I think overall quantum computers could be better than supercomputers but it is unlikely they will be used, widely in the consumer market without further advances in technology.

\newpage

\printbibliography

\end{document}

### 2018-01-30 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
Further Maths+EPQ Update

--- 2018-01-29 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
@@
 \documentclass{article}[18pt]
+\usepackage[dvipsnames]{xcolor}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{pgfplots}
+\usepackage{tabularx}
+
 \usepgfplotslibrary{fillbetween}
@@
 \usepackage{cancel}
+
+\setcounter{secnumdepth}{4}
+\titleformat{\paragraph}
+{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
+\titlespacing*{\paragraph}
+{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
+\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
+\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
+\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
 
@@
 \subsection{Dividing}
+\subsubsection{Trigonometric form}
+$$\frac{Z_1}{Z_2}=\frac{r_1(\cos\theta_1+i\sin\theta_1)}{r_2(\cos\theta_2+i\sin\theta_2)}$$
+Multiply by the complex conjugate 
+$$\frac{Z_1}{Z_2}=\frac{r_1(\cos\theta_1+i\sin\theta_1)}{r_2(\cos\theta_2+i\sin\theta_2)}\times\frac{\cos\theta_2-i\sin\theta_2}{\cos\theta_2-i\sin\theta_2}$$
+Expand
+$$\frac{Z_1}{Z_2}=\frac{r_1}{r_2}\times\frac{cos\theta_1\cos\theta_2-i\cos\theta_1\sin\theta_2+i\sin\theta_1\cos\theta_2+\sin\theta_1\sin\theta_2}{\cos^2\theta_2-i\cos\theta_2\sin\theta_2+i\sin\theta_2\cos\theta_2+\sin^2\theta_2}$$
+Simplify
+$$\frac{Z_1}{Z_2}=\frac{r_1}{r_2}\times\Big(\cos(\theta_1-\theta_2)+i\sin(\theta_1-\theta_2)\Big)$$
+\subsubsection{Exponential form}
+$$\mathlarger{\frac{Z_1}{Z_2}=\frac{r_1}{r_2}\times\frac{e^{i\theta_1}}{e^{i\theta_2}}}$$
+$$\mathlarger{\frac{Z_1}{Z_2}=\frac{r_1}{r_2}\times e^{i(\theta_1-\theta_2)}}$$
+\subsection{Comparison}
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+Multiplying&Dividing\\
+\hline	
+Multiply modulus, add arguments&Divide modulus, subtract arguments\\
+\hline
+\end{tabularx}
+\newpage
+\section{De Moivre's Theorem}
+\textcolor{red}{$$\mathlarger{[r(\cos\theta+i\sin\theta)]^n=r^n(\cos(n\theta)+i\sin(n\theta))}$$}
+\subsection{Positive proof}
+Prove true for n=1
+$$r(\cos\theta+i\sin\theta)=r(\cos\theta+i\sin\theta)$$
+\begin{center}
+True for n=1
+\end{center}
+Assume true for n=k
+$$\mathlarger{[r(\cos\theta+i\sin\theta)]^k=r^k(\cos(k\theta)+i\sin(k\theta))}$$
+Prove true for n=k+1
+$$[r(\cos\theta+i\sin\theta)]^{k+1}$$
+$$[r(\cos\theta+i\sin\theta)]^k\times(r(\cos\theta+i\sin\theta))^1$$
+$$r^k(\cos(k\theta)+i\sin(k\theta))\times r(\cos\theta+i\sin\theta)$$
+$$r^kr(\cos(k\theta+\theta)+i\sin(k\theta+\theta))$$
+$$r^{k+1}(\cos((k+1)\theta)+i\sin((k+1)\theta))$$
+True
+\subsection{Negative proof}
+n=-m
+$$[r(\cos\theta+i\sin\theta)]^{-m}$$
+Multiply by complex conjugate
+$$\frac{1}{[r(\cos\theta+i\sin\theta)]^m}\times\frac{[r(\cos\theta-i\sin\theta)]^m}{[r(\cos\theta-i\sin\theta)]^m}$$
+Apply positive De Moivre's Theorem
+$$\mathlarger{\frac{r^m(\cos(m\theta)-i\sin(m\theta))}{r^m(\cos(m\theta)+i\sin(m\theta))\times r^m(\cos(m\theta)-i\sin(m\theta))}}$$
+Simplify and expand
+$$\mathlarger{\frac{\cos(m\theta)-i\sin(m\theta)}{r^m(\cos^2m\theta-i\cos m\theta\sin m\theta+i\cos m\theta\sin m\theta+\sin^2m\theta}}$$
+Simplify
+$$\frac{\cos m\theta-i\sin m\theta}{r^m}=r^{-m}(\cos m\theta-i\sin m\theta)$$
+Rewrite
+$$r^{-m}(\cos(-m\theta)+i\sin(-m\theta))$$
+Replace -m with n
+$$r^n(\cos(n\theta)+i\sin(n\theta))$$
+\newpage
+\subsection{Applying De Moivres' Theorem}
+We can use the binomial expansion along with De Moivre's theorem to rewrite trigonometric expressions. This can be useful when integrating etc.
+\subsubsection{Example 1}
+\textit{Rewrite $\cos5\theta$ in powers of $\cos\theta$}
+$$(\cos\theta+i\sin\theta)^5$$
+Apply DM theorem
+$$\cos5\theta+i\sin5\theta$$
+Apply the binomial expansion to the initial expression
+$$\cos^5\theta+5\cos^4\theta i\sin\theta+10\cos^3\theta(i\sin\theta)^2+10\cos^2\theta(i\sin\theta)^3+5\cos\theta(i\sin\theta)^4+(i\sin\theta)^5$$
+Simplify
+$$\cos^5\theta+5i\cos^4\theta\sin\theta-10\cos^3\theta\sin^2\theta-10i\cos^2\theta\sin^3\theta+5\cos\theta\sin^4\theta+i\sin^5\theta$$
+Equate the real parts of this to the real parts of the result from DM theorem
+$$\cos5\theta=\cos^5\theta-10\cos^3\theta\sin^2\theta+5\cos\theta\sin^4\theta$$
+Replace sin terms with cos
+$$\cos5\theta=\cos^5\theta-10\cos^3\theta(1-\cos^2\theta)+5\cos\theta(1-\cos^2\theta)^2$$
+Simplify
+$$\cos5\theta=\cos^5\theta-10\cos^3\theta+10\cos^5\theta+5\cos\theta(1-\cos\cos^2\theta+cos^4\theta)$$
+Simplify further
+$$\cos5\theta=\cos^5\theta-10\cos^3\theta+10\cos^5\theta+5\cos\theta-10\cos63\theta+5\cos^5\theta$$
+Collect terms
+$$\cos5\theta=16\cos^5\theta-20\cos^3\theta+5\cos\theta$$
+\newpage
+\subsubsection{Z formulas}
+If $z=\cos\theta+i\sin\theta$
+$$z+\frac{1}{z}=2\cos\theta$$
+$$z-\frac{1}{z}=2i\sin\theta$$
+$$z^n+\frac{1}{z^n}=2\cos n\theta$$
+$$z^n-\frac{1}{z^n}=2i\sin n\theta$$
+\paragraph{Example}
+\textit{Express $\cos^5\theta$ in the form $a\cos5\theta+b\cos3\theta+c\cos\theta$}
+Create the situation using the z formulas
+$$\Bigg(z+\frac{1}{z}\Bigg)^5=(2\cos\theta)^5=32\cos^5\theta$$ 
+Expand using the binomial
+$$\textcolor{red}{z^5}+\textcolor{Green}{5z^4\times\frac{1}{z}}+\textcolor{Plum}{10z^3\times\frac{1}{z^2}}+\textcolor{Plum}{10z^2\times\frac{1}{z^3}}+\textcolor{Green}{5z\times\frac{1}{z^4}}+\textcolor{red}{\frac{1}{z^5}}$$
+Combine like coloured term using z formula
+$$32\cos^5\theta=\textcolor{red}{2\cos\theta}+\textcolor{Green}{10\cos3\theta}+\textcolor{Plum}{20\cos\theta}$$
+$$\cos^5\theta=\frac{\cos\theta}{16}+\frac{5\cos3\theta}{16}+\frac{5\cos\theta}{8}$$
 

### 2018-01-30 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
Maths Notes Update

@@
 $$\mathlarger{y=e^{3x}(A\cos(5x)+B\sin(5x))}$$
+\section{Solving \nth{2} ODE = f(x)}
+Of the type:
+$$a\frac{d^2y}{dx^2}+b\frac{dy}{dx}+cy=f(x)$$
+There are set forms of f(x)\\
+\\
+The LHS will be solved in the standard way and the general solution of the LHS will be called the \textbf{complementary solution} (CS)\\
+\\
+Solving the RHS will give us a \textbf{particular integral} (PI)
+\begin{center}
+Full general solution=Complementary function+Particular integral
+\end{center}
+\subsection{Standard forms of f(x)}
+$f(x)=\lambda$\\
+$f(x)=\lambda+\mu x$\\
+$f(x)=\lambda+\mu x+\nu x^2$\\
+$f(x)=ke^{px}$\\
+$f(x)=m\cos\omega x$\\
+$f(x)=m\sin\omega x$\\
+$f(x)=m\cos\omega x\pm n\sin\omega x$
+\newpage
+\subsection{Examples}
+$$\frac{d^2y}{dx^2}-5\frac{dy}{dx}+6y=f(x)$$
+Find complementary function
+$$m^2-5m+6=0$$
+$$m=2 \quad m=2$$
+$$\textrm{Complementary funtion}=Ae^{3x}+Be^{2x}$$
+\subsubsection{\nth{2} ODE=$\lambda$}
+$f(x)=3$\\
+Start with $y=\lambda$
+$$y=\lambda$$
+$$\frac{dy}{dx}=0$$
+$$\frac{d^2y}{dx^2}=0$$
+Substitute values into LHS
+$$0-5\times0+6\lambda=3$$
+$$\lambda=\frac{1}{2}$$
+Add Complementary function to particular integral
+$$y=Ae^{3x}+Be^{2x}+\frac{1}{2}$$
+\subsubsection{\nth{2} ODE=$\lambda+\mu x$}
+$f(x)=2x$\\
+Start with $y=\lambda+\mu x$
+$$y=\lambda+\mu x$$
+$$\frac{dy}{dx}=\mu$$
+$$\frac{d^2y}{dx^2}=0$$
+Substitute into LHS
+$$0-5\mu+6(\lambda+\mu x)=2x$$
+Equate x terms
+$$6\mu x=2x$$
+$$\mu=\frac{1}{3}$$
+Equate constant terms
+$$-\frac{5}{3}+6\lambda=0$$
+$$6\lambda=\frac{5}{3}$$
+$$\lambda=\frac{5}{18}$$
+Substitute into form for the particular integral
+$$y=\frac{1}{3}x+\frac{5}{18}$$
+Add the PI and CF to find the general solution
+$$y=Ae^{3x}+Be^{2x}+\frac{1}{3}x+\frac{5}{18}$$
+\newpage
+\subsubsection{\nth{2} ODE=$\lambda+\mu x+\nu x^2$}
+$f(x)=3x^2$\\
+Start with $y=\lambda+\mu x+\nu x^2$
+$$y=\lambda+\mu x+\nu x^2$$
+$$\frac{dy}{dx}=\mu+2\nu x$$
+$$\frac{d^2y}{dx^2}=2\nu$$
+Substitute into the LHS
+$$2\nu-5(\mu+2\nu x)+6(\lambda+\mu x+\nu x^2)=3x^2$$
+Equate $x^2$ terms
+$$6\nu=3 \quad \nu=\frac{1}{2}$$
+Equate x terms
+$$-10\times\frac{1}{2}\times x+6\mu x=0$$
+$$-5+6\mu=0$$
+$$\mu=\frac{5}{6}$$
+Equate constant coefficients
+$$1-5\times\frac{5}{6}+6\lambda=0$$
+$$6\lambda=\frac{19}{6}$$
+$$\lambda=\frac{19}{36}$$
+Substitute into the particular integral form
+$$y=\frac{1}{2}x^2+\frac{5}{6}x+\frac{19}{36}$$
+Add CF and PI to get the general solution
+$$y=Ae^{3x}+Be^{2x}+\frac{1}{2}x^2+\frac{5}{6}x+\frac{19}{36}$$
+
 \end{document}

### 2018-01-31 Physics Notes/Turning Points/Electrons/Electrons.tex
Notes Update

@@
 \usepackage{textcomp}
+\usepackage{pgfplots}
 \titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
@@
 \lhead{A Level Physics - Turning Points}
+
+\usepackage{tikz}
+\usetikzlibrary{scopes}
+
+\usepackage{mathtools}
+
+\newtagform{brackets}{[}{]}
+\usetagform{brackets}
+
 \begin{document}
@@
 This will produce a discrete spectrum which is seen in the positive column.
+\end{itemize}
 \section{Thermionic emission}
@@
 $$eV_a=\frac{1}{2}mv^2 \quad \frac{e}{m}=\frac{\frac{1}{2}v^2}{v_a}$$
-\end{itemize}
 2. Electrons pass through an electric field (Field strength, E) and are deflected.\\
@@
 $$\frac{e}{m}=\frac{2V_a}{(BR)^2}$$
+\newpage
+\section{Milikan's experiment}
+\begin{figure}[h]
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+\begin{tikzpicture}[
+    force/.style={>=latex,draw=black,fill=black},
+    m/.style={circle,draw=black,fill=white,radius=0.3cm,thin},
+]
+    \node[m] (m) {};
+    {[force,->]
+        \draw (m.north) -- ++(0,1) node[above] {Upthrust+Viscous drag};
+        \draw (m.south) -- ++(0,-1) node[below] {Weight};
+    }
+\end{tikzpicture}
+        \caption{No electric field}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+\begin{tikzpicture}[
+    force/.style={>=latex,draw=black,fill=black},
+    m/.style={circle,draw=black,fill=white,radius=0.3cm,thin},
+]
+    \node[m] (m) {};
+    {[force,->]
+        \draw (m.north) -- ++(0,1) node[above] {Upthrust+Electric force};
+        \draw (m.south) -- ++(0,-1) node[below] {Weight};
+    }
+\end{tikzpicture}    
+        \caption{Electric field}
+    \end{minipage}
+\end{figure}
+\subsection{With electric field}
+$$\textrm{Electric field}=\frac{QV}{d}$$
+$$\textrm{Weight}=mg$$
+$$\frac{QV}{d}=mg$$
+\subsection{Without electric field}
+$$F_D=6\pi r\eta v$$
+$$\textrm{Weight}=mg$$
+\begin{center}
+Mass=Density$\times$Volume
+$$\textrm{Mass}=\frac{4}{3}\pi r^3\rho$$
+$$6\pi r\eta v=\frac{4}{3}\pi r^3\rho g$$
+$$r^2=\frac{9\eta v}{2\rho g}$$
+\end{center}
+\subsection{Significance of results}
+These results were significant because it introduced the idea of quantisation of charge
+
 \end{document}

### 2018-01-31 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
Notes Update

@@
 \rfoot{Page \thepage}
+
+\setcounter{secnumdepth}{4}
+\titleformat{\paragraph}
+{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
+\titlespacing*{\paragraph}
+{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
+\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
+\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
+\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
+
+\usepackage{mathtools}
+
+\newtagform{brackets}{[}{]}
+\usetagform{brackets}
 
@@
 $$y=Ae^{3x}+Be^{2x}+\frac{1}{2}x^2+\frac{5}{6}x+\frac{19}{36}$$
+\newpage
+\subsubsection{Trigonometric f(x)}
+General forms:\\
+If $f(x)=m\cos\omega x$
+$$PI: \ y=P\cos\omega x+Q\sin\omega x$$
+If $f(x)=n\sin\omega x$
+$$PI: \ y=P\cos\omega x+Q\sin\omega x$$
+If $f(x)=m\cos\omega x\pm n\sin\omega x$
+$$PI: \ y=P\cos\omega x+Q\sin\omega x$$
+\paragraph{$f(x)=m\sin\omega x$ or $n\sin\omega x$}
+$f(x)=13\sin4x$
+$$PI: \ y=P\cos\omega x+Q\sin\omega x$$
+$$\frac{dy}{dx}=-\omega P\sin\omega x+\omega Q\cos\omega x$$
+$$\frac{d^2y}{dx^2}=-\omega^2P\cos\omega x-\omega^2Q\sin\omega x$$
+$$\textcolor{red}{\frac{d^2y}{dx^2}-5\frac{dy}{dx}+6y=13\sin3x}$$
+Substitute into LHS
+$$-\omega^2P\cos\omega x-\omega^2Q\sin\omega x-5(-\omega P\sin\omega x+\omega Q\cos\omega x)+6(P\cos\omega x+Q\sin\omega x)=13\sin3x$$
+Equate cos terms
+$$-\omega^2 P\cos\omega x-5\omega Q\cos\omega x+6P\cos\omega x=0$$
+Substitute $\omega=3$ and divide by $\cos3x$
+$$-9P-15Q+6P=0$$
+Simplify
+\begin{equation}\label{eq:cos}
+-3P-15Q=0
+\end{equation}
+Equate $\sin$ terms
+$$-\omega^2Q\sin\omega x+5\omega P\sin\omega x+6Q\sin\omega x=13\sin3x$$
+Substitute $\omega=3$ and divide by $\sin3x$
+$$-9Q+15P+6Q=13$$
+Simplify
+\begin{equation}\label{eq:sin}
+15P-3Q=13
+\end{equation}
+Multiply \eqref{eq:cos} by 5
+$$-15P-75Q=0$$
+Add the multiplied \eqref{eq:cos} and \eqref{eq:sin}
+$$-78Q=13$$
+Simplify
+$$Q=-\frac{1}{6}$$
+Substitute to find P
+$$15\times\frac{1}{6}=-3P \quad P=\frac{5}{6}$$
+Substitute and add to the CF to find the PI
+$$y=Ae^{3x}+Be^{2x}+\frac{5}{6}\cos3x-\frac{1}{6}\sin3x$$
 

### 2018-02-04 Physics Notes/Turning Points/Electrons/Electrons.tex
Notes Update
Physics Notes Update

@@
 1. Thermionic electrons are accelerated through a p.d. $V_a$ and gain kinetic energy:\\
-$$eV_a=\frac{1}{2}mv^2 \quad \frac{e}{m}=\frac{\frac{1}{2}v^2}{v_a}$$
+$$eV_a=\frac{1}{2}mv^2 \quad \frac{e}{m}=\frac{\frac{1}{2}v^2}{\textrm{v}_a}$$
 2. Electrons pass through an electric field (Field strength, E) and are deflected.\\
@@
 $$Bev=eE \quad v=\frac{E}{B}$$
-$$\frac{e}{m}=\frac{1}{2v_a}\Bigg(\frac{E}{B}\Bigg)^2$$
+$$\frac{e}{m}=\frac{1}{2\textrm{v}_a}\Bigg(\frac{E}{B}\Bigg)^2$$
 \subsection{Method 2}
@@
 $$\textrm{Magnetic force   F=Bev}$$
-$$\textrm{This is the centripetal force} \frac{mv^2}{R}$$
+$$\textrm{This is the centripetal force,} \quad \frac{mv^2}{R}$$
 $$\frac{e}{m}=\frac{v}{BR} \quad \quad v=\frac{e}{m}BR$$
@@
 These results were significant because it introduced the idea of quantisation of charge
-
+\newpage
+\begin{center}
+\underline{\huge Questions from past papers}
+\end{center}
+\section{Milikan's experiment}
+\textit{Why does an oil droplet reach a constant speed when the plate voltage is switched off in Milikan's experiment}
+\begin{center}
+Weight pulls droplet down, reaches terminal velocity
+\end{center}
+$ $\\
+\textit{Derive $r^2=\frac{9\eta v}{2\rho g}$}
+$$F_D=6\pi r\eta v$$
+$$\textrm{Weight}=mg$$
+\begin{center}
+Mass=Density$\times$Volume
+$$\textrm{Mass}=\frac{4}{3}\pi r^3\rho$$
+$$6\pi r\eta v=\frac{4}{3}\pi r^3\rho g$$
+$$r^2=\frac{9\eta v}{2\rho g}$$
+\end{center}
+$ $\\
+\textit{Determine the mass or radius of a droplet in Milikan's experiment}\\
+$$\textrm{Speed}=\frac{\textrm{Distance}}{\textrm{Time}}$$
+$$r=\sqrt{\frac{9\eta v}{2\rho g}}$$
+$$m=\frac{4}{3}\pi r^3\rho$$
+$ $\\
+\textit{Charge from mass}
+$$Q=\frac{mgd}{V}$$
+$ $\\
+\textit{Determine the sign of the charge carried by a stationary droplet in Milikan's experiment}
+\begin{center}
+Opposite to the charge of the top plate to ensure forces are balanced
+\end{center}
+$ $\\
+\textit{Comment on the significance of a charge calculated in Milikan's experiment}
+\begin{center}
+It will be a multiple of the charge of an electron
+\end{center}
+\section{Electron Guns}
+\textit{Speed of electrons from the voltage they are accelerated through a Voltage}\\
+$$\frac{1}{2}mv^2=eV$$
+$$v=\sqrt{\frac{eV}{\frac{1}{2}m}}$$
+$ $\\
+\textit{Why are there two power supplies in an electron gun?}
+\begin{center}
+One to cause thermionic emission, one to accelerate the electrons
+\end{center}
+\section{Electrons in magnetic fields}
+\textit{Does the speed of an electron change in a magnetic field}
+\begin{center}
+No as force is perpendicular to velocity, meaning no work is done
+\end{center}
+$ $\\
+\textit{Specific charge from radius of curvature, magnetic flux density and accelerating voltage}
+$$\frac{1}{2}mv^2=eV$$
+$$\frac{mv^2}{r}=BeV$$
+$$\frac{e}{m}=\frac{2V}{B^2r^2}$$
+$ $\\
+\textit{What is the velocity of an electron when magnetic and electric fields are equal}
+$$EQ=BQv$$
+$$v=\frac{E}{B}$$
+$ $\\
+\textit{Velocity of electrons in a magnetic field}
+$$\frac{mv^2}{r}=Bev$$
+$$v=\frac{Ber}{m}$$
+$ $\\
+\textit{Why do electrons undergo circular motion in a magnetic field}
+\begin{center}
+Force perpendicular to motion, does not change speed, causes direction of motion to change
+\end{center}
+$ $\\
+\section{Electrons in electric fields}
+\textit{Draw the path of an electron beam in an electric field}
+\begin{center}
+Curves up while between plates, straight line continuing up after leaving plates
+\end{center}
+$ $\\
+\textit{Specific charge of an electron from curving in an electric field}
+$$ma=\frac{eV}{d}$$
+\begin{center}
+Calculate acceleration using SUVAT
+\end{center}
+$$\frac{ad}{V}=\frac{e}{m}$$
+$ $\\
+\textit{Specific charge from electric field strength}
+$$EQ=mg$$
+$$\frac{Q}{m}=\frac{g}{E}$$
+$ $\\
+\textit{Why does an electron beam in an electric field curve at an increasing angle to the horizontal}
+\begin{center}
+The electrons feel a constant force, meaning they have constant vertical acceleration, causing the vertical component of the velocity to increase, while the horizontal component is constant, causing an increasing angle.
+\end{center}
+\section{Thermionic emission}
+\textit{Explain thermionic emission}
+\begin{center}
+The current heats the wire, meaning the electrons in the filament gain sufficient k.e. to leave the filament
+\end{center}
+$ $\\
+\textit{Why must the filament be in an evacuated tube for thermionic emission}
+\begin{center}
+So that there are no collisions
+\end{center}
+$ $\\
+\textit{Why is thermionic emission negligible when the filament current is too low}
+\begin{center}
+If the current is too low there is little heating effect, meaning that the electrons don't gain enough kinetic energy to be released
+\end{center}
+\section{Discharge Tubes}
+\textit{Why is light emitted in a Crooke's tube}
+\begin{center}
+Electrons present, collide with atoms, excitation occurs, emit photon as they return to the ground state
+\end{center}
+$ $\\
+\textit{Why can a glow not be seen until the pressure is low enough in a Discharge tube}
+\begin{center}
+The electrons can't gain enough kinetic energy as there are too many molecules present
+\end{center}
+$ $\\
 \end{document}

### 2018-02-05 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
Notes update

@@
 $$\cos^5\theta=\frac{\cos\theta}{16}+\frac{5\cos3\theta}{16}+\frac{5\cos\theta}{8}$$
-
+\section{Solving complex equations}
+For any complex number, we generally define the argument to be between $-\pi$ and $\pi$. However we can add multiples of $2\pi$ to the argument to get equivalent answers.\\
+\\
+We shall use this fact to find all solutions to complex equations.\\
+\\
+Note: The number of solutions is equal to the order of the equation.
+\subsection{Example}
+\textit{Solve:}\\
+$z^5=i$
+$$r=1 \quad \theta=\frac{\theta}{2}$$
+$$z^5=\cos(\frac{\pi}{2}+2k\pi)+i\sin(\frac{\pi}{2}+2k\pi)$$
+$$z=\cos\Bigg(\frac{\frac{\pi}{2}+2k\pi}{5}
+\Bigg)+i\sin\Bigg(\frac{\frac{\pi}{2}+2k\pi}{5}\Bigg)$$
+5 Solutions: k=-2,-1,0,1,2\\
+$k=-2 \quad z=-0.588-0.809i$\\
+$k=-1 \quad z=0.588-0.809i$\\
+$k=0 \quad z=0.951+0.309i$\\
+$k=1 \quad z=i$\\
+$k=2 \quad z=-0.951+0.309i$
 \end{document}

### 2018-02-06 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
Notes update

@@
 $$y=Ae^{3x}+Be^{2x}+\frac{5}{6}\cos3x-\frac{1}{6}\sin3x$$
-
+\newpage
+\section{Clash of terms between CF and PI}
+\textit{Solve:}
+$$\frac{d^2y}{dx^2}-5\frac{dy}{dx}+6y=e^{2x}$$
+Find the Complementary function
+$$m^2-5m+6=0$$
+$$CF: \ y=Ae^{3x}+Be^{2x}$$
+Here there will be a clash of terms between the CF and the PI so a different PI must be used, this will be given to you.
+$$\textrm{Use PI} \ y=\lambda xe^{2x}$$
+Differentiate twice
+$$\frac{dy}{dx}=\lambda e^{2x}+2\lambda xe^{2x}$$
+$$\frac{d^2y}{dx^2}=2\lambda e^{2x}+2\lambda e^{2x}+4\lambda xe^{2x}$$
+Substitute 
+$$2\lambda e^{2x}+2\lambda e^{2x}+4\lambda xe^{2x}-5(\lambda e^{2x}+2\lambda xe^{2x})+6\lambda xe^{2x}=e^{2x}$$
+$$\lambda=-1$$
+Substitute
+$$PI: \ y=-xe^{2x}$$
+\section{Applications of boundary conditions}
+If DE is in $\frac{d^2y}{dx^2}$ form then the numerical values for x,y and $\frac{dy}{dx}$ will be given for a value of x.\\
+\\
+If (as is common in exams) DE is in $\frac{d^2x}{dt^2}$ form then numerical values of x,t and $\frac{dx}{dt}$ will be given for a value of x.\\
+\\
+Used to find A and B in the CF. This gives a particular solution.
 \end{document}

### 2018-02-06 Maths Notes/Statistics/S3/Estimation/Estimation.tex
Notes update

@@
 \rfoot{Page \thepage}
+\pgfmathdeclarefunction{gauss}{2}{%
+  \pgfmathparse{1/(#2*sqrt(2*pi))*exp(-((x-#1)^2)/(2*#2^2))}%
+}
 
@@
 For this, the sample size must be greater than 50
+\section{Confidence intervals}
+A 95\% confidence interval is two values in which there is a probability of 0.95 that it will contain the population mean.\\
+\begin{tikzpicture}
+\begin{axis}[
+  no markers, domain=0:8, samples=100,
+  every axis y label/.style={at=(current axis.above origin),anchor=south},
+  every axis x label/.style={at=(current axis.right of origin),anchor=west},
+  height=5cm, width=12cm,
+  xtick={2,6},xticklabels={0.025,0.025}, ytick=\empty,
+  enlargelimits=false, clip=false,   ]
+  \addplot [fill=cyan!20, draw=none, domain=0:2] {gauss(4,1)} \closedcycle;
+  \addplot [fill=cyan!20, draw=none, domain=6:8] {gauss(4,1)} \closedcycle;
+  \addplot [very thick,cyan!50!black] {gauss(4,1)};
+  \node[] at (axis cs: 4,0.1) {95\%};
+\end{axis}
+\end{tikzpicture}
+\\
+Look up the value of one of the tails on the percentage points table and substitute into the formula.\\
+For example:\\
+At a 95\% confidence interval each of the tails is 0.025 and the corresponding z value is 1.96.\\
+$$\overline{x}\pm1.96\times\frac{\sigma}{\sqrt{n}}$$
+
 \end{document}

### 2018-02-07 Maths Notes/Statistics/S3/Estimation/Estimation.tex
Notes Update

@@
 $$\overline{x}\pm1.96\times\frac{\sigma}{\sqrt{n}}$$
+\section{Hypothesis testing}
+The test statistic for the population mean $\mu$ is $Z=\dfrac{X-\mu}{\frac{\sigma}{\sqrt{n}}}$\\
+\\
+A hypothesis test can be done quicker by finding the critical values from the percentage points table.
+\subsection{Example}
+$\mu=0.58 \ \sigma=0.015$\\
+Measured\\
+$n=50 \ \mu=0.577 \ \sigma=0.015$\\
+\\
+$H_0: \mu=0.50$\\
+$H_1: \mu\neq0.58$\\
+$$\overline{D}\sim N(0.58,\frac{0.015^2}{50})$$
+$$Z=\frac{0.577-0.58}{\sqrt{\frac{0.015^2}{50}}}=-1.41$$
+At 0.5\%  per level Z=2.5758
+$$-1.41>-2.5758$$
+Not in critical region so not significant, no evidence to reject $H_0$, the diameter of the bolts is not changed.
 

### 2018-02-07 Physics Notes/Nuclear Physics/Radioactivity/Radioactivity.tex
Notes Update

@@
 \\
-The dead time of the tube, the time taken to regain its non conducting state after an ionising particle enters it, is typically of the order of 0.2ms.
-\newpage
+The dead time of the tube, the time taken to regain its non conducting state after an ionising particle enters it, is typically of the order of 0.2ms.\\
+\section{Radioactive decay}
 \begin{tabularx}{\textwidth}{|c|X|X|X|}
@@
 \end{tabularx}
+\newpage
+\subsection{$\alpha$ decay}
 

### 2018-02-07 Physics Notes/Nuclear Physics/Radioactivity/Radioactivity.tex
Notes Update

--- 2018-01-28 Physics Notes/Nuclear Physics/Radioactivity/Radioactivity.tex
@@
 $$d=\frac{D}{10,000}$$
+\newpage
+\section{Radioactive materials}
+\subsection{Sources of background radiation by most common}
+\begin{enumerate}
+\item Air (e.g. radon gas)
+\item Medical
+\item Ground and buildings
+\item Food and drink
+\item Cosmic rays
+\item Nuclear weapons
+\item Air travel
+\item Nuclear power
+\end{enumerate}
+\subsection{Geiger M\"{u}ller tube}
+\includegraphics[width=10cm]{geiger.png}\\
+When a particle of ionising radiation enters the tube, the particle ionises the gas atoms along its track.
+The negative ions are attracted to the rod and the positive ions to the wall.
+These ions cause further ionisation, creating enough ions for a current to flow.
+A pulse of charge passes round the circuit through resistor R, causing the voltage pulse across R which is recorded as a single count by the pulse counter\\
+\\
+The dead time of the tube, the time taken to regain its non conducting state after an ionising particle enters it, is typically of the order of 0.2ms.\\
+\section{Radioactive decay}
+\begin{tabularx}{\textwidth}{|c|X|X|X|}
+\hline
+&Alpha&Beta&Gamma\\
+\hline
+Nature&2 Protons+2 Neutrons&High speed electron or positron&High energy photon\\
+\hline
+Range&Up to 10cm&Up to 1m&Infinite\\
+\hline 
+Deflection in a magnetic field&Deflected&Opposite direction to $\alpha$ particles and more easily deflected&Not deflected\\
+\hline
+Absorption&Paper&Aluminium&Lead \\
+\hline
+Ionisation&$10^4$ ions per mm&100 ions per mm&Very weak ionising effect\\
+\hline
+Energy of each particle&Constant for a given source&Varies up to a maximum for a given source&Constant for a given source\\
+\hline
+\end{tabularx}
+\newpage
+\subsection{$\alpha$ Decay}
+$$^{238}_{92}U\rightarrow^4_2\alpha+^{234}_{90}Th$$
+\subsection{$\beta^-$ Decay}
+Neutron to proton and $\beta^-$ particle
+$$^{14}_6C\rightarrow^0_{-1}\beta+^{14}_7N$$
+\subsection{$\beta^+$ Decay}
+Proton to neutron and $\beta^+$
+\subsection{Electron Capture}
+Proton+Electron$\rightarrow$ Neutron
+\subsection{Gamma Emission}
+No change to the structure of the nucleus.\\
+Often follows alpha or beta emission. Daughter nucleus can be in an excited state. It emits gamma radiation as it returns to its ground state.
+\subsection{NZ Plot}
+\includegraphics[width=5cm]{nz_plot.png} 
+\subsection{Half life}
+The half life of a radioactive substance is the time taken for half the atoms in the sample to decay.
+$$\textrm{The rate of decay}\propto\textrm{The number of nuclei left}$$
+$$-\frac{\Delta N}{\Delta t}\propto N$$
+The LHS of this equation is called the activity and has units Bq
+$$-\frac{\Delta N}{\Delta t}=\lambda N$$
+The solution to this equation
+$$N=N_0e^{-\lambda t}$$
+This can also be written as:
+$$\frac{N}{N_0}=e^{-\lambda t}$$
+\subsubsection{Linking the formula to half life}
+After a time, t=$T_{\frac{1}{2}}$ the fraction remaining is 0.5.
+$$0.5=e^{-\lambda t}$$
+$$ln(2)=\lambda t$$
+$$t=\frac{\ln(2)}{\lambda}$$
+$\lambda t$ is a "Pure Number". As long as the same units are used for both, you can use any unit of time.\\
+\\
+$\lambda$ is the fraction of nuclei decaying per unit time or the probability of an individual nucleus decaying per second.\\
+As N is proportional to Activity, Mass and Count Rate N can be replaced with any of these in the formula.
 \end{document}

### 2018-02-07 Maths Notes/Statistics/S2/Exam Questions/CRVs/CRV Exam Questions.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge CRV Exam Questions}
\end{center}
\section{Averages}
\subsection{Mean}
Use the formula on the data sheet:
$$\mu=\int_a^bxf(x) dx$$
Where a is the start of the range and b is the end.\\
If the variable has multiple ranges add all the means together to find the total mean.
\subsection{Variance}
Use the formula on the data sheet:
$$Var(X)=\int_a^b x^2f(x) \ dx-\mu^2$$
Where a is the start of the range and b is the end.\\
Find the mean using the method above

\subsection{Median}
To find the median set F(x) to 0.5. To do this you may need to convert the P.D.F to the C.D.F.\\
If the C.D.F has different equations for different ranges substitute in for any range. If the result is outside the range try a different range.
\subsubsection{Example}
{\renewcommand{\arraystretch}{1.5}
$
  F(x)=\left\{
  \begin{array}{@{}ll@{}}
    0, & \ x<0\\
    \frac{1}{4}x^2, &  0\leqslant x \leqslant 1\\
    \frac{1}{20}x^4+\frac{1}{5}, &  1\leqslant x \leqslant 2\\
    1 & x>2
  \end{array}\right.
$}\\
Testing between 0 and 1:
$$\frac{1}{4}x^2=0.5$$
$$x=1.41$$
As x is greater than 1 move to the next range
$$\frac{1}{20}x^4+\frac{1}{5}=0.5$$
$$x=1.57$$
This is in the range so is correct
\subsection{Mode}
With difficult problems differentiate f(x) and set to zero. Most will be able to be solved with logic though
\section{Conversions between the P.D.F and C.D.F}
\subsection{P.D.F to C.D.F}
To convert the P.D.F to the C.D.F it must be integrated.\\
This integration is done as normal but needs no +C.\\
If there are multiple ranges add the maximum value of the previous range to find the C.D.F.
\subsubsection{Example}
{\renewcommand{\arraystretch}{1.5}
$
  f(x)=\left\{
  \begin{array}{@{}ll@{}}
    \frac{1}{2}x, & \ 0\leqslant x\leqslant1\\
    \frac{1}{5}x^3, &  1\leqslant x \leqslant 2\\
    0 & \textrm{Otherwise}
  \end{array}\right.
$}\\

\end{document}

### 2018-02-08 Maths Notes/Statistics/S2/Exam Questions/CRVs/CRV Exam Questions.tex
Notes Update
S2 CRV Notes

@@
 With difficult problems differentiate f(x) and set to zero. Most will be able to be solved with logic though
+\newpage
 \section{Conversions between the P.D.F and C.D.F}
@@
 $}\\
+\\
+Start by integrating the first range
+$$\int_0^x \frac{1}{2}x \ dx=\frac{1}{4}x^2$$
+Integrate the second range, remembering to add the area under the first range.
+$$\int_1^x \frac{1}{5}x^3 dx+\int_0^1\frac{1}{2}x \ dx=\frac{1}{20}x^4+\frac{1}{5}$$
+Write this in function form\\
+\\
+{\renewcommand{\arraystretch}{1.5}
+$
+  F(x)=\left\{
+  \begin{array}{@{}ll@{}}
+  0 & x<0\\
+    \frac{1}{4}x^2, & \ 0\leqslant x\leqslant1\\
+    \frac{1}{20}x^4+\frac{1}{5}, &  1\leqslant x \leqslant 2\\
+    1 & x>2
+  \end{array}\right.
+$}\\
+\subsection{C.D.F to P.D.F}
+{\renewcommand{\arraystretch}{1.5}
+$
+  F(x)=\left\{
+  \begin{array}{@{}ll@{}}
+  0 & x<1\\
+    \frac{4}{9}(x^2+2x-3), & \ 1\leqslant x\leqslant1.5\\
+    1 & x>1.5\\
+  \end{array}\right.
+$}\\
+\\
+Differentiate $\frac{4}{9}(x^2+2x-3)$
+$$\frac{8}{9}(x+1)$$
+Write in function form\\
+{\renewcommand{\arraystretch}{1.5}
+$
+  F(x)=\left\{
+  \begin{array}{@{}ll@{}}
+    \frac{8}{9}(x+1), & \ 1\leqslant x\leqslant1.5\\
+    0 & \textrm{Otherwise}\\
+  \end{array}\right.
+$}\\
+\newpage
+\section{Finding unknown constants}
+To find unknown constants set one of the formulas to a value it is known to be and rearrange.\\
+\\
+For example with a C.D.F find the uppermost value and set it equal to one to find any constants.
+\section{Finding probabilities}
+For questions where a probability must be found, either an inequality or specific value, use the P.D.F or the C.D.F.
+\subsection{Specific value}
+To find the probability of a specific value substitute that value into the P.D.F.
+\subsection{Inequality}
+To find the probability of an inequality use the C.D.F. The C.D.F gives a less than or equal probability, so to find greater than probabilities the probability found must be subtracted from one.
 

### 2018-02-08 Maths Notes/Statistics/S2/Exam Questions/Continuous Distributions/Normal/Normal.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Continuous Distribution - Normal- Exam Questions}
\end{center}
\section{Approximations}
\subsection{Poisson}
\subsubsection{Cases where normal can be used to approximate poisson}
\begin{itemize}
\item $\lambda>10$
\end{itemize}
\subsubsection{Conversion}
$$X\sim P_o(\lambda)$$
$$X\sim N(\lambda,\lambda)$$
\subsubsection{Continuity correction}
As the poisson distribution is discrete and the normal distribution is continuous continuity correction must be used.\\
\\
{\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|}
\hline
Probability&Corrected Probability\\
\hline
$P(X=n)$&$P(n-0.5<X<n+0.5)$\\
\hline
$P(X>n)$&$P(X>n+0.5)$\\
\hline
$P(X\leqslant n)$ &$P(X<n+0.5)$\\
\hline
$P(X<n)$&$P(X<n-0.5)$\\
\hline
$P(X\geqslant n)$&$P(X>n-0.5)$\\
\hline
\end{tabular}}
\subsubsection{Example question}
\textit{During the summer the mean number of yachts hired per week is 25.}\\
\textit{The company has only 30 yachts for hire.}\\
\textit{Using a suitable approximation find the probability that the demand for yachts cannot be
met on a particular Saturday in the summer.}\\
\\
Let X Represent the number of yachts hired
$$X\sim P_o(25)$$
$$X\sim N(25,25)$$
Write inequality
$$P(X>30)$$
Apply continuity correction
$$P(X>30.5)$$
Do Z transformation
$$Z=\frac{30.5-25}{5}=1.1$$
Lookup value in tables
$$0.8643$$
Subtract from one as probability is greater than
$$1-0.8643=0.1357$$
\newpage
\subsection{Binomial}
\subsubsection{Conditions for normal to approximate binomial}
\begin{itemize}
\item $n>10$
\item $p<0.5$
\end{itemize}

\end{document}

### 2018-02-08 Maths Notes/Statistics/S2/Exam Questions/Continuous Distributions/Binomial/Binomial.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Continuous Distribution - Binomial - Exam Questions}
\end{center}
\section{Finding probabilities}
\textit{Bhim and Joe play each other at badminton and for each game, independently of all others, the
probability that Bhim loses is 0.2\\
Find the probability that, in 9 games:}
\subsection{P(X=?)}
\textit{Exactly 3 of the games}
\subsubsection{Method 1 - Tables}
Let X be the number of games lost
$$X\sim B(9,0.2)$$
Write the question in terms of inequalities (so tables can be used)
$$P(X=3)=P(X\leqslant3)-P(X\leqslant2)$$
Look up the values on the tables
$$0.9144-0.7382=0.1762$$
\subsubsection{Method 2 - Formula}
Let X be the number of games lost
$$X\sim B(9,0.2)$$
Write down the probability to be found:
$$P(X=3)$$
Use the formula on the data sheet:
\textcolor{red}{$$\binom{n}{x}p^x(1-p)^{n-x}$$}
Substitute values:
$$\binom{9}{3}\times(0.2)^3\times(1-0.2)^{9-3}=0.1762$$
\subsection{P(X$>$?) or P(X$<$?)}
\textit{Fewer than half the games}
Let X be the number of games lost
$$X\sim B(9,0.2)$$
Write down the probability to be found
$$P(X\leqslant4)$$
Look up the value on the tables
$$0.9804$$
\\
\\
If the inequality sign is the other way round subtract the probability from one.\\
\\
If the value is not on the table, use an approximation

\end{document}

### 2018-02-08 Maths Notes/Statistics/S2/Exam Questions/Continuous Distributions/Normal/Normal.tex
Notes Update

@@
 \end{itemize}
+\subsubsection{Conversion}
+$$X\sim B(n,p)$$
+$$X\sim N(np,np(1-p))$$
+\subsubsection{Continuity correction}
+Binomial will also require continuity correction when approximated to normal as it is discrete and normal is continuous.\\
+\\
+{\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{|c|c|}
+\hline
+Probability&Corrected Probability\\
+\hline
+$P(X=n)$&$P(n-0.5<X<n+0.5)$\\
+\hline
+$P(X>n)$&$P(X>n+0.5)$\\
+\hline
+$P(X\leqslant n)$ &$P(X<n+0.5)$\\
+\hline
+$P(X<n)$&$P(X<n-0.5)$\\
+\hline
+$P(X\geqslant n)$&$P(X>n-0.5)$\\
+\hline
+\end{tabular}}
+\subsubsection{Example Question}
+\textit{In a large college 58\% of students are female and 42\% are male.\\ A random sample of 100
+students is chosen from the college.\\ Using a suitable approximation find the probability that
+more than half the sample are female.}
+Write the question in the binomial for females
+$$X\sim B(100,0.58)$$
+Use the conversion formula to convert to normal
+$$X\sim N(58,24.36)$$
+Write the inequality then apply continuity correction
+$$P(X>50)\rightarrow P(X>50.5)$$
+Find the Z value
+$$Z=\frac{50.5-58}{\sqrt{24.36}}\approx-1.52$$
+Convert the Z value to a probability using the tables
+$$p=0.9357$$
+\newpage
 

### 2018-02-09 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
2nd ODE Notes

@@
 Used to find A and B in the CF. This gives a particular solution.
+\subsection{Example}
+\textit{When y=1 x=0 $\frac{dy}{dx}=0$}
+\\
+$$\frac{d^2y}{dx^2}+5\frac{dy}{dx}+6y=12e^x$$
+Find the complementary function
+$$y=Ae^{-3x}+Be^{-2x}$$
+Find the general form of the particular integral
+$$PI: \ \lambda e^x$$
+Differentiate the particular integral twice
+$$\frac{dy}{dx}=\lambda e^x$$
+$$\frac{d^2y}{dx^2}=\lambda e^x$$
+Substitute into the initial formula
+$$\lambda e^5+5\lambda e^x+6\lambda e^x=12e^x$$
+Simplify to find lambda
+$$12\lambda e^x=12e^x \quad	\lambda=1$$
+Add this to the complementary function to find the general solution
+$$GS:\ Ae^{-3x}+Be^{-2x}+e^x$$
+Substitute y=1 and x=0 into the general solution
+$$1=A+B+1$$
+Simplify
+$$A+B=0$$
+Substitute $\frac{dy}{dx}=0$ and $x=0$ into the differentiated form of the general solution\\
+Differentiate the general solution
+$$\frac{dy}{dx}=-3Ae^{-3x}-2Be^{-2x}+e^x$$
+Substitute values
+$$0=-3A-2B+1$$
+Solve simultaneous equations
+$$A=1 \quad B=-1$$
+Substitute into the general solution to find the particular solution
+$$PS: \ y=e^{-3x}-e^{-2x}+e^x$$
 \end{document}

### 2018-02-09 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
2nd ODE P5 Notes

@@
 $$PS: \ y=e^{-3x}-e^{-2x}+e^x$$
+\newpage
+\section{Substitution}
+\setcounter{equation}{0}
+\subsection{Example 1}
+\textit{Show that the substitution $x=e^u$ transforms}
+\begin{equation}\label{eq:1}
+x^2\frac{d^2y}{dx^2}+x\frac{dy}{dx}+y=0
+\end{equation}
+to
+\begin{equation}\label{eq:2}
+\frac{d^2y}{dx^2}+y=0
+\end{equation}
+\\
+Find $\frac{dx}{du}$
+$$\textrm{As} \ x=e^u, \ \frac{dx}{du}=e^u=x$$
+Find $\frac{dy}{du}$ using the chain rule
+\begin{equation}\label{eq:3}
+\frac{dy}{du}=\frac{dy}{dx}\times\frac{dx}{du}=e^u\frac{dy}{dx}=x\frac{dy}{dx}
+\end{equation}
+Find a simplification of $\frac{d^2y}{du^2}$
+$$\frac{d^2y}{du^2}=\frac{d}{du}\Bigg(\frac{dy}{du}\Bigg)$$
+Simplify using known expression for $\frac{dy}{du}$
+$$\frac{d^2y}{dx^2}=\frac{d}{du}\Bigg(e^u\frac{dy}{dx}\Bigg)$$
+Apply the product rule,using the chain rule to differentiate $\frac{dy}{dx}$ with respect to u
+$$\frac{d^2y}{dx^2}=e^u\frac{dy}{dx}+e^u\frac{d^2y}{dx^2}\frac{dx}{du}$$
+Replace $e^u\frac{dy}{dx}$ with $\frac{dy}{du}$ and $e^u$ and $\frac{dx}{du}$ each with x
+$$\frac{d^2y}{dx^2}=\frac{dy}{du}+x^2\frac{d^2y}{dx^2}$$
+Rearrange to find $x^2\frac{d^2y}{dx^2}$
+\begin{equation}\label{eq:4}
+x^2\frac{d^2y}{dx^2}=\frac{d^2y}{du^2}-\frac{dy}{du}
+\end{equation}
+Substitute the results from \eqref{eq:3} and \eqref{eq:4} into \eqref{eq:1}.
+$$\frac{d^2y}{dx^2}-\frac{dy}{du}+\frac{dy}{du}+y=0$$
+Simplify to find answer
+$$\frac{d^2y}{dx^2}+y=0$$
+\textit{Solve this to find the general solution}
+$$m^2+1=0$$
+$$m=\pm i$$
+Substitute into the general form
+$$y=A\cos u+B\sin u$$
+Substitute $u=\ln x$ to give GS in terms of x
+$$y=A\cos(\ln(x))+B\sin(\ln(x))$$
 \end{document}

### 2018-02-09 Maths Notes/Statistics/S2/Exam Questions/Continuous Distributions/Binomial/Binomial.tex
S2 Exam Qs Notes Update

@@
 \end{center}
+\section{Conditions}
+Conditions for a binomial distribution:
+\begin{itemize}
+\item There are a fixed number of trials, \textbf{n}
+\item There are two outcomes (success and failure)
+\item Each trial is independent
+\item The probability of success is constant, \textbf{p}
+\end{itemize}
+
 \section{Finding probabilities}
@@
 \subsection{P(X$>$?) or P(X$<$?)}
-\textit{Fewer than half the games}
+\textit{Fewer than half the games}\\
 Let X be the number of games lost
@@
 If the value is not on the table, use an approximation
+\subsection{What to do when $p>0.5$}
+Find the probability of the event not happening instead
 

### 2018-02-09 Maths Notes/Statistics/S2/Exam Questions/Continuous Distributions/Poisson/Poisson.tex
S2 Exam Qs Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Continuous Distribution - Poisson - Exam Questions}
\end{center}
\section{Conditions}
The conditions for a poisson distribution are:
\begin{itemize}
\item Events occur at random
\item Events occur independently of each other
\item The average rate of occurrences remains constant
\item There is zero probability of simultaneous occurrences 
\end{itemize}
\section{Finding probabilities}
\textit{A company has a large number of regular users logging onto its website. On average 4 users
every hour fail to connect to the company's website at their first attempt.\\
Find the probability that, in a randomly chosen \textbf{2 hour} period}
\subsection{P(X=?)}
\textit{All users connect at their first attempt}
\subsubsection{Method 1 - Tables}
Let X be the number of failed connections
$$X\sim P_o(8)$$
Write the question in terms of inequalities (so tables can be used)
$$P(X=0)=P(X\leqslant0)$$
Look up the value on the tables
$$0.0002$$
\subsubsection{Method 2 - Formula}
Let X be the number failed connections
$$X\sim P_o(8)$$
Write down the probability to be found:
$$P(X=0)$$
Use the formula on the data sheet:
\textcolor{red}{$$e^{-\lambda}\frac{\lambda^x}{x!}$$}
Substitute values:
$$e^{-8}\frac{8^0}{0!}=0.0003$$
\subsection{P(X$>$?) or P(X$<$?)}
\textit{At least 4 users fail to connect at their first attempt}\\
Let X be the number of failed connections
$$X\sim P_o(8)$$
Write down the probability to be found and rewrite in terms of less than
$$P(X\geqslant4)=1-P(X\leqslant3)$$
Look up the value on the tables
$$1-0.0424=0.9576$$

\end{document}

### 2018-02-09 Maths Notes/Statistics/S2/Exam Questions/Continuous Distributions/Uniform/Uniform.tex
S2 Exam Qs Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Continuous Distribution - Uniform - Exam Questions}
\end{center}
\section{Conditions}
The conditions for a uniform distribution are:
\begin{itemize}
\item All values have the same probability
\end{itemize}
\section{Finding probabilities}
The probability of any result in a uniform distribution in a range from a to b is:
$$\frac{1}{b-a}$$
\subsection{Example}
\textit{A rectangle has a perimeter of 20 cm. The length, x cm, of one side of this rectangle is
uniformly distributed between 1 cm and 7 cm.\\
Find the probability that the length of the longer side of the rectangle is more than 6 cm long}\\
Write down the distribution
$$X\sim U[1,7]$$
Find the probability wanted to be found
$$P(X<4)+P(X>6)$$
Find each probability
$$P(X>6)=1\times\frac{1}{6}=\frac{1}{6}$$
$$P(X<4)=3\times\frac{1}{6}=\frac{1}{2}$$
Add the probability to find the answer
$$\frac{1}{6}+\frac{1}{2}=\frac{2}{3}$$
\section{Mean and Variance}
\textit{Jean regularly takes a break from work to go to the post office. The amount of time Jean waits
in the queue to be served at the post office has a continuous uniform distribution between 0 and
10 minutes.}
\subsection{Mean}
\textit{Find the mean time Jean spends in the queue}\\
Write down the distribution
$$X\sim U[0,10]$$
Use the formula in the formula book
\textcolor{red}{$$\mu=\frac{1}{2}(a+b)$$}
$$\mu=\frac{1}{2}(0+10)=5$$
\subsection{Variance}
\textit{Find the variance of the time Jean spends in the queue}\\
Write down the distribution
$$X\sim U[0,10]$$
Use the formula in the formula book
\textcolor{red}{$$\textrm{Variance}=\frac{1}{12}(b-a)^2$$}
$$\textrm{Variance}=\frac{1}{12}(10-0)^2=\frac{25}{3}$$

\end{document}

### 2018-02-12 Maths Notes/Statistics/S2/Exam Questions/Discrete Distributions/Discrete Distributions.tex
Notes update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Discrete Distributions Exam Questions}
\end{center}
\textit{A bag contains a large number of coins. It contains only 1p and 2p coins in the ratio 1:3}
\section{Populations}
\subsection{Mean and variance}
\subsubsection{Mean}
\textit{Find the mean of the population of coins}\\
Use the formula on the data sheet:
\textcolor{red}{$$\mu=\Sigma xP(X=x)$$}
Create a table of probabilities and values of x
\begin{center}
{\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|}
\hline
$x$&1p&2p\\
\hline
$P(X=x)$&$\frac{1}{4}$&$\frac{3}{4}$\\
\hline
\end{tabular}}
\end{center}
Add together the columns multiplied together
$$\mu=1\times\frac{1}{4}+2\times\frac{3}{4}=\frac{7}{4}$$
\subsubsection{Variance}
\textit{Find the variance of the population of coins}\\
Use the formula on the data sheet:
\textcolor{red}{$$\mu=\Sigma x^2P(X=x)-\mu^2$$}
Create a table of probabilities and values of x
\begin{center}
{\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|}
\hline
$x^2$&1&4\\
\hline
$P(X=x)$&$\frac{1}{4}$&$\frac{3}{4}$\\
\hline
\end{tabular}}
\end{center}
Add together the columns multiplied together to find $E(X^2)$
$$E(X^2)=1\times\frac{1}{4}+4\times\frac{3}{4}=\frac{13}{4}$$
Subtract find $E(X^2)-E(X)^2$ to find the variance
$$\frac{13}{4}-\Bigg(\frac{7}{4}\Bigg)^2=\frac{3}{16}$$
\newpage
\section{Samples}
\textit{List all the possible samples that can be drawn}\\
When doing this remember:
\textcolor{red}{$$\textrm{Number of samples}=\textrm{Number of options}^\textrm{Sample size}$$}
For the example:\\
Number of options=2\\
Sample size=3\\
Number of samples=$2^3$=8\\
\\
\\
List of samples:\\
(1,1,1)\\
(1,1,2)$\times$3\\
(1,2,2)$\times$3\\
(2,2,2)\\
\\
\textit{Find the sampling distribution of the mean value of these samples.}\\
\\
List the possible means
$$1,\frac{4}{3},\frac{5}{3},2$$
Calculate the probability of each, given the probability of picking a coin
$$1: \ \Bigg(\frac{1}{4}\Bigg)^3=\frac{1}{64}$$
$$\frac{4}{3}: \ 3\times\frac{1}{4}\times\frac{1}{4}\times\frac{3}{4}=\frac{9}{64}$$
$$\frac{5}{3}: \ 3\times\frac{1}{4}\times\frac{3}{4}\times\frac{3}{4}=\frac{27}{64}$$
$$2: \ \Bigg(\frac{3}{4}\Bigg)^3=\frac{27}{64}$$
Write in a table\\
\\
{\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|c|c|}
\hline
$\overline{x}$&1&$\frac{4}{3}$&$\frac{5}{3}$&2\\
\hline
$P(\overline{X}=\overline{x})$&$\frac{1}{64}$&$\frac{9}{64}$&$\frac{24}{64}$&$\frac{27}{64}$\\
\hline

\end{tabular}}

\end{document}

### 2018-02-12 Maths Notes/Statistics/S2/Exam Questions/Hypothesis tests/Binomial/Binomial.tex
Notes update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Hypothesis tests - Binomial - Exam Questions}
\end{center}
\textit{A company claims that a quarter of the bolts sent to them are faulty. To test this claim the
number of faulty bolts in a random sample of 50 is recorded.}
\section{Finding the critical region}
\textit{Using a 5\% significance level, find the critical region for a two-tailed test of the
hypothesis that the probability of a bolt being faulty is $\frac{1}{4}$. The probability of rejection in
either tail should be as close as possible to 0.025}\\
\\
Write down the distribution:
$X\sim B(50,0.25)$
For the lower value, look for the value closest to the probability of rejection
$$P(X\leqslant6)=0.0194$$
To find the upper value look for the value closest to (1-probability of rejection). Then add one to this value as:
\textcolor{red}{$$P(X\geqslant c)=1-P(X\leqslant c-1)$$}
$$P(X\leqslant18)=0.9713$$
$$P(X\geqslant19)=0.0287$$
\begin{center}
The critical values are 6 and 19
\end{center}
\textit{Find the actual significance}\\
The actual significance is the true probability of rejection
$$0.0194+0.0287=0.0481$$
\section{One tailed test}
\textit{The machine making the bolts was reset and another sample of 50 bolts was taken. Only 5 were
found to be faulty}\\
\\
\textit{Test at the 1\% level of significance whether or not the probability of a faulty bolt has
decreased. State your hypotheses clearly.}\\
\\
State the null and alternative hypothesis related to the $\frac{1}{4}$ probability mentioned earlier in the question
$$H_0: \ p=0.25$$
$$H_1: \ p<0.25$$
Write a probability based on the information given in the question
$$P(X\leqslant5)$$
Look up the probability on the tables
$$P(X\leqslant5)=0.007$$
Compare this to the significance level
$$0.007<0.01$$
Write the conclusion
\begin{center}
5 is in the critical region, reject $H_0$, the test is significant, there is evidence that the probability of faulty bolts has decreased.
\end{center}
\newpage
\section{Two tailed test}
\textit{A teacher thinks that 20\% of the pupils in a school read the Deano comic regularly.\\
\\
He chooses 20 pupils at random and finds 9 of them read Deano.}

\end{document}

### 2018-02-12 Maths Notes/Statistics/S2/Exam Questions/Hypothesis tests/Poisson/Poisson.tex
Notes update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Hypothesis tests - Poisson - Exam Questions}
\end{center}
\section{One tailed test}
\textit{An effect of a certain disease is that a small number of the red blood cells are deformed. Emily
has this disease and the deformed blood cells occur randomly at a rate of 2.5 per ml of her
blood. Following a course of treatment, a random sample of 2 ml of Emily’s blood is found to
contain only 1 deformed red blood cell.\\
\\
Stating your hypotheses clearly and using a 5\% level of significance, test whether or not there
has been a decrease in the number of deformed red blood cells in Emily’s blood.}\\
\\
Write the null and alternate hypothesis, using information from the text
$$H_0:\ \lambda=5$$
$$H_1:\ \lambda<5$$
Write down the distribution the hypothesis test will be done on
$$X\sim P_o(5)$$
Write down a probability to test based on the data, in this case 1 one deformed red blood cell
$$P(X\leqslant1)$$
Find this value in the tables, or using an approximation if needed
$$P(X\leqslant1)=0.0404$$
Compare this to the significance level
$$0.0404<0.05$$
Write the conclusion, if in the critical region, reject $H_0$, if not accept it
\begin{center}
As $0.0404<0.05$ the result is significant, so reject $H_0$\\
There is evidence in a \textbf{decrease} in the mean \textbf{rate} of \textbf{deformed blood cells}
\end{center}
\section{Finding critical values}
\textit{A test statistic has a Poisson distribution with parameter $\lambda$.}\\
\textit{Given that:}
$$H_0: \ \lambda=9,\ H_1: \ \lambda\neq9$$ 
\textit{Find the critical region for the test statistic such that the probability in each tail is as close
as possible to 2.5\%.}\\
\\
Write down the distribution
$$X\sim P_o(9)$$
Find the lower value by looking on the tables at the column related to $\lambda$ and look for the closest value to the probability wanted (in this case 2.5\%)
$$P(X\leqslant3)=0.0212\approx0.025$$
To find the upper value look for the value closest to (1-wanted probability). Then add one to this value as:
\textcolor{red}{$$P(X\geqslant c)=1-P(X\leqslant c-1)$$}
$$P(X\leqslant15)=0.9780\approx0.975$$
$$P(X\geqslant16)=1-0.9780=0.022\approx0.025$$
Critical values are 3 and 16\\
\\
\textit{Write down the actual significance}
\\
Actual significance is the probability of a value being found in the critical region.
$$0.0212+0.022=0.0432$$
\newpage
\section{Two tailed test}
\textit{Bacteria are randomly distributed in a river at a rate of 5 per litre of water. A new factory opens
and a scientist claims it is polluting the river with bacteria. He takes a sample of 0.5 litres of
water from the river near the factory and finds that it contains 7 bacteria. Stating your
hypotheses clearly test, at the 5\% level of significance, the claim of the scientist.}\\
\\
Write down the null and alternative hypothesis
$$H_0: \ \lambda=2.5$$
$$H_1 \ \lambda\neq2.5$$
Write down the distribution to be tested
$$X\sim P_o(2.5)$$
Find a probability to test from the data
$$P(X\geqslant7)=1-P(X\leqslant6)$$
Look up the probability on the tables
$$1-P(X\leqslant6)=1-0.9858=0.0142$$
Compare with the significance level, remembering to split it
$$0.0142<0.025$$
Write the conclusion
\begin{center}
There is significant evidence that the factory is polluting the river with bacteria
\end{center}

\end{document}

### 2018-02-12 Maths Notes/Statistics/S2/Exam Questions/Hypothesis tests/Binomial/Binomial.tex
Notes update

@@
 \\
-He chooses 20 pupils at random and finds 9 of them read Deano.}
+He chooses 20 pupils at random and finds 9 of them read Deano.}\\
+\\
+\textit{Test, at the 5\% level of significance, whether or not there is evidence that the
+percentage of pupils that read Deano is different from 20\%. State your hypotheses
+clearly.}\\
+\\
+Write down the null and alternate hypothesis
+$$H_0: \ p=0.2$$
+$$H_1: \ p\neq0.2$$
+Write down the distribution
+$$X\sim B(20,0.2)$$
 
+Write down a probability based on information in the question
+$$P(X\geqslant9)$$
+Find this probability using the tables
+$$P(X\geqslant9)=1-P(X\leqslant8)=1-0.99=0.01$$
+Compare this value with the significance level, remembering to split it
+$$0.01<0.025$$
+Write conclusion
+\begin{center}
+Probability is smaller than significance level, reject $H_0$ accept $H_1$, there is evidence that the percentage of pupils that read beano is not 20\%. 
+\end{center}
 \end{document}

### 2018-02-14 Maths Notes/Mechanics/M2/Kinematics/Kinematics.tex
M2 Notes Update

--- 2017-12-06 Maths Notes/M2/Kinematics/Kinematics.tex
@@
 \rfoot{Page \thepage}
-
+\usepackage{mathtools}
+\newtagform{brackets}{[}{]}
+\usetagform{brackets}
 \begin{document}
@@
 $x=\dfrac{432}{10}-36=7.2\text{m}$
+\newpage
+\begin{center}
+\underline{\huge Kinematics Example - Finding direction of motion}
+\end{center}
+\textit{At $t=0$ a particle P is projected from a fixed point O with velocity $(7i+7\sqrt{3})ms^{-1}$.
+The particle moves freely under gravity.
+The position vector of a point on the path of P is $(x\mathbf{i}+y\mathbf{j})$m relative to O.}\\
+\textit{Show that:}
+$$y=\sqrt{3}x-\frac{g}{98}x^2$$
+\\
+\\
+$x$ has constant velocity so write in terms of t
+\begin{equation}\label{eq:1}
+x=7t
+\end{equation}
+Write an equation for y using $s=ut+\frac{1}{2}at^2$
+\begin{equation}\label{eq:2}
+y=7\sqrt{3}t-\frac{g}{2}t^2
+\end{equation}
+Substitute \eqref{eq:1} into the \eqref{eq:2}
+$$y=\sqrt{3}x-\frac{g}{2}\times\Big(\frac{x}{7}\Big)^2$$
+Simplify
+\begin{equation}\label{eq:3}
+y=\sqrt{3}x-\frac{g}{98}x^2
+\end{equation}
+\\
+\textit{Find the direction of motion of P when it passes through the point on the path where $x=20$}\\
+\\
+Differentiate \eqref{eq:3}
+$$\frac{dy}{dx}=\sqrt{3}-\frac{2gx}{98}$$
+Substitute in the value of x
+$$\frac{dy}{dx}=\sqrt{3}-\frac{40g}{98}$$
+\\
+\textcolor{red}{Arctan(gradient)=Angle to the positive horizontal as $\dfrac{dy}{dx}$ is the same as $\dfrac{O}{A}$
+}
+\\
+Perform arctan on the gradient to find the angle
+$$\arctan\Big(\sqrt{3}-\frac{40g}{98}\Big)=-66.2$$
 

### 2018-02-14 Physics Notes/Nuclear Physics/Nuclear Energy/Nuclear Energy.tex
M2 Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{tabularx}
\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty =10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Nuclear Physics}
\rfoot{Page \thepage}
\usepackage{mathtools}
\usetikzlibrary{calc,quotes,angles}
\tikzstyle{arrow} = [thick,->,>=stealth]
\begin{document}
\begin{center}
\underline{\huge Nuclear energy}
\end{center}
\section{Energy and mass}
\subsection{Annihilation and Pair production}
When a particle and its corresponding particle meet, they \textbf{annihilate} each other, and two gamma photons are produced, each with energy $mc^2$ where m is the mass of the particle.\\
\\
A single gamma photon of energy in excess of $2mc^2$ can produce a particle and an antiparticle, each of mass m, in a process called \textbf{pair production}.
\subsection{Energy changes in reactions}
$$\textrm{Energy released:} \ Q=\Delta mc^2$$ 
In any change where energy is released, such as radioactive decay, \textbf{total mass after $<$ total mass before} as some of the mass has been turned into energy, which has been released.
\begin{itemize}
\item In \textbf{Alpha Decay} the nucleus recoils when the $\alpha$ particle is emitted so the energy released is shared between the $\alpha$ particle and the nucleus. Conservation of momentum shows the energy released is shared between the $\alpha$ particle and the nucleus in inverse proportion to their masses.
\item In \textbf{Beta Decay} the energy released is shared between the $\beta$ particle, the nucleus and the neutrino/antineutrino. The vast majority of the energy goes with the $\beta$ particle and some of it with the nucleus.
\item In \textbf{Electron Capture} the nucleus emits a neutrino which carries away the energy released in the decay. The atom also emits an X-Ray photon when the inner shell vacancy is filled.
\end{itemize}
\subsubsection{Example Calculation}
\textit{The polonium isotope $^{210}_{84}Po$ emits $\alpha$ particles and decays to form the stable isotope of lead $^{206}_{82}Pb$. Write down an equation to represent this process and calculate the energy released when a $^{210}_{84}Po$ nucleus emits an $\alpha$ particle.\\
Mass of a $^{210}_{84}Po$ Nucleus=$209.93667u$\\
Mass of a $^{206}_{82}Pb$ Nucleus=$205.92936u$\\
Mass of a $\alpha$ particle=$4.00150u$\\
$1u=931.3MeV$}\\
$$^{206}_{82}Pb\rightarrow \ ^4_2\alpha+^{206}_{82}Pb+\textrm{Energy released}$$
$$\textrm{Mass difference}=\textrm{Total initial mass-total final mass}$$
$$\textrm{Mass difference}=209.93667-(205.92936+4.00150)$$
$$\textrm{Mass difference}=5.81\times10^{-3}u$$
$$\textrm{Energy released:}\ Q=\textrm{Mass difference in u}\times931.3=5.41MeV$$
\subsection{The strong nuclear force}
\begin{itemize}
\item The strength of the strong nuclear force can be estimated by working out the force of repulsion between two protons at a separation of 1fm(The approximate size of the nucleus). The strong nuclear force must be about the same magnitude as this force. This gives a value around 200N
\item The range of the strong nuclear force is no more than around 3-4fm. Experiments to measure the size of a nucleus show that nucleons are evenly spaced around 1fm apart, meaning that the strong force only acts between neighbour nucleons.
\item The energy needed to pull a nucleon out of the nucleus is on the order of MeV. This can be found from the force and distance to find the work done. $200\times3.5\times10^{-15}=4MeV$
\item The strong nuclear force must become repulsive at less than 0.5fm, otherwise the nucleus would compress further.
\end{itemize}
\newpage
\section{Binding energy}
\begin{center}
The \textbf{binding energy} of the nucleus is the work that must be done to separate a nucleus into its constituent neutrons and protons.
\end{center}
\begin{center}
The \textbf{mass defect}($\Delta m$) of a nucleus is defined as the difference between the mass of the separated nucleons and the mass of the nucleus. This exists as work is done to make a nucleus, reducing mass
\end{center}
\subsubsection{Mass defect calculation}
Nucleus of an isotope $^A_ZX$ has:\\
Z Protons\\
A-Z Neutrons\\
Mass=$M_{NUC}$
$$\textrm{Mass defect:} \ \Delta m=Zm_p+(A-Z)m_n-M_{NUC}$$
Where:\\
$m_p=\textrm{Mass of proton} \quad m_n=\textrm{Mass of neutron}$
\subsubsection{Binding energy calculation}
$$\textrm{Binding energy of a nucleus}=\Delta mc^2$$
When calculating with multiply the Mass defect in u by the MeV equivalent of 1u (931.3)
\subsection{Alpha particle tunnelling}
In a sufficiently large nucleus two protons and two neutrons may join together as a cluster. Because an alpha particle has a high binding energy the alpha particle gains enough energy to have a possibility of quantum tunnelling through the nucleus
\subsection{Nuclear stability}
The binding energy of each nuclide is different. The \textbf{binding energy per nucleon} of a nucleus is the average work done per nucleon to remove all the \textbf{nucleons} from a nucleus and so is a measure of the stability of a nucleus.\\
\\
If the binding energies per nucleon of two different nuclides are compared, the nucleus with more binding energy per nucleon is the more stable of the two.
\newpage
\section{Fission and fusion}
\subsection{Induced fission}
Fission is when a nucleus splits into two approximately equal fragments. This happens when a uranium nucleus is bombarded by neutrons and is called \textbf{induced fission}.\\
\\
Each fission event releases energy and two or three neutrons
\begin{itemize}
\item \textbf{Fission neutrons}, the neutrons released in a fission event, are capable of causing a further fission event in a \textbf{chain reaction}.
\item \textbf{Energy is released} when a fission event occurs because the fragments repel each other with sufficient charge to overcome the strong nuclear force holding them together. These nuclei and the neutrons then gain kinetic energy. The two fragment nuclei are smaller, and so have a higher binding energy than the original nucleus. The energy released is equal to the change in binding energy
\end{itemize}
\subsection{Nuclear fusion}
Fusion takes place when two nuclei combine to form a bigger nucleus. The binding energy per nucleon of the product nucleus is greater than of the initial nuclei. Energy is released equal to the binding energy.\\
\\
Fusion takes place when two nuclei combine at high speed, this is needed to overcome the electrostatic repulsion between the two nuclei so they can interact using the strong nuclear force.\\
\\
\textbf{Solar energy} is produced as a result of fusion inside the sun. The gas is at such high pressure that it turns into plasma and the nuclei have so much energy that they fuse when they collide.
\subsubsection{Fusion power}
Fusion reactors are still in prototype stage and as yet don't produce more energy than they use
\section{The thermal nuclear reactor}
\subsection{Inside a nuclear reactor}
A thermal nuclear reactor in a nuclear power station contains fuel rods spaced evenly in a steel vessel known as the \textbf{reactor core}. The reactor core also contains \textbf{control rods} and a \textbf{coolant} as well as the fuel rods and is connected by steel pipes to a \textbf{heat exchanger}. A pump is used to force the coolant through the reactor core and through the heat exchanger where it raises steam to drive turbines.\\
\\
\includegraphics[width=7cm]{reactor.png}
\begin{itemize}
\item The fuel rods contain enriched uranium
\item The control rods absorb neutrons to stop chain reactions
\item The fission neutrons need to be slowed to cause further fission. The fuel rods are surrounded by a moderator so the neutrons are slowed by repeated collisions. Water acts as the moderator
\item For a chain reaction to occur the mass of the uranium must be greater than a minimum mass called the \textbf{critical mass}. This to reduce the number of escaping neutrons to allow reactions to continue
\end{itemize}
\subsection{Safety features}
A nuclear reactor needs safety features to protect workers and the environment:
\begin{itemize}
\item The reactor core is made of thick steel to withstand high pressure and temperature. This also absorbs $\beta$ and some gamma radiation and neutrons from the core
\item The core is in a building with very thick concrete walls to absorb neutrons and gamma radiation
\item Every reactor has an emergency shut-down to insert the control rods to stop fission
\item The fuel rods are inserted and removed from the reactor by remote handling devices to protect workers.
\end{itemize}
\subsection{Radioactive waste}
Radioactive waste must be stored in cooling ponds for a year as they continue to release heat due to radioactive decay.\\
This is then processed and the unused uranium is then removed and stored in sealed containers. This is then stored for centuries.\\
\\
Lower level radioactive waste is stored in drums filled with concrete.
\end{document}

### 2018-02-14 Maths Notes/Statistics/S2/Exam Questions/Continuous Distributions/Uniform/Uniform.tex
S2 Notes Update

@@
 $$\textrm{Variance}=\frac{1}{12}(10-0)^2=\frac{25}{3}$$
+\newpage
+\subsubsection{Proof of variance formula}
+$$E(X)=\frac{1}{2}(a+b)$$
+$$E(X^2)=\frac{1}{b-a}\int^b_a x^2\ dx$$
+$$E(X^2)=\frac{1}{b-a}\Bigg[\frac{x^3}{3}\Bigg]^b_a$$
+$$E(X^2)=\frac{b^3-a^3}{b-a}$$
+$$E(X^2)=\frac{(b-a)(b^2+a^2+ab}{3(b-a)}$$
+$$E(X^2)=\frac{b^2+a^2+ab}{3}$$
+$$Var(X)=\frac{b^2+a^2+ab}{3}-\Big(\frac{a+b}{2}\Big)^2$$
+$$Var(X)=\frac{b^2+a^2+ab}{3}-\frac{a^2+2ab+b^2}{4}$$
+$$Var(X)=\frac{b^2-2ab+a^2}{12}$$
+$$Var(X)=\frac{(b-a)^2}{12}$$
 

### 2018-02-16 Physics Notes/Fields and their consequences/Gravitiational Fields/Gravitiational Fields.tex
Physics Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Fields}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Gravitational Fields Notes}
\end{center}
Gravitational field strength, $g$, is the force felt per unit mass on a unit mass placed at that point in a field.\\
$g=\dfrac{F}{m}$, unit=$NKg^{-1}$\\
The gravitational field is around all objects with mass and can be either \textbf{radial} or \textbf{uniform}.
\section{Introduction to Gravitational potential}
Definition: The potential at a point in a field is the work done in moving unit mass from infinity to that point.\\
\\
$V=\dfrac{\text{Work done}}{\text{Unit mass}}$ Unit: $JKg^{-1}$\\
In a radial field $v=\dfrac{-GM}{r}$\\
\begin{tikzpicture}[scale=0.5]
\begin{axis}[xmin=0,ymax=0,ticks=none,ylabel={v},xlabel={r},axis x line=top,axis y line=left,label style={font=\Huge},]
\addplot[color=black, domain=0:2]{-1/x};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\draw[ultra thin] (axis cs:\pgfkeysvalueof{/pgfplots/xmin},0) -- (axis cs:\pgfkeysvalueof{/pgfplots/xmax},0);

\end{axis}
\end{tikzpicture}
\\
Gravitational potential energy = $\Delta V\times m$\\
$V_o-V_s=\Delta V$ Unit:$JKg^{-1}$\\
$V_s$ = Potential on earth, $V_o$ = Potential in orbit.
\section{Potential gradient}
Potential gradient - Change in potential per unit change in distance
$$g=-\frac{\Delta V}{\Delta r}$$
\section{Newton's law of gravitation}
The force between two masses is attractive and is directly proportional to the product of the masses and is inversely proportional to the distance between them squared.
$$F=\frac{GM_1M_2}{r^2}$$
\section{Escape Velocity}
$$\frac{1}{2}mv^2=\frac{GMm}{r}$$
$$\frac{1}{2}v^2=\frac{GM}{r}$$
$$v^2=\frac{2GM}{r}$$
$$v=\sqrt{\frac{2GM}{r}}$$
\section{Satellite motion}
The force between a planet of mass M and the satellite of mass m is described by Newton's law of gravitation.\\
This force provides the \textbf{centripetal force} acting towards the centre of the orbit.
$$\frac{GMm}{r^2}=\frac{mv^2}{r}$$
$$GM=v^2r$$
$$\sqrt{\frac{GM}{r}}=v$$
$$v\propto r^{-\frac{1}{2}}$$
\section{Kepler's 3rd law}
$$F=\frac{GMm}{r^2}=\frac{mv^2}{r}=m\omega^2r$$
$$\frac{GMm}{r^2}=m\omega^2r$$
$$\frac{GM}{r^3}=\Big(\frac{2\pi}{T}\Big)^2$$
$$\frac{GM}{r^3}=\frac{4\pi^2}{T^2}$$
$$\frac{r^3}{T^2}=\frac{GM}{4\pi^2}$$
$$\textrm{As}\  r\uparrow \ T\downarrow$$
\section{Geostationary orbits}
Sometimes called geosynchronous orbits\\
$T=24h=86400s$\\
$r=42Mm=35857km$ above the earth\\
Geostationary - Orbiting in plane of the equator\\
Geosynchronous - 24h orbit inclined at an angle to the equator\\
\\
Geostationary orbits:
\begin{itemize}
\item Period of 24h
\item 36,000 km above the earth's surface
\item Circular
\item Equatorial (in plane of the equator)
\item Are in the same direction as the earth's rotation
\end{itemize}
\section{The time period of satellites}
$$\sqrt{\frac{GM}{r}}=\frac{2\pi r}{T}$$
$$\frac{GM}{r}=\frac{4\pi^2r^2}{T^2}$$
$$T^2=(\frac{4\pi^2}{GM})r^3$$
$$T^2\propto r^3$$
$$T=kr^{\frac{3}{2}}$$
$\log T=\frac{3}{2}\log r+\log k$ is in the form $y=mx+c$
This can also be used to fine the height that a satellite must be at to have any given orbit time.

\end{document}

### 2018-02-16 Physics Notes/Nuclear Physics/Nuclear Energy/Nuclear Energy.tex
Physics Notes Update

@@
 \\
-If the binding energies per nucleon of two different nuclides are compared, the nucleus with more binding energy per nucleon is the more stable of the two.
+If the binding energies per nucleon of two different nuclides are compared, the nucleus with more binding energy per nucleon is the more stable of the two.\\
+\\
+\includegraphics[width=8cm]{Binding_Energy.jpg}\\
+In \textbf{nuclear fission} the binding energy per nucleon increases as a large unstable nucleus splits into two more stable fragments.\\
+\\
+In \textbf{nuclear fusion} the binding energy per nucleon increases, provided the nucleon number does not exceed the peak on the graph (around 50).
+This is why fusion can only occur on the left side of the graph as fusing iron would lose energy.\\
+\\
+Atoms always want to increase binding energy, fusion goes right, fission goes left.
 \newpage

### 2018-02-19 Physics Notes/Fields and their consequences/Magnetic Fields/Magnetic Fields.tex
Notes Update

@@
 \renewcommand{\indent}{\hspace*{\tindent}}
-
+\hyphenpenalty=10000
 \pagestyle{fancy}
@@
 \\
-The same equation applies for many charges where:\\
-\\
-$I=\dfrac{Q}{t} \quad l=vt$\\
-\\
-$F=B\times\frac{Q}{t}\times vt$\\
-\\
-$F=BQv$\\
-\\
+The same equation applies for many charges where:
+$$I=\frac{Q}{t} \quad l=vt$$
+$$F=B\times\frac{Q}{t}\times vt$$
+$$F=BQv$$
 \subsection{The hall probe}
@@
 \\
-The negative charges go to the bottom of the material and so the top is positively charged, this creates a potential difference.\\
-\\
-$F_B=F_E$\\
-\\
-$BQV=\dfrac{VQ}{d}$\\
-\\
-$V=Bvd$\\
-\\
-$V\propto B$\\
-\\
+The negative charges go to the bottom of the material and so the top is positively charged, this creates a potential difference.
+$$F_B=F_E$$
+$$BQV=\frac{VQ}{d}$$
+$$V=Bvd$$
+$$V\propto B$$
 By measuring the voltage across the probe the magnetic field strength can be measured.
@@
 Causes a centripetal acceleration\\
-\\
-\\
 $$F=BQv=\dfrac{mv^2}{r}$$
@@
 \end{itemize}
-$r=\dfrac{mv}{BQ}$\\
-$r\propto\dfrac{1}{\frac{q}{m}}$
+$$r=\dfrac{mv}{BQ}$$
+$$r\propto\dfrac{1}{\frac{q}{m}}$$
 \subsubsection{Velocity selector}
@@
 For an ion to continue on a straight path the force from the magnetic field up must be equal to the force from the electric field down.\\
-\\
-$F=BQv=EQ$\\
-\\
-$BQv=\dfrac{V}{d}Q$\\
-\\
-$v=\dfrac{V}{Bd}$\\
-\\
+$$F=BQv=EQ$$
+$$BQv=\dfrac{V}{d}Q$$
+$$v=\dfrac{V}{Bd}$$
 This means that only particles of speed $v$ will travel through the gap

### 2018-02-19 Physics Notes/Further Mechanics and Thermal Physics/Circular Motion/Circular Motion.tex
Notes Update

@@
 \subsection{Formula not on formula book}
-$\omega=\dfrac{\Delta\theta}{\Delta t}$\\
-$a=\dfrac{\Delta V}{\Delta t}$\\
+$$\omega=\frac{\Delta\theta}{\Delta t}$$
+$$a=\frac{\Delta V}{\Delta t}$$
 Don't forget application of  $F=ma$ with the equations for force
@@
 \subsection{Calculations}
-$F_c=mg-R=\dfrac{mv^2}{r}$\\
+$$F_c=mg-R=\frac{mv^2}{r}$$
 \textbf{Calculating the speed at which the car will leave the ground (R=0)}\\
-$mg=\dfrac{mv_0^2}{r} \qquad V_0=\sqrt{gr}$\\
+$$mg=\frac{mv_0^2}{r} \qquad V_0=\sqrt{gr}$$
 Once the car has left the ground, use SUVAT equations rather than circular motion.
@@
 On a roundabout the centripetal force is provided by friction.\\
-$F_r=\dfrac{mv_0^2}{r}$\\
+$$F_r=\frac{mv_0^2}{r}$$
 To avoid slipping, the centripetal force must be less than the maximum possible for the car and road surface.\\

### 2018-02-19 Physics Notes/Fields and their consequences/Electric Fields/Electric Fields.tex
Physics Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Fields}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Electric Fields Notes}
\end{center}

\begin{obeylines}
\section{Static Electricity}
\textbf{Like charges repel; unlike charges attract}
Electrical conductors have many free electrons, these can move in the material and are not attached to any atom. To charge a metal, it must be isolated from the earth to stop the charge being neutralised by electrons from the earth. It can then be charged by direct contact with a charged object. If an isolated conductor is charged then earthed, the electrons will transfer to neutralise it.  
Electrically insulating materials do not contain free electrons, all electrons are attached to atoms. Some insulators can be charged easily because their surface atoms easily gain or lose electrons.

A \textbf{gold leaf electroscope} is used to detect charge. If it is in contact with charge the gold leaf and the metal stem have the same charge and so repel.
\section{Shuttling ball experiment}
A ball swinging between one positively charged plate and one negatively charged plate will lose electrons at the positive plate and so be repelled towards the negative plate where it will pick up electrons and gets repelled away, and so the process repeats.
\section{Field lines and patterns}
Electric fields surround each charged object, if a small charged object is placed near a larger same charged object the path the small charge will follow is called a \textbf{line of force} or \textbf{field line}. The direction of an electric field is the direction the charge moves.
\includegraphics[width=5in]{field_lines.png}
\section{Electric field strength}
The field strength of a uniform field is constant at all points.
The electric field strength, E, at a point in the field is defined as the force per unit charge on a positive test charge placed at that point.
The unit of electric field strength is Newton per coulomb $NC^{-1}$
If a positive charge of \textbf{Q} us acted on by a force \textbf{F} the electric field strength at that point is 
$E=\dfrac{F}{Q}$
\section{The electric field between two parallel plates}
Field lines between two parallel plates are:
\begin{itemize}
\item Parallel to each other
\item At right angles to the plates
\item From the positive plate to the negative plate
\item Uniform
\end{itemize}
$E=\dfrac{V}{d}$
V=Potential difference between plates
d= Separation between plates
Proof:
$F=QE$
$Work done= Force \times Distance$
$d=QEd$
$ $
$V=\dfrac{W}{Q}=\dfrac{QEd}{Q}=Ed$
$ $
$E=\dfrac{V}{d}$
\section{Field Factors}
The greater the charge on a body, the stronger the electric field is. The more concentrated the charge is on the surface, the greater the strength of the electric field is above the surface.
For a charge,\textbf{Q}, on a plate of surface area,\textbf{A}, the electric field is proportional to $\dfrac{Q}{A}$ 
Including a constant of proportionality the equation gives $\dfrac{Q}{A}=\epsilon_0E$
The unit of $\epsilon_0$ is $Fm^{-1}$ and is called the \textbf{Permittivity of free space} as it represents the charge per unit area on a surface in a vacuum that produces an electric field strength of one volt per one metre between the plates.
\section{The Van de Graff generator}
A Van de Graff generator works by rubbing a rubber belt against a pad up to a metal dome. This increased the PD between the dome and the earth until sparks start. 
The electric potential at a certain position in any electric field is defined as the work done per unit charge on a positive test charge when it is moved from infinity to that position.

$E_P=QV$ or $V=\dfrac{E_P}{Q}$

\section{Potential gradients}
Equipotentials are surfaces of constant potential. A test charge moving along an equipotential has constant potential energy. The \textbf{potential gradient} at any position in an electric field is the change in potential per unit change of distance in a given direction.
If the field is \textbf{non-uniform} the potential gradient varies according to position and direction. The closer the equipotentials are, the greater the potential gradient at right angles to the equipotentials. 
If the field is \textbf{uniform} the equipotentials between the plates are equally spaced lines parallel to the plates.
In a uniform field the potential gradient is 
\begin{itemize}
\item Constant
\item Potential increases in the opposite direction to the electric field
\item Equal to $\dfrac{V}{d}$
\end{itemize}
\textbf{The electric field strength is equal to the negative of the potential gradient}
The potential gradient at any position in an electric field is $\dfrac{\Delta V}{\Delta x}$ where $\Delta V$ is the potential difference between two points and $\Delta X$ is the distance between the points.
$E=-\dfrac{\Delta V}{\Delta X}$
\newpage
\section{Coulomb's law}
$F=\dfrac{KQ_1Q_2}{r^2}$
F=Force between two point charges
K=$\dfrac{1}{4\pi\epsilon_0}$
$Q_1$=Point charge 1
$Q_2$=Point charge 2
r=Distance between the two point charges

$F=\dfrac{1}{4\pi\epsilon_0}\dfrac{Q_1Q_2}{r^2}$
\section{Charged particles in electric fields}
\subsection{Force}
Force is the same throughout the journey.
Calculated by
\begin{itemize}
\item $f=EQ$
\item $E=\dfrac{V}{d}$
\end{itemize}
\subsection{Velocity}
Horizontal velocity is constant
Vertical velocity increases as the particle passes through the field
\section{Point charges}
A point charge is a charge where the distances considered are much larger than the object, meaning the charge can be thought of as being in one place.
The electric field strength at a distance r from Q is:
$E=\dfrac{Q}{4\pi\epsilon_0r^2}$
\textit{Note that Q is negative}
\subsection{Example Field strength question}
\begin{tikzpicture}
\draw[gray, thick,<->] (-1.8,0) -- (-0.2,0) node[above,midway] {0.2};
\draw[gray, thick,<->] (0.2,0) -- (7.8,0) node[above, midway] {0.8};
\filldraw[black] (0,0) circle (2pt) node[anchor=south] {X};
\filldraw[black] (-2,0) circle (2pt) node[anchor=east] {A};
\filldraw[black] (8,0) circle (2pt) node[anchor=west] {B};
\end{tikzpicture}
\textit{Find the field strength at the point X, the charge at A and B is $4\mu C$}\\
E at X due to A
$$\frac{1}{4\pi\epsilon_0}\times\frac{4\times10^{-6}}{0.2^2}=8.99\times10^5NC^{-1} \quad \textrm{Left to right}$$ 
E at X Due to B
$$\frac{1}{4\pi\epsilon_0}\times\frac{4\times10^{-6}}{0.8^2}=5.62\times10^4NC^{-1} \quad \textrm{Right to left}$$ 
Total E at X
$$8.99\times10^5-5.62\times10^4=8.43\times10^5NC^{-1}\quad \textrm{Left to right}$$
\newpage
\subsection{Example Electric Potential}
\textbf{For electric potential, ignore which side of the point the charge is on}
\begin{tikzpicture}
\draw[gray, thick,<->] (-4.8,0) -- (-0.2,0) node[above,midway] {r};
\draw[gray, thick,<->] (0.2,0) -- (4.8,0) node[above, midway] {r};
\filldraw[black] (0,0) circle (2pt) node[anchor=south] {-2Q};
\filldraw[black] (-5,0) circle (2pt) node[anchor=east] {+Q};
\filldraw[black] (5,0) circle (2pt) node[anchor=west] {P};
\end{tikzpicture}
\textit{Find the electric potential at P}\\
Electric potential due to +Q charge
$$V=\frac{1}{4\pi\epsilon_0}\times\frac{Q}{2r}$$
Electric potential due to -2Q charge
$$V=\frac{1}{4\pi\epsilon_0}\times\frac{-2Q}{r}$$
Add two equations
$$V=\frac{1}{4\pi\epsilon_0}\Bigg(\frac{Q}{2r}-\frac{2Q}{r}\Bigg)$$
Simplify
$$V=\frac{1}{4\pi\epsilon_0}\times\frac{-3Q}{2r}$$

\section{Electric field strength as a vector}
In general, the electric field strength is the vector sum of the individual electric field strengths
\subsection{Forces in the same direction}
$F=F_1+F_2=qE_1+qE_2$
Therefore $E=\dfrac{F}{q}=\dfrac{qE_1+qE_2}{q}=E_1+E_2$
\subsection{Forces in opposite directions}
$F=F_1-F_2=qE_1-qE_2$
Therefore $E=\dfrac{F}{q}=\dfrac{qE_1-qE_2}{q}=E_1-E_2$
\subsection{Forces at right angles to each other}
$F^2={F_1}^2+{F_2}^2$
$E=\dfrac{F}{q}$
$E^2={E_1}^2+{E_2}^2$
\section{More about radial fields}
The electric field lines surrounding a point charge are radial.
Coulomb's law and Newton's law are similar as they have inverse square relationships.
The equation for electric potential near a point charge and gravitational potential near a point mass are also very similar.
\section{The relationship between electric field strength and electric potential}
Electric field strength = -gradient of a potential vs distance graph. 
Change in potential = Area under an electric field vs distance graph.
\end{obeylines}

\section{Comparing electric fields and gravitational fields}
\begin{tabular}{ |p{5.5cm}|p{5.5cm}|p{5.5cm}|  }
\hline
&Gravitational Fields&Electrostatic fields\\
 \hline
 \multicolumn{3}{|c|}{Similarities} \\
 \hline
 Line of force&Path of a free test mass in the field & Path of a free test charge in the field\\
 \hline
 Inverse square law of gravitation & Newton's law of gravitation & Coulomb's law of force\\
 \hline
 Field strength & $g=\dfrac{F}{m}$ & $E=\dfrac{F}{q}$\\
 \hline
 Unit of field strength & $Nkg^{-1}$ or $ms^{-2}$ & $NC^{-1}$ or $Vm^{-1}$\\
 \hline
 Uniform fields & G is the same everywhere and field lines are parallel and equally spaced & E is the same everywhere and field lines are parallel and equally spaced \\
 \hline
 Unit of potential & $Jkg^{-1}$ & $JC^{-1}$ \\
 \hline
 Potential energy of two point mass or charges & $E_P=\dfrac{-Gm_1m_2}{r}$ & $E_P=\dfrac{Q_1Q_2}{4\pi\epsilon_0r}$\\
 \hline
 \multicolumn{3}{|c|}{Differences} \\
 \hline
 Action at a difference & Between any two masses & Between two charged objects \\
 \hline
 Force & Attracts only & Unlike charges attract; like charges repel \\
 \hline
 Constant of proportionality in force law & G & $\dfrac{1}{4\pi\epsilon_0}$ \\
 \hline

\end{tabular}

\end{document}

### 2018-02-20 Maths Notes/Mechanics/M2/Kinematics/Kinematics.tex
M2 Notes Update - Exam Questions

@@
 $$\arctan\Big(\sqrt{3}-\frac{40g}{98}\Big)=-66.2$$
+\newpage
+\begin{center}
+\underline{\Huge Problems with Vectors}
+\end{center}
+\includegraphics[width=10cm]{vector_problems.png}\\
+\textit{A ball B of mass 0.4 kg is struck by a bat at a point O which is 1.2 m above horizontal ground.
+The unit vectors i and j are respectively horizontal and vertical. Immediately before being
+struck, B has velocity $(-20i+4j) \ ms^{–1}$. Immediately after being struck it has velocity $(15i+
+16j) \ ms^{–1}$.\\
+After B has been struck, it moves freely under gravity and strikes the ground at the point A, as
+shown in the diagram above. The ball is modelled as a particle.}\\
+\\
+\textit{Calculate the magnitude of the impulse exerted by the bat on B. }
+\textcolor{red}{$$I=m(v-u)$$}
+Calculate the impulse as a vector using information from the question
+$$I=0.4(15i+16j-(-20i+4j)=14i+4.8j$$
+Calculate the magnitude of this vector
+$$|I|=\sqrt{14^2+4.8^2}=14.5Ns$$
+\\
+\textit{By using the principle of conservation of energy, or otherwise, find the speed of B when
+it reaches A.}
+Initial energy:
+$$\frac{1}{2}\times0.4\times\Big(\sqrt{15^2+16^2}\Big)^2=96.2J$$
+Energy gained from loss in GPE
+$$0.4\times9.8\times1.2=4.704J$$
+Add energies and set equal to final kinetic energy
+$$4.704+96.2=\frac{1}{2}\times0.4\times v^2$$
+Find v
+$$v=\sqrt{\frac{4.704+96.2}{0.5\times0.4}}=22.46$$
+\\
+\textit{Calculate the angle which the velocity of B makes with the ground when B reaches A.}\\
+Using the knowledge that horizontal velocity is constant and the speed is known, use cos to find the angle
+$$\arccos\Bigg(\frac{15}{22.5}\Bigg)=48\degree$$
+\\
+\textit{State two additional physical factors which could be taken into account in a refinement of
+the model of the situation which would make it more realistic}
+\begin{itemize}
+\item Air resistance
+\item Wind
+\item Rotation of ball (ball is not a particle)
+\end{itemize}
 

### 2018-02-20 Maths Notes/Mechanics/M2/Statics of rigid bodies/Statics of rigid bodies.tex
M2 Notes Update - Exam Questions

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{titlesec}
@@
 \end{itemize}
-
+\newpage
+\begin{center}
+\underline{\Huge Equilibrium of rigid bodies example}
+\end{center}
+\includegraphics[width=8cm]{eq_rigid.png}\\
+\textit{The diagram above shows a uniform rod AB of mass m and length 4a. The end A of the rod is
+freely hinged to a point on a vertical wall. A particle of mass m is attached to the rod at B. One
+end of a light inextensible string is attached to the rod at C, where AC = 3a. The other end of the
+string is attached to the wall at D, where AD = 2a and D is vertically above A. The rod rests
+horizontally in equilibrium in a vertical plane perpendicular to the wall and the tension in the
+string is T. }\\
+\\
+\textit{Show that T = $mg\sqrt{13}$}\\
+\\
+Take moments about A 
+$$3a\times T\cos\theta=2amg+4amg$$
+Calculate $\cos\theta$ from the lengths on the diagram
+$$\cos\theta=\frac{2}{\sqrt{3^2+2^2}}=\frac{2}{\sqrt{13}}$$
+Substitute in the value of $\cos\theta$ and divide through by $a$
+$$\frac{6}{\sqrt{13}}T=6mg$$
+Multiply both sides by $\frac{\sqrt{13}}{6}$
+$$T=mg\sqrt{13}$$
+\\
+\textit{The particle of mass m at B is removed from the rod and replaced by a particle of mass M which
+is attached to the rod at B. The string breaks if the tension exceeds $2mg\sqrt{13}$. Given that the
+string does not break,\\
+show that $M\leqslant\frac{5}{2}m$}\\
+\\
+Rewrite the moments equation with the new information from the question
+$$3a\times T\cos\theta=2amg+4aMg$$
+Write the inequality given
+$$T\leqslant 2mg\sqrt{13}$$
+Substitute in the value for T
+$$\frac{2mg+4Mg}{6}\sqrt{13}\leqslant2mg\sqrt{13}$$
+Simplify
+$$mg+2Mg\leqslant 6mg$$
+$$M\leqslant\frac{5}{2}m$$
 \end{document}

### 2018-02-20 Maths Notes/Mechanics/M2/Work, energy and power/Work, energy and power.tex
M2 Notes Update - Exam Questions
Notes Update
M2 Exam Questions

@@
 \usepackage{gensymb}
-
+\usetikzlibrary{positioning,scopes,decorations.text}
 \pgfplotsset{width=10cm,compat=1.9}
@@
 For work done against  gravity, use vertical distance.
-For work against friction, use distance in the direction of motion
+\subsection{Work done against friction}
+Work done against friction is:
+$$WD=\mu R\times \textrm{Distance}$$
+Where the distance is in the direction of motion
 \section{Energy}
@@
 \end{obeylines}
+\newpage
+\begin{center}
+\underline{\huge Work, Energy and Power Example - Conservation of energy}
+\end{center}
+\textit{A block of mass 10 kg is pulled along a straight horizontal road by a constant horizontal force
+of magnitude 70 N in the direction of the road. The block moves in a straight line passing
+through two points A and B on the road, where AB = 50 m.
+The block is modelled as a particle and the road is modelled as a rough plane.
+The coefficient of friction between the block and the road is $\frac{4}{7}$}\\
+\\
+\textit{Calculate the work done against friction in moving the block from A to B. }\\
+\\
+Calculate the force of friction
+$$F=\mu R=\frac{4}{7}\times10g=56N$$
+Multiply force by distance to find work done
+$$50\times56=2800J$$
+\\
+\textit{The block passes through A with a speed of $2ms^{-1}$.\\
+Find the speed of the block at B.}
+\\
+\\
+Subtract the work done against friction from the work done by the pulling force
+$$70\times50-2800=700J$$
+Write an expression for the change in kinetic energy
+$$\frac{1}{2}\times10\times v^2-\frac{1}{2}\times10\times2^2$$
+Set the excess energy from the work done equal to the change in kinetic energy and simplify
+$$700=5v^2-20$$
+$$v=12$$
+\newpage
+\begin{center}
+\underline{\huge Work, Energy and Power Example - Power}
+\end{center}
+\textit{A lorry of mass 2000 kg is moving down a straight road inclined at angle $\alpha$ to the horizontal,where $\sin\alpha=\frac{1}{25}$.
+The resistance to motion is modelled as a constant force of magnitude 1600 N.
+The lorry is moving at a constant speed of $14ms^{-1}$.\\
+Find, in kW, the rate at which the lorry's engine is working.}
+\\
+\\
+Draw a diagram to represent the information
+\def\iangle{35} % Angle of the inclined plane
+
+\def\down{-90}
+\def\arcr{0.5cm} % Radius of the arc used to indicate angles
+\begin{tikzpicture}[
+    force/.style={>=latex,draw=blue,fill=blue},
+    calculatedforce/.style={>=latex,draw=red,fill=red},
+    axis/.style={densely dashed,gray,font=\small},
+    M/.style={rectangle,draw,fill=lightgray,minimum size=0.5cm,thin},
+    m/.style={rectangle,draw=black,fill=lightgray,minimum size=0.3cm,thin},
+    plane/.style={draw=black,fill=blue!10},
+    string/.style={draw=red, thick},
+    pulley/.style={thick},
+    scale=2
+]
+
+    %% Free body diagram of M
+    \begin{scope}[rotate=\iangle]
+        \node[M,transform shape] (M) {};
+        % Draw axes and help lines
+
+        {[axis,-]
+            \draw (M.center) -- (0,-1) node[right] {};
+
+            % Indicate angle. The code is a bit awkward.
+
+            \draw[solid,shorten >=0.5pt] (\down-\iangle:\arcr)
+                arc(\down-\iangle:\down:\arcr);
+            \node at (\down-0.5*\iangle:1.3*\arcr) {$\alpha$};
+        }
+        % Forces
+        {[force,->]
+            % Assuming that Mg = 1. The normal force will therefore be cos(alpha)
+            \draw (M.south) -- ++(0,{cos(\iangle)*1.5}) node[above right] {$R$};
+            \draw (M.west) -- ++(-1,0) node[left] {$T_r$};
+            \draw (M.east) -- ++(1,0) node[above] {$1600$};   
+            }
+        {[calculatedforce,->]
+
+        \draw (0,-1) -- ++(-0.7,0) node[pos=0,right,sloped] {};
+        }
+        \draw[black, thick] (-3,-0.25) -- (2,-0.25);
+		\node at (0,-1.13) (nodeA) {};
+		\node at (-0.7,-1.13) (nodeB) {};
+		\draw [decoration={text along path,text={{\footnotesize $2000g\sin\theta$}{}},text align={center}},decorate]  (nodeB) -- (nodeA);
+    \end{scope}
+    % Draw gravity force. The code is put outside the rotated
+    % scope for simplicity. No need to do any angle calculations. 
+    \draw[force,->] (M.center) -- ++(0,-1.5) node[below] {$2000g$};
+    \draw[black, thick] (-2.31,-1.93) -- (1.76,-1.93);
+    \draw[thick, -] (-1.8,-1.93) arc (0:36:0.5);
+    \node[] at (-1.93,-1.8) {$\alpha$};
+\\
+;
+\end{tikzpicture}
+\\
+\\
+Equate forces
+$$T_r+2000g\sin\alpha=1600$$
+Solve
+$$T_r=1600-2000g\times\frac{1}{25}=816N$$
+Find power by multiplying force and velocity
+$$P=Fv=816\times14=11.4kW$$
 \end{document}

### 2018-02-27 Maths Notes/Statistics/S3/Estimation/Estimation.tex
S3 Notes Update

--- 2018-01-30 Maths Notes/Statistics/S3/Estimation/Estimation.tex
@@
 For this, the sample size must be greater than 50
+\section{Confidence intervals}
+A 95\% confidence interval is two values in which there is a probability of 0.95 that it will contain the population mean.\\
+\begin{tikzpicture}
+\begin{axis}[
+  no markers, domain=0:8, samples=100,
+  every axis y label/.style={at=(current axis.above origin),anchor=south},
+  every axis x label/.style={at=(current axis.right of origin),anchor=west},
+  height=5cm, width=12cm,
+  xtick={2,6},xticklabels={0.025,0.025}, ytick=\empty,
+  enlargelimits=false, clip=false,   ]
+  \addplot [fill=cyan!20, draw=none, domain=0:2] {gauss(4,1)} \closedcycle;
+  \addplot [fill=cyan!20, draw=none, domain=6:8] {gauss(4,1)} \closedcycle;
+  \addplot [very thick,cyan!50!black] {gauss(4,1)};
+  \node[] at (axis cs: 4,0.1) {95\%};
+\end{axis}
+\end{tikzpicture}
+\\
+Look up the value of one of the tails on the percentage points table and substitute into the formula.\\
+For example:\\
+At a 95\% confidence interval each of the tails is 0.025 and the corresponding z value is 1.96.\\
+$$\overline{x}\pm1.96\times\frac{\sigma}{\sqrt{n}}$$
+\section{Hypothesis testing}
+The test statistic for the population mean $\mu$ is $Z=\dfrac{X-\mu}{\frac{\sigma}{\sqrt{n}}}$\\
+\\
+A hypothesis test can be done quicker by finding the critical values from the percentage points table.
+\subsection{Example}
+$\mu=0.58 \ \sigma=0.015$\\
+Measured\\
+$n=50 \ \mu=0.577 \ \sigma=0.015$\\
+\\
+$H_0: \mu=0.50$\\
+$H_1: \mu\neq0.58$\\
+$$\overline{D}\sim N(0.58,\frac{0.015^2}{50})$$
+$$Z=\frac{0.577-0.58}{\sqrt{\frac{0.015^2}{50}}}=-1.41$$
+At 0.5\%  per level Z=2.5758
+$$-1.41>-2.5758$$
+Not in critical region so not significant, no evidence to reject $H_0$, the diameter of the bolts is not changed.
+\newpage
+\subsection{Hypothesis test for the difference between means}
+If $\overline{X}\sim N\Big(\mu_x,\frac{\sigma^2_x}{n}\Big)$ and $\overline{Y}\sim N\Big(\mu_y,\frac{\sigma^2_y}{n}\Big)$
+$$\overline{X}-\overline{Y}\sim N\Bigg(\mu_x-\mu_y,\frac{\sigma^2_x}{n}+\frac{\sigma^2_y}{n}\Bigg)$$
+$$z=\frac{\overline{X}-\overline{Y}-(\mu_x-\mu_y)}{\sqrt{\frac{\sigma^2_x}{n}+\frac{\sigma^2_y}{n}}}$$
+
 \end{document}

### 2018-02-27 Maths Notes/Statistics/S3/Estimation/Estimation.tex
S3 Notes Update

@@
 $$z=\frac{\overline{X}-\overline{Y}-(\mu_x-\mu_y)}{\sqrt{\frac{\sigma^2_x}{n}+\frac{\sigma^2_y}{n}}}$$
+\subsubsection{Example}
+\textit{The weight of boys and girls in a certain school are known to be normally distributed with standard deviations of 5kg and 8kg respectively.
+A random sample of 25 boys had a mean weight of 48kg and a random sample of 30 girls had a mean weight of 45kg.\\
+Stating your hypothesis clearly test, at the 5\% level of significance, whether or not there is evidence that the mean weight of boys in the school is greater than the mean weight of girls.}\\
+\\
+Write down the two distributions
+$$\overline{X_B}\sim N\Big(\mu_B,\frac{5^2}{25}\Big) \qquad \qquad \overline{X_G}\sim N\Big(\mu_G,\frac{8^2}{30}\Big)$$
+State the two hypotheses
+$$H_0: \ \mu_B=\mu_G$$
+$$H_1: \ \mu_B>\mu_G$$
+Find the $z$ value
+$$z=\frac{48-45-(0)}{\sqrt{\frac{5^2}{25}+\frac{8^2}{30}}}=1.6947$$
+Find the critical value from the percentage points table
+$$C.V.=1.6449$$
+Compare the critical value to the z value
+$$1.6449<1.6947$$
+Write conclusion
+As z is not in the critical region there is not enough evidence to reject $H_0$, there is not enough evidence to suggest that the mean weight of boys is greater than the mean weight of girls.
 

### 2018-03-06 Physics Notes/Nuclear Physics/Radioactivity/Radioactivity.tex
Physics Radioactivity notes update

@@
 \usepackage{tabularx}
+\usepackage{relsize}
 \usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing}
@@
 As N is proportional to Activity, Mass and Count Rate N can be replaced with any of these in the formula.
+\section{Nuclear radius}
+\subsection{High energy electron diffraction}
+When a beam of high energy electrons is directed at a thin solid sample of an element they are diffracted by the nuclei of the atoms.\\
+The electrons are diffracted by the nuclei because of their de Broglie wavelength, this is approximately equal to the radius of the nuclei.
+The detector measures the number of electrons per second at different angles.\\
+The scattering of the beam of electrons occurs due to the charge, this causes intensity to decrease as angle increases.\\
+The minimum on the graph can then be used to find the radius of the nucleus.
+\subsection{Dependence of nuclear radius on nucleon number}
+It can be shown that radius depends on mass according to:
+$$\mathlarger{R=r_0A^{\frac{1}{3}}}$$
+Where $r_0$ is the constant 1.05fm\\
+\\
+The graph of $\ln(R)$ against $\ln(A)$ gives a line with gradient $\frac{1}{3}$ and y intercept equal to $\ln(r_0)$\\
+\\
+The graph of R against $A^{\frac{1}{3}}$ gives a straight line through the origin with gradient $r_0$\\
+$$V=\frac{4}{3}\pi R^3=\frac{4}{3}\pi(r_0A^{\frac{1}{3}})^3=\frac{4}{3}\pi r_0^3A$$
+As $\textrm{Density}=\frac{\textrm{Mass}}{\textrm{Volume}}$
+$$\textrm{Density}=\frac{Au}{\frac{4}{3}\pi r_0^3A}=\frac{1u}{4\pi r_0^3}=\frac{1.661\times10^{-27}}{\frac{4}{3}\pi(1.05\times10^{-15})^3}=3.4\times10^{17}kgm^{-3}$$
+
 \end{document}

### 2018-03-06 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
FP2 Notes update, loci needs finishing

@@
 $k=2 \quad z=-0.951+0.309i$
+\newpage
+\section{Loci on the complex plane}
+\subsection{$\mathbf{|z-z_1|=r}$}
+$|z-z_1|=r$ is represented by a circle, centre $(x_1,y_1)$ with a radius r, where $z_1=x_1+iy_1$.\\
+\\
+This is the same as the Cartesian equation:
+$$(x-x_1)^2+(y-y_1)^2=r^2$$
+This looks like the graph:\\
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,ticks=none]
+\pgfplotsset{every tick label/.append style={font=\Large}}
+
+\draw (axis cs:1,2) circle [black, radius=3];
+    \node[] at (axis cs: 1,2) {$(x_1,y_1)$};
+    \node[] at (axis cs: 2,3.3) {$r$};
+
+           \node[anchor=west] (source) at (axis cs:1,2){};
+       \node (destination) at (axis cs:3,4.5){};
+       \draw[->](source)--(destination);
+\end{axis}
+\end{tikzpicture}
+\subsection{$\mathbf{|z-z_1|=|z-z_2|}$}
+$|z-z_1|=|z-z_2|$ is represented by a perpendicular bisector of the line segment joining points $z_1$ and $z_2$\\
+\\
+To find the Cartesian form, replace z with $x+iy$ and expand, squaring both sides to remove the modulus signs.\\
+\\
+This looks like the graph:\\
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,ticks=none]
+\pgfplotsset{every tick label/.append style={font=\Large}}
+
+    \node[] at (axis cs: 1,3) {$z_2$};
+    \node[] at (axis cs: 3,1) {$z_1$};
+\addplot coordinates { (-4,-4) (4,4) };
+
+\end{axis}
+\end{tikzpicture}\\
+For cases where there is a constant in front of one of the modulus signs, use the algebraic method to find the Cartesian form, then plot that.
+\newpage
+\subsection{$\mathbf{\arg(z-z_1)=\theta}$}
+$\arg(z-z_1)=\theta$ is represented by the half-line from the fixed point $z_1$, making an angle $\theta$ with a line from the fixed point $z_1$, parallel to the real axis.\\
+\\
+To find the Cartesian form, replace z with $x+iy$ and separate into the real and imaginary parts.
+Then use the trigonometric identity $\tan\theta=\dfrac{\textrm{Opposite}}{\textrm{Adjacent}}$ and simplify.\\
+\\
+When plotting remember that $\theta$ is the angle anticlockwise.\\
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[axis lines=middle,ymin=-2.5,ymax=2.5,xmin=-2.5,xmax=2.5,ticks=none]
+\pgfplotsset{every tick label/.append style={font=\Large}}
+
+\addplot coordinates { (0,0) (-2,1) };
+\draw (axis cs: 0.7,0) arc[radius=80, start angle= 0, end angle= 150];
+    \node[] at (axis cs: 0.7,0.7) {\Large $\theta$};
+\node[blue] at (axis cs: -2,1.2) {\LARGE $z_1$};
+
+\end{axis}
+\end{tikzpicture}
+\subsection{$\mathlarger{\mathbf{\arg\Big(\frac{z-z_1}{z-z_2}\Big)}}$}
+$\mathlarger{\arg\Big(\frac{z-z_1}{z-z_2}\Big)}$ represents an arc anticlockwise between $z_1$ and $z_2$
+
 \end{document}

### 2018-03-06 Maths Notes/Further Pure/FP2/Polar Coordinates/Polar Coordinates.tex
FP2 Notes update, loci needs finishing

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - FP2}
\rfoot{Page \thepage}

\usepackage{cancel}

\begin{document}
\begin{center}
\underline{\huge Polar Coordinates}
\end{center}
\begin{tikzpicture}[scale=0.7]
\begin{axis}[axis lines=middle,ymin=0,ymax=2.5,xmin=0,xmax=2.5,ticks=none]
\pgfplotsset{every tick label/.append style={font=\Huge}}

\addplot coordinates { (0,0) (2,2) };
\addplot [dashed] coordinates { (2,0) (2,2) };
\addplot [dashed] coordinates { (0,2) (2,2) };

\draw (axis cs: 0.7,0) arc[radius=70, start angle= 0, end angle= 45];
    \node[] at (axis cs: 0.5,0.2) {\huge $\theta$};
\node[blue] at (axis cs: 1,1.2) {\huge $r$};
\node[black] at (axis cs: 2.1,1) {\huge $y$};
\node[black] at (axis cs: 1,2.1) {\huge $x$};
\end{axis}
\end{tikzpicture}\\
Usual conventions are either $-\pi<\theta\leqslant\pi$ or $0\leqslant\theta<\pi$\\
\\
$x=r\cos\theta$\\
$y=r\sin\theta$\\
$r^2=x^2+y^2$\\
$\theta=\arctan\Big(\dfrac{y}{x}\Big)$
\section{Converting between polar and Cartesian form}
\subsection{Example 1}
\textit{Find the Cartesian equation of:}
$r=5$
$$\sqrt{x^2+y^2}=5$$
$$x^2+y^2=25$$
\subsection{Example 2}
\textit{Find the Cartesian equation of:}
$$r=2+\cos2\theta$$
Replace r and convert $\cos2\theta$
$$\sqrt{x^2+y^2}=2+\cos^2\theta-\sin^2\theta$$
Convert $\sin^2\theta$ and $\cos^2\theta$
$$\sqrt{x^2+y^2}=2+\frac{x^2}{x^2+y^2}-\frac{y^2}{x^2+y^2}$$
Multiply all terms by $x^2+y^2$
$$(x^2+y^2)^{\frac{3}{2}}=3x^2+y^2$$
\end{document}

### 2018-03-07 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
FP2 Loci Up to Date

@@
 \section{Loci on the complex plane}
-\subsection{$\mathbf{|z-z_1|=r}$}
+\subsection{Lines}
+\subsubsection{$\mathbf{|z-z_1|=r}$}
 $|z-z_1|=r$ is represented by a circle, centre $(x_1,y_1)$ with a radius r, where $z_1=x_1+iy_1$.\\
@@
 \end{tikzpicture}
-\subsection{$\mathbf{|z-z_1|=|z-z_2|}$}
+\subsubsection{$\mathbf{|z-z_1|=|z-z_2|}$}
 $|z-z_1|=|z-z_2|$ is represented by a perpendicular bisector of the line segment joining points $z_1$ and $z_2$\\
@@
 \newpage
-\subsection{$\mathbf{\arg(z-z_1)=\theta}$}
+\subsubsection{$\mathbf{\arg(z-z_1)=\theta}$}
 $\arg(z-z_1)=\theta$ is represented by the half-line from the fixed point $z_1$, making an angle $\theta$ with a line from the fixed point $z_1$, parallel to the real axis.\\
@@
 \end{tikzpicture}
-\subsection{$\mathlarger{\mathbf{\arg\Big(\frac{z-z_1}{z-z_2}\Big)}}$}
+\subsubsection{$\mathlarger{\mathbf{\arg\Big(\frac{z-z_1}{z-z_2}\Big)}}$}
 $\mathlarger{\arg\Big(\frac{z-z_1}{z-z_2}\Big)}$ represents an arc anticlockwise between $z_1$ and $z_2$
+\subsection{Regions}
+\subsubsection{$\mathbf{|z-(2+3i)|\leqslant3}$}
+This is the area inside the circle represented by $|z-(2+3i)|\leqslant3$\\
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,ticks=none]
+\pgfplotsset{every tick label/.append style={font=\Large}}
 
+\filldraw[gray,opacity=0.6] (axis cs:1,2) circle [black, radius=3];
+\draw (axis cs:1,2) circle [black, radius=3];
+\end{axis}
+\end{tikzpicture}
+\newpage
+\subsubsection{$\mathbf{|z-3|<|z-5|}$}
+This is the area to one side of the perpendicular bisector represented equal to $|z-3|=|z-5|$\\
+\pgfplotsset{compat=newest}
+
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,xtick={3,4,5}, ytick={0},ytick pos=right]
+\addplot coordinates { (4,-5) (4,5) };
+\filldraw [gray,opacity=0.6] (-5,-5) rectangle (4,5);
+\end{axis}
+\end{tikzpicture}
+\subsubsection{$\mathbf{0\leqslant\arg(z-2)<\frac{\pi}{4}}$}
+This is the area between the positive real axis and the half line equal to $\arg(z-2)=\frac{\pi}{4}$\\
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,xtick={2}, ytick={0},ytick pos=right]
+\addplot coordinates { (2,0) (5,3) };
+\filldraw[gray,opacity=0.6] (2,0) -- (5,0) -- (5,3) -- cycle;
+
+\end{axis}
+\end{tikzpicture}
 \end{document}

### 2018-03-07 Maths Notes/Further Pure/FP2/Polar Coordinates/Polar Coordinates.tex
Polar Coordinates notes up to date

@@
 $$(x^2+y^2)^{\frac{3}{2}}=3x^2+y^2$$
+\newpage
+\section{Sketching polar curves}
+To plot less standard types we look for axes intercepts and max and min values
+\subsection{Standard types}
+\subsubsection{r=a}
+A circle, centre (0,0) with a radius of a
+\subsubsection{$\theta=\alpha$}
+A half line starting from (0,0) making an angle of $\alpha$ with the initial line (positive x axis)
+\subsubsection{$r=a\theta$}
+A spiral starting at the origin
+\subsection{Cardioid type}
+\subsubsection{$r=a(1+\cos\theta)$}
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[
+    axis lines=center,
+    axis equal image,
+    enlargelimits=true,
+     ]
+    \addplot[data cs=polar,red,domain=0:360,samples=360,smooth] (x,{6*(1+cos(x))});
+\end{axis}
+\end{tikzpicture}
+\subsubsection{$r=a(p+q\cos\theta)$}
+\paragraph{p=q}
+Factor out the value of p and plot as normal
+\paragraph{$p\geqslant2q$}
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[
+    axis lines=center,
+    axis equal image,
+    enlargelimits=true,
+     ]
+    \addplot[data cs=polar,red,domain=0:360,samples=360,smooth] (x,{(5+2*cos(x))});
+\end{axis}
+\end{tikzpicture}
+\newpage
+\paragraph{$q\leqslant p<2q$}
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[
+    axis lines=center,
+    axis equal image,
+    enlargelimits=true,
+     ]
+    \addplot[data cs=polar,red,domain=0:360,samples=360,smooth] (x,{(3+2*cos(x))});
+\end{axis}
+\end{tikzpicture}
+\subsubsection{$r^2=a^2\cos2\theta$}
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[
+    axis lines=center,
+    axis equal image,
+    enlargelimits=true,
+     ]
+    \addplot[data cs=polar,red,domain=0:360,samples=10000] (x,{sqrt(cos(2*x))});
+\end{axis}
+\end{tikzpicture}
+\\
+The 4 asymptotes are half lines at $\theta=\frac{\pi}{4},\frac{3\pi}{4},\frac{5\pi}{4},\frac{7\pi}{4}$
 \end{document}

### 2018-03-08 Physics Notes/Turning Points/Wave Particle Duality/Electromagnetic Waves/Electromagnetic Waves.tex
Turning Points notes up to date

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{gensymb}
\usepackage{fancyhdr}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage{amsmath}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Turning Points}
\hyphenpenalty=10000
\begin{document}
\begin{center}
\underline{\huge Electromagnetic Waves}
\end{center}
\section{The nature of electromagnetic waves}
Electromagnetic waves, when passed through certain materials, are polarised, this caused the model of waves to be predicted as transverse, rather than longitudinal.\\
Maxwell then presented equations linking oscillating electric and magnetic fields, and predicted the existence of electromagnetic waves.\\
Maxwell predicted that an electromagnetic wave could exist when a changing magnetic field creates a changing magnetic field and so on. He explained that this self-sustaining electromagnetic wave could travel through space as a transverse wave with the electric and magnetic field components oscillating in phase, but at right angles to each other and the direction of travel.
\section{Maxwell's Formula}
Maxwell's prediction lead to a formula for the speed of light in a vacuum:
$$c=\frac{1}{\sqrt{\mu_0\epsilon_0}}$$
Where:\\
$\mu_0$ - Permeability of free space. It relates the magnetic flux density of a magnetic field to the electric current that created it. It has the value of $4\pi\times10^{-7}Hm^{-1}$ where the unit H is the Henry.\\
$\epsilon_0$ - Permittivity of free space. It relates the electric field strength to the charge that creates it. It has the value of $8.85\times10^{-12}Fm^{-1}$

\section{Hertz and radio waves}
Twenty years after Maxwell had theoretically predicted the existence of radio waves in his equations, Heinrich Hertz demonstrated how such waves could be produced and detected.\\
\includegraphics[width=6cm]{hertz_1.jpg}\\
While this diagram shows more detail than required, he found that:
\begin{itemize}
\item Radio waves were produced when a spark lept between the spark balls across an induction coil
\item These radio waves passed through the conductive loop, inducing an EMF across the loop which caused sparks to leap across the spark balls across the ring.
\end{itemize}
Hertz demonstrated that the waves couldn't pass through metal, as the sparks stopped when a metal sheet was placed in front of the ring. He then realised that the metal sheet reflects the waves, as a concave metal sheet behind the source increased the number of sparks across the ring due to more waves being reflected back towards the ring. Hertz also illustrated that the waves pass straight through insulating materials.
\subsection{Measurement of wavelength}
Hertz created standing waves by using a metal sheet to reflect waves back to the source. He moved the detector along a line from the source to the sheet, and observed nodes and antinodes. He calculated the distance between the nodes to be 33cm, meaning that the wavelength must be 66cm.
\subsection{Demonstration of polarity}
Hertz created a reflector that could focus radio waves onto a detector such that the oscillating electric fields creates an alternating pd across the detector, creating sparks at the spark plug. He discovered that when the detector was parallel to the spark gap of the source he obtained a strong signal, which reduced to 0 once the detector had been rotated $90\degree$. This implies that the waves created were polarised - at $90\degree$ the plane of the oscillating electric field was perpendicular to the detector aerials, and no alternating pd was induced.
\section{Fizeau's determination of the speed of light and its implications}
\includegraphics[width=8cm]{fizeau.JPG}\\
Fizeau’s experiment involved using a cog wheel rotating at high speeds while a narrow beam was directed parallel to the axis of the wheel so that it could pass through the gaps between teeth as the wheel rotated.\\
\\
This meant successive teeth and gaps would therefore chop the beam into pulses of light which then travelled to a distant mirror and were reflected back. If the observer could see the reflected light then it meant that the pulses of light were returning back through a gap.\\
\\
Fizeau increased the rotation frequency of the cog wheel from rest until the reflected light could not be seen, calling this frequency $f_0$. At this frequency the time taken for each pulse to travel from the wheel to the mirror and return (a distance equal to 2D, where D equals the distance between the wheel and the mirror) would be equal to the time, t, taken for a gap to be replaced by a tooth.
\newpage
Time for one rotation:
$$T=\frac{1}{f_0}$$
Time for the wheel to move one tooth, where n is the number of teeth
$$t=\frac{T}{2N}$$
Combine the two above equations
$$t=\frac{1}{2f_0N}$$
Apply $\textrm{Speed}=\frac{\textrm{Distance}}{\textrm{Time}}$
$$c=\frac{2D}{\frac{1}{2f_0N}}=4Df_0N$$
\\
Fizeau had a 720 toothed wheel 8633m away from the mirror and found $f_0$ to be equal to 12.6Hz, giving a value of 313,000 $\textrm{kms}^{-1}$ for the speed of light.\\
Fizeau’s determination of the speed of light was important because it was the first terrestrial method of finding the speed of light and was markedly more precise than the previous speed of light found by Ole Rømer (240,000 km/s). It was the first terrestrial method to confirm the speed of light as finite. Furthermore his value agreed with Maxwell’s theoretical value and hence validated Maxwell’s theory of electromagnetic waves.

\end{document}

### 2018-03-08 Physics Notes/Turning Points/Wave Particle Duality/Newton's CT of light/Newton's CT of Light.tex
Turning Points notes up to date

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{blindtext}
\usepackage{textcomp}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins and Fiona Turnbull}
\lhead{A Level Physics - Turning Points}
\begin{document}
\begin{center}
\underline{\huge Newton\textquotesingle s Corpuscular Theory of light}
\end{center}
Definition - Light is made up of tiny particles called corpuscles that always travel in a straight line
\section{Reflection and refraction}
Newton believed this theory was true as it can explain both reflection and refraction\\
\includegraphics[width=6cm]{reflection.png}
\includegraphics[width=6cm]{refraction.png}\\
\\
\textbf{Reflection} - These corpuscles have perfectly elastic collisions, meaning that the speed before is the speed after. The horizontal velocity doesn't change, the vertical velocity is inverted. Therefore angle of incidence equals angle of reflection.\\
\\
\textbf{Refraction} - Newton said the corpuscles were attracted into the material, causing them to travel faster, causing the component of the velocity perpendicular to the boundary to increase, causing angle with the normal to reduce. Newton was wrong.
\section{Rival theories}
Christiaan Huygens proposed the wave front theory, which is the theory we have been taught to describe refraction and diffraction. This described light travelling slower in a more dense material.\\
\\
Why Huygens' theory was rejected:
\begin{itemize}
\item It was not possible to measure the speed of light at that scale at that time, meaning neither theory could be proved correct or incorrect.
\item Newton had a better reputation
\item The wave theory only considered longitudinal waves so couldn't explain polarisation.
\end{itemize}

\end{document}

### 2018-03-08 Physics Notes/Turning Points/Wave Particle Duality/The significance of Young's double slit experiment/Young's Double slit.tex
Turning Points notes up to date

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{blindtext}
\usepackage{textcomp}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Turning Points}
\begin{document}
\begin{center}
\underline{\huge The Significance of Young’s double slit experiment}
\end{center}
\section{Explanation for fringes}
Young discovered that the creation of an interference pattern required two light sources that had a constant phase difference and so had to be created from the same original source. Young had discovered how to create coherent sources of light.\\
\includegraphics[width=8cm]{double_slit.png}\\
As interference is a wave property, this disproved Newton's Corpuscular Theory and Proved Huygens' Wave front theory.
\section{Delayed acceptance of Huygen's  Wave front theory}
Despite Young's conclusive evidence against Newton's Corpuscular Theory, there was still reluctance to drop the theory.\\
The theory wasn't dropped until Fizeau measured the speed of light in water and air, and calculated that the speed of light in water is slower than that in air, finally disproving Newton's corpuscular theory.
\end{document}

### 2018-03-08 Physics Notes/Turning Points/Wave Particle Duality/The discovery of photoelectricity/Photoelectricity.tex
Physics Turning Points notes update

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{blindtext}
\usepackage{textcomp}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Turning Points}
\begin{document}
\begin{center}
\underline{\huge The Discovery of photoelectricity}
\end{center}
\section{The ultraviolet catastrophe and black body radiation}
A black body is a theoretical object which is a perfect absorber and emitter of radiation, it would not reflect any radiation, nor allow it to be transmitted through.\\
The ultraviolet catastrophe is the situation where short wavelength radiation is incident on a black body, causing it to emit an infinite amount of power per unit wavelength.
\section{Planck's interpretation in terms of quanta}
Max Planck suggested that the energy from electromagnetic waves was quantised, rather than continuous, which solves the problem of the ultraviolet catastrophe. He formulated the equation:
$$E=hf$$
Where h is Planck's constant\\
\\
This theory was later used to explain photoelectricity.
\section{The failure of classical wave theory to explain observations on photoelectricity}
Predictions by Huygens' Wave theory:
\begin{itemize}
\item For a particular frequency, the energy of the wave depends on its amplitude and is spread evenly over a wave front. This would mean that each free electron in the metal surface would get a small amount of energy from each wavelength, so after a period of time would gain sufficient energy to escape.
\item There would be a time lag between the light being incident and the emission of an electron
\item Any frequency would be able to cause electron emission given enough time
\end{itemize}
These predictions are all wrong.
\section{Einstein's Explanation of photoelectricity}
Einstein proposed a particle theory of light, where electromagnetic waves are emitted in discrete amounts of energy of size $hf$. Einstein called a quantum of light a photon, and visualised the photoelectric effect as an interaction between one photon and one electron in the metal surface, with the photon giving all its energy to the electron, causing it to disappear.\\
He suggested that in order for an electron to leave the metal surface it must have enough energy to overcome the attractive electrical force holding it there, this energy is the work function, with symbol $\phi$. \\
If 
\begin{itemize}
\item $hf>\phi$ then the electron can escape from the surface
\item $hf<\phi$ then the electron gains energy, but does not escape the surface
\item $hf=\phi$ then the electron has enough energy to escape the metal but has zero kinetic energy once it has escaped. This frequency is called the threshold frequency, with symbol $f_0$
\end{itemize}
The kinetic energy the electron has once it has left the metal varies from zero to a maximum value as electrons have to do different amounts of work depending on how far they have to move through the metal.\\
He created the equation:
$$\frac{1}{2}mv^2=hf-\phi$$
\end{document}

### 2018-03-08 Physics Notes/Turning Points/Wave Particle Duality/Wave particle duality/Wave particle duality.tex
Physics Turning Points notes update

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{blindtext}
\usepackage{textcomp}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Turning Points}
\begin{document}
\begin{center}
\underline{\huge Wave particle duality}
\end{center}
\section{de Broglie's hypothesis}
de Broglie created the equation for the energy of a photon:
$$E=\frac{hc}{\lambda}$$
And also deduced that photon momentum is:
$$p=\frac{h}{\lambda}$$
This caused de Broglie to put forward the idea that all particles had wave like properties.\\
The de Broglie wavelength is calculated using the equation
$$\lambda=\frac{h}{p}=\frac{h}{mv}$$
\section{Electron diffraction}
Calculation to find the wavelength of electrons from an electron gun:\\
\\
Set kinetic energy equal to eV
$$\frac{1}{2}mv^2=eV$$
Multiply both sides by m and rearrange
$$m^2v^2=2meV$$
Squarerooting
$$mv=\sqrt{2meV}$$
Combining with de Broglie's equation $\lambda=\frac{h}{mv}$
$$\lambda=\frac{h}{\sqrt{2meV}}$$
\\
\\
When electrons are diffracted they show a very similar pattern to the pattern when photons are diffracted, evidence for the wavelike nature of electrons.

\end{document}

### 2018-03-09 Physics Notes/Nuclear Physics/Radioactivity/Radioactivity.tex
Radioactivity notes update

@@
 \tikzstyle{arrow} = [thick,->,>=stealth]
+
+\setcounter{secnumdepth}{4}
+\titleformat{\paragraph}
+{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
+\titlespacing*{\paragraph}
+{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
+\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
+\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
+\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
+
 \begin{document}
@@
 $$\textrm{Density}=\frac{Au}{\frac{4}{3}\pi r_0^3A}=\frac{1u}{4\pi r_0^3}=\frac{1.661\times10^{-27}}{\frac{4}{3}\pi(1.05\times10^{-15})^3}=3.4\times10^{17}kgm^{-3}$$
-
+\newpage
+\section{Radioactive isotopes in use}
+\subsection{Radioactive dating}
+\subsubsection{Carbon dating}
+Carbon-14 is used for carbon dating, this has a half life of 5570 years, meaning that there is very little decay while a plant is alive.
+However once the tree has died, the percentage of carbon-14 reduces as it decays.
+Because activity is proportional to the number of atoms still to decay, measuring the activity of the dead sample allows its age to be calculated.
+\paragraph{Example}
+\textit{A sample of dead wood is found to have an activity of 0.28Bq. An equal mass of living wood is found to have an activity of 1.3Bq.Calculate the age of the sample\\
+\\
+The half life of carbon-14 is 5570 years }\\
+\\
+Calculate the half life in seconds
+$$T_{\frac{1}{2}}=5570\times365\times24\times3600=1.76\times10^{11}s$$
+Calculate the decay constant using the formula on the formula sheet
+$$\lambda=\frac{\ln(2)}{1.76\times10^{11}}$$
+Use the formula $A=A_0e^{-\lambda t}$
+$$0.28=1.8e^{-\lambda t}$$
+Rearrange to find $\lambda t$
+$$e^{-\lambda t}=\frac{0.280}{1.30}=0.215$$
+$$\lambda t=1.535$$
+Rearrange and substitute in $\lambda$ to find t
+$$t=\frac{1.535}{\lambda}=\frac{1.535}{3.96\times10^{-12}}=3.88\times10^{11}s=12300 \ \textrm{years}$$
+\subsubsection{Argon dating}
+$$^{40}_{19}K+^0_{-1}e\rightarrow^{40}_{18}Ar+\nu_e$$
+The effective half-life of the decay of $^{40}_{19}K$ is 1250 million years. The age of the rock can be calculated by measuring the proportion of argon-40 to potassium-40.\\
+\\
+$^{40}_{19}K$ also decays to $^{40}_{20}Ca$.
+This process is eight times more probable than electron capture.
+This means that if there was one argon atom for every N potassium atoms, there would originally be N+9 potassium atoms, eight decaying to Calcium and one decaying to argon.
+\paragraph{Example}
+\textit{Suppose for every 4 potassium-40 atoms present a certain rock now mas 1 argon-40 atom, what is the age of the sample?}\\
+\\
+Find the values of $N$ and $N_0$ 
+$$N=4 \qquad N_0=4+9=13$$
+Substitute these values into $N=N_0e^{-\lambda t}$
+$$4-13e^{-\lambda t}$$
+Rearrange to find t 
+$$t=\frac{-\ln\frac{4}{13}}{\lambda}$$
+Substitute $\frac{\ln(2)}{T_{\frac{1}{2}}}$ for $\lambda$
+$$t=\frac{-\ln(\frac{4}{13})}{0.693}T_{\frac{1}{2}}$$
+Substitute in the known value of the half life of potassium
+$$1.7\times T_{\frac{1}{2}}=2120 \  \textrm{million years}$$
+\subsection{Radioactive tracers}
+A radioactive tracer follows the path of a substance through a system. These should:
+\begin{itemize}
+\item Have a half life stable enough for the necessary measurements to be made and short enough to decay quickly after use
+\item Emit $\beta$ radiation of $\gamma$ radiation so it can be detected outside the flow path
+\end{itemize}
+\subsection{Industrial uses}
+\subsubsection{Engine wear}
+The rate of wear of a piston ring can be measured by fitting a ring that is radioactive. This causes transfer of radioactive atoms from the ring to the engine oil, which can then be measured
+\subsubsection{Underground pipe leaks}
+Radioactive tracer is injected in the flow, A detector at the surface measures the leakage
+\subsubsection{Investigating the uptake of fertilisers by plants}
+The fertiliser is a $\beta^-$ emitter and so can be measured in the leaves.
+\subsubsection{Thickness monitoring}
+The thickness of continuous materials can be measured by placing a $\beta$ emitter and detector on either side of the material. This allows materials such as foil to have a uniform thickness.
+\subsubsection{Power sources for remote devices}
+Satellites, weather sensors etc can be powered using a radioactive isotope in a thermally insulated sealed container which absorbs all the radiation emitted by the isotope.
+A thermocouple attached to the container produces electricity of the container being warm.
 \end{document}

### 2018-03-09 Maths Notes/Statistics/S3/Goodness of fit and contingency tables/Goodness of fit and contingency tables.tex
S3 Notes Up to date

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{enumitem}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty=10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S3}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Goodness of fit and contingency tables}
\end{center}
Method for testing goodness of fit:
\begin{enumerate}
\item Determine which distribution would conceptually be most appropriate
\item Set significance level
\item Estimate parameters (if necessary) from observed data
\item Form hypotheses $H_0$ and $H_1$
\item Calculate expected frequencies
\item Combine expected frequencies so that none are $<5$
\item Find degrees of freedom
\item Calculate critical value of $\chi^2$ from the table
\item Calculate $\sum\frac{(O_i-E_i)^2}{E_i}$
\item See if the value is significant and draw conclusion
\end{enumerate}
$X^2$ is distributed with a chi squared distribution $\chi^2_\nu$\\
Where $\nu=$ degrees of freedom\\
$$\textrm{The number of degrees of freedom}=\textrm{Number of classes (after combining)}-1$$
\newpage
\subsection{Example}
\textit{The data in the table is thought to be modelled by a binomial $B(10,0.2)$. Use the table for the binomial cumulative distribution function to find expected values, and conduct a test to see if this is a good model. Use a 5\% significance level.}\\
\\
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
$x$&0&1&2&3&4&5&6&7&8\\
\hline
Freq of $x$&12&28&28&17&7&4&2&2&0\\
\hline
\end{tabular}
\\
\\
\textcolor{red}{Define Hypotheses}
$$H_0: \textrm{A B(10,0.2) distribution is suitable for the results}$$
$$H_1: \textrm{The distribution is not suitable for the results}$$
\textcolor{red}{Calculate the sum of frequencies}
$$N=100$$
\textcolor{red}{Complete the table of probabilities and expected frequencies, expected frequency=probability$\times$N}\\
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|X|X|}
\hline
$x$&0&1&2&3&4&5&6&7&8\\
\hline
$p(x)$&0.1074&0.2684&0.3020&0.2013&0.0881&0.0264&0.0055&0.0008&0.0001\\
\hline
Expected freq&10.74&26.84&30.20&20.13&8.81&2.64&0.55&0.08&0.01\\
\hline
\end{tabularx}
\\
\\
\textcolor{red}{As expected frequencies need to be greater than or equal to five, combine all probabilities greater than or equal to four}
\\
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
\hline
$x$&0&1&2&3&$\geqslant4$\\
\hline
$O_i$&12&28&28&17&15\\
\hline
$E_i$&10.74&26.84&30.20&20.13&12.09\\
\hline
$\dfrac{(O_i-E_i)^2}{E_i}$&0.1478&0.0501&0.1603&0.4867&0.7004\\
\hline
\end{tabularx}
\textcolor{red}{Find the value of $\nu$}
$$\nu=5-1=4$$
\textcolor{red}{Find the value of $X^2$}
$$X^2=0.1478+0.0501+0.1603+0.4867+0.7004=1.5453$$
\textcolor{red}{Compare the value of $X^2$ to the value on the tables corresponding to the 5\% significance level and $\nu=4$}
$$9.488>1.5453$$
\textcolor{red}{Write conclusion}
\begin{center}
Not in critical region so insufficient evidence to reject $H_0$, binomial is a possible model
\end{center}

\end{document}

### 2018-03-12 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
FP2 translation notes

@@
 \end{tikzpicture}
+\section{Translations}
+\begin{itemize}
+\item $w=z+a+ib$ represents a translation with translation vector $\begin{pmatrix}
+a\\b
+\end{pmatrix}$
+\item $w=kz$ represents an enlargement with scale factor $k$ centre $(0,0)$
+\item $w=kz+a+ib$ represents an enlargement scale factor $k$ centre $(0,0)$ followed by a translation with translation vector $\begin{pmatrix}
+a\\b
+\end{pmatrix}$
+\item $w=z^2$ multiply a shape by itself, for example a circle of radius 4 would go to radius 16
+\end{itemize}
 \end{document}

### 2018-03-12 Physics Notes/Turning Points/Wave Particle Duality/Microscopes/Microscopes.tex
Microscopes notes update

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{blindtext}
\usepackage{textcomp}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Turning Points}
\begin{document}
\begin{center}
\underline{\huge Microscopes}
\end{center}
\section{Producing electrons with de Broglie wavelength the size of an atom}
As shown in electron diffraction:
$$\lambda=\frac{h}{\sqrt{2meV}}$$
This can be rearranged to find the voltage required to produce electrons of a given wavelength. 
$$\lambda^2=\frac{h^2}{2meV}$$
$$V=\frac{h^2}{2me\lambda^2}$$
\section{Transmission electron microscope}
This involves firing a beam of electrons with anode voltage of 300kV at an ultra-thin specimen contained within the evacuated column of the microscope.\\
This beam of electrons if focused by a cylindrical magnetic condenser lens, which deflects electrons to form a wide beam that is incident on the spectrum.\\
\includegraphics[width=8cm]{tem.png}\\
When an electron wave encounters the specimen it can either:
\begin{itemize}
\item Pass straight through the specimen without interacting
\item Get absorbed
\item Diffract
\end{itemize}
The electrons that pass through the specimen form the main beam, and a series of additional magnetic lenses direct and focus this beam onto a fluorescent screen. This creates an image when the electrons strike a florescent screen. The darker areas of the image represent the parts of the specimen that are thicker as more electrons are absorbed.\\
\\
The image detail can be improved by increasing the anode voltage of the electron gun.\\
\\
The image detail may reduce when travelling through the specimen as some electrons may have a loss of speed, causing the magnetic lenses to be unable to focus the electrons, a type of material dispersion.
\section{Scanning tunnelling microscope}
The STM has a very fine conducting probe, which is used to scan a small area of the surface of a conducting sample. The probe is positioned so that the tip of the probe is 1nm above the surface of the sample. The STM creates images using an effect known as quantum tunnelling, which allows some of the electrons in the tip of the probe or the sample to move across the 1nm gap, creating a tunnelling current between the sample and the probe. A small voltage is maintained between the tip of the probe and the sample to ensure that the electrons cross the gap in only one direction, from negative to positive.\\
\includegraphics[width=5cm]{stm.png}\\
\\
Quantum tunnelling occurs because of the wave nature of electrons. Just as light can pass through a very thin metal film because the amplitude of the light is not reduced to zero by its passage through the film, matter waves can pass through an apparent barrier, such as an insulating air gap in a conducting circuit, if the gap is sufficiently narrow.\\
At room temperature the de Broglie wavelength of an electron in a metal is about 1nm, comparable to the gap between the sample surface and the probe tip, meaning there is a small probability that electrons can jump across the gap.\\
\\
A STM can be used in one of two ways:
\subsection{Method 1 - Constant height}
In this method the probe is kept at a constant height, so that only undulations in the surface of the sample affect the size of the gap. The smaller the gap, the more electrons move across the gap per second, increasing the current, which can then be measured.\\
The voltage between the surface and the probe tip must be kept constant, so the current at a given height is constant.\\
This has a vertical resolution of 0.001nm, much smaller than the smallest atom
\subsection{Method 2 - Constant current}
In this method the height of the probe is altered to keep the tunnelling current constant, and then variations in the vertical position of the probe can be used to image the surface of the sample.
\end{document}

### 2018-03-13 Maths Notes/Statistics/S3/Goodness of fit and contingency tables/Goodness of fit and contingency tables.tex
S3 Notes Update

@@
 \newpage
-\subsection{Example}
+\subsection{Testing a Binomial distribution as a model}
 \textit{The data in the table is thought to be modelled by a binomial $B(10,0.2)$.
@@
 \end{center}
-
+\newpage
+\subsection{What to do when p is not given}
+\textit{A study of the number of girls in families with 5 children was done on 100 such families. The results are summarised in the following table.}\\
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+Num girls(r)&0&1&2&3&4&5\\
+\hline
+Frequency(f)&13&18&38&20&10&1\\
+\hline
+\end{tabular}\\
+\textit{Test, at the 5\% significance level, whether or not a binomial distribution is a good model.}\\
+\\
+\textcolor{red}{State hypotheses}
+\begin{center}
+$H_0$: The binomial distribution is a good model\\
+$H_1$: The binomial distribution is not a suitable model
+\end{center}
+\textcolor{red}{Calculate the mean}
+$$\overline{x}=\frac{0\times13+1\times18+2\times38+3\times20+4\times10+5\times1}{100}=1.99$$
+\textcolor{red}{Divide the mean by n, the number of children in the families, 5, to find p.}
+$$p=\frac{1.99}{5}=0.398$$
+\textcolor{red}{Using the values of n and p, find the probability the value is a certain number, multiply by 100 to find the expected value.}
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|}
+\hline
+r&0&1&2&3&4&5\\
+\hline
+p(r)&0.079&0.261&0.3456&0.229&0.0755&0.0009\\
+\hline
+$E_i$&7.91&26.14&34.56&22.85&7.55&0.09\\
+\hline
+\end{tabularx}\\
+\\
+\textcolor{red}{Use the values in the two above tables to find the values of $O_i$, $E_i$ and $X^2$, combine expected values when under 5}\\
+\\
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|}
+\hline
+r&0&1&2&3&$>3$&Total\\
+\hline
+$O_i$&13&18&38&20&11&\\
+\hline
+$E_i$&7.91&26.14&34.56&22.85&8.54&\\
+\hline
+$\frac{(O_i-E_i)^2}{E_i}$&3.28&2.53&0.34&0.36&0.71&7.22\\
+\hline
+\end{tabularx}
+\textcolor{red}{Calculate the degrees of freedom, subtracting one for a constant frequency sum and one for the estimated p}
+$$\nu=5-1-1=3$$
+\textcolor{red}{Find the value of $\chi^2_3$ at a 5\% significance level}
+$$\chi^2_3=7.815$$
+\textcolor{red}{Compare the value of $\chi^2_3$ to $X^2$ to determine the correct hypothesis}
+$$7.22<7.81$$
+\begin{center}
+Not in critical region, so not significant, do not reject $H_0$, binomial is a suitable model
+\end{center}
+\newpage
+\subsection{Testing a poisson distribution as a model}
+\textit{The numbers of telephone calls arriving at an exchange in six-minute periods were recorded over a period of 8 hours, with the following results}\\
+\\
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
+\hline
+Num calls(r)&0&1&2&3&4&5&6&7&8\\
+\hline
+Freq(f)&8&19&26&13&7&5&1&1&0\\
+\hline
+\end{tabular}
+\\
+\textit{Can these results be modelled by a Poisson distribution? Test at the 5\% significance level}\\
+\\
+\textcolor{red}{Calculate $\lambda$ (the mean)}
+$$\lambda=\overline{x}=\frac{0\times8+1\times19+2\times26+3\times13+4\times7+5\times5+6\times1+7\times1+9\times0}{8+19+26+13+7+5+1+1+0}=2.2$$
+\textcolor{red}{Use this value of $\lambda$ to find $P(r)$ and $E(r)$ by multiplying by 80}\\
+\begin{tabularx}{\textwidth}{|X|X|X|}
+\hline
+r&$P(r)$&Expected freq of r\\
+\hline
+0&0.1108&8.864\\
+\hline
+1&0.2438&19.504\\
+\hline
+2&0.2681&21.448\\
+\hline
+3&0.1966&15.728\\
+\hline
+4&0.1082&8.656\\
+\hline
+5&0.0476&3.808\\
+\hline
+6&0.0174&1.392\\
+\hline
+$\geqslant7$&0.0075&0.6\\
+\hline
+\end{tabularx}
+\\
+\textcolor{red}{Use the two above tables to calculate $O_i$, $E_i$ and $X^2$, combining classes where needed}\\
+\begin{tabularx}{\textwidth}{|X|X|X|X|}
+\hline
+r&$O_i$&$E_i$&$\frac{(O_i-E_i)^2}{E_i}$\\
+\hline
+0&8&8.864&0.0842\\
+\hline
+1&19&19.504&0.0130\\
+\hline
+2&26&21.448&0.9661\\
+\hline
+3&13&15.728&0.4732\\
+\hline
+4&7&8.656&0.3168\\
+\hline
+$\geqslant5$&7&5.8&0.2483\\
+\hline
+\end{tabularx}\\
+\textcolor{red}{Find the value of $X^2$ by finding the sum of $\frac{(O_i-E_i)^2}{E_i}$}
+$$X^2=0.0842+0.0130+0.9661+0.4732+0.3168+0.2483$$
+\textcolor{red}{Calculate the degrees of freedom, subtracting for constant probability and estimated $\lambda$}
+$$\nu=6-1-1=4$$
+\textcolor{red}{Use the value for the degrees of freedom and significance level to find $\chi^2$}
+$$\chi^2_4=9.488$$
+\textcolor{red}{Compare the value of $\chi_4^2$ to the value of $X^2$ to determine the correct hypothesis}
+$$2.1016<9.488$$
+\begin{center}
+Value not in critical region, non significant, accept $H_0$ insufficient evidence to reject $H_0$
+\end{center}
 \end{document}

### 2018-03-13 Maths Notes/Further Pure/FP2/Polar Coordinates/Polar-Coordinates.tex
FP2 Notes Update - Includes saving tikz images

--- 2018-03-07 Maths Notes/Further Pure/FP2/Polar Coordinates/Polar Coordinates.tex
@@
-\documentclass{article}[18pt]
+\documentclass{article}
+% main document, called main.tex
+\usepackage{pgfplots}
+\usepackage{tikz}
+\usetikzlibrary{external}
+\tikzexternalize[prefix=tikz/] % activate!
+
 \usepackage[utf8]{inputenc}
 \usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
 \usepackage{amsmath}
@@
 \usepackage{titlesec}
-\usepackage{pgfplots}
-\usepgfplotslibrary{fillbetween}
+
 \usepackage{graphicx}
@@
 \renewcommand{\indent}{\hspace*{\tindent}}
-
 \pagestyle{fancy}
@@
      ]
-    \addplot[data cs=polar,red,domain=0:360,samples=10000] (x,{sqrt(cos(2*x))});
+    \addplot[data cs=polar,red,domain=0:360,samples=8000] (x,{sqrt(cos(2*x))});
 \end{axis}
@@
 The 4 asymptotes are half lines at $\theta=\frac{\pi}{4},\frac{3\pi}{4},\frac{5\pi}{4},\frac{7\pi}{4}$
+\subsection{$r^2=a^2\sin2\theta$}
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[
+    axis lines=center,
+    axis equal image,
+    enlargelimits=true,
+     ]
+    \addplot[data cs=polar,red,domain=0:360,samples=8000] (x,{sqrt(sin(2*x))});
+\end{axis}
+\end{tikzpicture}
+\\
+This is an anticlockwise rotation of $r^2=a^2\cos2\theta$ by $\frac{\pi}{4}$, it is this not $\frac{\pi}{2}$ as the phase difference between $\cos2\theta$ and $\sin2\theta$ is $\frac{\pi}{4}$ compared to $\frac{\pi}{2}$ with one $\theta$.
+\subsubsection{$r=a(p+q\sin\theta)$}
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[
+    axis lines=center,
+    axis equal image,
+    enlargelimits=true,
+    ticks=none
+     ]
+    \addplot[data cs=polar,red,domain=0:360,samples=360,smooth] (x,{6*(1+sin(x))});
+\end{axis}
+\end{tikzpicture}
+\\
+This is a rotation of $r=a(p+q\cos\theta)$ anticlockwise by $\frac{\pi}{2}$
+\subsection{Other types}
+\subsubsection{$r=a\sin3\theta$}
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[
+    axis lines=center,
+    axis equal image,
+    enlargelimits=true,
+     ]
+    \addplot[data cs=polar,red,domain=0:360,samples=360,smooth] (x,{sin(3*x)});
+\end{axis}
+\end{tikzpicture}
+\\
+Asymptotes occur when $r=0$
+\subsubsection{$r=2\sec(\theta-\frac{\pi}{3})$}
+\begin{tikzpicture}[scale=0.8]
+\begin{axis}[
+    axis lines=center,
+     ]
+    \addplot[data cs=polar,red,domain=-10:100,samples=360,smooth] (x,{2/(cos(x-60))});
+\end{axis}
+\end{tikzpicture}
+
 \end{document}

### 2018-03-14 Maths Notes/Statistics/S3/Goodness of fit and contingency tables/Goodness of fit and contingency tables.tex
S3 notes update

@@
 \end{center}
+\newpage
+\subsection{Testing a uniform distribution as a model}
+\textit{In a study of the habits of a flock of starlings, the direction in which they headed when they left their roost in the mornings was recorded over 240 days.
+The direction was sound by recording if they headed between certain features of the landscape.
+The compass bearings of these features were then measured.
+The results are given below.\\
+Suggest a suitable distribution, and test to see if the data supports this model}\\
+\\
+\textcolor{red}{State hypotheses}
+$$H_0:\textrm{The binomial distribution is a suitable model}$$
+$$H_1:\textrm{The binomial distribution is a suitable model}$$
+\\
+\textcolor{red}{Fill in the table below, calculating the expected value using $\frac{b-a}{\beta-\alpha}\times n$ where a and b are the start and end of the range, and $\alpha$ and $\beta$ are the start and end of the full range}\\
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|}
+\hline
+Direction (degrees)&$0\leqslant d<58$&$58\leqslant d<100$&$100\leqslant d<127$&$127\leqslant d<190$&$190\leqslant d<256$&$256\leqslant d<296$&$296\leqslant d<360$\\
+\hline
+Frequency(O)&31&40&47&40&32&30&20\\
+\hline
+E&38.67&28&18&42&44&26.67&42.67\\
+\hline
+$\frac{(O-E)^2}{E}$&1.52&5.14&46.72&0.095&3.27&0.42&12.04\\
+\hline
+\end{tabularx}\\
+\textcolor{red}{Calculate $X^2$}
+$$X^2=1.52+5.14+46.72+0.095+3.27+0.42+12.04=69.21$$
+\textcolor{red}{Calculate the degrees of freedom, only one restriction for constant frequency}
+$$\nu=7-1=6$$
+\textcolor{red}{Find the value of $\chi^2_6$ at 5\%}
+$$\chi^2_6=12.592$$
+\textcolor{red}{Compare the value of $\chi^2_6$ to the value of $X^2$ to determine the correct hypothesis}
+$$12.592<69.29$$
+\begin{center}
+In critical region, reject $H_0$, accept $H_1$, the uniform distribution is not a suitable model.
+\end{center}
 \end{document}

### 2018-03-14 Physics Notes/Nuclear Physics/Nuclear Energy/Nuclear Energy.tex
Notes update

@@
 \end{itemize}
+\subsubsection{Example}
+\textit{How much energy would be produced by the fission of 10kg of $^{235}_{92}U$}
+$$^{235}_{92}U+^1_0n\rightarrow ^{141}_{56}Br+^{92}_{36}Kr+3 \ ^1_0n$$
+$$235.04393u+1.00867u\rightarrow140.9408u+91.9298u+\times1.00867u$$
+$$\textrm{Difference}=0.15599u=145.3MeV$$
+Find the total number of atoms
+$$\textrm{Number of atoms}=\frac{\textrm{Mass}}{\textrm{Nucleon Number}}\times \textrm{Avagadro's constant}$$
+$$\textrm{Number of atoms}=\frac{10}{235.04393\times10^{-3}}\times6.02\times10^{23}=2.56\times10^{25}$$
+Multiply the energy released per atom by the number of atoms to find the total energy released
+$$\textrm{Total energy}=2.56\times10^{25}\times145.3=3.72\times10^{27}MeV$$
 \subsection{Nuclear fusion}

### 2018-03-20 Maths Notes/Further Pure/FP2/Maclaurin and Taylor Series/Maclaurin and Taylor Series.tex
Notes up to date

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - FP2}
\rfoot{Page \thepage}

\usepackage{cancel}

\begin{document}
\begin{center}
\underline{\huge Maclaurin and Taylor Series}
\end{center}
\section{Maclaurin's expansion}
$$f(x)=f(0)+f'(0)x+f''(0)\frac{x^2}{2!}+f'''(0)\frac{x^3}{3!}+...+f^r(0)\frac{x^r}{r!}...$$
\\
For the continuous function, f, given by $f:x\Rightarrow f(x)$(where $x$ is real), then providing $f(0),f'(0),f''(0)$ etc all have finite values. This is an infinite series.
\subsection{Example}
\textit{Given that $f(x)=e^x$ can be written as an infinite series in the form:}
$$f(x)=e^x=a_0+a_1x+a_2x^2+a_3x^3+...+a_rx^4+...$$
\textit{And that it is valid to differentiate an infinite series term by term, show that:}
$$e^2=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}+...+\frac{x^r}{r!}+...$$
\\
\\
\textcolor{red}{Find up to the third differential of $f(x)$ and the value of zero for each}\\
\begin{tabular}{l l}
$f(x)=e^x$&$f(0)=1$\\
$f'(x)=e^x$&$f''(0)=1$\\
$f''(x)=e^x$&$f''(0)=1$\\
$f'''(x)=e^x$&$f'''(0)=1$
\end{tabular}
\\
\\
$$f(x)=1+1\times x+1\times\frac{x^2}{2!}+1\times\frac{x^3}{3!}$$
$$f(x)=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}+...+\frac{x^r}{r!}+...$$
\subsection{Standard results}
Standard results are given on the data sheet, these can then be used for adapted forms of the results also. Remember to consider the limits where appropriate.

\end{document}

### 2018-03-20 Maths Notes/Further Pure/FP2/Polar Coordinates/Polar-Coordinates.tex
FP2 Notes Update
Notes up to date

@@
 \documentclass{article}
-% main document, called main.tex
 \usepackage{pgfplots}
@@
 \usetikzlibrary{external}
-\tikzexternalize[prefix=tikz/] % activate!
-
+\tikzexternalize[prefix=tikz/]
 \usepackage[utf8]{inputenc}
@@
 \end{tikzpicture}
+\newpage
+\section{Integration}
+$$\textrm{Area}=\frac{1}{2}\int^\beta_\alpha r^2 \ d\theta$$
+Where the area of the sector is bounded by the half lines $\theta=\alpha$ and $\theta=\beta$, the value of $\theta$ must always be in radians.\\
+\\
+The the radius in this sector must not drop to zero, choose angles so this doesn't happen. Or choose multiple sections and add together, or use symmetry. 
+\section{Differentiating Polar Equations to find tangents}
+We only find tangents parallel and perpendicular to the initial line.\\
+\\
+$x=r\cos\theta$\\
+$y=r\sin\theta$\\
+\\
+Using the chain rule:
+$$\frac{dy}{dx}=\frac{dy}{d\theta}\times\frac{d\theta}{dx}$$
+\\
+Parallel: $\frac{dy}{d\theta}=0$\\
+Perpendicular: $\frac{dx}{d\theta}=0$
+\subsection{Example}
+$r=a(1+\cos\theta)$\\
+\\
+Find the coordinates where the tangents are parallel to the initial line with $\theta=0$\\
+\\
+$$y=r\sin\theta$$
+\textcolor{red}{Replace r with $a(1+\cos\theta)$}
+$$y=a(\sin\theta+\sin\theta\cos\theta)$$
+\textcolor{red}{Now we can find $\frac{dy}{d\theta}$}
+$$\frac{dy}{d\theta}=a(\cos\theta+\cos^2\theta-\sin^2\theta)$$
+\textcolor{red}{Simplify and set equal to zero}
+$$2\cos^2\theta+\cos\theta-1$$
+$$0=(2\cos\theta-1)(\cos\theta+1)$$
+\textcolor{red}{Find $\cos\theta$, $\theta$ and $r$}
+$$\cos\theta \quad \cos\theta=-1$$
+$$\theta=\pm\frac{\pi}{3} \quad \theta=\pi$$
+$$r=\frac{3a}{2} \quad r=0$$
+\subsubsection{Finding the equations of tangents}
+$$\textrm{Cartesian equation:} \ y=r\sin\theta$$
+$$\textrm{Polar equation:} \ r=y\csc\theta=r\sin\theta\csc\theta$$
 

### 2018-03-20 Maths Notes/Statistics/S3/Goodness of fit and contingency tables/Goodness of fit and contingency tables.tex
Notes up to date

@@
 \end{center}
+\newpage
+\subsection{Testing the normal distribution as a model}
+We would fit data to a normal if:
+\begin{itemize}
+\item Data is continuous
+\item Symmetrical about the mean
+\item 68\% of the data falls within 1 standard deviation of the mean
+\end{itemize}
+\textit{During observations on the height of 200 male students the following data was observed:}\\
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|X|X|X|}
+\hline
+Height (cm)&150-154&155-159&160-164&165-169&170-174&175-179&180-184&185-189&190-194\\
+\hline
+Freq&4&6&12&30&64&52&18&10&4\\
+\hline
+\end{tabularx}
+\\
+\textit{Test at the 0.05 level of see if the height of the male students could be modelled by a normal distribution with mean 172 and standard deviation 6}\\
+\\
+\textcolor{red}{State the hypotheses}
+\begin{center}
+$H_0:$ Data can be modelled by a normal distribution $N(172,6^2)$\\
+$H_1:$ Data cannot be modelled by this normal distribution
+\end{center}
+\textcolor{red}{Fill in the below table, calculating the probabilities by finding the z values and converting to probabilities.
+Find E by multiplying the probability by 200.
+For the first and last values, find all values past this value}\\
+\begin{tabularx}{\textwidth}{|X|X|X|X|}
+\hline
+Class&Z upper limit&$P(a<x<b)$&E\\
+\hline
+$<154.5$&-2.92&0.0019&0.38\\
+\hline
+154.5-159.5&-2.08&0.0169&3.38\\
+\hline
+159.5-164.5&-1.25&0.0868&17.36\\
+\hline
+164.5-169.5&-0.42&0.2316&46.32\\
+\hline
+169.5-174.5&0.42&0.3256&65.12\\
+\hline
+174.5-179.5&1.25&0.2316&46.32\\
+\hline
+184.5-189.5&2.92&0.0169&3.38\\
+\hline
+$>189.5$&&0.0019&0.38\\
+\hline
+\end{tabularx}
+\\
+\textcolor{red}{Remember to combine rows so that all are greater than 5, find $X^2$}
+$$X^2=12.1$$
+\textcolor{red}{Find the degrees of freedom, subtracting one from the number of combined classes}
+$$\nu=5-1=4$$
+\textcolor{red}{Find the value of $\chi^2_4$ at 5\%}
+$$\chi^2_4 \ \textrm{At 5\%}=9.488$$
+\textcolor{red}{Compare the value of $\chi^2_4$ with the value of $X^2$ and state conclusions}
+$$X^2>\chi^2$$
+\begin{center}
+Significant result, reject $H_0$, does not follow a normal distribution
+\end{center}
 \end{document}

### 2018-03-20 Physics Notes/Nuclear Physics/Nuclear Energy/Nuclear Energy.tex
Notes up to date

@@
 Lower level radioactive waste is stored in drums filled with concrete.
+\begin{itemize}
+\item Radioactive waste from fuel rods
+\item Waste initially highly radioactive and needs to be remotely handled
+\item Waste initially placed in cooling ponds - remove heat and absorb radiation
+\item Plutonium/uranium separated to be recycled
+\item High level waste is vitrified - In liquid form radiation may leak, stable storage
+\item Transported in crash resistant containers for safety
+\item Placed in steel containers
+\item Stored deep underground
+\end{itemize}
 \end{document}

### 2018-03-23 Maths Notes/Further Pure/FP2/Maclaurin and Taylor Series/Maclaurin and Taylor Series.tex
Notes up to date

@@
 Standard results are given on the data sheet, these can then be used for adapted forms of the results also. Remember to consider the limits where appropriate.
-
+\newpage
+\section{Taylor expansion}
+The conditions of the Maclaurin expansion mean that some functions, such as $\ln x$ cannot be expanded as a series in ascending powers of x.\\
+\\
+The construction of the Maclaurin expansion focuses on $x=0$ and values of x very close to zero. The Taylor expansion focuses on $x=a$.\\
+\\
+Considering the functions f and g, where $f(x+a)\equiv g(x)$ then:\\
+$f^r(a)=g^r(0)$\\
+\\
+Turning the Maclaurin expansion for g from:
+$$g(x)=g(0)+g'(0)x+\frac{g''(0)}{2!}x^2...$$
+Into
+$$f(x+a)=f(a)+f'(a)x+\frac{f''(a)}{2!}x^2+...+\frac{f^r(a)}{r!}x^r$$
+Replacing x by x-a gives
+$$f(x)=f(a)+f'(a)(x-a)+\frac{f''(a)}{2!}(x-a)^2+...+\frac{f^r(a)}{r!}(x-a)^r$$
+These are the two forms of the Taylor expansion, when a=0, they both become the Maclaurin expansion.
 \end{document}

### 2018-03-23 Maths Notes/Statistics/S3/Goodness of fit and contingency tables/Goodness of fit and contingency tables.tex
Notes up to date

@@
 \usepackage{tabularx}
+\usepackage{multirow}
 \usepackage[english]{babel}
@@
 \end{center}
+\section{Goodness of fit}
 Method for testing goodness of fit:
@@
 \end{center}
+\newpage
+\section{Contingency tables}
+\begin{itemize}
+\item We use this test to see if two factors are independent of each other
+\item We describe them by: Number of rows $\times$ Number of columns
+\item $H_0$ is that they are independent
+\item $H_1$ is that they are independent
+\item $$\textrm{Expected values}=\frac{\textrm{Row total}\times\textrm{Column total}}{\textrm{Grand total}}$$
+\item $$\nu=(\textrm{Number of rows-1})(\textrm{Number of columns-1})$$
+\end{itemize}
+\subsection{Contingency tables}
+\textit{Determine to the 5\% significance level whether school and grade are dependent}\\
+
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
+\hline
+&&\multicolumn{3}{|X|}{Grade}&\multirow{2}{4em}{Totals}\\
+\cline{3-5}
+&&A&B&C&\\
+\hline
+\multirow{2}{4em}{School}&X&18&12&20&50\\
+\cline{2-6}
+&Y&26&12&32&70\\
+\hline
+Totals&&44&24&52&120\\
+\hline
+\end{tabularx}
+\\
+\\
+\textcolor{red}{Write the hypotheses}
+\begin{center}
+$H_0:$ School and grade are independent\\
+$H_1:$ School and grade are not independent\\
+\end{center}
+\textcolor{red}{Calculate the expected frequencies, using the formula to find expected values}\\
+
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
+\hline
+&&\multicolumn{3}{|X|}{Grade}\\
+\hline
+&&A&B&C\\
+\hline
+\multirow{2}{4em}{School}&X&$$\frac{55}{3}$$&$$10$$&$$\frac{65}{3}$$\\
+\cline{2-5}
+&Y&$$\frac{77}{3}$$&$$14$$&$$\frac{91}{3}$$\\
+\hline
+\end{tabularx}
+\textcolor{red}{Calculate the degrees of freedom}
+$$\nu=(2-1)(3-1)=2$$
+\textcolor{red}{Calculate $X^2$}
+$$X^2=0.916$$
+\textcolor{red}{Find the value of $\chi^2_2$ at 5\%}
+$$\chi^2_2=5.991$$
+\textcolor{red}{Compare values and write conclusion}
+\begin{center}
+$0.916<5.991$ don't reject $H_0$, insufficient evidence to suggest an association, independent
+\end{center}
 \end{document}

### 2018-03-23 Physics Notes/Turning Points/Special relativity/Special Relativity.tex
Notes up to date

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage{pgfplots}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Turning Points}

\usepackage{tikz}
\usetikzlibrary{scopes}

\usepackage{mathtools}

\newtagform{brackets}{[}{]}
\usetagform{brackets}

\begin{document}
\begin{center}
\underline{\huge Special Relativity}
\end{center}
\section{Frames of reference}
Einstein's theory of special relativity is the result of analysing the consequences of the absence of any universal frame of reference. Special relativity concentrates on frames of reference which are moving at a constant velocity relative to each other. These frames are known as \textbf{inertial frames of reference}.\\
\\
Special relativity is based on two postulates:
\begin{itemize}
\item The laws of physics, expressed in equations, have the same form in all inertial frames
\item The speed of light in free space is invariant (ie the same for all observers regardless of their state of motion and the speed of the light source)
\end{itemize}
\section{The Michelson-Morley experiment}
The experiment was carried out to find out if the direction of the Earth's motion through space differs from the speed of light in a perpendicular direction. This was investigated using the Michelson interferometer, shown below:\\
\includegraphics[width=10cm]{michelson.png}\\
The semi-silvered glass block splits the beam of monochromatic light into two beams at A which is on the silvered side of the block. The block, $P_2$, is necessary to ensure that both beams pass through the same thickness of glass and air. If the speed of light depended on the angle compared to the earth's rotation there would be interference at O due to the waves no longer being in phase. However this was not detected, meaning there is no difference in speed.
\section{Time dilation and proper time}
A consequence of the invariance of the speed of light in free space is that time runs slower when in motion. \\
\includegraphics[width=8cm]{time_dilation.png}\\
This shows that to an observer time is slower to an observer.\\
\\
$$t=\frac{t_0}{\sqrt{1-(\frac{v}{c})^2}}$$
t- Time measured by external observer\\
$t_0$ - Time measured in the moving frame (called the proper time)\\
v - Relative velocity of moving frame\\
c- Speed of light in a vacuum
\subsection{Example experiment}
When cosmic rays reach the ionosphere above the Earth's surface, unstable sub-atomic particles called muons are created, travelling at 0.966c. These particles have a half life of $1.5\mu s$.\\
\\
Measurements by Bruno Rossi showed that about 80\% of the muons created by cosmic radiation on a mountain top reached an observatory 2km below. In one half-life of $1.5\mu s$, muons moving at 0.996c would decay, resulting in fewer detected at the bottom than the top.
\section{Length contraction}
A moving observer sees an object to appear smaller than it is (as measured in the stationary frame).\\
\\
Time contraction is \textbf{only} along the direction of travel.\\
It s easier to think that a moving observer measures the distance they cover to be less than a stationary observer.
$$L=L_0\sqrt{1-(\frac{v}{c})^2}$$
L - Length measured by the moving observer\\
$L_0$ - Length measured by the stationary observer (called the proper length)\\
v- Relative velocity of the moving frame\\
c- Speed of light in a vacuum
\end{document}

### 2018-03-26 Maths Notes/Further Pure/FP2/Maclaurin and Taylor Series/Maclaurin and Taylor Series.tex
Notes up to date

@@
 These are the two forms of the Taylor expansion, when a=0, they both become the Maclaurin expansion.
+\subsection{Example}
+\textit{Find the Taylor expansion of $\cos2x$, in ascending powers of $(x-\frac{\pi}{4})$ up to $(x-\frac{\pi}{4})^5$}
+\textcolor{red}{Find the differentials of $f(x)$ up to the fifth derivative, and the associated values when $x=\frac{\pi}{4}$}\\
+\begin{tabular}{l l}
+$f(x)=\cos2x$&$f(\frac{\pi}{4})=0$\\
+$f'(x)=-2\sin2x$&$f(\frac{\pi}{4})=-2$\\
+$f''(x)=-4\cos2x$&$f(\frac{\pi}{4})=0$\\
+$f'''(x)=8\sin2x$&$f(\frac{\pi}{4})=8$\\
+$f''''(x)=16\cos2x$&$f(\frac{\pi}{4})=0$\\
+$f'''''(x)=-32\sin2x$&$f(\frac{\pi}{4})=-32$
+\end{tabular}\\
+\textcolor{red}{Substitute in the associated values into the formula}
+$$\cos2x=0-2\Big(x-\frac{\pi}{4}\Big)+0+\frac{8}{3!}\Big(x-\frac{\pi}{4}\Big)^3+0-\frac{32}{5!}\Big(x-\frac{\pi}{4}\Big)^5$$
+$$\cos2x=-2\Big(x-\frac{\pi}{4}\Big)+\frac{4}{5}\Big(x-\frac{\pi}{4}\Big)^3-\frac{4}{15}\Big(x-\frac{\pi}{4}\Big)^5$$
+
+\newpage
+\section{Finding the solution, in the form of a series to a differential equation using the Taylor series method}
+Suppose you have a first order differential equation of the form $\frac{dy}{dx}=f(x,y)$ and you know the initial condition that at $x=x_0$,$y=y_0$, then you can calculate \Large{$(\frac{dy}{dx})_{x_0}$} \normalsize by substituting $x_0$ and $y_0$ into the original differential equation.\\
+\\
+By successive differentiation of the original differential equation, the values of {\Large $(\frac{d^2y}{dx^2})_{x_0}$} and {\Large $(\frac{d^3y}{dx^3})_{x_0}$} and so on can be found by substituting previous results into the derived equations.\\
+\\
+The series solution to the differential equation is found using the Taylor series in the form:
+$$y=y_0+(x-x_0)\bigg(\frac{dy}{dx}\bigg)_{x_0}+\frac{(x-x_0)^2}{2!}\Bigg(\frac{d^2y}{dx^2}\Bigg)_{x_0}+\frac{(x-x_0)^3}{3!}\Bigg(\frac{d^3y}{dx^3}\Bigg)_{x_0}+...$$
+In the common situation where $x_0=0$ then this reduces to the Maclaurin series
+$$y=y_0+x\bigg(\frac{dy}{dx}\bigg)_{x_0}+\frac{x^2}{2!}\Bigg(\frac{d^2y}{dx^2}\Bigg)_{x_0}+\frac{x^3}{3!}\Bigg(\frac{d^3y}{dx^3}\Bigg)_{x_0}+...$$
+\subsection{Example}
+\textit{Using the Taylor method to find a series solution, in ascending powers of x up to and including the term in $x^3$, of:}
+$$\frac{d^2y}{dx^2}=y-\sin x$$
+\textit{Given that when $x=0$,$y=1$ and $\frac{dy}{dx}=2$}
+\\
+\textcolor{red}{Use the formula to find $\frac{d^2y}{dx^2}$}
+$$\frac{d^2y}{dx^2}=1-\sin(0)=1$$
+$$\mathbf{\frac{d^2y}{dx^2}=1}$$
+\textcolor{red}{Differentiate the formula to obtain a formula for $\frac{d^3y}{dx^3}$}
+$$\frac{d^3y}{dx^3}=\frac{dy}{dx}-\cos x=2-\cos(0)=1$$
+$$\mathbf{\frac{d^3y}{dx^3}=1}$$
+\textcolor{red}{Substitute the known values into the Maclaurin formula}
+$$y=1+x\times2+\frac{x^2}{2!}\times1+\frac{x^3}{3!}\times1$$
+$$y=1+2x+\frac{x^2}{2}+\frac{x^3}{6}$$
 \end{document}

### 2018-03-26 Physics Notes/Turning Points/Special relativity/Special Relativity.tex
Notes up to date

@@
 c- Speed of light in a vacuum
+\section{Relativistic mass, momentum and energy}
+\subsection{Relativistic mass}
+Rest mass (proper mass,$m_0$):Mass as measured by an observer who is stationary relative to the mass\\
+Relative mass(m): The apparent mass of an object that is moving relative to the observer (speed v)\\
+$$m=\frac{m_0}{\sqrt{1-(\frac{v}{c})^2}}$$
+Relativistic mass increases with speed
+\newpage
+\subsection{Relativistic momentum}
+$$p=mv-\frac{m_0v}{\sqrt{1-(\frac{v}{c})^2}}$$
+\subsection{Relativistic energy}
+$$E=mc^2=\frac{m_0c^2}{\sqrt{1-(\frac{v}{c})^2}}$$
+\subsubsection{Kinetic energy}
+\begin{center}
+Total energy=Rest energy+Relativistic KE
+\end{center}
+$$E=E_0+E_K$$
+$$E_K=E-E_0$$
+$$E_K=\frac{m_0c^2}{\sqrt{1-(\frac{v}{c})^2}}-m_0c^2$$
+$$E_K=m_0c^2\Bigg(\bigg(1-\bigg(\frac{v}{c}\bigg)^2\bigg)^{-\frac{1}{2}}-1\Bigg)$$
+\textcolor{red}{Apply binomial expansion to the first term}
+$$E_K=m_0c^2\Bigg(1+\frac{1}{2}\Big(\frac{v}{c}\Big)^2+\frac{-\frac{1}{2}(-\frac{1}{2}-1)}{2}\times\Big(\frac{v}{c}\Big)^4-1\Bigg)$$
+\textcolor{red}{Approximate away all terms larger than $\Big(\frac{v}{c}\Big)^2$ and simplify}
+$$E_K\approx m_0c^2\times\frac{1}{2}\times\frac{v^2}{c^2}=\frac{1}{2}m_0v^2$$
+Together mass and energy are conserved, but not necessaries individually
+\section{Summary of equations}
+\begin{tabular}{l l}
+Gamma factor&$\gamma=\sqrt{1-(\frac{v}{c})^2}$\\
+Length contraction&$L_0\gamma$\\
+Time dilation&\Large{$\frac{t_0}{\gamma}$}\\
+Relativistic mass&\Large{$\frac{m_0}{\gamma}$}\\
+Relativistic momentum&\Large{$\frac{m_0v}{\gamma}$}\\
+Relativistic energy&\Large{$\frac{m_0c^2}{\gamma}$}
+\end{tabular}
 \end{document}

### 2018-04-04 Physics Notes/Practical Notes/Practical Notes.tex
Physics Notes Update

@@
 \usepackage{amsmath}
+\usepackage{gensymb}
 \usepackage{titlesec}
@@
 \usepackage{graphicx}
+\usepackage{tabularx}
 \usepackage[english]{babel}
@@
 \end{center}
-\section{\% error on gradient}
+\section{Tabulating data}
+\begin{itemize}
+\item Left column is the independent variable, the rest are the dependent variables
+\item No units in the body of the table, only in the header
+\end{itemize}
+\subsection{Tabulating logarithmic values}
+Logs have no units, however the thing the log is of does, so it should have units\\
+Example:\\
+Log(Time/s)
+\section{Significant figures}
+Data should be written in tables to the same number of significant figures, determined by resolution or uncertainty.\\
+\\
+When crossing a multiple of 10, keep the same number of decimal laces, accuracy is more important than number of significant figures.\\
+\\
+Give answers to calculations to the least number of significant figures used in the calculation.\\
+\\
+Uncertainty should be rounded to the same number of decimal places as the value.\\
+\\
+For example a thermometer measuring to the nearest 0.5$\degree$C would have an uncertainty of $\pm 0.25$, but would be quoted at $\pm 0.3$ as the values are to one decimal place
+\section{Uncertainty}
+Examples of issues to consider when assessing uncertainty
+\begin{itemize}
+\item The resolution of the instrument used
+\item The manufacturer's tolerance on instruments
+\item The judgements made by the experimenter
+\item The procedures adopted
+\item The size of the increments available
+\end{itemize}
+Resolution is the \textbf{minimum} possible uncertainty
+\subsection{Readings and measurements}
+It is useful when discussing uncertainties to separate measurements into two forms:
+\begin{itemize}
+\item Readings: Values found from a single judgement when using a piece of equipments
+\item Measurements: Values taken as the difference between the judgements of two values
+\end{itemize}
+\begin{tabular}{|c|c|}
+\hline
+Reading&Measurement\\
+\hline
+Thermometer&Ruler\\
+\hline
+Top pan balance&Vernier calliper\\
+\hline
+Measuring cylinder&Micrometer\\
+\hline
+Digital voltmeter&Protractor\\
+\hline
+Geiger counter&Stopwatch\\
+\hline
+Pressure gauge&Analogue meter\\
+\hline
+\end{tabular}
+\\
+The uncertainty in a reading when using a particular instrument is \textbf{no smaller} than plus or minus half of the smallest division or greater.\\
+\\
+However when using a ruler, the readings of the start and end are made, meaning that instead of having $\pm 0.5$cm, it would instead have uncertainty of $\pm 1$cm.
+\subsection{Other factors}
+When using a stopwatch, the main uncertainty does not come from the resolution, but the person using the stopwatch.
+To show this, the number of significant figures should be reduced in the \textbf{final result only}.
+\subsection{Uncertainties in given values}
+In a given value, the uncertainty is assumed to be $\pm 1$ of the last significant digit.
+\subsection{Multiple instances of measurements}
+For example, when measuring the time for 10 pendulum swings to $\pm 0.1$s, the time for 1 pendulum swing is accurate to $\pm 0.01s$
+\subsection{Repeated measurements}
+With repeated measurements, the uncertainty is half the range of measured values.
+\subsection{Percentage uncertainties}
+$$\textrm{Percentage uncertainty}=\frac{\textrm{Uncertainty}}{\textrm{Value}}\times 100\%$$ 
+\subsubsection{Error bars}
+\begin{itemize}
+\item Plot the data point at the mean value
+\item Calculate the range of data, ignoring any anomalies
+\item Add error bars with the lengths equal to half the range on either side of the data point
+\end{itemize}
+\subsubsection{Uncertainties from gradients}
+To find the uncertainty in a gradient, two lines should be drawn on the graph.
+\begin{itemize}
+\item The "best" line of best fit
+\item The steepest or shallowest possible line of best fit
+\end{itemize}
+Uncertainty in gradient is calculated by:
+$$\textrm{Percentage uncertainty}=\frac{|\textrm{Best Gradient-Worst Gradient}|}{\textrm{Best Gradient}}\times 100\%$$
+In the same way, the percentage uncertainty in the y intercept can be found by:
+$$\textrm{Percentage uncertainty}=\frac{|\textrm{Best y intercept-Worst y intercept}|}{\textrm{Best y intercept}}\times 100\%$$
+
+\subsubsection{\% error on gradient}
 Total \% error = \% error on X + \% error on Y\\
@@
 \% error on Y = 1 Small Square/Number of squares on triangle\\
+\newpage
+\subsection{Combing uncertainties}
+\large
+{\renewcommand{\arraystretch}{2}
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+Combination&Operation\\
+\hline
+Adding or subtracting\newline $a=b+c$&Add the absolute uncertainties\newline $\Delta a=\Delta b+\Delta c$\\
+\hline
+Multiplying values\newline $a=b\times c$&Add the percentage uncertainties\newline $\epsilon a=\epsilon b+\epsilon c$\\
+\hline
+Dividing values\newline $a=\dfrac{b}{c}$&Add the percentage uncertainties\newline $\epsilon a=\epsilon b+\epsilon c$\\
+\hline
+Power rules\newline $a=b^c$&Multiply the percentage uncertainty by the power\newline $\epsilon a=c\times\epsilon b$\\
+\hline
+\end{tabularx}}
+Absolute uncertainty($\Delta$) - Same units as quantity\\
+Percentage uncertainty($\epsilon$) - No units
+\section{Graphing}
+Axis labels should have units, no units on the intervals.
+\\
+Data points should be marked with a cross
+\subsection{Scales and origins}
+Data should take up as much of the graph as possible
+Need to consider:
+\begin{itemize}
+\item The maximum and minimum values of each variable
+\item The size of the graph paper
+\item Whether the origin should be included as a data point
+\item If you need to calculate the equation of a line, needing the y intercept
+\item How to draw the axes without using difficult scale markings
+\item Plots should cover \textbf{at least half} the grid supplied with the graph
+\end{itemize}
+\subsection{Lines of best fit}
+Things to consider when drawing a line of best fit
+\begin{itemize}
+\item Is the data supposed to be following an equation - helps to decide if the line should be straight or curved
+\item Are there any anomalous results
+\item Are there uncertainties in the measurements - line of best fit should lie within the error bars
+\end{itemize}
+A non zero intercept may imply a systematic error
+\subsection{Dealing with anomalous results}
+Anomalous results can be ignored if you know the reason for it being there, or if the results are expected to be the same (when calculating a mean etc).\\
+\\
+Otherwise, it should be included to reduce the probability that a key point is being ignored.\\
+Anomalous results should be recorded, and only removed at the data analysis stage.\\
+It is good practice to repeat measurements where an anomalous result is found.
+\subsection{Measuring gradients}
+When finding the gradient of a line of best fit, a triangle should be drawn with the hypotenuse at least half as big as the line of best fit.
+It is best for the points on the triangle to lie on gridlines for more accurate measurements,\\
+\\
+When finding the gradient of a curve, draw a tangent at the relevant value of the independent variable.
+\subsection{Testing relationships}
+If plotting a graph results in a straight line, there is a relationship.\\
+\\
+One of the values may be raised to a power in order to get a straight line, this still shows a relationship.
+\subsubsection{More complex relationships}
+For more complex relationships given by a formula, they should be rearranged to give it in $y=mx+c$ form, c may be zero.
+\newpage
+\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
+\titlespacing\subsection{0pt}{8pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
+\titlespacing\subsubsection{0pt}{8pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
+\section{Definitions}
+\setcounter{secnumdepth}{0}
+\subsection{Accuracy}
+A measurement is considered accurate if it is judged to be close to the true value
+\subsection{Calibration}
+Marking a scale on a measuring instrument\\
+This involves establishing the relationship between indications of a measuring instrument against standard or reference values.
+\subsection{Data}
+Information, either qualitative or quantitative, that has been collected
+\subsection{Errors}
+\subsubsection{Measurement error}
+The difference between a measured value and the true value
+\subsubsection{Anomalies}
+These are values in a set of results which are judged not to be part of the variation caused by random uncertainty
+\subsubsection{Random error}
+These cause readings to be spread about the true value, due to results varying in an unpredictable way from one measurement to the next
+\subsubsection{Systematic error}
+These cause readings to differ from the true value by a consistent amount each time a measurement is made
+\subsubsection{Zero error}
+Any indication that a measuring system gives a false reading when the true value of a measured quantity
+\subsection{Evidence}
+Data which has been shown to be valid
+\subsection{Fair test}
+A fair test is one in which only the independent variable has been allowed to affect the dependent variable
+\subsection{Hypothesis}
+A proposal intended to explain certain facts or observations
+\subsection{Interval}
+The quantity between readings
+\subsection{Precision}
+Measurements where there is very little spread about the mean value
+\subsection{Prediction}
+A statement suggesting what will happen in the future, based on observation, experience or a hypothesis
+\subsection{Range}
+The maximum and minimum values of the independent or dependent variables
+\subsection{Repeatable}
+If the original experimenter repeats the investigation using the same method and equipment and obtains the same results
+\subsection{Reproducible}
+If the investigation is repeated by another person, or by using different equipment or techniques, and the same results are obtained
+\subsection{Resolution}
+The smallest change in the quantity being measured of a measuring instrument that gives a perceptible change in the reading
+\subsection{Sketch graph}
+A line graph showing the general relationship between two variables
+\subsection{True value}
+The value that would be obtained in an ideal measurement
+\subsection{Uncertainty}
+The interval within which the true value can be expected to lie, with a given level of confidence or probability
+\subsection{Validity}
+The suitability of the investigative procedure to answer the question being asked
+\subsection{Valid conclusion}
+A conclusion supported by valid data, obtained from an appropriate experimental design and based on sound reasoning
+\subsection{Variables}
+Physical, chemical or biological quantities or characteristics 
+\subsubsection{Categoric variables}
+Values that have labels
+\subsubsection{Continuous variables}
+Variables that have values
+\subsubsection{Control variables}
+A variable that may, in addition to the independent variable, affect the outcome of the investigation and so must be kept the same
+\subsubsection{Dependent variables}
+The variable of which the value is measured to each and every change of the independent variable
+\subsubsection{Independent variable}
+The variable for which values are changed or selected by the investigator
+
 \end{document}

### 2018-04-04 Maths Notes/Statistics/S3/Estimation, confidence intervals and tests/Estimation.tex
S3 Notes Update

--- 2018-02-27 Maths Notes/Statistics/S3/Estimation/Estimation.tex
@@
 \end{center}
+\section{Statistics}
+A statistic is defined as follows:\\
+If $X_1,X_2,X_3,...,X_n$ is a random sample of size n from some population, then a statistic T is a random variable consisting of the $X_i$ than involves no other quantities.\\
+\\
+Since it is possible to repeat the process of taking a sample, if all samples are taken, they will form a probability distribution called the \textbf{sampling distribution of T}.
+This will usually depend on the distribution of the population X.\\
+\\
+A random sample is defined as follows:\\
+A random sample of size n consists of the observations $X_1,X_2,X_3,...,X_n$ from a population where the $X_i$
+\begin{itemize}
+\item Are independent random variables
+\item Have the same distribution as the population
+\end{itemize}
+
 \section{Estimators}
@@
 $$E(T)-\theta$$
-If $E(T)=\theta$ then the statistic is unbiased
+If $E(T)=\theta$ then the statistic is unbiased\\
+\\
+{\large $\mathlarger{\hat{\theta}}$} represents an estimator of $\theta$, this is true for all population parameters, such as $\hat{\mu}$
 \subsection{Proving $\mathbf{E(\overline{X})=\mu}$}
@@
 $$S^2=\frac{1}{n-1}\Big(\Sigma X^2-n\overline{X}^2\Big)$$
+\\
+In formula book
+$$S^2=\frac{\Sigma(X_i-\overline{X})^2}{n-1}$$
+Replace the top of the fraction with $S_{xx}=\Sigma x^2_i-\frac{(\Sigma x_i)^2}{n}$
+\begin{center}
+{\huge$S^2=\frac{\Sigma x_i^2-\frac{(\Sigma x_i)^2}{n}}{n-1}$}
+\end{center}
+\newpage
 \subsection{Uniform Distributions}

### 2018-04-04 Maths Notes/Statistics/S3/Exam Questions/Chi Squared Tests/Goodness of fit and contingency tables.tex
S3 Notes Update

--- 2018-03-23 Maths Notes/Statistics/S3/Goodness of fit and contingency tables/Goodness of fit and contingency tables.tex
@@
 \end{center}
-\section{Goodness of fit}
-Method for testing goodness of fit:
-\begin{enumerate}
-\item Determine which distribution would conceptually be most appropriate
-\item Set significance level
-\item Estimate parameters (if necessary) from observed data
-\item Form hypotheses $H_0$ and $H_1$
-\item Calculate expected frequencies
-\item Combine expected frequencies so that none are $<5$
-\item Find degrees of freedom
-\item Calculate critical value of $\chi^2$ from the table
-\item Calculate $\sum\frac{(O_i-E_i)^2}{E_i}$
-\item See if the value is significant and draw conclusion
-\end{enumerate}
-$X^2$ is distributed with a chi squared distribution $\chi^2_\nu$\\
-Where $\nu=$ degrees of freedom\\
-$$\textrm{The number of degrees of freedom}=\textrm{Number of classes (after combining)}-1$$
-\newpage
 \subsection{Testing a Binomial distribution as a model}

### 2018-04-04 Maths Notes/Statistics/S3/Exam Questions/Combinations of random variables/Combinations of random variables.tex
S3 Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{enumitem}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty=10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S3}
\rfoot{Page \thepage}

\begin{document}
\begin{center}
\underline{\huge Exam Questions - Combinations of random variables}
\end{center}
\section{Example 1}
\textit{Philip and James are racing car drivers. Philip’s lap times, in seconds, are normally distributed with mean 90 and variance 9. James’ lap times, in seconds, are normally distributed with mean 91 and variance 12. The lap times of Philip and James are independent. Before a race, they each take a qualifying lap.\\
\\
Find the probability that James’ time for the qualifying lap is less than Philip’s.}\\
\textcolor{red}{Write down the two distributions}
$$P\sim N(90,9) \qquad J\sim N(91,12)$$
\textcolor{red}{Write the probability wanted to be found, and rearrange so the distributions are on the same side}
$$P(J<P)$$
$$P(J-P<0)$$
\textcolor{red}{Combine the two distributions}
$$(J-P)\sim N(1,21)$$
\textcolor{red}{Find the z value given the new distribution}
$$P(Z<\frac{0-1}{\sqrt{21}}$$
$$P(Z<-0.2182)$$
\textcolor{red}{Convert into a probability using the tables}
$$1-\Phi(0.2182)$$
$$1-0.5871=0.4129$$
\newpage
\section{Example 2}
\textit{The random variable A is defined as}
$$A=4X-3Y$$
\textit{where $X\sim N(30,3^2)$, $Y\sim N(20,2^2)$ and X and Y are independent\\
The random variables $Y_1$, $Y_2$, $Y_3$ and $Y_4$ are independent and each has the same distribution as Y.\\
The random variable B is defined as}
$$B=\sum^4_{i=1}Y_i$$
\textit{Find $P(B>A)$}\\
\textcolor{red}{Find the distributions of A and B}
$$E(A)=E(4X-3Y)=4E(X)-3E(Y)=4\times30-3\times20=60$$
$$Var(A)=Var(4X-3Y)=16Var(X)+9Var(Y)=16\times9+9\times4=180$$
$$E(B)=4E(Y)=4\times20=80$$
$$Var(B)=4Var(Y)=4\times4=16$$
\textcolor{red}{Rewrite the probability to get both distributions on the same side}
$$P(B-A>0)$$
\textcolor{red}{Combine A and B to form the distribution B-A}
$$E(B-A)=80-60=20$$
$$Var(B-A)=180+16=196$$
\textcolor{red}{Find the z value given the new distribution}
$$P(Z>\frac{-20}{\sqrt{196}}$$
$$P(Z>-1.428)$$
$$\Phi(1.428)=0.9236$$

\end{document}

### 2018-04-04 Maths Notes/Statistics/S3/Exam Questions/Confidence Intervals/Confidence Intervals.tex
S3 Notes Update

--- 2018-04-04 Maths Notes/Statistics/S3/Exam Questions/Combinations of random variables/Combinations of random variables.tex
@@
 \begin{center}
-\underline{\huge Exam Questions - Combinations of random variables}
+\underline{\huge Exam Questions - Confidence Intervals}
 \end{center}
-\section{Example 1}
-\textit{Philip and James are racing car drivers.
-Philip’s lap times, in seconds, are normally distributed with mean 90 and variance 9.
-James’ lap times, in seconds, are normally distributed with mean 91 and variance 12.
-The lap times of Philip and James are independent.
-Before a race, they each take a qualifying lap.\\
-\\
-Find the probability that James’ time for the qualifying lap is less than Philip’s.}\\
-\textcolor{red}{Write down the two distributions}
-$$P\sim N(90,9) \qquad J\sim N(91,12)$$
-\textcolor{red}{Write the probability wanted to be found, and rearrange so the distributions are on the same side}
-$$P(J<P)$$
-$$P(J-P<0)$$
-\textcolor{red}{Combine the two distributions}
-$$(J-P)\sim N(1,21)$$
-\textcolor{red}{Find the z value given the new distribution}
-$$P(Z<\frac{0-1}{\sqrt{21}}$$
-$$P(Z<-0.2182)$$
-\textcolor{red}{Convert into a probability using the tables}
-$$1-\Phi(0.2182)$$
-$$1-0.5871=0.4129$$
-\newpage
-\section{Example 2}
-\textit{The random variable A is defined as}
-$$A=4X-3Y$$
-\textit{where $X\sim N(30,3^2)$, $Y\sim N(20,2^2)$ and X and Y are independent\\
-The random variables $Y_1$, $Y_2$, $Y_3$ and $Y_4$ are independent and each has the same distribution as Y.\\
-The random variable B is defined as}
-$$B=\sum^4_{i=1}Y_i$$
-\textit{Find $P(B>A)$}\\
-\textcolor{red}{Find the distributions of A and B}
-$$E(A)=E(4X-3Y)=4E(X)-3E(Y)=4\times30-3\times20=60$$
-$$Var(A)=Var(4X-3Y)=16Var(X)+9Var(Y)=16\times9+9\times4=180$$
-$$E(B)=4E(Y)=4\times20=80$$
-$$Var(B)=4Var(Y)=4\times4=16$$
-\textcolor{red}{Rewrite the probability to get both distributions on the same side}
-$$P(B-A>0)$$
-\textcolor{red}{Combine A and B to form the distribution B-A}
-$$E(B-A)=80-60=20$$
-$$Var(B-A)=180+16=196$$
-\textcolor{red}{Find the z value given the new distribution}
-$$P(Z>\frac{-20}{\sqrt{196}}$$
-$$P(Z>-1.428)$$
-$$\Phi(1.428)=0.9236$$
+\section{Normal mean}
+\textit{A woodwork teacher measures the width, w mm, of a board. The measured width, x mm, is
+normally distributed with mean w mm and standard deviation 0.5 mm.\\
+The same board is measured 16 times and the results are recorded.\\
+Given that the mean of these 16 measurements is 35.6 mm,\\
+find a 98\% confidence interval for w.}
+\textcolor{red}{Find the standard error}
+$$\textrm{Standard error}=\frac{\sigma}{\sqrt{n}}=\frac{0.5}{\sqrt{16}}=\frac{1}{8}$$
+\textcolor{red}{Find the z greater value for 1\%}
+$$P(Z>2.3263)=0.01$$
+\textcolor{red}{Substitute in the values}
+$$\overline{x}\pm z\times\textrm{Standard error}$$
+$$35.6\pm2.3263\times\frac{1}{8}$$
 

### 2018-04-06 Cyber Security/Cyber Security.tex
Update of all files to shorten preamble

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-\usepackage{amssymb}
+\usepackage{/home/sam/Documents/School_Notes/format}
+\lhead{GCHQ Cyberfirst}
 
-\pgfplotsset{width=10cm,compat=1.9}
-
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
-\lhead{GCHQ Cyberfirst}
-\rfoot{Page \thepage}
-
-\usepackage{titlesec}
-
+%File specific Preamble
+%Format Paragraphs correctly
 \setcounter{secnumdepth}{4}
-
 \titleformat{\paragraph}
@@
 \item Spyware - Malware that records the activity of the user
-\item Botnets - Malware that records the activities of the user
+\item Botnets - A network of computers under the control of an attacker
 \item Vulnerability - A point at which there is potential for a security breach
@@
 \\
-\textbf{Signed programs} - The sue of cryptography when companies issue copies of a program, so that the user can check it for authenticity.
+\textbf{Signed programs} - The use of cryptography when companies issue copies of a program, so that the user can check it for authenticity.
 \section{How the internet works}
@@
 TCP ensures that data can be sent reliably over the internet. This works through software ports to keep data separate on the same computer.\\
-The port decides how the data is handled when it reaches it's destination.\\
+The port decides how the data is handled when it reaches its destination.\\
 \\
@@
 \\
-When IP receives data from the internet, it removes the IO datagram and passes it to TCP.
+When IP receives data from the internet, it removes the IP datagram and passes it to TCP.
 \paragraph{IP addresses}

### 2018-04-06 Maths Notes/Core/C3/C3/C3.tex
Update of all files to shorten preamble

--- 2017-11-01 Maths Notes/C3/C3/C3.tex
@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{amssymb}
-\pgfplotsset{width=10cm,compat=1.9}
-\usepackage{mwe}
-\usepackage{float}
+\usepackage{/home/sam/Documents/School_Notes/format}
+\lhead{A Level Maths - C3}
 
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
-\lhead{A Level Maths - C3}
-\rfoot{Page \thepage}
-
-\newcommand{\R}{\mathbb{R}}
+%File specific preamble
 \pgfplotsset{ytick style={draw=none}}
@@
 $x=\sqrt{\dfrac{y+7}{2}}$\\
-$f^{-1}x=\sqrt{\dfrac{y+7}{2}}$\\
+$f^{-1}x=\sqrt{\dfrac{x+7}{2}}$\\
 
@@
 \\
-$f(x)=3x^4+x$
+$f(x)=(3x^4+x)^5$
 \\
@@
  \hline
- $y=\sin f(x)$&$\dfrac{dy}{dx}=f'(x)\cos f(x)$\\
+ $\sin f(x)$&$f'(x)\cos f(x)$\\
  \hline
- $y=\cos f(x)$&$\dfrac{dy}{dx}=-f'(x)\sin f(x)$\\
+ $\cos f(x)$&$-f'(x)\sin f(x)$\\
  \hline
- $y=\tan f(x)$&$\dfrac{dy}{dx}=f'(x)\sec^2f(x)$\\
+ $\tan f(x)$&$f'(x)\sec^2f(x)$\\
  \hline
- $y=\csc f(x)$&$\dfrac{dy}{dx}=-f'(x)\csc f(x)\cot f(x)$\\
+ $\csc f(x)$&$-f'(x)\csc f(x)\cot f(x)$\\
  \hline
- $y=\sec f(x)$&$\dfrac{dy}{dx}=f'(x)\sec f(x)\tan f(x)$\\
+ $\sec f(x)$&$f'(x)\sec f(x)\tan f(x)$\\
  \hline
- $y=\cot f(x)$&$\dfrac{dy}{dx}=-f'(x)\csc^2f(x)$\\
+ $\cot f(x)$&$-f'(x)\csc^2f(x)$\\
  \hline

### 2018-04-06 Maths Notes/Further Pure/FP2/Polar Coordinates/Polar-Coordinates.tex
Update of all files to shorten preamble

@@
 \documentclass{article}
-\usepackage{pgfplots}
-\usepackage{tikz}
+\usepackage{/home/sam/Documents/School_Notes/format}
+\lhead{A Level Maths - FP2}
+
+%File specific Preamble
+
+%Externalise to save computation time
 \usetikzlibrary{external}
 \tikzexternalize[prefix=tikz/]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{titlesec}
 
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-\usepackage{relsize}
-\pgfplotsset{width=10cm,compat=1.9}
-\usepackage[super]{nth}
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
-\lhead{A Level Maths - FP2}
-\rfoot{Page \thepage}
-
-\usepackage{cancel}
-
+%Give paragraphs the same format as sections
 \setcounter{secnumdepth}{4}
@@
 {0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
-\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
-\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
-\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
 

### 2018-04-06 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
Update of all files to shorten preamble

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-\usepackage{relsize}
-\pgfplotsset{width=10cm,compat=1.9}
-\usepackage[super]{nth}
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
+\usepackage{/home/sam/Documents/School_Notes/format}
+\lhead{A Level Maths - FP2}
 
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
-\lhead{A Level Maths - FP2}
-\rfoot{Page \thepage}
-
-\setcounter{secnumdepth}{4}
-\titleformat{\paragraph}
-{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
-\titlespacing*{\paragraph}
-{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
-\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
-\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
-\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
-
-\usepackage{mathtools}
-
-\newtagform{brackets}{[}{]}
-\usetagform{brackets}
+%File specific Preable
+\usepackage[super]{nth} %Provides 2nd etc
 

### 2018-04-06 Maths Notes/Statistics/S2/Exam Questions/CRVs/CRV Exam Questions.tex
S2 Notes Update
Update of all files to shorten preamble

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-\usepackage{amssymb}
-
-\pgfplotsset{width=10cm,compat=1.9}
-
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
+\usepackage{/home/sam/Documents/School_Notes/format}
 \lhead{A Level Maths - S2}
-\rfoot{Page \thepage}
 
@@
   \begin{array}{@{}ll@{}}
-  0 & x<1\\
-    \frac{4}{9}(x^2+2x-3), & \ 1\leqslant x\leqslant1.5\\
-    1 & x>1.5\\
+  0 & x<2\\
+    \frac{1}{20}(x^2-4), & \ 2\leqslant x\leqslant4\\
+    \frac{1}{5}(2x-5), & \ 4< x\leqslant5\\
+    1 & x>5\\
   \end{array}\right.
@@
 \\
-Differentiate $\frac{4}{9}(x^2+2x-3)$
-$$\frac{8}{9}(x+1)$$
+Differentiate $\frac{1}{20}(x^2-4)$
+$$\frac{1}{10}x$$
+Differentiate $\frac{1}{5}(2x-5)$
+$$\frac{2}{5}$$
 Write in function form\\
@@
   \begin{array}{@{}ll@{}}
-    \frac{8}{9}(x+1), & \ 1\leqslant x\leqslant1.5\\
+    \frac{1}{10}x, & \ 2\leqslant x\leqslant4\\
+    \frac{2}{5}, & \ 4< x\leqslant5\\
     0 & \textrm{Otherwise}\\

### 2018-04-06 Maths Notes/Statistics/S3/Definitions/Definitions.tex
Update of all files to shorten preamble

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Maths - S3}

\begin{document}
\begin{center}
\underline{\huge Definitions}
\end{center}
\large
Hypothesis - A statement concerning a population parameter\\
Critical Region - The range of values that would lead to the rejection of $H_0$, and so the acceptance of $H_1$\\
Statistic - A random variable, a function of known observations from a population, no unknown parameters\\
Sampling unit - An individual unit of the population\\
Sampling frame - A list of all sampling units\\
Sampling distribution - All possible samples are chosen from the population\\
Census - When every member of the population is investigated\\
Hypothesis test - A mathematical procedure to examine a value of
a population parameter proposed by the null hypothesis compared with an alternative hypothesis\\
Population - A collection of all items\\
Finite Population - One in which each individual member can be given a number\\
Infinite population - One where it is impossible to number each individual member\\
Significance level - The probability of incorrectly rejecting $H_0$\\
Sample - A selection of items from a population\\

\end{document}

### 2018-04-06 Maths Notes/Statistics/S3/Regression and Correlation/Regression and Correlation.tex
Update of all files to shorten preamble

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Maths - S3}

\begin{document}
\begin{center}
\underline{\huge Regression and Correlation}
\end{center}
\section{Spearman's rank}
Spearman's rank shows whether two sets of data agree or disagree.\\
\\
$r_s$ can take values from 1 to -1 (inclusive)
\subsection{$\mathbf{r_s=1}$}
The total sets of data are in perfect rank order.\\
The gradient between each successive point is positive\\
\\
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=0,ticks=none]
\addplot[color=black,domain=-2:2]{exp(x)};
\end{axis}
\end{tikzpicture}
\\
\subsection{$\mathbf{r_s=-1}$}
The gradient between each point is negative\\
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=0,ticks=none]
\addplot[color=black,domain=0.1:2]{1/x};
\end{axis}
\end{tikzpicture}
\subsection{Formula}
$$r_s=1-\dfrac{6\Sigma d^2}{n(n^2-1)}$$
\subsection{Example}
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
\hline
Height of a sunflower(cm)&Rank&Width of stem(mm)&Rank&d&$d^2$\\
\hline
183&\textbf{4}&21&\textbf{4}&\textbf{0}&\textbf{0}\\
\hline
134&\textbf{3}&14&\textbf{1}&\textbf{2}&\textbf{4}\\
\hline
234&\textbf{6}&24&\textbf{5}&\textbf{1}&\textbf{1}\\
\hline
256&\textbf{7}&32&\textbf{7}&\textbf{0}&\textbf{0}\\
\hline
190&\textbf{5}&29&\textbf{6}&\textbf{1}&\textbf{1}\\
\hline
89&\textbf{1}&18&\textbf{2}&\textbf{1}&\textbf{1}\\
\hline
112&\textbf{2}&20&\textbf{3}&\textbf{1}&\textbf{1}\\
\hline
\end{tabularx}
$\Sigma d^2=8$\\
\\
$1-\dfrac{6\times8}{7(7^2-1)}=\dfrac{6}{7}$
\section{Hypothesis Test For $\mathbf{r_s}$}
\underline{Step 1}\\
State $H_0$ and $H_1$\\
\\
$H_0: \rho_s=0$ (always)\\
\\
$H_1: \rho_s\neq0$ or\\
$H_1: \rho_s>0$ or\\
$H_1: \rho<0$\\
\\
\underline{Step 2}\\
State critical value from tables\\
\\
\underline{Step 3}\\
Calculate $r_s$\\
\\
\underline{Step 4}\\
Compare $r_s$ to the critical value. If in the critical region, testis significant, reject $H_0$ in favour of $H_1$\\
\\
\underline{Step 5}\\
Make conclusion in context of question
\section{Tied ranks}
If there are tied ranks and average of the positions they would take up

\end{document}

### 2018-04-06 Physics Notes/AS Level/Waves/Refraction, Diffraction and Interference/Refraction, Diffraction and Interference - AS.tex
Update of all files to shorten preamble

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{float}
-\usepackage{graphicx}
-\usepackage{tabularx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{circuitikz}
+\usepackage{/home/sam/Documents/School_Notes/format}
+\lhead{AS Level Physics - Waves}
+
+%File specific Preamble
+%Refraction settings
 \usetikzlibrary{decorations.pathmorphing,arrows,shapes,positioning,decorations.markings,angles,quotes}
-
-\pgfplotsset{width=10cm,compat=1.9}
-\usepackage{relsize}
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
-\lhead{AS Level Physics - Waves}
-\rfoot{Page \thepage}
-
-\pgfkeys{/pgfplots/Axis Style/.style={
-    width=13.5cm, height=10cm,
-    axis x line=center, 
-    axis y line=middle, 
-    samples=100,
-    ymin=-1.2, ymax=1.2,
-    xmin=0, xmax=13.0,
-    domain=-4*pi:4*pi
-}}
-\pgfkeys{/pgfplots/Stationary Wave/.style={
-    width=13.5cm, height=5cm,
-    axis x line=center, 
-    axis y line=middle, 
-    samples=100,
-    ymin=-1.2, ymax=1.2,
-    xmin=0, xmax=13.0,
-    domain=-4*pi:4*pi
-}}
-
 \tikzstyle arrowstyle=[scale=1]

### 2018-04-06 Physics Notes/Fields and their consequences/Electromagnetic Induction/Electromagnetic Induction.tex
Update of all files to shorten preamble

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing}
-\pgfplotsset{width=10cm,compat=1.9}
+\usepackage{/home/sam/Documents/School_Notes/format}
+\lhead{A Level Physics - Fields}
+
+%File specific Preamble
+\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing,calc,quotes,angles}
 \usepackage[super]{nth}
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-\hyphenpenalty =10000
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
-\lhead{A Level Physics - Fields}
-\rfoot{Page \thepage}
-\usepackage{mathtools}
-\usetikzlibrary{calc,quotes,angles}
-
 \tikzstyle{arrow} = [thick,->,>=stealth]
@@
 }}
+
 \begin{document}

### 2018-04-06 Physics Notes/Further Mechanics and Thermal Physics/Simple Harmonic Motion/Simple harmonic motion.tex
Update of all files to shorten preamble

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Physics - Further Mechanics and Thermal Physics}

%File specific Preamble
\usepackage{tabu} %Table

\pgfkeys{/pgfplots/Axis Style/.style={
    width=13.5cm, height=5cm,
    axis x line=center, 
    axis y line=middle, 
    samples=100,
    ymin=-1.5, ymax=1.5,
    xmin=0, xmax=14.0,
    domain=-4*pi:4*pi
}}

%Diagram
\pgfdeclarelayer{background layer}
\pgfdeclarelayer{foreground layer}
\pgfsetlayers{background layer,main,foreground layer}

\begin{document}
\begin{center}
\underline{\huge Simple Harmonic Motion}
\end{center}

\section{Introduction}
An object is undergoing Simple harmonic motion if:
\begin{itemize}
\item Its acceleration is proportional to its displacement.
\item Acceleration is directed to the equilibrium point (in the opposite direction to the displacement.
\end{itemize}

Rules of simple harmonic motion:
\begin{itemize}
\item The object can't have frictional forces (no damping)
\item The oscillations must be small displacements
\end{itemize}

\begin{tikzpicture}
\begin{axis}[
    Axis Style,
    xtick={
        3.14159,6.28319,9.42478,12.56637
    },
    xticklabels={
        $\dfrac{T}{2}$,T,$\dfrac{3T}{2}$,2T
    },
    ytick={-1,1},
    yticklabels={-A,A},
    y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
    ylabel = {Displacement, x},
    xlabel= {Time, t}
]
\addplot [mark=none, ultra thick, black] {cos(deg(x))};
\end{axis}
\end{tikzpicture}
$x=Acos(\omega t)$
\\
\begin{tikzpicture}
\begin{axis}[
    Axis Style,
    xtick={
        3.14159,6.28319,9.42478,12.56637
    },
    xticklabels={
        $\dfrac{T}{2}$,T,$\dfrac{3T}{2}$,2T
    },
    ytick={-1,1},
    yticklabels={$-\omega A$,$\omega A$},
    y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
    ylabel = {Velocity, v},
    xlabel= {Time, t}
]
\addplot [mark=none, ultra thick, black] {-sin(deg(x))};
\end{axis}
\end{tikzpicture}
$v=-\omega A\sin(\omega t)$
\\
\begin{tikzpicture}
\begin{axis}[
    Axis Style,
    xtick={
        3.14159,6.28319,9.42478,12.56637
    },
    xticklabels={
        $\dfrac{T}{2}$,T,$\dfrac{3T}{2}$,2T
    },
    ytick={-1,1},
    yticklabels={$-\omega^2 A$,$\omega^2 A$},
    y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
    ylabel = {Acceleration, a},
    xlabel= {Time, t}
]
\addplot [mark=none, ultra thick, black] {-cos(deg(x))};
\end{axis}
\end{tikzpicture}
$a=-\omega^2A\cos(\omega t)$
\section{Acceleration vs Displacement SHM Graph}
\begin{tikzpicture}[scale=0.7]
\begin{axis}[axis lines=middle,xtick={-4,4},xticklabels={-A,A},ytick={-4,4},yticklabels={$-\omega^2A$,$\omega^2A$},
ylabel=a/$ms^{-2}$,y label style={at={(ticklabel* cs:1.1)},anchor=north},
xlabel=x/m,x label style={at={(ticklabel* cs:1.1)},anchor=east}
]
\addplot[domain=-4:4]{-x};
\end{axis}
\end{tikzpicture}
\newpage
\section{Period of a pendulum}
$T=2\pi\sqrt{\dfrac{L}{g}}$\\
$T^2=\dfrac{4\pi^2L}{g}$\\
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-0.01,ticks=none,ylabel=$T^2/s^2$,xlabel=$L/m$,axis lines=middle,label style={font=\large}]
\addplot[mark=none]{x};
\end{axis}
\end{tikzpicture}\\
The gradient of the graph is $\dfrac{4\pi^2}{g}$\\
\section{Energy in SHM}
\begin{tikzpicture}
\begin{axis}[
    Axis Style,
    xtick={
        3.14159,6.28319
    },
    xticklabels={
        $\dfrac{T}{2}$,T
    },
    ytick={1},
    yticklabels={$\frac{1}{2}m\omega^2A^2$},
    y label style={at={(axis description cs:-0,.25)},rotate=90,anchor=south},
    ylabel = {Energy/J},
    xlabel= {Time, t},
    x label style={at={(axis description cs:1.12,0)},anchor=east},
    xmax=6.28319,
    ymin=0
]
\addplot [mark=none, ultra thick, black,samples=200] {(cos(deg(x)))^2};
\addplot [mark=none, ultra thick, red,samples=200] {(sin(deg(x)))^2};
\end{axis}
\end{tikzpicture}
\\
Red - Kinetic Energy\\
Black - Gravitational potential energy\\
\\
\begin{tikzpicture}
\begin{axis}[ymin=0,ticks=none,xlabel={Displacement,x/m},ylabel={Energy/J}]
\addplot [mark=none, ultra thick, black,samples=200] {x^2};
\addplot [mark=none, ultra thick, red,samples=200] {-x^2+25};
\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
\end{axis}
\end{tikzpicture}
\newpage
\section{Barton's Pendulum}

\begin{tikzpicture}[scale=0.3,
bob/.style={circle, draw=black, fill=white, very thick, minimum size=5mm}
]
\draw[black, very thick] (0,0)rectangle (49,2) node[pos=.5] {Retaining Bar};
\draw (0,0) -- (9,-9);
\draw (9,-9) -- (49,0);
\node[bob] (driver) at (9,-20) {Driver};
\draw (9,-9) -- (driver.north);
\node[bob] (a) at (19,-15) {A};
\draw (19,-6.75) -- (a.north);
\node[bob] (b) at (29,-20) {B};
\draw (29,-4.5) -- (b.north);
\node[bob] (c) at (39,-25) {C};
\draw (39,-2.25) -- (c.north);
\begin{pgfonlayer}{background layer}
\draw[very thick] (0,-20) -- (49,-20);
\end{pgfonlayer}{background layer}
\end{tikzpicture}
\\
\\
All lengths are measured from the retaining bar to the centre of mass of the bob.\\
\\
The \textbf{natural} frequency is the frequency of an object oscillating in the absence of any driving or damping force \textbf{Driver in diagram}.\\
\\
The \textbf{driven} frequency is where an external force is provided, making the oscillator undergo forced vibrations. \textbf{A,B and C in diagram}.\\
\\
\textbf{Resonance} occurs when the frequency of the driving force is equal to the natural frequency and can result in large amplitude oscillations. \textbf{B in diagram}.\\
\\

\begin{tabu} to \textwidth { | X[c] | X[c] | X[c] | X[c] | }
 \hline
\textbf{Pendulum}&\textbf{Natural frequency}&\textbf{Amplitude(wrt driver)}&\textbf{Phase(wrt driver)} \\
\hline
A&Higher than driver&Small&In phase\\
\hline
B&Equal to driver (resonance)&Large&Out of phase$(90\degree or \frac{\pi}{2})$\\
\hline
C&Lower than driver&Smaller than resonant&Antiphase$(180\degree or \pi)$\\
\hline
\end{tabu}

\section{How do engineers prevent resonance}
Ways to prevent resonance
\begin{itemize}
\item Use several materials - they all have different resonance properties
\item Don't have symmetry - prevents standing waves
\item Use very stiff materials - High frequency, small wavelengths
\end{itemize}

\includegraphics[width=7cm] {damp_6.jpg}
\section{Damping}
Damping is the reduction in amplitude due to energy losses (e.g. overcoming friction).\\
\\
It will also cause the period to increase (it is essentially a driver).\\
\\
\textbf{Light(underdamping)} - Small amplitude change per oscillation\\
\textbf{Heavy(underdamping} - Large amplitude change per oscillation\\
\\
\textbf{Critical damping} - Reaches equilibrium in the shortest possible time \textbf{without} oscillating\\
\\
\textbf{Over damping} - Reaches equilibrium after a long period of time
\subsection{Damping graph}
\begin{tikzpicture}
\begin{axis}[axis lines=middle,samples=200,ymax=10,ticks=none,ylabel=Amplitude,ylabel style={rotate=90, anchor=south,at={(axis description cs:0,0.42)},},xlabel=Time,x label style={at={(axis description cs:1.1,0.42)},anchor=east},]
\addplot[blue,domain=0:21] {1/x};\addlegendentry{Critically Damped}
\addplot[red,domain=0.01:20.58] {78*sin(deg(x+7.7))/(x+7.7)};\addlegendentry{Under Damped}
\addplot[green,domain=0.01:21] {-3*ln(x+2)+12};\addlegendentry{Over damped}
\end{axis}
\end{tikzpicture}
\section{Mass spring system}
\subsection{Period of a mass-spring system}
The period of a mass-spring system is $T=2\pi\sqrt{\dfrac{m}{k}}$ or $T^2=\dfrac{4\pi^2m}{k}$\\
\begin{tikzpicture}[scale=0.5]
\begin{axis}[ymin=-0.001,ticks=none,ylabel=$T^2/s^2$,xlabel=$m/kg$,axis lines=middle,
label style={font=\large}
]
\addplot[mark=none]{x};
\end{axis}
\end{tikzpicture}\\
The gradient is $\dfrac{4\pi^2}{k}$\\
The line passes through the origin\\
This is only true for small oscillations as large oscillations go past the limit of proportionality
\subsection{Energy in a vertically oscillating spring}
\begin{tabular}{|c|c|c|c|}
\hline
&KE&GPE&Elastic Energy\\
\hline
Top&0&$2mgA$&$\frac{1}{2}k(e-A)^2$\\
\hline
Middle&Max=$\frac{1}{2}m\omega^2A^2$&$mgA$&$\frac{1}{2}ke^2$\\
\hline
Bottom&0&0&$\frac{1}{2}k(e+A)^2$\\
\hline
\end{tabular}

\end{document}

### 2018-04-06 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
Notes Update
Update of all files to shorten preamble

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{tikz}
-\usepackage{relsize}
+\usepackage{/home/sam/Documents/School_Notes/format}
+\lhead{A Level Physics - Further Mechanics and Thermal Physics}
+
+%File specific Preamble
+%Settings for cube diagram
 \usetikzlibrary{scopes,quotes,arrows.meta,arrows,shapes.geometric}
-\pgfplotsset{width=10cm,compat=1.9}
-\usepackage{gensymb}
-\usepackage{tabularx}
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
 \tikzstyle{arrow} = [thick,->,>=stealth]
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
-\lhead{A Level Physics - Further Mechanics and Thermal Physics}
-\rfoot{Page \thepage}
-\pgfdeclarelayer{background layer}
-\pgfdeclarelayer{foreground layer}
-\pgfsetlayers{background layer,main,foreground layer}
 
@@
 \\
-\textcolor{red}{Replace M(Mass of all particles) with Nm(Number of particles $\times$ the mass of one particle}\\
+\textcolor{red}{Replace M(Mass of all particles) with Nm(Number of particles $\times$ the mass of one particle)}\\
 \\

### 2018-04-06 Physics Notes/Nuclear Physics/Radioactivity/Radioactivity.tex
Update of all files to shorten preamble

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-\usepackage{tabularx}
-\usepackage{relsize}
+\usepackage{/home/sam/Documents/School_Notes/format}
+\lhead{A Level Physics - Nuclear Physics}
+
+%File specific preamble
+%Diagrams
 \usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing}
 \pgfplotsset{width=10cm,compat=1.9}
-\usepackage[super]{nth}
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-\hyphenpenalty =10000
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
-\lhead{A Level Physics - Nuclear Physics}
-\rfoot{Page \thepage}
-\usepackage{mathtools}
+
 \usetikzlibrary{calc,quotes,angles}
@@
 
+%Proper paragraph formatting
 \setcounter{secnumdepth}{4}

### 2018-04-06 Physics Notes/Turning Points/Wave Particle Duality/Microscopes/Microscopes.tex
Update of all files to shorten preamble

@@
 \documentclass[12pt]{article}
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{titlesec}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{blindtext}
-\usepackage{textcomp}
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
+\usepackage{/home/sam/Documents/School_Notes/format}
 \lhead{A Level Physics - Turning Points}
+
 \begin{document}

### 2018-04-06 Maths Notes/Statistics/S2/Definitions/Definitions.tex
S2/S3 Definitions update

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Maths - S2}

\begin{document}
\begin{center}
\underline{\huge Definitions}
\end{center}
\large
\section{Population and Samples}
Statistic - A random variable, a function of known observations from a population, no unknown parameters\\
\\
Sampling unit - An individual unit of the population\\
\\
Sampling frame - A list of all sampling units\\
\\
Sampling distribution - All possible samples are chosen from the population\\
\\
Census - When every member of the population is investigated\\
\\
Population - A collection of all items\\
\\
Finite Population - One in which each individual member can be given a number\\
\\
Infinite population - One where it is impossible to number each individual member\\
\\
Sample - A selection of items from a population\\
\\
Bias - Anything which prevents a sample from being truly representative\\
\\
\section{Hypothesis Tests}
Significance level - The probability of incorrectly rejecting $H_0$\\
\\
Hypothesis test - A mathematical procedure to examine a value of
a population parameter proposed by the null hypothesis compared with an alternative hypothesis\\
\\
Critical Region - The range of values that would lead to the rejection of $H_0$, and so the acceptance of $H_1$\\
\\
Hypothesis - A statement concerning a population parameter\\
\\
Test Statistic - Data collected to test a hypothesis
\end{document}

### 2018-04-09 Maths Notes/Further Pure/FP2/First Order Differential Equations/First Order Differential Equations.tex
Update of all files to shorten preamble
Tidied to work with all linux systems
Update to 1st ODE to give example for IF

--- 2018-01-26 Maths Notes/FP2/First Order Differential Equations/First Order Differential Equations.tex
@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-\usepackage{relsize}
-\pgfplotsset{width=10cm,compat=1.9}
-
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
+\usepackage{../../../../format}
 \lhead{A Level Maths - FP2}
-\rfoot{Page \thepage}
 
@@
 $$f(x)\frac{dy}{dx}+f'(x)y$$
+This form can then be shortened by integrating:
+$$\int f'(x)g(x)+f(x)g'(x) dx=f(x)g(x)+c$$
+Integrate both sides then simplify
+\subsection{Example}
+$$p\frac{dx}{dt}+qx=r \qquad \textrm{Where p,q and r are constants}$$
+\textit{Given that $x=0$ when $t=0$}\\
+\textit{Find x in terms of t}\\
+\\
+\textcolor{red}{Divide through by p to ensure $\frac{dx}{dt}$ has no multiplier}
+$$\frac{dx}{dt}+\frac{q}{p}x=\frac{r}{p}$$
+\textcolor{red}{Find the integrating factor (IF)}
+{\Large
+$$IF: \mathlarger{e^{\int \frac{q}{p} \ dt}=e^\frac{qt}{p}}$$}
+\textcolor{red}{Multiply through by the IF to make the equation in the right form}
+{\Large
+$$e^\frac{qt}{p}\frac{dx}{dt}+\frac{q}{t}xe^\frac{qt}{p}=\frac{r}{p}e^\frac{qt}{p}$$}
+\textcolor{red}{Integrate both sides, simplify the LHS}
+{\Large
+$$xe^\frac{qt}{p}=\int \frac{r}{p}e^\frac{qt}{p} \ dt$$}
+\textcolor{red}{Do the integration on the RHS and simplify}
+{\Large
+$$xe^\frac{qt}{p}=\frac{r}{q}e^\frac{qt}{p}+c$$}
+\textcolor{red}{Substitute in x=0 and t=0 to find the value of c}
+$$0=\frac{r}{q}+c$$
+$$c=-\frac{r}{q}$$
+\textcolor{red}{Substitute in the value of c and divide through by the IF}
+{\Large
+$$xe^\frac{qt}{p}=\frac{r}{q}e^\frac{qt}{p}-\frac{r}{q}$$
+$$x=\frac{r}{q}-\frac{r}{q}e^{-\frac{qt}{p}}$$}
 \section{First order DE with given substitution}

### 2018-04-10 Maths Notes/Further Pure/FP2/Exam Questions/Further Complex Numbers/Complex Numbers Exam.tex
FP2 Notes Update

\documentclass{article}[18pt]
\usepackage{../../../../../format}
\lhead{A Level Maths - FP2}

\begin{document}
\begin{center}
\underline{\huge Complex Numbers - Exam Questions}
\end{center}
\section{Example 1 - Finding roots of $z^a$}
\textit{Find the four roots of the equation {\large$z^4=8(\sqrt{3}+i)$} in the form {\large$z=re^{i\theta}$}}
\\
\textcolor{red}{Convert into the form {\large $z^4=re^{i\theta}$}}
$$\theta=\arctan\bigg(\frac{1}{\sqrt{3}}\bigg)=\frac{\pi}{6}$$
$$r=\sqrt{(8\sqrt{3})^2+8^2}=16$$
{\Large
$$z^4=16e^{i(\frac{\pi}{6}+2k\pi)}$$}
\textcolor{red}{Take the fourth root of both sides}
{\Large
$$z=2e^{i(\frac{\pi}{24}+\frac{1}{2}k\pi)}$$}
\textcolor{red}{Substitute in values of k to get values of $\theta$ between 0 and $2\pi$}
{\large
$$z=2e^{i\frac{\pi}{24}}$$
$$z=2e^{i\frac{13\pi}{24}}$$
$$z=2e^{i\frac{25\pi}{24}}$$
$$z=2e^{i\frac{37\pi}{24}}$$}

\end{document}

### 2018-04-12 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
Tidied to work with all linux systems
FP2 Notes Update

@@
 \documentclass{article}[18pt]
-\usepackage{/home/sam/Documents/School_Notes/format}
+\usepackage{../../../../format}
 \lhead{A Level Maths - FP2}
@@
 \usepackage[super]{nth} %Provides 2nd etc
+
+\usepackage{chngcntr} %Resets equation numbering after each section or subsection
+\counterwithin*{equation}{section}
+\counterwithin*{equation}{subsection}
 
@@
 \begin{equation}\label{eq:2}
-\frac{d^2y}{dx^2}+y=0
+\frac{d^2y}{du^2}+y=0
 \end{equation}
@@
 Simplify using known expression for $\frac{dy}{du}$
-$$\frac{d^2y}{dx^2}=\frac{d}{du}\Bigg(e^u\frac{dy}{dx}\Bigg)$$
+$$\frac{d^2y}{du^2}=\frac{d}{du}\Bigg(e^u\frac{dy}{dx}\Bigg)$$
 Apply the product rule,using the chain rule to differentiate $\frac{dy}{dx}$ with respect to u
@@
 Substitute the results from \eqref{eq:3} and \eqref{eq:4} into \eqref{eq:1}.
-$$\frac{d^2y}{dx^2}-\frac{dy}{du}+\frac{dy}{du}+y=0$$
+$$\frac{d^2y}{du^2}-\frac{dy}{du}+\frac{dy}{du}+y=0$$
 Simplify to find answer
-$$\frac{d^2y}{dx^2}+y=0$$
+$$\frac{d^2y}{du^2}+y=0$$
 \textit{Solve this to find the general solution}
@@
 $$y=A\cos(\ln(x))+B\sin(\ln(x))$$
+\newpage
+\subsection{Example 2}
+\textit{Show that the transformation $x=e^u$ transforms the differential equation}
+\begin{equation}\label{eq2:1}
+x^2\frac{d^2y}{dx^2}-7x\frac{dy}{dx}+16y=2\ln x, \ x>0
+\end{equation}
+into the differential equation
+\begin{equation}\label{eq2:2}
+\frac{d^2y}{du^2}-8\frac{dy}{du}+16y=2u
+\end{equation}
+\\
+\textcolor{red}{\large Find $\frac{dy}{dx}$ in terms of $\frac{dy}{du}$}
+$$x=e^u \quad \frac{dx}{du}=e^u \quad \frac{du}{dx}=e^{-u} \quad 
+\frac{dy}{dx}=\frac{dy}{du}\times\frac{du}{dx}=\mathbf{e^{-u}\frac{dy}{du}}
+$$
+\textcolor{red}{\large Find $\frac{d^2y}{dx^2}$ in terms of $\frac{d^2y}{du^2}$ and $\frac{dy}{du}$}\\
+\textcolor{red}{Find $\frac{dy}{du}\Big(\frac{dy}{dx}\Big)$ by applying the product rule}
+$$\frac{dy}{du}\Big(\frac{dy}{dx}\Big)=-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}$$
+\textcolor{red}{Multiply through by $\frac{du}{dx}$ to find the value of $\frac{d^2y}{dx^2}$}
+$$\frac{d^2y}{dx^2}=\frac{dy}{du}\Big(\frac{dy}{dx}\Big)\times\frac{du}{dx}$$
+$$\frac{d^2y}{dx^2}=e^{-u}\Big(-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}\Big)$$
+$$\frac{d^2y}{dx^2}=\mathbf{e^{-2u}\Big(-\frac{dy}{du}+\frac{d^2y}{du^2}\Big)}$$
+\textcolor{red}{Substitute the values into the original formula, replacing $x$ with $e^u$}
+$$e^{2u}\times e^{-2u}\Big(-\frac{dy}{du}+\frac{d^2y}{du^2}\Big)-7e^u\times e^{-u}\frac{dy}{du}+16y=2u$$
+$$-\frac{dy}{du}+\frac{d^2y}{du^2}-7\frac{dy}{du}+16y=2u$$
+$$\frac{d^2y}{du^2}-8\frac{dy}{du}+16y=2u$$
+
 \end{document}

### 2018-04-13 Maths Notes/Statistics/S3/Any kind of hypothesis test in S3/S3 Hypothesis Tests.tex
Notes Update

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - S3}

\begin{document}
\begin{center}
\underline{\huge What the hypotheses are for all S3 tests}
\end{center}
\section{Estimation, confidence intervals and tests}
\subsection{The difference between means}
$$H_0:\mu_a=\mu_b$$
$$H_1:\mu_a>\mu_b \ \textrm{or} \ 
\mu_a<\mu_b \  \textrm{or} \ 
\mu_a\neq\mu_b$$
\section{Goodness of fit and contingency tables}
\subsection{Goodness of fit of distributions}
\begin{center}
$H_0$: The distribution is suitable for the results\\
$H_1$: The distribution is not suitable for the results
\end{center}
\subsection{Contingency tables}
\begin{center}
$H_0$: The two data sets are independent\\
$H_1$: The two data sets are not independent
\end{center}
\section{Regression and correlation}
\subsection{Spearman's rank}
\begin{center}
$H_0$: $\rho_s=0$\\
$H_1$: $\rho_s<0$ or $\rho_s>0$ or $\rho_s\neq0$
\end{center}

\end{document}

### 2018-04-17 Maths Notes/Further Pure/FP2/Maclaurin and Taylor Series/Maclaurin and Taylor Series.tex
Update of all files to shorten preamble
Tidied to work with all linux systems
FP2 Summary Notes

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepgfplotslibrary{fillbetween}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-\usepackage{relsize}
-\pgfplotsset{width=10cm,compat=1.9}
-\usepackage[super]{nth}
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
+\usepackage{../../../../format}
 \lhead{A Level Maths - FP2}
-\rfoot{Page \thepage}
-
-\usepackage{cancel}
 
@@
 \textit{And that it is valid to differentiate an infinite series term by term, show that:}
-$$e^2=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}+...+\frac{x^r}{r!}+...$$
+$$e^x=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}+...+\frac{x^r}{r!}+...$$
 \\

### 2018-04-17 Maths Notes/Further Pure/FP2/Overall Notes/FP2 Notes.tex
FP2 Summary Notes

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - FP2}

\begin{document}
\begin{center}
\underline{\huge FP2}
\end{center}
\section{First order differential equations}
\subsection{Solving first order DE using an integrating factor}
Solving $\dfrac{dy}{dx}+P(x)y=Q(x)$\\
\\
IF(Integrating factor) is found by finding $\mathlarger{e^{\int p(x) \ dx}}$ And multiplying the DE by the IF.\\
\\
This will result in the DE being in the form:
$$f(x)\frac{dy}{dx}+f'(x)y$$
This form can then be shortened by integrating:
$$\int f'(x)g(x)+f(x)g'(x) dx=f(x)g(x)+c$$
Integrate both sides then simplify
\section{Further complex numbers}
\subsection{Converting between forms}
When converting from $x+iy$ to a form in r and $\theta$, take the angle from the positive $x$ axis
\subsection{Multiplying and dividing complex numbers}
It is easiest to use the exponential form, then convert if needed
\subsubsection{Multiplying}
$$Z_1Z_2=r_1e^{i\theta_1}\times r_2e^{i\theta_2}=r_1r_2e^{i(\theta_1+\theta_2)}$$
\subsubsection{Dividing}
$$\frac{Z_1}{Z_2}=r_1e^{i\theta_1}\div r_2e^{i\theta_2}=\frac{r+1}{r+2} e^{i(\theta_1-\theta_2)}$$
\subsection{De Moivre's theorem}
This is given on the data sheet
\subsubsection{Z formulas}
If $z=\cos\theta+i\sin\theta$
$$z+\frac{1}{z}=2\cos\theta$$
$$z-\frac{1}{z}=2i\sin\theta$$
$$z^n+\frac{1}{z^n}=2\cos n\theta$$
$$z^n-\frac{1}{z^n}=2i\sin n\theta$$
\subsection{Loci on the complex plane}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
Equation&Description\\
\hline
{\Large$|z-z_1|=r$}&A circle centre $(x_1,y_1)$ with a radius r\\
\hline
{\Large$|z-z_1|=|z-z_2|$}&A perpendicular bisector of the line segment joining points $z_1$ and $z_2$\\
\hline
{\Large$\arg(z-z_1)=\theta$}&The half line from a fixed point $z_1$, making an angle $\theta$ with the positive real axis\\
\hline
{\Large$\arg(\frac{z-z_1}{z-z_2})=\theta$}&An arc between the points $z_1$ and $z_2$ where the angle the lines from $z_1$ and $z_2$ to any point on the arc is $\theta$\\
\hline
\end{tabularx}
\subsection{Translations}
\begin{itemize}
\item $w=z+a+ib$ represents a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=kz$ represents an enlargement with scale factor $k$ centre $(0,0)$
\item $w=kz+a+ib$ represents an enlargement scale factor $k$ centre $(0,0)$ followed by a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=z^2$ multiply a shape by itself, for example a circle of radius 4 would go to radius 16
\end{itemize}
\section{Inequalities}
We can build upon our previous algebraic skills in order to solve more complex inequalities\\
Remember:
\begin{itemize}
\item Don't multiply anything that could be negative - use "squared" things
\item Find the critical values (f(x)=0)
\item Sketch the graph to solve
\end{itemize}
\section{Maclaurin and Taylor Series}
Use the formulas on the data sheet
\subsection{Solving differential equations using the Taylor expansion}
From the differential equation, calculate the values of $\frac{dy}{dx}$, $\frac{d^2y}{dx^2}$ etc up to whatever is needed.\\
Then substitute those values into the Taylor series to solve the differential equation

\end{document}

### 2018-04-18 Physics Notes/Turning Points/Special relativity/Special Relativity.tex
Update of all files to shorten preamble
Tidied to work with all linux systems
Bertozzi Notes

@@
 \documentclass[12pt]{article}
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{titlesec}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{blindtext}
-\usepackage{textcomp}
-\usepackage{pgfplots}
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
+\usepackage{../../../format}
 \lhead{A Level Physics - Turning Points}
-
-\usepackage{tikz}
-\usetikzlibrary{scopes}
-
-\usepackage{mathtools}
-
-\newtagform{brackets}{[}{]}
-\usetagform{brackets}
 
@@
 \section{Summary of equations}
+{\renewcommand{\arraystretch}{2}
 \begin{tabular}{l l}
@@
 Relativistic energy&\Large{$\frac{m_0c^2}{\gamma}$}
-\end{tabular}
+\end{tabular}}
+\newpage
+\section{Bertozzi's Experiment}
+\begin{center}
+\includegraphics[width=12cm]{Bertozzi.jpg}
+\end{center}
+The experiment was set out to determine the variation of the kinetic energy of an electron, based on derived measurements.\\
+\\
+Electrons were accelerated and fired across a gap to an aluminium plate.\\
+\\
+Electrons accelerated from rest, through a known P.D.\\
+Gain kinetic energy = eV (Known value)\\
+Calculate speed from $v=\frac{d}{t}$ (d=8.4m)\\
+\\
+As the bunch of electrons collided with the plate, the electrons give up their energy and the plate changes its temperature.\\
+\\
+Knowing the specific heat capacity, the energy can be determined
+$$E=mc\Delta\theta$$
+For a known number of electrons (n) the kinetic energy of one electron could be calculated
+$$E=\frac{mc\Delta\theta}{n}$$
+
 \end{document}

### 2018-04-19 Maths Notes/Further Pure/FP2/Overall Notes/FP2 Notes.tex
Summary Notes Update

@@
 \lhead{A Level Maths - FP2}
-
+\usepackage{tabularx}
 \begin{document}
@@
 Then substitute those values into the Taylor series to solve the differential equation
+\section{Polar Coordinates}
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+Equation&Description\\
+\hline
+$r=a$&A circle, centre (0,0) with a radius of a\\
+\hline
+$\theta=\alpha$&A half line starting from (0,0) making an angle $\alpha$ with the initial line\\
+\hline
+$r=a\theta$&A spiral starting at the origin\\
+\hline
+$r=a(1+\cos\theta)$&A cardioid with x intercept a\\
+\hline
+$r^2=a^2\cos2\theta$&An infinity symbol with x intercept of a\\
+\hline
+$r^2=a^2\sin2\theta$&Infinity symbol rotated by $\frac{\pi}{4}$\\
+\hline
+$r=a\sin3\theta$&A windmill with 3 blades\\
+\hline
+\end{tabularx}
+\newpage
+\subsection{Integration}
+$$\textrm{Area}=\frac{1}{2}\int_\alpha^\beta r^2 \ d\theta$$
+The area of the sector is bounded by the half lines $\theta=\alpha$ and $\theta=\beta$
+\subsection{Differentiation}
+To find tangents parallel and perpendicular to the initial line:\\
+\\
+Parallel: $\frac{dy}{d\theta}=0$\\
+Perpendicular: $\frac{dx}{d\theta}=0$
+\section{Second order differential equations}
+{\renewcommand{\arraystretch}{2}
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+\textbf{Solution to auxiliary equation}&\textbf{General solution}\\
+\hline
+Two real roots $b^2>4ac$&$Ae^{\alpha x}+Be^{\beta x}$\\
+\hline
+One real root $b^2=4ac$&$(A+bx)e^{\alpha x}$\\
+\hline
+Imaginary only root $b^2<4ac$&$y=Ae^{\alpha x}+Be^{-\alpha x}$\\
+\hline
+Complex root $b^2<4ac$&$y=Ae^{(\beta+\alpha i)x}+Be^{(\beta-\alpha i)x}$\\
+\hline
+\end{tabularx}}
+\subsection{Second ODE=f(x)}
+\subsubsection{Standard forms of f(x)}
+$f(x)=\lambda$\\
+$f(x)=\lambda+\mu x$\\
+$f(x)=\lambda+\mu x+\nu x^2$\\
+$f(x)=ke^{px}$\\
+$f(x)=m\cos\omega x$\\
+$f(x)=m\sin\omega x$\\
+$f(x)=m\cos\omega x\pm n\sin\omega x$
+\\
+To solve these find $\frac{dy}{dx}$ and $\frac{d^2y}{dx^2}$ and substitute them into the Second ODE, solving for the unknowns, then add them to the general solution.\\
+\\
+If there is a clash of terms between the CF and PI, then an alternate PI will be given to you.
+\subsection{Boundary conditions}
+If boundary conditions are given to you, the values of the unknowns can be found. Substitute the boundary conditions in and rearrange to find unknowns.
+\newpage
+\subsection{Substitution}
+Transformations can be used to simplify differential equations, leaving $\frac{d^2y}{dx^2}$ with no coefficient.\\
+Method:\\
+\textcolor{red}{\large Find $\frac{dy}{dx}$ in terms of $\frac{dy}{du}$}
+$$x=e^u \quad \frac{dx}{du}=e^u \quad \frac{du}{dx}=e^{-u} \quad 
+\frac{dy}{dx}=\frac{dy}{du}\times\frac{du}{dx}=\mathbf{e^{-u}\frac{dy}{du}}
+$$
+\textcolor{red}{\large Find $\frac{d^2y}{dx^2}$ in terms of $\frac{d^2y}{du^2}$ and $\frac{dy}{du}$}\\
+\textcolor{red}{Find $\frac{dy}{du}\Big(\frac{dy}{dx}\Big)$ by applying the product rule}
+$$\frac{dy}{du}\Big(\frac{dy}{dx}\Big)=-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}$$
+\textcolor{red}{Multiply through by $\frac{du}{dx}$ to find the value of $\frac{d^2y}{dx^2}$}
+$$\frac{d^2y}{dx^2}=\frac{dy}{du}\Big(\frac{dy}{dx}\Big)\times\frac{du}{dx}$$
+$$\frac{d^2y}{dx^2}=e^{-u}\Big(-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}\Big)$$
+$$\frac{d^2y}{dx^2}=\mathbf{e^{-2u}\Big(-\frac{dy}{du}+\frac{d^2y}{du^2}\Big)}$$
+\section{Series}
+Summations can sometimes be simplified using the method of differences\\
+\\
+This involves a summation where one term is subtracted from another, often gained from partial fractions.
+The terms in the middle of the series will then cancel with each other, leaving the summation just the terms at the beginning at the end, by summing these a simpler form can be gained.
 

### 2018-04-19 Maths Notes/Mechanics/M2/Centres of mass/Centres of mass.tex
Update of all files to shorten preamble
Tidied to work with all linux systems
Summary Notes Update

--- 2017-12-03 Maths Notes/M2/Centres of mass/Centres of mass.tex
@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-\usepackage{tabularx}
-
-\pgfplotsset{width=10cm,compat=1.9}
-
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
+\usepackage{../../../../format}
 \lhead{A Level Maths - M2}
-\rfoot{Page \thepage}
 
@@
 \begin{obeylines}
-\section{Centre if mass of a discrete mass distribution}
+\section{Centre of mass of a discrete mass distribution}
 $\bar{x}=\dfrac{\Sigma m_ix_i}{\Sigma m_i}$\\
@@
 \section{Equilibrium}
-To avoid tipping, the lime of action of the weight must be within the side of the lamina in contact with the plane.
+To avoid tipping, the line of action of the weight must be within the side of the lamina in contact with the plane.
 If a lamina is suspended from a fixed point, the centre of mass will be vertically below the point of suspension.
@@
 \end{center}
-\includegraphics[width=1.5in]{Equilibrium_Problem.JPG}\\
+\includegraphics[width=1.5in]{eq.jpg}\\
 \\
@@
 \\
-\textbf{Use symmetry to find the y coordinate of the centre of mass}\\
+\textbf{3. Use symmetry to find the y coordinate of the centre of mass}\\
 \\
@@
 \\
-\textbf{Re-draw to find angle}\\
+\textbf{4. Re-draw to find angle}\\
 \begin{tikzpicture}[scale=1.9]

### 2018-04-19 Maths Notes/Mechanics/M2/Overall notes/M2 Notes.tex
Summary Notes Update

--- 2017-12-06 Maths Notes/M2/Kinematics/Kinematics.tex
@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{relsize}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-\usepackage{tikz}
-\usetikzlibrary{positioning}
-\pgfplotsset{width=10cm,compat=1.9}
+\usepackage{../../../../format}
+\lhead{A Level Maths - M2}
 
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
-\lhead{A Level Maths - M2}
-\rfoot{Page \thepage}
+%File specific Preamble 
+\usetikzlibrary{positioning} %Used for diagram at bottom
 
@@
 \begin{center}
-\underline{\huge Kinematics}
+\underline{\huge M2 Notes}
 \end{center}
-\begin{obeylines}
-\section{Horizontal Projections}
-For a \textbf{constant speed} use \textbf{$Speed=\dfrac{Distance}{Time}$}
-
-For a \textbf{constant acceleration} use \textbf{SUVAT}
-
-For all projections:
-\begin{itemize}
-\item Assume air resistance to be zero
-\item Resolve horizontal and vertical motion
-\item Horizontal - Constant speed
-\item Vertical - Constant acceleration
-
-\end{itemize}
-
-\section{Angular projections}
-The same as horizontal projections but the initial vertical velocity isn't zero.
-Example:
-A particle is projected at a speed of $49ms^{-1}$ at an angle of $45 \degree$ above the horizontal.
-\textit{What is the time taken for the particle to reach its maximum height?}
-\begin{itemize}
-\item u=$49\sin45$
-\item v=0
-\item a=-g
-\item t=?
-\end{itemize}
-$0=49\sin45-gt$
-$t=\dfrac{49\sin45}{g}=\dfrac{5\sqrt{2}}{2}\approx3.54$
-\textit{What is the maximum height reached?}
-\begin{itemize}
-\item u=$49\sin45$
-\item v=0
-\item a=-g
-\item s=?
-\end{itemize}
-$v^2=u^2+2as$
-0=$(49\sin45)^2-2gs$
-$S=\dfrac{(49\sin45)^2}{2g}=61.3$
-\textit{What is the time of the flight?}
-\begin{itemize}
-\item u=$49\sin45$
-\item a=-g
-\item S=0
-\item t=?
-\end{itemize}
-$S=ut+\dfrac{1}{2}at^2$
-$ $
-$0=(49\sin45)t-\dfrac{1}{2}gt^2$
-0=$t(49\sin45-\dfrac{gt}{2}$
-$t=0$
-$49\sin45=\dfrac{gt}{2}$
-$t=\dfrac{2\times49\sin45}{g}=7.07$
-\textit{What is the horizontal range of the particle?}
-\begin{itemize}
-\item t=7.07
-\item Speed=$49\cos45$
-\end{itemize}
-$S=45\cos45\times7.07=245$
-\end{obeylines}
-\section{Displacement, velocity and acceleration}
-$v=\dfrac{dx}{dt}$\\
-\\
-$a=\dfrac{dv}{dt}$\\
-\\
+\section{Centres of mass}
+\subsection{Centre of mass of a discrete mass distribution}
+$$\overline{x}=\frac{\sum m_ix_i}{\sum m_i}$$
+\section{Collisions}
+\subsection{Impulse and Momentum}
+$$I=m(v-u)$$
+\subsection{Coefficient of restitution}
+$$e=\frac{\textrm{Speed of seperation}}{\textrm{Speed of approach}}$$
+This can be rearranged to give in in terms of heights
+$$e=\frac{\sqrt{h_2}}{\sqrt{h_1}}$$
+\section{Kinematics}
 \begin{tikzpicture}
@@
 \end{tikzpicture}
-\newpage
-\begin{center}
-\underline{\huge Kinematics Example - Problems with calculus}
-\end{center}
-\textit{A particle P moves along the x-axis in a straight line so that, at time t seconds, the velocity of P is $v \ \text{ms}^{-1}$, where}\\
-\\
-$
-  v=\left\{
-  \begin{array}{@{}ll@{}}
-    10t-2t^2, & \text{for}\ 0\leqslant t \leqslant 6  \\
-    -\dfrac{432}{t^2}, & t>6
-  \end{array}\right.
-$\\
-\\
-\\
-\textit{At $t = 0$, P is at the origin O. Find the displacement of P from O when}\\
-\\
-$\mathit{t = 6}$\\
-\\
-\textbf{Integrate velocity}\\
-\\
-\textcolor{red}{$\mathlarger{x=\int v \ dt}$}\\
-\\
-$x=\int 10t-2t^2 \ dt= 5t^2-\frac{2}{3}t^3+c$\\
-\\
-\\
-\textbf{Substitute in the value of t}\\
-\\
-$t=6$\\
-\\
-$x=5\times6^2-\frac{2}{3}\times6^3=36m$\\
-\\
-\\
-$\mathit{t = 10}$
-\\
-\textbf{Integrate velocity for the second half of the journey}\\
-\\
-$x=\mathlarger{\int-\dfrac{432}{t^2} \ dt=\int-432t^{-2} \ dt=\dfrac{-432t^{-1}}{-1}+k=\dfrac{432}{t}+k}$\\
-\\
-\textbf{Find value of k by using known distance at t=6}\\
-\\
-$t=6 \ \ x=36$\\
-\\
-$36=\dfrac{432}{6}+k$\\
-\\
-$k=36-72=-36$\\
-\\
-\textbf{Find distance using value of k and t}\\
-\\
-$t=10$\\
-\\
-$x=\dfrac{432}{10}-36=7.2\text{m}$
+\section{Work, Energy and Power}
+$$\textrm{Work}=\textrm{Force}\times\textrm{Distance}$$
+$$WD=\mu R\times\textrm{Distance}$$
+$$E_K=\frac{1}{2}mv^2$$
+$$E_P=mgh$$
+$$P=Fv$$
 

### 2018-04-19 Maths Notes/Statistics/S2/Overall Notes/S2 Notes.tex
Summary Notes Update

--- 2017-11-01 Maths Notes/S2/Hypothesis testing/Hypothesis testing.tex
@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-
-\pgfplotsset{width=10cm,compat=1.9}
-
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
+\usepackage{../../../../format}
 \lhead{A Level Maths - S2}
-\rfoot{Page \thepage}
 
@@
 \begin{center}
-\underline{\huge Hypothesis testing}
+\underline{\huge S2 Notes}
 \end{center}
-\section{Tests of hypotheses}
-\textbf{Statistical hypothesis} - An assertion or conjecture concerning a population.\\
-\\
-To test the validity of a statement a random sample is taken from the population and that data can them be used to provide evidence that either supports or does not support the hypothesis.\\
-\\
-\textbf{Null hypothesis} - $H_0$ - A hypothesis assumed to be true
-\textbf{Alternative hypothesis} - $H_1$ - The situation if $H_0$ is false.
-
-If the data leads to rejection of the null hypothesis the alternative hypothesis will be accepted.
-
-The sample data is used to evaluate the \textbf{test statistic}, probabilities related to it can be calculated using the null hypothesis.
-
-If the test statistic is found in the \textbf{critical region} the null hypothesis will be rejected.
-
-The \textbf{boundary values} of the critical region are called the critical values.
-\section{Method}
+\section{Continuous random variables}
+\subsection{Probability Density Function}
+\begin{itemize}
+\item $f(x)\geqslant 0$ for all values of $x$, so that no probabilities are negative.
+\item $\mathlarger{\int_{\infty}^{-\infty}} f(x) dx=1$  (The sum of all probabilities is 1)
+\item $P(a<x<b)=\mathlarger{\int_{a}^{b}} f(x) dx$
+\end{itemize}
+\subsection{Median}
+When finding the median of a CRV with multiple ranges, set F(x) to 0.5 and rearrange. If x lies outside the range, change to a different range until one works
+\section{Continuous distributions}
+\subsection{Continuity correction}
+{\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{|c|c|}
+\hline
+Probability&Corrected Probability\\
+\hline
+$P(X=n)$&$P(n-0.5<X<n+0.5)$\\
+\hline
+$P(X>n)$&$P(X>n+0.5)$\\
+\hline
+$P(X\leqslant n)$ &$P(X<n+0.5)$\\
+\hline
+$P(X<n)$&$P(X<n-0.5)$\\
+\hline
+$P(X\geqslant n)$&$P(X>n-0.5)$\\
+\hline
+\end{tabular}}
+\section{Discrete distributions}
+\subsection{Samples}
+When asked to list all the possible samples remember:
+$$\textrm{Number of samples}=\textrm{Number of options}^\textrm{Sample size}$$
+\section{Hypothesis tests}
+Remember to split the significance level for a two tailed test
+\subsection{Method}
 \begin{enumerate}
@@
 \end{enumerate}
-
 \end{document}

### 2018-04-19 Maths Notes/Statistics/S3/Overall Notes/S3 Notes.tex
Summary Notes Update

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - S3}

\begin{document}
\begin{center}
\underline{\huge S3 Notes}
\end{center}
\section{Estimation, confidence intervals and tests}
\subsection{Estimators}
Bias is:
$$E(T)-\theta$$
To make the formula for $S^2$ in the formula book easier to use replace the top of the fraction with $S_{xx}$ from the formula book
\subsection{Standard error}
Standard error is:
$$\frac{\sigma}{\sqrt{n}} \ \textrm{or} \ \frac{s}{\sqrt{n}}$$
This can be remembered as the square root of the approximated variance given in the formula book
\subsection{Central limit theorem}
CLT states that sample means from a distribution where n is greater than 50 is:
$$\overline{X}\sim N(\mu,\frac{\sigma^2}{n})$$
\subsection{Confidence intervals}
To calculate the confidence interval use:
$$\overline{x}\pm z\times\frac{\sigma}{\sqrt{n}}$$
Where z is the value from the percentage points table that correlates to the probability in each of the tails on the normal distribution
\section{Goodness of fit and Contingency tables}
\subsection{Goodness of fit method}
Method for testing goodness of fit:
\begin{enumerate}
\item Determine which distribution would conceptually be most appropriate
\item Set significance level
\item Estimate parameters (if necessary) from observed data
\item Form hypotheses $H_0$ and $H_1$
\item Calculate expected frequencies
\item Combine expected frequencies so that none are $<5$
\item Find degrees of freedom
\item Calculate critical value of $\chi^2$ from the table
\item Calculate $\sum\frac{(O_i-E_i)^2}{E_i}$
\item See if the value is significant and draw conclusion
\end{enumerate}
$X^2$ is distributed with a chi squared distribution $\chi^2_\nu$\\
Where $\nu=$ degrees of freedom\\
$$\textrm{The number of degrees of freedom}=\textrm{Number of classes (after combining)}-1$$
\subsection{Contingency tables}
\begin{itemize}
\item We use this test to see if two factors are independent of each other
\item We describe them by: Number of rows $\times$ Number of columns
\item $H_0$ is that they are independent
\item $H_1$ is that they are not independent
\item $$\textrm{Expected values}=\frac{\textrm{Row total}\times\textrm{Column total}}{\textrm{Grand total}}$$
\item $$\nu=(\textrm{Number of rows-1})(\textrm{Number of columns-1})$$
\end{itemize}
\section{Combinations of normal distributions}
\subsection{Sums and Differences}
$$\mu_{x+y}=\mu_x+\mu_y$$
$$\mu_{x-y}=\mu_x-\mu_y$$
$$\sigma^2_{x+y}=\sigma^2_x+\sigma^2_y$$
$$\sigma^2_{x-y}=\sigma^2_x+\sigma^2_y$$
\subsection{Multiples}
$$\mu_{ax+by}=a\mu_x+b\mu_y$$
$$\mu_{ax-by}=a\mu_x-b\mu_y$$
$$\sigma^2_{ax+by}=a^2\sigma^2_x+b^2\sigma^2_x$$
$$\sigma^2_{ax-by}=a^2\sigma^2_x+b^2\sigma^2_x$$
\subsection{Addition vs Multiplication}
$$E(X_1+X_2)=E(2X_1)$$
However
$$Var(X_1+X_2)\neq Var(2X_1)$$
\\
$$Var(X_1+X_2)=\sigma_1^2+\sigma_1^2=2\sigma_2^2$$
$$Var(2X_1)=4\sigma^2_1$$
\section{Regression and Correlation}
Spearman's rank: The tendency for y to increase as x increases\\
PMCC:The closeness of the data to follow linear relationship\\
\\
For example an $x^3$ graph would have a Spearman's rank of 1 as it always increases, however the PMCC would not be 1 as it does not follow a linear relationship.

\end{document}

### 2018-04-23 Maths Notes/Statistics/S3/Goodness of fit and contingency tables/Goodness of fit and contingency tables.tex
Goodness of fit notes update
Update of all files to shorten preamble
Tidied to work with all linux systems
Notes Update
Fixed incorrect word

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage{tabularx}
-\usepackage{multirow}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-\usepackage{relsize}
-\pgfplotsset{width=10cm,compat=1.9}
-\usepackage{enumitem}
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-\hyphenpenalty=10000
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
+\usepackage{../../../../format}
 \lhead{A Level Maths - S3}
-\rfoot{Page \thepage}
+
+%File specific Preamble
+\usepackage{multirow} %Merge cells in tables
 
@@
 $$\textrm{The number of degrees of freedom}=\textrm{Number of classes (after combining)}-1$$
+\\
+\\
+\\
+$$\sum\frac{(O_i-E_i)^2}{E_i} \textrm{can be rewritten as  } \quad \Bigg(\sum\frac{O^2_i}{E_i}\Bigg)-N$$
 \newpage
@@
 \textcolor{red}{State hypotheses}
-$$H_0:\textrm{The binomial distribution is a suitable model}$$
-$$H_1:\textrm{The binomial distribution is a suitable model}$$
+$$H_0:\textrm{The uniform distribution is a suitable model}$$
+$$H_1:\textrm{The uniform distribution is a suitable model}$$
 \\
@@
 \item $H_0$ is that they are independent
-\item $H_1$ is that they are independent
+\item $H_1$ is that they are not independent
 \item $$\textrm{Expected values}=\frac{\textrm{Row total}\times\textrm{Column total}}{\textrm{Grand total}}$$

### 2018-04-24 Physics Notes/Turning Points/Overall Notes/Turning Points.tex
Physics notes summary update

\documentclass[12pt]{article}
\usepackage{../../../format}
\lhead{A Level Physics - Turning Points}

\begin{document}
\begin{center}
\underline{\huge Turning Points}
\end{center}
\section{Electrons}
\subsection{Discharge tube}
A discharge tube has a high voltage applied across it, this voltage ionises the gas. These ions then accelerate towards the cathode, hitting it with enough energy to release free electrons from the surface. These combine with the ions, emitting light.
\subsection{Thermionic emission}
When a metal is heated free electrons are released from the surface
\subsection{Determining the specific charge of an electron}
\subsubsection{Method 1}
Adjust magnetic and electric field so the flow of electrons is horizontal\\
Combine
$$eV_a=\frac{1}{2}mv^2 \ \textrm{and} \ Bev=eE$$
To get
$$\frac{e}{m}=\frac{1}{2v_a}\Bigg(\frac{E}{B}\Bigg)^2$$
\subsubsection{Method 2}
Accelerate electrons in a circle using a magnetic field perpendicular to the direction of motion.\\
Combine
$$\frac{mv^2}{R}=Bev \ \textrm{and} \ eV_a=\frac{1}{2}mv^2$$
To get
$$\frac{e}{m}=\frac{2V_a}{(BR)^2}$$
\subsection{Milikan's experiment}
\begin{figure}[h]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
\begin{tikzpicture}[
    force/.style={>=latex,draw=black,fill=black},
    m/.style={circle,draw=black,fill=white,radius=0.3cm,thin},scale=0.5
]
    \node[m] (m) {};
    {[force,->]
        \draw (m.north) -- ++(0,1) node[above] {Upthrust+Viscous drag};
        \draw (m.south) -- ++(0,-1) node[below] {Weight};
    }
\end{tikzpicture}
        \caption{No electric field}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
\begin{tikzpicture}[
    force/.style={>=latex,draw=black,fill=black},
    m/.style={circle,draw=black,fill=white,radius=0.3cm,thin},scale=0.5
]
    \node[m] (m) {};
    {[force,->]
        \draw (m.north) -- ++(0,1) node[above] {Upthrust+Electric force};
        \draw (m.south) -- ++(0,-1) node[below] {Weight};
    }
\end{tikzpicture}    
        \caption{Electric field}
    \end{minipage}
\end{figure}
\subsubsection{With electric field}
$$\textrm{Electric field}=\frac{QV}{d}$$
$$\textrm{Weight}=mg$$
$$\frac{QV}{d}=mg$$
\subsubsection{Without electric field}
$$F_D=6\pi r\eta v$$
$$\textrm{Weight}=mg$$
\begin{center}
Mass=Density$\times$Volume
$$\textrm{Mass}=\frac{4}{3}\pi r^3\rho$$
$$6\pi r\eta v=\frac{4}{3}\pi r^3\rho g$$
$$r^2=\frac{9\eta v}{2\rho g}$$
\end{center}
\subsubsection{Significance of results}
These results were significant because it introduced the idea of quantisation of charge
\section{Special relativity}
Special relativity is based on two postulates:
\begin{itemize}
\item The laws of physics, expressed in equations, have the same form in all inertial frames
\item The speed of light in free space is the same for all observers regardless of their state of motion and the speed of the light source
\end{itemize}
\subsection{The Michelson-Morley Experiment}
\includegraphics[width=6cm]{michelson.png}
\subsection{Relativistic momentum}
$$p=mv-\frac{m_0v}{\sqrt{1-(\frac{v}{c})^2}}$$
\subsection{Relativistic kinetic energy}
\begin{center}
Total energy=Rest energy+Relativistic KE
\end{center}
$$E_K=E-E_0$$
$$E_K=\frac{m_0c^2}{\sqrt{1-(\frac{v}{c})^2}}-m_0c^2$$
$$E_K=m_0c^2\Bigg(\bigg(1-\bigg(\frac{v}{c}\bigg)^2\bigg)^{-\frac{1}{2}}-1\Bigg)$$
Apply binomial expansion and approximation to get
$$E_K=\frac{1}{2}m_0v^2$$
\subsection{Bertozzi's Experiment}
\begin{center}
\includegraphics[width=12cm]{Bertozzi.jpg}
\end{center}
The experiment was set out to determine the variation of the kinetic energy of an electron, based on derived measurements.\\
\\
Electrons accelerated from rest, through a known P.D.\\
Gain kinetic energy = eV (Known value)\\
Calculate speed from $v=\frac{d}{t}$ (d=8.4m)\\
\\
As the bunch of electrons collided with the plate, the electrons give up their energy and the plate changes its temperature.\\
\\
Knowing the specific heat capacity and the number of electrons, the energy of one electron can be determined
$$E=\frac{mc\Delta\theta}{n}$$
\section{Wave Particle Duality}
\subsection{Electromagnetic waves}
\subsubsection{The nature of electromagnetic waves}
Electromagnetic waves are formed of perpendicular electric and magnetic fields, each of which sustain the other.\\
\subsubsection{Maxwell's Formula}
Permeability of free space - Relates the magnetic flux density of a magnetic field to the electric current that creates it\\
Permittivity of free space - Relaters the electric field strength to the charge that creates it
\subsubsection{Hertz and Radio waves}
\includegraphics[width=6cm]{hertz_1.jpg}\\
Radio waves were produced when a spark lept between the spark balls across an induction coil\\
The radio waves induce an EMF across the loop, causing a spark.\\
By placing a metal sheet in different places Hertz discovered radio waves are reflected by metal and pass straight through insulating materials.\\
By creating a standing wave and measuring the position of nodes and antinodes, the wavelength could be calculated.\\
The waves were demonstrated to be polarised when the loop was rotated 90 degrees and no sparks appeared, as the electric field was perpendicular to the loop.
\newpage
\subsubsection{Fizeau's determination of the speed of light and it's implications}
\includegraphics[width=6cm]{fizeau.jpg}\\
This experiment used a fast moving cog wheel which was increased in speed until the reflected light could not be seen. This meant that twice the distance between the wheel and the mirror would be equal to the time for a gap to be replaced by a tooth.\\
Time for one rotation:
$$T=\frac{1}{f_0}$$
Time for the wheel to move one tooth, where n is the number of teeth
$$t=\frac{T}{2N}$$
Combine the two above equations
$$t=\frac{1}{2f_0N}$$
Apply $\textrm{Speed}=\frac{\textrm{Distance}}{\textrm{Time}}$
$$c=\frac{2D}{\frac{1}{2f_0N}}=4Df_0N$$

\end{document}

### 2018-04-25 Physics Notes/Turning Points/Overall Notes/Turning Points.tex
Notes update
Notes Update

@@
 $$c=\frac{2D}{\frac{1}{2f_0N}}=4Df_0N$$
+\section{Microscopes}
+To find the voltage required to produce electrons of a given wavelength, rearrange the equation on the formula book
+$$\lambda=\frac{h}{\sqrt{2meV}}\Rightarrow \ V=\frac{h^2}{2me\lambda^2}$$
+\subsection{Transmission electron microscope}
+\includegraphics[width=8cm]{tem.png}
+This involves firing a beam of electrons at a high voltage towards an ultra thin specimen.\\
+When an electron wave encounters the specimen it can either:
+\begin{itemize}
+\item Pass straight through the specimen without interacting
+\item Get absorbed
+\item Diffract
+\end{itemize}
+The image detail can be improved by increasing the anode voltage of the electron gun.\\
+Image detail may reduce when travelling through the specimen as some electrons lose speed.
+\subsection{Scanning Tunnelling Microscope}
+\includegraphics[width=6cm]{stm.png}
+This has a very fine conducting probe very close to the surface of the sample.
 

### 2018-04-25 Physics Notes/Turning Points/Overall Notes/Turning Points.tex
Notes Update

@@
 $$c=\frac{2D}{\frac{1}{2f_0N}}=4Df_0N$$
-\section{Microscopes}
+\subsection{Microscopes}
 To find the voltage required to produce electrons of a given wavelength, rearrange the equation on the formula book
 $$\lambda=\frac{h}{\sqrt{2meV}}\Rightarrow \ V=\frac{h^2}{2me\lambda^2}$$
-\subsection{Transmission electron microscope}
+\subsubsection{Transmission electron microscope}
 \includegraphics[width=8cm]{tem.png}
@@
 Image detail may reduce when travelling through the specimen as some electrons lose speed.
-\subsection{Scanning Tunnelling Microscope}
-\includegraphics[width=6cm]{stm.png}
+\subsubsection{Scanning Tunnelling Microscope}
+\includegraphics[width=6cm]{stm.png}\\
 This has a very fine conducting probe very close to the surface of the sample.
+Quantum tunnelling means that over the very short distance there is a small probability electrons will cross the gap.
+A small voltage is maintained between the tip of the probe and the sample to ensure the electrons travel the right way.\\
+\\
+An STM can either have the probe at a constant height, and measure the current, or alter the height to keep constant current, and measure the height.
+\subsection{Newton's CT of light}
+Definition - Light is made up of tiny particles called corpuscles that always travel in a straight line
+\subsubsection{Reflection and refraction}
+Newton believed this theory was true as it can explain both reflection and refraction\\
+\includegraphics[width=6cm]{reflection.png}
+\includegraphics[width=6cm]{refraction.png}\\
+\\
+\textbf{Reflection} - These corpuscles have perfectly elastic collisions, meaning that the speed before is the speed after.
+The horizontal velocity doesn't change, the vertical velocity is inverted.
+Therefore angle of incidence equals angle of reflection.\\
+\\
+\textbf{Refraction} - Newton said the corpuscles were attracted into the material, causing them to travel faster, causing the component of the velocity perpendicular to the boundary to increase, causing angle with the normal to reduce.
+Newton was wrong.
+\subsubsection{Rival theories}
+Christiaan Huygens proposed the wave front theory, which is the theory we have been taught to describe refraction and diffraction. This described light travelling slower in a more dense material.\\
+\\
+Why Huygens' theory was rejected:
+\begin{itemize}
+\item It was not possible to measure the speed of light at that scale at that time, meaning neither theory could be proved correct or incorrect.
+\item Newton had a better reputation
+\item The wave theory only considered longitudinal waves so couldn't explain polarisation.
+\end{itemize}
+\subsection{The Discovery of photoelectricity}
+Black body - A theoretical perfect absorber and emitter of radiation\\
+Ultraviolet catastrophe - Where short wavelength radiation is incident on a black body, causing it to emit an infinite amount of power per unit wavelength
+\subsubsection{The failure of classical wave theory to explain observations on photoelectricity}
+\begin{itemize}
+\item Wave theory suggested that given enough time, electrons would gain enough energy from a wave to escape
+\item There would be a time lag between the light being incident and the emission of an electron
+\item Any frequency would be able to cause electron emission given enough time
+\end{itemize}
+\subsubsection{Einstein's Explanation of photoelectricity}
+Einstein showed electrons must have energy greater than the work function in order to escape a metal. Kinetic energy is the energy difference between the energy of the electron and the work function.
+\subsection{The significance of Young's double slit experiment}
+Young's double slit experiment showed interference, disproving Newton's Corpuscular Theory, however Huygen's wave theory was not accepted until Fizeau compared the speed of light in water and air.
+\subsection{Wave particle duality}
+By using the equations
+$$\frac{1}{2}mv^2=eV \ \textrm{and} \ \lambda=\frac{h}{mv}$$
+They can be used to get the equation
+$$\lambda=\frac{h}{\sqrt{2meV}}$$
 

### 2018-04-25 Physics Notes/Turning Points/Wave Particle Duality/The discovery of photoelectricity/Photoelectricity.tex
Physics Notes Update
Update of all files to shorten preamble
Tidied to work with all linux systems
Notes updated to include stopping potential

@@
 \documentclass[12pt]{article}
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{titlesec}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{blindtext}
-\usepackage{textcomp}
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
+\usepackage{../../../../format}
 \lhead{A Level Physics - Turning Points}
+
 \begin{document}
@@
 $$\frac{1}{2}mv^2=hf-\phi$$
+\\
+\\
+\begin{tikzpicture}
+\begin{axis}[axis lines=middle,scale=0.8,ylabel=$V_s$,xlabel=Frequency,ylabel style={rotate=90,anchor=south},xlabel style={anchor=south},xmin=0,xmax=7,ymin=-5,ymax=7,xtick={2},xticklabels={$f_0$},ytick={-2},yticklabels={$-\frac{\phi}{e}$}
+]
+\addplot[color=black,domain=0:7]{x-2};
+\end{axis}
+\end{tikzpicture}
+\subsection{Stopping potential}
+The stopping potential is the potential difference at which the current between electrodes is zero. This prevents electrons from reaching the anode/cathode, and depends on the maximum KE.\\
+{\large
+$$V_S=\frac{E_{k(\textrm{max})}}{e}$$}
 \end{document}

### 2018-04-26 Physics Notes/Turning Points/Wave Particle Duality/Newton's CT of light/Newton's CT of Light.tex
Update of all files to shorten preamble
Tidied to work with all linux systems
Notes updated to include forces for Newton's CT

@@
 \documentclass[12pt]{article}
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{titlesec}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{blindtext}
+\usepackage{../../../../format}
+\lhead{A Level Physics - Turning Points}
+
+%File specific preamble
 \usepackage{textcomp}
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-\pagestyle{fancy}
-\fancyhf{}
 \rhead{Sam Robbins and Fiona Turnbull}
-\lhead{A Level Physics - Turning Points}
+
 \begin{document}
@@
 \\
-\textbf{Reflection} - These corpuscles have perfectly elastic collisions, meaning that the speed before is the speed after.
+\textbf{Reflection} - There is a short range repulsive force.These corpuscles have perfectly elastic collisions, meaning that the speed before is the speed after.
 The horizontal velocity doesn't change, the vertical velocity is inverted.
@@
 \\
-\textbf{Refraction} - Newton said the corpuscles were attracted into the material, causing them to travel faster, causing the component of the velocity perpendicular to the boundary to increase, causing angle with the normal to reduce.
+\textbf{Refraction} - There is a short range attractive force.
+Newton said the corpuscles were attracted into the material, causing them to travel faster, causing the component of the velocity perpendicular to the boundary to increase, causing angle with the normal to reduce.
 Newton was wrong.

### 2018-04-26 Physics Notes/Turning Points/Wave Particle Duality/The discovery of photoelectricity/Photoelectricity.tex
Notes updated to include forces for Newton's CT

@@
 The stopping potential is the potential difference at which the current between electrodes is zero. This prevents electrons from reaching the anode/cathode, and depends on the maximum KE.\\
+The stopping potential acts to attract the electrons back to the plate by creating an electric field between the anode and the cathode.
 {\large

### 2018-04-29 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
FP2 Notes Update
Notes update

@@
 This uses the same parameters as $r(\cos\theta+i\sin\theta)$
+\section{Absolute square}
+When squaring $|z|$, where $z=x+iy$, first find $|z|$, which is $\sqrt{x^2+y^2}$, then square it to get $x^2+y^2$.
+
 \newpage
@@
 Combine like coloured term using z formula
-$$32\cos^5\theta=\textcolor{red}{2\cos\theta}+\textcolor{Green}{10\cos3\theta}+\textcolor{Plum}{20\cos\theta}$$
-$$\cos^5\theta=\frac{\cos\theta}{16}+\frac{5\cos3\theta}{16}+\frac{5\cos\theta}{8}$$
+$$32\cos^5\theta=\textcolor{red}{2\cos5\theta}+\textcolor{Green}{10\cos3\theta}+\textcolor{Plum}{20\cos\theta}$$
+$$\cos^5\theta=\frac{\cos5\theta}{16}+\frac{5\cos3\theta}{16}+\frac{5\cos\theta}{8}$$
 \section{Solving complex equations}
@@
 \end{itemize}
+When doing translations, the input is $z=x+iy$ and the output is $w=u+iv$, unless otherwise stated.
 \end{document}

### 2018-04-30 Maths Notes/Mechanics/M2/Centres of mass/Centres of mass.tex
Notes Update

@@
 \end{center}
-\begin{obeylines}
 \section{Centre of mass of a discrete mass distribution}
-$\bar{x}=\dfrac{\Sigma m_ix_i}{\Sigma m_i}$\\
-$\bar{y}=\dfrac{\Sigma m_iy_i}{\Sigma m_i}$\\
-\textbf{Example}\\
-\end{obeylines}
+$$\bar{x}=\dfrac{\Sigma m_ix_i}{\Sigma m_i}$$
+$$\bar{y}=\dfrac{\Sigma m_iy_i}{\Sigma m_i}$$
+\subsection{Example}
 \begin{tabular}{|c|c|c|c|}
@@
 \\
+$$\bar{x}=\dfrac{2\times 2+3\times3+2\times-3}{2+3+2}=1$$
+$$\bar{y}=\dfrac{2\times3+3\times6+2\times2}{2+3+2}=4$$
+\section{Uniform laminae}
+For a triangular lamina the centre of mass is $\frac{2}{3}$ along the line from the vertex to the middle of the line opposite.\\
 \\
-\begin{obeylines}
-$\bar{x}=\dfrac{2\times 2+3\times3+2\times-3}{2+3+2}=1$
-$\bar{y}=\dfrac{2\times3+3\times6+2\times2}{2+3+2}=4$
-\section{Uniform laminae}
-For a triangular lamina the centre of mass is $\frac{2}{3}$ along the line from the vertex to the middle of the line opposite.
+If given the coordinates of the vertices of a triangle, the centre of mass is the has coordinates of the mean of the x coordinates, and the mean of the y coordinates.\\
+\\
 For a sector of a circle, radius r, where the angle at the centre is $2\alpha$ the centre of mass is $\dfrac{2r\sin\alpha}{3\alpha}$
@@
 
-\end{obeylines}
 \newpage

### 2018-04-30 Maths Notes/Mechanics/M2/Collisions/Collisions.tex
Update of all files to shorten preamble
Tidied to work with all linux systems
Notes Update

--- 2017-12-05 Maths Notes/M2/Collisions/Collisions.tex
@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-
-\pgfplotsset{width=10cm,compat=1.9}
-
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-\pretolerance=10000
-\hyphenpenalty=10000
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
+\usepackage{../../../../format}
 \lhead{A Level Maths - M2}
-\rfoot{Page \thepage}
 
@@
 \\
-$e=\dfrac{\text{Speed of seperation}}{\text{Speed of approach}}$
+$$e=\frac{\text{Speed of seperation}}{\text{Speed of approach}}$$
 \subsection{Alternate form of coefficient of restitution formula}
-$mgh=\frac{1}{2}mv^2$\\
-\\
-$v=\sqrt{2gh}$\\
-\\
-$e=\dfrac{\sqrt{2gh_2}}{\sqrt{2gh_1}}$\\
-\\
-$e=\dfrac{\sqrt{h_2}}{\sqrt{h_1}}$\\
-\\
+$$mgh=\frac{1}{2}mv^2$$
+$$v=\sqrt{2gh}$$
+$$e=\dfrac{\sqrt{2gh_2}}{\sqrt{2gh_1}}$$
+$$e=\dfrac{\sqrt{h_2}}{\sqrt{h_1}}$$
 $h_2$ - the height the ball bounces back to\\
@@
 \subsection{Calculations involving coefficient of restitution}
-When doing calculations involving the coefficient of restitution both the calculation for CoR and conservation of momentum will be needed.\\
-\textbf{Conservation of momentum:}
-$m_1u_1+m_2u_2=m_1v_1+m_2v_2$\\
-\\
-\textbf{Coefficient of restitution}\\
-\\
-$e=\dfrac{v_1}{u_1}$
+When doing calculations involving the coefficient of restitution both the calculation for CoR and conservation of momentum will be needed.
 \subsection{Successive Impacts}
 In some cases calculations will involve the impacts of multiple balls successively, like in newton's cradle.
+\newpage
 \subsubsection{Example}
@@
 \\
-\textbf{Conservation of momentum}\\
-\textcolor{red}{$m_1u_1=m_1v_1\Rightarrow u_1=v_1$}\\
+\textbf{Conservation of velocity}\\
+\textcolor{red}{$u_1=v_1$}\\
 \\
@@
 \\
-\textbf{Combine result from Conservation of Momentum and Restitution}
+\textbf{Combine result from Conservation of velocity and Restitution by division}\\
+\\
+$3\tan2\theta=8\tan\theta$\\
+\\
+\textbf{Use tan addition formula}\\
+\\
+$3\Bigg(\dfrac{2\tan\theta}{1-\tan^2\theta}\Bigg)=8\tan\theta$\\
+\\
+\textbf{Rearrange to solve}\\
+\\
+$\dfrac{6\tan\theta}{1-\tan^2\theta}=8\tan\theta$\\
+\\
+$6\tan\theta=8\tan\theta-8\tan^3\theta$\\
+\\
+$6=8-8\tan^2\theta$\\
+\\
+$-2=-8\tan^2\theta$\\
+\\
+$\dfrac{1}{4}=\tan^2\theta$\\
+\\
+$\dfrac{1}{2}=\tan\theta$
 

### 2018-04-30 Maths Notes/Mechanics/M2/Kinematics/Kinematics.tex
Update of all files to shorten preamble
Tidied to work with all linux systems
Notes Update

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{relsize}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-\usepackage{tikz}
-\usetikzlibrary{positioning}
-\pgfplotsset{width=10cm,compat=1.9}
+\usepackage{../../../../format}
+\lhead{A Level Maths - M2}
 
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
+%File specific Preamble 
+\usetikzlibrary{positioning} %Used for diagram at bottom
 
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
-\lhead{A Level Maths - M2}
-\rfoot{Page \thepage}
-\usepackage{mathtools}
-\newtagform{brackets}{[}{]}
-\usetagform{brackets}
 \begin{document}
@@
 \end{center}
-\begin{obeylines}
 \section{Horizontal Projections}
-For a \textbf{constant speed} use \textbf{$Speed=\dfrac{Distance}{Time}$}
-
-For a \textbf{constant acceleration} use \textbf{SUVAT}
-
+For a \textbf{constant speed} use \textbf{$Speed=\dfrac{Distance}{Time}$}\\
+For a \textbf{constant acceleration} use \textbf{SUVAT}\\
 For all projections:
@@
 \item Vertical - Constant acceleration
-
 \end{itemize}
-
 \section{Angular projections}
 The same as horizontal projections but the initial vertical velocity isn't zero.
-Example:
-A particle is projected at a speed of $49ms^{-1}$ at an angle of $45 \degree$ above the horizontal.
+\subsection{Example}
+\textit{A particle is projected at a speed of $49ms^{-1}$ at an angle of $45 \degree$ above the horizontal.}\\
 \textit{What is the time taken for the particle to reach its maximum height?}
-\begin{itemize}
-\item u=$49\sin45$
-\item v=0
-\item a=-g
-\item t=?
-\end{itemize}
-$0=49\sin45-gt$
-$t=\dfrac{49\sin45}{g}=\dfrac{5\sqrt{2}}{2}\approx3.54$
-\textit{What is the maximum height reached?}
-\begin{itemize}
-\item u=$49\sin45$
-\item v=0
-\item a=-g
-\item s=?
-\end{itemize}
-$v^2=u^2+2as$
-0=$(49\sin45)^2-2gs$
-$S=\dfrac{(49\sin45)^2}{2g}=61.3$
-\textit{What is the time of the flight?}
-\begin{itemize}
-\item u=$49\sin45$
-\item a=-g
-\item S=0
-\item t=?
-\end{itemize}
-$S=ut+\dfrac{1}{2}at^2$
-$ $
-$0=(49\sin45)t-\dfrac{1}{2}gt^2$
-0=$t(49\sin45-\dfrac{gt}{2}$
-$t=0$
-$49\sin45=\dfrac{gt}{2}$
-$t=\dfrac{2\times49\sin45}{g}=7.07$
-\textit{What is the horizontal range of the particle?}
-\begin{itemize}
-\item t=7.07
-\item Speed=$49\cos45$
-\end{itemize}
-$S=45\cos45\times7.07=245$
-\end{obeylines}
+
+u=$49\sin45$\\
+v=0\\
+a=-g\\
+t=?
+$$0=49\sin45-gt$$
+$$t=\dfrac{49\sin45}{g}=\dfrac{5\sqrt{2}}{2}\approx3.54$$
+\textit{What is the maximum height reached?}\\
+u=$49\sin45$\\
+v=0\\
+a=-g\\
+s=?
+$$v^2=u^2+2as$$
+$$0=(49\sin45)^2-2gs$$
+$$S=\dfrac{(49\sin45)^2}{2g}=61.3$$
+\textit{What is the time of the flight?}\\
+u= $49\sin45$\\
+a=-g\\
+S=0\\
+t=?
+
+$$S=ut+\dfrac{1}{2}at^2$$
+$$0=(49\sin45)t-\dfrac{1}{2}gt^2$$
+$$49\sin45=\dfrac{gt}{2}$$
+$$t=\dfrac{2\times49\sin45}{g}=7.07$$
+\textit{What is the horizontal range of the particle?}\\
+t=7.07\\
+Speed=$49\cos45$
+$$S=45\cos45\times7.07=245$$
 \section{Displacement, velocity and acceleration}
@@
 \\
+\begin{center}
 \begin{tikzpicture}
@@
 \end{tikzpicture}
+\end{center}
 \newpage
@@
 \\
-\textit{At $t = 0$, P is at the origin O. Find the displacement of P from O when}\\
+\textit{At $t = 0$, P is at the origin O. Find the displacement of P from O when} $\mathit{t = 6}$\\
 \\
-$\mathit{t = 6}$\\
-\\
-\textbf{Integrate velocity}\\
-\\
-\textcolor{red}{$\mathlarger{x=\int v \ dt}$}\\
-\\
-$x=\int 10t-2t^2 \ dt= 5t^2-\frac{2}{3}t^3+c$\\
-\\
-\\
-\textbf{Substitute in the value of t}\\
-\\
-$t=6$\\
-\\
-$x=5\times6^2-\frac{2}{3}\times6^3=36m$\\
-\\
-\\
-$\mathit{t = 10}$
-\\
-\textbf{Integrate velocity for the second half of the journey}\\
-\\
-$x=\mathlarger{\int-\dfrac{432}{t^2} \ dt=\int-432t^{-2} \ dt=\dfrac{-432t^{-1}}{-1}+k=\dfrac{432}{t}+k}$\\
-\\
-\textbf{Find value of k by using known distance at t=6}\\
-\\
-$t=6 \ \ x=36$\\
-\\
-$36=\dfrac{432}{6}+k$\\
-\\
-$k=36-72=-36$\\
-\\
-\textbf{Find distance using value of k and t}\\
-\\
-$t=10$\\
-\\
-$x=\dfrac{432}{10}-36=7.2\text{m}$
+\textbf{Integrate velocity}
+\textcolor{red}{$$\mathlarger{x=\int v \ dt}$$}
+$$x=\int 10t-2t^2 \ dt= 5t^2-\frac{2}{3}t^3+c$$
+\textbf{Substitute in the value of t}
+$$t=6$$
+$$x=5\times6^2-\frac{2}{3}\times6^3=36m$$
+\textit{Find the displacement from O when t = 10}\\
+\textbf{Integrate velocity for the second half of the journey}
+$$x=\mathlarger{\int-\dfrac{432}{t^2} \ dt=\int-432t^{-2} \ dt=\dfrac{-432t^{-1}}{-1}+k=\dfrac{432}{t}+k}$$
+\textbf{Find value of k by using known distance at t=6}
+$$t=6 \ \ x=36$$
+$$36=\dfrac{432}{6}+k$$
+$$k=36-72=-36$$
+\textbf{Find distance using value of k and t}
+$$t=10$$
+$$x=\dfrac{432}{10}-36=7.2\text{m}$$
 \newpage

### 2018-04-30 Maths Notes/Mechanics/M2/Work, energy and power/Work, energy and power.tex
Update of all files to shorten preamble
Tidied to work with all linux systems
Notes Update

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
+\usepackage{../../../../format}
+\lhead{A Level Maths - M2}
+
+%File specific Preamble
 \usetikzlibrary{positioning,scopes,decorations.text}
-\pgfplotsset{width=10cm,compat=1.9}
-
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
-\lhead{A Level Maths - M2}
-\rfoot{Page \thepage}
 
@@
 \section{Work}
-$\mathbf{Work(J)=Force(N)\times Distance(m)}$
+$$\mathbf{\textrm{Work(J)=Component of force in the direction of motion(N)}\times \textrm{Distance moved in the same direction(m)}}$$
 For work done against  gravity, use vertical distance.
@@
 \section{Energy}
-$\mathbf{E_K=\frac{1}{2}mv^2}$
-$ $
-$\mathbf{GPE=E_P=mgh}$
+$$E_K=\frac{1}{2}mv^2$$
+$$GPE=E_P=mgh$$
 \section{Conservation of energy}
@@
 \section{Power}
-$\mathbf{Power=Force\times Velocity}$
+$$\mathbf{Power=Force\times Velocity}$$
 Usually given in kW

### 2018-05-01 Maths Notes/Mechanics/M2/Statics of rigid bodies/Statics of rigid bodies.tex
Update of all files to shorten preamble
Tidied to work with all linux systems
Notes Update
Moment equation addition

@@
 \documentclass{article}[18pt]
-\usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
-\usepackage{parselines} 
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{titlesec}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{fancyhdr}
-\usepackage{gensymb}
-
-\pgfplotsset{width=10cm,compat=1.9}
-
-\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newlength\tindent
-\setlength{\tindent}{\parindent}
-\setlength{\parindent}{0pt}
-\renewcommand{\indent}{\hspace*{\tindent}}
-
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Sam Robbins 13SE}
+\usepackage{../../../../format}
 \lhead{A Level Maths - M2}
-\rfoot{Page \thepage}
 
@@
 \end{itemize}
+
+If a rigid body is in equilibrium under the action of three non parallel forces, the lines of actions of the three forces all pass through the same point.\\
+They can be arranged in a vector triangle to find forces
+
+$$\textrm{Moment of a force about a point P}=|\textrm{Force}|\times\textrm{Perpendicular distance of the line of action of the force from the point P}$$
+Essentially meaning, when taking non linear moments, the distances used should be the shortest distance from the point to where the force is acting.
 \newpage

### 2018-05-02 Maths Notes/Mechanics/M2/Statics of rigid bodies/Statics of rigid bodies.tex
Moment clarification

@@
 $$\textrm{Moment of a force about a point P}=|\textrm{Force}|\times\textrm{Perpendicular distance of the line of action of the force from the point P}$$
-Essentially meaning, when taking non linear moments, the distances used should be the shortest distance from the point to where the force is acting.
+Essentially meaning, when taking non linear moments, the distances used should be the shortest distance from the point to where the force is acting.\\
+The line of action is the line, both backwards and forwards from where the force is acting.
 \newpage

### 2018-05-02 Maths Notes/Further Pure/FP2/Overall Notes/FP2 Notes.tex
FP2 Notes updated to reflect mock

@@
 $$z^n-\frac{1}{z^n}=2i\sin n\theta$$
+\subsection{Solving complex equations}
+When solving $z^a=r(\cos(\theta)+i\sin(\theta))$ type questions, remember to first rewrite as:
+$$z^a=r(\cos(\theta+2k\pi)+i\sin(\theta+2k\pi))$$
+
 \subsection{Loci on the complex plane}

### 2018-05-03 Physics Notes/Turning Points/Wave Particle Duality/Microscopes/Microscopes.tex
Tidied to work with all linux systems
Microscopes notes update

@@
 \documentclass[12pt]{article}
-\usepackage{/home/sam/Documents/School_Notes/format}
+\usepackage{../../../../format}
 \lhead{A Level Physics - Turning Points}
@@
 \\
-The image detail may reduce when travelling through the specimen as some electrons may have a loss of speed, causing the magnetic lenses to be unable to focus the electrons, a type of material dispersion.
+The image detail may reduce when travelling through the specimen as some electrons may have a loss of speed, causing the magnetic lenses to be unable to focus the electrons, a type of material dispersion.\newpage
+\section{TEM Further notes}
+\subsection{Electron Gun}
+\begin{itemize}
+\item Electrons are produced by thermionic emission, causing a speed distribution dependent on temperature
+\item Accelerated through a p.d.
+\item To resolve atoms, the de Broglie wavelength of the electrons must be less than the diameter of an atom (0.1nm)
+\end{itemize}
+\subsection{Condenser lens}
+\begin{itemize}
+\item Gather electrons and focus them onto the specimen to illuminate only the area being examined
+\item Deflects electrons into a wide parallel beam incident uniformly on the sample
+\item Electrons through the middle undeflected
+\item Electrons on the edge are deflected towards the axis
+\item Reduces aberration 
+\end{itemize}
+\subsection{Specimen}
+\begin{itemize}
+\item Thick areas absorb more electrons, result in darker areas on the screen
+\item Thin areas absorb fewer electrons, result in lighter areas on the screen
+\item Electrons deflected are stopped by objective aperture
+\item A thicker specimen slows the electrons more, resulting in a lower resolution image
+\end{itemize}
+\subsection{Objective lens}
+\begin{itemize}
+\item Forms an image of the sample
+\item Used to focus and magnify the image
+\item Objective aperture set to smallest size to prevent diffracted beams contributing to the image
+\end{itemize}
+\subsection{Projector lens}
+\begin{itemize}
+\item Further magnifies the image and projects the image onto the fluorescent screen
+\end{itemize}
+
+\newpage
 \section{Scanning tunnelling microscope}

### 2018-05-11 Maths Notes/Core/C1/C1.tex
C1 Notes

\documentclass{article}[18pt]
\usepackage{../../../format}
\lhead{A Level Maths - C1}

\begin{document}
\begin{center}
\underline{\huge C1}
\end{center}
\section{Algebra and functions}
\subsection{Indices}
$a^m\times a^n=a^{m+n}$\\
$a^m\div a^n=a^{m-n}$\\
$(a^m)^n=a^{mn}$\\
$a^{-m}=\frac{1}{a^m}$\\
$a^{\frac{1}{m}}=\sqrt[m]{a}$\\
$a^{\frac{n}{m}}=\sqrt[m]{a^n}$\\
\section{Quadratic functions}
\subsection{Discriminant}
\begin{itemize}
\item $b^2>4ac$, Two real solutions
\item $b^2=4ac$, One repeated real solution
\item $b^2<4ac$, No real solution
\end{itemize}
\section{Sketching curves}
\subsection{Graph transformations}
\begin{itemize}
\item f(x)+a, $y$ coordinates increased by a
\item af(x), $y$ coordinates multiplied by a
\item -f(x), reflection in the $x$ axis
\item f(x+a), $x$ coordinates reduced by a
\item f(ax), $x$ coordinates divided by a
\item f(-x), reflection in the $y$ axis
\end{itemize}
\section{Coordinate geometry}
If two lines are perpendicular, the product of their gradients is -1.
\section{Sequences and series}
\subsection{Deriving the formula for the sub of an arithmetic series}
$$S_n=a+(a+d)+(a+2d)+...+(a+(n-1)d)$$
Reverse the sun
$$S_n=(a+(n-1)d)+(a+(n-2)d)+a(a+(n-3)d)+...+(a+d)+a$$
Add the two sums
$$2S_n=[2a+(n-1)d]+[2a+(n-1)d]+[2a+(n-1)d]+...+[2a+(n-1)d]$$
$$2S_n=n[2a+(n-1)d]$$
$$S_n=\frac{n}{2}[2a+(n-1)d]$$

\end{document}

### 2018-05-13 Maths Notes/Core/C1/C1.tex
Spelling fix

@@
 \section{Sequences and series}
-\subsection{Deriving the formula for the sub of an arithmetic series}
+\subsection{Deriving the formula for the sum of an arithmetic series}
 $$S_n=a+(a+d)+(a+2d)+...+(a+(n-1)d)$$

### 2018-05-19 Maths Notes/Statistics/S3/Cheat Sheet/S3 Cheat Sheet.tex
S3 Cheat Sheet

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - S3}

%File specific Preamble
\usepackage{enumitem} %Helps with lists in tables
\usepackage{pdfpages}
\usepackage{pdflscape}
\usepackage{setspace}
%File specific Preamble
\usepackage{multirow} %Merge cells in tables

\begin{document}
\begin{center}
\underline{\huge S3 Cheat Sheets}
\end{center}
\section{Combinations of random variables}
\subsection{Be able to combine two normally distributed variables}
$$E(X\pm Y)=E(X)\pm E(Y)$$
$$Var(X\pm Y)=Var(X)+Var(Y)$$
\textcolor{red}{Remember}
$$Var(2X)=2^2Var(X)$$
$$Var(X_1+X_2)=Var(X_1)+Var(X_2)=2Var(X)$$
None of this works for standard deviation, remember to square beforehand
\subsection{Be able to calculate $\mathbf{P(|X-Y|<k)}$ for some constant k}
$$P(|X-Y|<3)=P(-3<X-Y<3)=P(X-Y<3)-P(X-Y<-3)$$
\section{Sampling}
\subsection{Definitions}
Hypothesis - A statement concerning a population parameter\\ 
\\
Critical Region - The range of values that would lead to the rejection of $H_0$, and so the acceptance of $H_1$\\ 
\\
Statistic - A random variable, a function of known observations from a population, no unknown parameters\\ 
\\
Sampling unit - An individual unit of the population\\ 
\\
Sampling frame - A list of all sampling units\\ 
\\
Sampling distribution - All possible samples are chosen from the population\\ 
\\
Census - When every member of the population is investigated\\ 
\\
Hypothesis test - A mathematical procedure to examine a value of 
a population parameter proposed by the null hypothesis compared with an alternative hypothesis\\ 
\\
Population - A collection of all items\\ 
\\
Finite Population - One in which each individual member can be given a number\\ 
\\
Infinite population - One where it is impossible to number each individual member\\ 
\\
Significance level - The probability of incorrectly rejecting $H_0$\\ 
\\
Sample - A selection of items from a population\\

\includepdf[landscape=true]{Sampling2/Sampling2.pdf}
\newpage
\setcounter{subsection}{2}
\subsection{How to carry out samples}
\subsubsection{Simple random sampling}
\begin{itemize}
\item Allocate numbers to each member of the population
\item Use random number tables to select different numbers until enough have been selected
\item Members corresponding to the numbers become the sample
\end{itemize}
\subsubsection{Stratified sampling}
\begin{itemize}
\item Number the members in each strata
\item Use random numbers to select the members from each group
\item Number from each group in sample to be proportional to the number in the sample - calculate
\end{itemize}
\subsubsection{Systematic sampling}
\begin{itemize}
\item Randomly select first number between 1 and $Pop/sample$
\item Select every person at an interval of $Pop/sample$ after that
\end{itemize}
\subsubsection{Quota sampling}
\begin{itemize}
\item Non random sampling
\item Groups of the population
\end{itemize}
\section{Estimation, confidence intervals and tests}
\subsection{Know the definition of the central limit theorem}
\begin{itemize}
\item If $X_1,...,X_n$ is a random sample of size n, for large n
\item Drawn from the population of any distribution with mean $\mu$ and variance $\sigma^2$
\item The $\overline{X}$ is approximately $N(\mu,\frac{\sigma^2}{n})$
\end{itemize}
Most if this is under the sampling distributions header on the data sheet, just remember to include when n is large
\subsection{Know the definition of a statistic}
A random variable, a function of known observations from a population, no unknown parameters
\subsection{Understand what $\overline{X}$ is and find the distribution of $\overline{X}$}
$\overline{x}$ - Mean for a specific sample\\
$\overline{X}$  - A random variable allowing the sample mean to vary across different samples
$$\overline{X}\sim N\Bigg(\mu,\frac{\sigma^2}{n}\Bigg)$$
\textbf{Make sure when writing the distribution to use $\mu$, the population mean, rather than the sample mean}.
\subsection{Find value of n such that a value is in the confidence interval}
Use the formula:
$$\overline{X}\pm \times\frac{\sigma}{\sqrt{n}}$$
By setting this equal to a value, the value of n can be found such that the value will be in the confidence interval

\subsection{Find the minimum sample size required to have sufficient confidence that the sample mean lies in some range}
\textbf{Example}\\
$X\sim N(40,3^2)$. \textit{Find the minimum sample size such that the probability of the sample mean being greater than 42 is less than 5\%.}
$$\overline{X}\sim N\Bigg(40,\frac{9}{n}\Bigg)$$
$$P(\overline{X}>42)=P\Bigg(Z>\frac{42-40}{\frac{3}{\sqrt{n}}}\Bigg)$$
Find the C.V.
$$\frac{2}{\frac{3}{\sqrt{n}}}\geqslant1.6449\quad \Rightarrow n\geqslant6.087 \quad \therefore n=7$$
\subsection{Understand estimator notation}
$\hat{\mu}=\overline{x}$, anything with a hat on is an estimator
\subsection{Find the value of $S^2$}
$$S^2=\frac{\sum(X_i-\overline{X})^2}{n-1}$$
Replace the top of the fraction with $S_{xx}$
$$S^2=\frac{\sum x^2-\frac{(\sum x)^2}{n}}{n-1}$$
\subsection{Hypothesis test for the difference between means} 
When performing a hypothesis test for the difference between means, use the formula on the formula book:
$$\frac{(\overline{X}-\overline{Y})-(\mu_x-\mu_y)}{\sqrt{\frac{\sigma^2_x}{n_x}+\frac{\sigma^2_y}{n_y}}}$$
$H_0$ is always that the means are equal, or that they are equal with addition or subtraction to one\\
$H_1$ is always that one is greater, with the same addition or subtraction if stated in $H_0$
\subsection{State assumptions used to carry out a hypothesis test}
In general:
$$s^2=\sigma^2$$
Sample variance=Population variance
\subsection{Explain the relevance of the CLT}
It allows us to assume our means are normally distributed
\newpage
\section{Goodness of fit and Contingency tables}
\subsection{Goodness of fit method}
Method for testing goodness of fit:
\begin{enumerate}
\item Determine which distribution would conceptually be most appropriate
\item Set significance level
\item Estimate parameters (if necessary) from observed data
\item Form hypotheses $H_0$ and $H_1$
\item Calculate expected frequencies
\item Combine expected frequencies so that none are $<5$
\item Find degrees of freedom
\item Calculate critical value of $\chi^2$ from the table
\item Calculate $\sum\frac{(O_i-E_i)^2}{E_i}$
\item See if the value is significant and draw conclusion
\end{enumerate}
$X^2$ is distributed with a chi squared distribution $\chi^2_\nu$\\
Where $\nu=$ degrees of freedom\\
$$\textrm{The number of degrees of freedom}=\textrm{Number of classes (after combining)}-1$$
\\
$$\sum\frac{(O_i-E_i)^2}{E_i} \textrm{can be rewritten as  } \quad \Bigg(\sum\frac{O^2_i}{E_i}\Bigg)-N$$
$H_0$ is always that the distribution is a good model\\
$H_1$ is always that the distribution is not a good model
\subsubsection{Normal distribution}
When testing for a normal distribution the two ends of the table must extend to infinity to ensure that the probabilities add to 1
\subsubsection{Degrees of freedom}
The degrees of freedom starts as the number of columns, then 1 is subtracted from it for various reasons:
\begin{itemize}
\item Probabilities must add to 1 so one of the probabilities could be approximated
\item Approximation of p in binomial, or $\lambda$ in poisson when not given
\end{itemize}
\newpage
\subsection{Contingency tables}
\begin{itemize}
\item We use this test to see if two factors are independent of each other
\item We describe them by: Number of rows $\times$ Number of columns
\item $H_0$ is that they are independent
\item $H_1$ is that they are not independent
\item $$\textrm{Expected values}=\frac{\textrm{Row total}\times\textrm{Column total}}{\textrm{Grand total}}$$
\item $$\nu=(\textrm{Number of rows-1})(\textrm{Number of columns-1})$$
\item Remember that the same rule that expected frequencies cannot be less than 5 still applies
\end{itemize}
\section{Hypothesis tests for PMCC and Spearman's Rank Correlation Coefficient}
Spearman's rank - The tendency for y to increase as x increases\\
PMCC - How close x and y are to a linear relationship\\
\\
Spearman's rank is equivalent to PMCC if the data is ranked, this causes the data to adopt a linear relationship if y increases as x increases.\\
\\
The Spearman's rank formula does not work if there are tied ranks\\
\\
The critical values in the PMCC table assume that the data is jointly normally distributed, this is the assumption if asked for a hypothesis test. The spearman's rank distribution doesn't assume the data to be jointly normally distributed.\\
\\
$\rho$ is the population parameter which is the \textbf{actual} correlation between the variables.\\
$r$ and $r_s$ is the observed correlation based on the sample\\
\\
Hypothesis tests can be either one or two tailed, depending if you are just looking for a correlation or specifically a positive/negative correlation.
\newpage

\end{document}

### 2018-05-19 Maths Notes/Statistics/S3/Cheat Sheet/Sampling2/Sampling2.tex
S3 Cheat Sheet

--- 2018-01-27 Maths Notes/Statistics/S3/Sampling/Sampling.tex
@@
-\documentclass{article}[18pt]
+\documentclass{article}[5pt]
 \usepackage[utf8]{inputenc}
-\usepackage[margin=0.7in]{geometry}
+\usepackage[lmargin=0.1in,rmargin=0.1in,bmargin=0.1in,tmargin=0.6in,landscape,a4paper]{geometry}
 \usepackage{parselines} 
@@
 \usepackage{gensymb}
-\usepackage{relsize}
+\usepackage{pbox}
 \pgfplotsset{width=10cm,compat=1.9}
-\usepackage{enumitem}
+\usepackage{mathtools}
 \titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
@@
 \renewcommand{\indent}{\hspace*{\tindent}}
-\hyphenpenalty=10000
+\usepackage{relsize}
 \pagestyle{fancy}
@@
 \lhead{A Level Maths - S3}
-\rfoot{Page \thepage}
-
+\newcommand{\tabitem}{~~\llap{\textbullet}~~}
+\usepackage{tabularx}
+%File specific Preamble
+\usepackage{enumitem} %Helps with lists in tables
+\setitemize{noitemsep,topsep=-5pt,leftmargin=*}%Compress list
+\usepackage[none]{hyphenat}
 \begin{document}
-\begin{center}
-\underline{\huge Sampling}
-\end{center}
-\begin{tabularx}{\textwidth}{|c|X|X|X|}
+\setcounter{section}{2}
+\setcounter{subsection}{1}
+\subsection{Sampling}
+\begin{tabularx}{\textwidth}{|c|X|X|X|X|}
 \hline
-&What it is&Advantages&Disadvantages\\
+&What it is&When to use&Advantages&Disadvantages\\
 \hline
 Census&A collection of data from an entire population&Gives a completely accurate result&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
+\begin{itemize}
+\item Small population
+\item Easy to collect data
+\item Large variation of opinion
+\end{itemize}&
+
+\begin{itemize}
 \item Time consuming+Expensive
@@
 \hline
-Sample survey&A survey of a small sample of the population&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
-\item Cheaper
-\item Quicker
-\item Easier to process
+
+Random Sampling
+&Each thing has an equal chance of being selected&
+
+\begin{itemize}
+\item Large population
+\item Have a sampling frame
 \end{itemize}&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
-\item Data may not be accurate
-\item Data may not be large enough to represent small sub groups
-\end{itemize}\\
-\hline
-Random Sampling&Each thing has an equal chance of being selected&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
+
+\begin{itemize}
 \item Numbers truly random and free from bias
@@
 \end{itemize}&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
-\item Not suitable when population is large
+\begin{itemize}
+\item Needs a sampling frame
 \end{itemize}\\
 \hline
-Lottery sampling&Each element of a population put on a ticket. Tickets drawn randomly from container(without displacement)&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
-\item Tickets are drawn at random
-\item It is easy to use
-\item Each ticket has a known chance of selection
+
+Systematic sampling
+&Required elements are chosen at regular intervals in an ordered list&
+\begin{itemize}
+\item Time constraint
 \end{itemize}&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
-\item It is not suitable when the population is large
-\item A sampling frame is needed
-\end{itemize}\\
-\hline
-Systematic sampling&Required elements are chosen at regular intervals in an ordered list&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
+
+\begin{itemize}
 \item Simple to use
@@
 \end{itemize}&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
+\begin{itemize}
 \item Only random if ordered list is truly random
@@
 \hline
-Stratified sampling&Population is divided into groups and a simple random sample is carried out in each group&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
+
+Stratified sampling
+&Population is divided into groups and a simple random sample is carried out in each group&
+
+\begin{itemize}
+\item More accurate when strata are present
+\item Reflects population structure
+\end{itemize}&
+
+\begin{itemize}
 \item It can give more accurate estimates than simple random sampling where clear strata are present
@@
 \end{itemize}&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
+\begin{itemize}
 \item Within the strata, the problems are than same as for any simple random sample
@@
 \hline
-Quota sampling&The population is divided into groups by gender etc. A quota of people in each group is set to try and reflect the group's proportion in the whole population&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
+
+Quota sampling
+&The population is divided into groups by gender etc. A quota of people in each group is set to try and reflect the group's proportion in the whole population&
+\begin{itemize}
+\item There is no sampling frame
+\end{itemize}&
+
+\begin{itemize}
 \item Enables fieldwork to be done quickly because a small sample size is taken.
@@
 \end{itemize}&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
+\begin{itemize}
 \item Not possible to estimate the sampling errors
@@
 \end{tabularx}
-\newpage
-\begin{center}
-\underline{\huge Types of data}
-\end{center}
-\begin{tabularx}{\textwidth}{|c|X|X|}
-\hline
-Type of data&Advantages&Disadvantages\\
-\hline
-Primary&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
-\item The collection method is known
-\item The accuracy is known
-\item The exact data needed is collected
-\end{itemize}&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
-\item It is costly in time and effort
-\end{itemize}\\
-\hline
-Secondary&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
-\item They are cheap to obtain
-\item A large quantity of data is available
-\item Much of the data has been collected for years and can be used to plot trends
-\end{itemize}&
-\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
-\item Bias is not always recognised
-\item It can be in a form that is difficult to deal with
-\end{itemize}\\
-\hline
-
-\end{tabularx}
 

### 2018-05-21 Maths Notes/Core/C1/C1.tex
Recurrence relation C1

@@
 $$S_n=\frac{n}{2}[2a+(n-1)d]$$
+\subsection{Forming a recurrence relation}
+To create a recurrence relation formula from a formula given in n, substitute n+1 in place of n and rearrange.\\
+\textbf{Example}
+$$U_n=2^n+4n$$
+$$U_{n+1}=2^{n+1}+4{n+1}$$
+$$U_{n+1}=2U_n-4n+4$$
+\subsection{Finding a and d}
+Remember that the formula for the $\textrm{n}^\textrm{th}$ term may not be given in the form $a+(n-1)d$, and if it is not, it must be changed.\\
+\textbf{Example}\\
+$u_r=4r-7$\\
+$u_1=4-7=-3=a$\\
+$4r-7=-3+(r-1)d \quad \Rightarrow 4r-4=(r-1)d \quad \Rightarrow d=4$
+\subsection{Finding the nth term from a recurrence relation}
+To find the nth term, use a standard form, deducted from what is happening to the previous term.\\
+\textbf{Example}\\
+$U_{n+1}=2U_n-5$\\
+The multiplier by 2 implies doubling, and so the nth term will contain $A\times2^n$, the subtraction of 5 suggests there will also be a constant term, $B$.\\
+$$U_n=A\times2^n+B$$
+Given $U_1=6$, A and B can be found to be $\frac{1}{2}$ and 5.
 

### 2018-05-21 Maths Notes/Statistics/S3/Cheat Sheet/S3 Cheat Sheet.tex

@@
 When testing for a normal distribution the two ends of the table must extend to infinity to ensure that the probabilities add to 1
+\subsubsection{Continuous uniform distribution}
+Remember when testing for a uniform distribution to state that it is a \textbf{continuous} uniform distribution
 \subsubsection{Degrees of freedom}
@@
 \end{itemize}
+Contingency tables and PMCC tests both look for linear relationships, however a contingency table looks to see if the data lies on the line $y=x$, whereas the PMCC looks to see if the data lies on the line $y=kx$
+
 \section{Hypothesis tests for PMCC and Spearman's Rank Correlation Coefficient}
@@
 \newpage
+\begin{center}
+\underline{\huge Hypothesis tests}
+\end{center}
+\begin{tabularx}{\textwidth}{|X|X|X|}
+\hline
+\textbf{What is being tested}&$\mathbf{H_0}$&$\mathbf{H_1}$\\
+\hline
+Difference between means&$\mu_a=\mu_b$&$H_1:\mu_a>\mu_b \ \textrm{or} \ 
+\mu_a<\mu_b \  \textrm{or} \ 
+\mu_a\neq\mu_b$\\
+\hline
+Goodness of fit&A \underline{\hspace{1cm}} Distribution is a suitable model&A \underline{\hspace{1cm}} Distribution is not a suitable model\\
+\hline
+Contingency Tables&No association between the two data sets&Association between the two data sets\\
+\hline
+Spearman's rank&$\rho_s=0$&$\rho_s>0,\rho_s<0,\rho_s\neq0$\\
+\hline
+PMCC&$\rho=0$&$\rho>0,\rho<0,\rho\neq0$\\
+\hline
+\end{tabularx}
+\begin{center}
+\underline{\huge Tables}
+\end{center}
+\setcounter{section}{6}
+\subsection{Goodness of fit}
+{\renewcommand{\arraystretch}{2}
+\begin{tabularx}{\textwidth}{|X|X|X|}
+\hline
+Number&&\\
+\hline
+Observed&&\\
+\hline
+Expected&&\\
+\hline
+$\dfrac{(O-E)^2}{E}$&&\\
+\hline
+\end{tabularx}}
+\subsection{Contingency tables}
+{\renewcommand{\arraystretch}{2}
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|}
+\hline
+&\multicolumn{3}{|c|}{\centering C}&\multicolumn{3}{|c|}{\centering D}\\
+\cline{2-7}
+&O&E&$\frac{(O-E)^2}{E}$&O&E&$\frac{(O-E)^2}{E}$\\
+\hline
+A&&&&&&\\
+\hline
+B&&&&&&\\
+\hline
+\end{tabularx}}
+\subsection{Difference between means}
+{\renewcommand{\arraystretch}{2}
+\begin{tabularx}{\textwidth}{|X|X|X|}
+\hline
+&A&B\\
+\hline
+$\overline{x}$&&\\
+\hline
+$s^2$&&\\
+\hline
+n&&\\
+\hline
+\end{tabularx}
+\subsection{Spearman's rank}
+\begin{tabularx}{\textwidth}{|X|X|X|X|}
+\hline
+&A&B&C\\
+\hline
+Rank 1&&&\\
+\hline
+Rank 2&&&\\
+\hline
+$d^2$&&&\\
+\hline
+
+\end{tabularx}
 

### 2018-05-21 Test/Definitions/Definitions.tex
Update of all files to shorten preamble
Tidied to work with all linux systems

--- 2018-04-06 Maths Notes/Statistics/S3/Definitions/Definitions.tex
@@
-\documentclass{article}[18pt]
-\usepackage{/home/sam/Documents/School_Notes/format}
-\lhead{A Level Maths - S3}
+\documentclass{article}
+\usepackage[a4paper,hmargin=3cm,vmargin=5cm]{geometry}
+\usepackage{pdflscape,lipsum,graphicx}
+\usepackage[absolute]{textpos}
+\usepackage{fancyhdr}
+\usepackage{afterpage}
 
 \begin{document}
-\begin{center}
-\underline{\huge Definitions}
-\end{center}
-\large
-Hypothesis - A statement concerning a population parameter\\
-Critical Region - The range of values that would lead to the rejection of $H_0$, and so the acceptance of $H_1$\\
-Statistic - A random variable, a function of known observations from a population, no unknown parameters\\
-Sampling unit - An individual unit of the population\\
-Sampling frame - A list of all sampling units\\
-Sampling distribution - All possible samples are chosen from the population\\
-Census - When every member of the population is investigated\\
-Hypothesis test - A mathematical procedure to examine a value of
-a population parameter proposed by the null hypothesis compared with an alternative hypothesis\\
-Population - A collection of all items\\
-Finite Population - One in which each individual member can be given a number\\
-Infinite population - One where it is impossible to number each individual member\\
-Significance level - The probability of incorrectly rejecting $H_0$\\
-Sample - A selection of items from a population\\
+Test
+\newpage
 
+\newgeometry{landscape}     % use whatever margins you want for left, right, top and bottom.
+...
+... %<The contents of enlarged page(s)>
+...    
+\restoregeometry     %so it does not affect the rest of the pages.
 \end{document}

### 2018-05-21 Maths Notes/Statistics/S3/Cheat Sheet/S3 Cheat Sheet.tex
Distribution update to include discrete

@@
 When testing for a normal distribution the two ends of the table must extend to infinity to ensure that the probabilities add to 1
-\subsubsection{Continuous uniform distribution}
-Remember when testing for a uniform distribution to state that it is a \textbf{continuous} uniform distribution
+\subsubsection{Uniform distributions}
+It is necessary to state the type of uniform distribution:
+\begin{itemize}
+\item \textbf{Continuous} - Can take any of the values over the range
+\item \textbf{Discrete} - Can only take specific values over the range (for example odd numbers)
+\end{itemize}
 \subsubsection{Degrees of freedom}

### 2018-05-22 Maths Notes/Statistics/S3/Cheat Sheet/S3 Cheat Sheet.tex
Notes update

@@
 \begin{itemize}
-\item Non random sampling
-\item Groups of the population
+\item Divide population into distinct groups
+\item Sample sizes in proportion with population
+\item Sample any member of group until quota is filled
 \end{itemize}
@@
 \newpage
+\section{Conditions for distributions}
+\subsection{Normal Distribution}
+\begin{itemize}
+\item Probabilities symmetrical about the mean
+\end{itemize}
+\subsection{Binomial distribution}
+\begin{itemize}
+\item Fixed number of trials
+\item Two outcomes
+\item Independent trials
+\item Constant probability of success 
+\end{itemize}
+\subsection{Poisson distribution}
+\begin{itemize}
+\item Events occur at random
+\item Independent events
+\item Constant rate of occurrence
+\item No simultaneous events
+\end{itemize}
+\subsection{Uniform distribution}
+\begin{itemize}
+\item All outcomes have the same probability
+\end{itemize}
+$ $\\
+$ $\\
+\begin{center}
+\underline{\huge Things to look out for}
+\end{center}
+\begin{itemize}
+\item Being given standard deviation when you expect variance
+\item In Chi-Squared tests $H_0$ is what would happen if the expected and observed values were exactly the same
+\item When calculating confidence intervals, the z value should be from half the excluded percentage
+\item When doing goodness of fit on a uniform distribution, check the class widths
+\item Don't just round values of n, look at the inequalities 
+\item When it says differ, it could be either way, absolute value
+\item Actually state your hypotheses 
+\end{itemize}
+
+\newpage
 \begin{center}
@@
 \end{tabularx}
-
 \end{document}

### 2018-05-27 Maths Notes/Core/C4/Cheat Sheet/C4 Cheat Sheet.tex
Notes update

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - C4}

%File specific Preamble
\usepackage{polynom} %Provides long division

\begin{document}
\begin{center}
\underline{\huge C4 Cheat Sheet}
\end{center}
\section{Partial fractions}
\subsection{Split a fraction whose denominator is a product of linear expressions}
Set the fraction equal to the sum of constants over each linear expression, then multiply by the denominator and solve by substitution.
\subsection{Split a fraction where one or more of the factors in the denominator are squared}
Each squared term gets two terms in the summation, one of the non squared term, and one of the squared term.
\subsection{Deal with top heavy fractions}
Use long division to simplify, for example simplifying $\dfrac{3x^2-3x-2}{(x-1)(x-2)}$\\
\textbf{Long division to find remainder}\\
$\polylongdiv{3x^2-3x-2}{x^2-3x+2}$\\
\\
\textbf{Re-write with remainder}\\
\\
$3+\dfrac{6x-8}{(x-1)(x-2)}$\\
\textbf{Partial fractions can then be applied normally}
\section{Parametric equations}

\end{document}

### 2018-05-27 Maths Notes/Further Pure/FP2/Overall Notes/FP2 Notes.tex
Notes update

--- 2018-04-17 Maths Notes/Further Pure/FP2/Overall Notes/FP2 Notes.tex
@@
 \lhead{A Level Maths - FP2}
-
+\usepackage{tabularx}
 \begin{document}
 \begin{center}
-\underline{\huge FP2}
+\underline{\huge FP2 Cheat Sheet}
 \end{center}
-\section{First order differential equations}
-\subsection{Solving first order DE using an integrating factor}
-Solving $\dfrac{dy}{dx}+P(x)y=Q(x)$\\
+\section{Inequalities}
+We can build upon our previous algebraic skills in order to solve more complex inequalities\\
+Remember:
+\begin{itemize}
+\item Don't multiply anything that could be negative - use "squared" things
+\item Try to avoid fully expanding where possible
+\item Find the critical values (f(x)=0)
+\item Sketch the graph to solve
+\end{itemize}
+\section{Series}
+Summations can sometimes be simplified using the method of differences\\
 \\
-IF(Integrating factor) is found by finding $\mathlarger{e^{\int p(x) \ dx}}$ And multiplying the DE by the IF.\\
-\\
-This will result in the DE being in the form:
-$$f(x)\frac{dy}{dx}+f'(x)y$$
-This form can then be shortened by integrating:
-$$\int f'(x)g(x)+f(x)g'(x) dx=f(x)g(x)+c$$
-Integrate both sides then simplify
+This involves a summation where one term is subtracted from another, often gained from partial fractions.
+The terms in the middle of the series will then cancel with each other, leaving the summation just the terms at the beginning at the end, by summing these a simpler form can be gained.
 \section{Further complex numbers}
@@
 \subsection{De Moivre's theorem}
-This is given on the data sheet
+This is given on the data sheet and has multiple applications
 \subsubsection{Z formulas}
@@
 $$z^n-\frac{1}{z^n}=2i\sin n\theta$$
+\subsubsection{Roots of unity}
+
+\subsection{Solving complex equations}
+When solving $z^a=r(\cos(\theta)+i\sin(\theta))$ type questions, remember to first rewrite as:
+$$z^a=r(\cos(\theta+2k\pi)+i\sin(\theta+2k\pi))$$
+
 \subsection{Loci on the complex plane}
@@
 \end{itemize}
-\section{Inequalities}
-We can build upon our previous algebraic skills in order to solve more complex inequalities\\
-Remember:
-\begin{itemize}
-\item Don't multiply anything that could be negative - use "squared" things
-\item Find the critical values (f(x)=0)
-\item Sketch the graph to solve
-\end{itemize}
+
+\section{First order differential equations}
+\subsection{Solving first order DE using an integrating factor}
+Solving $\dfrac{dy}{dx}+P(x)y=Q(x)$\\
+\\
+IF(Integrating factor) is found by finding $\mathlarger{e^{\int p(x) \ dx}}$ And multiplying the DE by the IF.\\
+\\
+This will result in the DE being in the form:
+$$f(x)\frac{dy}{dx}+f'(x)y$$
+This form can then be shortened by integrating:
+$$\int f'(x)g(x)+f(x)g'(x) dx=f(x)g(x)+c$$
+Integrate both sides then simplify
+
 \section{Maclaurin and Taylor Series}
@@
 Then substitute those values into the Taylor series to solve the differential equation
+\section{Polar Coordinates}
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+Equation&Description\\
+\hline
+$r=a$&A circle, centre (0,0) with a radius of a\\
+\hline
+$\theta=\alpha$&A half line starting from (0,0) making an angle $\alpha$ with the initial line\\
+\hline
+$r=a\theta$&A spiral starting at the origin\\
+\hline
+$r=a(1+\cos\theta)$&A cardioid with x intercept a\\
+\hline
+$r^2=a^2\cos2\theta$&An infinity symbol with x intercept of a\\
+\hline
+$r^2=a^2\sin2\theta$&Infinity symbol rotated by $\frac{\pi}{4}$\\
+\hline
+$r=a\sin3\theta$&A windmill with 3 blades\\
+\hline
+\end{tabularx}
+\subsection{Integration}
+$$\textrm{Area}=\frac{1}{2}\int_\alpha^\beta r^2 \ d\theta$$
+The area of the sector is bounded by the half lines $\theta=\alpha$ and $\theta=\beta$
+\subsection{Differentiation}
+To find tangents parallel and perpendicular to the initial line:\\
+\\
+Parallel: $\frac{dy}{d\theta}=0$\\
+Perpendicular: $\frac{dx}{d\theta}=0$
+\section{Second order differential equations}
+{\renewcommand{\arraystretch}{2}
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+\textbf{Solution to auxiliary equation}&\textbf{General solution}\\
+\hline
+Two real roots $b^2>4ac$&$Ae^{\alpha x}+Be^{\beta x}$\\
+\hline
+One real root $b^2=4ac$&$(A+bx)e^{\alpha x}$\\
+\hline
+Imaginary only root $b^2<4ac$&$y=Ae^{\alpha x}+Be^{-\alpha x}$\\
+\hline
+Complex root $b^2<4ac$&$y=Ae^{(\beta+\alpha i)x}+Be^{(\beta-\alpha i)x}$\\
+\hline
+\end{tabularx}}
+\subsection{Second ODE=f(x)}
+\subsubsection{Standard forms of f(x)}
+$f(x)=\lambda$\\
+$f(x)=\lambda+\mu x$\\
+$f(x)=\lambda+\mu x+\nu x^2$\\
+$f(x)=ke^{px}$\\
+$f(x)=m\cos\omega x$\\
+$f(x)=m\sin\omega x$\\
+$f(x)=m\cos\omega x\pm n\sin\omega x$
+\\
+To solve these find $\frac{dy}{dx}$ and $\frac{d^2y}{dx^2}$ and substitute them into the Second ODE, solving for the unknowns, then add them to the general solution.\\
+\\
+If there is a clash of terms between the CF and PI, then an alternate PI will be given to you.
+\subsection{Boundary conditions}
+If boundary conditions are given to you, the values of the unknowns can be found. Substitute the boundary conditions in and rearrange to find unknowns.
+\newpage
+\subsection{Substitution}
+Transformations can be used to simplify differential equations, leaving $\frac{d^2y}{dx^2}$ with no coefficient.\\
+Method:\\
+\textcolor{red}{\large Find $\frac{dy}{dx}$ in terms of $\frac{dy}{du}$}
+$$x=e^u \quad \frac{dx}{du}=e^u \quad \frac{du}{dx}=e^{-u} \quad 
+\frac{dy}{dx}=\frac{dy}{du}\times\frac{du}{dx}=\mathbf{e^{-u}\frac{dy}{du}}
+$$
+\textcolor{red}{\large Find $\frac{d^2y}{dx^2}$ in terms of $\frac{d^2y}{du^2}$ and $\frac{dy}{du}$}\\
+\textcolor{red}{Find $\frac{dy}{du}\Big(\frac{dy}{dx}\Big)$ by applying the product rule}
+$$\frac{dy}{du}\Big(\frac{dy}{dx}\Big)=-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}$$
+\textcolor{red}{Multiply through by $\frac{du}{dx}$ to find the value of $\frac{d^2y}{dx^2}$}
+$$\frac{d^2y}{dx^2}=\frac{dy}{du}\Big(\frac{dy}{dx}\Big)\times\frac{du}{dx}$$
+$$\frac{d^2y}{dx^2}=e^{-u}\Big(-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}\Big)$$
+$$\frac{d^2y}{dx^2}=\mathbf{e^{-2u}\Big(-\frac{dy}{du}+\frac{d^2y}{du^2}\Big)}$$
 

### 2018-05-27 Maths Notes/Statistics/S2/Cheat Sheet/S2 Cheat Sheet.tex
Notes update

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - S2}
\usepackage{enumitem} %Helps with lists in tables
\setitemize{noitemsep,topsep=-5pt,leftmargin=*}%Compress list

\begin{document}
\begin{center}
\underline{\huge S2 Cheat Sheet}
\end{center}
\section{Binomial and Poisson}
\subsection{Be able to list the assumptions}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
Binomial&Poisson\\
\hline
\begin{itemize}
\item Fixed number of trials
\item Probability of success constant
\item Each trial is independent
\item Each trial has two outcomes
\end{itemize}&
\begin{itemize}
\item Events occur independently
\item No simultaneous events
\item A fixed rate at which events occur
\end{itemize}\\
\hline
\end{tabularx}
\subsection{Geometric distribution questions - Binomial}
Where $X$ is the distribution for the number of successes and Y is the distribution for the number of failures, and n is taken from the distribution
$$P(X<k)=P(Y>n-k)$$
$$P(X\geqslant k)=P(Y\leqslant n-k)$$
\subsection{Finding an unknown n or p from a context}
Set up the probability described in terms of the binomial distribution formula, then solve.\\
\textbf{Example}\\
\textit{I play a game for which the probability of winning is 0.7. If I win every game, what is the smallest number of times I play such that the probability of winning every game is less than 0.01?}\\
$$P(X=n)=0.7^n<0.01$$
$$n\log(0.7)<\log(0.01)$$
$$n>\frac{\log(0.01)}{\log(0.7)}=12.9$$
At least 13 games
\subsection{Solving double inequalities}
\textit{Given $X\sim B(50,0.6)$ find the smallest value of k such that $P(X<k)\geqslant0.9$}
$$X\sim B(50,0.6) \quad Y\sim B(50,0.4)$$
$$P(X<k)=P(Y>50-k)\geqslant0.9$$
$$1-P(Y\leqslant 50-k)\geqslant 0.9$$
$$P(Y\leqslant50-k)\leqslant0.1$$
$$50-k\leqslant15$$
$$k\geqslant35 \therefore k=35$$
\newpage
\subsection{Feeding a poisson into a binomial}
Sometimes the probability calculated by possion can then be fed into binomial for a further calculation, for example:\\
\textit{Defects occur at a rate of 0.5 per 10cm. If bob boys 6 planks each of length 100cm, find the probability fewer than 2 planks contain at most 3 defects}
$$X\sim P_o(5) \quad P(X\leqslant3)=0.2560$$
$$Y\sim B(6,0.256) \quad P(Y<2)=0.4987$$
\section{Continuous random variables}
\subsection{Find the probability of a range of values}
$$P(a<X<b)=\int^b_a f(x) \ dx$$
$$P(X>a)=\int^\infty_a f(x) \ dx$$
For the second term, the probability will become zero after a certain value of x, use this as the upper limit
\subsection{Point probabilities}
The probability at any given value of x for a continuous random variable is zero
\subsection{State the PDF given a graph}
The PDF from a graph is the equations of the lines over the range, but it is important to include the statement that the probability is zero otherwise, for example\\
$
  f(x)=\left\{
  \begin{array}{@{}ll@{}}
    \frac{1}{2}(x-3), & \text{for}\ 3\leq x \leq 5  \\
    0, & \text{otherwise}
  \end{array}\right.
$
\subsection{Calculate measures of location and spread}
Mean and variance and $E(X^2)$ are given on the formula book.\\
To calculate quartiles/deciles set $F(x)$ equal to the location through the distribution and solve. For example the first quartile would be found using $F(x)=0.25$ and the third quartile would be found using $F(x)=0.75$.\\
The mode can be found either graphically or where $f'(x)=0$, making sure that $f''(x)<0$
\subsection{Converting between f(x) and F(x)}
To find $F(x)$, integrate f(x), the +c should be used to make sure that the start of the next range is equal to the previous range
\subsection{Finding greater than probabilities}
As the probability of any given value:
$$P(X\geqslant10)=1-P(X\leqslant10)$$
Unlike for discrete distributions
\newpage
\section{Continuous uniform distribution}
\subsection{Proof of formulas on the data sheet}
\subsubsection{Mean}
$f(x)=\frac{1}{b-a}$
$$E(x)=\frac{1}{b-a}\int_a^bx \ dx=\frac{1}{b-a}\times\frac{1}{2}\Big[x^2\Big]^b_a=\frac{b^2-a^2}{2(b-a)}=\frac{(b-a)(b+a)}{2(b-a)}=\frac{1}{2}(a+b)$$
\subsubsection{Variance}
$f(x)=\frac{1}{b-a}$
$$E(x^2)=\frac{1}{b-a}\int_a^bx^2 \ dx=\frac{1}{b-a}\times\frac{1}{3}\Big[x^3\Big]^b_a=\frac{b^3-a^3}{3(b-a)}=\frac{(b-a)(a^2+ab+b^2)}{3(b-a)}=\frac{a^2+ab+b^2}{3}$$
$$Var(x)=E(x^2)-(E(x))^2$$
$$Var(x)=\frac{a^2+ab+b^2}{3}-\frac{(a+b)^2}{4}=\frac{4a^2+4ab+4b^2}{12}-\frac{3a^2+6ab+3b^2}{12}=\frac{a^2-2ab+b^2}{12}=\frac{(b-a)^2}{12}$$
\subsection{Finding probability over a range}
When finding the probability over a range, multiply the PDF by the width, but remember to check that the range does not extend beyond the range of the distribution, if so, multiply by the width that overlaps with the distribution.
\section{Approximations}
\begin{center}
\includegraphics[width=10cm]{approx.png}
\end{center}
All the values for approximation are given on the formula book
\subsection{Continuity correction}
Continuity correction is required when converting from a discrete to a continuous distribution.\\
Method:
\begin{itemize}
\item Make sure the inequality uses $\geqslant$ or $\leqslant$
\item "Extend" the range by 0.5 at each end
\end{itemize}
\newpage
\subsection{Method for a normal approximation}
\begin{enumerate}
\item Determine the correct approximation to use
\item Identify the original distribution
\item Write the approximation
\item Carry out continuity correction
\item Find the probability
\end{enumerate}
\section{Population and samples}
\subsection{Definitions}
\begin{itemize}
\item \textbf{Statistic} - A random variable which is some function of the sample and not dependent on any population parameters
\item \textbf{Population} - A collection of all items
\item \textbf{Sample} - Some subset of the population which is intended to be representative of the population
\item \textbf{Census} - When the entire population is samples
\item \textbf{Sampling unit} - Individual member or element of the population or sampling frame
\item \textbf{Sampling frame} - A list of all sampling units or all the population
\item \textbf{Sampling distribution} - All possible samples that are chosen from a population, the values of a statistic and the associated probabilities.
\end{itemize}

\end{document}

### 2018-05-28 Physics Notes/Paper 1/Paper 1.tex
Notes update

\documentclass[12pt]{article}
\usepackage{../../format}
\lhead{A Level Physics}

\begin{document}
\begin{center}
\underline{\huge Paper 1 Cheat Sheet}
\end{center}
\section{Measurements and their errors}
\textbf{Precision} - There is very little spread around the mean value\\
\textbf{Repeatability} - If the same experimenter repeats the investigation using the same method and equipment and obtains the same results\\
\textbf{Reproducibility} - If a different experimenter repeats the investigation, or uses a different experiment or technique, the same results are obtained\\
\textbf{Accuracy} - Close to the true value\\
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
Combination&Operation\\
\hline
Adding or subtracting\newline $a=b+c$&Add the absolute uncertainties\newline $\Delta a=\Delta b+\Delta c$\\
\hline
Multiplying values\newline $a=b\times c$&Add the percentage uncertainties\newline $\epsilon a=\epsilon b+\epsilon c$\\
\hline
Dividing values\newline $a=\dfrac{b}{c}$&Add the percentage uncertainties\newline $\epsilon a=\epsilon b+\epsilon c$\\
\hline
Power rules\newline $a=b^c$&Multiply the percentage uncertainty by the power\newline $\epsilon a=c\times\epsilon b$\\
\hline
\end{tabularx}}
\newpage
\section{Particles and radiation}
\subsection{Constituents of the atom}
Protons and neurons in the centre, with shells of electrons around them
$$\textrm{Specific charge}=\frac{Q}{m}$$
\textbf{Isotope} - An atom with the same number of protons and electrons as an element, but a different number of neutrons
\subsection{Stable and unstable nuclei}
\subsubsection{The strong nuclear force}
\begin{tabular}{|c|c|}
\hline
$<0.5fm$&Repulsion\\
\hline
$0.5-3fm$&Attraction\\
\hline
$3fm+$&No force\\
\hline
\end{tabular}
\subsubsection{Alpha decay}
{\large
$$^A_ZX\rightarrow ^{A-4}_{Z-2}Y+^4_2\alpha$$
\subsubsection{Beta decay}
$$^A_ZX\rightarrow ^A_{Z+1}+^0_{-1}\beta+\overline{\nu}$$}
Neutrinos were hypothesised to allow for energy to be conserved in the interaction
\subsection{Particles, antiparticles and photons}

\end{document}

### 2018-05-28 Physics Notes/Paper 2/Paper 2.tex
Notes update

\documentclass[12pt]{article}
\usepackage{../../format}
\lhead{A Level Physics}
\usepackage{enumitem}
\setcounter{secnumdepth}{4}
\begin{document}
\begin{center}
\underline{\huge Paper 2 Cheat Sheet}
\end{center}
\section{Thermal physics}
\subsection{Thermal energy transfer}
\textbf{Specific heat capacity} - The energy required to raise the temperature of a unit mass of a given substance by one degree\\
\textbf{Specific latent heat}  - The energy required to change the state of a material without changing the temperature\\
\textbf{Temperature} - The average kinetic energy of the atoms or molecules in the system\\
\textbf{Heat} - Energy transfer due to a difference in temperature
\subsubsection{Continuous flow}
By dividing the specific heat capacity formula by t it can be found that
$$IV=mc\frac{\Delta T}{t}$$
This gives the power per second, where a mass $m$ flows in a time $t$
\subsection{Ideal gases}
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
Law&Proportionality&Constant&Equation\\
\hline
Boyle's&$p\propto\dfrac{1}{v}$&Temperature, moles&$p_1v_1=p_2v_2$\\
\hline
Charles'&$V\propto T$&Pressure, moles&$\dfrac{v_1}{T_1}=\dfrac{v_2}{T_2}$\\
\hline
Gay-Lussac&$p\propto T$&Volume, moles&$\dfrac{p_1}{T_1}=\dfrac{p_2}{T_2}$\\
\hline
\end{tabularx}}
The two formulas on the formula book for the gas laws have $n$ moles and $N$ molecules
\subsubsection{Deriving Pressure volume work formula}
$$W=FS=F\times\Delta L=\frac{F}{A}\times A\Delta L=P\Delta V$$
\subsubsection{Types of masses}
\textbf{Molar mass} - The mass of a mole of a substance\\
\textbf{Molecular mass} - The mass of the molecules
\newpage
\subsection{Molecular kinetic theory model}
\subsubsection{Brownian motion as evidence for the existence of atoms}
\textbf{Brownian motion} - The random motion of smoke particles in a gas\\
As Newton's first law states that objects remain in motion until acted on by a force, the smoke particles should remain in motion, instead they move randomly, suggesting collisions with something else
\subsubsection{Explanation of relationships between p,V and T}
Increase pressure - More collisions, increase temperature. Same number of molecules, volume must decrease
\subsubsection{Empirical gas laws but theoretical kinetic theory}
By changing variables of a gas, the gas laws can be derived, however the kinetic theory is based on what else would be expected to be required to be constant.
\subsubsection{Derivation}
\textcolor{red}{Newton's $3^{\text{rd}}$ law - Every action has an equal and opposite reaction}\\
$\Delta mc=mc_{x1}--mc_{x1}=2mc_{x1}$\\
\\
\textcolor{red}{Use $\text{Velocity}=\dfrac{\text{Distance}}{\text{Time}}$}\\
Time=$\dfrac{\text{Distance}}{\text{Velocity}}=\dfrac{2l}{c_{x1}}$\\
\\
\textcolor{red}{Use force$=\dfrac{\text{Change in momentum}}{\text{time}}$}\\
$\text{Force}=\dfrac{\Delta mc}{\Delta t}=\dfrac{2mc{x1}}{2l/c_{x1}}=\dfrac{mc_{x1}^2}{l}$\\
\\
\textcolor{red}{Use Pressure$=\dfrac{\text{Force}}{\text{Area}}$}\\
\\
$p_1=\dfrac{mc_{x1}^2/l}{l^2}=\dfrac{mc_{x1}^2}{l^3}$\\
\\
\textcolor{red}{Expand for N particles}\\
$p=\Sigma p_n=p_1+p_2+p_3...+p_N$\\
\\
$p=\dfrac{mc_{x1}^2}{l^3}+\dfrac{mc_{x2}^2}{l^3}+\dfrac{mc_{x3}^2}{l^3}+\dfrac{mc_{xN}^2}{l^3}$\\
\\
$p=\dfrac{m}{l^3}(c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2)$\\
\\
\textcolor{red}{The mean of all the squares of the velocities is written as $\mathlarger{\bar{c_x^2}}$}\\
\\
$\mathlarger{\bar{c_x^2}}=\dfrac{c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2}{N}$\\
\\
$N\mathlarger{\bar{c_x^2}}=c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2$\\
\\
\\
\textcolor{red}{Simplify expression for pressure}\\
$p=\dfrac{Nm\mathlarger{\bar{c_x^2}}}{l^3}$\\
\\
\textcolor{red}{Consider in 3 dimensions}\\
\\
$\mathlarger{\bar{c^2}=\bar{c_x^2}+\bar{c_y^2}+\bar{c_z^2}}$\\
\textcolor{red}{Average of mean square velocity for each dimension are equal}\\
\\
$\mathlarger{\bar{c_x^2}=\bar{c_y^2}=\bar{c_z^2}}$\\
\textcolor{red}{Simplify 3D formula}\\
\\
$\mathlarger{\dfrac{\bar{c^2}}{3}=\bar{c_x^2}=\bar{c_y^2}=\bar{c_z^2}}$\\
\\
\textcolor{red}{Simplify pressure formula}\\
\\
$p=\dfrac{1}{3}\times\dfrac{Nm\mathlarger{\bar{c^2}}}{l^3}$\\
\\
\textcolor{red}{Insert Density formula}\\
\\
$\rho=\dfrac{\text{Mass}}{\text{Volume}}=\dfrac{Nm}{l^3}$
\\
\textcolor{red}{Substitute into Pressure formula}\\
$$p=\frac{1}{3}\rho\mathlarger{\bar{c^2}}$$
\section{Fields and their consequences}
\subsection{Fields}
Similarities and differences between gravitational and electrostatic forces\\
\setitemize{noitemsep,topsep=-5pt,leftmargin=*}%Compress list
\begin{tabularx}{\textwidth}{|X|X|}
\hline
Similarities&Differences\\
\hline
\begin{itemize}
\item Inverse square laws
\item Use of field lines
\item Use of potential
\item Use of equipotentials
\end{itemize}& Masses always attract, but charges may attract or repel\\
\hline
\end{tabularx}
\newpage
\subsection{Gravitational fields}
\subsubsection{Gravitational field strength}
\includegraphics[width=8cm]{gravity.jpg}
\subsubsection{Gravitational potential}
Gravitational potential has a value of 0 at infinity, then reduces as it approaches the planet.\\
\textbf{Gravitational potential} - The work done in moving a unit mass from infinity to that point int he field\\
\textbf{Gravitational potential difference} - The work done in moving a unit mass from one point to another \\
\textbf{Equipotential} - The group of points with the same potential energy\\
\\
The sign is negative because a negative amount of work has to be done to move the object from infinity to earth because the object is attracted to earth.
\subsubsection{Orbits of planets and satellites}
\paragraph{Kepler's law}
$$F=\frac{GMm}{r^2}=\frac{mv^2}{r}\quad \therefore \frac{GM}{r}=v^2$$
$$v=\frac{s}{t}=\frac{2\pi r}{T}$$
$$v^2=\frac{4\pi^2r^2}{T^2}=\frac{GM}{r}$$
$$\frac{r^2}{T^2}=\frac{GM}{4\pi^2}$$
RHS is a constant
$$r^2\propto T^2$$
\paragraph{Escape velocity}
$$\frac{1}{2}mv^2=\frac{GMm}{r}\quad \therefore v=\sqrt{\frac{2GM}{r}}$$
$$g=\frac{GM}{r^2}\quad \therefore gr=\frac{GM}{r}$$
$$v=\sqrt{2gr}$$
\paragraph{Total energy of an orbiting satellite}
$$\textrm{Total energy=KE+GPE}$$
$$KE=\frac{1}{2}mv^2$$

\end{document}

### 2018-05-29 Physics Notes/Paper 2/Paper 2.tex
Physics Paper 2 Notes

@@
 $$KE=\frac{1}{2}mv^2$$
+$$\frac{GM}{r^2}=\frac{v^2}{r}\quad \therefore v^2=\frac{GM}{r}$$
+$$KE=\frac{1}{2}m\frac{GM}{r}$$
+$$GPE=mV \quad	V=-\frac{GM}{r} \quad \therefore E_p=-\frac{GMm}{r}$$
+$$E_T=E_K+E_P=\frac{GMm}{2r}+-\frac{GMm}{r}=-\frac{GMm}{2r}$$
+\paragraph{Synchronous orbits}
+$ $\\
+\textbf{Geosynchronous orbit} - Time period of 24h, will be seen at the same place at the same time every day\\ 
+\textbf{Geostationary orbit} - Time period of 24h, but in the plane of the equator and travelling the same direction as the earth, appears stationary to an observer on the ground\\
+\\
+The height at which these satellites must be is determined by Kepler's law
+\subsection{Electric fields}
+\subsubsection{Coulomb's law}
+This is the first equation under electric fields on the data sheet, it describes the force between two point charges in a vacuum\\
+\textbf{Permittivity of free space} - The charge per unit area in coulombs per square metre on oppositely charged plates when the electric field strength between the plates is one volt per metre\\
+The difference between the permittivity of free space and the permittivity of air is so insignificant air can be treated as a vacuum.\\
+\textbf{Electric field strength} - At a point in an electric field, the force per unit charge on a small positively charged object in that field
+\begin{center}
+\includegraphics[width=12cm]{field_lines.png} 
+\end{center}
 
+\paragraph{Derive $Fd=Q\Delta V$}
+$$F=EQ \quad E=\frac{V}{d} \quad\therefore F=\frac{QV}{d} \quad\therefore Fd=QV$$
+\paragraph{Particle in a uniform electric field}
+\begin{center}
+\includegraphics[width=8cm]{particle.jpg}
+\end{center}
 \end{document}

### 2018-05-29 Maths Notes/Statistics/S2/Cheat Sheet/S2 Cheat Sheet.tex
S2 Cheat Sheet

@@
 $$Y\sim B(6,0.256) \quad P(Y<2)=0.4987$$
+\subsection{Probability questions involving population parameters}
+\textit{Find to 2d.p. the value of k so that $P(\mu-k\sigma<X<\mu+k\sigma)=0.5$}
+$$P(-k<Z<k)=0.5$$
+$$P(Z=k)=0.75$$
 \section{Continuous random variables}
@@
 Unlike for discrete distributions
+\subsection{Skew}
+$$\textrm{Positive skew:} Mean>Median>Mode$$
+$$\textrm{Negative skew:} Mean<Median<Mode$$
 \newpage
@@
 \section{Population and samples}
-\subsection{Definitions}
+\setitemize{}
 \begin{itemize}
@@
 \end{itemize}
-
+\setitemize{noitemsep,topsep=-5pt,leftmargin=*}
+\begin{tabularx}{\textwidth}{|X|X|X|}
+\hline
+&Advantages&Disadvantages\\
+\hline
+Sample survey&
+\begin{itemize}
+\item If the population is large and well mixed the sample will be representative
+\item Cheaper than a census
+\item Advantageous when testing results in destruction
+\item Data is more readily available
+\end{itemize}&
+\begin{itemize}
+\item Uncertainty as there is variation between samples
+\item Could have bias
+\end{itemize}\\
+\hline
+Census&
+\begin{itemize}
+\item Every single member of the population is used
+\item Unbiased
+\item Accurate
+\end{itemize}&
+\begin{itemize}
+\item Time
+\item Cost
+\item Difficult to ensure the whole population is surveyed
+\end{itemize}\\
+\hline
+\end{tabularx}
+\section{Hypothesis testing}
+\setitemize{}
+\subsection{Definitions}
+\begin{itemize}
+\item \textbf{Critical region} - The range of values such that the null hypothesis is rejected
+\item \textbf{Hypothesis test} - A procedure to examine a value of a population parameter proposed by the null hypothesis
+\item \textbf{Significance level} - The probability of incorrectly rejecting $H_0$
+\end{itemize}
+\subsection{Determining the critical region (from a table)}
+Remember to halve the significance level for a two tailed test\\
+Small value tail: Find the closest value under the significance level, unless otherwise stated\\
+Large value tail: Find the closest value above (1-Sig level), then add one to the value\\
+Remember to state the probability in each tail, and the actual critical region using inequalities, not just equations showing the critical values\\
+If the distribution has an upper limit, remember to state that too, for example in the binomial distribution, X cannot be greater than n.\\
+\textbf{Actual significance} - The sum of the probabilities in the two tails
+\newpage
+\subsection{Methods}
+\subsubsection{Without normal approximation}
+\begin{enumerate}
+\item Specify $H_0$ and $H_1$
+\item Specify the distribution for $X$ under the null hypothesis
+\item Determine the probability of the observed value or a more extreme value, or determine the critical region
+\item Use the probability to state whether $H_0$ is rejected or not, ensuring you directly compare the probability with the significance level
+\item Put the conclusion in context
+\end{enumerate}
+\subsubsection{With normal approximation}
+\begin{enumerate}
+\item Specify $H_0$ and $H_1$
+\item Specify the distribution for $X$ under the null hypothesis
+\item Specify the distribution for $Y$ for the normal approximation
+\item Do continuity correction
+\item Standardise to get a probability in $Z$
+\item Compare to the critical values on the data sheet
+\item Use the probability to state whether $H_0$ is rejected or not, ensuring you directly compare the probability with the significance level
+\item Put the conclusion in context
+\end{enumerate}
 \end{document}

### 2018-05-29 Physics Notes/Paper 1/Paper 1.tex
Physics Paper 1 Notes

@@
 \lhead{A Level Physics}
+\setcounter{secnumdepth}{5}
+\usepackage[compat=1.1.0]{tikz-feynman}
+
+%REMINDER: This needs to be compiled with LuaLaTeX to work
 
@@
 \subsection{Particles, antiparticles and photons}
-
+\subsubsection{Particle antiparticle pairs and their properties}
+{\def\arraystretch{1.5}
+\begin{tabularx}{\textwidth}{|X|X|X|}
+\hline
+\textbf{Property}&\textbf{Particle}&\textbf{Antiparticle}\\
+\hline
+Mass&x&x\\
+\hline
+\textcolor{red}{Charge}&x&-x\\
+\hline
+Rest Energy&x&x\\
+\hline
+\textcolor{red}{Baryon Number}&x&-x\\
+\hline
+\textcolor{red}{Lepton Number}&x&-x\\
+\hline
+\textcolor{red}{Strangeness}&x&-x\\
+\hline
+\end{tabularx}}
+\newpage
+\paragraph{Mesons}
+\subparagraph{Pions(All 0 Strangeness)}
+$ $\\
+{\def\arraystretch{1.5}
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+$\pi^0$&$U\bar{U}$ or $D\bar{D}$\\
+\hline
+$\pi^+$&$U\bar{D}$\\
+\hline
+$\pi^-$&$D\bar{U}$\\
+\hline
+\end{tabularx}}
+\subparagraph{Kaons (All strange)}
+$ $\\
+{\def\arraystretch{1.5}
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+$K^+$&$U\bar{S}$\\
+\hline
+$K^-$&$\bar{U}S$\\
+\hline
+$K^0$&$D\bar{S}$\\
+\hline
+$\bar{K^0}$&$\bar{D}S$\\
+\hline
+\end{tabularx}}
+\subsubsection{The photon model of electromagnetic radiation}
+A photon is a particle whose energy depends on its frequency. Formulas can be found on the data sheet to calculate this relationship
+\subsubsection{Methods of annihilation and pair production}
+\paragraph{Annihilation}
+When a particle and an antiparticle meet, they annihilate each other, releasing two photons, with energy sum equivalent to the sum of the energy of the particle and antiparticle.
+This energy can be calculated from the rest energy values on the data sheet.
+$$hf_{min}=E_0$$
+\paragraph{Pair production}
+In pair production a photon creates a particle and an antiparticle
+$$hf_{min}=2E_0$$
+\subsection{Particle interactions}
+\subsubsection{The four fundamental interactions}
+{\def\arraystretch{1.5}
+\begin{tabularx}{\textwidth}{|X|X|X|X|}
+\hline
+\textbf{Force}&\textbf{Affects}&\textbf{Gauge Boson}&\textbf{Range}\\
+\hline
+Gravitational&Mass&Graviton&Infinite\\
+\hline
+Electromagnetic&Charge&Photon&Infinite\\
+\hline
+Nuclear Strong&Quarks&Gluon(Pion)&$10^{-15}$m\\
+\hline
+Nuclear Weak&Leptons+Quarks&$W^+,W^-,Z^0$&$10^{-18}$m\\
+\hline
+\end{tabularx}}
+\newpage
+\subsubsection{Diagrams to represent the interactions}
+\includegraphics[width=6cm]{neutron-neutrino.png}
+\includegraphics[width=6cm]{proton-antineutrino.png}
+\includegraphics[width=6cm]{betaminus.png}
+\includegraphics[width=6cm]{betaplus.png}
+\includegraphics[width=6cm]{electron_capture.png}
+\subsection{Classifications of particles}
+{\renewcommand{\arraystretch}{2}
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|}
+\hline
+&\multicolumn{2}{|c|}{\centering Hadron}&\multicolumn{4}{|c|}{\centering Lepton}\\
+\cline{2-7}
+&Baryon&Meson&Electron&Muon&Electron neutrino&Muon neutrino\\
+\hline
+What it is&3 quarks&Quark antiquark pair&&&&\\
+\hline
+\end{tabularx}}
+\paragraph{Baryons}
+\begin{itemize}
+\item Baryon number is conserved during interactions
+\item The proton is the only stable baryon, all other baryons decay to it
+\end{itemize}
 \end{document}

### 2018-05-29 Maths Notes/Further Pure/FP2/Cheat Sheet/FP2 Cheat Sheet.tex
FP2 Cheat Sheet

--- 2018-05-27 Maths Notes/Further Pure/FP2/Overall Notes/FP2 Notes.tex
@@
 \section{Further complex numbers}
+Remember that complex fractions can be rationalised by multiplying the top and bottom by the complex conjugate
 \subsection{Converting between forms}
@@
 This is given on the data sheet and has multiple applications
-\subsubsection{Z formulas}
+\subsubsection{Roots of unity}
+When solving $z^a=r(\cos(\theta)+i\sin(\theta))$ type questions, remember to first rewrite as:
+$$z^a=r(\cos(\theta+2k\pi)+i\sin(\theta+2k\pi))$$
+\subsubsection{Powers of cos/sin$\rightarrow$Multiples of $\theta$}
 If $z=\cos\theta+i\sin\theta$
@@
 $$z^n-\frac{1}{z^n}=2i\sin n\theta$$
-\subsubsection{Roots of unity}
-
-\subsection{Solving complex equations}
-When solving $z^a=r(\cos(\theta)+i\sin(\theta))$ type questions, remember to first rewrite as:
-$$z^a=r(\cos(\theta+2k\pi)+i\sin(\theta+2k\pi))$$
+\subsubsection{Multiples of $\theta\rightarrow$ Powers of cos/sin}
+Whatever the multiple of $\theta$ is, raise $(\cos\theta+i\sin\theta)$ to that power.
+Use De Moivre's theorem to express this in multiples of $\theta$, and use binomial expansion to express it in terms of powers of $\theta$.
+Equate the real/imaginary parts, depending on whether it is cos or sin to simplify.
 
 \subsection{Loci on the complex plane}
+{\renewcommand{\arraystretch}{2}
 \begin{tabularx}{\textwidth}{|X|X|}
@@
 \hline
+{\Large$|z-z_1|=\lambda|z-z_2|$}&A circle, the equation of which is best found algebraically\\
+\hline
 {\Large$\arg(z-z_1)=\theta$}&The half line from a fixed point $z_1$, making an angle $\theta$ with the positive real axis\\
@@
 \hline
-\end{tabularx}
+\end{tabularx}}
+\subsubsection{Cartesian equations of loci}
+Method for modulus questions:
+\begin{itemize}
+\item Replace $z$ with $x+iy$
+\item Group real and imaginary parts if needed
+\item Use $|x+iy|=\sqrt{x^2+y^2}$
+\item Complete the square if you know you're going to get a circle
+\end{itemize}
+
 \subsection{Translations}
@@
 Integrate both sides then simplify
-
-\section{Maclaurin and Taylor Series}
-Use the formulas on the data sheet
-\subsection{Solving differential equations using the Taylor expansion}
-From the differential equation, calculate the values of $\frac{dy}{dx}$, $\frac{d^2y}{dx^2}$ etc up to whatever is needed.\\
-Then substitute those values into the Taylor series to solve the differential equation
-\section{Polar Coordinates}
-\begin{tabularx}{\textwidth}{|X|X|}
-\hline
-Equation&Description\\
-\hline
-$r=a$&A circle, centre (0,0) with a radius of a\\
-\hline
-$\theta=\alpha$&A half line starting from (0,0) making an angle $\alpha$ with the initial line\\
-\hline
-$r=a\theta$&A spiral starting at the origin\\
-\hline
-$r=a(1+\cos\theta)$&A cardioid with x intercept a\\
-\hline
-$r^2=a^2\cos2\theta$&An infinity symbol with x intercept of a\\
-\hline
-$r^2=a^2\sin2\theta$&Infinity symbol rotated by $\frac{\pi}{4}$\\
-\hline
-$r=a\sin3\theta$&A windmill with 3 blades\\
-\hline
-\end{tabularx}
-\subsection{Integration}
-$$\textrm{Area}=\frac{1}{2}\int_\alpha^\beta r^2 \ d\theta$$
-The area of the sector is bounded by the half lines $\theta=\alpha$ and $\theta=\beta$
-\subsection{Differentiation}
-To find tangents parallel and perpendicular to the initial line:\\
-\\
-Parallel: $\frac{dy}{d\theta}=0$\\
-Perpendicular: $\frac{dx}{d\theta}=0$
 \section{Second order differential equations}
@@
 \\
-If there is a clash of terms between the CF and PI, then an alternate PI will be given to you.
+If there is a clash of terms between the CF and PI, then an alternate PI will be given to you. If in doubt, multiply the standard form through by x, but this will not always work.
 \subsection{Boundary conditions}
@@
 $$\frac{d^2y}{dx^2}=\mathbf{e^{-2u}\Big(-\frac{dy}{du}+\frac{d^2y}{du^2}\Big)}$$
+\textcolor{red}{Then substitute the values for x,$\frac{dy}{dx}$, and $\frac{d^2y}{dx^2}$ into the original equation to simplify it}
+
+\section{Maclaurin and Taylor Series}
+Use the formulas on the data sheet, remember than things like lns can be simplified if they look impossible to solve.
+\subsection{Solving differential equations using the Taylor expansion}
+From the differential equation, calculate the values of $\frac{dy}{dx}$, $\frac{d^2y}{dx^2}$ etc up to whatever is needed.\\
+Then substitute those values into the Taylor series to solve the differential equation
+\section{Polar Coordinates}
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+Equation&Description\\
+\hline
+$r=a$&A circle, centre (0,0) with a radius of a\\
+\hline
+$\theta=\alpha$&A half line starting from (0,0) making an angle $\alpha$ with the initial line\\
+\hline
+$r=a\theta$&A spiral starting at the origin\\
+\hline
+$r=a(1+\cos\theta)$&A cardioid with x intercept a\\
+\hline
+$r^2=a^2\cos2\theta$&An infinity symbol with x intercept of a\\
+\hline
+$r^2=a^2\sin2\theta$&Infinity symbol rotated by $\frac{\pi}{4}$\\
+\hline
+$r=a\sin3\theta$&A windmill with 3 blades\\
+\hline
+\end{tabularx}
+\newpage
+\includegraphics[width=18cm]{polar.png}\\
+For $r=p\sec(\alpha-\theta)$ to solve it, divide both sides by $\sec(\alpha-\theta)$, then use the cos addition formula and simplify.
+\subsection{Integration}
+$$\textrm{Area}=\frac{1}{2}\int_\alpha^\beta r^2 \ d\theta$$
+The area of the sector is bounded by the half lines $\theta=\alpha$ and $\theta=\beta$
+\subsection{Differentiation}
+To find tangents parallel and perpendicular to the initial line:\\
+\\
+Parallel: $\frac{dy}{d\theta}=0$\\
+Perpendicular: $\frac{dx}{d\theta}=0$
 

### 2018-05-29 Physics Notes/Paper 2/Paper 2.tex
Paper 2 notes update

@@
 \setcounter{secnumdepth}{4}
+\usepackage{float}
 \begin{document}
@@
 \end{center}
+\subsubsection{Electric potential}
+\textbf{Absolute electric potential} - At a point in an electric field, the work done per unit charge on a small positively charged object to move it from infinity to that point in the field
+\subsection{Capacitance}
+\subsubsection{Capacitance, parallel plate capacitor and energy stored in a capacitor}
+\textbf{Capacitance} - The charge stored per unit p.d. of a capacitor\\
+In the presence of an electric field, the polar molecules in the electric field will rotate, causing it to become polarised, and so a better dielectric.
+This is why polar molecules are used for dielectrics instead of non polar molecules
+\subsubsection{Capacitor charge and discharge}
+\includegraphics[width=6cm]{charge.png}
+Voltage and charge follow the same pattern when charging and discharging, whereas current follows the opposite pattern.\\
+The time constant(RC) is the time it until 37\% of the charge on the capacitor is remaining.
+$$T_{\frac{1}{2}}=0.69RC$$
+\subsection{Magnetic fields}
+\subsubsection{Magnetic flux density}
+\textbf{Magnetic flux density} - The magnetic force per unit length per unit current on a current carrying conductor at right angles to the field lines (Derive from F=BIl)
+\subsubsection{Moving charges in a magnetic field}
+$$F=BQv \quad \textrm{When the field is perpendicular to the velocity}$$
+\paragraph{Cyclotron}
+\begin{center}
+\includegraphics[width=10cm]{cyclotron.jpg}
+\end{center}
+This accelerates the particles to very high speeds, for use in medicine
+\subsubsection{Magnetic flux and flux linkage}
+$$\textrm{Magnetic flux:}\phi=BA \quad \textrm{Where B is normal to A}$$
+\textbf{Flux} - $\phi=BA$ for a uniform magnetic field of flux density B that is perpendicular to an area A. Unit of Weber(Wb)\\
+\textbf{Flux Linkage} - Through a coil of N turns, $N\phi=BAN\cos\theta$ where B is the magnetic flux density perpendicular to area A, unit also of Wb
+\subsubsection{Electromagnetic induction}
+\textbf{Faraday's law} - The induced emf in a circuit is equal to the rate of change of the magnetic flux linkage through the circuit\\
+\textbf{Lenz's law} - When a current is induced in electromagnetic induction, the direction of the induced current is always such as to oppose the change that causes the current
+\subsubsection{Alternating currents}
+\textbf{Peak to peak} - The difference in the values between the two peak and the trough of an ac wave\\
+\textbf{Root mean square} - The DC voltage that will give the same effect as the AC voltage
+\paragraph{Oscilloscope}
+$x$ axis - Time base\\
+$y$ axis - Y sensitivity\\
+The position and size of the waveform should be adjusted so that it takes up as much of the screen as possible, reducing uncertainty.
+\subsubsection{Transformers}
+\textbf{Eddy currents} - Induced currents in metal parts of ac machines\\
+Inefficiencies:
+\begin{itemize}
+\item Eddy currents form in the metal core of the transformer, leading to a loss in power
+\item Resistance in the windings around the transformer resulting in energy wasted as heat
+\item Magnetisation and demagnetisation of the core causes loss in energy
+\end{itemize}
+Power is transmitted at high voltage in transmission lines so they can be at a low resistance, and as power dissipated is $I^2R$, the lower the current, the less power is wasted
+\section{Nuclear physics}
+\subsection{Radioactivity}
+\subsubsection{Rutherford scattering}
+\includegraphics[width=8cm]{scatter.png}
+Rutherford's experiment involved firing a beam of alpha particles at gold foil and measuring the paths of particles from the foil.
+\begin{itemize}
+\item Gold was used as it was expected to have a large nucleus
+\item The screen fluoresces when collided with
+\item This showed the atom was mostly empty space with a positive nucleus
+\end{itemize}
+\begin{figure}[H]
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+
+\includegraphics[width=6cm]{foil.jpg}  
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+Observation&Explanation\\
+\hline
+Most electrons pass all the way through&Atoms are mostly empty space\\
+\hline
+Some are deflected&The atom has a positive centre\\
+\hline
+Some are deflected by significant angles&The positive charge is condensed in a small area\\
+\hline
+\end{tabularx}
+    \end{minipage}
+\end{figure}
+\subsubsection{$\alpha$, $\beta$ and $\gamma$ radiation}
+\begin{tabularx}{\textwidth}{|c|X|X|X|}
+\hline
+&Alpha&Beta&Gamma\\
+\hline
+Nature&2 Protons+2 Neutrons&High speed electron or positron&High energy photon\\
+\hline
+Range&Up to 10cm&Up to 1m&Infinite\\
+\hline 
+Deflection in a magnetic field&Deflected&Opposite direction to $\alpha$ particles and more easily deflected&Not deflected\\
+\hline
+Absorption&Paper&Aluminium&Lead \\
+\hline
+Ionisation&$10^4$ ions per mm&100 ions per mm&Very weak ionising effect\\
+\hline
+Energy of each particle&Constant for a given source&Varies up to a maximum for a given source&Constant for a given source\\
+\hline
+\end{tabularx}
+\paragraph{Inverse square law for gamma radiation}
+$$I=\frac{k}{x^2}$$
+\paragraph{Safety}$ $\\
+Those working in areas of high radiation, for example nuclear power plants, should wear film badges which monitor a persons exposure to radiation
+\paragraph{Background radiation}$ $\\
+Background radiation has many sources:
+\begin{itemize}
+\item Air (Radon gas)
+\item Medical
+\item Ground and buildings
+\item Food and drink
+\end{itemize}
+\paragraph{Uses of radiation in medicine}$ $\\
+The health benefits from using radiation in medicine almost always outweigh the risks, but doctors must protect themselves as repeated exposure is dangerous
 \end{document}

### 2018-05-30 Maths Notes/Core/C3/Cheat sheet/C3 Cheat Sheet.tex
C3 Cheat sheet

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - C3}
\begin{document}
\begin{center}
\underline{\huge C3 Cheat Sheet}
\end{center}
\section{Algebraic fractions}
Algebraic long division can help to simplify a fraction, remember fractions can be expressed as:
$$Q(x)+\frac{R(x)}{D(x)}$$
Where $Q(x)$ is the quotient, $R(x)$ is the remainder and $D(x)$ is the divisor
\section{Functions}
\textbf{Domain} - Inputs\\
\textbf{Range} - Outputs\\
Reasons for a restricted domain:
\begin{itemize}
\item The denominator of the fraction can't be zero
\item You can't square root a negative number
\item You can't log numbers $\leqslant0$
\end{itemize}
Reasons for a restricted range:
\begin{itemize}
\item A restricted domain
\item Asymptotes
\item Minimum or maximum of a quadratic/trig graph
\end{itemize}
If the function doesn't have any obvious restrictions, still remember to put $x\in\mathbb{R}$, or $f(x)\in\mathbb{R}$
\subsection{Finding the inverse of a function}
Rearrange the function to make x the subject, then swap y for x and x for $f^{-1}(x)$\\
\\
The inverse function is a reflection in the line $y=x$ of the original function.\\
\\
If asked to find the values where the inverse function equals the original function, find where $f(x)=x$ as this will not have been transformed by the reflection\\
\\
A function will not have an inverse if it is a many to one function 
\subsection{Finding a composite function}
Substitute the inner function as x into the outer function
\subsection{What to do when not given an explicit function}
When not given an explicit function, remember that given a pair of coordinates $f(x)=f^{-1}(y)$, this can be used to find the function
\section{Exponential and log functions}
$$\log a+\log b=\log(ab)$$
$$\log a-\log b=\log(\frac{a}{b})$$
$$\log a^b=b\log a$$
Remember that you can only apply e to both sides when there is one term on each side, combine terms
\subsection{Quadratic functions}
Some questions with varying powers of $e$ are usually best solved as a quadratic, multiplying through by $e^{ax}$ then substituting $y=e^x$ and solving for $y$ then finding the natural log of the answer.
\subsection{Drawing graphs of $e^x$ and $\ln(x)$}
$\ln(x)$ is the inverse function of $e^x$, so just reflect in the line $y=x$, other than that, apply graph transformations as normal, remember to draw in asymptotes.
\section{Numerical methods}
To prove a root (turning point) is in a range, there will be a change of sign of the gradient.\\
Use the structure of the equation you are trying to rearrange to to help your method.
\section{Transforming graphs of functions}
\subsection{Modulus graphs}
$y=f(|x|)$ - Reflect in y axis (there can't be the correct values for negative x values)\\
$y=|f(x)|$ - Reflect in x axis (there can't be negative y values)\\
Remember that for curved graphs, the point of transformation will likely be sharp, rather than smooth
\subsection{Solving modulus equations}
To solve a modulus equation, use both the positive and negative versions, for example:
$$|3x-2|=x+4|$$
$$3x-2=x+4 \quad \textrm{and} -3x+2=x+4$$
Though remember to substitute the values found back into the original equation to check they are valid
\section{Trigonometry}
$$\sin(x)=\sin(180-x)$$
$$\cos(x)=\cos(360-x)$$
$$\sin \textrm{and} \cos \textrm{repeat every 360}\degree$$
$$\tan \textrm{repeats every 180}\degree$$
$$\sin(x)=\cos(90-x)$$
Remember to get the other identities, divide:
$$\sin^2x+\cos^2x=1$$
By either $\sin^2x$ or $\cos^2x$
\subsection{The R formula}
$a\sin\theta\pm b\cos\theta$ can be expressed in the form $R\sin(\theta\pm\alpha)$\\
$a\cos\theta\pm b\sin\theta$ can be expressed in the form $R\sin(\theta\mp\alpha)$\\
Where: 
$$R = \sqrt{a^2+b^2}$$
$$\alpha=\arctan(\frac{b}{a})$$
\newpage
\section{Differentiation}
Product rule:
$$y=f(x)g(x)\quad \textrm{then} \quad\frac{dy}{dx}=f'(x)g(x)+f(x)g'(x)$$
Quotient rule:
$$y=\frac{f(x)}{g(x)} \quad \textrm{then} \quad\frac{dy}{dx}=\frac{f'(x)g(x)-f(x)g'(x)}{(g(x))^2}$$
Chain rule:
$$y=[f(x)]^n \quad \textrm{then} \quad \frac{dy}{dx}=n[f(x)]^{n-1}f'(x)$$
$$y=f[g(x)] \quad \textrm{then} \quad \frac{dy}{dx}=f'[g(x)]g'(x)$$
$$\frac{dy}{dx}=\frac{dy}{du}\times\frac{du}{dx}$$
\end{document}

\end{document}

### 2018-05-30 Physics Notes/Paper 1/Paper 1.tex
Paper 1 Notes

@@
 \setcounter{secnumdepth}{5}
-\usepackage[compat=1.1.0]{tikz-feynman}
+\usepackage[english]{babel}
 
-%REMINDER: This needs to be compiled with LuaLaTeX to work
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{0ex}%
+    {-3.25ex plus -1ex minus -0.2ex}%
+    {1.5ex plus 0.2ex}%
+    {\normalfont\normalsize\bfseries}}
+\makeatother
 
@@
 \end{itemize}
+\paragraph{Kaons and pions}
+Kaons (K mesons) decay into Pions($\pi$ mesons), they decay by the weak interaction, so strangeness need not be conserved
+$$K^+\rightarrow \mu^++\nu_\mu$$
+$$K^+\rightarrow \pi^++\pi^0$$
+$$K^-\rightarrow \mu^-+\overline{\nu_\mu}$$
+$$K^-\rightarrow \pi^-+\pi^0$$
+$$K^-\rightarrow \pi^0+\mu^-+\overline{\nu_\mu}$$
+\paragraph{Leptons}
+Lepton number is conserved in an interaction, muons decay into electrons
+$$\mu^-\rightarrow e^-+\overline{\nu_e}+\nu_\mu$$
+$$\mu^+\rightarrow e^++\nu_e+\overline{\nu_\mu}$$
+\paragraph{Strange particles}
+Strange particles are produced through the strong interaction and decay through the weak interaction, this is because strangeness is conserved during the strong interaction, but not during the weak interaction.
+\subsubsection{Quarks and antiquarks}
+Differences between quarks and antiquarks
+\begin{itemize}
+\item Opposite strangeness
+\item Opposite charge
+\item Opposite strangeness
+\end{itemize}
+\paragraph{Quark compositions}
+\begin{itemize}
+\item Proton -UUD
+\item Neutron - DUD
+\item Pion - Not strange, sign indicates charge
+\item Kaon - Strange, sign indicates charge
+\end{itemize}
+\subsubsection{Applications of conservation laws}
+Changes of quark nature
+\begin{itemize}
+\item $\beta^-$, down $\rightarrow$ up
+\item $\beta^+$, up $\rightarrow$ down
+\end{itemize}
+\begin{center}
+\includegraphics[width=10cm]{quark_beta.png}
+\end{center}
+In all interactions, energy and momentum must be conserved
+\subsection{Electromagnetic radiation and quantum phenomena}
+\subsubsection{The photoelectric effect}
+\textbf{Photoelectric effect} - The emission of electrons from a metal surface when the surface is illuminated by a light of frequency greater than a minimum value known as the threshold frequency
+\paragraph{Threshold frequency}
+Because the energy of a photon is proportional to its frequency ($E=hf$), a minimum frequency must be reached so that the electrons have sufficient energy to escape the surface
+\paragraph{Work function and stopping potential}
+\textbf{Work function} - The minimum amount of energy needed by an electron to escape from a metal surface\\
+\textbf{Stopping potential} - The potential difference required to stop an electron
+\paragraph{The photoelectric equation}
+$$hf=\phi+E_{K(Max)}$$
+$hf$ is the energy of the incident photon\\
+$\phi$ is the work function\\
+$E_{K(max)}$ is the maximum kinetic energy\\
+Electrons emitted will have a range of kinetic energies, depending how much work is done to escape the metal
+\begin{tikzpicture}
+\begin{axis}[axis lines=middle,scale=0.8,ylabel = KE,xlabel=Frequency,ylabel style={rotate=90,anchor=south},xlabel style={anchor=south},xmin=0,xmax=7,ymin=-5,ymax=7,xtick={2},xticklabels={$F_0$},ytick={-2},yticklabels={$-\Phi$}
+]
+\addplot[color=black,domain=0:7]{x-2};
+\end{axis}
+\end{tikzpicture}\\
+The gradient of the line is Planck's constant
+\subsubsection{Collisions of electrons with atoms}
+\paragraph{Ionisation and excitation}
+\textbf{Ion} - A charged atom\\
+\textbf{Ionisation} - The process of creating ions\\
+\textbf{Excitation} - The process in which an atom absorbs energy without becoming ionised as a result of an electron inside an atom moving from an inner shell to an outer shell
+\paragraph{•}
+
 \end{document}

### 2018-05-30 Maths Notes/Core/C4/Cheat Sheet/C4 Cheat Sheet.tex
C4 Cheat Sheet

@@
 \section{Parametric equations}
-
+$$\frac{dy}{dx}=\frac{(\frac{dy}{dt})}{(\frac{dx}{dt})}$$
+$$\int y \ dx=\int y\frac{dx}{dt}dt$$
+Remember to make use of $\sin^2x+\cos^2x=1$ when converting between parametric and Cartesian
+\section{Binomial expansion}
+$$(a+bx)^n=a^n(a+\frac{b}{a}x)^n$$
+Remember that fractions can be simplified for binomial expansion using negative powers
+\section{Differentiation}
+On C3 data sheet:
+$$a^x=e^{\ln(a^x)}=e^{x\ln(a)}$$
+$$\frac{d}{dx}(a^x)=\ln a\times e^{x\ln a}=a^x\ln a$$
+\subsection{Implicit differentiation}
+$$\frac{d}{dx}(y^2)=2y\frac{dy}{dx}$$
+\subsection{Setting up differential equations}
+\textbf{Example:}\\
+\textit{Temperature falls at a rate proportional to its current temperature}
+$$\frac{dT}{dt}=-kT$$
+\subsection{Related rates of change}
+When given a rate and asked to find a different rate, use equations like
+$$\frac{dA}{dx}=\frac{dA}{dt}\times\frac{dt}{dx}$$
+Remember that finding relations between length, area and volume can be found using known formulas
+\section{Vectors}
+\subsection{Point of intersection}
+Set the two vector lines equal to each other, find $\lambda$ etc, substitute in to see if they agree, remember to write the final point
+\subsection{Angle between two lines}
+$$\cos\theta=\frac{a\cdot b}{|a||b|}$$
+This can be used when lines are perpendicular as then
+$$a\cdot b=|a||b|$$
+\subsection{Find a missing x/y/z value of a point on a line}
+Solve the equation for the two known points to find $\lambda$, then use that to find the other point
+\subsection{Find the length of a vector/distance between two points}
+Find the equation of the vector using the formula
+$$\overrightarrow{AB}=\begin{pmatrix}x_b-x_a\\y_b-y_a\\z_b-z_a\end{pmatrix}$$
+Then use
+$$|AB|=\sqrt{x^2+y^2+z^2}$$
+\subsection{Find the nearest point on a line to a point not on the line}
+The shortest distance is always at a right angle, so you can use the fact that:
+$$|a||b|=a\cdot b$$
+Set up the equation of the line including $\lambda$, then solve the equation of the two of them being at right angles to find the value of $\lambda$ and so find the point
+\subsection{Show that 3 points are collinear}
+Show that the vector between the first and second points is a multiple of the vector between the second and third points
+\subsection{Find the equation of a line from two points}
+Find the direction vector from $\overrightarrow{AB}$ then arrange it either the form:
+$$A+\lambda\Big(\overrightarrow{AB}\Big) \quad \textrm{or} \quad B+\lambda\Big(\overrightarrow{AB}\Big)$$
+\subsection{Find the reflection of a point in a line}
+Find the shortest distance vector from the point to the line, then draw the vector coming out the other side of the line (negative of the vector)
+\subsection{Find the point after going a specific distance in the direction of a given vector}
+\textbf{Example}:\\
+\textit{What is the position vector 10 units in the direction
+$\begin{pmatrix}1\\0\\3\end{pmatrix}$ from the point $\begin{pmatrix}2\\2\\2\end{pmatrix}$?}\\
+\textcolor{red}{Convert the direction into a unit vector}
+$$\sqrt{1^2+0^2+3^2}=2$$
+This means that the vector is 2 units away from the origin, so to create the unit vector (1 unit away from the origin) multiply it by $\frac{1}{2}$
+$$\frac{1}{2}\begin{pmatrix}2\\2\\2\end{pmatrix}$$
+Then add 10 of these units to the initial vector point to get the answer
+$$\begin{pmatrix}1\\2\\2\end{pmatrix}+10\times\frac{1}{2}\begin{pmatrix}2\\2\\2\end{pmatrix}=\begin{pmatrix}7\\2\\17\end{pmatrix}$$
+\section{Integration}
+\subsection{Integral of Trig squares}
+{\renewcommand{\arraystretch}{2}
+\begin{tabularx}{\textwidth}{|X|X|}
+\hline
+$f(x)$&$\int f(x) \ dx$\\
+\hline
+$\sec^2x$&On formula book\\
+\hline
+$\csc^2x$&On differentiation side of formula book\\
+\hline
+$\cot^2x$&Use the identity
+$1+\cot^2x=\csc^2x$, then use known integral of $\csc^2x$ to integrate\\
+\hline
+$\sin^2x$&Use cos addition formula\\
+\hline
+$\cos^2x$&Use cos addition formula\\
+\hline
+$\tan^2x$&Use the identity $\tan^2x+1=\sec^2x$\\
+\hline
+\end{tabularx}}
 \end{document}

### 2018-05-30 Physics Notes/Paper 2/Paper 2.tex
Physics paper 2

@@
 \usepackage{enumitem}
-\setcounter{secnumdepth}{4}
+\setcounter{secnumdepth}{6}
 \usepackage{float}
+\usepackage[english]{babel}
+
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{0ex}%
+    {-3.25ex plus -1ex minus -0.2ex}%
+    {1.5ex plus 0.2ex}%
+    {\normalfont\normalsize\bfseries}}
+\makeatother
+
+\makeatletter
+\renewcommand{\subparagraph}{\@startsection{subparagraph}{4}{0ex}%
+    {-3.25ex plus -1ex minus -0.2ex}%
+    {1.5ex plus 0.2ex}%
+    {\normalfont\normalsize\bfseries}}
+\makeatother
+
 \begin{document}
@@
 \paragraph{Synchronous orbits}
-$ $\\
 \textbf{Geosynchronous orbit} - Time period of 24h, will be seen at the same place at the same time every day\\ 
@@
 $$I=\frac{k}{x^2}$$
-\paragraph{Safety}$ $\\
+\paragraph{Safety}
 Those working in areas of high radiation, for example nuclear power plants, should wear film badges which monitor a persons exposure to radiation
-\paragraph{Background radiation}$ $\\
+\paragraph{Background radiation}
 Background radiation has many sources:
@@
 \end{itemize}
-\paragraph{Uses of radiation in medicine}$ $\\
+\paragraph{Uses of radiation in medicine}
 The health benefits from using radiation in medicine almost always outweigh the risks, but doctors must protect themselves as repeated exposure is dangerous
+\subsubsection{Radioactive decay}
+$$\frac{\Delta N}{\Delta t}=-\lambda N$$
+$$N=N_0e^{-\lambda t}$$
+$$A=\lambda N$$
+$$A=A_0e^{-\lambda t}$$
+$$m=m_0e^{-\lambda t}$$
+$$C=C_0e^{-\lambda t}$$
+$$T_{\frac{1}{2}}=\frac{\ln 2}{\lambda}$$
+$N$ - Number of nuclei\\
+$\lambda$ - Decay constant\\
+$A$ - Activity\\
+$m$ - Mass of the isotope\\
+$C$  - Count rate on a Geiger counter\\
+$T_{\frac{1}{2}}$ - Half life of the isotope
+\paragraph{Constant decay probability}
+There is a constant decay probability of an isotope, and the decays happen at random, this means that the number of nuclei that decay in a certain time interval depends only on the total number of nuclei present.
+\paragraph{Applications}
+\subparagraph{Carbon dating}
+The half life of carbon-14 is a known value and so can be used to determine the age of objects. By looking at the activity of a live equivalent of equal mass and comparing it, the age can be found.\\
+\textbf{Example}:\\
+Activity =0.28Bq, Live activity=1.3Bq, half life = 5570 years
+$$T_{\frac{1}{2}}=1.76\times 10^{11}$$
+$$\lambda=\frac{\ln 2}{1.76 \times 10^{11}}=3.95\times 10^{12}$$
+$$A=A_0e^{-\lambda t} \Rightarrow 0.28=1.3e^{-\lambda t} \Rightarrow \lambda t=1.535$$
+$$t=\frac{1.535}{\lambda}=\frac{1.535}{3.95\times 10^{-12}}=3.88\times 10^{11}s$$
+\subparagraph{Radioactive tracers}
+Radioactive tracers should:
+\begin{itemize}
+\item Have a half life long enough for the necessary measurements to be made, but short enough to decay quickly after use
+\item Emit $\beta$ or $\gamma$ radiation so that it can be detected outside the body
+\end{itemize}
+\subsubsection{Nuclear instability}
+\includegraphics[width=8cm]{nz_plot.png}
+\includegraphics[width=6cm]{nz_changes.png}
+Electron capture would be a horizontal line to the left
+\paragraph{Nuclear excited states}
+The nuclear excited state is where the nucleus has more energy than its basic state, to counteract this, the nucleus gives off the energy in the form of a $\gamma$ ray\\
+This can be used to make artificial gamma ray emitters
+\subsubsection{Nuclear radius}
+\paragraph{Closest approach of alpha particles}
+By determining the percentage of $\alpha$ particles that are deflected by more than 90\degree, around 1 in 10,000.
+Given n layers of atoms, the probability is 1 in 10,000n.
+Then determine the cross sectional area of the radius of the atom and nucleus as a ratio.
+$$\frac{\frac{1}{4}\pi d^2}{\frac{1}{4}\pi D^2}=\frac{1}{10,000n}$$
+$$d^2=\frac{D^2}{10000n}$$
+A typical value of n is 10,000
+$$d=\frac{D}{10000}$$
+As the diameter of an atom can be more easily measured, this gives a result of around 1fm
+\paragraph{Electron diffraction}
+The diffraction of electrons can be used to give a more accurate answer for the nuclear radius.
+Electrons are accelerated so that their de Broglie wavelength is approximately the radius of the nucleus so that they diffract best.\\
+There is an angle $\theta_{min}$ away from the normal at which there is a local minimum intensity, using the relation
+$$R\sin\theta_{min}=0.61\lambda$$
+The value of R can be found, $\lambda$ is the wavelength of the electrons
 \end{document}

### 2018-05-30 Maths Notes/Mechanics/M2/Cheat Sheet/M2 Cheat Sheet.tex
M2 Cheat Sheet

\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{A Level Maths - M2}

\begin{document}
\begin{center}
\underline{\huge M2 Cheat Sheet}
\end{center}
\section{Centres of mass}
\subsection{How to find the centre of mass of a system of particles of given position and mass}
\begin{tabularx}{\textwidth}{|X|X|X|X|X|}
\hline
Mass&&&&\\
\hline
Distance&&&&\\
\hline
\end{tabularx}
$$\bar{x}=\dfrac{\Sigma m_ix_i}{\Sigma m_i}$$
$$\bar{y}=\dfrac{\Sigma m_iy_i}{\Sigma m_i}$$
\subsection{How to locate centre of mass by appeal to symmetry}
In some cases, centre of mass may be balanced around a point due to symmetry, this will make calculations easier.
\subsection{How to find the centre of mass of a composite body}
In a body with many different shapes, put the masses into the table and the associated distances and treat as normal.\\
If all the composite shapes are the same, don't bother to find the true mass, set the mass of each shape to 1 and carry on.
\subsection{How to use the position of the centre of mass in problems involving the equilibrium of a rigid body}
When asked to the angle the vertical makes with a side when suspended about a point, draw the vertical from the point to the centre of mass, then use known distances to find the angle.\\
\\
In a more complicated question when you are given an angle, use trig to find the ratio between the two sides that are not the hypotenuse, then solve simultaneously to find what is needed
\section{Energy, work and power}
\subsection{How to calculate the work done by a force}
$$WD=FS$$
\subsection{How to calculate kinetic and gravitational potential energy}
$$KE=\frac{1}{2}mv^2$$
$$GPE=mgh$$
\subsection{The term mechanical energy and the work energy principle}
\textbf{The work energy principle} - The work done by all forces on a particle equals the change in kinetic energy of the particle\\
\textbf{Mechanical energy} - The sum of the kinetic and potential energy of an object
\subsection{How to apply the concept of power to the solution of problems}
$$P=Fv$$
\newpage
\section{Equilibrium of a rigid body}
$$\textrm{Moment}=\textrm{Force}\times\textrm{Distance}$$
\section{Momentum, restitution and impulse}
\subsection{What momentum is and how to calculate it}
$$\textrm{Momentum}=mv$$
Momentum is a vector quantity\\
Definition - The quantity of motion of a moving body
\subsection{Conservation of momentum}
In all collisions, momentum is conserved
$$m_1u_1+m_2u_2=m_1v_1+m_2v_2$$
\subsection{Coefficient of restitution}
$$e=\frac{SoS}{SoA}$$
If e=1, the collision is perfectly inelastic\\
If e=0, the collision is perfectly elastic
\subsection{Impulse}
$$\textrm{Impulse}=Ft=m(v-u)$$
\section{Projectiles}
$$v=u+at$$
$$s=ut+\frac{1}{2}at^2$$
$$s=\frac{u+v}{2}t$$
$$v^2=u^2+2as$$
$$s=vt-\frac{1}{2}at^2$$
\subsection{Forces on a projectile}
Assume:
\begin{itemize}
\item Only force acting is gravity
\item Projectile is a particle
\item Projectile is not powered
\item Air has no effect on the motion
\end{itemize}
There is no horizontal acceleration for the projectile
\subsection{Equation for path of a projectile (don't need to know, but might be useful)}
$$\ddot{x}=a=0$$
$$\dot{x}=v=v\cos\alpha$$
$$x=vt\cos\alpha$$
$$t=\frac{x}{v\cos\alpha}$$
\\
$$\ddot{y}=-g$$
$$\dot{y}=-gt+v\sin\alpha$$
$$y=-\frac{1}{2}gt^2+vt\sin\alpha$$
\\
$$y=-\frac{g}{2}\Bigg(\frac{x}{v\cos\alpha}\Bigg)^2+v\Bigg(\frac{x}{v\cos\alpha}\Bigg)\sin\alpha$$
$$y=x^2\Bigg(\frac{-g}{2v^2\cos^2\alpha}\Bigg)+x\Big(\tan\alpha\Big)$$
\end{document}

### 2018-06-02 Physics Notes/Paper 1/Paper 1.tex
Physics Paper 1

@@
 \makeatother
+
+\usetikzlibrary{decorations.pathmorphing,arrows}
+
+\pgfkeys{/pgfplots/Axis Style/.style={
+    width=13.5cm, height=10cm,
+    axis x line=center, 
+    axis y line=middle, 
+    samples=100,
+    ymin=-1.2, ymax=1.2,
+    xmin=0, xmax=13.0,
+    domain=-4*pi:4*pi
+}}
+
+\pgfkeys{/pgfplots/Stationary Wave/.style={
+    width=13.5cm, height=5cm,
+    axis x line=center, 
+    axis y line=middle, 
+    samples=100,
+    ymin=-1.2, ymax=1.2,
+    xmin=0, xmax=13.0,
+    domain=-4*pi:4*pi
+}}
 
@@
 $E_{K(max)}$ is the maximum kinetic energy\\
-Electrons emitted will have a range of kinetic energies, depending how much work is done to escape the metal
+Electrons emitted will have a range of kinetic energies, depending how much work is done to escape the metal\\
 \begin{tikzpicture}
@@
 \textbf{Excitation} - The process in which an atom absorbs energy without becoming ionised as a result of an electron inside an atom moving from an inner shell to an outer shell
-\paragraph{•}
+\paragraph{The fluorescent tube}
+\begin{itemize}
+\item Ionisation and excitation of the mercury atoms as they collide with each other and the electrons in the tube
+\item The mercury atoms emit visible and ultraviolet photons when they de excite
+\item The ultraviolet photons are absorbed by the atoms in the fluorescent coating, causing them to excite
+\item The atoms in the coating de excite, emitting visible light
+\end{itemize}
+\paragraph{The electron volt}
+\textbf{Electron volt} - The work done when an electron is moved through a P.D. of 1V
+\subsubsection{Energy levels and photon emission}
+\paragraph{Line spectra}
+Light is emitted from an atom when the electrons in it de-excite.
+Because the line spectra are discrete, this suggests that only certain changes in energies are possible in the atom, implying discrete energy levels
+$$hf=E_1-E_2$$
+Energies given in joules
+\subsubsection{Wave particle duality}
+\paragraph{Electron diffraction}
+When electrons are fired at a slit, they exhibit the same behaviour as light does, implying that particles can posses wave properties.
+\paragraph{The photoelectric effect}
+Because there is a threshold frequency for the photoelectric effect, light must have a particle nature, where one particle provides the energy to release the electron.
+If it had a wave nature, given enough time, an electron would be released, regardless of frequency
+\paragraph{The de Broglie Wavelength}
+$$\lambda=\frac{h}{p}=\frac{h}{mv}$$
+This causes the amount of diffraction to change based on the momentum of the particle, the greater the momentum, the smaller the wavelength, and so the less diffraction.
+\section{Waves}
+\subsection{Progressive and stationary waves}
+\subsubsection{Progressive waves}
+\textbf{Amplitude} - The maximum displacement of a vibrating particle\\
+\textbf{Frequency} - The number of cycles of a wave that pass a point per second\\
+\textbf{Period} - The time for one complete cycle of a wave to pass a point\\
+\textbf{Wavelength} - The least distance between two vibrating particles with the same displacement and velocity at the same time\\
+\textbf{Phase} - The position of a point in time on a waveform cycle\\
+\textbf{Phase difference} - The fraction of a cycle between the vibrations of two vibrating particles
+\subsubsection{Longitudinal and transverse waves}
+\paragraph{Transverse wave}
+\begin{tikzpicture}[scale=0.8]
+\tikzstyle{vlabel} = [fill=white,font=\footnotesize,inner sep=1pt,rotate=90]
+\tikzstyle{hlabel} = [fill=white,font=\normalsize,inner sep=1pt]
+\node[vlabel] at (1.2,6) {Amplitude};
+\draw[arrows=<->,red,ultra thick](1.35,4.2)--(1.35,7.6);
+\node[hlabel] at (7,3.3) {Wavelength};
+\draw[arrows=<->,red,ultra thick](3,3.6)--(8.9,3.6);
+
+\begin{axis}[
+    Axis Style,
+    y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
+    ylabel = {Displacement},
+    xlabel= {Distance},
+    ticks=none
+]
+\addplot [mark=none, ultra thick, black] {sin(deg(x))};
+\end{axis}
+\end{tikzpicture}
+\\
+\\
+Wave direction and energy are perpendicular
+\paragraph{Longitudinal wave}
+\begin{tikzpicture}[decoration={coil},scale=1.8]
+\tikzstyle{hlabel} = [fill=white,font=\normalsize,inner sep=1pt]
+\node[hlabel] at (5,0.8) {Wavelength};
+
+\draw[arrows=<->,red,ultra thick](3.26,0.5)--(6.74,0.5);
+\draw[arrows=->,red,ultra thick](3.26,-1)--(3.26,-0.5);
+\draw[arrows=->,red,ultra thick](8.5,-1)--(8.5,-0.5);
+\node[hlabel] at (3.26,-1.2) {Compression};
+\node[hlabel] at (8.5,-1.2) {Rarefaction};
+\draw[decorate, decoration={aspect=0.3, segment length=3mm, amplitude=3mm}] (0,0) --(3.03,0);
+\draw[decorate, decoration={aspect=0.3, segment length=0.5mm, amplitude=-3mm}] (3.03,0) -- (3.49,0); 
+\draw[decorate, decoration={aspect=0.3, segment length=3mm, amplitude=-3mm}] (3.48,0) -- (6.51,0);
+\draw[decorate, decoration={aspect=0.3, segment length=0.5mm, amplitude=-3mm}] (6.51,0) -- (6.97,0);
+\draw[decorate, decoration={aspect=0.3, segment length=3mm, amplitude=-3mm}] (6.97,0) -- (10,0);
+\end{tikzpicture}\\
+Wave direction and energy are parallel
+\paragraph{Polarisation}
+\begin{tikzpicture}[x={(0.866cm,-0.5cm)}, y={(0.866cm,0.5cm)}, z={(0cm,1cm)}, scale=.8,
+    %Option for nice arrows
+    >=stealth, %
+    inner sep=0pt, outer sep=2pt,%
+    axis/.style={thick,<-},
+    wave/.style={thick,color=#1,smooth},
+    polaroid/.style={fill=black!60!white, opacity=0.3},
+]
+    % Colors
+    \colorlet{darkgreen}{green!50!black}
+    \colorlet{lightgreen}{green!80!black}
+    \colorlet{darkred}{red!50!black}
+    \colorlet{lightred}{red!80!black}
+
+    % Frame
+    \coordinate (O) at (0, 0, 0);
+    \draw[axis] (O) -- +(14, 0,   0);
+    \draw[thick,dashed] (-2,0,0) -- (0,0,0);
+
+    % Electric field vectors
+    \draw[wave=blue, variable=\x,samples at={0,0.25,...,6}]
+        plot (\x,{sin(2*\x r)},0);
+    %Polarized light between polaroid and thin section
+    \foreach \x in{0, 0.25,...,6}
+        \draw[color=blue,->] (\x,0,0) -- (\x,{sin(2*\x r)},0);
+
+    \draw (3,1,1) node [text width=2.5cm, text centered]{Polarized light};
+
+    %Crystal thin section
+    \begin{scope}[thick]
+        \draw (6,-2,-1.5) -- (6,-2,1.5) node [above, sloped, midway]{Polarising filter}
+                -- (6, 2, 1.5) -- (6, 2, -1.5) -- cycle % First face
+            (6,  -2, -1.5) -- (6.2, -2,-1.5)
+            (6,   2, -1.5) -- (6.2,  2,-1.5)
+            (6,  -2,  1.5) -- (6.2, -2, 1.5)
+            (6,   2,  1.5) -- (6.2,  2, 1.5)
+            (6.2,-2, -1.5) -- (6.2, -2, 1.5) -- (6.2, 2, 1.5) 
+                -- (6.2, 2, -1.5) -- cycle; % Second face
+    \end{scope}
+
+    %Rays leaving thin section
+    \draw[wave=darkred,   variable=\x, samples at={6.2,6.45,...,12}] 
+        plot (\x, {0.26*0.26*sin(2*(\x-0.5) r)},  {0.966*0.26*sin(2*(\x-0.5) r)});  %n'g-oriented ray
+    \draw[wave=darkgreen, variable=\x, samples at={6.2,6.45,...,12}]
+        plot (\x, {0.966*0.966*sin(2*(\x-0.1) r)},{-0.26*0.966*sin(2*(\x-0.1) r)}); %n'p-oriented ray
+    \draw (10,1,1) node [text width=2.5cm, text centered] {Unpolarised light};
+
+    \foreach \x in{6.2,6.45,...,12} {
+        \draw[color=darkgreen, ->] (\x, 0, 0) --
+            (\x, {0.966*0.966*sin(2*(\x-0.1) r)}, {-0.26*0.966*sin(2*(\x-0.1) r)});
+        \draw[color=darkred,   ->] (\x, 0, 0) --
+            (\x, {0.26*0.26*sin(2*(\x-0.5) r)}, {0.966*0.26*sin(2*(\x-0.5) r)});
+            }
+\end{tikzpicture}\\
+Polarised light all travels in the same direction\\
+Unpolarised light travels in all directions\\
+Unpolarised light can be polarised using a polarising filter which contains stripes, only allowing one direction of light through\\
+\textbf{Only transverse waves can be polarised}
+\subsubsection{Principle of superposition of waves and formation of stationary waves}
+Stationary waves are formed when a wave collides with itself after reflection\\
+\\
+\\
+\begin{tikzpicture}
+\draw[black,ultra thick] (11.5,0.2) -- ++(0,3.1);
+\draw[black,ultra thick] (11.5,0.3) -- (12,0.7);
+\draw[black,ultra thick] (11.5,1) -- ++(0.5,0.4);
+\draw[black,ultra thick] (11.5,1.7) -- ++(0.5,0.4);
+\draw[black,ultra thick] (11.5,2.4) -- ++(0.5,0.4);
+\draw[black,ultra thick] (11.5,3.1) -- ++(0.5,0.4);
+\tikzstyle{hlabel} = [font=\normalsize,inner sep=1pt]
+\draw[arrows=->,red,ultra thick](3.26,3.5)--(6.74,3.5);
+\node[hlabel,red] at (5,3.7) {Incoming wave};
+\draw[arrows=<-,blue,ultra thick](3.26,-0.2)--(6.74,-0.2);
+\node[hlabel,blue] at (5,-0.4) {Reflected wave};
+\draw[arrows=->,orange,ultra thick](10.1,-0.7)-- ++(0,0.8);
+\node[hlabel,orange] at (10.1,-0.9) {Antinode};
+
+\draw[arrows=->,orange,ultra thick](8.65,4.5)-- ++(0,-2.5);
+\node[hlabel,orange] at (8.65,4.7) {Node};
+
+\begin{axis}[
+    Stationary Wave,
+    ticks=none,
+    axis line style={draw=none}
+]
+\addplot [mark=none, ultra thick, blue] {sin(deg(x))};
+\addplot [mark=none, ultra thick, red] {sin(deg(x+pi))};
+\end{axis}
+\end{tikzpicture}
+\\
+When both waves are at equilibrium there is a \textbf{node}\\
+When one wave is at a maximum and one at a minimum there is an \textbf{antinode}\\
+\\
+\textbf{Stationary wave} - Wave pattern with nodes and antinodes formed when two or more progressive waves of the same frequency and amplitude pass through each other\\
+\textbf{Node} - A fixed point in a stationary wave pattern where the amplitude is zero\\
+\textbf{Antinode} - A fixed point in a stationary wave pattern where the amplitude is a maximum
+\paragraph{Harmonics}
+$$f_1=\frac{1}{2l}\sqrt{\frac{T}{\mu}}$$
+T - String tension\\
+$\mu$ - Mass/Length\\
+\\
+The formula for the nth harmonic is:
+$$f_n=\frac{n}{2l}\sqrt{\frac{T}{\mu}}$$
+\subsection{Refraction, diffraction and interference}
+\subsubsection{Interference}
+\textbf{Path difference} - The difference in distances from two coherent sources to an interference fringe\\
+\textbf{Coherence} - Constant phase difference\\
+\includegraphics[width=8cm]{Interference.jpg}
+$$w=\frac{\lambda D}{s}$$
+w- Separation of fringes (Distance between adjacent brightest points etc)\\
+$\lambda$ - Wavelength\\
+D - Distance from slits to screen\\
+s - Separation of the two slits\\
+\includegraphics[width=8cm]{Diffraction_Colours.png}
+\subsubsection{Diffraction}
+\includegraphics[width=7cm]{Diffraction.png}\\
+Increasing the width of the slit causes the central maxima to get narrower, this can be remembered from the fringe spacing formula, remember the central maxima is double the width calculated using that formula though.
+\paragraph{Diffraction grating equation}
+\includegraphics[width=7cm]{nlambda_1.png}\\
+\includegraphics[width=7cm]{nlambda_2.png}\\
+Path difference =$d\sin\theta$\\
+$n\lambda=d\sin\theta$\\
+\\
+A diffraction grating can be used to analyse spectra
+\subsubsection{Refraction}
+\textbf{Refractive index} - $\frac{\textrm{Speed of light in free space}}{\textrm{Speed of light in that medium}}$\\
 

### 2018-06-02 Physics Notes/Paper 1/Paper 1.tex
Physics Notes Update

@@
 \subsubsection{Refraction}
-\textbf{Refractive index} - $\frac{\textrm{Speed of light in free space}}{\textrm{Speed of light in that medium}}$\\
+\textbf{Refractive index} - $\frac{\textrm{Speed of light in free space}}{\textrm{Speed of light in that medium}}$
+$$\textrm{Snell's law:} - n_1\sin\theta_1=n_2\sin\theta_2$$
+$$\sin\theta_c=\frac{n_1}{n_2}$$
+Total internal reflection occurs if the angle of incidence is \textbf{larger} than the critical value
+\paragraph{Fibre optics}
+\includegraphics[width=7cm]{Fibre_Optic_1.png}\\
+\includegraphics[width=7cm]{Fibre_Optic_2.jpg}\\
+\subsubsection{Modal Dispersion}
+Waves entering the fibre at different angles will reflect differently and so will have different path lengths
+\subsubsection{Material Dispersion}
+Different wavelengths of light enter the same but refract differently, causing a difference in path length
+\section{Mechanics and materials}
+\subsection{Forces, energy and momentum}
+\subsubsection{Moments}
+\textbf{Moment} - Force $\times$ perpendicular distance from the line of action of the force to the point\\
+\textbf{Couple} - A pair of equal and opposite coplanar forces
+$$\textrm{Moment of a couple}=Fd$$
+Where F is one of the forces, and d is the distance between them\\
+\textbf{Principle of moments} - For an object in equilibrium, the sum of clockwise moments equals the sum of anticlockwise moments\\
+\textbf{Centre of mass} - The point through which a single force on the body has no turning effect
+\subsubsection{Projectile motion}
+\paragraph{The effect of air resistance}
+\includegraphics[scale=0.25]{Air_Resistance.JPG}\\
+\textcolor{orange}{No Air Resistance}\\
+\textcolor{red}{Air resistance
+\begin{itemize}
+\item Steeper descent
+\item Peak Further Left
+\item Smaller Range
+\end{itemize}}
+\subsubsection{Newton's laws of motion}
+\textbf{1st law} - An object remains at rest or in uniform motion unless acted on by a resultant force\\
+\textbf{2nd law} - $F=ma$\\
+\textbf{3rd law} - Every action has an equal and opposite reaction
+\subsubsection{Momentum}
+\textbf{Momentum} - Mass$\times$Velocity\\
+\textbf{Impulse} - Change in momentum per second\\
+\textbf{Elastic collision} - No loss of kinetic energy\\
+\textbf{Inelastic collision} - Loss of kinetic energy
+\subsubsection{Work, energy and power}
+When \textbf{work} is done \textbf{energy} is transferred
+$$W=FS\cos\theta$$
+\subsubsection{Conservation of energy}
+\textbf{Principle of conservation of energy} - Energy cannot be created or destroyed
+\subsection{Materials}
+\subsubsection{Bulk properties of solids}
+\textbf{Hooke's law} - Force is proportional to extension, provided the proportionality limit has not been reached\\
+\textbf{Breaking stress (Ultimate tensile stress)} - Tensile stress needed to break a solid material\\
+\textbf{Plastic deformation} - Deformation of a solid beyond its elastic limit\\
+\textbf{Brittle} - Snaps without bending or stretching when subject to stress\\
+\textbf{Fracture} - The separation of a material into two or more pieces when subject to stress\\
+\includegraphics[width=6cm]{metal.jpg}
+\includegraphics[width=6cm]{rubber.jpg}
+\includegraphics[width=6cm]{Stress_Strain.jpg}
+\subsubsection{The Young Modulus}
+\textbf{Young Modulus} - Stress/Strain assuming the limit of proportionality has not been reached
+\section{Electricity}
+\subsection{Current electricity}
+\subsubsection{Basics of electricity}
+\textbf{Current} - The rate of flow of charge\\
+\textbf{Potential difference} - Work done per unit charge\\
+\textbf{Resistance} - Voltage/current
+\subsubsection{Current - Voltage characteristics}
+\paragraph{Ohmic Conductor}
+\begin{tikzpicture}
+\begin{axis}[axis lines=middle, ticks=none,scale=0.5,    ylabel = Current,xlabel=Voltage,ylabel style={rotate=90}
+]
+\addplot[color=black]{x};
+\end{axis}
+\end{tikzpicture}
+\paragraph{Bulb}
+\begin{tikzpicture}
+\begin{axis}[axis lines=middle, ticks=none,scale=0.5,    ylabel = Current,xlabel=Voltage,ylabel style={rotate=90}
+]
+\addplot[color=black,domain=-90:90]{sin(x)};
+\end{axis}
+\end{tikzpicture}
+\paragraph{Diode}
+\includegraphics[width=2in]{diode.jpeg}\\
+\textbf{Ohm's Law}: Current is proportional to voltage under constant physical conditions
+\subsubsection{Resistivity}
+\paragraph{The effect of temperature on conductors}
+The lower the temperature, the less the vibration of the atoms, and resistance reduces
+\textbf{Superconductor} - A material that has no electrical resistance\\
+\textbf{Critical temperature} - The temperature below which a conductor becomes a superconductor\\
+\\
+Superconductors are used for very high current applications.
+\subsubsection{Circuits}
+\paragraph{Resistor combinations}
+$$\textrm{Series}: R_T=R_1+R_2+R_3...$$
+$$\textrm{Parallel}: \frac{1}{R_T}=\frac{1}{R_1}+\frac{1}{R_2}+\frac{1}{R_3}+...$$
+\paragraph{Voltage in series and parallel}
+Parallel: Voltage across components in parallel is the same\\
+Series: The total voltage across all the components is the voltage supplied
+\paragraph{Current in series and parallel}
+The current entering a component or junction is the same as the current leaving the component, meaning current in series is the same for each component.\\
+For parallel circuits, use voltage and resistance to calculate
+\paragraph{Power}
+$$P=\frac{E}{t}$$
+\paragraph{Kirchoff's laws}
+Current in=Current out (Conservation of charge)\\
+The sum of all the voltages around the system is zero (Conservation of energy)
+\subsubsection{Potential divider}
+$$V_{Out}=V_{In}\frac{R_2}{R_1+R_2}$$
+Potential dividers can be used with environment sensors that change their resistance based on changed to the environment to change output voltage
+\subsubsection{The electromotive force and internal resistance}
+\textbf{Electromotive force} - The amount of electrical energy per unit charge produced inside a source of electrical energy\\
+\textbf{Internal resistance} - Resistance inside a source of electrical energy\\
+\textbf{Terminal pd} - The potential difference across the terminals of a power supply\\
+\begin{tikzpicture}
+\begin{axis}[axis lines=middle,scale=0.5,    ylabel = Vr,xlabel=Current,ylabel style={rotate=90,anchor=south},xlabel style={anchor=south},xmin=0,xmax=7,ymin=0,ymax=7,xtick={5},xticklabels={Short Circuit Current},ytick={5},yticklabels={$\epsilon$}
+]
+\addplot[color=black,domain=0:5]{-x+5};
+\end{axis}
+\end{tikzpicture}
+\\
+The equation of this line can be derived from:
+$$\epsilon=I(R+r)$$
+Remember that the terminal voltage is $Ir$
 

### 2018-06-05 Maths Notes/Further Pure/FP2/Cheat Sheet/FP2 Cheat Sheet.tex
FP2 Cheat Sheet

@@
 $$z^n-\frac{1}{z^n}=2i\sin n\theta$$
+These can be calculated by using DMs theorem to find $z^{-1} =\frac{1}{z}$ then adding or subtracting
 \subsubsection{Multiples of $\theta\rightarrow$ Powers of cos/sin}
@@
 {\renewcommand{\arraystretch}{2}
-\begin{tabularx}{\textwidth}{|X|X|}
+\begin{tabularx}{\textwidth}{|X|X|X|}
 \hline
-\textbf{Solution to auxiliary equation}&\textbf{General solution}\\
+\textbf{Solution to auxiliary equation}&\textbf{General solution}&\textbf{Trig general solution}\\
 \hline
-Two real roots $b^2>4ac$&$Ae^{\alpha x}+Be^{\beta x}$\\
+Two real roots $b^2>4ac$&$Ae^{\alpha x}+Be^{\beta x}$&\\
 \hline
-One real root $b^2=4ac$&$(A+bx)e^{\alpha x}$\\
+One real root $b^2=4ac$&$(A+bx)e^{\alpha x}$&\\
 \hline
-Imaginary only root $b^2<4ac$&$y=Ae^{\alpha x}+Be^{-\alpha x}$\\
+Imaginary only root $b^2<4ac$&$Ae^{\alpha x}+Be^{-\alpha x}$&
+$p\cos\alpha x+q\sin\alpha x$
+\\
 \hline
-Complex root $b^2<4ac$&$y=Ae^{(\beta+\alpha i)x}+Be^{(\beta-\alpha i)x}$\\
+Complex root $b^2<4ac$&$Ae^{(\beta+\alpha i)x}+Be^{(\beta-\alpha i)x}$&
+$e^{\beta x}(p\cos\alpha x+q\sin\alpha x)$
+\\
 \hline
 \end{tabularx}}
+P=A+B\\
+Q=i(A+B)
 \subsection{Second ODE=f(x)}

### 2018-06-05 Physics Notes/Paper 1/Paper 1.tex

@@
     xmin=0, xmax=13.0,
+    domain=-4*pi:4*pi
+}}
+
+\pgfkeys{/pgfplots/Axis Style 2/.style={
+    width=13.5cm, height=5cm,
+    axis x line=center, 
+    axis y line=middle, 
+    samples=100,
+    ymin=-1.5, ymax=1.5,
+    xmin=0, xmax=14.0,
     domain=-4*pi:4*pi
@@
 \paragraph{The effect of temperature on conductors}
-The lower the temperature, the less the vibration of the atoms, and resistance reduces
+The lower the temperature, the less the vibration of the atoms, and resistance reduces\\
 \textbf{Superconductor} - A material that has no electrical resistance\\
@@
 Remember that the terminal voltage is $Ir$
+\newpage
+\section{Periodic motion}
+\subsection{Circular motion}
+As circular motion has a constant speed but a changing direction, it is implied that there is a force perpendicular to the direction of motion, and so an acceleration\\
+$v$ (Velocity)- Displacement per unit time\\
+$\omega$ (Angular velocity)- Angle per unit time\\
+\subsection{Simple harmonic motion}
+\begin{tikzpicture}
+\begin{axis}[
+    Axis Style 2,
+    xtick={
+        3.14159,6.28319,9.42478,12.56637
+    },
+    xticklabels={
+        $\dfrac{T}{2}$,T,$\dfrac{3T}{2}$,2T
+    },
+    ytick={-1,1},
+    yticklabels={-A,A},
+    y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
+    ylabel = {Displacement, x},
+    xlabel= {Time, t}
+]
+\addplot [mark=none, ultra thick, black] {cos(deg(x))};
+\end{axis}
+\end{tikzpicture}
+$x=Acos(\omega t)$
+\\
+\begin{tikzpicture}
+\begin{axis}[
+    Axis Style 2,
+    xtick={
+        3.14159,6.28319,9.42478,12.56637
+    },
+    xticklabels={
+        $\dfrac{T}{2}$,T,$\dfrac{3T}{2}$,2T
+    },
+    ytick={-1,1},
+    yticklabels={$-\omega A$,$\omega A$},
+    y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
+    ylabel = {Velocity, v},
+    xlabel= {Time, t}
+]
+\addplot [mark=none, ultra thick, black] {-sin(deg(x))};
+\end{axis}
+\end{tikzpicture}
+$v=-\omega A\sin(\omega t)$
+\\
+\begin{tikzpicture}
+\begin{axis}[
+    Axis Style 2,
+    xtick={
+        3.14159,6.28319,9.42478,12.56637
+    },
+    xticklabels={
+        $\dfrac{T}{2}$,T,$\dfrac{3T}{2}$,2T
+    },
+    ytick={-1,1},
+    yticklabels={$-\omega^2 A$,$\omega^2 A$},
+    y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
+    ylabel = {Acceleration, a},
+    xlabel= {Time, t}
+]
+\addplot [mark=none, ultra thick, black] {-cos(deg(x))};
+\end{axis}
+\end{tikzpicture}
+$a=-\omega^2A\cos(\omega t)$\\
+\\
+All these equations can be derived from the equation $x=A\cos(\omega t)$, by differentiating it with respect to time.\\
+The maximum values of each of them can be found as the maximum value of cos or sin is 1
+\subsection{Simple harmonic systems}
+\subsubsection{Energy in SHM}
+\begin{tikzpicture}
+\begin{axis}[
+    Axis Style 2,
+    xtick={
+        3.14159,6.28319
+    },
+    xticklabels={
+        $\dfrac{T}{2}$,T
+    },
+    ytick={1},
+    yticklabels={$\frac{1}{2}m\omega^2A^2$},
+    y label style={at={(axis description cs:-0,.25)},rotate=90,anchor=south},
+    ylabel = {Energy/J},
+    xlabel= {Time, t},
+    x label style={at={(axis description cs:1.12,0)},anchor=east},
+    xmax=6.28319,
+    ymin=0
+]
+\addplot [mark=none, ultra thick, black,samples=200] {(cos(deg(x)))^2};
+\addplot [mark=none, ultra thick, red,samples=200] {(sin(deg(x)))^2};
+\end{axis}
+\end{tikzpicture}
+\\
+Red - Kinetic Energy\\
+Black - Gravitational potential energy\\
+\\
+\begin{tikzpicture}
+\begin{axis}[ymin=0,ticks=none,xlabel={Displacement,x/m},ylabel={Energy/J}]
+\addplot [mark=none, ultra thick, black,samples=200] {x^2};
+\addplot [mark=none, ultra thick, red,samples=200] {-x^2+25};
+\draw[ultra thin] (axis cs:0,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:0,\pgfkeysvalueof{/pgfplots/ymax});
+\end{axis}
+\end{tikzpicture}
+\subsubsection{Period of a mass-spring system}
+The period of a mass-spring system is $T=2\pi\sqrt{\dfrac{m}{k}}$ or $T^2=\dfrac{4\pi^2m}{k}$\\
+\begin{tikzpicture}[scale=0.5]
+\begin{axis}[ymin=-0.001,ticks=none,ylabel=$T^2/s^2$,xlabel=$m/kg$,axis lines=middle,
+label style={font=\large}
+]
+\addplot[mark=none]{x};
+\end{axis}
+\end{tikzpicture}\\
+The gradient is $\dfrac{4\pi^2}{k}$\\
+The line passes through the origin\\
+This is only true for small oscillations as large oscillations go past the limit of proportionality
+\subsubsection{Energy in a vertically oscillating spring}
+\begin{tabular}{|c|c|c|c|}
+\hline
+&KE&GPE&Elastic Energy\\
+\hline
+Top&0&$2mgA$&$\frac{1}{2}k(e-A)^2$\\
+\hline
+Middle&Max=$\frac{1}{2}m\omega^2A^2$&$mgA$&$\frac{1}{2}ke^2$\\
+\hline
+Bottom&0&0&$\frac{1}{2}k(e+A)^2$\\
+\hline
+\end{tabular}
+
+\subsubsection{Damping}
+Damping is the reduction in amplitude due to energy losses (e.g. overcoming friction).\\
+\\
+It will also cause the period to increase (it is essentially a driver).\\
+\\
+\textbf{Light(underdamping)} - Small amplitude change per oscillation\\
+\textbf{Heavy(underdamping)} - Large amplitude change per oscillation\\
+\\
+\textbf{Critical damping} - Reaches equilibrium in the shortest possible time \textbf{without} oscillating\\
+\\
+\textbf{Over damping} - Reaches equilibrium after a long period of time
+\paragraph{Damping graph}
+\begin{tikzpicture}
+\begin{axis}[axis lines=middle,samples=200,ymax=10,ticks=none,ylabel=Amplitude,ylabel style={rotate=90, anchor=south,at={(axis description cs:0,0.42)},},xlabel=Time,x label style={at={(axis description cs:1.1,0.42)},anchor=east},]
+\addplot[blue,domain=0:21] {1/x};\addlegendentry{Critically Damped}
+\addplot[red,domain=0.01:20.58] {78*sin(deg(x+7.7))/(x+7.7)};\addlegendentry{Under Damped}
+\addplot[green,domain=0.01:21] {-3*ln(x+2)+12};\addlegendentry{Over damped}
+\end{axis}
+\end{tikzpicture}
+\subsection{Forced vibrations and resonance}
+\textbf{Free vibrations} - Vibrations where there is no damping and no periodic force acting on the system, amplitude of the oscillations is constant\\
+\textbf{Forced vibrations} - Vibrations of a system subjected to an external periodic force
+\subsubsection{The effects of damping on the sharpness of resonance}
+\includegraphics[width=8cm]{damp_6.jpg}\\
+The less damping there is, the sharper the resonance
+\subsubsection{Standing waves}
+Standing waves can be produced at the resonant (natural) frequencies of a material, causing point on it to alternate between minimum and maximum amplitude, causing solid materials such as concrete to break.
 

### 2018-06-05 Maths Notes/Further Pure/FP2/Cheat Sheet/FP2 Cheat Sheet.tex
FP2 Notes

@@
 \end{itemize}
-
+Argument equations:
+For lines, check by looking at the graph, but use
+$$\frac{Im}{R_e}=\tan\theta$$
+Remove the i from the imaginary part when putting it in the fraction, but remember that x and y are supposed to stay\\
+For circles, find the centre and radius, and use this to form the equation, though remember to include $y>0$, where often necessary as it is an arc from the x axis
 \subsection{Translations}
@@
 Complex root $b^2<4ac$&$Ae^{(\beta+\alpha i)x}+Be^{(\beta-\alpha i)x}$&
-$e^{\beta x}(p\cos\alpha x+q\sin\alpha x)$
+$e^{\beta x}(P\cos\alpha x+Q\sin\alpha x)$
 \\

### 2018-06-06 Physics Notes/Paper 2/Paper 2.tex
Physics 2 notes

@@
 \subsubsection{Nuclear radius}
-\paragraph{Closest approach of alpha particles}
+\paragraph{Deflection}
 By determining the percentage of $\alpha$ particles that are deflected by more than 90\degree, around 1 in 10,000.
@@
 The value of R can be found, $\lambda$ is the wavelength of the electrons
+\paragraph{Closest approach of alpha particles}
+For this, use coulomb's equation:
+$$F=\frac{1}{4\pi\epsilon_0}\frac{Q_1Q_2}{r^2}$$
+\paragraph{Derivation of \large$\mathlarger{R=r_0A^{\frac{1}{3}}}$}
+$r_0$ is a constant $1.05fm$\\
+$R$ is the radius of the nucleus\\
+$A$ is mass number (not activity)\\
+\\
+Plotting a graph of $\ln R$ against $\ln A$ gives a straight line with gradient $\frac{1}{3}$ and y intercept $\ln r_0$, this gives the equation
+$$\ln R=\frac{1}{3}\ln A+\ln r_0$$
+By combining the logs, then doing e to both sides, it can be shown that
+$$R=r_0A^{\frac{1}{3}}$$
+\paragraph{Nuclear density}
+$$V=\frac{4}{3}\pi R^3=\frac{4}{3}\pi(r_0 A^{\frac{1}{3}})^3=\frac{4}{3}\pi r_0^3A$$
+$$\textrm{Density}=\frac{\textrm{Mass}}{\textrm{Volume}}=\frac{Au}{\frac{4}{3}\pi r_0^3 A}=\frac{u}{\frac{4}{3}\pi r_0^3}=\frac{1.661\times 10^{27}}{\frac{4}{3}\pi(1.05\times10^{-15})^3}=3.4\times10^{17}kgm^{-3}$$
+\subsubsection{Mass and energy}
+\paragraph{Mass difference and binding energy}
+The \textbf{binding energy} of the nucleus is the work that must be done to separate a nucleus into its constituent neutrons and protons.\\
+\\
+\subparagraph{Example Calculation}
+
+Nucleus of an isotope $^A_ZX$ has:\\
+Z Protons\\
+A-Z Neutrons\\
+Mass=$M_{NUC}$
+$$\textrm{Mass defect:} \ \Delta m=Zm_p+(A-Z)m_n-M_{NUC}$$
+Where:\\
+$m_p=\textrm{Mass of proton} \quad m_n=\textrm{Mass of neutron}$
+\\
+\\
+\textit{The polonium isotope $^{210}_{84}Po$ emits $\alpha$ particles and decays to form the stable isotope of lead $^{206}_{82}Pb$.
+Write down an equation to represent this process and calculate the energy released when a $^{210}_{84}Po$ nucleus emits an $\alpha$ particle.\\
+Mass of a $^{210}_{84}Po$ Nucleus=$209.93667u$\\
+Mass of a $^{206}_{82}Pb$ Nucleus=$205.92936u$\\
+Mass of a $\alpha$ particle=$4.00150u$\\
+$1u=931.3MeV$}\\
+$$^{206}_{82}Pb\rightarrow \ ^4_2\alpha+^{206}_{82}Pb+\textrm{Energy released}$$
+$$\textrm{Mass difference}=\textrm{Total initial mass-total final mass}$$
+$$\textrm{Mass difference}=209.93667-(205.92936+4.00150)$$
+$$\textrm{Mass difference}=5.81\times10^{-3}u$$
+$$\textrm{Energy released:}\ Q=\textrm{Mass difference in u}\times931.3=5.41MeV$$ 
+\subparagraph{Binding energy}
+$$E=\Delta mc^2$$
+\paragraph{Fission and fusion}
+\includegraphics[width=10cm]{Binding_Energy.jpg}\\
+In \textbf{nuclear fission} a large unstable nucleus splits into two more stable fragments,  binding energy per nucleon increases.\\
+In \textbf{nuclear fusion} two small nuclei fuse to form a larger nucleus with increased binding energy per nucleon\\
+Note that the gradient for fusion is much larger than for fusion, meaning that more energy is released in a fusion reaction than a fission reaction.
+\subsubsection{Induced fission}
+\textbf{Critical mass} - The minimum mass of the fissile isotope in a nuclear reactor necessary to produce a chain reaction\\
+\\
+The process:\\
+\includegraphics[width=6cm]{chain_reaction.png}\\
+\\
+Components of a nuclear reactor:
+\begin{itemize}
+\item Moderator - Slows the neutrons down so they can go on to produce further fission
+\item Control rods - Rods made of a neutron absorbing substance that are move in or out of the core of a nuclear reactor to control the rate of fission events in the reactor
+\item Coolant - A fluid used to prevent the reactor becoming dangerously hot
+\end{itemize}
+Neutrons undergo elastic collisions with the particles of the moderator, this causes the kinetic energy to transfer from the neutrons to the particles of the moderator, causing the neutrons to slow down.
+\paragraph{Factors affecting the choice of materials for the moderator, control rods and coolant}
+Moderator:
+\begin{itemize}
+\item Available in large amounts
+\item Small/light nuclei
+\item Not become radioactive when bombarded by neutrons
+\item High meting point if a solid is used
+\end{itemize} $ $\\
+Control rods:
+\begin{itemize}
+\item Absorb neutrons
+\item Have a high melting point
+\end{itemize} $ $\\
+Coolant:
+\begin{itemize}
+\item High specific heat capacity
+\item Non corrosive
+\item Stable at high temperatures
+\end{itemize}
+\subsubsection{Safety aspects}
+\begin{itemize}
+\item Thick steel reactor core to withstand high pressure/temperature and to absorb $\beta$ radiation and some $\gamma$ radiation and neutrons
+\item Building has thick concrete walls to absorb neutrons and $\gamma$ radiation
+\item Control rods to stop the reactions in an emergency
+\item Fuel rods removed by remote handling devices
+\end{itemize}
 \end{document}

### 2018-06-12 Maths Notes/Mechanics/M2/Cheat Sheet/M2 Cheat Sheet.tex
M2 Notes

@@
 \lhead{A Level Maths - M2}
+
+\usetikzlibrary{positioning} %Used for diagram at bottom
 
@@
 $$y=x^2\Bigg(\frac{-g}{2v^2\cos^2\alpha}\Bigg)+x\Big(\tan\alpha\Big)$$
+\section{Variable acceleration using differentiation and integration}
+When using more than 1 dimension, consider each component separately \\
+\begin{center}
+\begin{tikzpicture}
+  \node (disp) {\textbf{Displacement} $x$};
+  \node[right=2cm of disp] (vel) {\textbf{Velocity} $v$};
+  \node[right=2cm of vel] (acc) {\textbf{Acceleration} $a$};
+  \draw[-stealth,shorten >= 2pt] (disp.north) to[bend left] node[midway,above] {Differentiate} (vel.north);
+  \draw[-stealth] (vel.south) to[bend left] node[midway,below] {Integrate} (disp.south);
+  \draw[-stealth,shorten >= 2pt] (vel.north) to[bend left] node[midway,above] {Differentiate} (acc.north);
+    \draw[-stealth] (acc.south) to[bend left] node[midway,below] {Integrate} (vel.south);
+\end{tikzpicture}
+\end{center}
 \end{document}

### 2018-06-19 Maths Notes/Core/C3/Cheat sheet/C3 Cheat Sheet.tex
C3 Cheat Sheet
C3 Notes update

@@
 $a\sin\theta\pm b\cos\theta$ can be expressed in the form $R\sin(\theta\pm\alpha)$\\
-$a\cos\theta\pm b\sin\theta$ can be expressed in the form $R\sin(\theta\mp\alpha)$\\
+$a\cos\theta\pm b\sin\theta$ can be expressed in the form $R\cos(\theta\mp\alpha)$\\
 Where: 
@@
 $$\frac{dy}{dx}=\frac{dy}{du}\times\frac{du}{dx}$$
+\subsection{Parallel to the y axis}
+For a line to be parallel to the y axis, the gradient must be infinite, this would arise from dividing by zero, so if the function does this, the value at x at which this occurs is the tangent
 \end{document}

### 2018-06-27 Physics Notes/A2 Level/Nuclear Physics/Radioactivity/Radioactivity.tex
Tidied for upload to PMT

--- 2018-04-06 Physics Notes/Nuclear Physics/Radioactivity/Radioactivity.tex
@@
 \documentclass{article}[18pt]
-\usepackage{/home/sam/Documents/School_Notes/format}
+\usepackage{../../../format}
 \lhead{A Level Physics - Nuclear Physics}
@@
 A thermocouple attached to the container produces electricity of the container being warm.
+\section{Inverse square law for $\gamma$}
+$$\textrm{Intensity}\propto\frac{1}{d^2}$$
+$$I=\frac{k}{x^2}$$
+\section{Liquid drop model}
+This uses a water droplet as a model for the nucleus\\
+Molecules of water are held together by short range forces - similar to the nucleus\\
+\\
+It can become more stable by splitting into two smaller spherical droplets\\
+\\
+When a nucleus absorbs a neutron, oscillations can be set up which cause elongation.
+
 \end{document}

### 2018-06-27 Physics Notes/A2 Level/Turning Points/Overall Notes/Turning Points.tex
Tidied for upload to PMT

--- 2018-04-25 Physics Notes/Turning Points/Overall Notes/Turning Points.tex
@@
 \\
-\textbf{Reflection} - These corpuscles have perfectly elastic collisions, meaning that the speed before is the speed after.
+\textbf{Reflection} - There is a short range repulsive force.
+These corpuscles have perfectly elastic collisions, meaning that the speed before is the speed after.
 The horizontal velocity doesn't change, the vertical velocity is inverted.
@@
 \subsubsection{Einstein's Explanation of photoelectricity}
-Einstein showed electrons must have energy greater than the work function in order to escape a metal. Kinetic energy is the energy difference between the energy of the electron and the work function.
+Einstein showed electrons must have energy greater than the work function in order to escape a metal.
+Kinetic energy is the energy difference between the energy of the electron and the work function.\\
+\\
+The stopping potential is the potential at which no current flows, and is calculated by:
+$$V_s=\frac{E_{K(Max)}}{e}$$
+The stopping potential causes no current to flow as it creates an electric field which attracts the electrons back to the plate.
 \subsection{The significance of Young's double slit experiment}
